### 2022-12-02 writing/main.tex

\documentclass{article}
\usepackage{graphicx, setspace, booktabs, float, xcolor, rotating, lscape, lscape, sectsty, rotating}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper, portrait, margin=0.8in]{geometry}
\usepackage[shortlabels]{enumitem}
\usepackage[round, sort]{natbib}

\doublespacing

\title{Thesis Updates}
\author{Arjun}
\date{December 2, 2022}

\begin{document}
\input{output/01_exploratory/tables/summary_statistics.tex}

\input{}

\end{document}

### 2022-12-07 output/01_exploratory/tables/bldg_val_results_table.tex
Created estimation tables

{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabular}{l*{4}{c}}
\toprule
                    &\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}\\
\midrule
judgment\_for\_plaintiff&   2434984.3\sym{***}&   1161294.0\sym{*}  &   1161294.0\sym{*}  &   1055231.1         \\
                    &      (4.14)         &      (2.56)         &      (2.56)         &      (0.46)         \\
\addlinespace
file\_year=2019      &                     &           0         &           0         &                     \\
                    &                     &         (.)         &         (.)         &                     \\
\addlinespace
file\_year=2020      &                     &    192394.9         &    192394.9         &                     \\
                    &                     &      (0.41)         &      (0.41)         &                     \\
\addlinespace
file\_year=2021      &                     &   1461400.9         &   1461400.9         &                     \\
                    &                     &      (0.80)         &      (0.80)         &                     \\
\addlinespace
Abington            &                     &           0         &           0         &                     \\
                    &                     &         (.)         &         (.)         &                     \\
\addlinespace
Acton               &                     &  -6165616.0         &  -6165616.0         &                     \\
                    &                     &     (-0.97)         &     (-0.97)         &                     \\
\addlinespace
Adams               &                     & -21444727.6\sym{***}& -21444727.6\sym{***}&                     \\
                    &                     &     (-5.94)         &     (-5.94)         &                     \\
\addlinespace
Agawam              &                     & -18038332.4\sym{***}& -18038332.4\sym{***}&                     \\
                    &                     &     (-3.80)         &     (-3.80)         &                     \\
\addlinespace
Amesbury            &                     & -19407326.1\sym{**} & -19407326.1\sym{**} &                     \\
                    &                     &     (-3.07)         &     (-3.07)         &                     \\
\addlinespace
Amherst             &                     & -11242459.5\sym{*}  & -11242459.5\sym{*}  &                     \\
                    &                     &     (-2.45)         &     (-2.45)         &                     \\
\addlinespace
Andover             &                     &  -2085030.0         &  -2085030.0         &                     \\
                    &                     &     (-0.60)         &     (-0.60)         &                     \\
\addlinespace
Athol               &                     & -21616109.3\sym{***}& -21616109.3\sym{***}&                     \\
                    &                     &     (-4.16)         &     (-4.16)         &                     \\
\addlinespace
Attleboro           &                     & -19494997.4\sym{***}& -19494997.4\sym{***}&                     \\
                    &                     &     (-5.39)         &     (-5.39)         &                     \\
\addlinespace
Auburn              &                     & -21471031.4\sym{***}& -21471031.4\sym{***}&                     \\
                    &                     &     (-3.67)         &     (-3.67)         &                     \\
\addlinespace
Bedford             &                     &   2478285.3         &   2478285.3         &                     \\
                    &                     &      (0.42)         &      (0.42)         &                     \\
\addlinespace
Belchertown         &                     & -20404418.7\sym{***}& -20404418.7\sym{***}&                     \\
                    &                     &     (-5.40)         &     (-5.40)         &                     \\
\addlinespace
Bellingham          &                     &  18138281.2\sym{**} &  18138281.2\sym{**} &                     \\
                    &                     &      (3.10)         &      (3.10)         &                     \\
\addlinespace
Beverly             &                     & -14079413.5\sym{***}& -14079413.5\sym{***}&                     \\
                    &                     &     (-4.85)         &     (-4.85)         &                     \\
\addlinespace
Billerica           &                     &   6526049.6         &   6526049.6         &                     \\
                    &                     &      (1.83)         &      (1.83)         &                     \\
\addlinespace
Braintree           &                     &  22784206.9\sym{***}&  22784206.9\sym{***}&                     \\
                    &                     &      (6.46)         &      (6.46)         &                     \\
\addlinespace
Brewster            &                     & -20607212.4\sym{**} & -20607212.4\sym{**} &                     \\
                    &                     &     (-3.26)         &     (-3.26)         &                     \\
\addlinespace
Bridgewater         &                     &   9388781.6\sym{**} &   9388781.6\sym{**} &                     \\
                    &                     &      (2.95)         &      (2.95)         &                     \\
\addlinespace
Brockton            &                     & -17475780.0\sym{***}& -17475780.0\sym{***}&                     \\
                    &                     &     (-7.32)         &     (-7.32)         &                     \\
\addlinespace
Brookline           &                     & -16179317.8\sym{**} & -16179317.8\sym{**} &                     \\
                    &                     &     (-2.77)         &     (-2.77)         &                     \\
\addlinespace
Cambridge           &                     &  26938732.3\sym{***}&  26938732.3\sym{***}&                     \\
                    &                     &      (7.34)         &      (7.34)         &                     \\
\addlinespace
Canton              &                     &   3432893.5         &   3432893.5         &                     \\
                    &                     &      (0.99)         &      (0.99)         &                     \\
\addlinespace
Chelmsford          &                     &  -4604628.5         &  -4604628.5         &                     \\
                    &                     &     (-0.73)         &     (-0.73)         &                     \\
\addlinespace
Chelsea             &                     &  -3808897.8         &  -3808897.8         &                     \\
                    &                     &     (-0.88)         &     (-0.88)         &                     \\
\addlinespace
Chicopee            &                     & -19004695.9\sym{***}& -19004695.9\sym{***}&                     \\
                    &                     &     (-6.87)         &     (-6.87)         &                     \\
\addlinespace
Clinton             &                     & -21059441.8\sym{***}& -21059441.8\sym{***}&                     \\
                    &                     &     (-4.43)         &     (-4.43)         &                     \\
\addlinespace
Concord             &                     &  29495396.8\sym{***}&  29495396.8\sym{***}&                     \\
                    &                     &      (5.04)         &      (5.04)         &                     \\
\addlinespace
Danvers             &                     &  -5577347.4         &  -5577347.4         &                     \\
                    &                     &     (-1.29)         &     (-1.29)         &                     \\
\addlinespace
Dracut              &                     & -19485987.8\sym{***}& -19485987.8\sym{***}&                     \\
                    &                     &     (-4.52)         &     (-4.52)         &                     \\
\addlinespace
Dudley              &                     & -21722608.3\sym{***}& -21722608.3\sym{***}&                     \\
                    &                     &     (-3.96)         &     (-3.96)         &                     \\
\addlinespace
Duxbury             &                     & -15198237.7\sym{**} & -15198237.7\sym{**} &                     \\
                    &                     &     (-2.77)         &     (-2.77)         &                     \\
\addlinespace
East Wareham        &                     & -15344281.4\sym{**} & -15344281.4\sym{**} &                     \\
                    &                     &     (-2.62)         &     (-2.62)         &                     \\
\addlinespace
Everett             &                     &  -7534870.7\sym{*}  &  -7534870.7\sym{*}  &                     \\
                    &                     &     (-2.05)         &     (-2.05)         &                     \\
\addlinespace
Fairhaven           &                     & -21231090.0\sym{***}& -21231090.0\sym{***}&                     \\
                    &                     &     (-5.71)         &     (-5.71)         &                     \\
\addlinespace
Fall River          &                     & -18210525.7\sym{***}& -18210525.7\sym{***}&                     \\
                    &                     &     (-7.32)         &     (-7.32)         &                     \\
\addlinespace
Feeding Hills       &                     & -18650234.9\sym{***}& -18650234.9\sym{***}&                     \\
                    &                     &     (-5.23)         &     (-5.23)         &                     \\
\addlinespace
Fitchburg           &                     & -20960701.9\sym{***}& -20960701.9\sym{***}&                     \\
                    &                     &     (-8.30)         &     (-8.30)         &                     \\
\addlinespace
Foxboro             &                     &  20690798.8\sym{***}&  20690798.8\sym{***}&                     \\
                    &                     &      (4.35)         &      (4.35)         &                     \\
\addlinespace
Foxborough          &                     &  19142493.9\sym{**} &  19142493.9\sym{**} &                     \\
                    &                     &      (3.03)         &      (3.03)         &                     \\
\addlinespace
Framingham          &                     &  -2290752.1         &  -2290752.1         &                     \\
                    &                     &     (-0.83)         &     (-0.83)         &                     \\
\addlinespace
Franklin            &                     &  -4710134.2         &  -4710134.2         &                     \\
                    &                     &     (-1.25)         &     (-1.25)         &                     \\
\addlinespace
Gardner             &                     & -18492792.1\sym{***}& -18492792.1\sym{***}&                     \\
                    &                     &     (-5.24)         &     (-5.24)         &                     \\
\addlinespace
Gloucester          &                     & -14776186.1\sym{***}& -14776186.1\sym{***}&                     \\
                    &                     &     (-4.80)         &     (-4.80)         &                     \\
\addlinespace
Grafton             &                     & -11539053.6         & -11539053.6         &                     \\
                    &                     &     (-1.82)         &     (-1.82)         &                     \\
\addlinespace
Greenfield          &                     & -19186461.0\sym{***}& -19186461.0\sym{***}&                     \\
                    &                     &     (-4.88)         &     (-4.88)         &                     \\
\addlinespace
Hanson              &                     & -21517852.4\sym{***}& -21517852.4\sym{***}&                     \\
                    &                     &     (-3.40)         &     (-3.40)         &                     \\
\addlinespace
Haverhill           &                     & -18493946.4\sym{***}& -18493946.4\sym{***}&                     \\
                    &                     &     (-6.52)         &     (-6.52)         &                     \\
\addlinespace
Holyoke             &                     & -19922013.6\sym{***}& -19922013.6\sym{***}&                     \\
                    &                     &     (-7.02)         &     (-7.02)         &                     \\
\addlinespace
Hudson              &                     & -21242768.8\sym{***}& -21242768.8\sym{***}&                     \\
                    &                     &     (-3.63)         &     (-3.63)         &                     \\
\addlinespace
Hull                &                     & -14403896.8\sym{***}& -14403896.8\sym{***}&                     \\
                    &                     &     (-3.67)         &     (-3.67)         &                     \\
\addlinespace
Hyannis             &                     & -19591284.6\sym{***}& -19591284.6\sym{***}&                     \\
                    &                     &     (-4.27)         &     (-4.27)         &                     \\
\addlinespace
Indian Orchard      &                     & -20946341.5\sym{***}& -20946341.5\sym{***}&                     \\
                    &                     &     (-7.04)         &     (-7.04)         &                     \\
\addlinespace
Ipswich             &                     & -19517731.6\sym{***}& -19517731.6\sym{***}&                     \\
                    &                     &     (-3.94)         &     (-3.94)         &                     \\
\addlinespace
Lakeville           &                     & -17182100.0\sym{***}& -17182100.0\sym{***}&                     \\
                    &                     &     (-3.88)         &     (-3.88)         &                     \\
\addlinespace
Lawrence            &                     & -18777158.2\sym{***}& -18777158.2\sym{***}&                     \\
                    &                     &     (-7.91)         &     (-7.91)         &                     \\
\addlinespace
Leominster          &                     & -17218870.0\sym{***}& -17218870.0\sym{***}&                     \\
                    &                     &     (-5.85)         &     (-5.85)         &                     \\
\addlinespace
Lowell              &                     & -15677026.1\sym{***}& -15677026.1\sym{***}&                     \\
                    &                     &     (-6.66)         &     (-6.66)         &                     \\
\addlinespace
Ludlow              &                     & -20818614.1\sym{***}& -20818614.1\sym{***}&                     \\
                    &                     &     (-5.20)         &     (-5.20)         &                     \\
\addlinespace
Lunenburg           &                     & -21732251.2\sym{***}& -21732251.2\sym{***}&                     \\
                    &                     &     (-3.44)         &     (-3.44)         &                     \\
\addlinespace
Lynn                &                     & -18818313.7\sym{***}& -18818313.7\sym{***}&                     \\
                    &                     &     (-7.06)         &     (-7.06)         &                     \\
\addlinespace
Lynnfield           &                     &  -3055971.2         &  -3055971.2         &                     \\
                    &                     &     (-0.48)         &     (-0.48)         &                     \\
\addlinespace
Malden              &                     &    998329.8         &    998329.8         &                     \\
                    &                     &      (0.35)         &      (0.35)         &                     \\
\addlinespace
Mansfield           &                     & -13438414.8\sym{***}& -13438414.8\sym{***}&                     \\
                    &                     &     (-3.43)         &     (-3.43)         &                     \\
\addlinespace
Marblehead          &                     & -20700912.8\sym{***}& -20700912.8\sym{***}&                     \\
                    &                     &     (-4.36)         &     (-4.36)         &                     \\
\addlinespace
Marshfield          &                     & -20789134.1\sym{***}& -20789134.1\sym{***}&                     \\
                    &                     &     (-5.80)         &     (-5.80)         &                     \\
\addlinespace
Mashpee             &                     & -19830247.1\sym{***}& -19830247.1\sym{***}&                     \\
                    &                     &     (-3.39)         &     (-3.39)         &                     \\
\addlinespace
Methuen             &                     & -15000192.3\sym{***}& -15000192.3\sym{***}&                     \\
                    &                     &     (-5.53)         &     (-5.53)         &                     \\
\addlinespace
Middleboro          &                     & -12265582.7\sym{***}& -12265582.7\sym{***}&                     \\
                    &                     &     (-3.94)         &     (-3.94)         &                     \\
\addlinespace
Milford             &                     &  -9017182.4\sym{*}  &  -9017182.4\sym{*}  &                     \\
                    &                     &     (-2.34)         &     (-2.34)         &                     \\
\addlinespace
Millbury            &                     & -18658188.7\sym{***}& -18658188.7\sym{***}&                     \\
                    &                     &     (-3.59)         &     (-3.59)         &                     \\
\addlinespace
Needham             &                     &  39077459.2\sym{***}&  39077459.2\sym{***}&                     \\
                    &                     &      (9.08)         &      (9.08)         &                     \\
\addlinespace
New Bedford         &                     & -20447207.1\sym{***}& -20447207.1\sym{***}&                     \\
                    &                     &     (-8.55)         &     (-8.55)         &                     \\
\addlinespace
Newburyport         &                     & -17619838.9\sym{***}& -17619838.9\sym{***}&                     \\
                    &                     &     (-4.30)         &     (-4.30)         &                     \\
\addlinespace
North Adams         &                     & -20332323.4\sym{***}& -20332323.4\sym{***}&                     \\
                    &                     &     (-5.28)         &     (-5.28)         &                     \\
\addlinespace
North Andover       &                     &  -4927981.2         &  -4927981.2         &                     \\
                    &                     &     (-1.52)         &     (-1.52)         &                     \\
\addlinespace
North Attleboro     &                     & -20284380.8\sym{***}& -20284380.8\sym{***}&                     \\
                    &                     &     (-5.45)         &     (-5.45)         &                     \\
\addlinespace
North Billerica     &                     &  -8556369.2         &  -8556369.2         &                     \\
                    &                     &     (-1.80)         &     (-1.80)         &                     \\
\addlinespace
North Dartmouth     &                     & -13208231.2\sym{*}  & -13208231.2\sym{*}  &                     \\
                    &                     &     (-2.09)         &     (-2.09)         &                     \\
\addlinespace
Northampton         &                     & -20101965.1\sym{***}& -20101965.1\sym{***}&                     \\
                    &                     &     (-4.40)         &     (-4.40)         &                     \\
\addlinespace
Northborough        &                     &  40356948.8\sym{***}&  40356948.8\sym{***}&                     \\
                    &                     &      (8.49)         &      (8.49)         &                     \\
\addlinespace
Norton              &                     &  -6420841.7         &  -6420841.7         &                     \\
                    &                     &     (-1.49)         &     (-1.49)         &                     \\
\addlinespace
Norwood             &                     &  94746120.3\sym{***}&  94746120.3\sym{***}&                     \\
                    &                     &     (29.37)         &     (29.37)         &                     \\
\addlinespace
Oxford              &                     &  -9152764.4         &  -9152764.4         &                     \\
                    &                     &     (-1.76)         &     (-1.76)         &                     \\
\addlinespace
Peabody             &                     &   9805861.1\sym{***}&   9805861.1\sym{***}&                     \\
                    &                     &      (3.68)         &      (3.68)         &                     \\
\addlinespace
Pittsfield          &                     & -20746717.5\sym{***}& -20746717.5\sym{***}&                     \\
                    &                     &     (-7.86)         &     (-7.86)         &                     \\
\addlinespace
Plymouth            &                     & -20826306.6\sym{***}& -20826306.6\sym{***}&                     \\
                    &                     &     (-4.65)         &     (-4.65)         &                     \\
\addlinespace
Quincy              &                     &  -1743417.5         &  -1743417.5         &                     \\
                    &                     &     (-0.44)         &     (-0.44)         &                     \\
\addlinespace
Randolph            &                     &  -2226994.8         &  -2226994.8         &                     \\
                    &                     &     (-0.79)         &     (-0.79)         &                     \\
\addlinespace
Revere              &                     &   -159168.5         &   -159168.5         &                     \\
                    &                     &     (-0.03)         &     (-0.03)         &                     \\
\addlinespace
Rockland            &                     & -20101861.1\sym{***}& -20101861.1\sym{***}&                     \\
                    &                     &     (-6.55)         &     (-6.55)         &                     \\
\addlinespace
Salem               &                     & -16857836.8\sym{***}& -16857836.8\sym{***}&                     \\
                    &                     &     (-5.79)         &     (-5.79)         &                     \\
\addlinespace
Sandwich            &                     & -20722231.4\sym{***}& -20722231.4\sym{***}&                     \\
                    &                     &     (-3.54)         &     (-3.54)         &                     \\
\addlinespace
Saugus              &                     &   -340363.5         &   -340363.5         &                     \\
                    &                     &     (-0.10)         &     (-0.10)         &                     \\
\addlinespace
Seekonk             &                     &  17681397.2\sym{***}&  17681397.2\sym{***}&                     \\
                    &                     &      (4.89)         &      (4.89)         &                     \\
\addlinespace
Shirley             &                     & -21737007.4\sym{***}& -21737007.4\sym{***}&                     \\
                    &                     &     (-4.90)         &     (-4.90)         &                     \\
\addlinespace
Shrewsbury          &                     & -12117923.8\sym{*}  & -12117923.8\sym{*}  &                     \\
                    &                     &     (-2.45)         &     (-2.45)         &                     \\
\addlinespace
Somerville          &                     & -19566426.9\sym{***}& -19566426.9\sym{***}&                     \\
                    &                     &     (-3.77)         &     (-3.77)         &                     \\
\addlinespace
South Hadley        &                     & -20340123.7\sym{***}& -20340123.7\sym{***}&                     \\
                    &                     &     (-4.97)         &     (-4.97)         &                     \\
\addlinespace
Southbridge         &                     & -21059479.9\sym{***}& -21059479.9\sym{***}&                     \\
                    &                     &     (-7.09)         &     (-7.09)         &                     \\
\addlinespace
Southwick           &                     & -20440194.9\sym{***}& -20440194.9\sym{***}&                     \\
                    &                     &     (-3.73)         &     (-3.73)         &                     \\
\addlinespace
Spencer             &                     & -21062533.5\sym{***}& -21062533.5\sym{***}&                     \\
                    &                     &     (-5.26)         &     (-5.26)         &                     \\
\addlinespace
Springfield         &                     & -17446784.4\sym{***}& -17446784.4\sym{***}&                     \\
                    &                     &     (-7.56)         &     (-7.56)         &                     \\
\addlinespace
Stoughton           &                     & -11389546.7\sym{***}& -11389546.7\sym{***}&                     \\
                    &                     &     (-3.83)         &     (-3.83)         &                     \\
\addlinespace
Swampscott          &                     &  -4547859.6         &  -4547859.6         &                     \\
                    &                     &     (-1.08)         &     (-1.08)         &                     \\
\addlinespace
Taunton             &                     & -20276710.6\sym{***}& -20276710.6\sym{***}&                     \\
                    &                     &     (-7.44)         &     (-7.44)         &                     \\
\addlinespace
Tewksbury           &                     &   5281791.2         &   5281791.2         &                     \\
                    &                     &      (1.50)         &      (1.50)         &                     \\
\addlinespace
Three Rivers        &                     & -21263534.4\sym{***}& -21263534.4\sym{***}&                     \\
                    &                     &     (-3.88)         &     (-3.88)         &                     \\
\addlinespace
Tyngsboro           &                     & -19043379.7\sym{***}& -19043379.7\sym{***}&                     \\
                    &                     &     (-3.47)         &     (-3.47)         &                     \\
\addlinespace
Wakefield           &                     & -12951456.3\sym{**} & -12951456.3\sym{**} &                     \\
                    &                     &     (-3.24)         &     (-3.24)         &                     \\
\addlinespace
Walpole             &                     & -10254842.1\sym{*}  & -10254842.1\sym{*}  &                     \\
                    &                     &     (-2.24)         &     (-2.24)         &                     \\
\addlinespace
Waltham             &                     &  -4458163.9         &  -4458163.9         &                     \\
                    &                     &     (-1.57)         &     (-1.57)         &                     \\
\addlinespace
Ware                &                     & -21385935.2\sym{***}& -21385935.2\sym{***}&                     \\
                    &                     &     (-5.84)         &     (-5.84)         &                     \\
\addlinespace
Watertown           &                     &  14594615.7\sym{**} &  14594615.7\sym{**} &                     \\
                    &                     &      (2.81)         &      (2.81)         &                     \\
\addlinespace
Webster             &                     & -20767336.3\sym{***}& -20767336.3\sym{***}&                     \\
                    &                     &     (-4.19)         &     (-4.19)         &                     \\
\addlinespace
West Springfield    &                     & -20814715.6\sym{***}& -20814715.6\sym{***}&                     \\
                    &                     &     (-6.16)         &     (-6.16)         &                     \\
\addlinespace
Westborough         &                     &   4823814.7         &   4823814.7         &                     \\
                    &                     &      (1.40)         &      (1.40)         &                     \\
\addlinespace
Westwood            &                     &   3245897.8         &   3245897.8         &                     \\
                    &                     &      (0.56)         &      (0.56)         &                     \\
\addlinespace
Weymouth            &                     &  -4254268.3         &  -4254268.3         &                     \\
                    &                     &     (-1.01)         &     (-1.01)         &                     \\
\addlinespace
Whitinsville        &                     & -21120051.2\sym{***}& -21120051.2\sym{***}&                     \\
                    &                     &     (-3.34)         &     (-3.34)         &                     \\
\addlinespace
Whitman             &                     & -19787518.2\sym{***}& -19787518.2\sym{***}&                     \\
                    &                     &     (-4.83)         &     (-4.83)         &                     \\
\addlinespace
Winchendon          &                     & -21661279.7\sym{***}& -21661279.7\sym{***}&                     \\
                    &                     &     (-3.95)         &     (-3.95)         &                     \\
\addlinespace
Woburn              &                     &  42856970.1\sym{***}&  42856970.1\sym{***}&                     \\
                    &                     &      (9.65)         &      (9.65)         &                     \\
\addlinespace
Worcester           &                     & -19269002.4\sym{***}& -19269002.4\sym{***}&                     \\
                    &                     &     (-8.12)         &     (-8.12)         &                     \\
\addlinespace
group(property\_address\_city file\_year)=1&                     &                     &                     &           0         \\
                    &                     &                     &                     &         (.)         \\
\addlinespace
group(property\_address\_city file\_year)=2&                     &                     &                     & -21747387.2\sym{**} \\
                    &                     &                     &                     &     (-3.04)         \\
\addlinespace
group(property\_address\_city file\_year)=3&                     &                     &                     & -16553233.1         \\
                    &                     &                     &                     &     (-1.57)         \\
\addlinespace
group(property\_address\_city file\_year)=7&                     &                     &                     & -31817166.7\sym{***}\\
                    &                     &                     &                     &     (-4.84)         \\
\addlinespace
group(property\_address\_city file\_year)=8&                     &                     &                     & -31572134.4\sym{***}\\
                    &                     &                     &                     &     (-4.79)         \\
\addlinespace
group(property\_address\_city file\_year)=9&                     &                     &                     & -28362311.8\sym{***}\\
                    &                     &                     &                     &     (-4.12)         \\
\addlinespace
group(property\_address\_city file\_year)=11&                     &                     &                     & -29517698.0\sym{***}\\
                    &                     &                     &                     &     (-4.40)         \\
\addlinespace
group(property\_address\_city file\_year)=12&                     &                     &                     & -21429968.1\sym{**} \\
                    &                     &                     &                     &     (-3.13)         \\
\addlinespace
group(property\_address\_city file\_year)=13&                     &                     &                     &  -7726729.5         \\
                    &                     &                     &                     &     (-0.93)         \\
\addlinespace
group(property\_address\_city file\_year)=14&                     &                     &                     & -16546877.7         \\
                    &                     &                     &                     &     (-1.92)         \\
\addlinespace
group(property\_address\_city file\_year)=23&                     &                     &                     & -31739739.1\sym{***}\\
                    &                     &                     &                     &     (-4.83)         \\
\addlinespace
group(property\_address\_city file\_year)=24&                     &                     &                     & -29812227.4\sym{***}\\
                    &                     &                     &                     &     (-4.49)         \\
\addlinespace
group(property\_address\_city file\_year)=26&                     &                     &                     & -31616757.7\sym{***}\\
                    &                     &                     &                     &     (-4.81)         \\
\addlinespace
group(property\_address\_city file\_year)=31&                     &                     &                     &  -7667441.0         \\
                    &                     &                     &                     &     (-0.74)         \\
\addlinespace
group(property\_address\_city file\_year)=33&                     &                     &                     & -31058487.8\sym{***}\\
                    &                     &                     &                     &     (-4.72)         \\
\addlinespace
group(property\_address\_city file\_year)=34&                     &                     &                     & -29958013.6\sym{***}\\
                    &                     &                     &                     &     (-4.53)         \\
\addlinespace
group(property\_address\_city file\_year)=35&                     &                     &                     &   7817837.2         \\
                    &                     &                     &                     &      (0.33)         \\
\addlinespace
group(property\_address\_city file\_year)=39&                     &                     &                     & -23427539.3\sym{***}\\
                    &                     &                     &                     &     (-3.45)         \\
\addlinespace
group(property\_address\_city file\_year)=40&                     &                     &                     & -26490197.7\sym{***}\\
                    &                     &                     &                     &     (-3.84)         \\
\addlinespace
group(property\_address\_city file\_year)=42&                     &                     &                     &  -1787415.9         \\
                    &                     &                     &                     &     (-0.24)         \\
\addlinespace
group(property\_address\_city file\_year)=43&                     &                     &                     &  -7367293.9         \\
                    &                     &                     &                     &     (-0.88)         \\
\addlinespace
group(property\_address\_city file\_year)=53&                     &                     &                     &  12651738.5         \\
                    &                     &                     &                     &      (1.56)         \\
\addlinespace
group(property\_address\_city file\_year)=54&                     &                     &                     & -30931191.8\sym{***}\\
                    &                     &                     &                     &     (-4.68)         \\
\addlinespace
group(property\_address\_city file\_year)=56&                     &                     &                     &   -941258.6         \\
                    &                     &                     &                     &     (-0.12)         \\
\addlinespace
group(property\_address\_city file\_year)=58&                     &                     &                     & -27434049.1\sym{***}\\
                    &                     &                     &                     &     (-4.15)         \\
\addlinespace
group(property\_address\_city file\_year)=59&                     &                     &                     & -28035133.5\sym{***}\\
                    &                     &                     &                     &     (-4.23)         \\
\addlinespace
group(property\_address\_city file\_year)=60&                     &                     &                     & -26482084.7\sym{***}\\
                    &                     &                     &                     &     (-3.56)         \\
\addlinespace
group(property\_address\_city file\_year)=66&                     &                     &                     &  16595560.5         \\
                    &                     &                     &                     &      (1.21)         \\
\addlinespace
group(property\_address\_city file\_year)=67&                     &                     &                     &  -3516394.1         \\
                    &                     &                     &                     &     (-0.44)         \\
\addlinespace
group(property\_address\_city file\_year)=68&                     &                     &                     & -15346166.3         \\
                    &                     &                     &                     &     (-1.61)         \\
\addlinespace
group(property\_address\_city file\_year)=73&                     &                     &                     & -14757425.6\sym{*}  \\
                    &                     &                     &                     &     (-2.24)         \\
\addlinespace
group(property\_address\_city file\_year)=74&                     &                     &                     & -25535691.0\sym{***}\\
                    &                     &                     &                     &     (-3.40)         \\
\addlinespace
group(property\_address\_city file\_year)=75&                     &                     &                     &  -4233310.1         \\
                    &                     &                     &                     &     (-0.46)         \\
\addlinespace
group(property\_address\_city file\_year)=83&                     &                     &                     & -29174821.6\sym{***}\\
                    &                     &                     &                     &     (-4.40)         \\
\addlinespace
group(property\_address\_city file\_year)=84&                     &                     &                     & -31372814.9\sym{***}\\
                    &                     &                     &                     &     (-4.76)         \\
\addlinespace
group(property\_address\_city file\_year)=88&                     &                     &                     &  19157275.7         \\
                    &                     &                     &                     &      (1.72)         \\
\addlinespace
group(property\_address\_city file\_year)=92&                     &                     &                     & -15712195.5         \\
                    &                     &                     &                     &     (-1.86)         \\
\addlinespace
group(property\_address\_city file\_year)=99&                     &                     &                     & -29653470.5\sym{***}\\
                    &                     &                     &                     &     (-4.43)         \\
\addlinespace
group(property\_address\_city file\_year)=100&                     &                     &                     & -32025375.2\sym{***}\\
                    &                     &                     &                     &     (-4.86)         \\
\addlinespace
group(property\_address\_city file\_year)=103&                     &                     &                     & -25516156.4\sym{***}\\
                    &                     &                     &                     &     (-3.59)         \\
\addlinespace
group(property\_address\_city file\_year)=113&                     &                     &                     & -25490007.7\sym{***}\\
                    &                     &                     &                     &     (-3.43)         \\
\addlinespace
group(property\_address\_city file\_year)=120&                     &                     &                     & -17660394.5\sym{*}  \\
                    &                     &                     &                     &     (-1.98)         \\
\addlinespace
group(property\_address\_city file\_year)=121&                     &                     &                     & -31937592.6\sym{***}\\
                    &                     &                     &                     &     (-4.85)         \\
\addlinespace
group(property\_address\_city file\_year)=122&                     &                     &                     & -30621970.7\sym{***}\\
                    &                     &                     &                     &     (-4.62)         \\
\addlinespace
group(property\_address\_city file\_year)=123&                     &                     &                     & -28326993.2\sym{***}\\
                    &                     &                     &                     &     (-4.29)         \\
\addlinespace
group(property\_address\_city file\_year)=125&                     &                     &                     & -29342045.6\sym{***}\\
                    &                     &                     &                     &     (-4.42)         \\
\addlinespace
group(property\_address\_city file\_year)=126&                     &                     &                     & -28176986.1\sym{***}\\
                    &                     &                     &                     &     (-4.09)         \\
\addlinespace
group(property\_address\_city file\_year)=127&                     &                     &                     & -31295574.7\sym{***}\\
                    &                     &                     &                     &     (-4.76)         \\
\addlinespace
group(property\_address\_city file\_year)=128&                     &                     &                     & -31064464.4\sym{***}\\
                    &                     &                     &                     &     (-4.72)         \\
\addlinespace
group(property\_address\_city file\_year)=132&                     &                     &                     &  10388032.0         \\
                    &                     &                     &                     &      (1.57)         \\
\addlinespace
group(property\_address\_city file\_year)=134&                     &                     &                     &   9032122.0         \\
                    &                     &                     &                     &      (1.36)         \\
\addlinespace
group(property\_address\_city file\_year)=135&                     &                     &                     & -12412590.3         \\
                    &                     &                     &                     &     (-1.78)         \\
\addlinespace
group(property\_address\_city file\_year)=136&                     &                     &                     & -19582760.6\sym{*}  \\
                    &                     &                     &                     &     (-2.57)         \\
\addlinespace
group(property\_address\_city file\_year)=137&                     &                     &                     &  -8576722.7         \\
                    &                     &                     &                     &     (-0.98)         \\
\addlinespace
group(property\_address\_city file\_year)=138&                     &                     &                     & -28607583.4\sym{***}\\
                    &                     &                     &                     &     (-4.29)         \\
\addlinespace
group(property\_address\_city file\_year)=142&                     &                     &                     & -25588880.8\sym{***}\\
                    &                     &                     &                     &     (-3.77)         \\
\addlinespace
group(property\_address\_city file\_year)=143&                     &                     &                     & -23441624.9\sym{***}\\
                    &                     &                     &                     &     (-3.39)         \\
\addlinespace
group(property\_address\_city file\_year)=144&                     &                     &                     & -21884245.6\sym{**} \\
                    &                     &                     &                     &     (-2.77)         \\
\addlinespace
group(property\_address\_city file\_year)=147&                     &                     &                     & -29352983.9\sym{***}\\
                    &                     &                     &                     &     (-4.39)         \\
\addlinespace
group(property\_address\_city file\_year)=153&                     &                     &                     & -31841831.8\sym{***}\\
                    &                     &                     &                     &     (-4.84)         \\
\addlinespace
group(property\_address\_city file\_year)=156&                     &                     &                     & -28639093.1\sym{***}\\
                    &                     &                     &                     &     (-4.34)         \\
\addlinespace
group(property\_address\_city file\_year)=164&                     &                     &                     & -30086286.3\sym{***}\\
                    &                     &                     &                     &     (-4.55)         \\
\addlinespace
group(property\_address\_city file\_year)=167&                     &                     &                     & -31563212.8\sym{***}\\
                    &                     &                     &                     &     (-4.80)         \\
\addlinespace
group(property\_address\_city file\_year)=168&                     &                     &                     & -26148336.2\sym{***}\\
                    &                     &                     &                     &     (-3.44)         \\
\addlinespace
group(property\_address\_city file\_year)=169&                     &                     &                     & -21888879.5\sym{*}  \\
                    &                     &                     &                     &     (-2.50)         \\
\addlinespace
group(property\_address\_city file\_year)=171&                     &                     &                     & -29740224.9\sym{***}\\
                    &                     &                     &                     &     (-4.49)         \\
\addlinespace
group(property\_address\_city file\_year)=172&                     &                     &                     & -31399983.4\sym{***}\\
                    &                     &                     &                     &     (-4.78)         \\
\addlinespace
group(property\_address\_city file\_year)=173&                     &                     &                     & -30775755.6\sym{***}\\
                    &                     &                     &                     &     (-4.61)         \\
\addlinespace
group(property\_address\_city file\_year)=174&                     &                     &                     & -29867637.5\sym{***}\\
                    &                     &                     &                     &     (-4.51)         \\
\addlinespace
group(property\_address\_city file\_year)=179&                     &                     &                     & -29450518.0\sym{***}\\
                    &                     &                     &                     &     (-4.43)         \\
\addlinespace
group(property\_address\_city file\_year)=180&                     &                     &                     & -24582985.6\sym{***}\\
                    &                     &                     &                     &     (-3.56)         \\
\addlinespace
group(property\_address\_city file\_year)=182&                     &                     &                     & -29062568.7\sym{***}\\
                    &                     &                     &                     &     (-4.41)         \\
\addlinespace
group(property\_address\_city file\_year)=183&                     &                     &                     & -28961589.8\sym{***}\\
                    &                     &                     &                     &     (-4.39)         \\
\addlinespace
group(property\_address\_city file\_year)=187&                     &                     &                     & -27536485.7\sym{***}\\
                    &                     &                     &                     &     (-4.16)         \\
\addlinespace
group(property\_address\_city file\_year)=194&                     &                     &                     & -24983783.9\sym{***}\\
                    &                     &                     &                     &     (-3.79)         \\
\addlinespace
group(property\_address\_city file\_year)=195&                     &                     &                     & -27444446.8\sym{***}\\
                    &                     &                     &                     &     (-4.16)         \\
\addlinespace
group(property\_address\_city file\_year)=196&                     &                     &                     & -30678002.5\sym{***}\\
                    &                     &                     &                     &     (-4.64)         \\
\addlinespace
group(property\_address\_city file\_year)=197&                     &                     &                     & -31478427.5\sym{***}\\
                    &                     &                     &                     &     (-4.77)         \\
\addlinespace
group(property\_address\_city file\_year)=198&                     &                     &                     & -32035018.0\sym{***}\\
                    &                     &                     &                     &     (-4.86)         \\
\addlinespace
group(property\_address\_city file\_year)=199&                     &                     &                     & -28721146.1\sym{***}\\
                    &                     &                     &                     &     (-4.35)         \\
\addlinespace
group(property\_address\_city file\_year)=200&                     &                     &                     & -28530907.5\sym{***}\\
                    &                     &                     &                     &     (-4.29)         \\
\addlinespace
group(property\_address\_city file\_year)=201&                     &                     &                     & -13358738.0         \\
                    &                     &                     &                     &     (-1.71)         \\
\addlinespace
group(property\_address\_city file\_year)=203&                     &                     &                     & -11773931.9         \\
                    &                     &                     &                     &     (-1.55)         \\
\addlinespace
group(property\_address\_city file\_year)=204&                     &                     &                     &  -7249428.5         \\
                    &                     &                     &                     &     (-0.97)         \\
\addlinespace
group(property\_address\_city file\_year)=206&                     &                     &                     & -24920666.9\sym{***}\\
                    &                     &                     &                     &     (-3.66)         \\
\addlinespace
group(property\_address\_city file\_year)=207&                     &                     &                     & -21421751.4\sym{**} \\
                    &                     &                     &                     &     (-2.98)         \\
\addlinespace
group(property\_address\_city file\_year)=208&                     &                     &                     & -30633853.1\sym{***}\\
                    &                     &                     &                     &     (-4.57)         \\
\addlinespace
group(property\_address\_city file\_year)=209&                     &                     &                     & -31329599.4\sym{***}\\
                    &                     &                     &                     &     (-4.72)         \\
\addlinespace
group(property\_address\_city file\_year)=212&                     &                     &                     & -30116514.1\sym{***}\\
                    &                     &                     &                     &     (-4.53)         \\
\addlinespace
group(property\_address\_city file\_year)=213&                     &                     &                     & -29659399.3\sym{***}\\
                    &                     &                     &                     &     (-4.48)         \\
\addlinespace
group(property\_address\_city file\_year)=214&                     &                     &                     & -31497392.3\sym{***}\\
                    &                     &                     &                     &     (-4.79)         \\
\addlinespace
group(property\_address\_city file\_year)=216&                     &                     &                     & -29958296.2\sym{***}\\
                    &                     &                     &                     &     (-4.54)         \\
\addlinespace
group(property\_address\_city file\_year)=224&                     &                     &                     & -25191502.6\sym{***}\\
                    &                     &                     &                     &     (-3.69)         \\
\addlinespace
group(property\_address\_city file\_year)=225&                     &                     &                     & -25256604.5\sym{***}\\
                    &                     &                     &                     &     (-3.71)         \\
\addlinespace
group(property\_address\_city file\_year)=226&                     &                     &                     & -29751606.3\sym{***}\\
                    &                     &                     &                     &     (-4.40)         \\
\addlinespace
group(property\_address\_city file\_year)=227&                     &                     &                     & -16565988.0\sym{*}  \\
                    &                     &                     &                     &     (-2.19)         \\
\addlinespace
group(property\_address\_city file\_year)=229&                     &                     &                     & -22558870.7\sym{**} \\
                    &                     &                     &                     &     (-2.95)         \\
\addlinespace
group(property\_address\_city file\_year)=230&                     &                     &                     & -17095348.7\sym{*}  \\
                    &                     &                     &                     &     (-2.47)         \\
\addlinespace
group(property\_address\_city file\_year)=232&                     &                     &                     & -28960955.5\sym{***}\\
                    &                     &                     &                     &     (-4.23)         \\
\addlinespace
group(property\_address\_city file\_year)=242&                     &                     &                     &  12661382.0         \\
                    &                     &                     &                     &      (0.72)         \\
\addlinespace
group(property\_address\_city file\_year)=243&                     &                     &                     &  39024648.4\sym{***}\\
                    &                     &                     &                     &      (4.88)         \\
\addlinespace
group(property\_address\_city file\_year)=246&                     &                     &                     & -30756034.7\sym{***}\\
                    &                     &                     &                     &     (-4.67)         \\
\addlinespace
group(property\_address\_city file\_year)=248&                     &                     &                     & -26979715.6\sym{***}\\
                    &                     &                     &                     &     (-4.08)         \\
\addlinespace
group(property\_address\_city file\_year)=249&                     &                     &                     & -29764479.4\sym{***}\\
                    &                     &                     &                     &     (-4.47)         \\
\addlinespace
group(property\_address\_city file\_year)=251&                     &                     &                     & -30369071.2\sym{***}\\
                    &                     &                     &                     &     (-4.61)         \\
\addlinespace
group(property\_address\_city file\_year)=252&                     &                     &                     & -31063119.1\sym{***}\\
                    &                     &                     &                     &     (-4.70)         \\
\addlinespace
group(property\_address\_city file\_year)=253&                     &                     &                     &  -9953427.2         \\
                    &                     &                     &                     &     (-1.27)         \\
\addlinespace
group(property\_address\_city file\_year)=254&                     &                     &                     & -19744724.7\sym{**} \\
                    &                     &                     &                     &     (-2.61)         \\
\addlinespace
group(property\_address\_city file\_year)=255&                     &                     &                     & -30457504.7\sym{***}\\
                    &                     &                     &                     &     (-4.60)         \\
\addlinespace
group(property\_address\_city file\_year)=256&                     &                     &                     & -30847319.4\sym{***}\\
                    &                     &                     &                     &     (-4.65)         \\
\addlinespace
group(property\_address\_city file\_year)=257&                     &                     &                     & -18894051.8\sym{*}  \\
                    &                     &                     &                     &     (-1.97)         \\
\addlinespace
group(property\_address\_city file\_year)=258&                     &                     &                     & -18653038.0\sym{*}  \\
                    &                     &                     &                     &     (-1.96)         \\
\addlinespace
group(property\_address\_city file\_year)=261&                     &                     &                     & -23510998.0\sym{**} \\
                    &                     &                     &                     &     (-3.22)         \\
\addlinespace
group(property\_address\_city file\_year)=271&                     &                     &                     & -31532639.4\sym{***}\\
                    &                     &                     &                     &     (-4.76)         \\
\addlinespace
group(property\_address\_city file\_year)=273&                     &                     &                     & -28289201.2\sym{***}\\
                    &                     &                     &                     &     (-4.14)         \\
\addlinespace
group(property\_address\_city file\_year)=274&                     &                     &                     &  30054182.0\sym{***}\\
                    &                     &                     &                     &      (4.56)         \\
\addlinespace
group(property\_address\_city file\_year)=277&                     &                     &                     & -25086958.0\sym{**} \\
                    &                     &                     &                     &     (-2.97)         \\
\addlinespace
group(property\_address\_city file\_year)=278&                     &                     &                     & -11343893.9         \\
                    &                     &                     &                     &     (-1.31)         \\
\addlinespace
group(property\_address\_city file\_year)=279&                     &                     &                     & 118496709.8\sym{***}\\
                    &                     &                     &                     &      (7.37)         \\
\addlinespace
group(property\_address\_city file\_year)=280&                     &                     &                     &  43750508.2\sym{***}\\
                    &                     &                     &                     &      (3.55)         \\
\addlinespace
group(property\_address\_city file\_year)=288&                     &                     &                     & -19468789.1\sym{*}  \\
                    &                     &                     &                     &     (-1.99)         \\
\addlinespace
group(property\_address\_city file\_year)=290&                     &                     &                     &  -4604103.0         \\
                    &                     &                     &                     &     (-0.62)         \\
\addlinespace
group(property\_address\_city file\_year)=291&                     &                     &                     &   6168772.8         \\
                    &                     &                     &                     &      (0.74)         \\
\addlinespace
group(property\_address\_city file\_year)=296&                     &                     &                     & -31250792.0\sym{***}\\
                    &                     &                     &                     &     (-4.75)         \\
\addlinespace
group(property\_address\_city file\_year)=297&                     &                     &                     & -30530442.5\sym{***}\\
                    &                     &                     &                     &     (-4.64)         \\
\addlinespace
group(property\_address\_city file\_year)=299&                     &                     &                     & -29688885.1\sym{***}\\
                    &                     &                     &                     &     (-4.39)         \\
\addlinespace
group(property\_address\_city file\_year)=302&                     &                     &                     & -10610238.6         \\
                    &                     &                     &                     &     (-1.10)         \\
\addlinespace
group(property\_address\_city file\_year)=303&                     &                     &                     & -13613772.3         \\
                    &                     &                     &                     &     (-1.89)         \\
\addlinespace
group(property\_address\_city file\_year)=304&                     &                     &                     & -10758486.3         \\
                    &                     &                     &                     &     (-1.10)         \\
\addlinespace
group(property\_address\_city file\_year)=308&                     &                     &                     & -10311965.6         \\
                    &                     &                     &                     &     (-0.78)         \\
\addlinespace
group(property\_address\_city file\_year)=310&                     &                     &                     & -30407214.8\sym{***}\\
                    &                     &                     &                     &     (-4.60)         \\
\addlinespace
group(property\_address\_city file\_year)=318&                     &                     &                     & -27004230.1\sym{***}\\
                    &                     &                     &                     &     (-4.06)         \\
\addlinespace
group(property\_address\_city file\_year)=320&                     &                     &                     & -30867957.7\sym{***}\\
                    &                     &                     &                     &     (-4.69)         \\
\addlinespace
group(property\_address\_city file\_year)=321&                     &                     &                     & -17030155.6         \\
                    &                     &                     &                     &     (-1.94)         \\
\addlinespace
group(property\_address\_city file\_year)=322&                     &                     &                     &  -4839964.1         \\
                    &                     &                     &                     &     (-0.37)         \\
\addlinespace
group(property\_address\_city file\_year)=323&                     &                     &                     &   3439082.0         \\
                    &                     &                     &                     &      (0.25)         \\
\addlinespace
group(property\_address\_city file\_year)=325&                     &                     &                     &   2301259.0         \\
                    &                     &                     &                     &      (0.20)         \\
\addlinespace
group(property\_address\_city file\_year)=326&                     &                     &                     &   9455152.7         \\
                    &                     &                     &                     &      (1.15)         \\
\addlinespace
group(property\_address\_city file\_year)=330&                     &                     &                     & -31814129.5\sym{***}\\
                    &                     &                     &                     &     (-4.84)         \\
\addlinespace
group(property\_address\_city file\_year)=331&                     &                     &                     & -32090701.4\sym{***}\\
                    &                     &                     &                     &     (-4.87)         \\
\addlinespace
group(property\_address\_city file\_year)=332&                     &                     &                     & -22228295.8\sym{*}  \\
                    &                     &                     &                     &     (-2.47)         \\
\addlinespace
group(property\_address\_city file\_year)=334&                     &                     &                     & -29882451.6\sym{***}\\
                    &                     &                     &                     &     (-4.52)         \\
\addlinespace
group(property\_address\_city file\_year)=344&                     &                     &                     & -30622664.1\sym{***}\\
                    &                     &                     &                     &     (-4.64)         \\
\addlinespace
group(property\_address\_city file\_year)=345&                     &                     &                     & -30534219.0\sym{***}\\
                    &                     &                     &                     &     (-4.62)         \\
\addlinespace
group(property\_address\_city file\_year)=350&                     &                     &                     & -31222278.5\sym{***}\\
                    &                     &                     &                     &     (-4.74)         \\
\addlinespace
group(property\_address\_city file\_year)=351&                     &                     &                     & -31474184.8\sym{***}\\
                    &                     &                     &                     &     (-4.78)         \\
\addlinespace
group(property\_address\_city file\_year)=352&                     &                     &                     & -30758113.6\sym{***}\\
                    &                     &                     &                     &     (-4.63)         \\
\addlinespace
group(property\_address\_city file\_year)=353&                     &                     &                     & -31385187.2\sym{***}\\
                    &                     &                     &                     &     (-4.77)         \\
\addlinespace
group(property\_address\_city file\_year)=355&                     &                     &                     & -28884085.3\sym{***}\\
                    &                     &                     &                     &     (-4.39)         \\
\addlinespace
group(property\_address\_city file\_year)=356&                     &                     &                     & -25817895.7\sym{***}\\
                    &                     &                     &                     &     (-3.89)         \\
\addlinespace
group(property\_address\_city file\_year)=359&                     &                     &                     & -24039316.5\sym{***}\\
                    &                     &                     &                     &     (-3.40)         \\
\addlinespace
group(property\_address\_city file\_year)=360&                     &                     &                     & -19620579.8\sym{**} \\
                    &                     &                     &                     &     (-2.59)         \\
\addlinespace
group(property\_address\_city file\_year)=366&                     &                     &                     & -14873354.2         \\
                    &                     &                     &                     &     (-1.67)         \\
\addlinespace
group(property\_address\_city file\_year)=369&                     &                     &                     & -29903518.7\sym{***}\\
                    &                     &                     &                     &     (-4.53)         \\
\addlinespace
group(property\_address\_city file\_year)=370&                     &                     &                     & -30828394.3\sym{***}\\
                    &                     &                     &                     &     (-4.68)         \\
\addlinespace
group(property\_address\_city file\_year)=372&                     &                     &                     &  -6925805.9         \\
                    &                     &                     &                     &     (-0.86)         \\
\addlinespace
group(property\_address\_city file\_year)=373&                     &                     &                     &  -1071951.6         \\
                    &                     &                     &                     &     (-0.10)         \\
\addlinespace
group(property\_address\_city file\_year)=375&                     &                     &                     & -31419361.8\sym{***}\\
                    &                     &                     &                     &     (-4.77)         \\
\addlinespace
group(property\_address\_city file\_year)=377&                     &                     &                     & -29346146.6\sym{***}\\
                    &                     &                     &                     &     (-4.44)         \\
\addlinespace
group(property\_address\_city file\_year)=383&                     &                     &                     & -20344933.3\sym{**} \\
                    &                     &                     &                     &     (-2.73)         \\
\addlinespace
group(property\_address\_city file\_year)=384&                     &                     &                     & -26847799.3\sym{***}\\
                    &                     &                     &                     &     (-3.96)         \\
\addlinespace
group(property\_address\_city file\_year)=385&                     &                     &                     & -20557608.9\sym{*}  \\
                    &                     &                     &                     &     (-2.35)         \\
\addlinespace
group(property\_address\_city file\_year)=386&                     &                     &                     & -12889024.4         \\
                    &                     &                     &                     &     (-1.72)         \\
\addlinespace
group(property\_address\_city file\_year)=387&                     &                     &                     & -19353269.5\sym{*}  \\
                    &                     &                     &                     &     (-2.51)         \\
\addlinespace
group(property\_address\_city file\_year)=388&                     &                     &                     & -31519945.1\sym{***}\\
                    &                     &                     &                     &     (-4.79)         \\
\addlinespace
group(property\_address\_city file\_year)=389&                     &                     &                     & -30694986.0\sym{***}\\
                    &                     &                     &                     &     (-4.62)         \\
\addlinespace
group(property\_address\_city file\_year)=393&                     &                     &                     &   4470985.9         \\
                    &                     &                     &                     &      (0.31)         \\
\addlinespace
group(property\_address\_city file\_year)=394&                     &                     &                     & -30901277.8\sym{***}\\
                    &                     &                     &                     &     (-4.68)         \\
\addlinespace
group(property\_address\_city file\_year)=401&                     &                     &                     & -30955391.3\sym{***}\\
                    &                     &                     &                     &     (-4.71)         \\
\addlinespace
group(property\_address\_city file\_year)=406&                     &                     &                     &  -2979054.9         \\
                    &                     &                     &                     &     (-0.40)         \\
\addlinespace
group(property\_address\_city file\_year)=407&                     &                     &                     & -13672579.5         \\
                    &                     &                     &                     &     (-1.83)         \\
\addlinespace
group(property\_address\_city file\_year)=413&                     &                     &                     &  -7074546.2         \\
                    &                     &                     &                     &     (-0.93)         \\
\addlinespace
group(property\_address\_city file\_year)=414&                     &                     &                     & -14379792.2\sym{*}  \\
                    &                     &                     &                     &     (-1.98)         \\
\addlinespace
group(property\_address\_city file\_year)=415&                     &                     &                     & -31422818.0\sym{***}\\
                    &                     &                     &                     &     (-4.76)         \\
\addlinespace
group(property\_address\_city file\_year)=417&                     &                     &                     & -30097355.9\sym{***}\\
                    &                     &                     &                     &     (-4.55)         \\
\addlinespace
group(property\_address\_city file\_year)=423&                     &                     &                     & -31964046.6\sym{***}\\
                    &                     &                     &                     &     (-4.85)         \\
\addlinespace
group(property\_address\_city file\_year)=426&                     &                     &                     &  32737759.6\sym{**} \\
                    &                     &                     &                     &      (2.60)         \\
\addlinespace
group(property\_address\_city file\_year)=427&                     &                     &                     & -29581259.1\sym{***}\\
                    &                     &                     &                     &     (-4.49)         \\
\addlinespace
Constant            &   6023455.1\sym{***}&  20725757.2\sym{***}&  20725757.2\sym{***}&  31134586.9\sym{***}\\
                    &     (11.62)         &      (8.99)         &      (8.99)         &      (4.57)         \\
\midrule
Observations        &        5567         &        5567         &        5567         &        5567         \\
\bottomrule
\multicolumn{5}{l}{\footnotesize \textit{t} statistics in parentheses}\\
\multicolumn{5}{l}{\footnotesize \sym{*} \(p<0.05\), \sym{**} \(p<0.01\), \sym{***} \(p<0.001\)}\\
\end{tabular}
}

### 2022-12-07 output/01_exploratory/tables/total_val_results_table.tex
Created estimation tables

{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabular}{l*{4}{c}}
\toprule
                    &\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}\\
\midrule
judgment\_for\_plaintiff&   3259178.0\sym{***}&   1507062.7\sym{**} &   1507062.7\sym{**} &    751962.4         \\
                    &      (4.27)         &      (2.61)         &      (2.61)         &      (0.26)         \\
\addlinespace
file\_year=2019      &                     &           0         &           0         &                     \\
                    &                     &         (.)         &         (.)         &                     \\
\addlinespace
file\_year=2020      &                     &   -129326.5         &   -129326.5         &                     \\
                    &                     &     (-0.22)         &     (-0.22)         &                     \\
\addlinespace
file\_year=2021      &                     &   2343272.8         &   2343272.8         &                     \\
                    &                     &      (1.01)         &      (1.01)         &                     \\
\addlinespace
Abington            &                     &           0         &           0         &                     \\
                    &                     &         (.)         &         (.)         &                     \\
\addlinespace
Acton               &                     &  -8845941.7         &  -8845941.7         &                     \\
                    &                     &     (-1.10)         &     (-1.10)         &                     \\
\addlinespace
Adams               &                     & -26295427.0\sym{***}& -26295427.0\sym{***}&                     \\
                    &                     &     (-5.72)         &     (-5.72)         &                     \\
\addlinespace
Agawam              &                     & -22781989.3\sym{***}& -22781989.3\sym{***}&                     \\
                    &                     &     (-3.77)         &     (-3.77)         &                     \\
\addlinespace
Amesbury            &                     & -22667125.4\sym{**} & -22667125.4\sym{**} &                     \\
                    &                     &     (-2.82)         &     (-2.82)         &                     \\
\addlinespace
Amherst             &                     & -13994734.3\sym{*}  & -13994734.3\sym{*}  &                     \\
                    &                     &     (-2.40)         &     (-2.40)         &                     \\
\addlinespace
Andover             &                     &   -749699.0         &   -749699.0         &                     \\
                    &                     &     (-0.17)         &     (-0.17)         &                     \\
\addlinespace
Athol               &                     & -26350442.5\sym{***}& -26350442.5\sym{***}&                     \\
                    &                     &     (-3.99)         &     (-3.99)         &                     \\
\addlinespace
Attleboro           &                     & -24327184.2\sym{***}& -24327184.2\sym{***}&                     \\
                    &                     &     (-5.29)         &     (-5.29)         &                     \\
\addlinespace
Auburn              &                     & -26064121.1\sym{***}& -26064121.1\sym{***}&                     \\
                    &                     &     (-3.50)         &     (-3.50)         &                     \\
\addlinespace
Bedford             &                     &   5756678.9         &   5756678.9         &                     \\
                    &                     &      (0.77)         &      (0.77)         &                     \\
\addlinespace
Belchertown         &                     & -25142479.5\sym{***}& -25142479.5\sym{***}&                     \\
                    &                     &     (-5.23)         &     (-5.23)         &                     \\
\addlinespace
Bellingham          &                     &  18531792.0\sym{*}  &  18531792.0\sym{*}  &                     \\
                    &                     &      (2.49)         &      (2.49)         &                     \\
\addlinespace
Beverly             &                     & -15591295.2\sym{***}& -15591295.2\sym{***}&                     \\
                    &                     &     (-4.23)         &     (-4.23)         &                     \\
\addlinespace
Billerica           &                     &   9390507.4\sym{*}  &   9390507.4\sym{*}  &                     \\
                    &                     &      (2.07)         &      (2.07)         &                     \\
\addlinespace
Braintree           &                     &  35327975.2\sym{***}&  35327975.2\sym{***}&                     \\
                    &                     &      (7.88)         &      (7.88)         &                     \\
\addlinespace
Brewster            &                     & -25347499.3\sym{**} & -25347499.3\sym{**} &                     \\
                    &                     &     (-3.15)         &     (-3.15)         &                     \\
\addlinespace
Bridgewater         &                     &  11554226.6\sym{**} &  11554226.6\sym{**} &                     \\
                    &                     &      (2.85)         &      (2.85)         &                     \\
\addlinespace
Brockton            &                     & -21848926.9\sym{***}& -21848926.9\sym{***}&                     \\
                    &                     &     (-7.20)         &     (-7.20)         &                     \\
\addlinespace
Brookline           &                     & -14165718.5         & -14165718.5         &                     \\
                    &                     &     (-1.90)         &     (-1.90)         &                     \\
\addlinespace
Cambridge           &                     &  42468310.1\sym{***}&  42468310.1\sym{***}&                     \\
                    &                     &      (9.10)         &      (9.10)         &                     \\
\addlinespace
Canton              &                     &   5921639.1         &   5921639.1         &                     \\
                    &                     &      (1.34)         &      (1.34)         &                     \\
\addlinespace
Chelmsford          &                     &  -3878300.3         &  -3878300.3         &                     \\
                    &                     &     (-0.48)         &     (-0.48)         &                     \\
\addlinespace
Chelsea             &                     &  -6087119.2         &  -6087119.2         &                     \\
                    &                     &     (-1.11)         &     (-1.11)         &                     \\
\addlinespace
Chicopee            &                     & -23100145.0\sym{***}& -23100145.0\sym{***}&                     \\
                    &                     &     (-6.57)         &     (-6.57)         &                     \\
\addlinespace
Clinton             &                     & -25980685.6\sym{***}& -25980685.6\sym{***}&                     \\
                    &                     &     (-4.30)         &     (-4.30)         &                     \\
\addlinespace
Concord             &                     &  36262535.7\sym{***}&  36262535.7\sym{***}&                     \\
                    &                     &      (4.88)         &      (4.88)         &                     \\
\addlinespace
Danvers             &                     &   -350734.0         &   -350734.0         &                     \\
                    &                     &     (-0.06)         &     (-0.06)         &                     \\
\addlinespace
Dracut              &                     & -23566660.9\sym{***}& -23566660.9\sym{***}&                     \\
                    &                     &     (-4.30)         &     (-4.30)         &                     \\
\addlinespace
Dudley              &                     & -26862280.4\sym{***}& -26862280.4\sym{***}&                     \\
                    &                     &     (-3.85)         &     (-3.85)         &                     \\
\addlinespace
Duxbury             &                     & -16553871.4\sym{*}  & -16553871.4\sym{*}  &                     \\
                    &                     &     (-2.37)         &     (-2.37)         &                     \\
\addlinespace
East Wareham        &                     & -18675454.5\sym{*}  & -18675454.5\sym{*}  &                     \\
                    &                     &     (-2.51)         &     (-2.51)         &                     \\
\addlinespace
Everett             &                     &  -8839883.1         &  -8839883.1         &                     \\
                    &                     &     (-1.89)         &     (-1.89)         &                     \\
\addlinespace
Fairhaven           &                     & -25898741.3\sym{***}& -25898741.3\sym{***}&                     \\
                    &                     &     (-5.48)         &     (-5.48)         &                     \\
\addlinespace
Fall River          &                     & -21875817.7\sym{***}& -21875817.7\sym{***}&                     \\
                    &                     &     (-6.91)         &     (-6.91)         &                     \\
\addlinespace
Feeding Hills       &                     & -22823447.4\sym{***}& -22823447.4\sym{***}&                     \\
                    &                     &     (-5.03)         &     (-5.03)         &                     \\
\addlinespace
Fitchburg           &                     & -25581554.5\sym{***}& -25581554.5\sym{***}&                     \\
                    &                     &     (-7.97)         &     (-7.97)         &                     \\
\addlinespace
Foxboro             &                     &  22618498.2\sym{***}&  22618498.2\sym{***}&                     \\
                    &                     &      (3.74)         &      (3.74)         &                     \\
\addlinespace
Foxborough          &                     &  21596274.6\sym{**} &  21596274.6\sym{**} &                     \\
                    &                     &      (2.68)         &      (2.68)         &                     \\
\addlinespace
Framingham          &                     &  -4392422.6         &  -4392422.6         &                     \\
                    &                     &     (-1.26)         &     (-1.26)         &                     \\
\addlinespace
Franklin            &                     &  -3437183.4         &  -3437183.4         &                     \\
                    &                     &     (-0.72)         &     (-0.72)         &                     \\
\addlinespace
Gardner             &                     & -22989976.9\sym{***}& -22989976.9\sym{***}&                     \\
                    &                     &     (-5.12)         &     (-5.12)         &                     \\
\addlinespace
Gloucester          &                     & -18804855.2\sym{***}& -18804855.2\sym{***}&                     \\
                    &                     &     (-4.80)         &     (-4.80)         &                     \\
\addlinespace
Grafton             &                     & -16016646.8\sym{*}  & -16016646.8\sym{*}  &                     \\
                    &                     &     (-1.99)         &     (-1.99)         &                     \\
\addlinespace
Greenfield          &                     & -23459956.9\sym{***}& -23459956.9\sym{***}&                     \\
                    &                     &     (-4.69)         &     (-4.69)         &                     \\
\addlinespace
Hanson              &                     & -26499939.3\sym{***}& -26499939.3\sym{***}&                     \\
                    &                     &     (-3.29)         &     (-3.29)         &                     \\
\addlinespace
Haverhill           &                     & -20800293.3\sym{***}& -20800293.3\sym{***}&                     \\
                    &                     &     (-5.77)         &     (-5.77)         &                     \\
\addlinespace
Holyoke             &                     & -24189959.6\sym{***}& -24189959.6\sym{***}&                     \\
                    &                     &     (-6.70)         &     (-6.70)         &                     \\
\addlinespace
Hudson              &                     & -26242808.0\sym{***}& -26242808.0\sym{***}&                     \\
                    &                     &     (-3.53)         &     (-3.53)         &                     \\
\addlinespace
Hull                &                     & -17550050.6\sym{***}& -17550050.6\sym{***}&                     \\
                    &                     &     (-3.52)         &     (-3.52)         &                     \\
\addlinespace
Hyannis             &                     & -23763038.9\sym{***}& -23763038.9\sym{***}&                     \\
                    &                     &     (-4.08)         &     (-4.08)         &                     \\
\addlinespace
Indian Orchard      &                     & -25842404.0\sym{***}& -25842404.0\sym{***}&                     \\
                    &                     &     (-6.83)         &     (-6.83)         &                     \\
\addlinespace
Ipswich             &                     & -23775846.2\sym{***}& -23775846.2\sym{***}&                     \\
                    &                     &     (-3.77)         &     (-3.77)         &                     \\
\addlinespace
Lakeville           &                     & -21406455.4\sym{***}& -21406455.4\sym{***}&                     \\
                    &                     &     (-3.80)         &     (-3.80)         &                     \\
\addlinespace
Lawrence            &                     & -23418520.4\sym{***}& -23418520.4\sym{***}&                     \\
                    &                     &     (-7.75)         &     (-7.75)         &                     \\
\addlinespace
Leominster          &                     & -21878759.1\sym{***}& -21878759.1\sym{***}&                     \\
                    &                     &     (-5.85)         &     (-5.85)         &                     \\
\addlinespace
Lowell              &                     & -19476530.9\sym{***}& -19476530.9\sym{***}&                     \\
                    &                     &     (-6.51)         &     (-6.51)         &                     \\
\addlinespace
Ludlow              &                     & -25548082.3\sym{***}& -25548082.3\sym{***}&                     \\
                    &                     &     (-5.02)         &     (-5.02)         &                     \\
\addlinespace
Lunenburg           &                     & -26707931.8\sym{***}& -26707931.8\sym{***}&                     \\
                    &                     &     (-3.32)         &     (-3.32)         &                     \\
\addlinespace
Lynn                &                     & -21462921.1\sym{***}& -21462921.1\sym{***}&                     \\
                    &                     &     (-6.33)         &     (-6.33)         &                     \\
\addlinespace
Lynnfield           &                     &    429208.2         &    429208.2         &                     \\
                    &                     &      (0.05)         &      (0.05)         &                     \\
\addlinespace
Malden              &                     &   6937988.9         &   6937988.9         &                     \\
                    &                     &      (1.94)         &      (1.94)         &                     \\
\addlinespace
Mansfield           &                     & -15826011.6\sym{**} & -15826011.6\sym{**} &                     \\
                    &                     &     (-3.17)         &     (-3.17)         &                     \\
\addlinespace
Marblehead          &                     & -24872624.7\sym{***}& -24872624.7\sym{***}&                     \\
                    &                     &     (-4.12)         &     (-4.12)         &                     \\
\addlinespace
Marshfield          &                     & -25486617.7\sym{***}& -25486617.7\sym{***}&                     \\
                    &                     &     (-5.59)         &     (-5.59)         &                     \\
\addlinespace
Mashpee             &                     & -24274364.9\sym{**} & -24274364.9\sym{**} &                     \\
                    &                     &     (-3.26)         &     (-3.26)         &                     \\
\addlinespace
Methuen             &                     & -17599579.2\sym{***}& -17599579.2\sym{***}&                     \\
                    &                     &     (-5.10)         &     (-5.10)         &                     \\
\addlinespace
Middleboro          &                     & -15039148.7\sym{***}& -15039148.7\sym{***}&                     \\
                    &                     &     (-3.79)         &     (-3.79)         &                     \\
\addlinespace
Milford             &                     &  -7530303.0         &  -7530303.0         &                     \\
                    &                     &     (-1.54)         &     (-1.54)         &                     \\
\addlinespace
Millbury            &                     & -23455764.3\sym{***}& -23455764.3\sym{***}&                     \\
                    &                     &     (-3.55)         &     (-3.55)         &                     \\
\addlinespace
Needham             &                     &  45061315.4\sym{***}&  45061315.4\sym{***}&                     \\
                    &                     &      (8.23)         &      (8.23)         &                     \\
\addlinespace
New Bedford         &                     & -25410999.4\sym{***}& -25410999.4\sym{***}&                     \\
                    &                     &     (-8.35)         &     (-8.35)         &                     \\
\addlinespace
Newburyport         &                     & -21570253.8\sym{***}& -21570253.8\sym{***}&                     \\
                    &                     &     (-4.14)         &     (-4.14)         &                     \\
\addlinespace
North Adams         &                     & -24978653.4\sym{***}& -24978653.4\sym{***}&                     \\
                    &                     &     (-5.11)         &     (-5.11)         &                     \\
\addlinespace
North Andover       &                     &  -4813790.9         &  -4813790.9         &                     \\
                    &                     &     (-1.16)         &     (-1.16)         &                     \\
\addlinespace
North Attleboro     &                     & -24642950.8\sym{***}& -24642950.8\sym{***}&                     \\
                    &                     &     (-5.21)         &     (-5.21)         &                     \\
\addlinespace
North Billerica     &                     &  -9778512.3         &  -9778512.3         &                     \\
                    &                     &     (-1.62)         &     (-1.62)         &                     \\
\addlinespace
North Dartmouth     &                     & -15474811.8         & -15474811.8         &                     \\
                    &                     &     (-1.92)         &     (-1.92)         &                     \\
\addlinespace
Northampton         &                     & -25051692.1\sym{***}& -25051692.1\sym{***}&                     \\
                    &                     &     (-4.31)         &     (-4.31)         &                     \\
\addlinespace
Northborough        &                     &  49673648.2\sym{***}&  49673648.2\sym{***}&                     \\
                    &                     &      (8.22)         &      (8.22)         &                     \\
\addlinespace
Norton              &                     &  -7666259.5         &  -7666259.5         &                     \\
                    &                     &     (-1.40)         &     (-1.40)         &                     \\
\addlinespace
Norwood             &                     & 135282132.6\sym{***}& 135282132.6\sym{***}&                     \\
                    &                     &     (32.98)         &     (32.98)         &                     \\
\addlinespace
Oxford              &                     & -12619694.0         & -12619694.0         &                     \\
                    &                     &     (-1.91)         &     (-1.91)         &                     \\
\addlinespace
Peabody             &                     &   9977389.1\sym{**} &   9977389.1\sym{**} &                     \\
                    &                     &      (2.94)         &      (2.94)         &                     \\
\addlinespace
Pittsfield          &                     & -25617594.5\sym{***}& -25617594.5\sym{***}&                     \\
                    &                     &     (-7.64)         &     (-7.64)         &                     \\
\addlinespace
Plymouth            &                     & -26008178.7\sym{***}& -26008178.7\sym{***}&                     \\
                    &                     &     (-4.57)         &     (-4.57)         &                     \\
\addlinespace
Quincy              &                     &  -5122621.6         &  -5122621.6         &                     \\
                    &                     &     (-1.03)         &     (-1.03)         &                     \\
\addlinespace
Randolph            &                     &  -2407969.7         &  -2407969.7         &                     \\
                    &                     &     (-0.67)         &     (-0.67)         &                     \\
\addlinespace
Revere              &                     &   3580359.7         &   3580359.7         &                     \\
                    &                     &      (0.45)         &      (0.45)         &                     \\
\addlinespace
Rockland            &                     & -20926211.3\sym{***}& -20926211.3\sym{***}&                     \\
                    &                     &     (-5.36)         &     (-5.36)         &                     \\
\addlinespace
Salem               &                     & -19892879.6\sym{***}& -19892879.6\sym{***}&                     \\
                    &                     &     (-5.38)         &     (-5.38)         &                     \\
\addlinespace
Sandwich            &                     & -25081254.5\sym{***}& -25081254.5\sym{***}&                     \\
                    &                     &     (-3.37)         &     (-3.37)         &                     \\
\addlinespace
Saugus              &                     &   -340993.8         &   -340993.8         &                     \\
                    &                     &     (-0.08)         &     (-0.08)         &                     \\
\addlinespace
Seekonk             &                     &  12790285.1\sym{**} &  12790285.1\sym{**} &                     \\
                    &                     &      (2.78)         &      (2.78)         &                     \\
\addlinespace
Shirley             &                     & -26310641.7\sym{***}& -26310641.7\sym{***}&                     \\
                    &                     &     (-4.67)         &     (-4.67)         &                     \\
\addlinespace
Shrewsbury          &                     & -13932047.6\sym{*}  & -13932047.6\sym{*}  &                     \\
                    &                     &     (-2.21)         &     (-2.21)         &                     \\
\addlinespace
Somerville          &                     & -23932481.5\sym{***}& -23932481.5\sym{***}&                     \\
                    &                     &     (-3.63)         &     (-3.63)         &                     \\
\addlinespace
South Hadley        &                     & -24837142.8\sym{***}& -24837142.8\sym{***}&                     \\
                    &                     &     (-4.77)         &     (-4.77)         &                     \\
\addlinespace
Southbridge         &                     & -25986587.2\sym{***}& -25986587.2\sym{***}&                     \\
                    &                     &     (-6.88)         &     (-6.88)         &                     \\
\addlinespace
Southwick           &                     & -25424600.0\sym{***}& -25424600.0\sym{***}&                     \\
                    &                     &     (-3.65)         &     (-3.65)         &                     \\
\addlinespace
Spencer             &                     & -26098696.3\sym{***}& -26098696.3\sym{***}&                     \\
                    &                     &     (-5.12)         &     (-5.12)         &                     \\
\addlinespace
Springfield         &                     & -21965898.8\sym{***}& -21965898.8\sym{***}&                     \\
                    &                     &     (-7.48)         &     (-7.48)         &                     \\
\addlinespace
Stoughton           &                     & -13918342.5\sym{***}& -13918342.5\sym{***}&                     \\
                    &                     &     (-3.68)         &     (-3.68)         &                     \\
\addlinespace
Swampscott          &                     &  -6303624.1         &  -6303624.1         &                     \\
                    &                     &     (-1.18)         &     (-1.18)         &                     \\
\addlinespace
Taunton             &                     & -25117756.6\sym{***}& -25117756.6\sym{***}&                     \\
                    &                     &     (-7.25)         &     (-7.25)         &                     \\
\addlinespace
Tewksbury           &                     &   4960284.1         &   4960284.1         &                     \\
                    &                     &      (1.11)         &      (1.11)         &                     \\
\addlinespace
Three Rivers        &                     & -25876069.9\sym{***}& -25876069.9\sym{***}&                     \\
                    &                     &     (-3.71)         &     (-3.71)         &                     \\
\addlinespace
Tyngsboro           &                     & -23326009.0\sym{***}& -23326009.0\sym{***}&                     \\
                    &                     &     (-3.35)         &     (-3.35)         &                     \\
\addlinespace
Wakefield           &                     & -13733066.0\sym{**} & -13733066.0\sym{**} &                     \\
                    &                     &     (-2.70)         &     (-2.70)         &                     \\
\addlinespace
Walpole             &                     & -13399797.3\sym{*}  & -13399797.3\sym{*}  &                     \\
                    &                     &     (-2.30)         &     (-2.30)         &                     \\
\addlinespace
Waltham             &                     &    435329.0         &    435329.0         &                     \\
                    &                     &      (0.12)         &      (0.12)         &                     \\
\addlinespace
Ware                &                     & -26606046.0\sym{***}& -26606046.0\sym{***}&                     \\
                    &                     &     (-5.72)         &     (-5.72)         &                     \\
\addlinespace
Watertown           &                     &  22686557.5\sym{***}&  22686557.5\sym{***}&                     \\
                    &                     &      (3.44)         &      (3.44)         &                     \\
\addlinespace
Webster             &                     & -25363678.1\sym{***}& -25363678.1\sym{***}&                     \\
                    &                     &     (-4.03)         &     (-4.03)         &                     \\
\addlinespace
West Springfield    &                     & -25265471.7\sym{***}& -25265471.7\sym{***}&                     \\
                    &                     &     (-5.88)         &     (-5.88)         &                     \\
\addlinespace
Westborough         &                     &   5644711.5         &   5644711.5         &                     \\
                    &                     &      (1.29)         &      (1.29)         &                     \\
\addlinespace
Westwood            &                     &   5943592.0         &   5943592.0         &                     \\
                    &                     &      (0.80)         &      (0.80)         &                     \\
\addlinespace
Weymouth            &                     &  -2354873.6         &  -2354873.6         &                     \\
                    &                     &     (-0.44)         &     (-0.44)         &                     \\
\addlinespace
Whitinsville        &                     & -26113031.8\sym{**} & -26113031.8\sym{**} &                     \\
                    &                     &     (-3.25)         &     (-3.25)         &                     \\
\addlinespace
Whitman             &                     & -24430447.6\sym{***}& -24430447.6\sym{***}&                     \\
                    &                     &     (-4.69)         &     (-4.69)         &                     \\
\addlinespace
Winchendon          &                     & -26829580.4\sym{***}& -26829580.4\sym{***}&                     \\
                    &                     &     (-3.85)         &     (-3.85)         &                     \\
\addlinespace
Woburn              &                     &  51069929.9\sym{***}&  51069929.9\sym{***}&                     \\
                    &                     &      (9.05)         &      (9.05)         &                     \\
\addlinespace
Worcester           &                     & -23487792.3\sym{***}& -23487792.3\sym{***}&                     \\
                    &                     &     (-7.79)         &     (-7.79)         &                     \\
\addlinespace
group(property\_address\_city file\_year)=1&                     &                     &                     &           0         \\
                    &                     &                     &                     &         (.)         \\
\addlinespace
group(property\_address\_city file\_year)=2&                     &                     &                     & -25607702.2\sym{**} \\
                    &                     &                     &                     &     (-2.99)         \\
\addlinespace
group(property\_address\_city file\_year)=3&                     &                     &                     & -21284383.9         \\
                    &                     &                     &                     &     (-1.85)         \\
\addlinespace
group(property\_address\_city file\_year)=7&                     &                     &                     & -38581122.2\sym{***}\\
                    &                     &                     &                     &     (-4.94)         \\
\addlinespace
group(property\_address\_city file\_year)=8&                     &                     &                     & -38411331.2\sym{***}\\
                    &                     &                     &                     &     (-4.90)         \\
\addlinespace
group(property\_address\_city file\_year)=9&                     &                     &                     & -34767371.4\sym{***}\\
                    &                     &                     &                     &     (-4.31)         \\
\addlinespace
group(property\_address\_city file\_year)=11&                     &                     &                     & -34630813.9\sym{***}\\
                    &                     &                     &                     &     (-4.27)         \\
\addlinespace
group(property\_address\_city file\_year)=12&                     &                     &                     & -26507586.7\sym{**} \\
                    &                     &                     &                     &     (-3.25)         \\
\addlinespace
group(property\_address\_city file\_year)=13&                     &                     &                     &  -7386286.8         \\
                    &                     &                     &                     &     (-0.72)         \\
\addlinespace
group(property\_address\_city file\_year)=14&                     &                     &                     & -17859840.8         \\
                    &                     &                     &                     &     (-1.64)         \\
\addlinespace
group(property\_address\_city file\_year)=23&                     &                     &                     & -38408518.6\sym{***}\\
                    &                     &                     &                     &     (-4.91)         \\
\addlinespace
group(property\_address\_city file\_year)=24&                     &                     &                     & -36264514.4\sym{***}\\
                    &                     &                     &                     &     (-4.60)         \\
\addlinespace
group(property\_address\_city file\_year)=26&                     &                     &                     & -38279509.7\sym{***}\\
                    &                     &                     &                     &     (-4.89)         \\
\addlinespace
group(property\_address\_city file\_year)=31&                     &                     &                     &  -6458709.7         \\
                    &                     &                     &                     &     (-0.48)         \\
\addlinespace
group(property\_address\_city file\_year)=33&                     &                     &                     & -37591120.1\sym{***}\\
                    &                     &                     &                     &     (-4.81)         \\
\addlinespace
group(property\_address\_city file\_year)=34&                     &                     &                     & -36376733.5\sym{***}\\
                    &                     &                     &                     &     (-4.63)         \\
\addlinespace
group(property\_address\_city file\_year)=35&                     &                     &                     &   6571579.9         \\
                    &                     &                     &                     &      (0.24)         \\
\addlinespace
group(property\_address\_city file\_year)=39&                     &                     &                     & -26410797.0\sym{**} \\
                    &                     &                     &                     &     (-3.22)         \\
\addlinespace
group(property\_address\_city file\_year)=40&                     &                     &                     & -30562560.8\sym{***}\\
                    &                     &                     &                     &     (-3.63)         \\
\addlinespace
group(property\_address\_city file\_year)=42&                     &                     &                     &     17743.6         \\
                    &                     &                     &                     &      (0.00)         \\
\addlinespace
group(property\_address\_city file\_year)=43&                     &                     &                     &  -7566228.0         \\
                    &                     &                     &                     &     (-0.73)         \\
\addlinespace
group(property\_address\_city file\_year)=53&                     &                     &                     &  23206974.1\sym{*}  \\
                    &                     &                     &                     &      (2.30)         \\
\addlinespace
group(property\_address\_city file\_year)=54&                     &                     &                     & -37332881.4\sym{***}\\
                    &                     &                     &                     &     (-4.76)         \\
\addlinespace
group(property\_address\_city file\_year)=56&                     &                     &                     &   -474304.1         \\
                    &                     &                     &                     &     (-0.05)         \\
\addlinespace
group(property\_address\_city file\_year)=58&                     &                     &                     & -33587109.7\sym{***}\\
                    &                     &                     &                     &     (-4.28)         \\
\addlinespace
group(property\_address\_city file\_year)=59&                     &                     &                     & -34174537.7\sym{***}\\
                    &                     &                     &                     &     (-4.34)         \\
\addlinespace
group(property\_address\_city file\_year)=60&                     &                     &                     & -26000080.5\sym{**} \\
                    &                     &                     &                     &     (-2.61)         \\
\addlinespace
group(property\_address\_city file\_year)=66&                     &                     &                     &  30346290.9         \\
                    &                     &                     &                     &      (1.64)         \\
\addlinespace
group(property\_address\_city file\_year)=67&                     &                     &                     &  -1766588.2         \\
                    &                     &                     &                     &     (-0.18)         \\
\addlinespace
group(property\_address\_city file\_year)=68&                     &                     &                     & -17027153.2         \\
                    &                     &                     &                     &     (-1.44)         \\
\addlinespace
group(property\_address\_city file\_year)=73&                     &                     &                     & -16144028.9\sym{*}  \\
                    &                     &                     &                     &     (-2.06)         \\
\addlinespace
group(property\_address\_city file\_year)=74&                     &                     &                     & -31298276.4\sym{***}\\
                    &                     &                     &                     &     (-3.53)         \\
\addlinespace
group(property\_address\_city file\_year)=75&                     &                     &                     &  -7340083.6         \\
                    &                     &                     &                     &     (-0.70)         \\
\addlinespace
group(property\_address\_city file\_year)=83&                     &                     &                     & -35489242.1\sym{***}\\
                    &                     &                     &                     &     (-4.50)         \\
\addlinespace
group(property\_address\_city file\_year)=84&                     &                     &                     & -37890557.6\sym{***}\\
                    &                     &                     &                     &     (-4.84)         \\
\addlinespace
group(property\_address\_city file\_year)=88&                     &                     &                     &  24176473.6         \\
                    &                     &                     &                     &      (1.77)         \\
\addlinespace
group(property\_address\_city file\_year)=92&                     &                     &                     & -12488676.4         \\
                    &                     &                     &                     &     (-1.06)         \\
\addlinespace
group(property\_address\_city file\_year)=99&                     &                     &                     & -35936941.8\sym{***}\\
                    &                     &                     &                     &     (-4.50)         \\
\addlinespace
group(property\_address\_city file\_year)=100&                     &                     &                     & -38696642.4\sym{***}\\
                    &                     &                     &                     &     (-4.94)         \\
\addlinespace
group(property\_address\_city file\_year)=103&                     &                     &                     & -28496105.0\sym{**} \\
                    &                     &                     &                     &     (-3.22)         \\
\addlinespace
group(property\_address\_city file\_year)=113&                     &                     &                     & -30890843.1\sym{***}\\
                    &                     &                     &                     &     (-3.52)         \\
\addlinespace
group(property\_address\_city file\_year)=120&                     &                     &                     & -20911443.0         \\
                    &                     &                     &                     &     (-1.95)         \\
\addlinespace
group(property\_address\_city file\_year)=121&                     &                     &                     & -38546947.5\sym{***}\\
                    &                     &                     &                     &     (-4.93)         \\
\addlinespace
group(property\_address\_city file\_year)=122&                     &                     &                     & -36566747.8\sym{***}\\
                    &                     &                     &                     &     (-4.61)         \\
\addlinespace
group(property\_address\_city file\_year)=123&                     &                     &                     & -33882902.8\sym{***}\\
                    &                     &                     &                     &     (-4.31)         \\
\addlinespace
group(property\_address\_city file\_year)=125&                     &                     &                     & -35520028.9\sym{***}\\
                    &                     &                     &                     &     (-4.50)         \\
\addlinespace
group(property\_address\_city file\_year)=126&                     &                     &                     & -34208737.4\sym{***}\\
                    &                     &                     &                     &     (-4.16)         \\
\addlinespace
group(property\_address\_city file\_year)=127&                     &                     &                     & -37615554.7\sym{***}\\
                    &                     &                     &                     &     (-4.81)         \\
\addlinespace
group(property\_address\_city file\_year)=128&                     &                     &                     & -37542381.2\sym{***}\\
                    &                     &                     &                     &     (-4.80)         \\
\addlinespace
group(property\_address\_city file\_year)=132&                     &                     &                     &  10784136.1         \\
                    &                     &                     &                     &      (1.37)         \\
\addlinespace
group(property\_address\_city file\_year)=134&                     &                     &                     &   9632586.1         \\
                    &                     &                     &                     &      (1.22)         \\
\addlinespace
group(property\_address\_city file\_year)=135&                     &                     &                     & -16437743.6\sym{*}  \\
                    &                     &                     &                     &     (-1.99)         \\
\addlinespace
group(property\_address\_city file\_year)=136&                     &                     &                     & -20864508.2\sym{*}  \\
                    &                     &                     &                     &     (-2.23)         \\
\addlinespace
group(property\_address\_city file\_year)=137&                     &                     &                     &  -7993710.8         \\
                    &                     &                     &                     &     (-0.74)         \\
\addlinespace
group(property\_address\_city file\_year)=138&                     &                     &                     & -34985127.9\sym{***}\\
                    &                     &                     &                     &     (-4.42)         \\
\addlinespace
group(property\_address\_city file\_year)=142&                     &                     &                     & -31556449.3\sym{***}\\
                    &                     &                     &                     &     (-3.94)         \\
\addlinespace
group(property\_address\_city file\_year)=143&                     &                     &                     & -28620927.6\sym{***}\\
                    &                     &                     &                     &     (-3.48)         \\
\addlinespace
group(property\_address\_city file\_year)=144&                     &                     &                     & -28153048.9\sym{**} \\
                    &                     &                     &                     &     (-3.16)         \\
\addlinespace
group(property\_address\_city file\_year)=147&                     &                     &                     & -35823404.4\sym{***}\\
                    &                     &                     &                     &     (-4.51)         \\
\addlinespace
group(property\_address\_city file\_year)=153&                     &                     &                     & -38485321.4\sym{***}\\
                    &                     &                     &                     &     (-4.92)         \\
\addlinespace
group(property\_address\_city file\_year)=156&                     &                     &                     & -33011555.7\sym{***}\\
                    &                     &                     &                     &     (-4.19)         \\
\addlinespace
group(property\_address\_city file\_year)=164&                     &                     &                     & -36537387.6\sym{***}\\
                    &                     &                     &                     &     (-4.65)         \\
\addlinespace
group(property\_address\_city file\_year)=167&                     &                     &                     & -38203020.1\sym{***}\\
                    &                     &                     &                     &     (-4.89)         \\
\addlinespace
group(property\_address\_city file\_year)=168&                     &                     &                     & -31817841.1\sym{***}\\
                    &                     &                     &                     &     (-3.55)         \\
\addlinespace
group(property\_address\_city file\_year)=169&                     &                     &                     & -25178303.5\sym{*}  \\
                    &                     &                     &                     &     (-2.30)         \\
\addlinespace
group(property\_address\_city file\_year)=171&                     &                     &                     & -36001309.4\sym{***}\\
                    &                     &                     &                     &     (-4.57)         \\
\addlinespace
group(property\_address\_city file\_year)=172&                     &                     &                     & -38116676.0\sym{***}\\
                    &                     &                     &                     &     (-4.88)         \\
\addlinespace
group(property\_address\_city file\_year)=173&                     &                     &                     & -37655672.3\sym{***}\\
                    &                     &                     &                     &     (-4.75)         \\
\addlinespace
group(property\_address\_city file\_year)=174&                     &                     &                     & -35945808.4\sym{***}\\
                    &                     &                     &                     &     (-4.55)         \\
\addlinespace
group(property\_address\_city file\_year)=179&                     &                     &                     & -35689685.3\sym{***}\\
                    &                     &                     &                     &     (-4.52)         \\
\addlinespace
group(property\_address\_city file\_year)=180&                     &                     &                     & -30243768.9\sym{***}\\
                    &                     &                     &                     &     (-3.70)         \\
\addlinespace
group(property\_address\_city file\_year)=182&                     &                     &                     & -35512860.3\sym{***}\\
                    &                     &                     &                     &     (-4.53)         \\
\addlinespace
group(property\_address\_city file\_year)=183&                     &                     &                     & -35437021.0\sym{***}\\
                    &                     &                     &                     &     (-4.52)         \\
\addlinespace
group(property\_address\_city file\_year)=187&                     &                     &                     & -33818835.1\sym{***}\\
                    &                     &                     &                     &     (-4.30)         \\
\addlinespace
group(property\_address\_city file\_year)=194&                     &                     &                     & -30351764.1\sym{***}\\
                    &                     &                     &                     &     (-3.87)         \\
\addlinespace
group(property\_address\_city file\_year)=195&                     &                     &                     & -33456532.5\sym{***}\\
                    &                     &                     &                     &     (-4.26)         \\
\addlinespace
group(property\_address\_city file\_year)=196&                     &                     &                     & -37376620.2\sym{***}\\
                    &                     &                     &                     &     (-4.76)         \\
\addlinespace
group(property\_address\_city file\_year)=197&                     &                     &                     & -38272695.2\sym{***}\\
                    &                     &                     &                     &     (-4.87)         \\
\addlinespace
group(property\_address\_city file\_year)=198&                     &                     &                     & -38542293.9\sym{***}\\
                    &                     &                     &                     &     (-4.92)         \\
\addlinespace
group(property\_address\_city file\_year)=199&                     &                     &                     & -33415366.0\sym{***}\\
                    &                     &                     &                     &     (-4.23)         \\
\addlinespace
group(property\_address\_city file\_year)=200&                     &                     &                     & -32091179.2\sym{***}\\
                    &                     &                     &                     &     (-3.98)         \\
\addlinespace
group(property\_address\_city file\_year)=201&                     &                     &                     & -11405153.9         \\
                    &                     &                     &                     &     (-1.15)         \\
\addlinespace
group(property\_address\_city file\_year)=203&                     &                     &                     &  -8575986.1         \\
                    &                     &                     &                     &     (-0.88)         \\
\addlinespace
group(property\_address\_city file\_year)=204&                     &                     &                     &  -2489181.1         \\
                    &                     &                     &                     &     (-0.26)         \\
\addlinespace
group(property\_address\_city file\_year)=206&                     &                     &                     & -29161593.4\sym{***}\\
                    &                     &                     &                     &     (-3.56)         \\
\addlinespace
group(property\_address\_city file\_year)=207&                     &                     &                     & -25289163.9\sym{**} \\
                    &                     &                     &                     &     (-2.94)         \\
\addlinespace
group(property\_address\_city file\_year)=208&                     &                     &                     & -36814423.9\sym{***}\\
                    &                     &                     &                     &     (-4.59)         \\
\addlinespace
group(property\_address\_city file\_year)=209&                     &                     &                     & -37786016.4\sym{***}\\
                    &                     &                     &                     &     (-4.79)         \\
\addlinespace
group(property\_address\_city file\_year)=212&                     &                     &                     & -35944881.1\sym{***}\\
                    &                     &                     &                     &     (-4.54)         \\
\addlinespace
group(property\_address\_city file\_year)=213&                     &                     &                     & -35623833.5\sym{***}\\
                    &                     &                     &                     &     (-4.50)         \\
\addlinespace
group(property\_address\_city file\_year)=214&                     &                     &                     & -37873195.8\sym{***}\\
                    &                     &                     &                     &     (-4.84)         \\
\addlinespace
group(property\_address\_city file\_year)=216&                     &                     &                     & -36363903.5\sym{***}\\
                    &                     &                     &                     &     (-4.64)         \\
\addlinespace
group(property\_address\_city file\_year)=224&                     &                     &                     & -29612338.5\sym{***}\\
                    &                     &                     &                     &     (-3.61)         \\
\addlinespace
group(property\_address\_city file\_year)=225&                     &                     &                     & -29769927.3\sym{***}\\
                    &                     &                     &                     &     (-3.64)         \\
\addlinespace
group(property\_address\_city file\_year)=226&                     &                     &                     & -35920725.6\sym{***}\\
                    &                     &                     &                     &     (-4.46)         \\
\addlinespace
group(property\_address\_city file\_year)=227&                     &                     &                     & -19714858.5\sym{*}  \\
                    &                     &                     &                     &     (-2.18)         \\
\addlinespace
group(property\_address\_city file\_year)=229&                     &                     &                     & -24169190.7\sym{*}  \\
                    &                     &                     &                     &     (-2.43)         \\
\addlinespace
group(property\_address\_city file\_year)=230&                     &                     &                     & -16642502.5\sym{*}  \\
                    &                     &                     &                     &     (-1.99)         \\
\addlinespace
group(property\_address\_city file\_year)=232&                     &                     &                     & -35290126.4\sym{***}\\
                    &                     &                     &                     &     (-4.36)         \\
\addlinespace
group(property\_address\_city file\_year)=242&                     &                     &                     &  15453086.1         \\
                    &                     &                     &                     &      (0.73)         \\
\addlinespace
group(property\_address\_city file\_year)=243&                     &                     &                     &  44111906.4\sym{***}\\
                    &                     &                     &                     &      (4.45)         \\
\addlinespace
group(property\_address\_city file\_year)=246&                     &                     &                     & -37288510.0\sym{***}\\
                    &                     &                     &                     &     (-4.76)         \\
\addlinespace
group(property\_address\_city file\_year)=248&                     &                     &                     & -32621058.9\sym{***}\\
                    &                     &                     &                     &     (-4.15)         \\
\addlinespace
group(property\_address\_city file\_year)=249&                     &                     &                     & -36158196.4\sym{***}\\
                    &                     &                     &                     &     (-4.55)         \\
\addlinespace
group(property\_address\_city file\_year)=251&                     &                     &                     & -36677620.1\sym{***}\\
                    &                     &                     &                     &     (-4.68)         \\
\addlinespace
group(property\_address\_city file\_year)=252&                     &                     &                     & -37842382.7\sym{***}\\
                    &                     &                     &                     &     (-4.81)         \\
\addlinespace
group(property\_address\_city file\_year)=253&                     &                     &                     &  -9891138.9         \\
                    &                     &                     &                     &     (-1.03)         \\
\addlinespace
group(property\_address\_city file\_year)=254&                     &                     &                     & -23094891.8\sym{*}  \\
                    &                     &                     &                     &     (-2.52)         \\
\addlinespace
group(property\_address\_city file\_year)=255&                     &                     &                     & -36366273.9\sym{***}\\
                    &                     &                     &                     &     (-4.62)         \\
\addlinespace
group(property\_address\_city file\_year)=256&                     &                     &                     & -37392816.4\sym{***}\\
                    &                     &                     &                     &     (-4.74)         \\
\addlinespace
group(property\_address\_city file\_year)=257&                     &                     &                     & -21949701.4         \\
                    &                     &                     &                     &     (-1.85)         \\
\addlinespace
group(property\_address\_city file\_year)=258&                     &                     &                     & -21556393.9         \\
                    &                     &                     &                     &     (-1.83)         \\
\addlinespace
group(property\_address\_city file\_year)=261&                     &                     &                     & -27309173.9\sym{**} \\
                    &                     &                     &                     &     (-3.08)         \\
\addlinespace
group(property\_address\_city file\_year)=271&                     &                     &                     & -38347156.4\sym{***}\\
                    &                     &                     &                     &     (-4.86)         \\
\addlinespace
group(property\_address\_city file\_year)=273&                     &                     &                     & -34577851.5\sym{***}\\
                    &                     &                     &                     &     (-4.24)         \\
\addlinespace
group(property\_address\_city file\_year)=274&                     &                     &                     &  37839286.1\sym{***}\\
                    &                     &                     &                     &      (4.83)         \\
\addlinespace
group(property\_address\_city file\_year)=277&                     &                     &                     & -30100413.9\sym{**} \\
                    &                     &                     &                     &     (-2.94)         \\
\addlinespace
group(property\_address\_city file\_year)=278&                     &                     &                     & -13288240.5         \\
                    &                     &                     &                     &     (-1.28)         \\
\addlinespace
group(property\_address\_city file\_year)=279&                     &                     &                     & 171070980.6\sym{***}\\
                    &                     &                     &                     &      (7.17)         \\
\addlinespace
group(property\_address\_city file\_year)=280&                     &                     &                     &  66019571.9\sym{***}\\
                    &                     &                     &                     &      (3.83)         \\
\addlinespace
group(property\_address\_city file\_year)=288&                     &                     &                     & -24548443.6\sym{*}  \\
                    &                     &                     &                     &     (-2.28)         \\
\addlinespace
group(property\_address\_city file\_year)=290&                     &                     &                     &  -6453926.4         \\
                    &                     &                     &                     &     (-0.73)         \\
\addlinespace
group(property\_address\_city file\_year)=291&                     &                     &                     &   4959403.0         \\
                    &                     &                     &                     &      (0.52)         \\
\addlinespace
group(property\_address\_city file\_year)=296&                     &                     &                     & -37918902.4\sym{***}\\
                    &                     &                     &                     &     (-4.85)         \\
\addlinespace
group(property\_address\_city file\_year)=297&                     &                     &                     & -37250575.6\sym{***}\\
                    &                     &                     &                     &     (-4.76)         \\
\addlinespace
group(property\_address\_city file\_year)=299&                     &                     &                     & -35650288.1\sym{***}\\
                    &                     &                     &                     &     (-4.42)         \\
\addlinespace
group(property\_address\_city file\_year)=302&                     &                     &                     & -14794934.9         \\
                    &                     &                     &                     &     (-1.32)         \\
\addlinespace
group(property\_address\_city file\_year)=303&                     &                     &                     & -15642334.1         \\
                    &                     &                     &                     &     (-1.81)         \\
\addlinespace
group(property\_address\_city file\_year)=304&                     &                     &                     & -12480878.8         \\
                    &                     &                     &                     &     (-1.05)         \\
\addlinespace
group(property\_address\_city file\_year)=308&                     &                     &                     &  -8685368.9         \\
                    &                     &                     &                     &     (-0.49)         \\
\addlinespace
group(property\_address\_city file\_year)=310&                     &                     &                     & -32778990.4\sym{***}\\
                    &                     &                     &                     &     (-4.16)         \\
\addlinespace
group(property\_address\_city file\_year)=318&                     &                     &                     & -32113017.2\sym{***}\\
                    &                     &                     &                     &     (-4.04)         \\
\addlinespace
group(property\_address\_city file\_year)=320&                     &                     &                     & -37296643.1\sym{***}\\
                    &                     &                     &                     &     (-4.76)         \\
\addlinespace
group(property\_address\_city file\_year)=321&                     &                     &                     & -21065231.0\sym{*}  \\
                    &                     &                     &                     &     (-2.04)         \\
\addlinespace
group(property\_address\_city file\_year)=322&                     &                     &                     &  -3778856.1         \\
                    &                     &                     &                     &     (-0.23)         \\
\addlinespace
group(property\_address\_city file\_year)=323&                     &                     &                     &   6070469.5         \\
                    &                     &                     &                     &      (0.36)         \\
\addlinespace
group(property\_address\_city file\_year)=325&                     &                     &                     &  -4489793.1         \\
                    &                     &                     &                     &     (-0.36)         \\
\addlinespace
group(property\_address\_city file\_year)=326&                     &                     &                     &   2727158.8         \\
                    &                     &                     &                     &      (0.29)         \\
\addlinespace
group(property\_address\_city file\_year)=330&                     &                     &                     & -38186853.5\sym{***}\\
                    &                     &                     &                     &     (-4.89)         \\
\addlinespace
group(property\_address\_city file\_year)=331&                     &                     &                     & -38358330.5\sym{***}\\
                    &                     &                     &                     &     (-4.89)         \\
\addlinespace
group(property\_address\_city file\_year)=332&                     &                     &                     & -25895736.1\sym{*}  \\
                    &                     &                     &                     &     (-2.53)         \\
\addlinespace
group(property\_address\_city file\_year)=334&                     &                     &                     & -35861231.1\sym{***}\\
                    &                     &                     &                     &     (-4.56)         \\
\addlinespace
group(property\_address\_city file\_year)=344&                     &                     &                     & -36847731.1\sym{***}\\
                    &                     &                     &                     &     (-4.69)         \\
\addlinespace
group(property\_address\_city file\_year)=345&                     &                     &                     & -37030915.7\sym{***}\\
                    &                     &                     &                     &     (-4.71)         \\
\addlinespace
group(property\_address\_city file\_year)=350&                     &                     &                     & -37844551.0\sym{***}\\
                    &                     &                     &                     &     (-4.83)         \\
\addlinespace
group(property\_address\_city file\_year)=351&                     &                     &                     & -38140516.2\sym{***}\\
                    &                     &                     &                     &     (-4.87)         \\
\addlinespace
group(property\_address\_city file\_year)=352&                     &                     &                     & -37366833.5\sym{***}\\
                    &                     &                     &                     &     (-4.75)         \\
\addlinespace
group(property\_address\_city file\_year)=353&                     &                     &                     & -38074639.7\sym{***}\\
                    &                     &                     &                     &     (-4.86)         \\
\addlinespace
group(property\_address\_city file\_year)=355&                     &                     &                     & -35317254.9\sym{***}\\
                    &                     &                     &                     &     (-4.51)         \\
\addlinespace
group(property\_address\_city file\_year)=356&                     &                     &                     & -32231981.1\sym{***}\\
                    &                     &                     &                     &     (-4.09)         \\
\addlinespace
group(property\_address\_city file\_year)=359&                     &                     &                     & -28430715.7\sym{***}\\
                    &                     &                     &                     &     (-3.37)         \\
\addlinespace
group(property\_address\_city file\_year)=360&                     &                     &                     & -23835191.3\sym{**} \\
                    &                     &                     &                     &     (-2.72)         \\
\addlinespace
group(property\_address\_city file\_year)=366&                     &                     &                     & -18299793.4         \\
                    &                     &                     &                     &     (-1.76)         \\
\addlinespace
group(property\_address\_city file\_year)=369&                     &                     &                     & -36289434.6\sym{***}\\
                    &                     &                     &                     &     (-4.62)         \\
\addlinespace
group(property\_address\_city file\_year)=370&                     &                     &                     & -36493934.4\sym{***}\\
                    &                     &                     &                     &     (-4.65)         \\
\addlinespace
group(property\_address\_city file\_year)=372&                     &                     &                     &  -9326920.9         \\
                    &                     &                     &                     &     (-0.98)         \\
\addlinespace
group(property\_address\_city file\_year)=373&                     &                     &                     &  -2475268.6         \\
                    &                     &                     &                     &     (-0.20)         \\
\addlinespace
group(property\_address\_city file\_year)=375&                     &                     &                     & -38163372.8\sym{***}\\
                    &                     &                     &                     &     (-4.87)         \\
\addlinespace
group(property\_address\_city file\_year)=377&                     &                     &                     & -35160371.0\sym{***}\\
                    &                     &                     &                     &     (-4.47)         \\
\addlinespace
group(property\_address\_city file\_year)=383&                     &                     &                     & -22375844.4\sym{*}  \\
                    &                     &                     &                     &     (-2.42)         \\
\addlinespace
group(property\_address\_city file\_year)=384&                     &                     &                     & -30123833.5\sym{***}\\
                    &                     &                     &                     &     (-3.63)         \\
\addlinespace
group(property\_address\_city file\_year)=385&                     &                     &                     & -25234159.3\sym{*}  \\
                    &                     &                     &                     &     (-2.51)         \\
\addlinespace
group(property\_address\_city file\_year)=386&                     &                     &                     &  -8854952.2         \\
                    &                     &                     &                     &     (-0.95)         \\
\addlinespace
group(property\_address\_city file\_year)=387&                     &                     &                     & -18318728.6         \\
                    &                     &                     &                     &     (-1.88)         \\
\addlinespace
group(property\_address\_city file\_year)=388&                     &                     &                     & -38189648.1\sym{***}\\
                    &                     &                     &                     &     (-4.88)         \\
\addlinespace
group(property\_address\_city file\_year)=389&                     &                     &                     & -37389578.2\sym{***}\\
                    &                     &                     &                     &     (-4.73)         \\
\addlinespace
group(property\_address\_city file\_year)=393&                     &                     &                     &  10628481.4         \\
                    &                     &                     &                     &      (0.58)         \\
\addlinespace
group(property\_address\_city file\_year)=394&                     &                     &                     & -37495166.7\sym{***}\\
                    &                     &                     &                     &     (-4.78)         \\
\addlinespace
group(property\_address\_city file\_year)=401&                     &                     &                     & -37444903.2\sym{***}\\
                    &                     &                     &                     &     (-4.79)         \\
\addlinespace
group(property\_address\_city file\_year)=406&                     &                     &                     &  -3258867.6         \\
                    &                     &                     &                     &     (-0.37)         \\
\addlinespace
group(property\_address\_city file\_year)=407&                     &                     &                     & -16465803.5         \\
                    &                     &                     &                     &     (-1.83)         \\
\addlinespace
group(property\_address\_city file\_year)=413&                     &                     &                     &  -6016620.1         \\
                    &                     &                     &                     &     (-0.63)         \\
\addlinespace
group(property\_address\_city file\_year)=414&                     &                     &                     & -14426433.5         \\
                    &                     &                     &                     &     (-1.63)         \\
\addlinespace
group(property\_address\_city file\_year)=415&                     &                     &                     & -37947393.9\sym{***}\\
                    &                     &                     &                     &     (-4.83)         \\
\addlinespace
group(property\_address\_city file\_year)=417&                     &                     &                     & -36315149.7\sym{***}\\
                    &                     &                     &                     &     (-4.62)         \\
\addlinespace
group(property\_address\_city file\_year)=423&                     &                     &                     & -38663942.4\sym{***}\\
                    &                     &                     &                     &     (-4.93)         \\
\addlinespace
group(property\_address\_city file\_year)=426&                     &                     &                     &  39043316.3\sym{**} \\
                    &                     &                     &                     &      (2.60)         \\
\addlinespace
group(property\_address\_city file\_year)=427&                     &                     &                     & -35389716.0\sym{***}\\
                    &                     &                     &                     &     (-4.52)         \\
\addlinespace
Constant            &   7494901.5\sym{***}&  25580389.2\sym{***}&  25580389.2\sym{***}&  38169851.5\sym{***}\\
                    &     (11.15)         &      (8.72)         &      (8.72)         &      (4.70)         \\
\midrule
Observations        &        5567         &        5567         &        5567         &        5567         \\
\bottomrule
\multicolumn{5}{l}{\footnotesize \textit{t} statistics in parentheses}\\
\multicolumn{5}{l}{\footnotesize \sym{*} \(p<0.05\), \sym{**} \(p<0.01\), \sym{***} \(p<0.001\)}\\
\end{tabular}
}

### 2022-12-07 output/01_exploratory/tables/bldg_val_results_table.tex
Created estimation tables

@@
                     &\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}\\
+                    &        b/se&        b/se&        b/se&        b/se\\
 \midrule
-judgment\_for\_plaintiff&   2434984.3\sym{***}&   1161294.0\sym{*}  &   1161294.0\sym{*}  &   1055231.1         \\
-                    &      (4.14)         &      (2.56)         &      (2.56)         &      (0.46)         \\
-\addlinespace
-file\_year=2019      &                     &           0         &           0         &                     \\
-                    &                     &         (.)         &         (.)         &                     \\
-\addlinespace
-file\_year=2020      &                     &    192394.9         &    192394.9         &                     \\
-                    &                     &      (0.41)         &      (0.41)         &                     \\
-\addlinespace
-file\_year=2021      &                     &   1461400.9         &   1461400.9         &                     \\
-                    &                     &      (0.80)         &      (0.80)         &                     \\
-\addlinespace
-Abington            &                     &           0         &           0         &                     \\
-                    &                     &         (.)         &         (.)         &                     \\
-\addlinespace
-Acton               &                     &  -6165616.0         &  -6165616.0         &                     \\
-                    &                     &     (-0.97)         &     (-0.97)         &                     \\
-\addlinespace
-Adams               &                     & -21444727.6\sym{***}& -21444727.6\sym{***}&                     \\
-                    &                     &     (-5.94)         &     (-5.94)         &                     \\
-\addlinespace
-Agawam              &                     & -18038332.4\sym{***}& -18038332.4\sym{***}&                     \\
-                    &                     &     (-3.80)         &     (-3.80)         &                     \\
-\addlinespace
-Amesbury            &                     & -19407326.1\sym{**} & -19407326.1\sym{**} &                     \\
-                    &                     &     (-3.07)         &     (-3.07)         &                     \\
-\addlinespace
-Amherst             &                     & -11242459.5\sym{*}  & -11242459.5\sym{*}  &                     \\
-                    &                     &     (-2.45)         &     (-2.45)         &                     \\
-\addlinespace
-Andover             &                     &  -2085030.0         &  -2085030.0         &                     \\
-                    &                     &     (-0.60)         &     (-0.60)         &                     \\
-\addlinespace
-Athol               &                     & -21616109.3\sym{***}& -21616109.3\sym{***}&                     \\
-                    &                     &     (-4.16)         &     (-4.16)         &                     \\
-\addlinespace
-Attleboro           &                     & -19494997.4\sym{***}& -19494997.4\sym{***}&                     \\
-                    &                     &     (-5.39)         &     (-5.39)         &                     \\
-\addlinespace
-Auburn              &                     & -21471031.4\sym{***}& -21471031.4\sym{***}&                     \\
-                    &                     &     (-3.67)         &     (-3.67)         &                     \\
-\addlinespace
-Bedford             &                     &   2478285.3         &   2478285.3         &                     \\
-                    &                     &      (0.42)         &      (0.42)         &                     \\
-\addlinespace
-Belchertown         &                     & -20404418.7\sym{***}& -20404418.7\sym{***}&                     \\
-                    &                     &     (-5.40)         &     (-5.40)         &                     \\
-\addlinespace
-Bellingham          &                     &  18138281.2\sym{**} &  18138281.2\sym{**} &                     \\
-                    &                     &      (3.10)         &      (3.10)         &                     \\
-\addlinespace
-Beverly             &                     & -14079413.5\sym{***}& -14079413.5\sym{***}&                     \\
-                    &                     &     (-4.85)         &     (-4.85)         &                     \\
-\addlinespace
-Billerica           &                     &   6526049.6         &   6526049.6         &                     \\
-                    &                     &      (1.83)         &      (1.83)         &                     \\
-\addlinespace
-Braintree           &                     &  22784206.9\sym{***}&  22784206.9\sym{***}&                     \\
-                    &                     &      (6.46)         &      (6.46)         &                     \\
-\addlinespace
-Brewster            &                     & -20607212.4\sym{**} & -20607212.4\sym{**} &                     \\
-                    &                     &     (-3.26)         &     (-3.26)         &                     \\
-\addlinespace
-Bridgewater         &                     &   9388781.6\sym{**} &   9388781.6\sym{**} &                     \\
-                    &                     &      (2.95)         &      (2.95)         &                     \\
-\addlinespace
-Brockton            &                     & -17475780.0\sym{***}& -17475780.0\sym{***}&                     \\
-                    &                     &     (-7.32)         &     (-7.32)         &                     \\
-\addlinespace
-Brookline           &                     & -16179317.8\sym{**} & -16179317.8\sym{**} &                     \\
-                    &                     &     (-2.77)         &     (-2.77)         &                     \\
-\addlinespace
-Cambridge           &                     &  26938732.3\sym{***}&  26938732.3\sym{***}&                     \\
-                    &                     &      (7.34)         &      (7.34)         &                     \\
-\addlinespace
-Canton              &                     &   3432893.5         &   3432893.5         &                     \\
-                    &                     &      (0.99)         &      (0.99)         &                     \\
-\addlinespace
-Chelmsford          &                     &  -4604628.5         &  -4604628.5         &                     \\
-                    &                     &     (-0.73)         &     (-0.73)         &                     \\
-\addlinespace
-Chelsea             &                     &  -3808897.8         &  -3808897.8         &                     \\
-                    &                     &     (-0.88)         &     (-0.88)         &                     \\
-\addlinespace
-Chicopee            &                     & -19004695.9\sym{***}& -19004695.9\sym{***}&                     \\
-                    &                     &     (-6.87)         &     (-6.87)         &                     \\
-\addlinespace
-Clinton             &                     & -21059441.8\sym{***}& -21059441.8\sym{***}&                     \\
-                    &                     &     (-4.43)         &     (-4.43)         &                     \\
-\addlinespace
-Concord             &                     &  29495396.8\sym{***}&  29495396.8\sym{***}&                     \\
-                    &                     &      (5.04)         &      (5.04)         &                     \\
-\addlinespace
-Danvers             &                     &  -5577347.4         &  -5577347.4         &                     \\
-                    &                     &     (-1.29)         &     (-1.29)         &                     \\
-\addlinespace
-Dracut              &                     & -19485987.8\sym{***}& -19485987.8\sym{***}&                     \\
-                    &                     &     (-4.52)         &     (-4.52)         &                     \\
-\addlinespace
-Dudley              &                     & -21722608.3\sym{***}& -21722608.3\sym{***}&                     \\
-                    &                     &     (-3.96)         &     (-3.96)         &                     \\
-\addlinespace
-Duxbury             &                     & -15198237.7\sym{**} & -15198237.7\sym{**} &                     \\
-                    &                     &     (-2.77)         &     (-2.77)         &                     \\
-\addlinespace
-East Wareham        &                     & -15344281.4\sym{**} & -15344281.4\sym{**} &                     \\
-                    &                     &     (-2.62)         &     (-2.62)         &                     \\
-\addlinespace
-Everett             &                     &  -7534870.7\sym{*}  &  -7534870.7\sym{*}  &                     \\
-                    &                     &     (-2.05)         &     (-2.05)         &                     \\
-\addlinespace
-Fairhaven           &                     & -21231090.0\sym{***}& -21231090.0\sym{***}&                     \\
-                    &                     &     (-5.71)         &     (-5.71)         &                     \\
-\addlinespace
-Fall River          &                     & -18210525.7\sym{***}& -18210525.7\sym{***}&                     \\
-                    &                     &     (-7.32)         &     (-7.32)         &                     \\
-\addlinespace
-Feeding Hills       &                     & -18650234.9\sym{***}& -18650234.9\sym{***}&                     \\
-                    &                     &     (-5.23)         &     (-5.23)         &                     \\
-\addlinespace
-Fitchburg           &                     & -20960701.9\sym{***}& -20960701.9\sym{***}&                     \\
-                    &                     &     (-8.30)         &     (-8.30)         &                     \\
-\addlinespace
-Foxboro             &                     &  20690798.8\sym{***}&  20690798.8\sym{***}&                     \\
-                    &                     &      (4.35)         &      (4.35)         &                     \\
-\addlinespace
-Foxborough          &                     &  19142493.9\sym{**} &  19142493.9\sym{**} &                     \\
-                    &                     &      (3.03)         &      (3.03)         &                     \\
-\addlinespace
-Framingham          &                     &  -2290752.1         &  -2290752.1         &                     \\
-                    &                     &     (-0.83)         &     (-0.83)         &                     \\
-\addlinespace
-Franklin            &                     &  -4710134.2         &  -4710134.2         &                     \\
-                    &                     &     (-1.25)         &     (-1.25)         &                     \\
-\addlinespace
-Gardner             &                     & -18492792.1\sym{***}& -18492792.1\sym{***}&                     \\
-                    &                     &     (-5.24)         &     (-5.24)         &                     \\
-\addlinespace
-Gloucester          &                     & -14776186.1\sym{***}& -14776186.1\sym{***}&                     \\
-                    &                     &     (-4.80)         &     (-4.80)         &                     \\
-\addlinespace
-Grafton             &                     & -11539053.6         & -11539053.6         &                     \\
-                    &                     &     (-1.82)         &     (-1.82)         &                     \\
-\addlinespace
-Greenfield          &                     & -19186461.0\sym{***}& -19186461.0\sym{***}&                     \\
-                    &                     &     (-4.88)         &     (-4.88)         &                     \\
-\addlinespace
-Hanson              &                     & -21517852.4\sym{***}& -21517852.4\sym{***}&                     \\
-                    &                     &     (-3.40)         &     (-3.40)         &                     \\
-\addlinespace
-Haverhill           &                     & -18493946.4\sym{***}& -18493946.4\sym{***}&                     \\
-                    &                     &     (-6.52)         &     (-6.52)         &                     \\
-\addlinespace
-Holyoke             &                     & -19922013.6\sym{***}& -19922013.6\sym{***}&                     \\
-                    &                     &     (-7.02)         &     (-7.02)         &                     \\
-\addlinespace
-Hudson              &                     & -21242768.8\sym{***}& -21242768.8\sym{***}&                     \\
-                    &                     &     (-3.63)         &     (-3.63)         &                     \\
-\addlinespace
-Hull                &                     & -14403896.8\sym{***}& -14403896.8\sym{***}&                     \\
-                    &                     &     (-3.67)         &     (-3.67)         &                     \\
-\addlinespace
-Hyannis             &                     & -19591284.6\sym{***}& -19591284.6\sym{***}&                     \\
-                    &                     &     (-4.27)         &     (-4.27)         &                     \\
-\addlinespace
-Indian Orchard      &                     & -20946341.5\sym{***}& -20946341.5\sym{***}&                     \\
-                    &                     &     (-7.04)         &     (-7.04)         &                     \\
-\addlinespace
-Ipswich             &                     & -19517731.6\sym{***}& -19517731.6\sym{***}&                     \\
-                    &                     &     (-3.94)         &     (-3.94)         &                     \\
-\addlinespace
-Lakeville           &                     & -17182100.0\sym{***}& -17182100.0\sym{***}&                     \\
-                    &                     &     (-3.88)         &     (-3.88)         &                     \\
-\addlinespace
-Lawrence            &                     & -18777158.2\sym{***}& -18777158.2\sym{***}&                     \\
-                    &                     &     (-7.91)         &     (-7.91)         &                     \\
-\addlinespace
-Leominster          &                     & -17218870.0\sym{***}& -17218870.0\sym{***}&                     \\
-                    &                     &     (-5.85)         &     (-5.85)         &                     \\
-\addlinespace
-Lowell              &                     & -15677026.1\sym{***}& -15677026.1\sym{***}&                     \\
-                    &                     &     (-6.66)         &     (-6.66)         &                     \\
-\addlinespace
-Ludlow              &                     & -20818614.1\sym{***}& -20818614.1\sym{***}&                     \\
-                    &                     &     (-5.20)         &     (-5.20)         &                     \\
-\addlinespace
-Lunenburg           &                     & -21732251.2\sym{***}& -21732251.2\sym{***}&                     \\
-                    &                     &     (-3.44)         &     (-3.44)         &                     \\
-\addlinespace
-Lynn                &                     & -18818313.7\sym{***}& -18818313.7\sym{***}&                     \\
-                    &                     &     (-7.06)         &     (-7.06)         &                     \\
-\addlinespace
-Lynnfield           &                     &  -3055971.2         &  -3055971.2         &                     \\
-                    &                     &     (-0.48)         &     (-0.48)         &                     \\
-\addlinespace
-Malden              &                     &    998329.8         &    998329.8         &                     \\
-                    &                     &      (0.35)         &      (0.35)         &                     \\
-\addlinespace
-Mansfield           &                     & -13438414.8\sym{***}& -13438414.8\sym{***}&                     \\
-                    &                     &     (-3.43)         &     (-3.43)         &                     \\
-\addlinespace
-Marblehead          &                     & -20700912.8\sym{***}& -20700912.8\sym{***}&                     \\
-                    &                     &     (-4.36)         &     (-4.36)         &                     \\
-\addlinespace
-Marshfield          &                     & -20789134.1\sym{***}& -20789134.1\sym{***}&                     \\
-                    &                     &     (-5.80)         &     (-5.80)         &                     \\
-\addlinespace
-Mashpee             &                     & -19830247.1\sym{***}& -19830247.1\sym{***}&                     \\
-                    &                     &     (-3.39)         &     (-3.39)         &                     \\
-\addlinespace
-Methuen             &                     & -15000192.3\sym{***}& -15000192.3\sym{***}&                     \\
-                    &                     &     (-5.53)         &     (-5.53)         &                     \\
-\addlinespace
-Middleboro          &                     & -12265582.7\sym{***}& -12265582.7\sym{***}&                     \\
-                    &                     &     (-3.94)         &     (-3.94)         &                     \\
-\addlinespace
-Milford             &                     &  -9017182.4\sym{*}  &  -9017182.4\sym{*}  &                     \\
-                    &                     &     (-2.34)         &     (-2.34)         &                     \\
-\addlinespace
-Millbury            &                     & -18658188.7\sym{***}& -18658188.7\sym{***}&                     \\
-                    &                     &     (-3.59)         &     (-3.59)         &                     \\
-\addlinespace
-Needham             &                     &  39077459.2\sym{***}&  39077459.2\sym{***}&                     \\
-                    &                     &      (9.08)         &      (9.08)         &                     \\
-\addlinespace
-New Bedford         &                     & -20447207.1\sym{***}& -20447207.1\sym{***}&                     \\
-                    &                     &     (-8.55)         &     (-8.55)         &                     \\
-\addlinespace
-Newburyport         &                     & -17619838.9\sym{***}& -17619838.9\sym{***}&                     \\
-                    &                     &     (-4.30)         &     (-4.30)         &                     \\
-\addlinespace
-North Adams         &                     & -20332323.4\sym{***}& -20332323.4\sym{***}&                     \\
-                    &                     &     (-5.28)         &     (-5.28)         &                     \\
-\addlinespace
-North Andover       &                     &  -4927981.2         &  -4927981.2         &                     \\
-                    &                     &     (-1.52)         &     (-1.52)         &                     \\
-\addlinespace
-North Attleboro     &                     & -20284380.8\sym{***}& -20284380.8\sym{***}&                     \\
-                    &                     &     (-5.45)         &     (-5.45)         &                     \\
-\addlinespace
-North Billerica     &                     &  -8556369.2         &  -8556369.2         &                     \\
-                    &                     &     (-1.80)         &     (-1.80)         &                     \\
-\addlinespace
-North Dartmouth     &                     & -13208231.2\sym{*}  & -13208231.2\sym{*}  &                     \\
-                    &                     &     (-2.09)         &     (-2.09)         &                     \\
-\addlinespace
-Northampton         &                     & -20101965.1\sym{***}& -20101965.1\sym{***}&                     \\
-                    &                     &     (-4.40)         &     (-4.40)         &                     \\
-\addlinespace
-Northborough        &                     &  40356948.8\sym{***}&  40356948.8\sym{***}&                     \\
-                    &                     &      (8.49)         &      (8.49)         &                     \\
-\addlinespace
-Norton              &                     &  -6420841.7         &  -6420841.7         &                     \\
-                    &                     &     (-1.49)         &     (-1.49)         &                     \\
-\addlinespace
-Norwood             &                     &  94746120.3\sym{***}&  94746120.3\sym{***}&                     \\
-                    &                     &     (29.37)         &     (29.37)         &                     \\
-\addlinespace
-Oxford              &                     &  -9152764.4         &  -9152764.4         &                     \\
-                    &                     &     (-1.76)         &     (-1.76)         &                     \\
-\addlinespace
-Peabody             &                     &   9805861.1\sym{***}&   9805861.1\sym{***}&                     \\
-                    &                     &      (3.68)         &      (3.68)         &                     \\
-\addlinespace
-Pittsfield          &                     & -20746717.5\sym{***}& -20746717.5\sym{***}&                     \\
-                    &                     &     (-7.86)         &     (-7.86)         &                     \\
-\addlinespace
-Plymouth            &                     & -20826306.6\sym{***}& -20826306.6\sym{***}&                     \\
-                    &                     &     (-4.65)         &     (-4.65)         &                     \\
-\addlinespace
-Quincy              &                     &  -1743417.5         &  -1743417.5         &                     \\
-                    &                     &     (-0.44)         &     (-0.44)         &                     \\
-\addlinespace
-Randolph            &                     &  -2226994.8         &  -2226994.8         &                     \\
-                    &                     &     (-0.79)         &     (-0.79)         &                     \\
-\addlinespace
-Revere              &                     &   -159168.5         &   -159168.5         &                     \\
-                    &                     &     (-0.03)         &     (-0.03)         &                     \\
-\addlinespace
-Rockland            &                     & -20101861.1\sym{***}& -20101861.1\sym{***}&                     \\
-                    &                     &     (-6.55)         &     (-6.55)         &                     \\
-\addlinespace
-Salem               &                     & -16857836.8\sym{***}& -16857836.8\sym{***}&                     \\
-                    &                     &     (-5.79)         &     (-5.79)         &                     \\
-\addlinespace
-Sandwich            &                     & -20722231.4\sym{***}& -20722231.4\sym{***}&                     \\
-                    &                     &     (-3.54)         &     (-3.54)         &                     \\
-\addlinespace
-Saugus              &                     &   -340363.5         &   -340363.5         &                     \\
-                    &                     &     (-0.10)         &     (-0.10)         &                     \\
-\addlinespace
-Seekonk             &                     &  17681397.2\sym{***}&  17681397.2\sym{***}&                     \\
-                    &                     &      (4.89)         &      (4.89)         &                     \\
-\addlinespace
-Shirley             &                     & -21737007.4\sym{***}& -21737007.4\sym{***}&                     \\
-                    &                     &     (-4.90)         &     (-4.90)         &                     \\
-\addlinespace
-Shrewsbury          &                     & -12117923.8\sym{*}  & -12117923.8\sym{*}  &                     \\
-                    &                     &     (-2.45)         &     (-2.45)         &                     \\
-\addlinespace
-Somerville          &                     & -19566426.9\sym{***}& -19566426.9\sym{***}&                     \\
-                    &                     &     (-3.77)         &     (-3.77)         &                     \\
-\addlinespace
-South Hadley        &                     & -20340123.7\sym{***}& -20340123.7\sym{***}&                     \\
-                    &                     &     (-4.97)         &     (-4.97)         &                     \\
-\addlinespace
-Southbridge         &                     & -21059479.9\sym{***}& -21059479.9\sym{***}&                     \\
-                    &                     &     (-7.09)         &     (-7.09)         &                     \\
-\addlinespace
-Southwick           &                     & -20440194.9\sym{***}& -20440194.9\sym{***}&                     \\
-                    &                     &     (-3.73)         &     (-3.73)         &                     \\
-\addlinespace
-Spencer             &                     & -21062533.5\sym{***}& -21062533.5\sym{***}&                     \\
-                    &                     &     (-5.26)         &     (-5.26)         &                     \\
-\addlinespace
-Springfield         &                     & -17446784.4\sym{***}& -17446784.4\sym{***}&                     \\
-                    &                     &     (-7.56)         &     (-7.56)         &                     \\
-\addlinespace
-Stoughton           &                     & -11389546.7\sym{***}& -11389546.7\sym{***}&                     \\
-                    &                     &     (-3.83)         &     (-3.83)         &                     \\
-\addlinespace
-Swampscott          &                     &  -4547859.6         &  -4547859.6         &                     \\
-                    &                     &     (-1.08)         &     (-1.08)         &                     \\
-\addlinespace
-Taunton             &                     & -20276710.6\sym{***}& -20276710.6\sym{***}&                     \\
-                    &                     &     (-7.44)         &     (-7.44)         &                     \\
-\addlinespace
-Tewksbury           &                     &   5281791.2         &   5281791.2         &                     \\
-                    &                     &      (1.50)         &      (1.50)         &                     \\
-\addlinespace
-Three Rivers        &                     & -21263534.4\sym{***}& -21263534.4\sym{***}&                     \\
-                    &                     &     (-3.88)         &     (-3.88)         &                     \\
-\addlinespace
-Tyngsboro           &                     & -19043379.7\sym{***}& -19043379.7\sym{***}&                     \\
-                    &                     &     (-3.47)         &     (-3.47)         &                     \\
-\addlinespace
-Wakefield           &                     & -12951456.3\sym{**} & -12951456.3\sym{**} &                     \\
-                    &                     &     (-3.24)         &     (-3.24)         &                     \\
-\addlinespace
-Walpole             &                     & -10254842.1\sym{*}  & -10254842.1\sym{*}  &                     \\
-                    &                     &     (-2.24)         &     (-2.24)         &                     \\
-\addlinespace
-Waltham             &                     &  -4458163.9         &  -4458163.9         &                     \\
-                    &                     &     (-1.57)         &     (-1.57)         &                     \\
-\addlinespace
-Ware                &                     & -21385935.2\sym{***}& -21385935.2\sym{***}&                     \\
-                    &                     &     (-5.84)         &     (-5.84)         &                     \\
-\addlinespace
-Watertown           &                     &  14594615.7\sym{**} &  14594615.7\sym{**} &                     \\
-                    &                     &      (2.81)         &      (2.81)         &                     \\
-\addlinespace
-Webster             &                     & -20767336.3\sym{***}& -20767336.3\sym{***}&                     \\
-                    &                     &     (-4.19)         &     (-4.19)         &                     \\
-\addlinespace
-West Springfield    &                     & -20814715.6\sym{***}& -20814715.6\sym{***}&                     \\
-                    &                     &     (-6.16)         &     (-6.16)         &                     \\
-\addlinespace
-Westborough         &                     &   4823814.7         &   4823814.7         &                     \\
-                    &                     &      (1.40)         &      (1.40)         &                     \\
-\addlinespace
-Westwood            &                     &   3245897.8         &   3245897.8         &                     \\
-                    &                     &      (0.56)         &      (0.56)         &                     \\
-\addlinespace
-Weymouth            &                     &  -4254268.3         &  -4254268.3         &                     \\
-                    &                     &     (-1.01)         &     (-1.01)         &                     \\
-\addlinespace
-Whitinsville        &                     & -21120051.2\sym{***}& -21120051.2\sym{***}&                     \\
-                    &                     &     (-3.34)         &     (-3.34)         &                     \\
-\addlinespace
-Whitman             &                     & -19787518.2\sym{***}& -19787518.2\sym{***}&                     \\
-                    &                     &     (-4.83)         &     (-4.83)         &                     \\
-\addlinespace
-Winchendon          &                     & -21661279.7\sym{***}& -21661279.7\sym{***}&                     \\
-                    &                     &     (-3.95)         &     (-3.95)         &                     \\
-\addlinespace
-Woburn              &                     &  42856970.1\sym{***}&  42856970.1\sym{***}&                     \\
-                    &                     &      (9.65)         &      (9.65)         &                     \\
-\addlinespace
-Worcester           &                     & -19269002.4\sym{***}& -19269002.4\sym{***}&                     \\
-                    &                     &     (-8.12)         &     (-8.12)         &                     \\
-\addlinespace
-group(property\_address\_city file\_year)=1&                     &                     &                     &           0         \\
-                    &                     &                     &                     &         (.)         \\
-\addlinespace
-group(property\_address\_city file\_year)=2&                     &                     &                     & -21747387.2\sym{**} \\
-                    &                     &                     &                     &     (-3.04)         \\
-\addlinespace
-group(property\_address\_city file\_year)=3&                     &                     &                     & -16553233.1         \\
-                    &                     &                     &                     &     (-1.57)         \\
-\addlinespace
-group(property\_address\_city file\_year)=7&                     &                     &                     & -31817166.7\sym{***}\\
-                    &                     &                     &                     &     (-4.84)         \\
-\addlinespace
-group(property\_address\_city file\_year)=8&                     &                     &                     & -31572134.4\sym{***}\\
-                    &                     &                     &                     &     (-4.79)         \\
-\addlinespace
-group(property\_address\_city file\_year)=9&                     &                     &                     & -28362311.8\sym{***}\\
-                    &                     &                     &                     &     (-4.12)         \\
-\addlinespace
-group(property\_address\_city file\_year)=11&                     &                     &                     & -29517698.0\sym{***}\\
-                    &                     &                     &                     &     (-4.40)         \\
-\addlinespace
-group(property\_address\_city file\_year)=12&                     &                     &                     & -21429968.1\sym{**} \\
-                    &                     &                     &                     &     (-3.13)         \\
-\addlinespace
-group(property\_address\_city file\_year)=13&                     &                     &                     &  -7726729.5         \\
-                    &                     &                     &                     &     (-0.93)         \\
-\addlinespace
-group(property\_address\_city file\_year)=14&                     &                     &                     & -16546877.7         \\
-                    &                     &                     &                     &     (-1.92)         \\
-\addlinespace
-group(property\_address\_city file\_year)=23&                     &                     &                     & -31739739.1\sym{***}\\
-                    &                     &                     &                     &     (-4.83)         \\
-\addlinespace
-group(property\_address\_city file\_year)=24&                     &                     &                     & -29812227.4\sym{***}\\
-                    &                     &                     &                     &     (-4.49)         \\
-\addlinespace
-group(property\_address\_city file\_year)=26&                     &                     &                     & -31616757.7\sym{***}\\
-                    &                     &                     &                     &     (-4.81)         \\
-\addlinespace
-group(property\_address\_city file\_year)=31&                     &                     &                     &  -7667441.0         \\
-                    &                     &                     &                     &     (-0.74)         \\
-\addlinespace
-group(property\_address\_city file\_year)=33&                     &                     &                     & -31058487.8\sym{***}\\
-                    &                     &                     &                     &     (-4.72)         \\
-\addlinespace
-group(property\_address\_city file\_year)=34&                     &                     &                     & -29958013.6\sym{***}\\
-                    &                     &                     &                     &     (-4.53)         \\
-\addlinespace
-group(property\_address\_city file\_year)=35&                     &                     &                     &   7817837.2         \\
-                    &                     &                     &                     &      (0.33)         \\
-\addlinespace
-group(property\_address\_city file\_year)=39&                     &                     &                     & -23427539.3\sym{***}\\
-                    &                     &                     &                     &     (-3.45)         \\
-\addlinespace
-group(property\_address\_city file\_year)=40&                     &                     &                     & -26490197.7\sym{***}\\
-                    &                     &                     &                     &     (-3.84)         \\
-\addlinespace
-group(property\_address\_city file\_year)=42&                     &                     &                     &  -1787415.9         \\
-                    &                     &                     &                     &     (-0.24)         \\
-\addlinespace
-group(property\_address\_city file\_year)=43&                     &                     &                     &  -7367293.9         \\
-                    &                     &                     &                     &     (-0.88)         \\
-\addlinespace
-group(property\_address\_city file\_year)=53&                     &                     &                     &  12651738.5         \\
-                    &                     &                     &                     &      (1.56)         \\
-\addlinespace
-group(property\_address\_city file\_year)=54&                     &                     &                     & -30931191.8\sym{***}\\
-                    &                     &                     &                     &     (-4.68)         \\
-\addlinespace
-group(property\_address\_city file\_year)=56&                     &                     &                     &   -941258.6         \\
-                    &                     &                     &                     &     (-0.12)         \\
-\addlinespace
-group(property\_address\_city file\_year)=58&                     &                     &                     & -27434049.1\sym{***}\\
-                    &                     &                     &                     &     (-4.15)         \\
-\addlinespace
-group(property\_address\_city file\_year)=59&                     &                     &                     & -28035133.5\sym{***}\\
-                    &                     &                     &                     &     (-4.23)         \\
-\addlinespace
-group(property\_address\_city file\_year)=60&                     &                     &                     & -26482084.7\sym{***}\\
-                    &                     &                     &                     &     (-3.56)         \\
-\addlinespace
-group(property\_address\_city file\_year)=66&                     &                     &                     &  16595560.5         \\
-                    &                     &                     &                     &      (1.21)         \\
-\addlinespace
-group(property\_address\_city file\_year)=67&                     &                     &                     &  -3516394.1         \\
-                    &                     &                     &                     &     (-0.44)         \\
-\addlinespace
-group(property\_address\_city file\_year)=68&                     &                     &                     & -15346166.3         \\
-                    &                     &                     &                     &     (-1.61)         \\
-\addlinespace
-group(property\_address\_city file\_year)=73&                     &                     &                     & -14757425.6\sym{*}  \\
-                    &                     &                     &                     &     (-2.24)         \\
-\addlinespace
-group(property\_address\_city file\_year)=74&                     &                     &                     & -25535691.0\sym{***}\\
-                    &                     &                     &                     &     (-3.40)         \\
-\addlinespace
-group(property\_address\_city file\_year)=75&                     &                     &                     &  -4233310.1         \\
-                    &                     &                     &                     &     (-0.46)         \\
-\addlinespace
-group(property\_address\_city file\_year)=83&                     &                     &                     & -29174821.6\sym{***}\\
-                    &                     &                     &                     &     (-4.40)         \\
-\addlinespace
-group(property\_address\_city file\_year)=84&                     &                     &                     & -31372814.9\sym{***}\\
-                    &                     &                     &                     &     (-4.76)         \\
-\addlinespace
-group(property\_address\_city file\_year)=88&                     &                     &                     &  19157275.7         \\
-                    &                     &                     &                     &      (1.72)         \\
-\addlinespace
-group(property\_address\_city file\_year)=92&                     &                     &                     & -15712195.5         \\
-                    &                     &                     &                     &     (-1.86)         \\
-\addlinespace
-group(property\_address\_city file\_year)=99&                     &                     &                     & -29653470.5\sym{***}\\
-                    &                     &                     &                     &     (-4.43)         \\
-\addlinespace
-group(property\_address\_city file\_year)=100&                     &                     &                     & -32025375.2\sym{***}\\
-                    &                     &                     &                     &     (-4.86)         \\
-\addlinespace
-group(property\_address\_city file\_year)=103&                     &                     &                     & -25516156.4\sym{***}\\
-                    &                     &                     &                     &     (-3.59)         \\
-\addlinespace
-group(property\_address\_city file\_year)=113&                     &                     &                     & -25490007.7\sym{***}\\
-                    &                     &                     &                     &     (-3.43)         \\
-\addlinespace
-group(property\_address\_city file\_year)=120&                     &                     &                     & -17660394.5\sym{*}  \\
-                    &                     &                     &                     &     (-1.98)         \\
-\addlinespace
-group(property\_address\_city file\_year)=121&                     &                     &                     & -31937592.6\sym{***}\\
-                    &                     &                     &                     &     (-4.85)         \\
-\addlinespace
-group(property\_address\_city file\_year)=122&                     &                     &                     & -30621970.7\sym{***}\\
-                    &                     &                     &                     &     (-4.62)         \\
-\addlinespace
-group(property\_address\_city file\_year)=123&                     &                     &                     & -28326993.2\sym{***}\\
-                    &                     &                     &                     &     (-4.29)         \\
-\addlinespace
-group(property\_address\_city file\_year)=125&                     &                     &                     & -29342045.6\sym{***}\\
-                    &                     &                     &                     &     (-4.42)         \\
-\addlinespace
-group(property\_address\_city file\_year)=126&                     &                     &                     & -28176986.1\sym{***}\\
-                    &                     &                     &                     &     (-4.09)         \\
-\addlinespace
-group(property\_address\_city file\_year)=127&                     &                     &                     & -31295574.7\sym{***}\\
-                    &                     &                     &                     &     (-4.76)         \\
-\addlinespace
-group(property\_address\_city file\_year)=128&                     &                     &                     & -31064464.4\sym{***}\\
-                    &                     &                     &                     &     (-4.72)         \\
-\addlinespace
-group(property\_address\_city file\_year)=132&                     &                     &                     &  10388032.0         \\
-                    &                     &                     &                     &      (1.57)         \\
-\addlinespace
-group(property\_address\_city file\_year)=134&                     &                     &                     &   9032122.0         \\
-                    &                     &                     &                     &      (1.36)         \\
-\addlinespace
-group(property\_address\_city file\_year)=135&                     &                     &                     & -12412590.3         \\
-                    &                     &                     &                     &     (-1.78)         \\
-\addlinespace
-group(property\_address\_city file\_year)=136&                     &                     &                     & -19582760.6\sym{*}  \\
-                    &                     &                     &                     &     (-2.57)         \\
-\addlinespace
-group(property\_address\_city file\_year)=137&                     &                     &                     &  -8576722.7         \\
-                    &                     &                     &                     &     (-0.98)         \\
-\addlinespace
-group(property\_address\_city file\_year)=138&                     &                     &                     & -28607583.4\sym{***}\\
-                    &                     &                     &                     &     (-4.29)         \\
-\addlinespace
-group(property\_address\_city file\_year)=142&                     &                     &                     & -25588880.8\sym{***}\\
-                    &                     &                     &                     &     (-3.77)         \\
-\addlinespace
-group(property\_address\_city file\_year)=143&                     &                     &                     & -23441624.9\sym{***}\\
-                    &                     &                     &                     &     (-3.39)         \\
-\addlinespace
-group(property\_address\_city file\_year)=144&                     &                     &                     & -21884245.6\sym{**} \\
-                    &                     &                     &                     &     (-2.77)         \\
-\addlinespace
-group(property\_address\_city file\_year)=147&                     &                     &                     & -29352983.9\sym{***}\\
-                    &                     &                     &                     &     (-4.39)         \\
-\addlinespace
-group(property\_address\_city file\_year)=153&                     &                     &                     & -31841831.8\sym{***}\\
-                    &                     &                     &                     &     (-4.84)         \\
-\addlinespace
-group(property\_address\_city file\_year)=156&                     &                     &                     & -28639093.1\sym{***}\\
-                    &                     &                     &                     &     (-4.34)         \\
-\addlinespace
-group(property\_address\_city file\_year)=164&                     &                     &                     & -30086286.3\sym{***}\\
-                    &                     &                     &                     &     (-4.55)         \\
-\addlinespace
-group(property\_address\_city file\_year)=167&                     &                     &                     & -31563212.8\sym{***}\\
-                    &                     &                     &                     &     (-4.80)         \\
-\addlinespace
-group(property\_address\_city file\_year)=168&                     &                     &                     & -26148336.2\sym{***}\\
-                    &                     &                     &                     &     (-3.44)         \\
-\addlinespace
-group(property\_address\_city file\_year)=169&                     &                     &                     & -21888879.5\sym{*}  \\
-                    &                     &                     &                     &     (-2.50)         \\
-\addlinespace
-group(property\_address\_city file\_year)=171&                     &                     &                     & -29740224.9\sym{***}\\
-                    &                     &                     &                     &     (-4.49)         \\
-\addlinespace
-group(property\_address\_city file\_year)=172&                     &                     &                     & -31399983.4\sym{***}\\
-                    &                     &                     &                     &     (-4.78)         \\
-\addlinespace
-group(property\_address\_city file\_year)=173&                     &                     &                     & -30775755.6\sym{***}\\
-                    &                     &                     &                     &     (-4.61)         \\
-\addlinespace
-group(property\_address\_city file\_year)=174&                     &                     &                     & -29867637.5\sym{***}\\
-                    &                     &                     &                     &     (-4.51)         \\
-\addlinespace
-group(property\_address\_city file\_year)=179&                     &                     &                     & -29450518.0\sym{***}\\
-                    &                     &                     &                     &     (-4.43)         \\
-\addlinespace
-group(property\_address\_city file\_year)=180&                     &                     &                     & -24582985.6\sym{***}\\
-                    &                     &                     &                     &     (-3.56)         \\
-\addlinespace
-group(property\_address\_city file\_year)=182&                     &                     &                     & -29062568.7\sym{***}\\
-                    &                     &                     &                     &     (-4.41)         \\
-\addlinespace
-group(property\_address\_city file\_year)=183&                     &                     &                     & -28961589.8\sym{***}\\
-                    &                     &                     &                     &     (-4.39)         \\
-\addlinespace
-group(property\_address\_city file\_year)=187&                     &                     &                     & -27536485.7\sym{***}\\
-                    &                     &                     &                     &     (-4.16)         \\
-\addlinespace
-group(property\_address\_city file\_year)=194&                     &                     &                     & -24983783.9\sym{***}\\
-                    &                     &                     &                     &     (-3.79)         \\
-\addlinespace
-group(property\_address\_city file\_year)=195&                     &                     &                     & -27444446.8\sym{***}\\
-                    &                     &                     &                     &     (-4.16)         \\
-\addlinespace
-group(property\_address\_city file\_year)=196&                     &                     &                     & -30678002.5\sym{***}\\
-                    &                     &                     &                     &     (-4.64)         \\
-\addlinespace
-group(property\_address\_city file\_year)=197&                     &                     &                     & -31478427.5\sym{***}\\
-                    &                     &                     &                     &     (-4.77)         \\
-\addlinespace
-group(property\_address\_city file\_year)=198&                     &                     &                     & -32035018.0\sym{***}\\
-                    &                     &                     &                     &     (-4.86)         \\
-\addlinespace
-group(property\_address\_city file\_year)=199&                     &                     &                     & -28721146.1\sym{***}\\
-                    &                     &                     &                     &     (-4.35)         \\
-\addlinespace
-group(property\_address\_city file\_year)=200&                     &                     &                     & -28530907.5\sym{***}\\
-                    &                     &                     &                     &     (-4.29)         \\
-\addlinespace
-group(property\_address\_city file\_year)=201&                     &                     &                     & -13358738.0         \\
-                    &                     &                     &                     &     (-1.71)         \\
-\addlinespace
-group(property\_address\_city file\_year)=203&                     &                     &                     & -11773931.9         \\
-                    &                     &                     &                     &     (-1.55)         \\
-\addlinespace
-group(property\_address\_city file\_year)=204&                     &                     &                     &  -7249428.5         \\
-                    &                     &                     &                     &     (-0.97)         \\
-\addlinespace
-group(property\_address\_city file\_year)=206&                     &                     &                     & -24920666.9\sym{***}\\
-                    &                     &                     &                     &     (-3.66)         \\
-\addlinespace
-group(property\_address\_city file\_year)=207&                     &                     &                     & -21421751.4\sym{**} \\
-                    &                     &                     &                     &     (-2.98)         \\
-\addlinespace
-group(property\_address\_city file\_year)=208&                     &                     &                     & -30633853.1\sym{***}\\
-                    &                     &                     &                     &     (-4.57)         \\
-\addlinespace
-group(property\_address\_city file\_year)=209&                     &                     &                     & -31329599.4\sym{***}\\
-                    &                     &                     &                     &     (-4.72)         \\
-\addlinespace
-group(property\_address\_city file\_year)=212&                     &                     &                     & -30116514.1\sym{***}\\
-                    &                     &                     &                     &     (-4.53)         \\
-\addlinespace
-group(property\_address\_city file\_year)=213&                     &                     &                     & -29659399.3\sym{***}\\
-                    &                     &                     &                     &     (-4.48)         \\
-\addlinespace
-group(property\_address\_city file\_year)=214&                     &                     &                     & -31497392.3\sym{***}\\
-                    &                     &                     &                     &     (-4.79)         \\
-\addlinespace
-group(property\_address\_city file\_year)=216&                     &                     &                     & -29958296.2\sym{***}\\
-                    &                     &                     &                     &     (-4.54)         \\
-\addlinespace
-group(property\_address\_city file\_year)=224&                     &                     &                     & -25191502.6\sym{***}\\
-                    &                     &                     &                     &     (-3.69)         \\
-\addlinespace
-group(property\_address\_city file\_year)=225&                     &                     &                     & -25256604.5\sym{***}\\
-                    &                     &                     &                     &     (-3.71)         \\
-\addlinespace
-group(property\_address\_city file\_year)=226&                     &                     &                     & -29751606.3\sym{***}\\
-                    &                     &                     &                     &     (-4.40)         \\
-\addlinespace
-group(property\_address\_city file\_year)=227&                     &                     &                     & -16565988.0\sym{*}  \\
-                    &                     &                     &                     &     (-2.19)         \\
-\addlinespace
-group(property\_address\_city file\_year)=229&                     &                     &                     & -22558870.7\sym{**} \\
-                    &                     &                     &                     &     (-2.95)         \\
-\addlinespace
-group(property\_address\_city file\_year)=230&                     &                     &                     & -17095348.7\sym{*}  \\
-                    &                     &                     &                     &     (-2.47)         \\
-\addlinespace
-group(property\_address\_city file\_year)=232&                     &                     &                     & -28960955.5\sym{***}\\
-                    &                     &                     &                     &     (-4.23)         \\
-\addlinespace
-group(property\_address\_city file\_year)=242&                     &                     &                     &  12661382.0         \\
-                    &                     &                     &                     &      (0.72)         \\
-\addlinespace
-group(property\_address\_city file\_year)=243&                     &                     &                     &  39024648.4\sym{***}\\
-                    &                     &                     &                     &      (4.88)         \\
-\addlinespace
-group(property\_address\_city file\_year)=246&                     &                     &                     & -30756034.7\sym{***}\\
-                    &                     &                     &                     &     (-4.67)         \\
-\addlinespace
-group(property\_address\_city file\_year)=248&                     &                     &                     & -26979715.6\sym{***}\\
-                    &                     &                     &                     &     (-4.08)         \\
-\addlinespace
-group(property\_address\_city file\_year)=249&                     &                     &                     & -29764479.4\sym{***}\\
-                    &                     &                     &                     &     (-4.47)         \\
-\addlinespace
-group(property\_address\_city file\_year)=251&                     &                     &                     & -30369071.2\sym{***}\\
-                    &                     &                     &                     &     (-4.61)         \\
-\addlinespace
-group(property\_address\_city file\_year)=252&                     &                     &                     & -31063119.1\sym{***}\\
-                    &                     &                     &                     &     (-4.70)         \\
-\addlinespace
-group(property\_address\_city file\_year)=253&                     &                     &                     &  -9953427.2         \\
-                    &                     &                     &                     &     (-1.27)         \\
-\addlinespace
-group(property\_address\_city file\_year)=254&                     &                     &                     & -19744724.7\sym{**} \\
-                    &                     &                     &                     &     (-2.61)         \\
-\addlinespace
-group(property\_address\_city file\_year)=255&                     &                     &                     & -30457504.7\sym{***}\\
-                    &                     &                     &                     &     (-4.60)         \\
-\addlinespace
-group(property\_address\_city file\_year)=256&                     &                     &                     & -30847319.4\sym{***}\\
-                    &                     &                     &                     &     (-4.65)         \\
-\addlinespace
-group(property\_address\_city file\_year)=257&                     &                     &                     & -18894051.8\sym{*}  \\
-                    &                     &                     &                     &     (-1.97)         \\
-\addlinespace
-group(property\_address\_city file\_year)=258&                     &                     &                     & -18653038.0\sym{*}  \\
-                    &                     &                     &                     &     (-1.96)         \\
-\addlinespace
-group(property\_address\_city file\_year)=261&                     &                     &                     & -23510998.0\sym{**} \\
-                    &                     &                     &                     &     (-3.22)         \\
-\addlinespace
-group(property\_address\_city file\_year)=271&                     &                     &                     & -31532639.4\sym{***}\\
-                    &                     &                     &                     &     (-4.76)         \\
-\addlinespace
-group(property\_address\_city file\_year)=273&                     &                     &                     & -28289201.2\sym{***}\\
-                    &                     &                     &                     &     (-4.14)         \\
-\addlinespace
-group(property\_address\_city file\_year)=274&                     &                     &                     &  30054182.0\sym{***}\\
-                    &                     &                     &                     &      (4.56)         \\
-\addlinespace
-group(property\_address\_city file\_year)=277&                     &                     &                     & -25086958.0\sym{**} \\
-                    &                     &                     &                     &     (-2.97)         \\
-\addlinespace
-group(property\_address\_city file\_year)=278&                     &                     &                     & -11343893.9         \\
-                    &                     &                     &                     &     (-1.31)         \\
-\addlinespace
-group(property\_address\_city file\_year)=279&                     &                     &                     & 118496709.8\sym{***}\\
-                    &                     &                     &                     &      (7.37)         \\
-\addlinespace
-group(property\_address\_city file\_year)=280&                     &                     &                     &  43750508.2\sym{***}\\
-                    &                     &                     &                     &      (3.55)         \\
-\addlinespace
-group(property\_address\_city file\_year)=288&                     &                     &                     & -19468789.1\sym{*}  \\
-                    &                     &                     &                     &     (-1.99)         \\
-\addlinespace
-group(property\_address\_city file\_year)=290&                     &                     &                     &  -4604103.0         \\
-                    &                     &                     &                     &     (-0.62)         \\
-\addlinespace
-group(property\_address\_city file\_year)=291&                     &                     &                     &   6168772.8         \\
-                    &                     &                     &                     &      (0.74)         \\
-\addlinespace
-group(property\_address\_city file\_year)=296&                     &                     &                     & -31250792.0\sym{***}\\
-                    &                     &                     &                     &     (-4.75)         \\
-\addlinespace
-group(property\_address\_city file\_year)=297&                     &                     &                     & -30530442.5\sym{***}\\
-                    &                     &                     &                     &     (-4.64)         \\
-\addlinespace
-group(property\_address\_city file\_year)=299&                     &                     &                     & -29688885.1\sym{***}\\
-                    &                     &                     &                     &     (-4.39)         \\
-\addlinespace
-group(property\_address\_city file\_year)=302&                     &                     &                     & -10610238.6         \\
-                    &                     &                     &                     &     (-1.10)         \\
-\addlinespace
-group(property\_address\_city file\_year)=303&                     &                     &                     & -13613772.3         \\
-                    &                     &                     &                     &     (-1.89)         \\
-\addlinespace
-group(property\_address\_city file\_year)=304&                     &                     &                     & -10758486.3         \\
-                    &                     &                     &                     &     (-1.10)         \\
-\addlinespace
-group(property\_address\_city file\_year)=308&                     &                     &                     & -10311965.6         \\
-                    &                     &                     &                     &     (-0.78)         \\
-\addlinespace
-group(property\_address\_city file\_year)=310&                     &                     &                     & -30407214.8\sym{***}\\
-                    &                     &                     &                     &     (-4.60)         \\
-\addlinespace
-group(property\_address\_city file\_year)=318&                     &                     &                     & -27004230.1\sym{***}\\
-                    &                     &                     &                     &     (-4.06)         \\
-\addlinespace
-group(property\_address\_city file\_year)=320&                     &                     &                     & -30867957.7\sym{***}\\
-                    &                     &                     &                     &     (-4.69)         \\
-\addlinespace
-group(property\_address\_city file\_year)=321&                     &                     &                     & -17030155.6         \\
-                    &                     &                     &                     &     (-1.94)         \\
-\addlinespace
-group(property\_address\_city file\_year)=322&                     &                     &                     &  -4839964.1         \\
-                    &                     &                     &                     &     (-0.37)         \\
-\addlinespace
-group(property\_address\_city file\_year)=323&                     &                     &                     &   3439082.0         \\
-                    &                     &                     &                     &      (0.25)         \\
-\addlinespace
-group(property\_address\_city file\_year)=325&                     &                     &                     &   2301259.0         \\
-                    &                     &                     &                     &      (0.20)         \\
-\addlinespace
-group(property\_address\_city file\_year)=326&                     &                     &                     &   9455152.7         \\
-                    &                     &                     &                     &      (1.15)         \\
-\addlinespace
-group(property\_address\_city file\_year)=330&                     &                     &                     & -31814129.5\sym{***}\\
-                    &                     &                     &                     &     (-4.84)         \\
-\addlinespace
-group(property\_address\_city file\_year)=331&                     &                     &                     & -32090701.4\sym{***}\\
-                    &                     &                     &                     &     (-4.87)         \\
-\addlinespace
-group(property\_address\_city file\_year)=332&                     &                     &                     & -22228295.8\sym{*}  \\
-                    &                     &                     &                     &     (-2.47)         \\
-\addlinespace
-group(property\_address\_city file\_year)=334&                     &                     &                     & -29882451.6\sym{***}\\
-                    &                     &                     &                     &     (-4.52)         \\
-\addlinespace
-group(property\_address\_city file\_year)=344&                     &                     &                     & -30622664.1\sym{***}\\
-                    &                     &                     &                     &     (-4.64)         \\
-\addlinespace
-group(property\_address\_city file\_year)=345&                     &                     &                     & -30534219.0\sym{***}\\
-                    &                     &                     &                     &     (-4.62)         \\
-\addlinespace
-group(property\_address\_city file\_year)=350&                     &                     &                     & -31222278.5\sym{***}\\
-                    &                     &                     &                     &     (-4.74)         \\
-\addlinespace
-group(property\_address\_city file\_year)=351&                     &                     &                     & -31474184.8\sym{***}\\
-                    &                     &                     &                     &     (-4.78)         \\
-\addlinespace
-group(property\_address\_city file\_year)=352&                     &                     &                     & -30758113.6\sym{***}\\
-                    &                     &                     &                     &     (-4.63)         \\
-\addlinespace
-group(property\_address\_city file\_year)=353&                     &                     &                     & -31385187.2\sym{***}\\
-                    &                     &                     &                     &     (-4.77)         \\
-\addlinespace
-group(property\_address\_city file\_year)=355&                     &                     &                     & -28884085.3\sym{***}\\
-                    &                     &                     &                     &     (-4.39)         \\
-\addlinespace
-group(property\_address\_city file\_year)=356&                     &                     &                     & -25817895.7\sym{***}\\
-                    &                     &                     &                     &     (-3.89)         \\
-\addlinespace
-group(property\_address\_city file\_year)=359&                     &                     &                     & -24039316.5\sym{***}\\
-                    &                     &                     &                     &     (-3.40)         \\
-\addlinespace
-group(property\_address\_city file\_year)=360&                     &                     &                     & -19620579.8\sym{**} \\
-                    &                     &                     &                     &     (-2.59)         \\
-\addlinespace
-group(property\_address\_city file\_year)=366&                     &                     &                     & -14873354.2         \\
-                    &                     &                     &                     &     (-1.67)         \\
-\addlinespace
-group(property\_address\_city file\_year)=369&                     &                     &                     & -29903518.7\sym{***}\\
-                    &                     &                     &                     &     (-4.53)         \\
-\addlinespace
-group(property\_address\_city file\_year)=370&                     &                     &                     & -30828394.3\sym{***}\\
-                    &                     &                     &                     &     (-4.68)         \\
-\addlinespace
-group(property\_address\_city file\_year)=372&                     &                     &                     &  -6925805.9         \\
-                    &                     &                     &                     &     (-0.86)         \\
-\addlinespace
-group(property\_address\_city file\_year)=373&                     &                     &                     &  -1071951.6         \\
-                    &                     &                     &                     &     (-0.10)         \\
-\addlinespace
-group(property\_address\_city file\_year)=375&                     &                     &                     & -31419361.8\sym{***}\\
-                    &                     &                     &                     &     (-4.77)         \\
-\addlinespace
-group(property\_address\_city file\_year)=377&                     &                     &                     & -29346146.6\sym{***}\\
-                    &                     &                     &                     &     (-4.44)         \\
-\addlinespace
-group(property\_address\_city file\_year)=383&                     &                     &                     & -20344933.3\sym{**} \\
-                    &                     &                     &                     &     (-2.73)         \\
-\addlinespace
-group(property\_address\_city file\_year)=384&                     &                     &                     & -26847799.3\sym{***}\\
-                    &                     &                     &                     &     (-3.96)         \\
-\addlinespace
-group(property\_address\_city file\_year)=385&                     &                     &                     & -20557608.9\sym{*}  \\
-                    &                     &                     &                     &     (-2.35)         \\
-\addlinespace
-group(property\_address\_city file\_year)=386&                     &                     &                     & -12889024.4         \\
-                    &                     &                     &                     &     (-1.72)         \\
-\addlinespace
-group(property\_address\_city file\_year)=387&                     &                     &                     & -19353269.5\sym{*}  \\
-                    &                     &                     &                     &     (-2.51)         \\
-\addlinespace
-group(property\_address\_city file\_year)=388&                     &                     &                     & -31519945.1\sym{***}\\
-                    &                     &                     &                     &     (-4.79)         \\
-\addlinespace
-group(property\_address\_city file\_year)=389&                     &                     &                     & -30694986.0\sym{***}\\
-                    &                     &                     &                     &     (-4.62)         \\
-\addlinespace
-group(property\_address\_city file\_year)=393&                     &                     &                     &   4470985.9         \\
-                    &                     &                     &                     &      (0.31)         \\
-\addlinespace
-group(property\_address\_city file\_year)=394&                     &                     &                     & -30901277.8\sym{***}\\
-                    &                     &                     &                     &     (-4.68)         \\
-\addlinespace
-group(property\_address\_city file\_year)=401&                     &                     &                     & -30955391.3\sym{***}\\
-                    &                     &                     &                     &     (-4.71)         \\
-\addlinespace
-group(property\_address\_city file\_year)=406&                     &                     &                     &  -2979054.9         \\
-                    &                     &                     &                     &     (-0.40)         \\
-\addlinespace
-group(property\_address\_city file\_year)=407&                     &                     &                     & -13672579.5         \\
-                    &                     &                     &                     &     (-1.83)         \\
-\addlinespace
-group(property\_address\_city file\_year)=413&                     &                     &                     &  -7074546.2         \\
-                    &                     &                     &                     &     (-0.93)         \\
-\addlinespace
-group(property\_address\_city file\_year)=414&                     &                     &                     & -14379792.2\sym{*}  \\
-                    &                     &                     &                     &     (-1.98)         \\
-\addlinespace
-group(property\_address\_city file\_year)=415&                     &                     &                     & -31422818.0\sym{***}\\
-                    &                     &                     &                     &     (-4.76)         \\
-\addlinespace
-group(property\_address\_city file\_year)=417&                     &                     &                     & -30097355.9\sym{***}\\
-                    &                     &                     &                     &     (-4.55)         \\
-\addlinespace
-group(property\_address\_city file\_year)=423&                     &                     &                     & -31964046.6\sym{***}\\
-                    &                     &                     &                     &     (-4.85)         \\
-\addlinespace
-group(property\_address\_city file\_year)=426&                     &                     &                     &  32737759.6\sym{**} \\
-                    &                     &                     &                     &      (2.60)         \\
-\addlinespace
-group(property\_address\_city file\_year)=427&                     &                     &                     & -29581259.1\sym{***}\\
-                    &                     &                     &                     &     (-4.49)         \\
-\addlinespace
-Constant            &   6023455.1\sym{***}&  20725757.2\sym{***}&  20725757.2\sym{***}&  31134586.9\sym{***}\\
-                    &     (11.62)         &      (8.99)         &      (8.99)         &      (4.57)         \\
+judgment\_for\_plaintiff& 2434984.290& 1161293.951& 1161293.951& 1055231.099\\
+                    & (588147.83)& (453836.79)& (453836.79)&(2319051.94)\\
 \midrule
-Observations        &        5567         &        5567         &        5567         &        5567         \\
+Observations        &        5567&        5567&        5567&        5567\\
 \bottomrule
-\multicolumn{5}{l}{\footnotesize \textit{t} statistics in parentheses}\\
-\multicolumn{5}{l}{\footnotesize \sym{*} \(p<0.05\), \sym{**} \(p<0.01\), \sym{***} \(p<0.001\)}\\
 \end{tabular}

### 2022-12-07 output/01_exploratory/tables/total_val_results_table.tex
Created estimation tables

@@
                     &\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}\\
+                    &        b/se&        b/se&        b/se&        b/se\\
 \midrule
-judgment\_for\_plaintiff&   3259178.0\sym{***}&   1507062.7\sym{**} &   1507062.7\sym{**} &    751962.4         \\
-                    &      (4.27)         &      (2.61)         &      (2.61)         &      (0.26)         \\
-\addlinespace
-file\_year=2019      &                     &           0         &           0         &                     \\
-                    &                     &         (.)         &         (.)         &                     \\
-\addlinespace
-file\_year=2020      &                     &   -129326.5         &   -129326.5         &                     \\
-                    &                     &     (-0.22)         &     (-0.22)         &                     \\
-\addlinespace
-file\_year=2021      &                     &   2343272.8         &   2343272.8         &                     \\
-                    &                     &      (1.01)         &      (1.01)         &                     \\
-\addlinespace
-Abington            &                     &           0         &           0         &                     \\
-                    &                     &         (.)         &         (.)         &                     \\
-\addlinespace
-Acton               &                     &  -8845941.7         &  -8845941.7         &                     \\
-                    &                     &     (-1.10)         &     (-1.10)         &                     \\
-\addlinespace
-Adams               &                     & -26295427.0\sym{***}& -26295427.0\sym{***}&                     \\
-                    &                     &     (-5.72)         &     (-5.72)         &                     \\
-\addlinespace
-Agawam              &                     & -22781989.3\sym{***}& -22781989.3\sym{***}&                     \\
-                    &                     &     (-3.77)         &     (-3.77)         &                     \\
-\addlinespace
-Amesbury            &                     & -22667125.4\sym{**} & -22667125.4\sym{**} &                     \\
-                    &                     &     (-2.82)         &     (-2.82)         &                     \\
-\addlinespace
-Amherst             &                     & -13994734.3\sym{*}  & -13994734.3\sym{*}  &                     \\
-                    &                     &     (-2.40)         &     (-2.40)         &                     \\
-\addlinespace
-Andover             &                     &   -749699.0         &   -749699.0         &                     \\
-                    &                     &     (-0.17)         &     (-0.17)         &                     \\
-\addlinespace
-Athol               &                     & -26350442.5\sym{***}& -26350442.5\sym{***}&                     \\
-                    &                     &     (-3.99)         &     (-3.99)         &                     \\
-\addlinespace
-Attleboro           &                     & -24327184.2\sym{***}& -24327184.2\sym{***}&                     \\
-                    &                     &     (-5.29)         &     (-5.29)         &                     \\
-\addlinespace
-Auburn              &                     & -26064121.1\sym{***}& -26064121.1\sym{***}&                     \\
-                    &                     &     (-3.50)         &     (-3.50)         &                     \\
-\addlinespace
-Bedford             &                     &   5756678.9         &   5756678.9         &                     \\
-                    &                     &      (0.77)         &      (0.77)         &                     \\
-\addlinespace
-Belchertown         &                     & -25142479.5\sym{***}& -25142479.5\sym{***}&                     \\
-                    &                     &     (-5.23)         &     (-5.23)         &                     \\
-\addlinespace
-Bellingham          &                     &  18531792.0\sym{*}  &  18531792.0\sym{*}  &                     \\
-                    &                     &      (2.49)         &      (2.49)         &                     \\
-\addlinespace
-Beverly             &                     & -15591295.2\sym{***}& -15591295.2\sym{***}&                     \\
-                    &                     &     (-4.23)         &     (-4.23)         &                     \\
-\addlinespace
-Billerica           &                     &   9390507.4\sym{*}  &   9390507.4\sym{*}  &                     \\
-                    &                     &      (2.07)         &      (2.07)         &                     \\
-\addlinespace
-Braintree           &                     &  35327975.2\sym{***}&  35327975.2\sym{***}&                     \\
-                    &                     &      (7.88)         &      (7.88)         &                     \\
-\addlinespace
-Brewster            &                     & -25347499.3\sym{**} & -25347499.3\sym{**} &                     \\
-                    &                     &     (-3.15)         &     (-3.15)         &                     \\
-\addlinespace
-Bridgewater         &                     &  11554226.6\sym{**} &  11554226.6\sym{**} &                     \\
-                    &                     &      (2.85)         &      (2.85)         &                     \\
-\addlinespace
-Brockton            &                     & -21848926.9\sym{***}& -21848926.9\sym{***}&                     \\
-                    &                     &     (-7.20)         &     (-7.20)         &                     \\
-\addlinespace
-Brookline           &                     & -14165718.5         & -14165718.5         &                     \\
-                    &                     &     (-1.90)         &     (-1.90)         &                     \\
-\addlinespace
-Cambridge           &                     &  42468310.1\sym{***}&  42468310.1\sym{***}&                     \\
-                    &                     &      (9.10)         &      (9.10)         &                     \\
-\addlinespace
-Canton              &                     &   5921639.1         &   5921639.1         &                     \\
-                    &                     &      (1.34)         &      (1.34)         &                     \\
-\addlinespace
-Chelmsford          &                     &  -3878300.3         &  -3878300.3         &                     \\
-                    &                     &     (-0.48)         &     (-0.48)         &                     \\
-\addlinespace
-Chelsea             &                     &  -6087119.2         &  -6087119.2         &                     \\
-                    &                     &     (-1.11)         &     (-1.11)         &                     \\
-\addlinespace
-Chicopee            &                     & -23100145.0\sym{***}& -23100145.0\sym{***}&                     \\
-                    &                     &     (-6.57)         &     (-6.57)         &                     \\
-\addlinespace
-Clinton             &                     & -25980685.6\sym{***}& -25980685.6\sym{***}&                     \\
-                    &                     &     (-4.30)         &     (-4.30)         &                     \\
-\addlinespace
-Concord             &                     &  36262535.7\sym{***}&  36262535.7\sym{***}&                     \\
-                    &                     &      (4.88)         &      (4.88)         &                     \\
-\addlinespace
-Danvers             &                     &   -350734.0         &   -350734.0         &                     \\
-                    &                     &     (-0.06)         &     (-0.06)         &                     \\
-\addlinespace
-Dracut              &                     & -23566660.9\sym{***}& -23566660.9\sym{***}&                     \\
-                    &                     &     (-4.30)         &     (-4.30)         &                     \\
-\addlinespace
-Dudley              &                     & -26862280.4\sym{***}& -26862280.4\sym{***}&                     \\
-                    &                     &     (-3.85)         &     (-3.85)         &                     \\
-\addlinespace
-Duxbury             &                     & -16553871.4\sym{*}  & -16553871.4\sym{*}  &                     \\
-                    &                     &     (-2.37)         &     (-2.37)         &                     \\
-\addlinespace
-East Wareham        &                     & -18675454.5\sym{*}  & -18675454.5\sym{*}  &                     \\
-                    &                     &     (-2.51)         &     (-2.51)         &                     \\
-\addlinespace
-Everett             &                     &  -8839883.1         &  -8839883.1         &                     \\
-                    &                     &     (-1.89)         &     (-1.89)         &                     \\
-\addlinespace
-Fairhaven           &                     & -25898741.3\sym{***}& -25898741.3\sym{***}&                     \\
-                    &                     &     (-5.48)         &     (-5.48)         &                     \\
-\addlinespace
-Fall River          &                     & -21875817.7\sym{***}& -21875817.7\sym{***}&                     \\
-                    &                     &     (-6.91)         &     (-6.91)         &                     \\
-\addlinespace
-Feeding Hills       &                     & -22823447.4\sym{***}& -22823447.4\sym{***}&                     \\
-                    &                     &     (-5.03)         &     (-5.03)         &                     \\
-\addlinespace
-Fitchburg           &                     & -25581554.5\sym{***}& -25581554.5\sym{***}&                     \\
-                    &                     &     (-7.97)         &     (-7.97)         &                     \\
-\addlinespace
-Foxboro             &                     &  22618498.2\sym{***}&  22618498.2\sym{***}&                     \\
-                    &                     &      (3.74)         &      (3.74)         &                     \\
-\addlinespace
-Foxborough          &                     &  21596274.6\sym{**} &  21596274.6\sym{**} &                     \\
-                    &                     &      (2.68)         &      (2.68)         &                     \\
-\addlinespace
-Framingham          &                     &  -4392422.6         &  -4392422.6         &                     \\
-                    &                     &     (-1.26)         &     (-1.26)         &                     \\
-\addlinespace
-Franklin            &                     &  -3437183.4         &  -3437183.4         &                     \\
-                    &                     &     (-0.72)         &     (-0.72)         &                     \\
-\addlinespace
-Gardner             &                     & -22989976.9\sym{***}& -22989976.9\sym{***}&                     \\
-                    &                     &     (-5.12)         &     (-5.12)         &                     \\
-\addlinespace
-Gloucester          &                     & -18804855.2\sym{***}& -18804855.2\sym{***}&                     \\
-                    &                     &     (-4.80)         &     (-4.80)         &                     \\
-\addlinespace
-Grafton             &                     & -16016646.8\sym{*}  & -16016646.8\sym{*}  &                     \\
-                    &                     &     (-1.99)         &     (-1.99)         &                     \\
-\addlinespace
-Greenfield          &                     & -23459956.9\sym{***}& -23459956.9\sym{***}&                     \\
-                    &                     &     (-4.69)         &     (-4.69)         &                     \\
-\addlinespace
-Hanson              &                     & -26499939.3\sym{***}& -26499939.3\sym{***}&                     \\
-                    &                     &     (-3.29)         &     (-3.29)         &                     \\
-\addlinespace
-Haverhill           &                     & -20800293.3\sym{***}& -20800293.3\sym{***}&                     \\
-                    &                     &     (-5.77)         &     (-5.77)         &                     \\
-\addlinespace
-Holyoke             &                     & -24189959.6\sym{***}& -24189959.6\sym{***}&                     \\
-                    &                     &     (-6.70)         &     (-6.70)         &                     \\
-\addlinespace
-Hudson              &                     & -26242808.0\sym{***}& -26242808.0\sym{***}&                     \\
-                    &                     &     (-3.53)         &     (-3.53)         &                     \\
-\addlinespace
-Hull                &                     & -17550050.6\sym{***}& -17550050.6\sym{***}&                     \\
-                    &                     &     (-3.52)         &     (-3.52)         &                     \\
-\addlinespace
-Hyannis             &                     & -23763038.9\sym{***}& -23763038.9\sym{***}&                     \\
-                    &                     &     (-4.08)         &     (-4.08)         &                     \\
-\addlinespace
-Indian Orchard      &                     & -25842404.0\sym{***}& -25842404.0\sym{***}&                     \\
-                    &                     &     (-6.83)         &     (-6.83)         &                     \\
-\addlinespace
-Ipswich             &                     & -23775846.2\sym{***}& -23775846.2\sym{***}&                     \\
-                    &                     &     (-3.77)         &     (-3.77)         &                     \\
-\addlinespace
-Lakeville           &                     & -21406455.4\sym{***}& -21406455.4\sym{***}&                     \\
-                    &                     &     (-3.80)         &     (-3.80)         &                     \\
-\addlinespace
-Lawrence            &                     & -23418520.4\sym{***}& -23418520.4\sym{***}&                     \\
-                    &                     &     (-7.75)         &     (-7.75)         &                     \\
-\addlinespace
-Leominster          &                     & -21878759.1\sym{***}& -21878759.1\sym{***}&                     \\
-                    &                     &     (-5.85)         &     (-5.85)         &                     \\
-\addlinespace
-Lowell              &                     & -19476530.9\sym{***}& -19476530.9\sym{***}&                     \\
-                    &                     &     (-6.51)         &     (-6.51)         &                     \\
-\addlinespace
-Ludlow              &                     & -25548082.3\sym{***}& -25548082.3\sym{***}&                     \\
-                    &                     &     (-5.02)         &     (-5.02)         &                     \\
-\addlinespace
-Lunenburg           &                     & -26707931.8\sym{***}& -26707931.8\sym{***}&                     \\
-                    &                     &     (-3.32)         &     (-3.32)         &                     \\
-\addlinespace
-Lynn                &                     & -21462921.1\sym{***}& -21462921.1\sym{***}&                     \\
-                    &                     &     (-6.33)         &     (-6.33)         &                     \\
-\addlinespace
-Lynnfield           &                     &    429208.2         &    429208.2         &                     \\
-                    &                     &      (0.05)         &      (0.05)         &                     \\
-\addlinespace
-Malden              &                     &   6937988.9         &   6937988.9         &                     \\
-                    &                     &      (1.94)         &      (1.94)         &                     \\
-\addlinespace
-Mansfield           &                     & -15826011.6\sym{**} & -15826011.6\sym{**} &                     \\
-                    &                     &     (-3.17)         &     (-3.17)         &                     \\
-\addlinespace
-Marblehead          &                     & -24872624.7\sym{***}& -24872624.7\sym{***}&                     \\
-                    &                     &     (-4.12)         &     (-4.12)         &                     \\
-\addlinespace
-Marshfield          &                     & -25486617.7\sym{***}& -25486617.7\sym{***}&                     \\
-                    &                     &     (-5.59)         &     (-5.59)         &                     \\
-\addlinespace
-Mashpee             &                     & -24274364.9\sym{**} & -24274364.9\sym{**} &                     \\
-                    &                     &     (-3.26)         &     (-3.26)         &                     \\
-\addlinespace
-Methuen             &                     & -17599579.2\sym{***}& -17599579.2\sym{***}&                     \\
-                    &                     &     (-5.10)         &     (-5.10)         &                     \\
-\addlinespace
-Middleboro          &                     & -15039148.7\sym{***}& -15039148.7\sym{***}&                     \\
-                    &                     &     (-3.79)         &     (-3.79)         &                     \\
-\addlinespace
-Milford             &                     &  -7530303.0         &  -7530303.0         &                     \\
-                    &                     &     (-1.54)         &     (-1.54)         &                     \\
-\addlinespace
-Millbury            &                     & -23455764.3\sym{***}& -23455764.3\sym{***}&                     \\
-                    &                     &     (-3.55)         &     (-3.55)         &                     \\
-\addlinespace
-Needham             &                     &  45061315.4\sym{***}&  45061315.4\sym{***}&                     \\
-                    &                     &      (8.23)         &      (8.23)         &                     \\
-\addlinespace
-New Bedford         &                     & -25410999.4\sym{***}& -25410999.4\sym{***}&                     \\
-                    &                     &     (-8.35)         &     (-8.35)         &                     \\
-\addlinespace
-Newburyport         &                     & -21570253.8\sym{***}& -21570253.8\sym{***}&                     \\
-                    &                     &     (-4.14)         &     (-4.14)         &                     \\
-\addlinespace
-North Adams         &                     & -24978653.4\sym{***}& -24978653.4\sym{***}&                     \\
-                    &                     &     (-5.11)         &     (-5.11)         &                     \\
-\addlinespace
-North Andover       &                     &  -4813790.9         &  -4813790.9         &                     \\
-                    &                     &     (-1.16)         &     (-1.16)         &                     \\
-\addlinespace
-North Attleboro     &                     & -24642950.8\sym{***}& -24642950.8\sym{***}&                     \\
-                    &                     &     (-5.21)         &     (-5.21)         &                     \\
-\addlinespace
-North Billerica     &                     &  -9778512.3         &  -9778512.3         &                     \\
-                    &                     &     (-1.62)         &     (-1.62)         &                     \\
-\addlinespace
-North Dartmouth     &                     & -15474811.8         & -15474811.8         &                     \\
-                    &                     &     (-1.92)         &     (-1.92)         &                     \\
-\addlinespace
-Northampton         &                     & -25051692.1\sym{***}& -25051692.1\sym{***}&                     \\
-                    &                     &     (-4.31)         &     (-4.31)         &                     \\
-\addlinespace
-Northborough        &                     &  49673648.2\sym{***}&  49673648.2\sym{***}&                     \\
-                    &                     &      (8.22)         &      (8.22)         &                     \\
-\addlinespace
-Norton              &                     &  -7666259.5         &  -7666259.5         &                     \\
-                    &                     &     (-1.40)         &     (-1.40)         &                     \\
-\addlinespace
-Norwood             &                     & 135282132.6\sym{***}& 135282132.6\sym{***}&                     \\
-                    &                     &     (32.98)         &     (32.98)         &                     \\
-\addlinespace
-Oxford              &                     & -12619694.0         & -12619694.0         &                     \\
-                    &                     &     (-1.91)         &     (-1.91)         &                     \\
-\addlinespace
-Peabody             &                     &   9977389.1\sym{**} &   9977389.1\sym{**} &                     \\
-                    &                     &      (2.94)         &      (2.94)         &                     \\
-\addlinespace
-Pittsfield          &                     & -25617594.5\sym{***}& -25617594.5\sym{***}&                     \\
-                    &                     &     (-7.64)         &     (-7.64)         &                     \\
-\addlinespace
-Plymouth            &                     & -26008178.7\sym{***}& -26008178.7\sym{***}&                     \\
-                    &                     &     (-4.57)         &     (-4.57)         &                     \\
-\addlinespace
-Quincy              &                     &  -5122621.6         &  -5122621.6         &                     \\
-                    &                     &     (-1.03)         &     (-1.03)         &                     \\
-\addlinespace
-Randolph            &                     &  -2407969.7         &  -2407969.7         &                     \\
-                    &                     &     (-0.67)         &     (-0.67)         &                     \\
-\addlinespace
-Revere              &                     &   3580359.7         &   3580359.7         &                     \\
-                    &                     &      (0.45)         &      (0.45)         &                     \\
-\addlinespace
-Rockland            &                     & -20926211.3\sym{***}& -20926211.3\sym{***}&                     \\
-                    &                     &     (-5.36)         &     (-5.36)         &                     \\
-\addlinespace
-Salem               &                     & -19892879.6\sym{***}& -19892879.6\sym{***}&                     \\
-                    &                     &     (-5.38)         &     (-5.38)         &                     \\
-\addlinespace
-Sandwich            &                     & -25081254.5\sym{***}& -25081254.5\sym{***}&                     \\
-                    &                     &     (-3.37)         &     (-3.37)         &                     \\
-\addlinespace
-Saugus              &                     &   -340993.8         &   -340993.8         &                     \\
-                    &                     &     (-0.08)         &     (-0.08)         &                     \\
-\addlinespace
-Seekonk             &                     &  12790285.1\sym{**} &  12790285.1\sym{**} &                     \\
-                    &                     &      (2.78)         &      (2.78)         &                     \\
-\addlinespace
-Shirley             &                     & -26310641.7\sym{***}& -26310641.7\sym{***}&                     \\
-                    &                     &     (-4.67)         &     (-4.67)         &                     \\
-\addlinespace
-Shrewsbury          &                     & -13932047.6\sym{*}  & -13932047.6\sym{*}  &                     \\
-                    &                     &     (-2.21)         &     (-2.21)         &                     \\
-\addlinespace
-Somerville          &                     & -23932481.5\sym{***}& -23932481.5\sym{***}&                     \\
-                    &                     &     (-3.63)         &     (-3.63)         &                     \\
-\addlinespace
-South Hadley        &                     & -24837142.8\sym{***}& -24837142.8\sym{***}&                     \\
-                    &                     &     (-4.77)         &     (-4.77)         &                     \\
-\addlinespace
-Southbridge         &                     & -25986587.2\sym{***}& -25986587.2\sym{***}&                     \\
-                    &                     &     (-6.88)         &     (-6.88)         &                     \\
-\addlinespace
-Southwick           &                     & -25424600.0\sym{***}& -25424600.0\sym{***}&                     \\
-                    &                     &     (-3.65)         &     (-3.65)         &                     \\
-\addlinespace
-Spencer             &                     & -26098696.3\sym{***}& -26098696.3\sym{***}&                     \\
-                    &                     &     (-5.12)         &     (-5.12)         &                     \\
-\addlinespace
-Springfield         &                     & -21965898.8\sym{***}& -21965898.8\sym{***}&                     \\
-                    &                     &     (-7.48)         &     (-7.48)         &                     \\
-\addlinespace
-Stoughton           &                     & -13918342.5\sym{***}& -13918342.5\sym{***}&                     \\
-                    &                     &     (-3.68)         &     (-3.68)         &                     \\
-\addlinespace
-Swampscott          &                     &  -6303624.1         &  -6303624.1         &                     \\
-                    &                     &     (-1.18)         &     (-1.18)         &                     \\
-\addlinespace
-Taunton             &                     & -25117756.6\sym{***}& -25117756.6\sym{***}&                     \\
-                    &                     &     (-7.25)         &     (-7.25)         &                     \\
-\addlinespace
-Tewksbury           &                     &   4960284.1         &   4960284.1         &                     \\
-                    &                     &      (1.11)         &      (1.11)         &                     \\
-\addlinespace
-Three Rivers        &                     & -25876069.9\sym{***}& -25876069.9\sym{***}&                     \\
-                    &                     &     (-3.71)         &     (-3.71)         &                     \\
-\addlinespace
-Tyngsboro           &                     & -23326009.0\sym{***}& -23326009.0\sym{***}&                     \\
-                    &                     &     (-3.35)         &     (-3.35)         &                     \\
-\addlinespace
-Wakefield           &                     & -13733066.0\sym{**} & -13733066.0\sym{**} &                     \\
-                    &                     &     (-2.70)         &     (-2.70)         &                     \\
-\addlinespace
-Walpole             &                     & -13399797.3\sym{*}  & -13399797.3\sym{*}  &                     \\
-                    &                     &     (-2.30)         &     (-2.30)         &                     \\
-\addlinespace
-Waltham             &                     &    435329.0         &    435329.0         &                     \\
-                    &                     &      (0.12)         &      (0.12)         &                     \\
-\addlinespace
-Ware                &                     & -26606046.0\sym{***}& -26606046.0\sym{***}&                     \\
-                    &                     &     (-5.72)         &     (-5.72)         &                     \\
-\addlinespace
-Watertown           &                     &  22686557.5\sym{***}&  22686557.5\sym{***}&                     \\
-                    &                     &      (3.44)         &      (3.44)         &                     \\
-\addlinespace
-Webster             &                     & -25363678.1\sym{***}& -25363678.1\sym{***}&                     \\
-                    &                     &     (-4.03)         &     (-4.03)         &                     \\
-\addlinespace
-West Springfield    &                     & -25265471.7\sym{***}& -25265471.7\sym{***}&                     \\
-                    &                     &     (-5.88)         &     (-5.88)         &                     \\
-\addlinespace
-Westborough         &                     &   5644711.5         &   5644711.5         &                     \\
-                    &                     &      (1.29)         &      (1.29)         &                     \\
-\addlinespace
-Westwood            &                     &   5943592.0         &   5943592.0         &                     \\
-                    &                     &      (0.80)         &      (0.80)         &                     \\
-\addlinespace
-Weymouth            &                     &  -2354873.6         &  -2354873.6         &                     \\
-                    &                     &     (-0.44)         &     (-0.44)         &                     \\
-\addlinespace
-Whitinsville        &                     & -26113031.8\sym{**} & -26113031.8\sym{**} &                     \\
-                    &                     &     (-3.25)         &     (-3.25)         &                     \\
-\addlinespace
-Whitman             &                     & -24430447.6\sym{***}& -24430447.6\sym{***}&                     \\
-                    &                     &     (-4.69)         &     (-4.69)         &                     \\
-\addlinespace
-Winchendon          &                     & -26829580.4\sym{***}& -26829580.4\sym{***}&                     \\
-                    &                     &     (-3.85)         &     (-3.85)         &                     \\
-\addlinespace
-Woburn              &                     &  51069929.9\sym{***}&  51069929.9\sym{***}&                     \\
-                    &                     &      (9.05)         &      (9.05)         &                     \\
-\addlinespace
-Worcester           &                     & -23487792.3\sym{***}& -23487792.3\sym{***}&                     \\
-                    &                     &     (-7.79)         &     (-7.79)         &                     \\
-\addlinespace
-group(property\_address\_city file\_year)=1&                     &                     &                     &           0         \\
-                    &                     &                     &                     &         (.)         \\
-\addlinespace
-group(property\_address\_city file\_year)=2&                     &                     &                     & -25607702.2\sym{**} \\
-                    &                     &                     &                     &     (-2.99)         \\
-\addlinespace
-group(property\_address\_city file\_year)=3&                     &                     &                     & -21284383.9         \\
-                    &                     &                     &                     &     (-1.85)         \\
-\addlinespace
-group(property\_address\_city file\_year)=7&                     &                     &                     & -38581122.2\sym{***}\\
-                    &                     &                     &                     &     (-4.94)         \\
-\addlinespace
-group(property\_address\_city file\_year)=8&                     &                     &                     & -38411331.2\sym{***}\\
-                    &                     &                     &                     &     (-4.90)         \\
-\addlinespace
-group(property\_address\_city file\_year)=9&                     &                     &                     & -34767371.4\sym{***}\\
-                    &                     &                     &                     &     (-4.31)         \\
-\addlinespace
-group(property\_address\_city file\_year)=11&                     &                     &                     & -34630813.9\sym{***}\\
-                    &                     &                     &                     &     (-4.27)         \\
-\addlinespace
-group(property\_address\_city file\_year)=12&                     &                     &                     & -26507586.7\sym{**} \\
-                    &                     &                     &                     &     (-3.25)         \\
-\addlinespace
-group(property\_address\_city file\_year)=13&                     &                     &                     &  -7386286.8         \\
-                    &                     &                     &                     &     (-0.72)         \\
-\addlinespace
-group(property\_address\_city file\_year)=14&                     &                     &                     & -17859840.8         \\
-                    &                     &                     &                     &     (-1.64)         \\
-\addlinespace
-group(property\_address\_city file\_year)=23&                     &                     &                     & -38408518.6\sym{***}\\
-                    &                     &                     &                     &     (-4.91)         \\
-\addlinespace
-group(property\_address\_city file\_year)=24&                     &                     &                     & -36264514.4\sym{***}\\
-                    &                     &                     &                     &     (-4.60)         \\
-\addlinespace
-group(property\_address\_city file\_year)=26&                     &                     &                     & -38279509.7\sym{***}\\
-                    &                     &                     &                     &     (-4.89)         \\
-\addlinespace
-group(property\_address\_city file\_year)=31&                     &                     &                     &  -6458709.7         \\
-                    &                     &                     &                     &     (-0.48)         \\
-\addlinespace
-group(property\_address\_city file\_year)=33&                     &                     &                     & -37591120.1\sym{***}\\
-                    &                     &                     &                     &     (-4.81)         \\
-\addlinespace
-group(property\_address\_city file\_year)=34&                     &                     &                     & -36376733.5\sym{***}\\
-                    &                     &                     &                     &     (-4.63)         \\
-\addlinespace
-group(property\_address\_city file\_year)=35&                     &                     &                     &   6571579.9         \\
-                    &                     &                     &                     &      (0.24)         \\
-\addlinespace
-group(property\_address\_city file\_year)=39&                     &                     &                     & -26410797.0\sym{**} \\
-                    &                     &                     &                     &     (-3.22)         \\
-\addlinespace
-group(property\_address\_city file\_year)=40&                     &                     &                     & -30562560.8\sym{***}\\
-                    &                     &                     &                     &     (-3.63)         \\
-\addlinespace
-group(property\_address\_city file\_year)=42&                     &                     &                     &     17743.6         \\
-                    &                     &                     &                     &      (0.00)         \\
-\addlinespace
-group(property\_address\_city file\_year)=43&                     &                     &                     &  -7566228.0         \\
-                    &                     &                     &                     &     (-0.73)         \\
-\addlinespace
-group(property\_address\_city file\_year)=53&                     &                     &                     &  23206974.1\sym{*}  \\
-                    &                     &                     &                     &      (2.30)         \\
-\addlinespace
-group(property\_address\_city file\_year)=54&                     &                     &                     & -37332881.4\sym{***}\\
-                    &                     &                     &                     &     (-4.76)         \\
-\addlinespace
-group(property\_address\_city file\_year)=56&                     &                     &                     &   -474304.1         \\
-                    &                     &                     &                     &     (-0.05)         \\
-\addlinespace
-group(property\_address\_city file\_year)=58&                     &                     &                     & -33587109.7\sym{***}\\
-                    &                     &                     &                     &     (-4.28)         \\
-\addlinespace
-group(property\_address\_city file\_year)=59&                     &                     &                     & -34174537.7\sym{***}\\
-                    &                     &                     &                     &     (-4.34)         \\
-\addlinespace
-group(property\_address\_city file\_year)=60&                     &                     &                     & -26000080.5\sym{**} \\
-                    &                     &                     &                     &     (-2.61)         \\
-\addlinespace
-group(property\_address\_city file\_year)=66&                     &                     &                     &  30346290.9         \\
-                    &                     &                     &                     &      (1.64)         \\
-\addlinespace
-group(property\_address\_city file\_year)=67&                     &                     &                     &  -1766588.2         \\
-                    &                     &                     &                     &     (-0.18)         \\
-\addlinespace
-group(property\_address\_city file\_year)=68&                     &                     &                     & -17027153.2         \\
-                    &                     &                     &                     &     (-1.44)         \\
-\addlinespace
-group(property\_address\_city file\_year)=73&                     &                     &                     & -16144028.9\sym{*}  \\
-                    &                     &                     &                     &     (-2.06)         \\
-\addlinespace
-group(property\_address\_city file\_year)=74&                     &                     &                     & -31298276.4\sym{***}\\
-                    &                     &                     &                     &     (-3.53)         \\
-\addlinespace
-group(property\_address\_city file\_year)=75&                     &                     &                     &  -7340083.6         \\
-                    &                     &                     &                     &     (-0.70)         \\
-\addlinespace
-group(property\_address\_city file\_year)=83&                     &                     &                     & -35489242.1\sym{***}\\
-                    &                     &                     &                     &     (-4.50)         \\
-\addlinespace
-group(property\_address\_city file\_year)=84&                     &                     &                     & -37890557.6\sym{***}\\
-                    &                     &                     &                     &     (-4.84)         \\
-\addlinespace
-group(property\_address\_city file\_year)=88&                     &                     &                     &  24176473.6         \\
-                    &                     &                     &                     &      (1.77)         \\
-\addlinespace
-group(property\_address\_city file\_year)=92&                     &                     &                     & -12488676.4         \\
-                    &                     &                     &                     &     (-1.06)         \\
-\addlinespace
-group(property\_address\_city file\_year)=99&                     &                     &                     & -35936941.8\sym{***}\\
-                    &                     &                     &                     &     (-4.50)         \\
-\addlinespace
-group(property\_address\_city file\_year)=100&                     &                     &                     & -38696642.4\sym{***}\\
-                    &                     &                     &                     &     (-4.94)         \\
-\addlinespace
-group(property\_address\_city file\_year)=103&                     &                     &                     & -28496105.0\sym{**} \\
-                    &                     &                     &                     &     (-3.22)         \\
-\addlinespace
-group(property\_address\_city file\_year)=113&                     &                     &                     & -30890843.1\sym{***}\\
-                    &                     &                     &                     &     (-3.52)         \\
-\addlinespace
-group(property\_address\_city file\_year)=120&                     &                     &                     & -20911443.0         \\
-                    &                     &                     &                     &     (-1.95)         \\
-\addlinespace
-group(property\_address\_city file\_year)=121&                     &                     &                     & -38546947.5\sym{***}\\
-                    &                     &                     &                     &     (-4.93)         \\
-\addlinespace
-group(property\_address\_city file\_year)=122&                     &                     &                     & -36566747.8\sym{***}\\
-                    &                     &                     &                     &     (-4.61)         \\
-\addlinespace
-group(property\_address\_city file\_year)=123&                     &                     &                     & -33882902.8\sym{***}\\
-                    &                     &                     &                     &     (-4.31)         \\
-\addlinespace
-group(property\_address\_city file\_year)=125&                     &                     &                     & -35520028.9\sym{***}\\
-                    &                     &                     &                     &     (-4.50)         \\
-\addlinespace
-group(property\_address\_city file\_year)=126&                     &                     &                     & -34208737.4\sym{***}\\
-                    &                     &                     &                     &     (-4.16)         \\
-\addlinespace
-group(property\_address\_city file\_year)=127&                     &                     &                     & -37615554.7\sym{***}\\
-                    &                     &                     &                     &     (-4.81)         \\
-\addlinespace
-group(property\_address\_city file\_year)=128&                     &                     &                     & -37542381.2\sym{***}\\
-                    &                     &                     &                     &     (-4.80)         \\
-\addlinespace
-group(property\_address\_city file\_year)=132&                     &                     &                     &  10784136.1         \\
-                    &                     &                     &                     &      (1.37)         \\
-\addlinespace
-group(property\_address\_city file\_year)=134&                     &                     &                     &   9632586.1         \\
-                    &                     &                     &                     &      (1.22)         \\
-\addlinespace
-group(property\_address\_city file\_year)=135&                     &                     &                     & -16437743.6\sym{*}  \\
-                    &                     &                     &                     &     (-1.99)         \\
-\addlinespace
-group(property\_address\_city file\_year)=136&                     &                     &                     & -20864508.2\sym{*}  \\
-                    &                     &                     &                     &     (-2.23)         \\
-\addlinespace
-group(property\_address\_city file\_year)=137&                     &                     &                     &  -7993710.8         \\
-                    &                     &                     &                     &     (-0.74)         \\
-\addlinespace
-group(property\_address\_city file\_year)=138&                     &                     &                     & -34985127.9\sym{***}\\
-                    &                     &                     &                     &     (-4.42)         \\
-\addlinespace
-group(property\_address\_city file\_year)=142&                     &                     &                     & -31556449.3\sym{***}\\
-                    &                     &                     &                     &     (-3.94)         \\
-\addlinespace
-group(property\_address\_city file\_year)=143&                     &                     &                     & -28620927.6\sym{***}\\
-                    &                     &                     &                     &     (-3.48)         \\
-\addlinespace
-group(property\_address\_city file\_year)=144&                     &                     &                     & -28153048.9\sym{**} \\
-                    &                     &                     &                     &     (-3.16)         \\
-\addlinespace
-group(property\_address\_city file\_year)=147&                     &                     &                     & -35823404.4\sym{***}\\
-                    &                     &                     &                     &     (-4.51)         \\
-\addlinespace
-group(property\_address\_city file\_year)=153&                     &                     &                     & -38485321.4\sym{***}\\
-                    &                     &                     &                     &     (-4.92)         \\
-\addlinespace
-group(property\_address\_city file\_year)=156&                     &                     &                     & -33011555.7\sym{***}\\
-                    &                     &                     &                     &     (-4.19)         \\
-\addlinespace
-group(property\_address\_city file\_year)=164&                     &                     &                     & -36537387.6\sym{***}\\
-                    &                     &                     &                     &     (-4.65)         \\
-\addlinespace
-group(property\_address\_city file\_year)=167&                     &                     &                     & -38203020.1\sym{***}\\
-                    &                     &                     &                     &     (-4.89)         \\
-\addlinespace
-group(property\_address\_city file\_year)=168&                     &                     &                     & -31817841.1\sym{***}\\
-                    &                     &                     &                     &     (-3.55)         \\
-\addlinespace
-group(property\_address\_city file\_year)=169&                     &                     &                     & -25178303.5\sym{*}  \\
-                    &                     &                     &                     &     (-2.30)         \\
-\addlinespace
-group(property\_address\_city file\_year)=171&                     &                     &                     & -36001309.4\sym{***}\\
-                    &                     &                     &                     &     (-4.57)         \\
-\addlinespace
-group(property\_address\_city file\_year)=172&                     &                     &                     & -38116676.0\sym{***}\\
-                    &                     &                     &                     &     (-4.88)         \\
-\addlinespace
-group(property\_address\_city file\_year)=173&                     &                     &                     & -37655672.3\sym{***}\\
-                    &                     &                     &                     &     (-4.75)         \\
-\addlinespace
-group(property\_address\_city file\_year)=174&                     &                     &                     & -35945808.4\sym{***}\\
-                    &                     &                     &                     &     (-4.55)         \\
-\addlinespace
-group(property\_address\_city file\_year)=179&                     &                     &                     & -35689685.3\sym{***}\\
-                    &                     &                     &                     &     (-4.52)         \\
-\addlinespace
-group(property\_address\_city file\_year)=180&                     &                     &                     & -30243768.9\sym{***}\\
-                    &                     &                     &                     &     (-3.70)         \\
-\addlinespace
-group(property\_address\_city file\_year)=182&                     &                     &                     & -35512860.3\sym{***}\\
-                    &                     &                     &                     &     (-4.53)         \\
-\addlinespace
-group(property\_address\_city file\_year)=183&                     &                     &                     & -35437021.0\sym{***}\\
-                    &                     &                     &                     &     (-4.52)         \\
-\addlinespace
-group(property\_address\_city file\_year)=187&                     &                     &                     & -33818835.1\sym{***}\\
-                    &                     &                     &                     &     (-4.30)         \\
-\addlinespace
-group(property\_address\_city file\_year)=194&                     &                     &                     & -30351764.1\sym{***}\\
-                    &                     &                     &                     &     (-3.87)         \\
-\addlinespace
-group(property\_address\_city file\_year)=195&                     &                     &                     & -33456532.5\sym{***}\\
-                    &                     &                     &                     &     (-4.26)         \\
-\addlinespace
-group(property\_address\_city file\_year)=196&                     &                     &                     & -37376620.2\sym{***}\\
-                    &                     &                     &                     &     (-4.76)         \\
-\addlinespace
-group(property\_address\_city file\_year)=197&                     &                     &                     & -38272695.2\sym{***}\\
-                    &                     &                     &                     &     (-4.87)         \\
-\addlinespace
-group(property\_address\_city file\_year)=198&                     &                     &                     & -38542293.9\sym{***}\\
-                    &                     &                     &                     &     (-4.92)         \\
-\addlinespace
-group(property\_address\_city file\_year)=199&                     &                     &                     & -33415366.0\sym{***}\\
-                    &                     &                     &                     &     (-4.23)         \\
-\addlinespace
-group(property\_address\_city file\_year)=200&                     &                     &                     & -32091179.2\sym{***}\\
-                    &                     &                     &                     &     (-3.98)         \\
-\addlinespace
-group(property\_address\_city file\_year)=201&                     &                     &                     & -11405153.9         \\
-                    &                     &                     &                     &     (-1.15)         \\
-\addlinespace
-group(property\_address\_city file\_year)=203&                     &                     &                     &  -8575986.1         \\
-                    &                     &                     &                     &     (-0.88)         \\
-\addlinespace
-group(property\_address\_city file\_year)=204&                     &                     &                     &  -2489181.1         \\
-                    &                     &                     &                     &     (-0.26)         \\
-\addlinespace
-group(property\_address\_city file\_year)=206&                     &                     &                     & -29161593.4\sym{***}\\
-                    &                     &                     &                     &     (-3.56)         \\
-\addlinespace
-group(property\_address\_city file\_year)=207&                     &                     &                     & -25289163.9\sym{**} \\
-                    &                     &                     &                     &     (-2.94)         \\
-\addlinespace
-group(property\_address\_city file\_year)=208&                     &                     &                     & -36814423.9\sym{***}\\
-                    &                     &                     &                     &     (-4.59)         \\
-\addlinespace
-group(property\_address\_city file\_year)=209&                     &                     &                     & -37786016.4\sym{***}\\
-                    &                     &                     &                     &     (-4.79)         \\
-\addlinespace
-group(property\_address\_city file\_year)=212&                     &                     &                     & -35944881.1\sym{***}\\
-                    &                     &                     &                     &     (-4.54)         \\
-\addlinespace
-group(property\_address\_city file\_year)=213&                     &                     &                     & -35623833.5\sym{***}\\
-                    &                     &                     &                     &     (-4.50)         \\
-\addlinespace
-group(property\_address\_city file\_year)=214&                     &                     &                     & -37873195.8\sym{***}\\
-                    &                     &                     &                     &     (-4.84)         \\
-\addlinespace
-group(property\_address\_city file\_year)=216&                     &                     &                     & -36363903.5\sym{***}\\
-                    &                     &                     &                     &     (-4.64)         \\
-\addlinespace
-group(property\_address\_city file\_year)=224&                     &                     &                     & -29612338.5\sym{***}\\
-                    &                     &                     &                     &     (-3.61)         \\
-\addlinespace
-group(property\_address\_city file\_year)=225&                     &                     &                     & -29769927.3\sym{***}\\
-                    &                     &                     &                     &     (-3.64)         \\
-\addlinespace
-group(property\_address\_city file\_year)=226&                     &                     &                     & -35920725.6\sym{***}\\
-                    &                     &                     &                     &     (-4.46)         \\
-\addlinespace
-group(property\_address\_city file\_year)=227&                     &                     &                     & -19714858.5\sym{*}  \\
-                    &                     &                     &                     &     (-2.18)         \\
-\addlinespace
-group(property\_address\_city file\_year)=229&                     &                     &                     & -24169190.7\sym{*}  \\
-                    &                     &                     &                     &     (-2.43)         \\
-\addlinespace
-group(property\_address\_city file\_year)=230&                     &                     &                     & -16642502.5\sym{*}  \\
-                    &                     &                     &                     &     (-1.99)         \\
-\addlinespace
-group(property\_address\_city file\_year)=232&                     &                     &                     & -35290126.4\sym{***}\\
-                    &                     &                     &                     &     (-4.36)         \\
-\addlinespace
-group(property\_address\_city file\_year)=242&                     &                     &                     &  15453086.1         \\
-                    &                     &                     &                     &      (0.73)         \\
-\addlinespace
-group(property\_address\_city file\_year)=243&                     &                     &                     &  44111906.4\sym{***}\\
-                    &                     &                     &                     &      (4.45)         \\
-\addlinespace
-group(property\_address\_city file\_year)=246&                     &                     &                     & -37288510.0\sym{***}\\
-                    &                     &                     &                     &     (-4.76)         \\
-\addlinespace
-group(property\_address\_city file\_year)=248&                     &                     &                     & -32621058.9\sym{***}\\
-                    &                     &                     &                     &     (-4.15)         \\
-\addlinespace
-group(property\_address\_city file\_year)=249&                     &                     &                     & -36158196.4\sym{***}\\
-                    &                     &                     &                     &     (-4.55)         \\
-\addlinespace
-group(property\_address\_city file\_year)=251&                     &                     &                     & -36677620.1\sym{***}\\
-                    &                     &                     &                     &     (-4.68)         \\
-\addlinespace
-group(property\_address\_city file\_year)=252&                     &                     &                     & -37842382.7\sym{***}\\
-                    &                     &                     &                     &     (-4.81)         \\
-\addlinespace
-group(property\_address\_city file\_year)=253&                     &                     &                     &  -9891138.9         \\
-                    &                     &                     &                     &     (-1.03)         \\
-\addlinespace
-group(property\_address\_city file\_year)=254&                     &                     &                     & -23094891.8\sym{*}  \\
-                    &                     &                     &                     &     (-2.52)         \\
-\addlinespace
-group(property\_address\_city file\_year)=255&                     &                     &                     & -36366273.9\sym{***}\\
-                    &                     &                     &                     &     (-4.62)         \\
-\addlinespace
-group(property\_address\_city file\_year)=256&                     &                     &                     & -37392816.4\sym{***}\\
-                    &                     &                     &                     &     (-4.74)         \\
-\addlinespace
-group(property\_address\_city file\_year)=257&                     &                     &                     & -21949701.4         \\
-                    &                     &                     &                     &     (-1.85)         \\
-\addlinespace
-group(property\_address\_city file\_year)=258&                     &                     &                     & -21556393.9         \\
-                    &                     &                     &                     &     (-1.83)         \\
-\addlinespace
-group(property\_address\_city file\_year)=261&                     &                     &                     & -27309173.9\sym{**} \\
-                    &                     &                     &                     &     (-3.08)         \\
-\addlinespace
-group(property\_address\_city file\_year)=271&                     &                     &                     & -38347156.4\sym{***}\\
-                    &                     &                     &                     &     (-4.86)         \\
-\addlinespace
-group(property\_address\_city file\_year)=273&                     &                     &                     & -34577851.5\sym{***}\\
-                    &                     &                     &                     &     (-4.24)         \\
-\addlinespace
-group(property\_address\_city file\_year)=274&                     &                     &                     &  37839286.1\sym{***}\\
-                    &                     &                     &                     &      (4.83)         \\
-\addlinespace
-group(property\_address\_city file\_year)=277&                     &                     &                     & -30100413.9\sym{**} \\
-                    &                     &                     &                     &     (-2.94)         \\
-\addlinespace
-group(property\_address\_city file\_year)=278&                     &                     &                     & -13288240.5         \\
-                    &                     &                     &                     &     (-1.28)         \\
-\addlinespace
-group(property\_address\_city file\_year)=279&                     &                     &                     & 171070980.6\sym{***}\\
-                    &                     &                     &                     &      (7.17)         \\
-\addlinespace
-group(property\_address\_city file\_year)=280&                     &                     &                     &  66019571.9\sym{***}\\
-                    &                     &                     &                     &      (3.83)         \\
-\addlinespace
-group(property\_address\_city file\_year)=288&                     &                     &                     & -24548443.6\sym{*}  \\
-                    &                     &                     &                     &     (-2.28)         \\
-\addlinespace
-group(property\_address\_city file\_year)=290&                     &                     &                     &  -6453926.4         \\
-                    &                     &                     &                     &     (-0.73)         \\
-\addlinespace
-group(property\_address\_city file\_year)=291&                     &                     &                     &   4959403.0         \\
-                    &                     &                     &                     &      (0.52)         \\
-\addlinespace
-group(property\_address\_city file\_year)=296&                     &                     &                     & -37918902.4\sym{***}\\
-                    &                     &                     &                     &     (-4.85)         \\
-\addlinespace
-group(property\_address\_city file\_year)=297&                     &                     &                     & -37250575.6\sym{***}\\
-                    &                     &                     &                     &     (-4.76)         \\
-\addlinespace
-group(property\_address\_city file\_year)=299&                     &                     &                     & -35650288.1\sym{***}\\
-                    &                     &                     &                     &     (-4.42)         \\
-\addlinespace
-group(property\_address\_city file\_year)=302&                     &                     &                     & -14794934.9         \\
-                    &                     &                     &                     &     (-1.32)         \\
-\addlinespace
-group(property\_address\_city file\_year)=303&                     &                     &                     & -15642334.1         \\
-                    &                     &                     &                     &     (-1.81)         \\
-\addlinespace
-group(property\_address\_city file\_year)=304&                     &                     &                     & -12480878.8         \\
-                    &                     &                     &                     &     (-1.05)         \\
-\addlinespace
-group(property\_address\_city file\_year)=308&                     &                     &                     &  -8685368.9         \\
-                    &                     &                     &                     &     (-0.49)         \\
-\addlinespace
-group(property\_address\_city file\_year)=310&                     &                     &                     & -32778990.4\sym{***}\\
-                    &                     &                     &                     &     (-4.16)         \\
-\addlinespace
-group(property\_address\_city file\_year)=318&                     &                     &                     & -32113017.2\sym{***}\\
-                    &                     &                     &                     &     (-4.04)         \\
-\addlinespace
-group(property\_address\_city file\_year)=320&                     &                     &                     & -37296643.1\sym{***}\\
-                    &                     &                     &                     &     (-4.76)         \\
-\addlinespace
-group(property\_address\_city file\_year)=321&                     &                     &                     & -21065231.0\sym{*}  \\
-                    &                     &                     &                     &     (-2.04)         \\
-\addlinespace
-group(property\_address\_city file\_year)=322&                     &                     &                     &  -3778856.1         \\
-                    &                     &                     &                     &     (-0.23)         \\
-\addlinespace
-group(property\_address\_city file\_year)=323&                     &                     &                     &   6070469.5         \\
-                    &                     &                     &                     &      (0.36)         \\
-\addlinespace
-group(property\_address\_city file\_year)=325&                     &                     &                     &  -4489793.1         \\
-                    &                     &                     &                     &     (-0.36)         \\
-\addlinespace
-group(property\_address\_city file\_year)=326&                     &                     &                     &   2727158.8         \\
-                    &                     &                     &                     &      (0.29)         \\
-\addlinespace
-group(property\_address\_city file\_year)=330&                     &                     &                     & -38186853.5\sym{***}\\
-                    &                     &                     &                     &     (-4.89)         \\
-\addlinespace
-group(property\_address\_city file\_year)=331&                     &                     &                     & -38358330.5\sym{***}\\
-                    &                     &                     &                     &     (-4.89)         \\
-\addlinespace
-group(property\_address\_city file\_year)=332&                     &                     &                     & -25895736.1\sym{*}  \\
-                    &                     &                     &                     &     (-2.53)         \\
-\addlinespace
-group(property\_address\_city file\_year)=334&                     &                     &                     & -35861231.1\sym{***}\\
-                    &                     &                     &                     &     (-4.56)         \\
-\addlinespace
-group(property\_address\_city file\_year)=344&                     &                     &                     & -36847731.1\sym{***}\\
-                    &                     &                     &                     &     (-4.69)         \\
-\addlinespace
-group(property\_address\_city file\_year)=345&                     &                     &                     & -37030915.7\sym{***}\\
-                    &                     &                     &                     &     (-4.71)         \\
-\addlinespace
-group(property\_address\_city file\_year)=350&                     &                     &                     & -37844551.0\sym{***}\\
-                    &                     &                     &                     &     (-4.83)         \\
-\addlinespace
-group(property\_address\_city file\_year)=351&                     &                     &                     & -38140516.2\sym{***}\\
-                    &                     &                     &                     &     (-4.87)         \\
-\addlinespace
-group(property\_address\_city file\_year)=352&                     &                     &                     & -37366833.5\sym{***}\\
-                    &                     &                     &                     &     (-4.75)         \\
-\addlinespace
-group(property\_address\_city file\_year)=353&                     &                     &                     & -38074639.7\sym{***}\\
-                    &                     &                     &                     &     (-4.86)         \\
-\addlinespace
-group(property\_address\_city file\_year)=355&                     &                     &                     & -35317254.9\sym{***}\\
-                    &                     &                     &                     &     (-4.51)         \\
-\addlinespace
-group(property\_address\_city file\_year)=356&                     &                     &                     & -32231981.1\sym{***}\\
-                    &                     &                     &                     &     (-4.09)         \\
-\addlinespace
-group(property\_address\_city file\_year)=359&                     &                     &                     & -28430715.7\sym{***}\\
-                    &                     &                     &                     &     (-3.37)         \\
-\addlinespace
-group(property\_address\_city file\_year)=360&                     &                     &                     & -23835191.3\sym{**} \\
-                    &                     &                     &                     &     (-2.72)         \\
-\addlinespace
-group(property\_address\_city file\_year)=366&                     &                     &                     & -18299793.4         \\
-                    &                     &                     &                     &     (-1.76)         \\
-\addlinespace
-group(property\_address\_city file\_year)=369&                     &                     &                     & -36289434.6\sym{***}\\
-                    &                     &                     &                     &     (-4.62)         \\
-\addlinespace
-group(property\_address\_city file\_year)=370&                     &                     &                     & -36493934.4\sym{***}\\
-                    &                     &                     &                     &     (-4.65)         \\
-\addlinespace
-group(property\_address\_city file\_year)=372&                     &                     &                     &  -9326920.9         \\
-                    &                     &                     &                     &     (-0.98)         \\
-\addlinespace
-group(property\_address\_city file\_year)=373&                     &                     &                     &  -2475268.6         \\
-                    &                     &                     &                     &     (-0.20)         \\
-\addlinespace
-group(property\_address\_city file\_year)=375&                     &                     &                     & -38163372.8\sym{***}\\
-                    &                     &                     &                     &     (-4.87)         \\
-\addlinespace
-group(property\_address\_city file\_year)=377&                     &                     &                     & -35160371.0\sym{***}\\
-                    &                     &                     &                     &     (-4.47)         \\
-\addlinespace
-group(property\_address\_city file\_year)=383&                     &                     &                     & -22375844.4\sym{*}  \\
-                    &                     &                     &                     &     (-2.42)         \\
-\addlinespace
-group(property\_address\_city file\_year)=384&                     &                     &                     & -30123833.5\sym{***}\\
-                    &                     &                     &                     &     (-3.63)         \\
-\addlinespace
-group(property\_address\_city file\_year)=385&                     &                     &                     & -25234159.3\sym{*}  \\
-                    &                     &                     &                     &     (-2.51)         \\
-\addlinespace
-group(property\_address\_city file\_year)=386&                     &                     &                     &  -8854952.2         \\
-                    &                     &                     &                     &     (-0.95)         \\
-\addlinespace
-group(property\_address\_city file\_year)=387&                     &                     &                     & -18318728.6         \\
-                    &                     &                     &                     &     (-1.88)         \\
-\addlinespace
-group(property\_address\_city file\_year)=388&                     &                     &                     & -38189648.1\sym{***}\\
-                    &                     &                     &                     &     (-4.88)         \\
-\addlinespace
-group(property\_address\_city file\_year)=389&                     &                     &                     & -37389578.2\sym{***}\\
-                    &                     &                     &                     &     (-4.73)         \\
-\addlinespace
-group(property\_address\_city file\_year)=393&                     &                     &                     &  10628481.4         \\
-                    &                     &                     &                     &      (0.58)         \\
-\addlinespace
-group(property\_address\_city file\_year)=394&                     &                     &                     & -37495166.7\sym{***}\\
-                    &                     &                     &                     &     (-4.78)         \\
-\addlinespace
-group(property\_address\_city file\_year)=401&                     &                     &                     & -37444903.2\sym{***}\\
-                    &                     &                     &                     &     (-4.79)         \\
-\addlinespace
-group(property\_address\_city file\_year)=406&                     &                     &                     &  -3258867.6         \\
-                    &                     &                     &                     &     (-0.37)         \\
-\addlinespace
-group(property\_address\_city file\_year)=407&                     &                     &                     & -16465803.5         \\
-                    &                     &                     &                     &     (-1.83)         \\
-\addlinespace
-group(property\_address\_city file\_year)=413&                     &                     &                     &  -6016620.1         \\
-                    &                     &                     &                     &     (-0.63)         \\
-\addlinespace
-group(property\_address\_city file\_year)=414&                     &                     &                     & -14426433.5         \\
-                    &                     &                     &                     &     (-1.63)         \\
-\addlinespace
-group(property\_address\_city file\_year)=415&                     &                     &                     & -37947393.9\sym{***}\\
-                    &                     &                     &                     &     (-4.83)         \\
-\addlinespace
-group(property\_address\_city file\_year)=417&                     &                     &                     & -36315149.7\sym{***}\\
-                    &                     &                     &                     &     (-4.62)         \\
-\addlinespace
-group(property\_address\_city file\_year)=423&                     &                     &                     & -38663942.4\sym{***}\\
-                    &                     &                     &                     &     (-4.93)         \\
-\addlinespace
-group(property\_address\_city file\_year)=426&                     &                     &                     &  39043316.3\sym{**} \\
-                    &                     &                     &                     &      (2.60)         \\
-\addlinespace
-group(property\_address\_city file\_year)=427&                     &                     &                     & -35389716.0\sym{***}\\
-                    &                     &                     &                     &     (-4.52)         \\
-\addlinespace
-Constant            &   7494901.5\sym{***}&  25580389.2\sym{***}&  25580389.2\sym{***}&  38169851.5\sym{***}\\
-                    &     (11.15)         &      (8.72)         &      (8.72)         &      (4.70)         \\
+judgment\_for\_plaintiff& 3259177.986& 1507062.672& 1507062.672&  751962.414\\
+                    & (762388.53)& (577088.19)& (577088.19)&(2866558.93)\\
 \midrule
-Observations        &        5567         &        5567         &        5567         &        5567         \\
+Observations        &        5567&        5567&        5567&        5567\\
 \bottomrule
-\multicolumn{5}{l}{\footnotesize \textit{t} statistics in parentheses}\\
-\multicolumn{5}{l}{\footnotesize \sym{*} \(p<0.05\), \sym{**} \(p<0.01\), \sym{***} \(p<0.001\)}\\
 \end{tabular}

### 2022-12-07 output/01_exploratory/tables/bldg_val_results_table.tex
Created estimation tables

@@
                     &\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}\\
-                    &        b/se&        b/se&        b/se&        b/se\\
+                    &        b/se         &        b/se         &        b/se         &        b/se         \\
 \midrule
-judgment\_for\_plaintiff& 2434984.290& 1161293.951& 1161293.951& 1055231.099\\
-                    & (588147.83)& (453836.79)& (453836.79)&(2319051.94)\\
+judgment\_for\_plaintiff& 2434984.290\sym{***}& 1161293.951\sym{*}  & 1161293.951\sym{*}  & 1055231.099         \\
+                    & (588147.83)         & (453836.79)         & (453836.79)         &(2319051.94)         \\
 \midrule
-Observations        &        5567&        5567&        5567&        5567\\
+Observations        &        5567         &        5567         &        5567         &        5567         \\
+$\text{R}^2$        &     0.00307         &       0.491         &       0.491         &       0.527         \\
+City F.E.           &          No         &         Yes         &         Yes         &          No         \\
+Year F.E.           &          No         &         Yes         &         Yes         &          No         \\
+Case Controls       &          No         &          No         &         Yes         &          No         \\
+I.V. Estimate       &          No         &          No         &          No         &         Yes         \\
 \bottomrule

### 2022-12-07 output/01_exploratory/tables/total_val_results_table.tex
Created estimation tables

@@
                     &\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}\\
-                    &        b/se&        b/se&        b/se&        b/se\\
+                    &        b/se         &        b/se         &        b/se         &        b/se         \\
 \midrule
-judgment\_for\_plaintiff& 3259177.986& 1507062.672& 1507062.672&  751962.414\\
-                    & (762388.53)& (577088.19)& (577088.19)&(2866558.93)\\
+judgment\_for\_plaintiff& 3259177.986\sym{***}& 1507062.672\sym{**} & 1507062.672\sym{**} &  751962.414         \\
+                    & (762388.53)         & (577088.19)         & (577088.19)         &(2866558.93)         \\
 \midrule
-Observations        &        5567&        5567&        5567&        5567\\
+Observations        &        5567         &        5567         &        5567         &        5567         \\
+$\text{R}^2$        &     0.00327         &       0.510         &       0.510         &       0.549         \\
+City F.E.           &          No         &         Yes         &         Yes         &          No         \\
+Year F.E.           &          No         &         Yes         &         Yes         &          No         \\
+Case Controls       &          No         &          No         &         Yes         &          No         \\
+I.V. Estimate       &          No         &          No         &          No         &         Yes         \\
 \bottomrule

### 2022-12-07 writing/main.tex
Updates from Overleaf

@@
 \documentclass{article}
-\usepackage{graphicx, setspace, booktabs, float, xcolor, rotating, lscape, lscape, sectsty, rotating}
+\usepackage{graphicx, setspace, booktabs, float, xcolor, rotating, lscape, lscape, sectsty, rotating, pdflscape}
 \usepackage[utf8]{inputenc}
@@
 \begin{document}
+
+\maketitle
 \input{output/01_exploratory/tables/summary_statistics.tex}
 
-\input{}
+\begin{landscape}
+\input{output/01_exploratory/tables/balance_table.tex}
+\end{landscape}
+
+\input{output/01_exploratory/tables/total_val_results_table.tex}
 

### 2022-12-07 output/01_exploratory/tables/ln_total_val_results_table.tex
Added placebo first stage regs and edited main results

\begin{table}[htbp]\centering
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\caption{Estimates of the Impact of Eviction}
\begin{tabular}{l*{4}{c}}
\toprule
                    &\multicolumn{1}{c}{ln\_total\_val}&\multicolumn{1}{c}{ln\_total\_val}&\multicolumn{1}{c}{ln\_total\_val}&\multicolumn{1}{c}{ln\_total\_val}\\
\midrule
Plaintiff Victory   &       0.326\sym{***}&       0.171\sym{*}  &       0.171\sym{*}  &       0.315         \\
                    &      (0.08)         &      (0.07)         &      (0.07)         &      (0.36)         \\
\midrule
Observations        &        3331         &        3331         &        3331         &        3331         \\
$\text{R}^2$        &     0.00510         &       0.321         &       0.321         &       0.325         \\
City F.E.           &          No         &         Yes         &         Yes         &          No         \\
Year F.E.           &          No         &         Yes         &         Yes         &          No         \\
Case Controls       &          No         &          No         &         Yes         &          No         \\
I.V. Estimate       &          No         &          No         &          No         &         Yes         \\
\bottomrule
\end{tabular}
\end{table}

### 2022-12-07 output/01_exploratory/tables/ln_total_val_results_table.tex
Added placebo first stage regs and edited main results

@@
 \caption{Estimates of the Impact of Eviction}
-\begin{tabular}{l*{4}{c}}
+\begin{tabular}{l*{3}{c}}
 \toprule
-                    &\multicolumn{1}{c}{ln\_total\_val}&\multicolumn{1}{c}{ln\_total\_val}&\multicolumn{1}{c}{ln\_total\_val}&\multicolumn{1}{c}{ln\_total\_val}\\
+                    &\multicolumn{1}{c}{ln\_total\_val}&\multicolumn{1}{c}{ln\_total\_val}&\multicolumn{1}{c}{ln\_total\_val}\\
 \midrule
-Plaintiff Victory   &       0.326\sym{***}&       0.171\sym{*}  &       0.171\sym{*}  &       0.315         \\
-                    &      (0.08)         &      (0.07)         &      (0.07)         &      (0.36)         \\
+Plaintiff Victory   &       0.326\sym{***}&       0.171\sym{*}  &      -3.209         \\
+                    &      (0.08)         &      (0.07)         &      (8.08)         \\
 \midrule
-Observations        &        3331         &        3331         &        3331         &        3331         \\
-$\text{R}^2$        &     0.00510         &       0.321         &       0.321         &       0.325         \\
-City F.E.           &          No         &         Yes         &         Yes         &          No         \\
-Year F.E.           &          No         &         Yes         &         Yes         &          No         \\
-Case Controls       &          No         &          No         &         Yes         &          No         \\
-I.V. Estimate       &          No         &          No         &          No         &         Yes         \\
+Observations        &        3331         &        3331         &        2251         \\
+$\text{R}^2$        &     0.00510         &       0.321         &       0.529         \\
+City F.E.           &          No         &         Yes         &          No         \\
+Year F.E.           &          No         &         Yes         &          No         \\
+Controls for Potential I.V. Confounders&          No         &          No         &         Yes         \\
+I.V. Estimate       &          No         &          No         &         Yes         \\
 \bottomrule

### 2022-12-07 writing/presentations/december_7.tex

\documentclass [xcolor=svgnames, t] {beamer} 
\usepackage[utf8]{inputenc}
\usepackage{booktabs, comment} 
\usepackage[absolute, overlay]{textpos} 
\usepackage{pgfpages}
\usepackage[font=footnotesize]{caption}
\useoutertheme{infolines}

\definecolor{brownbrown}{RGB}{56, 28, 0}
\definecolor{brownred}{RGB}{228, 0, 43}

\setbeamercolor{title in head/foot}{bg=brownred, fg=brownbrown}
\setbeamercolor{author in head/foot}{bg=myuniversity}
\setbeamertemplate{page number in head/foot}{}
\usepackage{csquotes}

\usepackage{amsmath}
\usepackage[makeroom]{cancel}

\usepackage{textpos}

\usepackage{tikz}

\usetheme{Madrid}
\definecolor{myuniversity}{RGB}{56, 28, 0}
\usecolortheme[named=myuniversity]{structure}
\usepackage{tikz}

\title[Eviction and Property Values]{Estimating the Effect of Eviction on Assessment Values}

\institute[]{Department of Earth, Environmental, and Planetary Sciences  \\Brown University}

\author[Arjun Shanmugam]{}

\date{\today}

\addtobeamertemplate{navigation symbols}{}{%
    \usebeamerfont{footline}%
    \usebeamercolor[fg]{footline}%
    \hspace{1em}%
    \insertframenumber/\inserttotalframenumber
}

\begin{document}
\begin{frame}
\maketitle
\end{frame}

\begin{frame}
\frametitle{Table of Contents}
\tableofcontents
\end{frame}

\section{Introduction}
\begin{frame}{Introduction and Literature}
   \begin{enumerate}
       \item Eviction is a bigger problem in America than in other rich countries
       \begin{enumerate}
           \item Most poor renting families in America
spend over half of their incomes on rent (Desmond, 2017)
       \end{enumerate}
       \item Sociologists have found large effects of evictions using non-experimental methods
       \begin{enumerate}
           \item Increased probability of job loss (Desmond, Gershenson, 2016)
           \item Increased probability of depression (Desmond, Kimbro, 2015)
       \end{enumerate} 
       \item However, these estimates are likely confounded
       \begin{enumerate}
           \item ``Ashenfelter dip''
           \item Observable and unobservable confounders
       \end{enumerate}
       \item Only recently have economists began to apply quasi-experimental methods to study eviction
        \begin{enumerate}
            \item Van Dijk et al. find effects on durable consumption, access to credit, and more
        \end{enumerate}
   \end{enumerate}
\end{frame}

\section{Motivation}

\begin{frame}{Motivation}
\begin{enumerate}
    \item Strong negative correlation between the presence of eviction and property values
    \item Several potential channels through which eviction might affect property values
    \begin{enumerate}
        \item Evidence suggests that longer tenancy can increase property values
        \item Or, perhaps landlords are evicting problematic tenants
    \end{enumerate}
    \item Either way—property values determine school district 
    funding, so kids' outcomes could be at stake
    \item Ideally, I would have \emph{market} values instead of assessment values
\end{enumerate}
\end{frame}

\section{Data}
\begin{frame}{Data}
    \begin{enumerate}
        \item Eviction data from MassLandlords, a trade association
        \begin{enumerate}
            \item Scraped around 50,000 eviction case records
            \item Collects case outcome data, including method of resolution, judge name, and more
        \end{enumerate}
        \item Assessment values data from the Massachusetts Office of Geographic Information Services
        \begin{enumerate}
            \item Unbalanced panel data on assessor values for nearly every property in Massachussetts
        \end{enumerate}
        \item Link evictions to assessment records on fiscal year and location
    \end{enumerate}
\end{frame}

\begin{frame}{Data}
\begin{table}[H]
    \centering
    \tiny
    \input{output/01_exploratory/tables/summary_statistics.tex}
    \caption{Caption}
    \label{tab:my_label}
\end{table}
\end{frame}

\input{output/01_exploratory/tables/balance_table.tex}

\section{Empirical Strategy}

\begin{frame} [allowframebreaks]\frametitle{References}

        \bibliographystyle{apalike}
        \bibliography{bibfile}
\end{frame}

\end{document}
Close

### 2022-12-20 src/01_build/01_clean_evictions.py
Ran DiD

@@ -1,5 +1,5 @@
 """
-02_clean_evictions.py
+01_clean_evictions.py
 
 Cleans eviction dataset from MassLandlords.
 """
@@ -9,7 +9,6 @@ from src.utilities.dataframe_utilities import batch_df
 
 INPUT_DATA_EVICTIONS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/gather20221121_aug.csv"
 OUTPUT_DATA = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions.csv"
-OUTPUT_DATA_RESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions_restricted.csv"
 GEOCODIO_API_KEY = "060167a66c7587887a81c38077996a71c963638"
 evictions_df = pd.read_csv(INPUT_DATA_EVICTIONS, encoding='unicode_escape')
 original_N = len(evictions_df)
@@ -91,59 +90,3 @@ if VERBOSE:
 if VERBOSE:
     print("Saving unrestricted evictions dataset.")
 evictions_df.to_csv(OUTPUT_DATA, index=False)
-
-"""
-# Restrict to cases where court_person_type is 'judge'
-mask = (evictions_df['court_person_type'] == 'judge')
-print(
-    f"Dropping {(~mask).sum()} observations where court_person_type is not \'judge\' ({100 * ((~mask).sum() / original_N):.3} percent of original dataset).")
-evictions_df = evictions_df.loc[mask, :]
-
-# Drop cases which were resolved via mediation.
-mask = evictions_df['disposition_found'] != "Mediated"
-print(
-    f"Dropping {(~mask).sum()} observations where disposition_found is \'Mediated\' ({100 * (((~mask).sum()) / original_N):.3} percent of original dataset).")
-evictions_df = evictions_df.loc[mask, :]
-
-# Drop cases which were resolved by voluntary dismissal (dropped by plaintiff).
-mask = ~(evictions_df['disposition'].str.contains("R 41(a)(1) Voluntary Dismissal on", regex=False))
-print(
-    f"Dropping {(~mask).sum()} observations resolved through voluntary dismissal ({100 * (((~mask).sum()) / original_N):.3} percent of original dataset).")
-evictions_df = evictions_df.loc[mask, :]
-
-# Drop cases where disposition_found is "Other".
-mask = ~(evictions_df['disposition_found'] == "Other")
-print(
[…]

### 2022-12-20 src/01_build/02_POST_batched_addresses.py

@@ -1,0 +1,26 @@
+"""
+02_POST_batched_addresses.py
+
+Sends POST requests containing batches of addresses.
+"""
+
+import csv
+import os
+import time
+import pandas as pd
+from build_utilities import batch_df
+from zillow_utilities import POST_batch_ZPID_request, to_binary
+
+INPUT_DATA = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions.csv"
+BATCHED_ADDRESSES = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/batched_addresses"
+OUTPUT_DATA = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/job_numbers.csv"
+evictions_df = pd.read_csv(INPUT_DATA)
+
+"""Get ZPIDs for each property."""
+# Save eviction addresses in 100-row batches.
+batched_addresses = batch_df(df=evictions_df['property_address_full'], batch_size=100)
+filepaths = [os.path.join(BATCHED_ADDRESSES, f"batch_{i}.txt") for i, batched_address in enumerate(batched_addresses)]
+[to_binary(filepath=filepath, series=batch, index=False, header=False) for filepath, batch in zip(filepaths, batched_addresses)]
+job_numbers = [POST_batch_ZPID_request(filepath) for filepath in filepaths]
+job_numbers = pd.Series(job_numbers)
+job_numbers.to_csv(OUTPUT_DATA, index=False, header=False)

### 2022-12-20 src/01_build/03_GET_zpids_and_merge.py

@@ -1,0 +1,13 @@
+"""
+03_GET_zpids_and_merge.py
+"""
+import pandas as pd
+from zillow_utilities import GET_processed_ZPIDs
+INPUT_DATA_EVICTIONS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions.csv"
+INPUT_DATA_JOB_NUMBERS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/job_numbers.csv"
+OUTPUT_DATA = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions_with_zpids.csv"
+evictions_df = pd.read_csv(INPUT_DATA_EVICTIONS)
+job_numbers = pd.read_csv(INPUT_DATA_JOB_NUMBERS, header=None)[0]
+addresses_with_zpids = pd.concat([GET_processed_ZPIDs(job_number) for job_number in job_numbers], axis=0).reset_index(drop=True)
+evictions_df = pd.concat([evictions_df, addresses_with_zpids], axis=1)
+evictions_df[['case_number', 'zpid']].to_csv(OUTPUT_DATA, index=False)

### 2022-12-20 src/01_build/03_merge_cross_section.py

@@ -1,155 +1,0 @@
-"""
-03_merge_cross_section.py
-
-Merge eviction data with assessment values.
-"""
-import pandas as pd
-import geopandas as gpd
-
-
-INPUT_DATA_EVICTIONS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions.csv"
-INPUT_DATA_TAX_PARCELS_EAST = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/Statewide_parcels_SHP/L3_TAXPAR_POLY_ASSESS_EAST.shp"
-INPUT_DATA_TAX_PARCELS_WEST = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/Statewide_parcels_SHP/L3_TAXPAR_POLY_ASSESS_WEST.shp"
-INPUT_DATA_ASSESSMENT_VALUES = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/assessor_values.csv"
-OUTPUT_DATA_UNRESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/cross_section_unrestricted.csv"
-OUTPUT_DATA_RESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/cross_section_restricted.csv"
-VERBOSE = True
-
-# Load evictions data.
-evictions_df = pd.read_csv(INPUT_DATA_EVICTIONS)
-evictions_gdf = gpd.GeoDataFrame(evictions_df, geometry=gpd.points_from_xy(evictions_df['longitude'], evictions_df['latitude']))
-evictions_gdf = evictions_gdf.set_crs("EPSG:4326")  # crs attribute is currently unassigned.
-
-# Load tax parcel files.
-tax_parcel_columns_to_keep = ['MAP_PAR_ID', 'LOC_ID', 'POLY_TYPE', 'SITE_ADDR', 'CITY', 'ZIP', 'SHAPE_Leng', 'SHAPE_Area',
-                              'geometry']
-tax_parcels_gdf = pd.concat([gpd.read_file(INPUT_DATA_TAX_PARCELS_EAST)[tax_parcel_columns_to_keep],
[…]

### 2022-12-20 src/01_build/04_GET_zillow_data.py

@@ -1,0 +1,26 @@
+"""
+04_GET_zillow_data.py
+"""
+import pandas as pd
+from zillow_utilities import GET_zestimate_history
+INPUT_DATA = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions_with_zpids.csv"
+OUTPUT_DATA = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/zestimates.csv"
+
+# Get Zestimates and concatenate into a single DataFrame.
+zpids_df = pd.read_csv(INPUT_DATA, dtype={'zpid': str}).dropna()
+zestimates_df = pd.concat([GET_zestimate_history(zpid, case_number) for zpid, case_number in zip(zpids_df['zpid'], zpids_df['case_number'])], axis=0)
+zestimates_df = zestimates_df.reset_index()
+
+# Produce month and year columns.
+zestimates_df.loc[:, 'time'] = pd.to_datetime(zestimates_df['time'], unit='s')
+zestimates_df.loc[:, 'month_year'] = zestimates_df['time'].dt.to_period('M')
+zestimates_df = zestimates_df.drop(columns='time')
+
+# Average Zestimates to the month-case level.
+zestimates_df = zestimates_df.groupby(by=['case_number', 'month_year']).mean().reset_index()
+
+# Reshape from long to wide.
+zestimates_df = pd.pivot(zestimates_df, index=['case_number'], columns=['month_year'], values='zestimate')
+
+# Save to CSV.
+zestimates_df.to_csv(OUTPUT_DATA)

### 2022-12-20 src/01_build/06_merge.py

@@ -1,9 +1,8 @@
 """
-03_merge_cross_section.py
+06_merge.py
 
-Merge eviction data with assessment values, producing a panel dataset..
+Merge eviction data with assessment values.
 """
-import numpy as np
 import pandas as pd
 import geopandas as gpd
 
@@ -11,9 +10,10 @@ import geopandas as gpd
 INPUT_DATA_EVICTIONS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions.csv"
 INPUT_DATA_TAX_PARCELS_EAST = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/Statewide_parcels_SHP/L3_TAXPAR_POLY_ASSESS_EAST.shp"
 INPUT_DATA_TAX_PARCELS_WEST = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/Statewide_parcels_SHP/L3_TAXPAR_POLY_ASSESS_WEST.shp"
+INPUT_DATA_ZESTIMATES = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/zestimates.csv"
 INPUT_DATA_ASSESSMENT_VALUES = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/assessor_values.csv"
-OUTPUT_DATA_UNRESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/panel_unrestricted.csv"
-OUTPUT_DATA_RESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/panel_restricted.csv"
+OUTPUT_DATA_UNRESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/unrestricted.csv"
+OUTPUT_DATA_RESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/restricted.csv"
 VERBOSE = True
 
 # Load evictions data.
@@ -37,24 +37,28 @@ if VERBOSE:
     print(f"Successfully matched {successfully_matched_observations} evictions ({successfully_matched_observations / len(evictions_gdf)}"
           f" percent of observations) to parcels.")
 
+tax_parcels_gdf.loc[:, 'file_month'] = pd.to_datetime(tax_parcels_gdf['file_date']).dt.month
[…]

### 2022-12-20 src/01_build/scratch.py

@@ -1,0 +1,4 @@
+import pandas as pd
+from zillow_utilities import GET_zestimate_history
+df = GET_zestimate_history(81826510, "1")
+print(df)

### 2022-12-20 src/01_build/zillow_utilities.py

@@ -1,0 +1,131 @@
+"""
+zillow_utilities.py
+
+Defines useful functions for pulling data from Zillow.
+"""
+import time
+import json
+from io import StringIO
+from typing import List
+import pandas as pd
+import requests
+from googlesearch import search
+
+API_KEY = "91ac630dccmshb123beb8366a49ap124b4djsn4bdf0c892172"
+
+
+def GET_zestimate_history(zpid: int, case_number: str):
+    """
+    :param zpid: The Zillow property ID for which we want to fetch zestimates.
+    :return: A DataFrame containing the past Zestimates associated with the provided ZPID.
+    """
+    import requests
+    # Obey call frequency limits.
+    time.sleep(0.34)
+    print(f"Getting Zestimates for ZPID: {zpid}")
+    url = "https://zillow-com1.p.rapidapi.com/zestimateHistory"
+
+    querystring = {"zpid": str(zpid)}
+
+    headers = {
+        "X-RapidAPI-Key": "251c7df1e1msha0e9511aa2bea51p144754jsna6dcc56ce15d",
+        "X-RapidAPI-Host": "zillow-com1.p.rapidapi.com"
+    }
+
+    response = requests.request("GET", url, headers=headers, params=querystring)
+    df = pd.DataFrame.from_dict(json.loads(response.text)).rename(columns={'t': 'time', 'v': 'zestimate'})
+    if df.empty:
+        print(f"Could not get Zestimates for ZPID: {zpid}")
+    else:
+        print(f"Successfully got Zestimates for ZPID: {zpid}")
+        df.loc[:, 'case_number'] = case_number
+    return df
+
+def get_zillow_url(property_address: str, master_list: List):
+    """
+    Finds the URL of a specified property's page on Zillow.
+    :param master_list:
+    :param property_address: The address of the property.
+    :return:
+    """
+    # Avoid 429 error from Google.
+    time.sleep(.5)
+
+    # Get the URL of the first search result.
+    result = search(f"zillow {property_address}", num_results=1)
+    first_url = next(result)
+
+    # Return the URL if it appears to the Zillow URL of the requested property
+    print(first_url)
+    if first_url.startswith("https://www.zillow.com/homedetails/"):
+        print(f"Found Zillow URL for {property_address}.")
+        master_list.append((property_address, first_url))
+    else:
+        print(f"Unable to find Zillow URL for {property_address}.")
+        master_list.append((property_address, "Unable to find Zillow URL."))
+
+
[…]

### 2022-12-20 src/05_merge_panel.py

@@ -1,0 +1,68 @@
+"""
+05_merge_panel.py
+"""
+import pandas as pd
+
+INPUT_DATA_ZESTIMATES = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/zestimates.csv"
+INPUT_DATA_EVICTIONS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions.csv"
+OUTPUT_DATA_UNRESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/zillow_panel_unrestricted.csv"
+OUTPUT_DATA_RESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/zillow_panel_restricted.csv"
+
+zestimates_df = pd.read_csv(INPUT_DATA_ZESTIMATES)
+evictions_df = pd.read_csv(INPUT_DATA_EVICTIONS)
+merged_df = zestimates_df.merge(evictions_df, on='case_number', how='inner', validate='1:1')
+
+merged_df.loc[:, 'file_year'] = pd.to_datetime(merged_df['file_date']).dt.year
+merged_df.to_csv(OUTPUT_DATA_UNRESTRICTED)
+
+original_N = len(merged_df)
+
+
+# Drop cases which were resolved via mediation.
+mask = (merged_df['disposition_found'] != "Mediated")
+print(
+    f"Dropping {(~mask).sum()} observations where disposition_found is \'Mediated\' ({100 * (((~mask).sum()) / original_N):.3} percent of original dataset).")
+merged_df = merged_df.loc[mask, :]
+
+# Drop cases which were resolved by voluntary dismissal (dropped by plaintiff).
+mask = ~(merged_df['disposition'].str.contains("R 41(a)(1) Voluntary Dismissal on", na=False, regex=False))
+print(
+    f"Dropping {(~mask).sum()} observations resolved through voluntary dismissal ({100 * (((~mask).sum()) / original_N):.3} percent of original dataset).")
+merged_df = merged_df.loc[mask, :]
+
+# Drop cases where disposition_found is "Other".
+mask = ~(merged_df['disposition_found'] == "Other")
+print(
+    f"Dropping {(~mask).sum()} observations where disposition_found is \'Other\' ({100 * (((~mask).sum()) / original_N):.3} percent of original dataset).")
[…]

### 2022-12-23 writing/presentations/december_7.tex
Updates from Overleaf

@@
 
-\institute[]{Department of Earth, Environmental, and Planetary Sciences  \\Brown University}
-
 \author[Arjun Shanmugam]{}
+\setbeamertemplate{navigation symbols}{}
 
@@
     \input{output/01_exploratory/tables/summary_statistics.tex}
-    \caption{Caption}
     \label{tab:my_label}
@@
 
+\begin{frame}{Data}
+\begin{table}[H]
+    \centering
+    \tiny
     \input{output/01_exploratory/tables/balance_table.tex}
+    \label{tab:my_label}
+\end{table}
+\end{frame}
 
 \section{Empirical Strategy}
+\begin{frame}{Empirical Strategy}
+    \begin{enumerate}
+        \item Most eviction cases in Massachusetts are filed in the Massachusetts Housing Court
+        \item Within the Housing Court, cases are assigned to about 15 judges quasi-randomly conditional on city and time
+        \item This is the basis for an examiner design study, which uses judge dummies as instruments
+    \end{enumerate}
+\end{frame}
 
-\begin{frame} [allowframebreaks]\frametitle{References}
+\begin{frame}{Empirical Strategy}
+\begin{table}[H]
+    \centering
+    \tiny
+    \input{output/01_exploratory/tables/placebo_first_stage.tex}
+    \label{tab:my_label}
+\end{table}    
+\end{frame}
 
-        \bibliographystyle{apalike}
-        \bibliography{bibfile}
+\begin{frame}{Preliminary Results}
+    \begin{table}[H]
+        \centering
+        \tiny
+        \input{output/01_exploratory/tables/ln_total_val_results_table.tex}
+        \label{tab:my_label}
+    \end{table}
+\end{frame}
+\begin{frame}{Preliminary Results}
+    \begin{table}[H]
+        \centering
+        \tiny
+        \input{output/01_exploratory/tables/ln_bldg_val_results_table.tex}
+        \label{tab:my_label}
+    \end{table}
+\end{frame}
+
+\begin{frame}{Next Steps}
+    \begin{enumerate}
+        \item Figure out what to do about my lack of power
+        \item Find a systematic way to drop observations in sparse city-years
+        \item Speak to an assessor from Massachusetts to understand whether there is even a mechanism through which I might see an effect
+        \item Think about whether my instrument is truly valid
+    \end{enumerate}
 \end{frame}

### 2022-12-23 writing/paper/main.tex

--- 2022-12-02 writing/main.tex
@@
-\documentclass{article}
-\usepackage{graphicx, setspace, booktabs, float, xcolor, rotating, lscape, lscape, sectsty, rotating}
-\usepackage[utf8]{inputenc}
-\usepackage[letterpaper, portrait, margin=0.8in]{geometry}
-\usepackage[shortlabels]{enumitem}
-\usepackage[round, sort]{natbib}
+\documentclass[12pt]{article}
+
+\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,natbib,pdflscape,subfigure,array,hyperref}
+
+\normalem
+
+\onehalfspacing
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{proposition}{Proposition}
+\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
+
+\newtheorem{hyp}{Hypothesis}
+\newtheorem{subhyp}{Hypothesis}[hyp]
+\renewcommand{\thesubhyp}{\thehyp\alph{subhyp}}
+
+\newcommand{\red}[1]{{\color{red} #1}}
+\newcommand{\blue}[1]{{\color{blue} #1}}
+
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
+\newcolumntype{C}[1]{>{\centering\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
+\newcolumntype{R}[1]{>{\raggedleft\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
+
+\geometry{left=1.0in,right=1.0in,top=1.0in,bottom=1.0in}
+
+\begin{document}
+
+\begin{titlepage}
+\title{Arjun Shanmugam's Senior Thesis}
+\author{Arjun Shanmugam}
+\date{\today}
+\maketitle
+\begin{abstract}
+\noindent Placeholder\\
+
+\bigskip
+\end{abstract}
+\setcounter{page}{0}
+\thispagestyle{empty}
+\end{titlepage}
+\pagebreak \newpage
 
@@
 
-\title{Thesis Updates}
-\author{Arjun}
-\date{December 2, 2022}
+\section{Introduction} \label{sec:introduction}
 
-\begin{document}
-\input{output/01_exploratory/tables/summary_statistics.tex}
+\section{Literature Review} \label{sec:literature}
 
-\input{}
+\section{Data} \label{sec:data}
+    \subsection{Evictions Data}
+    \subsection{Tax Assessment Records}
+    \subsection{Zestimates}
+    \subsection{Summary Statistics}
+        \begin{table}[]
+            \centering
+            \begin{tabular}{c|c}
+                 &  \\
+                 & 
+            \end{tabular}
+            \caption{Caption}
+            \label{tab:my_label}
+        \end{table}
+
+\section{Results} \label{sec:result}
+
+\section{Discussions} \label{sec:discussion}
+
+\section{Conclusion} \label{sec:conclusion}
+
+\singlespacing
+\setlength\bibsep{0pt}
+\bibliographystyle{my-style}
+\bibliography{Placeholder}
+
+\clearpage
+
+\onehalfspacing
+
+\section*{Tables} \label{sec:tab}
+\addcontentsline{toc}{section}{Tables}
+
+\clearpage
+
+\section*{Figures} \label{sec:fig}
+\addcontentsline{toc}{section}{Figures}
+
+\clearpage
+
+\section*{Appendix A. Placeholder} \label{sec:appendixa}
+\addcontentsline{toc}{section}{Appendix A}
 

### 2022-12-23 output/summary_statistics/tables/summary_statistics.tex
Fixed unrestricted summ stats table bug

\begin{tabular}{llrrr}
\toprule
 &  & Mean & S.D. & N \\
\midrule
\multirow[c]{8}{*}{Panel A: Case Initiation} & for_cause & 0.13 & 0.33 & 30, 505 \\
 & for_cause_transfer & 0.01 & 0.09 & 30, 505 \\
 & foreclosure & 0.02 & 0.15 & 30, 505 \\
 & foreclosure_transfer & 0.00 & 0.03 & 30, 505 \\
 & no_cause & 0.11 & 0.31 & 30, 505 \\
 & no_cause_transfer & 0.01 & 0.08 & 30, 505 \\
 & non_payment & 0.71 & 0.46 & 30, 505 \\
 & non_payment_transfer & 0.02 & 0.13 & 30, 505 \\
\multirow[c]{5}{*}{Panel B: Case Resolution} & defaulted & 0.24 & 0.43 & 30, 505 \\
 & dismissed & 0.12 & 0.33 & 30, 505 \\
 & heard & 0.07 & 0.26 & 30, 505 \\
 & mediated & 0.52 & 0.50 & 30, 505 \\
 & voluntary_dismissal & 0.00 & 0.00 & 30, 505 \\
\multirow[c]{5}{*}{Panel C: Defendant and Plaintiff Characteristics} & hasAttyD & 0.10 & 0.30 & 30, 505 \\
 & hasAttyP & 0.82 & 0.39 & 30, 505 \\
 & isEntityD & 0.01 & 0.08 & 30, 505 \\
 & isEntityP & 0.66 & 0.47 & 30, 505 \\
 & judgment & 4706.79 & 7661.71 & 15, 588 \\
\multirow[c]{5}{*}{Panel C: Tax Assessment Records from F.Y. Following Eviction Filing} & BLDG_VAL & 7731082.50 & 18211631.86 & 12, 089 \\
 & LAND_VAL & 2007807.90 & 5532224.22 & 12, 089 \\
 & OTHER_VAL & 99020.63 & 539763.97 & 12, 089 \\
 & TOTAL_VAL & 9827333.04 & 22977540.22 & 12, 089 \\
 & UNITS & 39.15 & 113.83 & 12, 089 \\
\multirow[c]{9}{*}{Panel E: Zestimates Around Treatment} & zestimate_-1_years_relative_to_treatment & 352784.42 & 300314.15 & 6, 992 \\
 & zestimate_-2_years_relative_to_treatment & 344030.70 & 1167207.98 & 6, 966 \\
 & zestimate_-3_years_relative_to_treatment & 305906.07 & 337719.48 & 6, 950 \\
 & zestimate_-4_years_relative_to_treatment & 283010.66 & 265189.42 & 6, 848 \\
 & zestimate_-5_years_relative_to_treatment & 263662.99 & 223748.00 & 6, 766 \\
 & zestimate_0_years_relative_to_treatment & 395691.50 & 416306.93 & 7, 045 \\
 & zestimate_1_years_relative_to_treatment & 435193.84 & 476324.79 & 6, 943 \\
 & zestimate_2_years_relative_to_treatment & 474304.25 & 446024.13 & 4, 910 \\
 & zestimate_3_years_relative_to_treatment & 507403.55 & 1140138.35 & 2, 680 \\
\bottomrule
\end{tabular}

### 2022-12-23 writing/paper/main.tex

@@
 
-\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,natbib,pdflscape,subfigure,array,hyperref}
+\usepackage{amssymb,amsmath,amsfonts,booktabs,eurosym,float,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,natbib,pdflscape,subfigure,array,hyperref}
 
@@
     \subsection{Summary Statistics}
-        \begin{table}[]
+        \begin{table}[H]
             \centering
-            \begin{tabular}{c|c}
-                 &  \\
-                 & 
-            \end{tabular}
+            \input{output/summary_statistics/tables/summary_statistics.tex}
             \caption{Caption}

### 2022-12-23 output/summary_statistics/tables/summary_statistics.tex
Fixed unrestricted summ stats table bug

@@
 \midrule
-\multirow[c]{8}{*}{Panel A: Case Initiation} & for_cause & 0.13 & 0.33 & 30, 505 \\
- & for_cause_transfer & 0.01 & 0.09 & 30, 505 \\
- & foreclosure & 0.02 & 0.15 & 30, 505 \\
- & foreclosure_transfer & 0.00 & 0.03 & 30, 505 \\
- & no_cause & 0.11 & 0.31 & 30, 505 \\
- & no_cause_transfer & 0.01 & 0.08 & 30, 505 \\
- & non_payment & 0.71 & 0.46 & 30, 505 \\
- & non_payment_transfer & 0.02 & 0.13 & 30, 505 \\
-\multirow[c]{5}{*}{Panel B: Case Resolution} & defaulted & 0.24 & 0.43 & 30, 505 \\
- & dismissed & 0.12 & 0.33 & 30, 505 \\
- & heard & 0.07 & 0.26 & 30, 505 \\
- & mediated & 0.52 & 0.50 & 30, 505 \\
- & voluntary_dismissal & 0.00 & 0.00 & 30, 505 \\
-\multirow[c]{5}{*}{Panel C: Defendant and Plaintiff Characteristics} & hasAttyD & 0.10 & 0.30 & 30, 505 \\
- & hasAttyP & 0.82 & 0.39 & 30, 505 \\
- & isEntityD & 0.01 & 0.08 & 30, 505 \\
- & isEntityP & 0.66 & 0.47 & 30, 505 \\
- & judgment & 4706.79 & 7661.71 & 15, 588 \\
-\multirow[c]{5}{*}{Panel C: Tax Assessment Records from F.Y. Following Eviction Filing} & BLDG_VAL & 7731082.50 & 18211631.86 & 12, 089 \\
- & LAND_VAL & 2007807.90 & 5532224.22 & 12, 089 \\
- & OTHER_VAL & 99020.63 & 539763.97 & 12, 089 \\
- & TOTAL_VAL & 9827333.04 & 22977540.22 & 12, 089 \\
- & UNITS & 39.15 & 113.83 & 12, 089 \\
-\multirow[c]{9}{*}{Panel E: Zestimates Around Treatment} & zestimate_-1_years_relative_to_treatment & 352784.42 & 300314.15 & 6, 992 \\
- & zestimate_-2_years_relative_to_treatment & 344030.70 & 1167207.98 & 6, 966 \\
- & zestimate_-3_years_relative_to_treatment & 305906.07 & 337719.48 & 6, 950 \\
- & zestimate_-4_years_relative_to_treatment & 283010.66 & 265189.42 & 6, 848 \\
- & zestimate_-5_years_relative_to_treatment & 263662.99 & 223748.00 & 6, 766 \\
- & zestimate_0_years_relative_to_treatment & 395691.50 & 416306.93 & 7, 045 \\
- & zestimate_1_years_relative_to_treatment & 435193.84 & 476324.79 & 6, 943 \\
- & zestimate_2_years_relative_to_treatment & 474304.25 & 446024.13 & 4, 910 \\
- & zestimate_3_years_relative_to_treatment & 507403.55 & 1140138.35 & 2, 680 \\
+\multirow[c]{8}{*}{Panel A: Case Initiation} & For cause & 0.13 & 0.33 & 30, 505 \\
+ & For cause; transferred from B.M.C. or D.C. & 0.01 & 0.09 & 30, 505 \\
+ & Foreclosure & 0.02 & 0.15 & 30, 505 \\
+ & Foreclosure; transferred from B.M.C. or D.C. & 0.00 & 0.03 & 30, 505 \\
+ & No cause & 0.11 & 0.31 & 30, 505 \\
+ & No cause; transferred from B.M.C. or D.C. & 0.01 & 0.08 & 30, 505 \\
+ & Non-payment of rent & 0.71 & 0.46 & 30, 505 \\
+ & Non-payment of rent; transferred from B.M.C. or D.C. & 0.02 & 0.13 & 30, 505 \\
+\multirow[c]{5}{*}{Panel B: Case Resolution} & Case defaulted & 0.24 & 0.43 & 30, 505 \\
+ & Case heard & 0.07 & 0.26 & 30, 505 \\
+ & Case involuntarily dismissed & 0.12 & 0.33 & 30, 505 \\
+ & Case mediated & 0.52 & 0.50 & 30, 505 \\
+ & Case voluntarily dismissed & 0.00 & 0.00 & 30, 505 \\
+\multirow[c]{5}{*}{Panel C: Defendant and Plaintiff Characteristics} & Defendant has an attorney & 0.10 & 0.30 & 30, 505 \\
+ & Defendant is an entity & 0.01 & 0.08 & 30, 505 \\
+ & Money judgment & 4706.79 & 7661.71 & 15, 588 \\
+ & Plaintiff has an attorney & 0.82 & 0.39 & 30, 505 \\
+ & Plaintiff is an entity & 0.66 & 0.47 & 30, 505 \\
+\multirow[c]{5}{*}{Panel C: Tax Assessment Records from F.Y. Following Eviction Filing} & Building value & 2007807.90 & 5532224.22 & 12, 089 \\
+ & Land value & 99020.63 & 539763.97 & 12, 089 \\
+ & Other value & 9827333.04 & 22977540.22 & 12, 089 \\
+ & Total property value & 7731082.50 & 18211631.86 & 12, 089 \\
+ & Total value & 39.15 & 113.83 & 12, 089 \\
+\multirow[c]{9}{*}{Panel E: Zestimates Around Treatment} & Five years before latest docket date & 283010.66 & 265189.42 & 6, 848 \\
+ & Four years before latest docket date & 305906.07 & 337719.48 & 6, 950 \\
+ & Latest docket date & 435193.84 & 476324.79 & 6, 943 \\
+ & One year after latest docket date & 474304.25 & 446024.13 & 4, 910 \\
+ & One year before latest docket date & 395691.50 & 416306.93 & 7, 045 \\
+ & Three years before latest docket date & 344030.70 & 1167207.98 & 6, 966 \\
+ & Two years after latest docket date & 507403.55 & 1140138.35 & 2, 680 \\
+ & Two years before latest docket date & 352784.42 & 300314.15 & 6, 992 \\
+ & Units & 263662.99 & 223748.00 & 6, 766 \\
 \bottomrule

### 2022-12-23 writing/paper/main.tex

@@
 
-\usepackage{amssymb,amsmath,amsfonts,booktabs,eurosym,float,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,natbib,pdflscape,subfigure,array,hyperref}
+\usepackage{amssymb,amsmath,amsfonts,booktabs,eurosym,float,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,multicol, multirow,natbib,pdflscape,subfigure,array,hyperref, pdflscape}
 
@@
     \subsection{Summary Statistics}
+    \begin{landscape}
          \begin{table}[H]
@@
         \end{table}
+
+    \end{landscape}
 

### 2022-12-23 output/summary_statistics/tables/summary_statistics.tex
Fixed unrestricted summ stats table bug

@@
 \midrule
-\multirow[c]{8}{*}{Panel A: Case Initiation} & For cause & 0.13 & 0.33 & 30, 505 \\
+\multirow[c]{8}{*}{\textit{Panel A: Case Initiation}} & For cause & 0.13 & 0.33 & 30, 505 \\
  & For cause; transferred from B.M.C. or D.C. & 0.01 & 0.09 & 30, 505 \\
@@
  & Non-payment of rent; transferred from B.M.C. or D.C. & 0.02 & 0.13 & 30, 505 \\
-\multirow[c]{5}{*}{Panel B: Case Resolution} & Case defaulted & 0.24 & 0.43 & 30, 505 \\
+\cline{1-5}
+\multirow[c]{5}{*}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.24 & 0.43 & 30, 505 \\
  & Case heard & 0.07 & 0.26 & 30, 505 \\
@@
  & Case voluntarily dismissed & 0.00 & 0.00 & 30, 505 \\
-\multirow[c]{5}{*}{Panel C: Defendant and Plaintiff Characteristics} & Defendant has an attorney & 0.10 & 0.30 & 30, 505 \\
+\cline{1-5}
+\multirow[c]{5}{*}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Building value & 2007807.90 & 5532224.22 & 12, 089 \\
+ & Land value & 99020.63 & 539763.97 & 12, 089 \\
+ & Other value & 9827333.04 & 22977540.22 & 12, 089 \\
+ & Total property value & 7731082.50 & 18211631.86 & 12, 089 \\
+ & Total value & 39.15 & 113.83 & 12, 089 \\
+\cline{1-5}
+\multirow[c]{5}{*}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.10 & 0.30 & 30, 505 \\
  & Defendant is an entity & 0.01 & 0.08 & 30, 505 \\
@@
  & Plaintiff is an entity & 0.66 & 0.47 & 30, 505 \\
-\multirow[c]{5}{*}{Panel C: Tax Assessment Records from F.Y. Following Eviction Filing} & Building value & 2007807.90 & 5532224.22 & 12, 089 \\
- & Land value & 99020.63 & 539763.97 & 12, 089 \\
- & Other value & 9827333.04 & 22977540.22 & 12, 089 \\
- & Total property value & 7731082.50 & 18211631.86 & 12, 089 \\
- & Total value & 39.15 & 113.83 & 12, 089 \\
-\multirow[c]{9}{*}{Panel E: Zestimates Around Treatment} & Five years before latest docket date & 283010.66 & 265189.42 & 6, 848 \\
+\cline{1-5}
+\multirow[c]{9}{*}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 283010.66 & 265189.42 & 6, 848 \\
  & Four years before latest docket date & 305906.07 & 337719.48 & 6, 950 \\
@@
  & Units & 263662.99 & 223748.00 & 6, 766 \\
+\cline{1-5}
 \bottomrule

### 2022-12-23 output/summary_statistics/tables/summary_statistics.tex
Fixed unrestricted summ stats table bug

--- 2022-12-23 output/summary_statistics/tables/summary_statistics.tex
@@
  &  & Mean & S.D. & N \\
+Panel & Variable &  &  &  \\
 \midrule
-\multirow[c]{8}{*}{Panel A: Case Initiation} & for_cause & 0.13 & 0.33 & 30, 505 \\
- & for_cause_transfer & 0.01 & 0.09 & 30, 505 \\
- & foreclosure & 0.02 & 0.15 & 30, 505 \\
- & foreclosure_transfer & 0.00 & 0.03 & 30, 505 \\
- & no_cause & 0.11 & 0.31 & 30, 505 \\
- & no_cause_transfer & 0.01 & 0.08 & 30, 505 \\
- & non_payment & 0.71 & 0.46 & 30, 505 \\
- & non_payment_transfer & 0.02 & 0.13 & 30, 505 \\
-\multirow[c]{5}{*}{Panel B: Case Resolution} & defaulted & 0.24 & 0.43 & 30, 505 \\
- & dismissed & 0.12 & 0.33 & 30, 505 \\
- & heard & 0.07 & 0.26 & 30, 505 \\
- & mediated & 0.52 & 0.50 & 30, 505 \\
- & voluntary_dismissal & 0.00 & 0.00 & 30, 505 \\
-\multirow[c]{5}{*}{Panel C: Defendant and Plaintiff Characteristics} & hasAttyD & 0.10 & 0.30 & 30, 505 \\
- & hasAttyP & 0.82 & 0.39 & 30, 505 \\
- & isEntityD & 0.01 & 0.08 & 30, 505 \\
- & isEntityP & 0.66 & 0.47 & 30, 505 \\
- & judgment & 4706.79 & 7661.71 & 15, 588 \\
-\multirow[c]{5}{*}{Panel C: Tax Assessment Records from F.Y. Following Eviction Filing} & BLDG_VAL & 7731082.50 & 18211631.86 & 12, 089 \\
- & LAND_VAL & 2007807.90 & 5532224.22 & 12, 089 \\
- & OTHER_VAL & 99020.63 & 539763.97 & 12, 089 \\
- & TOTAL_VAL & 9827333.04 & 22977540.22 & 12, 089 \\
- & UNITS & 39.15 & 113.83 & 12, 089 \\
-\multirow[c]{9}{*}{Panel E: Zestimates Around Treatment} & zestimate_-1_years_relative_to_treatment & 352784.42 & 300314.15 & 6, 992 \\
- & zestimate_-2_years_relative_to_treatment & 344030.70 & 1167207.98 & 6, 966 \\
- & zestimate_-3_years_relative_to_treatment & 305906.07 & 337719.48 & 6, 950 \\
- & zestimate_-4_years_relative_to_treatment & 283010.66 & 265189.42 & 6, 848 \\
- & zestimate_-5_years_relative_to_treatment & 263662.99 & 223748.00 & 6, 766 \\
- & zestimate_0_years_relative_to_treatment & 395691.50 & 416306.93 & 7, 045 \\
- & zestimate_1_years_relative_to_treatment & 435193.84 & 476324.79 & 6, 943 \\
- & zestimate_2_years_relative_to_treatment & 474304.25 & 446024.13 & 4, 910 \\
- & zestimate_3_years_relative_to_treatment & 507403.55 & 1140138.35 & 2, 680 \\
+\multirow[c]{8}{*}{\textit{Panel A: Case Initiation}} & For cause & 0.13 & 0.33 & 30,505 \\
+ & For cause; transferred from B.M.C. or D.C. & 0.01 & 0.09 & 30,505 \\
+ & Foreclosure & 0.02 & 0.15 & 30,505 \\
+ & Foreclosure; transferred from B.M.C. or D.C. & 0.00 & 0.03 & 30,505 \\
+ & No cause & 0.11 & 0.31 & 30,505 \\
+ & No cause; transferred from B.M.C. or D.C. & 0.01 & 0.08 & 30,505 \\
+ & Non-payment of rent & 0.71 & 0.46 & 30,505 \\
+ & Non-payment of rent; transferred from B.M.C. or D.C. & 0.02 & 0.13 & 30,505 \\
+\cline{1-5}
+\multirow[c]{5}{*}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.24 & 0.43 & 30,505 \\
+ & Case involuntarily dismissed & 0.12 & 0.33 & 30,505 \\
+ & Case heard & 0.07 & 0.26 & 30,505 \\
+ & Case mediated & 0.52 & 0.50 & 30,505 \\
+ & Case voluntarily dismissed & 0.00 & 0.00 & 30,505 \\
+\cline{1-5}
+\multirow[c]{5}{*}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.10 & 0.30 & 30,505 \\
+ & Plaintiff has an attorney & 0.82 & 0.39 & 30,505 \\
+ & Defendant is an entity & 0.01 & 0.08 & 30,505 \\
+ & Plaintiff is an entity & 0.66 & 0.47 & 30,505 \\
+ & Money judgment & 4706.79 & 7661.71 & 15,588 \\
+\cline{1-5}
+\multirow[c]{5}{*}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 7731082.50 & 18211631.86 & 12,089 \\
+ & Building value & 2007807.90 & 5532224.22 & 12,089 \\
+ & Land value & 99020.63 & 539763.97 & 12,089 \\
+ & Other value & 9827333.04 & 22977540.22 & 12,089 \\
+ & Total value & 39.15 & 113.83 & 12,089 \\
+\cline{1-5}
+\multirow[c]{9}{*}{\textit{Panel E: Zestimates Around Treatment}} & Units & 263662.99 & 223748.00 & 6,766 \\
+ & Five years before latest docket date & 283010.66 & 265189.42 & 6,848 \\
+ & Four years before latest docket date & 305906.07 & 337719.48 & 6,950 \\
+ & Three years before latest docket date & 344030.70 & 1167207.98 & 6,966 \\
+ & Two years before latest docket date & 352784.42 & 300314.15 & 6,992 \\
+ & One year before latest docket date & 395691.50 & 416306.93 & 7,045 \\
+ & Latest docket date & 435193.84 & 476324.79 & 6,943 \\
+ & One year after latest docket date & 474304.25 & 446024.13 & 4,910 \\
+ & Two years after latest docket date & 507403.55 & 1140138.35 & 2,680 \\
+\cline{1-5}
 \bottomrule

### 2022-12-23 output/summary_statistics/tables/summary_statistics.tex
Fixed unrestricted summ stats table bug

@@
  & Plaintiff is an entity & 0.66 & 0.47 & 30,505 \\
- & Money judgment & 4706.79 & 7661.71 & 15,588 \\
+ & Money judgment & 2405.16 & 5960.84 & 30,505 \\
 \cline{1-5}
@@
  & Other value & 9827333.04 & 22977540.22 & 12,089 \\
- & Total value & 39.15 & 113.83 & 12,089 \\
+ & Units & 39.15 & 113.83 & 12,089 \\
 \cline{1-5}
-\multirow[c]{9}{*}{\textit{Panel E: Zestimates Around Treatment}} & Units & 263662.99 & 223748.00 & 6,766 \\
- & Five years before latest docket date & 283010.66 & 265189.42 & 6,848 \\
- & Four years before latest docket date & 305906.07 & 337719.48 & 6,950 \\
- & Three years before latest docket date & 344030.70 & 1167207.98 & 6,966 \\
- & Two years before latest docket date & 352784.42 & 300314.15 & 6,992 \\
- & One year before latest docket date & 395691.50 & 416306.93 & 7,045 \\
- & Latest docket date & 435193.84 & 476324.79 & 6,943 \\
- & One year after latest docket date & 474304.25 & 446024.13 & 4,910 \\
- & Two years after latest docket date & 507403.55 & 1140138.35 & 2,680 \\
+\multirow[c]{9}{*}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 263662.99 & 223748.00 & 6,766 \\
+ & Four years before latest docket date & 283010.66 & 265189.42 & 6,848 \\
+ & Three years before latest docket date & 305906.07 & 337719.48 & 6,950 \\
+ & Two years before latest docket date & 344030.70 & 1167207.98 & 6,966 \\
+ & One year before latest docket date & 352784.42 & 300314.15 & 6,992 \\
+ & Latest docket date & 395691.50 & 416306.93 & 7,045 \\
+ & One year after latest docket date & 435193.84 & 476324.79 & 6,943 \\
+ & Two years after latest docket date & 474304.25 & 446024.13 & 4,910 \\
+ & Three years after latest docket date & 507403.55 & 1140138.35 & 2,680 \\
 \cline{1-5}

### 2022-12-23 output/summary_statistics/tables/summary_statistics.tex
Fixed unrestricted summ stats table bug

@@
 \multirow[c]{8}{*}{\textit{Panel A: Case Initiation}} & For cause & 0.13 & 0.33 & 30,505 \\
- & For cause; transferred from B.M.C. or D.C. & 0.01 & 0.09 & 30,505 \\
+ & For cause (transfer) & 0.01 & 0.09 & 30,505 \\
  & Foreclosure & 0.02 & 0.15 & 30,505 \\
- & Foreclosure; transferred from B.M.C. or D.C. & 0.00 & 0.03 & 30,505 \\
+ & Foreclosure (transfer) & 0.00 & 0.03 & 30,505 \\
  & No cause & 0.11 & 0.31 & 30,505 \\
- & No cause; transferred from B.M.C. or D.C. & 0.01 & 0.08 & 30,505 \\
+ & No cause (transfer) & 0.01 & 0.08 & 30,505 \\
  & Non-payment of rent & 0.71 & 0.46 & 30,505 \\
- & Non-payment of rent; transferred from B.M.C. or D.C. & 0.02 & 0.13 & 30,505 \\
+ & Non-payment of rent (transfer) & 0.02 & 0.13 & 30,505 \\
 \cline{1-5}

### 2022-12-23 output/summary_statistics/tables/summary_statistics.tex
Fixed unrestricted summ stats table bug

@@
 \midrule
-\multirow[c]{8}{*}{\textit{Panel A: Case Initiation}} & For cause & 0.13 & 0.33 & 30,505 \\
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.13 & 0.33 & 30,505 \\
  & For cause (transfer) & 0.01 & 0.09 & 30,505 \\
@@
 \cline{1-5}
-\multirow[c]{5}{*}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.24 & 0.43 & 30,505 \\
+\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.24 & 0.43 & 30,505 \\
  & Case involuntarily dismissed & 0.12 & 0.33 & 30,505 \\
@@
 \cline{1-5}
-\multirow[c]{5}{*}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.10 & 0.30 & 30,505 \\
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.10 & 0.30 & 30,505 \\
  & Plaintiff has an attorney & 0.82 & 0.39 & 30,505 \\
@@
 \cline{1-5}
-\multirow[c]{5}{*}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 7731082.50 & 18211631.86 & 12,089 \\
+\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 7731082.50 & 18211631.86 & 12,089 \\
  & Building value & 2007807.90 & 5532224.22 & 12,089 \\
@@
 \cline{1-5}
-\multirow[c]{9}{*}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 263662.99 & 223748.00 & 6,766 \\
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 263662.99 & 223748.00 & 6,766 \\
  & Four years before latest docket date & 283010.66 & 265189.42 & 6,848 \\

### 2022-12-23 output/summary_statistics/tables/balance_table.tex
Fixed unrestricted summ stats table bug

\begin{table}[H]
\begin{tabular}{llrrrrrr}
\toprule
 &  & \multicolumn{3}{r}{Control Group} & \multicolumn{3}{r}{Treatment Group} \\
 &  & Mean & S.D. & N & Mean & S.D. & N \\
Panel & Variable &  &  &  &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.33 & 3651 & 0.12 & 0.32 & 10708 \\
 & For cause (transfer) & 0.01 & 0.10 & 3651 & 0.01 & 0.08 & 10708 \\
 & Foreclosure & 0.01 & 0.12 & 3651 & 0.03 & 0.18 & 10708 \\
 & Foreclosure (transfer) & 0.00 & 0.03 & 3651 & 0.00 & 0.04 & 10708 \\
 & No cause & 0.12 & 0.32 & 3651 & 0.10 & 0.30 & 10708 \\
 & No cause (transfer) & 0.02 & 0.12 & 3651 & 0.00 & 0.07 & 10708 \\
 & Non-payment of rent & 0.69 & 0.46 & 3651 & 0.72 & 0.45 & 10708 \\
 & Non-payment of rent (transfer) & 0.03 & 0.18 & 3651 & 0.01 & 0.11 & 10708 \\
\cline{1-8}
\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 0.00 & 3651 & 0.70 & 0.46 & 10708 \\
 & Case involuntarily dismissed & 0.99 & 0.09 & 3651 & 0.00 & 0.00 & 10708 \\
 & Case heard & 0.01 & 0.09 & 3651 & 0.21 & 0.40 & 10708 \\
 & Case mediated & 0.00 & 0.00 & 3651 & 0.00 & 0.00 & 10708 \\
 & Case voluntarily dismissed & 0.00 & 0.00 & 3651 & 0.00 & 0.00 & 10708 \\
\cline{1-8}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.22 & 0.42 & 3651 & 0.07 & 0.26 & 10708 \\
 & Plaintiff has an attorney & 0.78 & 0.41 & 3651 & 0.81 & 0.39 & 10708 \\
 & Defendant is an entity & 0.01 & 0.10 & 3651 & 0.01 & 0.09 & 10708 \\
 & Plaintiff is an entity & 0.62 & 0.49 & 3651 & 0.67 & 0.47 & 10708 \\
 & Money judgment & 63.61 & 1217.82 & 3651 & 3688.76 & 7607.02 & 10708 \\
\cline{1-8}
\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 16950095.01 & 1256 & 8995455.63 & 20109262.79 & 3992 \\
 & Building value & 1605427.57 & 4134089.33 & 1256 & 2352344.15 & 6424083.30 & 3992 \\
 & Land value & 61247.49 & 398867.96 & 1256 & 100993.11 & 421815.08 & 3992 \\
 & Other value & 8138231.73 & 20310157.76 & 1256 & 11437647.57 & 25728253.86 & 3992 \\
 & Units & 41.23 & 100.49 & 1256 & 42.09 & 135.69 & 3992 \\
\cline{1-8}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 252041.76 & 194239.55 & 865 & 279947.69 & 259889.60 & 2362 \\
 & Four years before latest docket date & 279493.58 & 317170.86 & 875 & 302370.92 & 305380.02 & 2388 \\
 & Three years before latest docket date & 308864.59 & 503061.61 & 885 & 324126.19 & 384074.19 & 2423 \\
 & Two years before latest docket date & 331594.86 & 537209.62 & 888 & 348565.94 & 395933.37 & 2427 \\
 & One year before latest docket date & 343934.24 & 324782.38 & 906 & 372571.00 & 316190.70 & 2447 \\
 & Latest docket date & 387984.48 & 362874.22 & 920 & 422781.76 & 426973.62 & 2471 \\
 & One year after latest docket date & 428426.83 & 363569.88 & 899 & 467437.35 & 682448.07 & 2402 \\
 & Two years after latest docket date & 451677.43 & 511837.97 & 483 & 507407.77 & 488063.38 & 1656 \\
 & Three years after latest docket date & 514122.00 & 863333.21 & 250 & 502458.89 & 430807.14 & 924 \\
\cline{1-8}
\bottomrule
\end{tabular}
\end{table}

### 2022-12-23 output/summary_statistics/tables/balance_table.tex
Fixed unrestricted summ stats table bug

@@
 \begin{table}[H]
-\begin{tabular}{llrrrrrr}
+\begin{tabular}{llrrrr}
 \toprule
- &  & \multicolumn{3}{r}{Control Group} & \multicolumn{3}{r}{Treatment Group} \\
- &  & Mean & S.D. & N & Mean & S.D. & N \\
-Panel & Variable &  &  &  &  &  &  \\
+ &  & \multicolumn{2}{c}{Control Group} & \multicolumn{2}{c}{Treatment Group} \\
+ &  & Mean & N & Mean & N \\
+Panel & Variable &  &  &  &  \\
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.33 & 3651 & 0.12 & 0.32 & 10708 \\
- & For cause (transfer) & 0.01 & 0.10 & 3651 & 0.01 & 0.08 & 10708 \\
- & Foreclosure & 0.01 & 0.12 & 3651 & 0.03 & 0.18 & 10708 \\
- & Foreclosure (transfer) & 0.00 & 0.03 & 3651 & 0.00 & 0.04 & 10708 \\
- & No cause & 0.12 & 0.32 & 3651 & 0.10 & 0.30 & 10708 \\
- & No cause (transfer) & 0.02 & 0.12 & 3651 & 0.00 & 0.07 & 10708 \\
- & Non-payment of rent & 0.69 & 0.46 & 3651 & 0.72 & 0.45 & 10708 \\
- & Non-payment of rent (transfer) & 0.03 & 0.18 & 3651 & 0.01 & 0.11 & 10708 \\
-\cline{1-8}
-\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 0.00 & 3651 & 0.70 & 0.46 & 10708 \\
- & Case involuntarily dismissed & 0.99 & 0.09 & 3651 & 0.00 & 0.00 & 10708 \\
- & Case heard & 0.01 & 0.09 & 3651 & 0.21 & 0.40 & 10708 \\
- & Case mediated & 0.00 & 0.00 & 3651 & 0.00 & 0.00 & 10708 \\
- & Case voluntarily dismissed & 0.00 & 0.00 & 3651 & 0.00 & 0.00 & 10708 \\
-\cline{1-8}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.22 & 0.42 & 3651 & 0.07 & 0.26 & 10708 \\
- & Plaintiff has an attorney & 0.78 & 0.41 & 3651 & 0.81 & 0.39 & 10708 \\
- & Defendant is an entity & 0.01 & 0.10 & 3651 & 0.01 & 0.09 & 10708 \\
- & Plaintiff is an entity & 0.62 & 0.49 & 3651 & 0.67 & 0.47 & 10708 \\
- & Money judgment & 63.61 & 1217.82 & 3651 & 3688.76 & 7607.02 & 10708 \\
-\cline{1-8}
-\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 16950095.01 & 1256 & 8995455.63 & 20109262.79 & 3992 \\
- & Building value & 1605427.57 & 4134089.33 & 1256 & 2352344.15 & 6424083.30 & 3992 \\
- & Land value & 61247.49 & 398867.96 & 1256 & 100993.11 & 421815.08 & 3992 \\
- & Other value & 8138231.73 & 20310157.76 & 1256 & 11437647.57 & 25728253.86 & 3992 \\
- & Units & 41.23 & 100.49 & 1256 & 42.09 & 135.69 & 3992 \\
-\cline{1-8}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 252041.76 & 194239.55 & 865 & 279947.69 & 259889.60 & 2362 \\
- & Four years before latest docket date & 279493.58 & 317170.86 & 875 & 302370.92 & 305380.02 & 2388 \\
- & Three years before latest docket date & 308864.59 & 503061.61 & 885 & 324126.19 & 384074.19 & 2423 \\
- & Two years before latest docket date & 331594.86 & 537209.62 & 888 & 348565.94 & 395933.37 & 2427 \\
- & One year before latest docket date & 343934.24 & 324782.38 & 906 & 372571.00 & 316190.70 & 2447 \\
- & Latest docket date & 387984.48 & 362874.22 & 920 & 422781.76 & 426973.62 & 2471 \\
- & One year after latest docket date & 428426.83 & 363569.88 & 899 & 467437.35 & 682448.07 & 2402 \\
- & Two years after latest docket date & 451677.43 & 511837.97 & 483 & 507407.77 & 488063.38 & 1656 \\
- & Three years after latest docket date & 514122.00 & 863333.21 & 250 & 502458.89 & 430807.14 & 924 \\
-\cline{1-8}
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 3651 & 0.12 & 10708 \\
+ & For cause (transfer) & 0.01 & 3651 & 0.01 & 10708 \\
+ & Foreclosure & 0.01 & 3651 & 0.03 & 10708 \\
+ & Foreclosure (transfer) & 0.00 & 3651 & 0.00 & 10708 \\
+ & No cause & 0.12 & 3651 & 0.10 & 10708 \\
+ & No cause (transfer) & 0.02 & 3651 & 0.00 & 10708 \\
+ & Non-payment of rent & 0.69 & 3651 & 0.72 & 10708 \\
+ & Non-payment of rent (transfer) & 0.03 & 3651 & 0.01 & 10708 \\
+\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 3651 & 0.70 & 10708 \\
+ & Case involuntarily dismissed & 0.99 & 3651 & 0.00 & 10708 \\
+ & Case heard & 0.01 & 3651 & 0.21 & 10708 \\
+ & Case mediated & 0.00 & 3651 & 0.00 & 10708 \\
+ & Case voluntarily dismissed & 0.00 & 3651 & 0.00 & 10708 \\
+\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.22 & 3651 & 0.07 & 10708 \\
+ & Plaintiff has an attorney & 0.78 & 3651 & 0.81 & 10708 \\
+ & Defendant is an entity & 0.01 & 3651 & 0.01 & 10708 \\
+ & Plaintiff is an entity & 0.62 & 3651 & 0.67 & 10708 \\
+ & Money judgment & 63.61 & 3651 & 3688.76 & 10708 \\
+\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 1256 & 8995455.63 & 3992 \\
+ & Building value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
+ & Land value & 61247.49 & 1256 & 100993.11 & 3992 \\
+ & Other value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
+ & Units & 41.23 & 1256 & 42.09 & 3992 \\
+\cline{1-6}
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 252041.76 & 865 & 279947.69 & 2362 \\
+ & Four years before latest docket date & 279493.58 & 875 & 302370.92 & 2388 \\
+ & Three years before latest docket date & 308864.59 & 885 & 324126.19 & 2423 \\
+ & Two years before latest docket date & 331594.86 & 888 & 348565.94 & 2427 \\
+ & One year before latest docket date & 343934.24 & 906 & 372571.00 & 2447 \\
+ & Latest docket date & 387984.48 & 920 & 422781.76 & 2471 \\
+ & One year after latest docket date & 428426.83 & 899 & 467437.35 & 2402 \\
+ & Two years after latest docket date & 451677.43 & 483 & 507407.77 & 1656 \\
+ & Three years after latest docket date & 514122.00 & 250 & 502458.89 & 924 \\
+\cline{1-6}
 \bottomrule

### 2022-12-23 output/summary_statistics/tables/balance_table.tex
Updates from Overleaf

@@
 \begin{table}[H]
-\begin{tabular}{llrrrr}
+\begin{tabular}{llrrrrrr}
 \toprule
- &  & \multicolumn{2}{c}{Control Group} & \multicolumn{2}{c}{Treatment Group} \\
- &  & Mean & N & Mean & N \\
-Panel & Variable &  &  &  &  \\
+ &  & \multicolumn{3}{r}{Control Group} & \multicolumn{3}{r}{Treatment Group} \\
+ &  & Mean & S.D. & N & Mean & S.D. & N \\
+Panel & Variable &  &  &  &  &  &  \\
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 3651 & 0.12 & 10708 \\
- & For cause (transfer) & 0.01 & 3651 & 0.01 & 10708 \\
- & Foreclosure & 0.01 & 3651 & 0.03 & 10708 \\
- & Foreclosure (transfer) & 0.00 & 3651 & 0.00 & 10708 \\
- & No cause & 0.12 & 3651 & 0.10 & 10708 \\
- & No cause (transfer) & 0.02 & 3651 & 0.00 & 10708 \\
- & Non-payment of rent & 0.69 & 3651 & 0.72 & 10708 \\
- & Non-payment of rent (transfer) & 0.03 & 3651 & 0.01 & 10708 \\
-\cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 3651 & 0.70 & 10708 \\
- & Case involuntarily dismissed & 0.99 & 3651 & 0.00 & 10708 \\
- & Case heard & 0.01 & 3651 & 0.21 & 10708 \\
- & Case mediated & 0.00 & 3651 & 0.00 & 10708 \\
- & Case voluntarily dismissed & 0.00 & 3651 & 0.00 & 10708 \\
-\cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.22 & 3651 & 0.07 & 10708 \\
- & Plaintiff has an attorney & 0.78 & 3651 & 0.81 & 10708 \\
- & Defendant is an entity & 0.01 & 3651 & 0.01 & 10708 \\
- & Plaintiff is an entity & 0.62 & 3651 & 0.67 & 10708 \\
- & Money judgment & 63.61 & 3651 & 3688.76 & 10708 \\
-\cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 1256 & 8995455.63 & 3992 \\
- & Building value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
- & Land value & 61247.49 & 1256 & 100993.11 & 3992 \\
- & Other value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
- & Units & 41.23 & 1256 & 42.09 & 3992 \\
-\cline{1-6}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 252041.76 & 865 & 279947.69 & 2362 \\
- & Four years before latest docket date & 279493.58 & 875 & 302370.92 & 2388 \\
- & Three years before latest docket date & 308864.59 & 885 & 324126.19 & 2423 \\
- & Two years before latest docket date & 331594.86 & 888 & 348565.94 & 2427 \\
- & One year before latest docket date & 343934.24 & 906 & 372571.00 & 2447 \\
- & Latest docket date & 387984.48 & 920 & 422781.76 & 2471 \\
- & One year after latest docket date & 428426.83 & 899 & 467437.35 & 2402 \\
- & Two years after latest docket date & 451677.43 & 483 & 507407.77 & 1656 \\
- & Three years after latest docket date & 514122.00 & 250 & 502458.89 & 924 \\
-\cline{1-6}
+\multirow[c]{8}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.33 & 3651 & 0.12 & 0.32 & 10708 \\
+ & For cause (transfer) & 0.01 & 0.10 & 3651 & 0.01 & 0.08 & 10708 \\
+ & Foreclosure & 0.01 & 0.12 & 3651 & 0.03 & 0.18 & 10708 \\
+ & Foreclosure (transfer) & 0.00 & 0.03 & 3651 & 0.00 & 0.04 & 10708 \\
+ & No cause & 0.12 & 0.32 & 3651 & 0.10 & 0.30 & 10708 \\
+ & No cause (transfer) & 0.02 & 0.12 & 3651 & 0.00 & 0.07 & 10708 \\
+ & Non-payment of rent & 0.69 & 0.46 & 3651 & 0.72 & 0.45 & 10708 \\
+ & Non-payment of rent (transfer) & 0.03 & 0.18 & 3651 & 0.01 & 0.11 & 10708 \\
+\cline{1-8}
+\multirow[c]{5}{3cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 0.00 & 3651 & 0.70 & 0.46 & 10708 \\
+ & Case involuntarily dismissed & 0.99 & 0.09 & 3651 & 0.00 & 0.00 & 10708 \\
+ & Case heard & 0.01 & 0.09 & 3651 & 0.21 & 0.40 & 10708 \\
+ & Case mediated & 0.00 & 0.00 & 3651 & 0.00 & 0.00 & 10708 \\
+ & Case voluntarily dismissed & 0.00 & 0.00 & 3651 & 0.00 & 0.00 & 10708 \\
+\cline{1-8}
+\multirow[c]{5}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.22 & 0.42 & 3651 & 0.07 & 0.26 & 10708 \\
+ & Plaintiff has an attorney & 0.78 & 0.41 & 3651 & 0.81 & 0.39 & 10708 \\
+ & Defendant is an entity & 0.01 & 0.10 & 3651 & 0.01 & 0.09 & 10708 \\
+ & Plaintiff is an entity & 0.62 & 0.49 & 3651 & 0.67 & 0.47 & 10708 \\
+ & Money judgment & 63.61 & 1217.82 & 3651 & 3688.76 & 7607.02 & 10708 \\
+\cline{1-8}
+\multirow[c]{5}{3cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 16950095.01 & 1256 & 8995455.63 & 20109262.79 & 3992 \\
+ & Building value & 1605427.57 & 4134089.33 & 1256 & 2352344.15 & 6424083.30 & 3992 \\
+ & Land value & 61247.49 & 398867.96 & 1256 & 100993.11 & 421815.08 & 3992 \\
+ & Other value & 8138231.73 & 20310157.76 & 1256 & 11437647.57 & 25728253.86 & 3992 \\
+ & Units & 41.23 & 100.49 & 1256 & 42.09 & 135.69 & 3992 \\
+\cline{1-8}
+\multirow[c]{9}{3cm}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 252041.76 & 194239.55 & 865 & 279947.69 & 259889.60 & 2362 \\
+ & Four years before latest docket date & 279493.58 & 317170.86 & 875 & 302370.92 & 305380.02 & 2388 \\
+ & Three years before latest docket date & 308864.59 & 503061.61 & 885 & 324126.19 & 384074.19 & 2423 \\
+ & Two years before latest docket date & 331594.86 & 537209.62 & 888 & 348565.94 & 395933.37 & 2427 \\
+ & One year before latest docket date & 343934.24 & 324782.38 & 906 & 372571.00 & 316190.70 & 2447 \\
+ & Latest docket date & 387984.48 & 362874.22 & 920 & 422781.76 & 426973.62 & 2471 \\
+ & One year after latest docket date & 428426.83 & 363569.88 & 899 & 467437.35 & 682448.07 & 2402 \\
+ & Two years after latest docket date & 451677.43 & 511837.97 & 483 & 507407.77 & 488063.38 & 1656 \\
+ & Three years after latest docket date & 514122.00 & 863333.21 & 250 & 502458.89 & 430807.14 & 924 \\
+\cline{1-8}
 \bottomrule

### 2022-12-23 output/summary_statistics/tables/balance_table.tex
Updates from Overleaf
Fixed unrestricted summ stats table bug

--- 2022-12-23 output/summary_statistics/tables/balance_table.tex
@@
-\begin{table}[H]
 \begin{tabular}{llrrrr}
 \toprule
- &  & \multicolumn{2}{c}{Control Group} & \multicolumn{2}{c}{Treatment Group} \\
+ &  & \multicolumn{2}{c}{Cases Won by Defendant} & \multicolumn{2}{c}{Cases Won by Plaintiff} \\
  &  & Mean & N & Mean & N \\
@@
 \end{tabular}
-\end{table}

### 2022-12-23 output/summary_statistics/tables/balance_table.tex
Fixed unrestricted summ stats table bug

@@
 \toprule
- &  & \multicolumn{2}{c}{Cases Won by Defendant} & \multicolumn{2}{c}{Cases Won by Plaintiff} \\
+ &  & \multicolumn{2}{|c|}{Cases Won by Defendant} & \multicolumn{2}{|c|}{Cases Won by Plaintiff} \\
  &  & Mean & N & Mean & N \\

### 2022-12-23 output/summary_statistics/tables/balance_table.tex
Fixed unrestricted summ stats table bug
Plotted evictions map
Italicized outermost column labels in balance table

--- 2022-12-23 output/summary_statistics/tables/balance_table.tex
@@
-\begin{tabular}{llrrrr}
+\begin{tabular}{llcccc}
 \toprule
- &  & \multicolumn{2}{c}{Cases Won by Defendant} & \multicolumn{2}{c}{Cases Won by Plaintiff} \\
+ &  & \multicolumn{2}{c}{\textit{Cases Won by Defendant}} & \multicolumn{2}{c}{\textit{Cases Won by Plaintiff}} \\
  &  & Mean & N & Mean & N \\

### 2022-12-23 output/summary_statistics/tables/balance_table.tex
Created trends in zestimates graph

@@
 \cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 3651 & 0.70 & 10708 \\
+\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 3651 & 0.70 & 10708 \\
  & Case involuntarily dismissed & 0.99 & 3651 & 0.00 & 10708 \\
@@
  & Case mediated & 0.00 & 3651 & 0.00 & 10708 \\
- & Case voluntarily dismissed & 0.00 & 3651 & 0.00 & 10708 \\
 \cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.22 & 3651 & 0.07 & 10708 \\
- & Plaintiff has an attorney & 0.78 & 3651 & 0.81 & 10708 \\
- & Defendant is an entity & 0.01 & 3651 & 0.01 & 10708 \\
- & Plaintiff is an entity & 0.62 & 3651 & 0.67 & 10708 \\
- & Money judgment & 63.61 & 3651 & 3688.76 & 10708 \\
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Case voluntarily dismissed & 0.22 & 3651 & 0.07 & 10708 \\
+ & Defendant has an attorney & 0.78 & 3651 & 0.81 & 10708 \\
+ & Plaintiff has an attorney & 0.01 & 3651 & 0.01 & 10708 \\
+ & Defendant is an entity & 0.62 & 3651 & 0.67 & 10708 \\
+ & Plaintiff is an entity & 63.61 & 3651 & 3688.76 & 10708 \\
 \cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 1256 & 8995455.63 & 3992 \\
- & Building value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
- & Land value & 61247.49 & 1256 & 100993.11 & 3992 \\
- & Other value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
- & Units & 41.23 & 1256 & 42.09 & 3992 \\
+\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Money judgment & 6478531.48 & 1256 & 8995455.63 & 3992 \\
+ & Total property value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
+ & Building value & 61247.49 & 1256 & 100993.11 & 3992 \\
+ & Land value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
+ & Other value & 41.23 & 1256 & 42.09 & 3992 \\
 \cline{1-6}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 252041.76 & 865 & 279947.69 & 2362 \\
- & Four years before latest docket date & 279493.58 & 875 & 302370.92 & 2388 \\
- & Three years before latest docket date & 308864.59 & 885 & 324126.19 & 2423 \\
- & Two years before latest docket date & 331594.86 & 888 & 348565.94 & 2427 \\
- & One year before latest docket date & 343934.24 & 906 & 372571.00 & 2447 \\
- & Latest docket date & 387984.48 & 920 & 422781.76 & 2471 \\
- & One year after latest docket date & 428426.83 & 899 & 467437.35 & 2402 \\
- & Two years after latest docket date & 451677.43 & 483 & 507407.77 & 1656 \\
- & Three years after latest docket date & 514122.00 & 250 & 502458.89 & 924 \\
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Units & 252041.76 & 865 & 279947.69 & 2362 \\
+ & Five years before latest docket date & 279493.58 & 875 & 302370.92 & 2388 \\
+ & Four years before latest docket date & 308864.59 & 885 & 324126.19 & 2423 \\
+ & Three years before latest docket date & 331594.86 & 888 & 348565.94 & 2427 \\
+ & Two years before latest docket date & 343934.24 & 906 & 372571.00 & 2447 \\
+ & One year before latest docket date & 387984.48 & 920 & 422781.76 & 2471 \\
+ & Latest docket date & 428426.83 & 899 & 467437.35 & 2402 \\
+ & One year after latest docket date & 451677.43 & 483 & 507407.77 & 1656 \\
+ & Two years after latest docket date & 514122.00 & 250 & 502458.89 & 924 \\
 \cline{1-6}

### 2022-12-23 output/summary_statistics/tables/summary_statistics.tex
Fixed unrestricted summ stats table bug
Plotted evictions map
Created trends in zestimates graph

--- 2022-12-23 output/summary_statistics/tables/summary_statistics.tex
@@
-\begin{tabular}{llrrr}
+\begin{tabular}{llccc}
 \toprule
@@
 \midrule
-\multirow[c]{8}{*}{\textit{Panel A: Case Initiation}} & For cause & 0.13 & 0.33 & 30,505 \\
- & For cause (transfer) & 0.01 & 0.09 & 30,505 \\
- & Foreclosure & 0.02 & 0.15 & 30,505 \\
- & Foreclosure (transfer) & 0.00 & 0.03 & 30,505 \\
- & No cause & 0.11 & 0.31 & 30,505 \\
- & No cause (transfer) & 0.01 & 0.08 & 30,505 \\
- & Non-payment of rent & 0.71 & 0.46 & 30,505 \\
- & Non-payment of rent (transfer) & 0.02 & 0.13 & 30,505 \\
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.32 & 37,943 \\
+ & For cause (transfer) & 0.01 & 0.08 & 37,943 \\
+ & Foreclosure & 0.02 & 0.14 & 37,943 \\
+ & Foreclosure (transfer) & 0.00 & 0.03 & 37,943 \\
+ & No cause & 0.10 & 0.30 & 37,943 \\
+ & No cause (transfer) & 0.01 & 0.08 & 37,943 \\
+ & Non-payment of rent & 0.74 & 0.44 & 37,943 \\
+ & Non-payment of rent (transfer) & 0.02 & 0.13 & 37,943 \\
 \cline{1-5}
-\multirow[c]{5}{*}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.24 & 0.43 & 30,505 \\
- & Case involuntarily dismissed & 0.12 & 0.33 & 30,505 \\
- & Case heard & 0.07 & 0.26 & 30,505 \\
- & Case mediated & 0.52 & 0.50 & 30,505 \\
- & Case voluntarily dismissed & 0.00 & 0.00 & 30,505 \\
+\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 37,943 \\
+ & Case involuntarily dismissed & 0.30 & 0.46 & 37,943 \\
+ & Case heard & 0.06 & 0.24 & 37,943 \\
+ & Case mediated & 0.42 & 0.49 & 37,943 \\
 \cline{1-5}
-\multirow[c]{5}{*}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.10 & 0.30 & 30,505 \\
- & Plaintiff has an attorney & 0.82 & 0.39 & 30,505 \\
- & Defendant is an entity & 0.01 & 0.08 & 30,505 \\
- & Plaintiff is an entity & 0.66 & 0.47 & 30,505 \\
- & Money judgment & 2405.16 & 5960.84 & 30,505 \\
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Case voluntarily dismissed & 0.09 & 0.28 & 37,943 \\
+ & Defendant has an attorney & 0.84 & 0.37 & 37,943 \\
+ & Plaintiff has an attorney & 0.01 & 0.08 & 37,943 \\
+ & Defendant is an entity & 0.70 & 0.46 & 37,943 \\
+ & Plaintiff is an entity & 1943.41 & 5422.12 & 37,943 \\
 \cline{1-5}
-\multirow[c]{5}{*}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 7731082.50 & 18211631.86 & 12,089 \\
- & Building value & 2007807.90 & 5532224.22 & 12,089 \\
- & Land value & 99020.63 & 539763.97 & 12,089 \\
- & Other value & 9827333.04 & 22977540.22 & 12,089 \\
- & Units & 39.15 & 113.83 & 12,089 \\
+\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Money judgment & 9435708.78 & 20612629.31 & 14,491 \\
+ & Total property value & 2482603.38 & 6470958.91 & 14,491 \\
+ & Building value & 113817.19 & 536568.37 & 14,491 \\
+ & Land value & 12020146.88 & 26285935.89 & 14,491 \\
+ & Other value & 42.25 & 112.87 & 14,491 \\
 \cline{1-5}
-\multirow[c]{9}{*}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 263662.99 & 223748.00 & 6,766 \\
- & Four years before latest docket date & 283010.66 & 265189.42 & 6,848 \\
- & Three years before latest docket date & 305906.07 & 337719.48 & 6,950 \\
- & Two years before latest docket date & 344030.70 & 1167207.98 & 6,966 \\
- & One year before latest docket date & 352784.42 & 300314.15 & 6,992 \\
- & Latest docket date & 395691.50 & 416306.93 & 7,045 \\
- & One year after latest docket date & 435193.84 & 476324.79 & 6,943 \\
- & Two years after latest docket date & 474304.25 & 446024.13 & 4,910 \\
- & Three years after latest docket date & 507403.55 & 1140138.35 & 2,680 \\
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Units & 268580.04 & 261642.26 & 8,273 \\
+ & Five years before latest docket date & 288822.75 & 298902.01 & 8,384 \\
+ & Four years before latest docket date & 311679.90 & 330953.69 & 8,508 \\
+ & Three years before latest docket date & 351524.51 & 1127830.09 & 8,524 \\
+ & Two years before latest docket date & 358534.63 & 303605.64 & 8,547 \\
+ & One year before latest docket date & 402381.22 & 400555.10 & 8,602 \\
+ & Latest docket date & 443118.39 & 459237.85 & 8,539 \\
+ & One year after latest docket date & 481103.73 & 437176.87 & 5,752 \\
+ & Two years after latest docket date & 510339.87 & 1057656.48 & 3,171 \\
 \cline{1-5}

### 2022-12-23 src/01_build/05_merge.py

@@ -70,10 +70,6 @@ if VERBOSE:
         f"of original dataset).")
 merged_df = merged_df.loc[mask, :]
 
-# Mark cases which were resolved by voluntary dismissal (dropped by plaintiff).
-mask = merged_df['disposition'].str.contains("R 41(a)(1) Voluntary Dismissal on", na=False, regex=False)
-merged_df.loc[:, 'voluntary_dismissal'] = np.where(mask, 1, 0)
-
 # Clean the values in the judgment_for_pdu variable.
 judgment_for_pdu_replacement_dict = {"unknown": "Unknown",
                                      "plaintiff": "Plaintiff",
@@ -92,6 +88,12 @@ if VERBOSE:
     print(
         f"Dropping {(~mask).sum()} observations where disposition_found is \'Mediated\' ({100 * (((~mask).sum()) / original_N):.3} "
         f"percent of original dataset).")
+merged_df = merged_df.loc[mask, :]
+
+# Drop cases which were resolved by voluntary dismissal (dropped by plaintiff).
+mask = ~(merged_df['disposition'].str.contains("R 41(a)(1) Voluntary Dismissal on", na=False, regex=False))
+print(
+    f"Dropping {(~mask).sum()} observations resolved through voluntary dismissal ({100 * (((~mask).sum()) / original_N):.3} percent of original dataset).")
 merged_df = merged_df.loc[mask, :]
 
 # Drop cases where disposition_found is "Other".
@@ -120,7 +122,7 @@ merged_df = merged_df.loc[mask, :]
 
 # Generate a variable indicating judgement in favor of defendant.
 merged_df.loc[:, 'judgment_for_defendant'] = 0
-mask = (merged_df['disposition_found'] == "Dismissed") | (merged_df['judgment_for_pdu'] == "Defendant") | (merged_df['voluntary_dismissal'] == 1)
+mask = (merged_df['disposition_found'] == "Dismissed") | (merged_df['judgment_for_pdu'] == "Defendant")
 merged_df.loc[mask, 'judgment_for_defendant'] = 1
 
 # Generate a variable indicating judgement in favor of plaintiff.

### 2022-12-25 output/summary_statistics/tables/balance_table.tex
Added GETting of all zpids when several are returned for one address

@@
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 3651 & 0.12 & 10708 \\
- & For cause (transfer) & 0.01 & 3651 & 0.01 & 10708 \\
- & Foreclosure & 0.01 & 3651 & 0.03 & 10708 \\
- & Foreclosure (transfer) & 0.00 & 3651 & 0.00 & 10708 \\
- & No cause & 0.12 & 3651 & 0.10 & 10708 \\
- & No cause (transfer) & 0.02 & 3651 & 0.00 & 10708 \\
- & Non-payment of rent & 0.69 & 3651 & 0.72 & 10708 \\
- & Non-payment of rent (transfer) & 0.03 & 3651 & 0.01 & 10708 \\
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 4090 & 0.12 & 11921 \\
+ & For cause (transfer) & 0.01 & 4090 & 0.01 & 11921 \\
+ & Foreclosure & 0.01 & 4090 & 0.03 & 11921 \\
+ & Foreclosure (transfer) & 0.00 & 4090 & 0.00 & 11921 \\
+ & No cause & 0.12 & 4090 & 0.10 & 11921 \\
+ & No cause (transfer) & 0.01 & 4090 & 0.00 & 11921 \\
+ & Non-payment of rent & 0.69 & 4090 & 0.72 & 11921 \\
+ & Non-payment of rent (transfer) & 0.03 & 4090 & 0.01 & 11921 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 3651 & 0.70 & 10708 \\
- & Case involuntarily dismissed & 0.99 & 3651 & 0.00 & 10708 \\
- & Case heard & 0.01 & 3651 & 0.21 & 10708 \\
- & Case mediated & 0.00 & 3651 & 0.00 & 10708 \\
+\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 4090 & 0.67 & 11921 \\
+ & Case involuntarily dismissed & 0.99 & 4090 & 0.00 & 11921 \\
+ & Case heard & 0.01 & 4090 & 0.19 & 11921 \\
+ & Case mediated & 0.00 & 4090 & 0.00 & 11921 \\
 \cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Case voluntarily dismissed & 0.22 & 3651 & 0.07 & 10708 \\
- & Defendant has an attorney & 0.78 & 3651 & 0.81 & 10708 \\
- & Plaintiff has an attorney & 0.01 & 3651 & 0.01 & 10708 \\
- & Defendant is an entity & 0.62 & 3651 & 0.67 & 10708 \\
- & Plaintiff is an entity & 63.61 & 3651 & 3688.76 & 10708 \\
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.20 & 4090 & 0.07 & 11921 \\
+ & Plaintiff has an attorney & 0.79 & 4090 & 0.81 & 11921 \\
+ & Defendant is an entity & 0.01 & 4090 & 0.01 & 11921 \\
+ & Plaintiff is an entity & 0.63 & 4090 & 0.67 & 11921 \\
+ & Money judgment & 57.56 & 4090 & 3444.31 & 11921 \\
 \cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Money judgment & 6478531.48 & 1256 & 8995455.63 & 3992 \\
- & Total property value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
- & Building value & 61247.49 & 1256 & 100993.11 & 3992 \\
- & Land value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
- & Other value & 41.23 & 1256 & 42.09 & 3992 \\
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 1256 & 8995455.63 & 3992 \\
+ & Building value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
+ & Land value & 61247.49 & 1256 & 100993.11 & 3992 \\
+ & Other value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
+ & Units & 41.23 & 1256 & 42.09 & 3992 \\
 \cline{1-6}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Units & 252041.76 & 865 & 279947.69 & 2362 \\
- & Five years before latest docket date & 279493.58 & 875 & 302370.92 & 2388 \\
- & Four years before latest docket date & 308864.59 & 885 & 324126.19 & 2423 \\
- & Three years before latest docket date & 331594.86 & 888 & 348565.94 & 2427 \\
- & Two years before latest docket date & 343934.24 & 906 & 372571.00 & 2447 \\
- & One year before latest docket date & 387984.48 & 920 & 422781.76 & 2471 \\
- & Latest docket date & 428426.83 & 899 & 467437.35 & 2402 \\
- & One year after latest docket date & 451677.43 & 483 & 507407.77 & 1656 \\
- & Two years after latest docket date & 514122.00 & 250 & 502458.89 & 924 \\
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 245078.62 & 957 & 275426.28 & 2603 \\
+ & Four years before latest docket date & 265248.64 & 977 & 294572.61 & 2635 \\
+ & Three years before latest docket date & 308529.26 & 992 & 317382.82 & 2706 \\
+ & Two years before latest docket date & 330329.21 & 998 & 346565.14 & 2709 \\
+ & One year before latest docket date & 336544.68 & 1002 & 364931.93 & 2715 \\
+ & Latest docket date & 364629.48 & 991 & 391919.00 & 2701 \\
+ & One year after latest docket date & 412421.05 & 1045 & 440748.11 & 2796 \\
+ & Two years after latest docket date & 450898.44 & 801 & 509321.48 & 2493 \\
+ & Three years after latest docket date & 485688.38 & 441 & 512215.31 & 1613 \\
 \cline{1-6}

### 2022-12-25 output/summary_statistics/tables/summary_statistics.tex
Added GETting of all zpids when several are returned for one address

@@
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.32 & 37,943 \\
- & For cause (transfer) & 0.01 & 0.08 & 37,943 \\
- & Foreclosure & 0.02 & 0.14 & 37,943 \\
- & Foreclosure (transfer) & 0.00 & 0.03 & 37,943 \\
- & No cause & 0.10 & 0.30 & 37,943 \\
- & No cause (transfer) & 0.01 & 0.08 & 37,943 \\
- & Non-payment of rent & 0.74 & 0.44 & 37,943 \\
- & Non-payment of rent (transfer) & 0.02 & 0.13 & 37,943 \\
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.32 & 40,735 \\
+ & For cause (transfer) & 0.01 & 0.08 & 40,735 \\
+ & Foreclosure & 0.02 & 0.14 & 40,735 \\
+ & Foreclosure (transfer) & 0.00 & 0.03 & 40,735 \\
+ & No cause & 0.10 & 0.30 & 40,735 \\
+ & No cause (transfer) & 0.01 & 0.08 & 40,735 \\
+ & Non-payment of rent & 0.73 & 0.44 & 40,735 \\
+ & Non-payment of rent (transfer) & 0.02 & 0.13 & 40,735 \\
 \cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 37,943 \\
- & Case involuntarily dismissed & 0.30 & 0.46 & 37,943 \\
- & Case heard & 0.06 & 0.24 & 37,943 \\
- & Case mediated & 0.42 & 0.49 & 37,943 \\
+\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,735 \\
+ & Case involuntarily dismissed & 0.29 & 0.45 & 40,735 \\
+ & Case heard & 0.06 & 0.23 & 40,735 \\
+ & Case mediated & 0.41 & 0.49 & 40,735 \\
 \cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Case voluntarily dismissed & 0.09 & 0.28 & 37,943 \\
- & Defendant has an attorney & 0.84 & 0.37 & 37,943 \\
- & Plaintiff has an attorney & 0.01 & 0.08 & 37,943 \\
- & Defendant is an entity & 0.70 & 0.46 & 37,943 \\
- & Plaintiff is an entity & 1943.41 & 5422.12 & 37,943 \\
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,735 \\
+ & Plaintiff has an attorney & 0.84 & 0.37 & 40,735 \\
+ & Defendant is an entity & 0.01 & 0.08 & 40,735 \\
+ & Plaintiff is an entity & 0.70 & 0.46 & 40,735 \\
+ & Money judgment & 1890.04 & 5279.02 & 40,735 \\
 \cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Money judgment & 9435708.78 & 20612629.31 & 14,491 \\
- & Total property value & 2482603.38 & 6470958.91 & 14,491 \\
- & Building value & 113817.19 & 536568.37 & 14,491 \\
- & Land value & 12020146.88 & 26285935.89 & 14,491 \\
- & Other value & 42.25 & 112.87 & 14,491 \\
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 9435708.78 & 20612629.31 & 14,491 \\
+ & Building value & 2482603.38 & 6470958.91 & 14,491 \\
+ & Land value & 113817.19 & 536568.37 & 14,491 \\
+ & Other value & 12020146.88 & 26285935.89 & 14,491 \\
+ & Units & 42.25 & 112.87 & 14,491 \\
 \cline{1-5}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Units & 268580.04 & 261642.26 & 8,273 \\
- & Five years before latest docket date & 288822.75 & 298902.01 & 8,384 \\
- & Four years before latest docket date & 311679.90 & 330953.69 & 8,508 \\
- & Three years before latest docket date & 351524.51 & 1127830.09 & 8,524 \\
- & Two years before latest docket date & 358534.63 & 303605.64 & 8,547 \\
- & One year before latest docket date & 402381.22 & 400555.10 & 8,602 \\
- & Latest docket date & 443118.39 & 459237.85 & 8,539 \\
- & One year after latest docket date & 481103.73 & 437176.87 & 5,752 \\
- & Two years after latest docket date & 510339.87 & 1057656.48 & 3,171 \\
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 261403.18 & 249286.93 & 8,865 \\
+ & Four years before latest docket date & 280115.12 & 286856.77 & 8,994 \\
+ & Three years before latest docket date & 306539.18 & 377212.67 & 9,198 \\
+ & Two years before latest docket date & 341425.83 & 1033374.53 & 9,210 \\
+ & One year before latest docket date & 350912.11 & 314096.19 & 9,217 \\
+ & Latest docket date & 376241.94 & 315819.32 & 9,129 \\
+ & One year after latest docket date & 421391.90 & 347409.45 & 9,476 \\
+ & Two years after latest docket date & 478657.38 & 468642.16 & 8,363 \\
+ & Three years after latest docket date & 503342.65 & 795669.13 & 5,368 \\
 \cline{1-5}

### 2022-12-25 src/01_build/02_POST_batched_addresses.py

@@ -20,7 +20,7 @@ evictions_df = pd.read_csv(INPUT_DATA)
 # Save eviction addresses in 100-row batches.
 batched_addresses = batch_df(df=evictions_df['property_address_full'], batch_size=100)
 filepaths = [os.path.join(BATCHED_ADDRESSES, f"batch_{i}.txt") for i, batched_address in enumerate(batched_addresses)]
-[to_binary(filepath=filepath, series=batch, index=False, header=False) for filepath, batch in zip(filepaths, batched_addresses)]
+[batch.to_csv(filepath, index=False, header=False, sep=';') for filepath, batch in zip(filepaths, batched_addresses)]
 job_numbers = [POST_batch_ZPID_request(filepath) for filepath in filepaths]
 job_numbers = pd.Series(job_numbers)
 job_numbers.to_csv(OUTPUT_DATA, index=False, header=False)

### 2022-12-25 src/01_build/03_GET_zpids_and_merge.py

@@ -9,5 +9,4 @@ OUTPUT_DATA = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_inter
 evictions_df = pd.read_csv(INPUT_DATA_EVICTIONS)
 job_numbers = pd.read_csv(INPUT_DATA_JOB_NUMBERS, header=None)[0]
 addresses_with_zpids = pd.concat([GET_processed_ZPIDs(job_number) for job_number in job_numbers], axis=0).reset_index(drop=True)
-evictions_df = pd.concat([evictions_df, addresses_with_zpids], axis=1)
-evictions_df[['case_number', 'zpid']].to_csv(OUTPUT_DATA, index=False)
+addresses_with_zpids.to_csv(OUTPUT_DATA, index=False)

### 2022-12-25 src/01_build/04_GET_zillow_data.py

@@ -7,8 +7,9 @@ INPUT_DATA = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_interm
 OUTPUT_DATA = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/zestimates.csv"
 
 # Get Zestimates and concatenate into a single DataFrame.
-zpids_df = pd.read_csv(INPUT_DATA, dtype={'zpid': str}).dropna()
-zestimates_df = pd.concat([GET_zestimate_history(zpid, case_number) for zpid, case_number in zip(zpids_df['zpid'], zpids_df['case_number'])], axis=0)
+zpids_df = pd.read_csv(INPUT_DATA, dtype={'zpid': str}).fillna(" ")
+zestimates_df = pd.concat([GET_zestimate_history(zpid, address) for zpid, address in zip(zpids_df['zpid'], zpids_df['property_address_full'])], axis=0)
+# TODO: Resume here. Start by adapting GET_zestimate_history to the new way that ZPIDs are stored on disk.
 zestimates_df = zestimates_df.reset_index()
 
 # Produce month and year columns.

### 2022-12-25 src/01_build/05_merge.py

@@ -63,10 +63,10 @@ if VERBOSE:
 original_N = len(merged_df)
 
 # Drop cases missing latest_docket date.
-mask = merged_df['latest_docket_date'].notna()
+mask = merged_df['file_date'].notna()
 if VERBOSE:
     print(
-        f"Dropping {(~mask).sum()} observations where latest_docket_date is missing ({100 * (((~mask).sum()) / original_N):.3} percent "
+        f"Dropping {(~mask).sum()} observations where file_date is missing ({100 * (((~mask).sum()) / original_N):.3} percent "
         f"of original dataset).")
 merged_df = merged_df.loc[mask, :]
 

### 2022-12-25 src/01_build/zillow_utilities.py

@@ -7,6 +7,8 @@ import time
 import json
 from io import StringIO
 from typing import List
+
+import numpy as np
 import pandas as pd
 import requests
 from googlesearch import search
@@ -126,6 +128,26 @@ def GET_processed_ZPIDs(job_number):
     if "isn't complete!" in response.text:
         raise RuntimeError("The specified job_number was requested before it was completed on the server.")
     else:
-        result = pd.read_csv(StringIO(response.text), header=None, usecols=[0, 1], names=['property_address_full', 'zpid'])
-        result.loc[:, 'property_address_full'] = result['property_address_full'].str.replace("\"", "", regex=False)
+        # Read in the text of the response as a CSV with a separator that isn't actually present in the text.
+        # This ensures that we read in the text of the CSV as a single column.
+        result = pd.read_csv(StringIO(response.text), header=None, sep="NOT_A_SEPARATOR")[0]  # Get the first and only column.
+
+        split = result.str.split("\"")  # Split on the address's closing quotes.
+        # Build one column containing addresses and another containing lists of ZPIDs.
+        ZPIDs = split.str[2].str.split(",")
+        for index, zpid_list in enumerate(ZPIDs):
+            new_list = [element for element in zpid_list if element != ""]
+            if len(new_list) == 0:
+                ZPIDs.loc[index] = [np.nan]
+            else:
+                ZPIDs.loc[index] = new_list
+        ZPIDs = pd.DataFrame(ZPIDs.tolist())
+        ZPIDs.columns = "zpid" + (ZPIDs.columns + 1).astype(str)
+        addresses = split.str[1]
+        addresses.name = "property_address_full"
+
+        # Return result.
+        result = pd.concat([addresses, ZPIDs], axis=1)
+        result = pd.wide_to_long(result, stubnames='zpid', i='address', j='j').reset_index().drop(columns='j').reset_index(drop=True)
+
         return result

### 2022-12-25 src/02_analysis/figure_utilities.py

@@ -93,7 +93,6 @@ def plot_scatter_with_error_bars(ax: plt.Axes,
     :param zorder:
     """
     yerr = (y_upper - y_lower) / 2
-    print(yerr)
     ecolor = to_rgba(error_color, alpha=error_opacity)
     if zorder is None:
         ax.errorbar(x, y, yerr=yerr, color=point_color, ms=point_size, ecolor=ecolor, fmt=marker, label=label, capsize=3)

### 2022-12-25 src/02_analysis/scratch.py

@@ -1,16 +1,25 @@
+import numpy as np
 import pandas as pd
 from matplotlib import pyplot as plt
 
 from figure_utilities import plot_scatter_with_error_bars
 
-y = pd.Series(1, index=range(0, 10))
-y_upper = pd.Series(2, index=range(0, 10))
-y_lower = pd.Series(0, index=range(0, 10))
+result = pd.read_csv("/Users/arjunshanmugam/Desktop/zpid_result_test.txt", header=None, sep="NOT_A_SEPARATOR")[0]  # Get the first and only column.
 
-fig, ax = plt.subplots()
-plot_scatter_with_error_bars(ax,
-                             y.index,
-                             y,
-                             y_upper,
-                             y_lower)
-plt.show()
+split = result.str.split("\"")  # Split on the address's closing quotes.
+# Build one column containing addresses and another containing lists of ZPIDs.
+ZPIDs = split.str[2].str.split(",")
+for index, zpid_list in enumerate(ZPIDs):
+    new_list = [element for element in zpid_list if element != ""]
+    if len(new_list) == 0:
+        ZPIDs.loc[index] = [np.nan]
+    else:
+        ZPIDs.loc[index] = new_list
+ZPIDs = pd.DataFrame(ZPIDs.tolist())
+ZPIDs.columns = "zpid" + (ZPIDs.columns + 1).astype(str)
+addresses = split.str[1]
+addresses.name = "address"
+
+# Return result.
+result = pd.concat([addresses, ZPIDs], axis=1)
+result = pd.wide_to_long(result, stubnames='zpid', i='address', j='j').reset_index().drop(columns='j').reset_index(drop=True)

### 2022-12-28 output/summary_statistics/tables/balance_table.tex
About to revamp DiD observed periodS

@@
 \cline{1-6}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 245078.62 & 957 & 275426.28 & 2603 \\
- & Four years before latest docket date & 265248.64 & 977 & 294572.61 & 2635 \\
- & Three years before latest docket date & 308529.26 & 992 & 317382.82 & 2706 \\
- & Two years before latest docket date & 330329.21 & 998 & 346565.14 & 2709 \\
- & One year before latest docket date & 336544.68 & 1002 & 364931.93 & 2715 \\
- & Latest docket date & 364629.48 & 991 & 391919.00 & 2701 \\
- & One year after latest docket date & 412421.05 & 1045 & 440748.11 & 2796 \\
- & Two years after latest docket date & 450898.44 & 801 & 509321.48 & 2493 \\
- & Three years after latest docket date & 485688.38 & 441 & 512215.31 & 1613 \\
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 255601.88 & 1019 & 267829.81 & 2904 \\
+ & Four years before latest docket date & 278440.18 & 1035 & 286996.41 & 2939 \\
+ & Three years before latest docket date & 297578.04 & 1052 & 313182.84 & 3015 \\
+ & Two years before latest docket date & 332743.89 & 1055 & 341145.74 & 3016 \\
+ & One year before latest docket date & 338598.45 & 1058 & 360142.85 & 3018 \\
+ & Latest docket date & 373816.17 & 1044 & 387035.91 & 2993 \\
+ & One year after latest docket date & 419391.34 & 1086 & 431642.67 & 3087 \\
+ & Two years after latest docket date & 446124.50 & 824 & 491836.71 & 2726 \\
+ & Three years after latest docket date & 482504.08 & 455 & 508987.34 & 1793 \\
 \cline{1-6}

### 2022-12-28 output/summary_statistics/tables/summary_statistics.tex
About to revamp DiD observed periodS

@@
 \cline{1-5}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 261403.18 & 249286.93 & 8,865 \\
- & Four years before latest docket date & 280115.12 & 286856.77 & 8,994 \\
- & Three years before latest docket date & 306539.18 & 377212.67 & 9,198 \\
- & Two years before latest docket date & 341425.83 & 1033374.53 & 9,210 \\
- & One year before latest docket date & 350912.11 & 314096.19 & 9,217 \\
- & Latest docket date & 376241.94 & 315819.32 & 9,129 \\
- & One year after latest docket date & 421391.90 & 347409.45 & 9,476 \\
- & Two years after latest docket date & 478657.38 & 468642.16 & 8,363 \\
- & Three years after latest docket date & 503342.65 & 795669.13 & 5,368 \\
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 261450.07 & 238031.93 & 9,843 \\
+ & Four years before latest docket date & 280231.05 & 276040.32 & 9,969 \\
+ & Three years before latest docket date & 307124.02 & 369747.73 & 10,173 \\
+ & Two years before latest docket date & 341068.35 & 987098.31 & 10,183 \\
+ & One year before latest docket date & 351156.71 & 311971.28 & 10,191 \\
+ & Latest docket date & 377366.88 & 316634.29 & 10,097 \\
+ & One year after latest docket date & 421583.49 & 344317.43 & 10,444 \\
+ & Two years after latest docket date & 477926.97 & 457674.35 & 9,176 \\
+ & Three years after latest docket date & 501586.74 & 780403.17 & 5,895 \\
 \cline{1-5}

### 2022-12-28 src/02_analysis/figure_and_table_constants.py

@@ -13,5 +13,11 @@ class Colors:
     P9 = "#FFD400"
     P10 = "#6BBD45"
 
+    SUMMARY_STATISTICS_COLOR = 'black'
+    LABELING_COLOR = 'grey'
+    TREATMENT_COLOR = 'red'
+    CONTROL_COLOR = 'blue'
+
+
 class Text:
     DEFAULT_DECIMAL_PLACES = 3

### 2022-12-31 output/summary_statistics/tables/balance_table.tex
Added median to summary statistics

--- 2022-12-23 output/summary_statistics/tables/balance_table.tex
@@
 \toprule
- &  & \multicolumn{2}{c}{\textit{Cases Won by Defendant}} & \multicolumn{2}{c}{\textit{Cases Won by Plaintiff}} \\
- &  & Mean & N & Mean & N \\
-Panel & Variable &  &  &  &  \\
+ &  & \multicolumn{3}{c}{\textit{Cases Won by Defendant}} & \multicolumn{3}{c}{\textit{Cases Won by Plaintiff}} \\
+ &  & Mean & median & N & Mean & median & N \\
+Panel & Variable &  &  &  &  &  &  \\
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 3651 & 0.12 & 10708 \\
- & For cause (transfer) & 0.01 & 3651 & 0.01 & 10708 \\
- & Foreclosure & 0.01 & 3651 & 0.03 & 10708 \\
- & Foreclosure (transfer) & 0.00 & 3651 & 0.00 & 10708 \\
- & No cause & 0.12 & 3651 & 0.10 & 10708 \\
- & No cause (transfer) & 0.02 & 3651 & 0.00 & 10708 \\
- & Non-payment of rent & 0.69 & 3651 & 0.72 & 10708 \\
- & Non-payment of rent (transfer) & 0.03 & 3651 & 0.01 & 10708 \\
-\cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 3651 & 0.70 & 10708 \\
- & Case involuntarily dismissed & 0.99 & 3651 & 0.00 & 10708 \\
- & Case heard & 0.01 & 3651 & 0.21 & 10708 \\
- & Case mediated & 0.00 & 3651 & 0.00 & 10708 \\
-\cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Case voluntarily dismissed & 0.22 & 3651 & 0.07 & 10708 \\
- & Defendant has an attorney & 0.78 & 3651 & 0.81 & 10708 \\
- & Plaintiff has an attorney & 0.01 & 3651 & 0.01 & 10708 \\
- & Defendant is an entity & 0.62 & 3651 & 0.67 & 10708 \\
- & Plaintiff is an entity & 63.61 & 3651 & 3688.76 & 10708 \\
-\cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Money judgment & 6478531.48 & 1256 & 8995455.63 & 3992 \\
- & Total property value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
- & Building value & 61247.49 & 1256 & 100993.11 & 3992 \\
- & Land value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
- & Other value & 41.23 & 1256 & 42.09 & 3992 \\
-\cline{1-6}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Units & 252041.76 & 865 & 279947.69 & 2362 \\
- & Five years before latest docket date & 279493.58 & 875 & 302370.92 & 2388 \\
- & Four years before latest docket date & 308864.59 & 885 & 324126.19 & 2423 \\
- & Three years before latest docket date & 331594.86 & 888 & 348565.94 & 2427 \\
- & Two years before latest docket date & 343934.24 & 906 & 372571.00 & 2447 \\
- & One year before latest docket date & 387984.48 & 920 & 422781.76 & 2471 \\
- & Latest docket date & 428426.83 & 899 & 467437.35 & 2402 \\
- & One year after latest docket date & 451677.43 & 483 & 507407.77 & 1656 \\
- & Two years after latest docket date & 514122.00 & 250 & 502458.89 & 924 \\
-\cline{1-6}
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.000000 & 4082 & 0.12 & 0.000000 & 11912 \\
+ & For cause (transfer) & 0.01 & 0.000000 & 4082 & 0.01 & 0.000000 & 11912 \\
+ & Foreclosure & 0.01 & 0.000000 & 4082 & 0.03 & 0.000000 & 11912 \\
+ & Foreclosure (transfer) & 0.00 & 0.000000 & 4082 & 0.00 & 0.000000 & 11912 \\
+ & No cause & 0.12 & 0.000000 & 4082 & 0.10 & 0.000000 & 11912 \\
+ & No cause (transfer) & 0.01 & 0.000000 & 4082 & 0.00 & 0.000000 & 11912 \\
+ & Non-payment of rent & 0.69 & 1.000000 & 4082 & 0.72 & 1.000000 & 11912 \\
+ & Non-payment of rent (transfer) & 0.03 & 0.000000 & 4082 & 0.01 & 0.000000 & 11912 \\
+\cline{1-8}
+\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 97.63 & 61.000000 & 4082 & 58.85 & 20.000000 & 10273 \\
+ & Case defaulted & 0.00 & 0.000000 & 4082 & 0.67 & 1.000000 & 11912 \\
+ & Case involuntarily dismissed & 0.99 & 1.000000 & 4082 & 0.00 & 0.000000 & 11912 \\
+ & Case heard & 0.01 & 0.000000 & 4082 & 0.19 & 0.000000 & 11912 \\
+ & Case mediated & 0.00 & 0.000000 & 4082 & 0.00 & 0.000000 & 11912 \\
+\cline{1-8}
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.20 & 0.000000 & 4082 & 0.07 & 0.000000 & 11912 \\
+ & Plaintiff has an attorney & 0.79 & 1.000000 & 4082 & 0.81 & 1.000000 & 11912 \\
+ & Defendant is an entity & 0.01 & 0.000000 & 4082 & 0.01 & 0.000000 & 11912 \\
+ & Plaintiff is an entity & 0.63 & 1.000000 & 4082 & 0.67 & 1.000000 & 11912 \\
+ & Money judgment & 57.67 & 0.000000 & 4082 & 3440.73 & 1,310.940000 & 11912 \\
+\cline{1-8}
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 641,200.000000 & 1256 & 8997593.33 & 579,400.000000 & 3991 \\
+ & Building value & 1605427.57 & 169,600.000000 & 1256 & 2352903.60 & 161,000.000000 & 3991 \\
+ & Land value & 61247.49 & 1,100.000000 & 1256 & 101018.42 & 2,100.000000 & 3991 \\
+ & Other value & 8138231.73 & 823,450.000000 & 1256 & 11440367.23 & 808,100.000000 & 3991 \\
+ & Units & 41.23 & 2.000000 & 1256 & 42.10 & 1.000000 & 3991 \\
+\cline{1-8}
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 255719.80 & 185,330.500000 & 1018 & 267442.86 & 218,825.000000 & 2901 \\
+ & Four years before latest docket date & 278556.70 & 195,892.500000 & 1034 & 285983.57 & 228,526.000000 & 2936 \\
+ & Three years before latest docket date & 297696.16 & 210,030.000000 & 1051 & 312711.10 & 244,821.500000 & 3012 \\
+ & Two years before latest docket date & 332887.98 & 223,501.000000 & 1054 & 339939.67 & 264,659.000000 & 3013 \\
+ & One year before latest docket date & 338734.41 & 240,000.000000 & 1057 & 359532.30 & 285,032.000000 & 3015 \\
+ & Latest docket date & 373978.71 & 270,184.000000 & 1043 & 385699.20 & 313,104.500000 & 2990 \\
+ & One year after latest docket date & 419565.10 & 317,500.000000 & 1085 & 431037.20 & 354,320.000000 & 3084 \\
+ & Two years after latest docket date & 446321.14 & 348,300.000000 & 823 & 490315.74 & 404,600.000000 & 2723 \\
+ & Three years after latest docket date & 482787.35 & 363,650.000000 & 454 & 507050.53 & 419,600.000000 & 1791 \\
+\cline{1-8}
 \bottomrule

### 2022-12-31 output/summary_statistics/tables/summary_statistics.tex
Added median to summary statistics

--- 2022-12-23 output/summary_statistics/tables/summary_statistics.tex
@@
 \toprule
- &  & Mean & S.D. & N \\
-Panel & Variable &  &  &  \\
+ &  & Mean & median & S.D. & N \\
+Panel & Variable &  &  &  &  \\
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.32 & 37,943 \\
- & For cause (transfer) & 0.01 & 0.08 & 37,943 \\
- & Foreclosure & 0.02 & 0.14 & 37,943 \\
- & Foreclosure (transfer) & 0.00 & 0.03 & 37,943 \\
- & No cause & 0.10 & 0.30 & 37,943 \\
- & No cause (transfer) & 0.01 & 0.08 & 37,943 \\
- & Non-payment of rent & 0.74 & 0.44 & 37,943 \\
- & Non-payment of rent (transfer) & 0.02 & 0.13 & 37,943 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 37,943 \\
- & Case involuntarily dismissed & 0.30 & 0.46 & 37,943 \\
- & Case heard & 0.06 & 0.24 & 37,943 \\
- & Case mediated & 0.42 & 0.49 & 37,943 \\
-\cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Case voluntarily dismissed & 0.09 & 0.28 & 37,943 \\
- & Defendant has an attorney & 0.84 & 0.37 & 37,943 \\
- & Plaintiff has an attorney & 0.01 & 0.08 & 37,943 \\
- & Defendant is an entity & 0.70 & 0.46 & 37,943 \\
- & Plaintiff is an entity & 1943.41 & 5422.12 & 37,943 \\
-\cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Money judgment & 9435708.78 & 20612629.31 & 14,491 \\
- & Total property value & 2482603.38 & 6470958.91 & 14,491 \\
- & Building value & 113817.19 & 536568.37 & 14,491 \\
- & Land value & 12020146.88 & 26285935.89 & 14,491 \\
- & Other value & 42.25 & 112.87 & 14,491 \\
-\cline{1-5}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Units & 268580.04 & 261642.26 & 8,273 \\
- & Five years before latest docket date & 288822.75 & 298902.01 & 8,384 \\
- & Four years before latest docket date & 311679.90 & 330953.69 & 8,508 \\
- & Three years before latest docket date & 351524.51 & 1127830.09 & 8,524 \\
- & Two years before latest docket date & 358534.63 & 303605.64 & 8,547 \\
- & One year before latest docket date & 402381.22 & 400555.10 & 8,602 \\
- & Latest docket date & 443118.39 & 459237.85 & 8,539 \\
- & One year after latest docket date & 481103.73 & 437176.87 & 5,752 \\
- & Two years after latest docket date & 510339.87 & 1057656.48 & 3,171 \\
-\cline{1-5}
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.000000 & 0.32 & 40,727 \\
+ & For cause (transfer) & 0.01 & 0.000000 & 0.08 & 40,727 \\
+ & Foreclosure & 0.02 & 0.000000 & 0.14 & 40,727 \\
+ & Foreclosure (transfer) & 0.00 & 0.000000 & 0.03 & 40,727 \\
+ & No cause & 0.10 & 0.000000 & 0.30 & 40,727 \\
+ & No cause (transfer) & 0.01 & 0.000000 & 0.08 & 40,727 \\
+ & Non-payment of rent & 0.73 & 1.000000 & 0.44 & 40,727 \\
+ & Non-payment of rent (transfer) & 0.02 & 0.000000 & 0.13 & 40,727 \\
+\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 57.81 & 21.000000 & 78.29 & 39,087 \\
+ & Case defaulted & 0.20 & 0.000000 & 0.40 & 40,727 \\
+ & Case involuntarily dismissed & 0.29 & 0.000000 & 0.45 & 40,727 \\
+ & Case heard & 0.06 & 0.000000 & 0.23 & 40,727 \\
+ & Case mediated & 0.41 & 0.000000 & 0.49 & 40,727 \\
+\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.000000 & 0.28 & 40,727 \\
+ & Plaintiff has an attorney & 0.84 & 1.000000 & 0.37 & 40,727 \\
+ & Defendant is an entity & 0.01 & 0.000000 & 0.08 & 40,727 \\
+ & Plaintiff is an entity & 0.70 & 1.000000 & 0.46 & 40,727 \\
+ & Money judgment & 1890.34 & 0.000000 & 5279.49 & 40,727 \\
+\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 9435708.78 & 775,200.000000 & 20612629.31 & 14,491 \\
+ & Building value & 2482603.38 & 190,000.000000 & 6470958.91 & 14,491 \\
+ & Land value & 113817.19 & 2,600.000000 & 536568.37 & 14,491 \\
+ & Other value & 12020146.88 & 1,067,000.000000 & 26285935.89 & 14,491 \\
+ & Units & 42.25 & 1.000000 & 112.87 & 14,491 \\
+\cline{1-6}
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 261462.86 & 213,270.600000 & 238040.64 & 9,842 \\
+ & Four years before latest docket date & 280243.32 & 225,065.750000 & 276051.45 & 9,968 \\
+ & Three years before latest docket date & 307137.16 & 240,097.375000 & 369763.53 & 10,172 \\
+ & Two years before latest docket date & 341084.08 & 259,176.000000 & 987145.51 & 10,182 \\
+ & One year before latest docket date & 351172.05 & 278,722.250000 & 311982.74 & 10,190 \\
+ & Latest docket date & 377384.02 & 305,144.000000 & 316645.29 & 10,096 \\
+ & One year after latest docket date & 421601.75 & 347,550.000000 & 344328.86 & 10,443 \\
+ & Two years after latest docket date & 477948.08 & 393,900.000000 & 457694.83 & 9,175 \\
+ & Three years after latest docket date & 501611.80 & 414,600.000000 & 780467.01 & 5,894 \\
+\cline{1-6}
 \bottomrule

### 2022-12-31 src/01_build/05_merge.py

@@ -85,6 +85,9 @@ merged_df = merged_df.loc[~merged_df['property_address_full'].str.contains("span
 # Drop addresses without ZIP codes.
 merged_df = merged_df.loc[merged_df['property_address_zip'].notna(), :]
 
+# Rename duration to case_duration.
+merged_df = merged_df.rename(columns={'duration': 'case_duration'})
+
 # Save unrestricted data file.
 merged_df.to_csv(OUTPUT_DATA_UNRESTRICTED, index=False)
 

### 2022-12-31 output/summary_statistics/tables/balance_table.tex
Added median to summary statistics

--- 2022-12-25 output/summary_statistics/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 4090 & 0.12 & 11921 \\
- & For cause (transfer) & 0.01 & 4090 & 0.01 & 11921 \\
- & Foreclosure & 0.01 & 4090 & 0.03 & 11921 \\
- & Foreclosure (transfer) & 0.00 & 4090 & 0.00 & 11921 \\
- & No cause & 0.12 & 4090 & 0.10 & 11921 \\
- & No cause (transfer) & 0.01 & 4090 & 0.00 & 11921 \\
- & Non-payment of rent & 0.69 & 4090 & 0.72 & 11921 \\
- & Non-payment of rent (transfer) & 0.03 & 4090 & 0.01 & 11921 \\
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 4082 & 0.12 & 11912 \\
+ & For cause (transfer) & 0.01 & 4082 & 0.01 & 11912 \\
+ & Foreclosure & 0.01 & 4082 & 0.03 & 11912 \\
+ & Foreclosure (transfer) & 0.00 & 4082 & 0.00 & 11912 \\
+ & No cause & 0.12 & 4082 & 0.10 & 11912 \\
+ & No cause (transfer) & 0.01 & 4082 & 0.00 & 11912 \\
+ & Non-payment of rent & 0.69 & 4082 & 0.72 & 11912 \\
+ & Non-payment of rent (transfer) & 0.03 & 4082 & 0.01 & 11912 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 4090 & 0.67 & 11921 \\
- & Case involuntarily dismissed & 0.99 & 4090 & 0.00 & 11921 \\
- & Case heard & 0.01 & 4090 & 0.19 & 11921 \\
- & Case mediated & 0.00 & 4090 & 0.00 & 11921 \\
+\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 97.63 & 4082 & 58.85 & 10273 \\
+ & Case defaulted & 0.00 & 4082 & 0.67 & 11912 \\
+ & Case involuntarily dismissed & 0.99 & 4082 & 0.00 & 11912 \\
+ & Case heard & 0.01 & 4082 & 0.19 & 11912 \\
+ & Case mediated & 0.00 & 4082 & 0.00 & 11912 \\
 \cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.20 & 4090 & 0.07 & 11921 \\
- & Plaintiff has an attorney & 0.79 & 4090 & 0.81 & 11921 \\
- & Defendant is an entity & 0.01 & 4090 & 0.01 & 11921 \\
- & Plaintiff is an entity & 0.63 & 4090 & 0.67 & 11921 \\
- & Money judgment & 57.56 & 4090 & 3444.31 & 11921 \\
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.20 & 4082 & 0.07 & 11912 \\
+ & Plaintiff has an attorney & 0.79 & 4082 & 0.81 & 11912 \\
+ & Defendant is an entity & 0.01 & 4082 & 0.01 & 11912 \\
+ & Plaintiff is an entity & 0.63 & 4082 & 0.67 & 11912 \\
+ & Money judgment & 57.67 & 4082 & 3440.73 & 11912 \\
 \cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 1256 & 8995455.63 & 3992 \\
- & Building value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
- & Land value & 61247.49 & 1256 & 100993.11 & 3992 \\
- & Other value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
- & Units & 41.23 & 1256 & 42.09 & 3992 \\
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 1256 & 8997593.33 & 3991 \\
+ & Building value & 1605427.57 & 1256 & 2352903.60 & 3991 \\
+ & Land value & 61247.49 & 1256 & 101018.42 & 3991 \\
+ & Other value & 8138231.73 & 1256 & 11440367.23 & 3991 \\
+ & Units & 41.23 & 1256 & 42.10 & 3991 \\
 \cline{1-6}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 245078.62 & 957 & 275426.28 & 2603 \\
- & Four years before latest docket date & 265248.64 & 977 & 294572.61 & 2635 \\
- & Three years before latest docket date & 308529.26 & 992 & 317382.82 & 2706 \\
- & Two years before latest docket date & 330329.21 & 998 & 346565.14 & 2709 \\
- & One year before latest docket date & 336544.68 & 1002 & 364931.93 & 2715 \\
- & Latest docket date & 364629.48 & 991 & 391919.00 & 2701 \\
- & One year after latest docket date & 412421.05 & 1045 & 440748.11 & 2796 \\
- & Two years after latest docket date & 450898.44 & 801 & 509321.48 & 2493 \\
- & Three years after latest docket date & 485688.38 & 441 & 512215.31 & 1613 \\
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 255719.80 & 1018 & 267442.86 & 2901 \\
+ & Four years before latest docket date & 278556.70 & 1034 & 285983.57 & 2936 \\
+ & Three years before latest docket date & 297696.16 & 1051 & 312711.10 & 3012 \\
+ & Two years before latest docket date & 332887.98 & 1054 & 339939.67 & 3013 \\
+ & One year before latest docket date & 338734.41 & 1057 & 359532.30 & 3015 \\
+ & Latest docket date & 373978.71 & 1043 & 385699.20 & 2990 \\
+ & One year after latest docket date & 419565.10 & 1085 & 431037.20 & 3084 \\
+ & Two years after latest docket date & 446321.14 & 823 & 490315.74 & 2723 \\
+ & Three years after latest docket date & 482787.35 & 454 & 507050.53 & 1791 \\
 \cline{1-6}

### 2022-12-31 output/summary_statistics/tables/summary_statistics.tex
Added median to summary statistics

--- 2022-12-25 output/summary_statistics/tables/summary_statistics.tex
@@
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.32 & 40,735 \\
- & For cause (transfer) & 0.01 & 0.08 & 40,735 \\
- & Foreclosure & 0.02 & 0.14 & 40,735 \\
- & Foreclosure (transfer) & 0.00 & 0.03 & 40,735 \\
- & No cause & 0.10 & 0.30 & 40,735 \\
- & No cause (transfer) & 0.01 & 0.08 & 40,735 \\
- & Non-payment of rent & 0.73 & 0.44 & 40,735 \\
- & Non-payment of rent (transfer) & 0.02 & 0.13 & 40,735 \\
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.32 & 40,727 \\
+ & For cause (transfer) & 0.01 & 0.08 & 40,727 \\
+ & Foreclosure & 0.02 & 0.14 & 40,727 \\
+ & Foreclosure (transfer) & 0.00 & 0.03 & 40,727 \\
+ & No cause & 0.10 & 0.30 & 40,727 \\
+ & No cause (transfer) & 0.01 & 0.08 & 40,727 \\
+ & Non-payment of rent & 0.73 & 0.44 & 40,727 \\
+ & Non-payment of rent (transfer) & 0.02 & 0.13 & 40,727 \\
 \cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,735 \\
- & Case involuntarily dismissed & 0.29 & 0.45 & 40,735 \\
- & Case heard & 0.06 & 0.23 & 40,735 \\
- & Case mediated & 0.41 & 0.49 & 40,735 \\
+\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 57.81 & 78.29 & 39,087 \\
+ & Case defaulted & 0.20 & 0.40 & 40,727 \\
+ & Case involuntarily dismissed & 0.29 & 0.45 & 40,727 \\
+ & Case heard & 0.06 & 0.23 & 40,727 \\
+ & Case mediated & 0.41 & 0.49 & 40,727 \\
 \cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,735 \\
- & Plaintiff has an attorney & 0.84 & 0.37 & 40,735 \\
- & Defendant is an entity & 0.01 & 0.08 & 40,735 \\
- & Plaintiff is an entity & 0.70 & 0.46 & 40,735 \\
- & Money judgment & 1890.04 & 5279.02 & 40,735 \\
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,727 \\
+ & Plaintiff has an attorney & 0.84 & 0.37 & 40,727 \\
+ & Defendant is an entity & 0.01 & 0.08 & 40,727 \\
+ & Plaintiff is an entity & 0.70 & 0.46 & 40,727 \\
+ & Money judgment & 1890.34 & 5279.49 & 40,727 \\
 \cline{1-5}
@@
 \cline{1-5}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 261403.18 & 249286.93 & 8,865 \\
- & Four years before latest docket date & 280115.12 & 286856.77 & 8,994 \\
- & Three years before latest docket date & 306539.18 & 377212.67 & 9,198 \\
- & Two years before latest docket date & 341425.83 & 1033374.53 & 9,210 \\
- & One year before latest docket date & 350912.11 & 314096.19 & 9,217 \\
- & Latest docket date & 376241.94 & 315819.32 & 9,129 \\
- & One year after latest docket date & 421391.90 & 347409.45 & 9,476 \\
- & Two years after latest docket date & 478657.38 & 468642.16 & 8,363 \\
- & Three years after latest docket date & 503342.65 & 795669.13 & 5,368 \\
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 261462.86 & 238040.64 & 9,842 \\
+ & Four years before latest docket date & 280243.32 & 276051.45 & 9,968 \\
+ & Three years before latest docket date & 307137.16 & 369763.53 & 10,172 \\
+ & Two years before latest docket date & 341084.08 & 987145.51 & 10,182 \\
+ & One year before latest docket date & 351172.05 & 311982.74 & 10,190 \\
+ & Latest docket date & 377384.02 & 316645.29 & 10,096 \\
+ & One year after latest docket date & 421601.75 & 344328.86 & 10,443 \\
+ & Two years after latest docket date & 477948.08 & 457694.83 & 9,175 \\
+ & Three years after latest docket date & 501611.80 & 780467.01 & 5,894 \\
 \cline{1-5}

### 2022-12-31 output/summary_statistics/tables/balance_table.tex
Added median to summary statistics

--- 2022-12-28 output/summary_statistics/tables/balance_table.tex
@@
 \toprule
- &  & \multicolumn{2}{c}{\textit{Cases Won by Defendant}} & \multicolumn{2}{c}{\textit{Cases Won by Plaintiff}} \\
- &  & Mean & N & Mean & N \\
-Panel & Variable &  &  &  &  \\
+ &  & \multicolumn{3}{c}{\textit{Cases Won by Defendant}} & \multicolumn{3}{c}{\textit{Cases Won by Plaintiff}} \\
+ &  & 50% & Mean & N & 50% & Mean & N \\
+Panel & Variable &  &  &  &  &  &  \\
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 4090 & 0.12 & 11921 \\
- & For cause (transfer) & 0.01 & 4090 & 0.01 & 11921 \\
- & Foreclosure & 0.01 & 4090 & 0.03 & 11921 \\
- & Foreclosure (transfer) & 0.00 & 4090 & 0.00 & 11921 \\
- & No cause & 0.12 & 4090 & 0.10 & 11921 \\
- & No cause (transfer) & 0.01 & 4090 & 0.00 & 11921 \\
- & Non-payment of rent & 0.69 & 4090 & 0.72 & 11921 \\
- & Non-payment of rent (transfer) & 0.03 & 4090 & 0.01 & 11921 \\
-\cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 4090 & 0.67 & 11921 \\
- & Case involuntarily dismissed & 0.99 & 4090 & 0.00 & 11921 \\
- & Case heard & 0.01 & 4090 & 0.19 & 11921 \\
- & Case mediated & 0.00 & 4090 & 0.00 & 11921 \\
-\cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.20 & 4090 & 0.07 & 11921 \\
- & Plaintiff has an attorney & 0.79 & 4090 & 0.81 & 11921 \\
- & Defendant is an entity & 0.01 & 4090 & 0.01 & 11921 \\
- & Plaintiff is an entity & 0.63 & 4090 & 0.67 & 11921 \\
- & Money judgment & 57.56 & 4090 & 3444.31 & 11921 \\
-\cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 1256 & 8995455.63 & 3992 \\
- & Building value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
- & Land value & 61247.49 & 1256 & 100993.11 & 3992 \\
- & Other value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
- & Units & 41.23 & 1256 & 42.09 & 3992 \\
-\cline{1-6}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 255601.88 & 1019 & 267829.81 & 2904 \\
- & Four years before latest docket date & 278440.18 & 1035 & 286996.41 & 2939 \\
- & Three years before latest docket date & 297578.04 & 1052 & 313182.84 & 3015 \\
- & Two years before latest docket date & 332743.89 & 1055 & 341145.74 & 3016 \\
- & One year before latest docket date & 338598.45 & 1058 & 360142.85 & 3018 \\
- & Latest docket date & 373816.17 & 1044 & 387035.91 & 2993 \\
- & One year after latest docket date & 419391.34 & 1086 & 431642.67 & 3087 \\
- & Two years after latest docket date & 446124.50 & 824 & 491836.71 & 2726 \\
- & Three years after latest docket date & 482504.08 & 455 & 508987.34 & 1793 \\
-\cline{1-6}
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.000000 & 0.12 & 4082 & 0.000000 & 0.12 & 11912 \\
+ & For cause (transfer) & 0.000000 & 0.01 & 4082 & 0.000000 & 0.01 & 11912 \\
+ & Foreclosure & 0.000000 & 0.01 & 4082 & 0.000000 & 0.03 & 11912 \\
+ & Foreclosure (transfer) & 0.000000 & 0.00 & 4082 & 0.000000 & 0.00 & 11912 \\
+ & No cause & 0.000000 & 0.12 & 4082 & 0.000000 & 0.10 & 11912 \\
+ & No cause (transfer) & 0.000000 & 0.01 & 4082 & 0.000000 & 0.00 & 11912 \\
+ & Non-payment of rent & 1.000000 & 0.69 & 4082 & 1.000000 & 0.72 & 11912 \\
+ & Non-payment of rent (transfer) & 0.000000 & 0.03 & 4082 & 0.000000 & 0.01 & 11912 \\
+\cline{1-8}
+\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 61.000000 & 97.63 & 4082 & 20.000000 & 58.85 & 10273 \\
+ & Case defaulted & 0.000000 & 0.00 & 4082 & 1.000000 & 0.67 & 11912 \\
+ & Case involuntarily dismissed & 1.000000 & 0.99 & 4082 & 0.000000 & 0.00 & 11912 \\
+ & Case heard & 0.000000 & 0.01 & 4082 & 0.000000 & 0.19 & 11912 \\
+ & Case mediated & 0.000000 & 0.00 & 4082 & 0.000000 & 0.00 & 11912 \\
+\cline{1-8}
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.000000 & 0.20 & 4082 & 0.000000 & 0.07 & 11912 \\
+ & Plaintiff has an attorney & 1.000000 & 0.79 & 4082 & 1.000000 & 0.81 & 11912 \\
+ & Defendant is an entity & 0.000000 & 0.01 & 4082 & 0.000000 & 0.01 & 11912 \\
+ & Plaintiff is an entity & 1.000000 & 0.63 & 4082 & 1.000000 & 0.67 & 11912 \\
+ & Money judgment & 0.000000 & 57.67 & 4082 & 1,310.940000 & 3440.73 & 11912 \\
+\cline{1-8}
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 641,200.000000 & 6478531.48 & 1256 & 579,400.000000 & 8997593.33 & 3991 \\
+ & Building value & 169,600.000000 & 1605427.57 & 1256 & 161,000.000000 & 2352903.60 & 3991 \\
+ & Land value & 1,100.000000 & 61247.49 & 1256 & 2,100.000000 & 101018.42 & 3991 \\
+ & Other value & 823,450.000000 & 8138231.73 & 1256 & 808,100.000000 & 11440367.23 & 3991 \\
+ & Units & 2.000000 & 41.23 & 1256 & 1.000000 & 42.10 & 3991 \\
+\cline{1-8}
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 185,330.500000 & 255719.80 & 1018 & 218,825.000000 & 267442.86 & 2901 \\
+ & Four years before latest docket date & 195,892.500000 & 278556.70 & 1034 & 228,526.000000 & 285983.57 & 2936 \\
+ & Three years before latest docket date & 210,030.000000 & 297696.16 & 1051 & 244,821.500000 & 312711.10 & 3012 \\
+ & Two years before latest docket date & 223,501.000000 & 332887.98 & 1054 & 264,659.000000 & 339939.67 & 3013 \\
+ & One year before latest docket date & 240,000.000000 & 338734.41 & 1057 & 285,032.000000 & 359532.30 & 3015 \\
+ & Latest docket date & 270,184.000000 & 373978.71 & 1043 & 313,104.500000 & 385699.20 & 2990 \\
+ & One year after latest docket date & 317,500.000000 & 419565.10 & 1085 & 354,320.000000 & 431037.20 & 3084 \\
+ & Two years after latest docket date & 348,300.000000 & 446321.14 & 823 & 404,600.000000 & 490315.74 & 2723 \\
+ & Three years after latest docket date & 363,650.000000 & 482787.35 & 454 & 419,600.000000 & 507050.53 & 1791 \\
+\cline{1-8}
 \bottomrule

### 2022-12-31 output/summary_statistics/tables/summary_statistics.tex
Added median to summary statistics

--- 2022-12-28 output/summary_statistics/tables/summary_statistics.tex
@@
 \toprule
- &  & Mean & S.D. & N \\
-Panel & Variable &  &  &  \\
+ &  & 50% & Mean & S.D. & N \\
+Panel & Variable &  &  &  &  \\
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.32 & 40,735 \\
- & For cause (transfer) & 0.01 & 0.08 & 40,735 \\
- & Foreclosure & 0.02 & 0.14 & 40,735 \\
- & Foreclosure (transfer) & 0.00 & 0.03 & 40,735 \\
- & No cause & 0.10 & 0.30 & 40,735 \\
- & No cause (transfer) & 0.01 & 0.08 & 40,735 \\
- & Non-payment of rent & 0.73 & 0.44 & 40,735 \\
- & Non-payment of rent (transfer) & 0.02 & 0.13 & 40,735 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,735 \\
- & Case involuntarily dismissed & 0.29 & 0.45 & 40,735 \\
- & Case heard & 0.06 & 0.23 & 40,735 \\
- & Case mediated & 0.41 & 0.49 & 40,735 \\
-\cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,735 \\
- & Plaintiff has an attorney & 0.84 & 0.37 & 40,735 \\
- & Defendant is an entity & 0.01 & 0.08 & 40,735 \\
- & Plaintiff is an entity & 0.70 & 0.46 & 40,735 \\
- & Money judgment & 1890.04 & 5279.02 & 40,735 \\
-\cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 9435708.78 & 20612629.31 & 14,491 \\
- & Building value & 2482603.38 & 6470958.91 & 14,491 \\
- & Land value & 113817.19 & 536568.37 & 14,491 \\
- & Other value & 12020146.88 & 26285935.89 & 14,491 \\
- & Units & 42.25 & 112.87 & 14,491 \\
-\cline{1-5}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 261450.07 & 238031.93 & 9,843 \\
- & Four years before latest docket date & 280231.05 & 276040.32 & 9,969 \\
- & Three years before latest docket date & 307124.02 & 369747.73 & 10,173 \\
- & Two years before latest docket date & 341068.35 & 987098.31 & 10,183 \\
- & One year before latest docket date & 351156.71 & 311971.28 & 10,191 \\
- & Latest docket date & 377366.88 & 316634.29 & 10,097 \\
- & One year after latest docket date & 421583.49 & 344317.43 & 10,444 \\
- & Two years after latest docket date & 477926.97 & 457674.35 & 9,176 \\
- & Three years after latest docket date & 501586.74 & 780403.17 & 5,895 \\
-\cline{1-5}
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.000000 & 0.12 & 0.32 & 40,727 \\
+ & For cause (transfer) & 0.000000 & 0.01 & 0.08 & 40,727 \\
+ & Foreclosure & 0.000000 & 0.02 & 0.14 & 40,727 \\
+ & Foreclosure (transfer) & 0.000000 & 0.00 & 0.03 & 40,727 \\
+ & No cause & 0.000000 & 0.10 & 0.30 & 40,727 \\
+ & No cause (transfer) & 0.000000 & 0.01 & 0.08 & 40,727 \\
+ & Non-payment of rent & 1.000000 & 0.73 & 0.44 & 40,727 \\
+ & Non-payment of rent (transfer) & 0.000000 & 0.02 & 0.13 & 40,727 \\
+\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 21.000000 & 57.81 & 78.29 & 39,087 \\
+ & Case defaulted & 0.000000 & 0.20 & 0.40 & 40,727 \\
+ & Case involuntarily dismissed & 0.000000 & 0.29 & 0.45 & 40,727 \\
+ & Case heard & 0.000000 & 0.06 & 0.23 & 40,727 \\
+ & Case mediated & 0.000000 & 0.41 & 0.49 & 40,727 \\
+\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.000000 & 0.09 & 0.28 & 40,727 \\
+ & Plaintiff has an attorney & 1.000000 & 0.84 & 0.37 & 40,727 \\
+ & Defendant is an entity & 0.000000 & 0.01 & 0.08 & 40,727 \\
+ & Plaintiff is an entity & 1.000000 & 0.70 & 0.46 & 40,727 \\
+ & Money judgment & 0.000000 & 1890.34 & 5279.49 & 40,727 \\
+\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 775,200.000000 & 9435708.78 & 20612629.31 & 14,491 \\
+ & Building value & 190,000.000000 & 2482603.38 & 6470958.91 & 14,491 \\
+ & Land value & 2,600.000000 & 113817.19 & 536568.37 & 14,491 \\
+ & Other value & 1,067,000.000000 & 12020146.88 & 26285935.89 & 14,491 \\
+ & Units & 1.000000 & 42.25 & 112.87 & 14,491 \\
+\cline{1-6}
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 213,270.600000 & 261462.86 & 238040.64 & 9,842 \\
+ & Four years before latest docket date & 225,065.750000 & 280243.32 & 276051.45 & 9,968 \\
+ & Three years before latest docket date & 240,097.375000 & 307137.16 & 369763.53 & 10,172 \\
+ & Two years before latest docket date & 259,176.000000 & 341084.08 & 987145.51 & 10,182 \\
+ & One year before latest docket date & 278,722.250000 & 351172.05 & 311982.74 & 10,190 \\
+ & Latest docket date & 305,144.000000 & 377384.02 & 316645.29 & 10,096 \\
+ & One year after latest docket date & 347,550.000000 & 421601.75 & 344328.86 & 10,443 \\
+ & Two years after latest docket date & 393,900.000000 & 477948.08 & 457694.83 & 9,175 \\
+ & Three years after latest docket date & 414,600.000000 & 501611.80 & 780467.01 & 5,894 \\
+\cline{1-6}
 \bottomrule

### 2022-12-31 writing/paper/main.tex
Updates from Overleaf

@@
 \section{Introduction} \label{sec:introduction}
+\subsection{Literature Review}
 
-\section{Literature Review} \label{sec:literature}
-
+\section{Institutional Context}
+    \subsection{Eviction in Massachusetts}
+        \subsubsection{The Massachusetts Housing Court}
+        \subsubsection{The Eviction Process}
+    \subsubsection{Property Tax Assessment}
+        \subsubsection{The Property Value Assessment Process}
+    \subsection{Zestimates}
+        \subsubsection{How Are Zestimates Produced?}
+        \subsubsection{Reliability}
 \section{Data} \label{sec:data}
+    \begin{landscape}
     \subsection{Evictions Data}
+        \begin{figure}[H]
+            \centering
+            \includegraphics{output/summary_statistics/figures/evictions_map.png}
+            \caption{Spatial Incidence of Eviction}
+            \label{fig:my_label}
+        \end{figure}
+    \end{landscape}
     \subsection{Tax Assessment Records}
     \subsection{Zestimates}
+        \begin{figure}[H]
+            \centering
+            \includegraphics{output/summary_statistics/figures/trends_in_zestimates.png}
+            \caption{Trends in Zestimates}
+            \label{fig:my_label}
+        \end{figure}
+    \begin{landscape}
     \subsection{Summary Statistics}
-    \begin{landscape}
          \begin{table}[H]
             \centering
+            \tiny
             \input{output/summary_statistics/tables/summary_statistics.tex}
-            \caption{Caption}
+            \caption{Summary Statistics}
+            \label{tab:table_1}
+        \end{table}
+        \newpage
+        \begin{table}[H]
+            \centering
+            \tiny
+            \input{output/summary_statistics/tables/balance_table.tex}
+            \caption{Balance Table}
             \label{tab:my_label}
         \end{table}
-
     \end{landscape}
 
+\section{Empirical Strategy: Difference-in-Difference}
+    \subsection{Estimating the ATT in the Staggered Treatment Case}
+    I will use Callaway and Sant'Anna' (2021)'s multiperiod, staggered treatment difference-in-difference estimators.
+The following bullets summarize the empirical strategy informally; this information will eventually be placed appropriately into the subsection headers below this brief summary.
+    \begin{enumerate}
+        \item Reject conventional TWFE-DiD estimator.
+This estimator essentially estimates the ATT by performing a bunch of 2 unit, 2 period DiDs, then averages the calculated treatment effects.
+Goodman-Bacon (2021) shows that this estimator is composed in part of DiD estimates involving \emph{two units which are both treated during both periods}.
+This is in violation of the spirit of DiD.
+These incorrect DiD estimates are known as ``forbidden comparisons.''
+        \item The way to properly recover the ATT is to basically perform all of the ``non-forbidden'' comparisons possible in our panel dataset. More formally:
+        \begin{enumerate}
+            \item We begin with a panel dataset of properties whose Zestimates are observed monthly.
+At each property $i$, an eviction case concludes during month $G_i=g$, resulting in a plaintiff victory or a defendant victory.
+These properties are collectively known as ``cohort $g$.'' If the eviction case at property $i$ resulted in a defendant victory, let $C_i=1$
+            \item Break the units into ``cohorts'' according to the month in which their cases conclude. 
+            \item We estimate $ATT(g, t)$, which is the average treatment effect on the treated for cohort $g$ at time $t$, by calculating the sample analog of:
+
+            $E[Y_t - Y_{g-1}|G=g] - [Y_t - Y_{g-1}|C=1]$
+
+            \item Intuitively, $ATT(g, t)$ comes from 2 period, 2 unit difference in difference estimate.
+The treatment group contains all units where we observe a plaintiff victory and the case was resolved at time $g$.
+The control group contains all units where we observe a defendant victory and the case was resolved at time $g$.
+We adjust the change in observed outcomes in the treatment group by the change in observed outcomes in the control group to get our estimate.
+
+        \end{enumerate}
+        \item The parallel trends and no anticipation assumptions are extended to the staggered treatment context.
+            \begin{enumerate}
+                \item \textbf{Staggered Treatment Adoption Assumption.} Let $D_it=1$ if unit $i$ has been treated by period $t$ and $D_it=0$ otherwise.
+Then, for $t=1,...,\tau$, $D_{it}=1 \rightarrow D_{it+1} = 1$.
+Basically, once a unit becomes treated, it stays treated.
+
+                \item \textbf{Parallel Trends Assumption Based On Never Treated Units}. For all $g=2,...,\tau, t=2,...,\tau$ with $t\geq g$, we have
+
+                $E[Y_t(0)-Y_{g-1}(0)|G=g]$ = $E[Y_t(0)-Y_{g-1}(0)|C=1]$
+
+                Basically, for every possible 2 unit, 2 period DiD that we can run in our panel dataset between treated units and never-treated units, the canonical parallel trends assumption holds.
+
+                \item \textbf{Parallel Trends Assumption Based On Not Yet Treated Units}. For all $g=2,...,\tau, s, t=2,...,\tau$ with $t \geq g$ and $s \geq t$, we have
+
+                $E[Y_t(0) - Y_{t-1}(0)|G=g] = E[Y_t(0) - Y_{t-1}(0)|D_s=1, G \neq g]$
+
+                This assumption allows us to use \emph{not yet treated} observations as a comparison group for \emph{treated} units.
+This is clearly a stronger assumption than the previous one and I have to think hard about whether I can make it in my case.
+Note that the graph in section 5.3 does NOT make this assumption.
+
+            \end{enumerate}
+        \item Now, we have a bunch of $ATT(g, t)$s. How do we aggregate them?
+            \begin{enumerate}
+                \item Take frequency-weighted averages across $t$ to get $ATT(g)$s, or ATTs for each cohort.
+                \item Take frequency-weighted averages across $g$ to get $ATT(t)$s, or ATTs for each time period.
+                \item Most convincing: calculate event time $e = t - g$.
+Now, $ATT(g, e_i)$ expresses the ATT on cohort $g$ at time relative to the end of the eviction case involving property $i$.
+Take frequency weighted averages across $g$ to get $ATT(e)s$, or ATTs for each period relative to the treatment period.
+            \end{enumerate}
+    \end{enumerate}
+    \subsection{Parallel Trends Assumptions in the Staggered Treatment Case}
+
+        \subsection{Testing Parallel Trends Empirically Using Rambachan and Roth (2022)}
+    \subsection{Aggregating Treatment Effects Across Cohort and Time}
+        \subsubsection{ATTs Across Cohorts}
+        \subsubsection{ATTs Across Time Periods}
+        \subsubsection{Event-Study ATTs}
+
 \section{Results} \label{sec:result}
-
-\section{Discussions} \label{sec:discussion}
+    \subsection{ATTs Across Cohorts}
+    \subsection{ATTs Across Time Periods}
+    \subsection{Event-Study ATTs}
+        \begin{figure}[H]
+            \centering
+            \includegraphics{output/DiD/figures/att_gt_estimates_event_study.png}
+            \caption{$ATT(e)$s}
+            \label{fig:my_label}
+        \end{figure}
 
@@
 
-\section*{Tables} \label{sec:tab}
-\addcontentsline{toc}{section}{Tables}
+% \section*{Tables} \label{sec:tab}
+% \addcontentsline{toc}{section}{Tables}
 
-\clearpage
+% \clearpage
 
-\section*{Figures} \label{sec:fig}
-\addcontentsline{toc}{section}{Figures}
+% \section*{Figures} \label{sec:fig}
+% \addcontentsline{toc}{section}{Figures}
 
-\clearpage
+% \clearpage
 
-\section*{Appendix A. Placeholder} \label{sec:appendixa}
-\addcontentsline{toc}{section}{Appendix A}
+% \section*{Appendix A. Placeholder} \label{sec:appendixa}
+% \addcontentsline{toc}{section}{Appendix A}
 

### 2022-12-31 output/summary_statistics/tables/balance_table.tex
Added median to summary statistics

@@
  &  & \multicolumn{3}{c}{\textit{Cases Won by Defendant}} & \multicolumn{3}{c}{\textit{Cases Won by Plaintiff}} \\
- &  & 50% & Mean & N & 50% & Mean & N \\
+ &  & Median & Mean & N & Median & Mean & N \\
 Panel & Variable &  &  &  &  &  &  \\

### 2022-12-31 output/summary_statistics/tables/balance_table.tex
Added median to summary statistics

--- 2022-12-31 output/summary_statistics/tables/balance_table.tex
@@
 \toprule
- &  & \multicolumn{2}{c}{\textit{Cases Won by Defendant}} & \multicolumn{2}{c}{\textit{Cases Won by Plaintiff}} \\
- &  & Mean & N & Mean & N \\
-Panel & Variable &  &  &  &  \\
+ &  & \multicolumn{3}{c}{\textit{Cases Won by Defendant}} & \multicolumn{3}{c}{\textit{Cases Won by Plaintiff}} \\
+ &  & Median & Mean & N & Median & Mean & N \\
+Panel & Variable &  &  &  &  &  &  \\
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 4082 & 0.12 & 11912 \\
- & For cause (transfer) & 0.01 & 4082 & 0.01 & 11912 \\
- & Foreclosure & 0.01 & 4082 & 0.03 & 11912 \\
- & Foreclosure (transfer) & 0.00 & 4082 & 0.00 & 11912 \\
- & No cause & 0.12 & 4082 & 0.10 & 11912 \\
- & No cause (transfer) & 0.01 & 4082 & 0.00 & 11912 \\
- & Non-payment of rent & 0.69 & 4082 & 0.72 & 11912 \\
- & Non-payment of rent (transfer) & 0.03 & 4082 & 0.01 & 11912 \\
-\cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 97.63 & 4082 & 58.85 & 10273 \\
- & Case defaulted & 0.00 & 4082 & 0.67 & 11912 \\
- & Case involuntarily dismissed & 0.99 & 4082 & 0.00 & 11912 \\
- & Case heard & 0.01 & 4082 & 0.19 & 11912 \\
- & Case mediated & 0.00 & 4082 & 0.00 & 11912 \\
-\cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.20 & 4082 & 0.07 & 11912 \\
- & Plaintiff has an attorney & 0.79 & 4082 & 0.81 & 11912 \\
- & Defendant is an entity & 0.01 & 4082 & 0.01 & 11912 \\
- & Plaintiff is an entity & 0.63 & 4082 & 0.67 & 11912 \\
- & Money judgment & 57.67 & 4082 & 3440.73 & 11912 \\
-\cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 1256 & 8997593.33 & 3991 \\
- & Building value & 1605427.57 & 1256 & 2352903.60 & 3991 \\
- & Land value & 61247.49 & 1256 & 101018.42 & 3991 \\
- & Other value & 8138231.73 & 1256 & 11440367.23 & 3991 \\
- & Units & 41.23 & 1256 & 42.10 & 3991 \\
-\cline{1-6}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 255719.80 & 1018 & 267442.86 & 2901 \\
- & Four years before latest docket date & 278556.70 & 1034 & 285983.57 & 2936 \\
- & Three years before latest docket date & 297696.16 & 1051 & 312711.10 & 3012 \\
- & Two years before latest docket date & 332887.98 & 1054 & 339939.67 & 3013 \\
- & One year before latest docket date & 338734.41 & 1057 & 359532.30 & 3015 \\
- & Latest docket date & 373978.71 & 1043 & 385699.20 & 2990 \\
- & One year after latest docket date & 419565.10 & 1085 & 431037.20 & 3084 \\
- & Two years after latest docket date & 446321.14 & 823 & 490315.74 & 2723 \\
- & Three years after latest docket date & 482787.35 & 454 & 507050.53 & 1791 \\
-\cline{1-6}
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.00 & 0.12 & 4082 & 0.00 & 0.12 & 11912 \\
+ & For cause (transfer) & 0.00 & 0.01 & 4082 & 0.00 & 0.01 & 11912 \\
+ & Foreclosure & 0.00 & 0.01 & 4082 & 0.00 & 0.03 & 11912 \\
+ & Foreclosure (transfer) & 0.00 & 0.00 & 4082 & 0.00 & 0.00 & 11912 \\
+ & No cause & 0.00 & 0.12 & 4082 & 0.00 & 0.10 & 11912 \\
+ & No cause (transfer) & 0.00 & 0.01 & 4082 & 0.00 & 0.00 & 11912 \\
+ & Non-payment of rent & 1.00 & 0.69 & 4082 & 1.00 & 0.72 & 11912 \\
+ & Non-payment of rent (transfer) & 0.00 & 0.03 & 4082 & 0.00 & 0.01 & 11912 \\
+\cline{1-8}
+\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 61.00 & 97.63 & 4082 & 20.00 & 58.85 & 10273 \\
+ & Case defaulted & 0.00 & 0.00 & 4082 & 1.00 & 0.67 & 11912 \\
+ & Case involuntarily dismissed & 1.00 & 0.99 & 4082 & 0.00 & 0.00 & 11912 \\
+ & Case heard & 0.00 & 0.01 & 4082 & 0.00 & 0.19 & 11912 \\
+ & Case mediated & 0.00 & 0.00 & 4082 & 0.00 & 0.00 & 11912 \\
+\cline{1-8}
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.00 & 0.20 & 4082 & 0.00 & 0.07 & 11912 \\
+ & Plaintiff has an attorney & 1.00 & 0.79 & 4082 & 1.00 & 0.81 & 11912 \\
+ & Defendant is an entity & 0.00 & 0.01 & 4082 & 0.00 & 0.01 & 11912 \\
+ & Plaintiff is an entity & 1.00 & 0.63 & 4082 & 1.00 & 0.67 & 11912 \\
+ & Money judgment & 0.00 & 57.67 & 4082 & 1310.94 & 3440.73 & 11912 \\
+\cline{1-8}
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 641200.00 & 6478531.48 & 1256 & 579400.00 & 8997593.33 & 3991 \\
+ & Building value & 169600.00 & 1605427.57 & 1256 & 161000.00 & 2352903.60 & 3991 \\
+ & Land value & 1100.00 & 61247.49 & 1256 & 2100.00 & 101018.42 & 3991 \\
+ & Other value & 823450.00 & 8138231.73 & 1256 & 808100.00 & 11440367.23 & 3991 \\
+ & Units & 2.00 & 41.23 & 1256 & 1.00 & 42.10 & 3991 \\
+\cline{1-8}
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 185330.50 & 255719.80 & 1018 & 218825.00 & 267442.86 & 2901 \\
+ & Four years before latest docket date & 195892.50 & 278556.70 & 1034 & 228526.00 & 285983.57 & 2936 \\
+ & Three years before latest docket date & 210030.00 & 297696.16 & 1051 & 244821.50 & 312711.10 & 3012 \\
+ & Two years before latest docket date & 223501.00 & 332887.98 & 1054 & 264659.00 & 339939.67 & 3013 \\
+ & One year before latest docket date & 240000.00 & 338734.41 & 1057 & 285032.00 & 359532.30 & 3015 \\
+ & Latest docket date & 270184.00 & 373978.71 & 1043 & 313104.50 & 385699.20 & 2990 \\
+ & One year after latest docket date & 317500.00 & 419565.10 & 1085 & 354320.00 & 431037.20 & 3084 \\
+ & Two years after latest docket date & 348300.00 & 446321.14 & 823 & 404600.00 & 490315.74 & 2723 \\
+ & Three years after latest docket date & 363650.00 & 482787.35 & 454 & 419600.00 & 507050.53 & 1791 \\
+\cline{1-8}
 \bottomrule

### 2022-12-31 output/summary_statistics/tables/summary_statistics.tex
Added median to summary statistics

--- 2022-12-31 output/summary_statistics/tables/summary_statistics.tex
@@
 \toprule
- &  & Mean & S.D. & N \\
-Panel & Variable &  &  &  \\
+ &  & Median & Mean & S.D. & N \\
+Panel & Variable &  &  &  &  \\
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.32 & 40,727 \\
- & For cause (transfer) & 0.01 & 0.08 & 40,727 \\
- & Foreclosure & 0.02 & 0.14 & 40,727 \\
- & Foreclosure (transfer) & 0.00 & 0.03 & 40,727 \\
- & No cause & 0.10 & 0.30 & 40,727 \\
- & No cause (transfer) & 0.01 & 0.08 & 40,727 \\
- & Non-payment of rent & 0.73 & 0.44 & 40,727 \\
- & Non-payment of rent (transfer) & 0.02 & 0.13 & 40,727 \\
-\cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 57.81 & 78.29 & 39,087 \\
- & Case defaulted & 0.20 & 0.40 & 40,727 \\
- & Case involuntarily dismissed & 0.29 & 0.45 & 40,727 \\
- & Case heard & 0.06 & 0.23 & 40,727 \\
- & Case mediated & 0.41 & 0.49 & 40,727 \\
-\cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,727 \\
- & Plaintiff has an attorney & 0.84 & 0.37 & 40,727 \\
- & Defendant is an entity & 0.01 & 0.08 & 40,727 \\
- & Plaintiff is an entity & 0.70 & 0.46 & 40,727 \\
- & Money judgment & 1890.34 & 5279.49 & 40,727 \\
-\cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 9435708.78 & 20612629.31 & 14,491 \\
- & Building value & 2482603.38 & 6470958.91 & 14,491 \\
- & Land value & 113817.19 & 536568.37 & 14,491 \\
- & Other value & 12020146.88 & 26285935.89 & 14,491 \\
- & Units & 42.25 & 112.87 & 14,491 \\
-\cline{1-5}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 261462.86 & 238040.64 & 9,842 \\
- & Four years before latest docket date & 280243.32 & 276051.45 & 9,968 \\
- & Three years before latest docket date & 307137.16 & 369763.53 & 10,172 \\
- & Two years before latest docket date & 341084.08 & 987145.51 & 10,182 \\
- & One year before latest docket date & 351172.05 & 311982.74 & 10,190 \\
- & Latest docket date & 377384.02 & 316645.29 & 10,096 \\
- & One year after latest docket date & 421601.75 & 344328.86 & 10,443 \\
- & Two years after latest docket date & 477948.08 & 457694.83 & 9,175 \\
- & Three years after latest docket date & 501611.80 & 780467.01 & 5,894 \\
-\cline{1-5}
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.00 & 0.12 & 0.32 & 40,727 \\
+ & For cause (transfer) & 0.00 & 0.01 & 0.08 & 40,727 \\
+ & Foreclosure & 0.00 & 0.02 & 0.14 & 40,727 \\
+ & Foreclosure (transfer) & 0.00 & 0.00 & 0.03 & 40,727 \\
+ & No cause & 0.00 & 0.10 & 0.30 & 40,727 \\
+ & No cause (transfer) & 0.00 & 0.01 & 0.08 & 40,727 \\
+ & Non-payment of rent & 1.00 & 0.73 & 0.44 & 40,727 \\
+ & Non-payment of rent (transfer) & 0.00 & 0.02 & 0.13 & 40,727 \\
+\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 21.00 & 57.81 & 78.29 & 39,087 \\
+ & Case defaulted & 0.00 & 0.20 & 0.40 & 40,727 \\
+ & Case involuntarily dismissed & 0.00 & 0.29 & 0.45 & 40,727 \\
+ & Case heard & 0.00 & 0.06 & 0.23 & 40,727 \\
+ & Case mediated & 0.00 & 0.41 & 0.49 & 40,727 \\
+\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.00 & 0.09 & 0.28 & 40,727 \\
+ & Plaintiff has an attorney & 1.00 & 0.84 & 0.37 & 40,727 \\
+ & Defendant is an entity & 0.00 & 0.01 & 0.08 & 40,727 \\
+ & Plaintiff is an entity & 1.00 & 0.70 & 0.46 & 40,727 \\
+ & Money judgment & 0.00 & 1890.34 & 5279.49 & 40,727 \\
+\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 775200.00 & 9435708.78 & 20612629.31 & 14,491 \\
+ & Building value & 190000.00 & 2482603.38 & 6470958.91 & 14,491 \\
+ & Land value & 2600.00 & 113817.19 & 536568.37 & 14,491 \\
+ & Other value & 1067000.00 & 12020146.88 & 26285935.89 & 14,491 \\
+ & Units & 1.00 & 42.25 & 112.87 & 14,491 \\
+\cline{1-6}
+\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 213270.60 & 261462.86 & 238040.64 & 9,842 \\
+ & Four years before latest docket date & 225065.75 & 280243.32 & 276051.45 & 9,968 \\
+ & Three years before latest docket date & 240097.38 & 307137.16 & 369763.53 & 10,172 \\
+ & Two years before latest docket date & 259176.00 & 341084.08 & 987145.51 & 10,182 \\
+ & One year before latest docket date & 278722.25 & 351172.05 & 311982.74 & 10,190 \\
+ & Latest docket date & 305144.00 & 377384.02 & 316645.29 & 10,096 \\
+ & One year after latest docket date & 347550.00 & 421601.75 & 344328.86 & 10,443 \\
+ & Two years after latest docket date & 393900.00 & 477948.08 & 457694.83 & 9,175 \\
+ & Three years after latest docket date & 414600.00 & 501611.80 & 780467.01 & 5,894 \\
+\cline{1-6}
 \bottomrule

### 2023-01-03 output/summary_statistics/tables/summary_statistics.tex
Added median to summary statistics
Created treatment timing table

@@
-\begin{tabular}{llccc}
+\begin{tabular}{llcccc}
 \toprule
@@
 \cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 21.00 & 57.81 & 78.29 & 39,087 \\
- & Case defaulted & 0.00 & 0.20 & 0.40 & 40,727 \\
+\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 0.20 & 0.40 & 40,727 \\
+ & Case duration & 21.00 & 57.81 & 78.29 & 39,087 \\
+ & Case heard & 0.00 & 0.06 & 0.23 & 40,727 \\
  & Case involuntarily dismissed & 0.00 & 0.29 & 0.45 & 40,727 \\
- & Case heard & 0.00 & 0.06 & 0.23 & 40,727 \\
  & Case mediated & 0.00 & 0.41 & 0.49 & 40,727 \\
-\cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.00 & 0.09 & 0.28 & 40,727 \\
- & Plaintiff has an attorney & 1.00 & 0.84 & 0.37 & 40,727 \\
- & Defendant is an entity & 0.00 & 0.01 & 0.08 & 40,727 \\
- & Plaintiff is an entity & 1.00 & 0.70 & 0.46 & 40,727 \\
  & Money judgment & 0.00 & 1890.34 & 5279.49 & 40,727 \\
 \cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 775200.00 & 9435708.78 & 20612629.31 & 14,491 \\
- & Building value & 190000.00 & 2482603.38 & 6470958.91 & 14,491 \\
- & Land value & 2600.00 & 113817.19 & 536568.37 & 14,491 \\
- & Other value & 1067000.00 & 12020146.88 & 26285935.89 & 14,491 \\
- & Units & 1.00 & 42.25 & 112.87 & 14,491 \\
+\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.00 & 0.09 & 0.28 & 40,727 \\
+ & Defendant is an entity & 0.00 & 0.01 & 0.08 & 40,727 \\
+ & Plaintiff has an attorney & 1.00 & 0.84 & 0.37 & 40,727 \\
+ & Plaintiff is an entity & 1.00 & 0.70 & 0.46 & 40,727 \\
+\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 192400.00 & 2471065.61 & 6218383.08 & 36,587 \\
+ & Land value & 1000.00 & 112575.80 & 659661.29 & 36,587 \\
+ & Other value & 954900.00 & 10900678.30 & 26482630.60 & 36,587 \\
+ & Total property value & 636500.00 & 8350204.19 & 22073916.94 & 36,587 \\
+ & Units & 0.00 & 40.76 & 157.57 & 36,587 \\
 \cline{1-6}
@@
  & Four years before latest docket date & 225065.75 & 280243.32 & 276051.45 & 9,968 \\
- & Three years before latest docket date & 240097.38 & 307137.16 & 369763.53 & 10,172 \\
- & Two years before latest docket date & 259176.00 & 341084.08 & 987145.51 & 10,182 \\
- & One year before latest docket date & 278722.25 & 351172.05 & 311982.74 & 10,190 \\
  & Latest docket date & 305144.00 & 377384.02 & 316645.29 & 10,096 \\
  & One year after latest docket date & 347550.00 & 421601.75 & 344328.86 & 10,443 \\
+ & One year before latest docket date & 278722.25 & 351172.05 & 311982.74 & 10,190 \\
+ & Three years after latest docket date & 414600.00 & 501611.80 & 780467.01 & 5,894 \\
+ & Three years before latest docket date & 240097.38 & 307137.16 & 369763.53 & 10,172 \\
  & Two years after latest docket date & 393900.00 & 477948.08 & 457694.83 & 9,175 \\
- & Three years after latest docket date & 414600.00 & 501611.80 & 780467.01 & 5,894 \\
+ & Two years before latest docket date & 259176.00 & 341084.08 & 987145.51 & 10,182 \\
 \cline{1-6}

### 2023-01-03 src/01_build/05_merge.py

@@ -18,11 +18,13 @@ VERBOSE = True
 
 # Load evictions data.
 evictions_df = pd.read_csv(INPUT_DATA_EVICTIONS)
-evictions_gdf = gpd.GeoDataFrame(evictions_df, geometry=gpd.points_from_xy(evictions_df['longitude'], evictions_df['latitude']))
+evictions_gdf = gpd.GeoDataFrame(evictions_df,
+                                 geometry=gpd.points_from_xy(evictions_df['longitude'], evictions_df['latitude']))
 evictions_gdf = evictions_gdf.set_crs("EPSG:4326")  # crs attribute is currently unassigned.
 
 # Load tax parcel files.
-tax_parcel_columns_to_keep = ['MAP_PAR_ID', 'LOC_ID', 'POLY_TYPE', 'SITE_ADDR', 'CITY', 'ZIP', 'SHAPE_Leng', 'SHAPE_Area',
+tax_parcel_columns_to_keep = ['MAP_PAR_ID', 'LOC_ID', 'POLY_TYPE', 'SITE_ADDR', 'CITY', 'ZIP', 'SHAPE_Leng',
+                              'SHAPE_Area',
                               'geometry']
 tax_parcels_gdf = pd.concat([gpd.read_file(INPUT_DATA_TAX_PARCELS_EAST)[tax_parcel_columns_to_keep],
                              gpd.read_file(INPUT_DATA_TAX_PARCELS_WEST)[tax_parcel_columns_to_keep]], axis=0)
@@ -30,34 +32,40 @@ tax_parcels_gdf = tax_parcels_gdf.to_crs("EPSG:4326")
 tax_parcels_gdf = tax_parcels_gdf.dissolve(by='LOC_ID').reset_index()
 
 # Spatial join.
-spatially_joined_columns_to_drop = ['index_right', 'geometry', 'MAP_PAR_ID', 'POLY_TYPE', 'SITE_ADDR', 'CITY', 'ZIP', 'SHAPE_Leng', 'SHAPE_Area']
-tax_parcels_gdf = gpd.sjoin(evictions_gdf, tax_parcels_gdf, how='left', predicate='within').drop(columns=spatially_joined_columns_to_drop)
+spatially_joined_columns_to_drop = ['index_right', 'geometry', 'MAP_PAR_ID', 'POLY_TYPE', 'SITE_ADDR', 'CITY', 'ZIP',
+                                    'SHAPE_Leng', 'SHAPE_Area']
[…]

### 2023-01-08 output/DiD/tables/balance_table.tex
balance table v1

\begin{tabular}{llcccccc}
\toprule
 &  & Cases Won By Plaintiff & Unweighted Difference & Unweighted P-Value \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.119672 & 0.012446 & 0.328395 \\
 & For cause (transfer) & 0.004508 & -0.007147 & 0.023588 \\
 & Foreclosure & 0.043033 & 0.027881 & 0.000154 \\
 & Foreclosure (transfer) & 0.000820 & -0.000346 & 0.772644 \\
 & No cause & 0.105328 & -0.021712 & 0.081632 \\
 & No cause (transfer) & 0.005738 & -0.005917 & 0.079465 \\
 & Non-payment of rent & 0.710246 & 0.005118 & 0.776611 \\
 & Non-payment of rent (transfer) & 0.010656 & -0.010323 & 0.023390 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.065984 & -0.135648 & 0.000000 \\
 & Plaintiff has an attorney & 0.795902 & 0.011519 & 0.474007 \\
 & Defendant is an entity & 0.011885 & 0.003727 & 0.366334 \\
 & Plaintiff is an entity & 0.659426 & 0.028890 & 0.126590 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Total property value & 6,554,743.504986 & 184,134.628913 & 0.785066 \\
 & Building value & 1,897,710.995467 & 25,986.913258 & 0.898541 \\
 & Land value & 87,585.642792 & 22,095.386351 & 0.212030 \\
 & Other value & 8,535,625.582956 & 232,361.889704 & 0.784872 \\
 & Units & 28.734814 & -24.040646 & 0.000030 \\
\cline{1-5}
\bottomrule
\end{tabular}

### 2023-01-08 output/DiD/tables/balance_table.tex
balance table v1

@@
 \toprule
- &  & Cases Won By Plaintiff & Unweighted Difference & Unweighted P-Value \\
+ &  & \textit{Cases Won by Plaintiff} & \textit{('Difference in Cases Won by Defendant', 'Unweighted')} & \textit{('Difference in Cases Won by Defendant', 'P-Value')} \\
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.119672 & 0.012446 & 0.328395 \\
- & For cause (transfer) & 0.004508 & -0.007147 & 0.023588 \\
- & Foreclosure & 0.043033 & 0.027881 & 0.000154 \\
- & Foreclosure (transfer) & 0.000820 & -0.000346 & 0.772644 \\
- & No cause & 0.105328 & -0.021712 & 0.081632 \\
- & No cause (transfer) & 0.005738 & -0.005917 & 0.079465 \\
- & Non-payment of rent & 0.710246 & 0.005118 & 0.776611 \\
- & Non-payment of rent (transfer) & 0.010656 & -0.010323 & 0.023390 \\
+\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.33 \\
+ & For cause (transfer) & 0.00 & -0.01 & 0.02 \\
+ & Foreclosure & 0.04 & 0.03 & 0.00 \\
+ & Foreclosure (transfer) & 0.00 & -0.00 & 0.77 \\
+ & No cause & 0.11 & -0.02 & 0.08 \\
+ & No cause (transfer) & 0.01 & -0.01 & 0.08 \\
+ & Non-payment of rent & 0.71 & 0.01 & 0.78 \\
+ & Non-payment of rent (transfer) & 0.01 & -0.01 & 0.02 \\
 \cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.065984 & -0.135648 & 0.000000 \\
- & Plaintiff has an attorney & 0.795902 & 0.011519 & 0.474007 \\
- & Defendant is an entity & 0.011885 & 0.003727 & 0.366334 \\
- & Plaintiff is an entity & 0.659426 & 0.028890 & 0.126590 \\
+\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 \\
+ & Plaintiff has an attorney & 0.80 & 0.01 & 0.47 \\
+ & Defendant is an entity & 0.01 & 0.00 & 0.37 \\
+ & Plaintiff is an entity & 0.66 & 0.03 & 0.13 \\
 \cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Total property value & 6,554,743.504986 & 184,134.628913 & 0.785066 \\
- & Building value & 1,897,710.995467 & 25,986.913258 & 0.898541 \\
- & Land value & 87,585.642792 & 22,095.386351 & 0.212030 \\
- & Other value & 8,535,625.582956 & 232,361.889704 & 0.784872 \\
- & Units & 28.734814 & -24.040646 & 0.000030 \\
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Total property value & 6554743.50 & 184134.63 & 0.79 \\
+ & Building value & 1897711.00 & 25986.91 & 0.90 \\
+ & Land value & 87585.64 & 22095.39 & 0.21 \\
+ & Other value & 8535625.58 & 232361.89 & 0.78 \\
+ & Units & 28.73 & -24.04 & 0.00 \\
 \cline{1-5}

### 2023-01-08 output/DiD/tables/balance_table.tex
balance table v1

@@
 \toprule
- &  & \textit{Cases Won by Plaintiff} & \textit{('Difference in Cases Won by Defendant', 'Unweighted')} & \textit{('Difference in Cases Won by Defendant', 'P-Value')} \\
+ &  & \textit{} & \multicolumn{2}{r}{\textit{Difference in Cases Won by Defendant}} \\
+ &  & Cases Won by Plaintiff & Unweighted & P-Value \\
 \midrule

### 2023-01-08 output/DiD/tables/balance_table.tex
balance table v1

@@
-\begin{tabular}{llcccccc}
+\begin{tabular}{llccc}
 \toprule
- &  & \textit{} & \multicolumn{2}{r}{\textit{Difference in Cases Won by Defendant}} \\
+ &  & \textit{} & \multicolumn{2}{|c|}{\textit{Difference in Cases Won by Defendant}} \\
  &  & Cases Won by Plaintiff & Unweighted & P-Value \\
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.33 \\
- & For cause (transfer) & 0.00 & -0.01 & 0.02 \\
+\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 \\
  & Foreclosure & 0.04 & 0.03 & 0.00 \\
- & Foreclosure (transfer) & 0.00 & -0.00 & 0.77 \\
- & No cause & 0.11 & -0.02 & 0.08 \\
- & No cause (transfer) & 0.01 & -0.01 & 0.08 \\
- & Non-payment of rent & 0.71 & 0.01 & 0.78 \\
- & Non-payment of rent (transfer) & 0.01 & -0.01 & 0.02 \\
+ & No cause & 0.11 & -0.03 & 0.03 \\
+ & Non-payment of rent & 0.72 & -0.01 & 0.77 \\
+ & Transferred From Other Court & 0.06 & 0.00 & 0.67 \\
 \cline{1-5}

### 2023-01-08 output/summary_statistics/tables/summary_statistics.tex
balance table v1

@@
 \midrule
-\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.00 & 0.12 & 0.32 & 40,727 \\
- & For cause (transfer) & 0.00 & 0.01 & 0.08 & 40,727 \\
+\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.00 & 0.12 & 0.33 & 40,727 \\
  & Foreclosure & 0.00 & 0.02 & 0.14 & 40,727 \\
- & Foreclosure (transfer) & 0.00 & 0.00 & 0.03 & 40,727 \\
- & No cause & 0.00 & 0.10 & 0.30 & 40,727 \\
- & No cause (transfer) & 0.00 & 0.01 & 0.08 & 40,727 \\
- & Non-payment of rent & 1.00 & 0.73 & 0.44 & 40,727 \\
- & Non-payment of rent (transfer) & 0.00 & 0.02 & 0.13 & 40,727 \\
+ & No cause & 0.00 & 0.11 & 0.31 & 40,727 \\
+ & Non-payment of rent & 1.00 & 0.75 & 0.43 & 40,727 \\
+ & Transferred from Other Court & 0.00 & 0.05 & 0.22 & 40,727 \\
 \cline{1-6}

### 2023-01-08 src/02_analysis/analysis_utilities.py

@@ -13,18 +13,20 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     :return:
     """
     # Panel A: Case Initiaton
-    panel_A_columns = ['for_cause', 'foreclosure', 'no_cause', 'non_payment', 'for_cause_transfer',
-                       'foreclosure_transfer',
-                       'non_payment_transfer', 'no_cause_transfer']
+    panel_A_columns = ['for_cause', 'foreclosure', 'no_cause', 'non_payment', 'transfer']
     origin_columns = ['initiating_action', 'initiating_action', 'initiating_action', 'initiating_action',
-                      'initiating_action', 'initiating_action', 'initiating_action', 'initiating_action']
-    target_values = ["SP Summons and Complaint - Cause", "SP Summons and Complaint - Foreclosure",
-                     "SP Summons and Complaint - No Cause", "SP Summons and Complaint - Non-payment of Rent",
-                     "SP Transfer - Cause", "SP Transfer - Foreclosure", "SP Transfer - Non-payment of Rent",
-                     "SP Transfer- No Cause"]
+                      'initiating_action']
+    target_values = [("SP Summons and Complaint - Cause", "SP Transfer - Cause"),
+                     ("SP Summons and Complaint - Foreclosure", "SP Transfer - Foreclosure"),
+                     ("SP Summons and Complaint - No Cause", "SP Transfer- No Cause"),
+                     ("SP Summons and Complaint - Non-payment of Rent", "SP Transfer - Non-payment of Rent"),
+                     'Transfer']
 
     for dummy_column, origin_column, target_value in zip(panel_A_columns, origin_columns, target_values):
-        df.loc[:, dummy_column] = np.where(df[origin_column] == target_value, 1, 0)
+        df.loc[:, dummy_column] = np.where((df[origin_column].str.contains(target_value[0])) |
+                                           (df[origin_column].str.contains(target_value[1])),
+                                           1,
+                                           0)
 
     panel_A = df[sorted(panel_A_columns)].describe().T
     panel_A = pd.concat([panel_A], keys=["Panel A: Case Initiation"])

### 2023-01-10 output/DiD/tables/balance_table.tex
Added census tract characteristics to summary stats and balance tables

@@
  & Non-payment of rent & 0.72 & -0.01 & 0.77 \\
- & Transferred From Other Court & 0.06 & 0.00 & 0.67 \\
+ & Transferred from other court & 0.06 & 0.00 & 0.67 \\
 \cline{1-5}
@@
 \cline{1-5}
+\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 50437.17 & 2602.09 & 0.02 \\
+ & Population density (2010) & 9315.08 & 1151.91 & 0.00 \\
+ & Median two bedroom rent (2015) & 1047.12 & 32.18 & 0.05 \\
+ & Portion white (2010) & 0.59 & 0.04 & 0.00 \\
+\cline{1-5}
 \bottomrule

### 2023-01-10 output/summary_statistics/tables/summary_statistics.tex
Added census tract characteristics to summary stats and balance tables

@@
 \toprule
- &  & Median & Mean & S.D. & N \\
-Panel & Variable &  &  &  &  \\
+ &  & Mean & S.D. & N \\
+Panel & Variable &  &  &  \\
 \midrule
-\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.00 & 0.12 & 0.33 & 40,727 \\
- & Foreclosure & 0.00 & 0.02 & 0.14 & 40,727 \\
- & No cause & 0.00 & 0.11 & 0.31 & 40,727 \\
- & Non-payment of rent & 1.00 & 0.75 & 0.43 & 40,727 \\
- & Transferred from Other Court & 0.00 & 0.05 & 0.22 & 40,727 \\
-\cline{1-6}
-\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 0.20 & 0.40 & 40,727 \\
- & Case duration & 21.00 & 57.81 & 78.29 & 39,087 \\
- & Case heard & 0.00 & 0.06 & 0.23 & 40,727 \\
- & Case involuntarily dismissed & 0.00 & 0.29 & 0.45 & 40,727 \\
- & Case mediated & 0.00 & 0.41 & 0.49 & 40,727 \\
- & Money judgment & 0.00 & 1890.34 & 5279.49 & 40,727 \\
-\cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.00 & 0.09 & 0.28 & 40,727 \\
- & Defendant is an entity & 0.00 & 0.01 & 0.08 & 40,727 \\
- & Plaintiff has an attorney & 1.00 & 0.84 & 0.37 & 40,727 \\
- & Plaintiff is an entity & 1.00 & 0.70 & 0.46 & 40,727 \\
-\cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 192400.00 & 2471065.61 & 6218383.08 & 36,587 \\
- & Land value & 1000.00 & 112575.80 & 659661.29 & 36,587 \\
- & Other value & 954900.00 & 10900678.30 & 26482630.60 & 36,587 \\
- & Total property value & 636500.00 & 8350204.19 & 22073916.94 & 36,587 \\
- & Units & 0.00 & 40.76 & 157.57 & 36,587 \\
-\cline{1-6}
-\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 213270.60 & 261462.86 & 238040.64 & 9,842 \\
- & Four years before latest docket date & 225065.75 & 280243.32 & 276051.45 & 9,968 \\
- & Latest docket date & 305144.00 & 377384.02 & 316645.29 & 10,096 \\
- & One year after latest docket date & 347550.00 & 421601.75 & 344328.86 & 10,443 \\
- & One year before latest docket date & 278722.25 & 351172.05 & 311982.74 & 10,190 \\
- & Three years after latest docket date & 414600.00 & 501611.80 & 780467.01 & 5,894 \\
- & Three years before latest docket date & 240097.38 & 307137.16 & 369763.53 & 10,172 \\
- & Two years after latest docket date & 393900.00 & 477948.08 & 457694.83 & 9,175 \\
- & Two years before latest docket date & 259176.00 & 341084.08 & 987145.51 & 10,182 \\
-\cline{1-6}
+\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.33 & 40,735 \\
+ & Foreclosure & 0.02 & 0.14 & 40,735 \\
+ & No cause & 0.11 & 0.31 & 40,735 \\
+ & Non-payment of rent & 0.75 & 0.43 & 40,735 \\
+ & Transferred from other court & 0.05 & 0.22 & 40,735 \\
+\cline{1-5}
+\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,735 \\
+ & Case duration & 57.81 & 78.28 & 39,095 \\
+ & Case heard & 0.06 & 0.23 & 40,735 \\
+ & Case involuntarily dismissed & 0.29 & 0.45 & 40,735 \\
+ & Case mediated & 0.41 & 0.49 & 40,735 \\
+ & Money judgment & 1890.04 & 5279.02 & 40,735 \\
+\cline{1-5}
+\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,735 \\
+ & Defendant is an entity & 0.01 & 0.08 & 40,735 \\
+ & Plaintiff has an attorney & 0.84 & 0.37 & 40,735 \\
+ & Plaintiff is an entity & 0.70 & 0.46 & 40,735 \\
+\cline{1-5}
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 2471018.52 & 6218058.67 & 36,593 \\
+ & Land value & 112582.19 & 659613.02 & 36,593 \\
+ & Other value & 10900588.00 & 26481310.62 & 36,593 \\
+ & Total property value & 8350149.14 & 22072704.88 & 36,593 \\
+ & Units & 40.75 & 157.56 & 36,593 \\
+\cline{1-5}
+\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 50657.19 & 26561.46 & 35,061 \\
+ & Median two bedroom rent (2015) & 1063.29 & 352.37 & 26,193 \\
+ & Population density (2010) & 9309.43 & 9457.63 & 35,061 \\
+ & Portion white (2010) & 0.56 & 0.30 & 35,061 \\
+\cline{1-5}
+\multirow[c]{9}{4cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377366.88 & 316634.29 & 10,097 \\
+ & Five years before filing date & 261450.07 & 238031.93 & 9,843 \\
+ & Four years before filing date & 280231.05 & 276040.32 & 9,969 \\
+ & One year after filing date & 421583.49 & 344317.43 & 10,444 \\
+ & One year before filing date & 351156.71 & 311971.28 & 10,191 \\
+ & Three years after filing date & 501586.74 & 780403.17 & 5,895 \\
+ & Three years before filing date & 307124.02 & 369747.73 & 10,173 \\
+ & Two years after filing date & 477926.97 & 457674.35 & 9,176 \\
+ & Two years before filing date & 341068.35 & 987098.31 & 10,183 \\
+\cline{1-5}
 \bottomrule

### 2023-01-10 src/01_build/02_clean_evictions.py

@@ -1,11 +1,11 @@
 """
-01_clean_evictions.py
+02_clean_evictions.py
 
 Cleans eviction dataset from MassLandlords.
 """
 import pandas as pd
 from geocodio import GeocodioClient
-from src.old.utilities.dataframe_utilities import batch_df
+from build_utilities import batch_df
 
 INPUT_DATA_EVICTIONS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/gather20221121_aug.csv"
 OUTPUT_DATA = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions.csv"

### 2023-01-10 src/01_build/03_clean_census_tract_covariates.py

@@ -1,0 +1,27 @@
+"""
+clean_census_tract_covariates.py
+
+Cleans census tract level data from Opportunity Insights.
+"""
+import pandas as pd
+
+INPUT_DATA = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/tract_covariates.csv"
+OUTPUT_DATA = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/tracts.csv"
+
+# Load data.
+tracts_df = pd.read_csv(INPUT_DATA)
+
+# Keep only rows corresponding to Massachusetts.
+tracts_df = tracts_df.loc[tracts_df['state'] == 25, :]
+
+# Generate a GEOID column.
+tracts_df.loc[:, 'county'] = tracts_df['county'].astype(str).str.zfill(3)
+tracts_df.loc[:, 'tract'] = tracts_df['tract'].astype(str).str.zfill(6)
+tracts_df.loc[:, 'tract_geoid'] = tracts_df['state'].astype(str) + tracts_df['county'] + tracts_df['tract']
+
+# Keep only specified columns.
+columns_to_keep = ['tract_geoid', 'med_hhinc2016', 'frac_coll_plus2010', 'foreign_share2010', 'poor_share2010',
+                   'share_white2010', 'rent_twobed2015', 'popdensity2010', 'job_density_2013']
+
+# Save data.
+tracts_df[columns_to_keep].to_csv(OUTPUT_DATA)

### 2023-01-10 src/01_build/04_GET_zpids_and_merge.py

@@ -1,5 +1,5 @@
 """
-03_GET_zpids_and_merge.py
+04_GET_zpids_and_merge.py
 """
 import pandas as pd
 from zillow_utilities import GET_processed_ZPIDs

### 2023-01-10 src/01_build/05_merge.py

@@ -1,157 +1,0 @@
-"""
-06_merge.py
-
-Merge eviction data with assessment values.
-"""
-import numpy as np
-import pandas as pd
-import geopandas as gpd
-
-INPUT_DATA_EVICTIONS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions.csv"
-INPUT_DATA_TAX_PARCELS_EAST = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/Statewide_parcels_SHP/L3_TAXPAR_POLY_ASSESS_EAST.shp"
-INPUT_DATA_TAX_PARCELS_WEST = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/Statewide_parcels_SHP/L3_TAXPAR_POLY_ASSESS_WEST.shp"
-INPUT_DATA_ZESTIMATES = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/zestimates.csv"
-INPUT_DATA_ASSESSMENT_VALUES = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/assessor_values.csv"
-OUTPUT_DATA_UNRESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/unrestricted.csv"
-OUTPUT_DATA_RESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/restricted.csv"
-VERBOSE = True
-
-# Load evictions data.
-evictions_df = pd.read_csv(INPUT_DATA_EVICTIONS)
-evictions_gdf = gpd.GeoDataFrame(evictions_df,
-                                 geometry=gpd.points_from_xy(evictions_df['longitude'], evictions_df['latitude']))
-evictions_gdf = evictions_gdf.set_crs("EPSG:4326")  # crs attribute is currently unassigned.
-
-# Load tax parcel files.
-tax_parcel_columns_to_keep = ['MAP_PAR_ID', 'LOC_ID', 'POLY_TYPE', 'SITE_ADDR', 'CITY', 'ZIP', 'SHAPE_Leng',
-                              'SHAPE_Area',
-                              'geometry']
[…]

### 2023-01-10 src/01_build/06_merge.py

@@ -1,0 +1,166 @@
+"""
+06_merge.py
+
+Merge eviction data with assessment values.
+"""
+if __name__ == '__main__':
+    import pandas as pd
+    import geopandas as gpd
+    from build_utilities import geocode_coordinates
+
+    INPUT_DATA_EVICTIONS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions.csv"
+    INPUT_DATA_TAX_PARCELS_EAST = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/Statewide_parcels_SHP/L3_TAXPAR_POLY_ASSESS_EAST.shp"
+    INPUT_DATA_TAX_PARCELS_WEST = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/Statewide_parcels_SHP/L3_TAXPAR_POLY_ASSESS_WEST.shp"
+    INPUT_DATA_TRACTS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/tracts.csv"
+    INPUT_DATA_ZESTIMATES = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/zestimates.csv"
+    INPUT_DATA_ASSESSMENT_VALUES = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/assessor_values.csv"
+    OUTPUT_DATA_UNRESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/unrestricted.csv"
+    OUTPUT_DATA_RESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/restricted.csv"
+    VERBOSE = True
+
+    # Load evictions data.
+    evictions_df = pd.read_csv(INPUT_DATA_EVICTIONS)
+    evictions_gdf = gpd.GeoDataFrame(evictions_df,
+                                     geometry=gpd.points_from_xy(evictions_df['longitude'], evictions_df['latitude']))
+    evictions_gdf = evictions_gdf.set_crs("EPSG:4326")  # crs attribute is currently unassigned.
+
+    # Load tax parcel files.
[…]

### 2023-01-10 src/01_build/build_utilities.py

@@ -6,7 +6,7 @@ from time import sleep
 
 import pandas as pd
 import numpy as np
-import censusgeocode
+import censusgeocode as cg
 from typing import List
 from joblib import Parallel, delayed
 from multiprocessing import Manager
@@ -32,83 +32,26 @@ def sjoin_tax_parcels_with_evictions(tax_parcels_gdf: gpd.GeoDataFrame,
     return gdf
 
 
-def geocode_single_address(row):
-    """
-    Function meant to be applied to a single row of a DataFrame.
-    :param row:
-    """
-    sleep(3)  # Sleep to avoid over-pinging the API server.
-    id_num = int(row['id'])
-    tokenized_address = row['address'].split(", ")
-    if len(tokenized_address) > 4:  # If there is an extra comma in the address tokenized address may have too many items.
-        return row  # Abort if this happens.
-    street_address = tokenized_address[0]
-    city = tokenized_address[1]
-    state = tokenized_address[2]
-    zipcode = tokenized_address[3]
-    if len(zipcode) > 10:
-        return row  # Abort if zipcode is longer than 10 characters.
-    result = censusgeocode.address(street_address, city=city, state=state, zip=zipcode)
-    print(result)
-    if len(result) > 0:  # If a match is found:
-        row['parsed'] = result[0]['matchedAddress']
-        row['match'] = True
-        row['tigerlineid'] = result[0]['tigerLine']['tigerLineId']
-        row['side'] = result[0]['tigerLine']['side']
-        row['statefp'] = result[0]['geographies']['Census Tracts'][0]['STATE']
-        row['countyfp'] = result[0]['geographies']['Census Tracts'][0]['COUNTY']
-        row['tract'] = result[0]['geographies']['Census Tracts'][0]['TRACT']
-        row['block'] = result[0]['geographies']['2020 Census Blocks'][0]['BLOCK']
-        row['lat'] = result[0]['coordinates']['y']
-        row['lon'] = result[0]['coordinates']['x']
+def geocode_single_point(master_list: List, index: int, latitude: float, longitude: float):
+    print(f"Geocoding row {index} at latitude {latitude} and longitude {longitude}.")
+    if np.isnan(latitude) or np.isnan(longitude):
+        master_list.append((index, np.nan))
     else:
-        row['match'] = False
-    print(row)
-    return row
+        try:
+            master_list.append((index, cg.coordinates(longitude, latitude)['Census Tracts'][0]['GEOID']))
[…]

### 2023-01-10 writing/paper/main.tex

@@
 \usepackage{amssymb,amsmath,amsfonts,booktabs,eurosym,float,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,multicol, multirow,natbib,pdflscape,subfigure,array,hyperref, pdflscape}
+\bibliographystyle{unsrtnat}
 
 \normalem
-
-\onehalfspacing
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{proposition}{Proposition}
-\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
-
-\newtheorem{hyp}{Hypothesis}
-\newtheorem{subhyp}{Hypothesis}[hyp]
-\renewcommand{\thesubhyp}{\thehyp\alph{subhyp}}
-
-\newcommand{\red}[1]{{\color{red} #1}}
-\newcommand{\blue}[1]{{\color{blue} #1}}
-
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{C}[1]{>{\centering\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
 
@@
 \section{Introduction} \label{sec:introduction}
+\bibliography{writing/paper/citations}
 \subsection{Literature Review}
@@
         \subsubsection{The Eviction Process}
-    \subsubsection{Property Tax Assessment}
+    \subsection{Property Tax Assessment}
         \subsubsection{The Property Value Assessment Process}
@@
         \end{figure}
+
+        \begin{figure}[H]
+            \centering
+            \includegraphics{output/summary_statistics/figures/filings_over_time.png}
+            \caption{Eviction Filings Over Time}
+            \label{fig:my_label}
+        \end{figure}
     \end{landscape}
+        \begin{table}[H]
+            \centering
+            \input{output/summary_statistics/tables/treatment_timings.tex}
+            \caption{Distribution of Eviction Filings and Outcomes}
+            \label{tab:my_label}
+        \end{table}
+
     \subsection{Tax Assessment Records}
@@
             \centering
-            \tiny
+            \small
             \input{output/summary_statistics/tables/summary_statistics.tex}
@@
             \centering
-            \tiny
+            \small
             \input{output/summary_statistics/tables/balance_table.tex}
@@
 \section{Empirical Strategy: Difference-in-Difference}
+    I seek to estimate average treatment effects of plaintiff victory on treated properties.
+Let $G_i$ be the treatment cohort for eviction case $i$; $G_i = g \in \{\text{May}\:2019, \text{June}\:2019, ..., \text{May}\:2021\}$ if eviction case $i$ resulted in a victory for the plaintiff.
+Let $C_i = 1$ if eviction case $i$ resulted in a victory for the defendant and $0$ otherwise.
+I use  the staggered difference-in-difference estimator proposed in \cite{callaway_sant'anna_2021}, which estimates time- and cohort-specific average treatment effects on the treated using canonical difference-in-difference estimators and then aggregates them, weighting by cohort size, to produce summaries of the average treatment effect on the treated.
+
     \subsection{Estimating the ATT in the Staggered Treatment Case}
@@
     \end{enumerate}
+
+    \newpage
+    \begin{landscape}
+       \begin{table}[H]
+        \centering
+        \input{output/DiD/tables/balance_table.tex}
+        \caption{Caption}
+        \label{tab:my_label}
+    \end{table} 
+    \end{landscape}
+
     \subsection{Parallel Trends Assumptions in the Staggered Treatment Case}

### 2023-01-11 output/summary_statistics/tables/summary_statistics.tex
Added commas to numbers in summary statistics table

@@
 \midrule
-\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.33 & 40,735 \\
- & Foreclosure & 0.02 & 0.14 & 40,735 \\
- & No cause & 0.11 & 0.31 & 40,735 \\
- & Non-payment of rent & 0.75 & 0.43 & 40,735 \\
- & Transferred from other court & 0.05 & 0.22 & 40,735 \\
+\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.33 & 40,727 \\
+ & Foreclosure & 0.02 & 0.14 & 40,727 \\
+ & No cause & 0.11 & 0.31 & 40,727 \\
+ & Non-payment of rent & 0.75 & 0.43 & 40,727 \\
+ & Transferred from other court & 0.05 & 0.22 & 40,727 \\
 \cline{1-5}
-\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,735 \\
- & Case duration & 57.81 & 78.28 & 39,095 \\
- & Case heard & 0.06 & 0.23 & 40,735 \\
- & Case involuntarily dismissed & 0.29 & 0.45 & 40,735 \\
- & Case mediated & 0.41 & 0.49 & 40,735 \\
- & Money judgment & 1890.04 & 5279.02 & 40,735 \\
+\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,727 \\
+ & Case duration & 57.81 & 78.29 & 39,087 \\
+ & Case heard & 0.06 & 0.23 & 40,727 \\
+ & Case involuntarily dismissed & 0.29 & 0.45 & 40,727 \\
+ & Case mediated & 0.41 & 0.49 & 40,727 \\
+ & Money judgment & 1890.34 & 5279.49 & 40,727 \\
 \cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,735 \\
- & Defendant is an entity & 0.01 & 0.08 & 40,735 \\
- & Plaintiff has an attorney & 0.84 & 0.37 & 40,735 \\
- & Plaintiff is an entity & 0.70 & 0.46 & 40,735 \\
+\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,727 \\
+ & Defendant is an entity & 0.01 & 0.08 & 40,727 \\
+ & Plaintiff has an attorney & 0.84 & 0.37 & 40,727 \\
+ & Plaintiff is an entity & 0.70 & 0.46 & 40,727 \\
 \cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 2471018.52 & 6218058.67 & 36,593 \\
- & Land value & 112582.19 & 659613.02 & 36,593 \\
- & Other value & 10900588.00 & 26481310.62 & 36,593 \\
- & Total property value & 8350149.14 & 22072704.88 & 36,593 \\
- & Units & 40.75 & 157.56 & 36,593 \\
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 2471065.61 & 6218383.08 & 36,587 \\
+ & Land value & 112575.80 & 659661.29 & 36,587 \\
+ & Other value & 10900678.30 & 26482630.60 & 36,587 \\
+ & Total property value & 8350204.19 & 22073916.94 & 36,587 \\
+ & Units & 40.76 & 157.57 & 36,587 \\
 \cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 50657.19 & 26561.46 & 35,061 \\
- & Median two bedroom rent (2015) & 1063.29 & 352.37 & 26,193 \\
- & Population density (2010) & 9309.43 & 9457.63 & 35,061 \\
- & Portion white (2010) & 0.56 & 0.30 & 35,061 \\
+\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 50658.53 & 26562.19 & 35,058 \\
+ & Median two bedroom rent (2015) & 1063.30 & 352.38 & 26,191 \\
+ & Population density (2010) & 9309.47 & 9457.90 & 35,058 \\
+ & Portion white (2010) & 0.56 & 0.30 & 35,058 \\
 \cline{1-5}
-\multirow[c]{9}{4cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377366.88 & 316634.29 & 10,097 \\
- & Five years before filing date & 261450.07 & 238031.93 & 9,843 \\
- & Four years before filing date & 280231.05 & 276040.32 & 9,969 \\
- & One year after filing date & 421583.49 & 344317.43 & 10,444 \\
- & One year before filing date & 351156.71 & 311971.28 & 10,191 \\
- & Three years after filing date & 501586.74 & 780403.17 & 5,895 \\
- & Three years before filing date & 307124.02 & 369747.73 & 10,173 \\
- & Two years after filing date & 477926.97 & 457674.35 & 9,176 \\
- & Two years before filing date & 341068.35 & 987098.31 & 10,183 \\
+\multirow[c]{9}{4cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377384.02 & 316645.29 & 10,096 \\
+ & Five years before filing date & 261462.86 & 238040.64 & 9,842 \\
+ & Four years before filing date & 280243.32 & 276051.45 & 9,968 \\
+ & One year after filing date & 421601.75 & 344328.86 & 10,443 \\
+ & One year before filing date & 351172.05 & 311982.74 & 10,190 \\
+ & Three years after filing date & 501611.80 & 780467.01 & 5,894 \\
+ & Three years before filing date & 307137.16 & 369763.53 & 10,172 \\
+ & Two years after filing date & 477948.08 & 457694.83 & 9,175 \\
+ & Two years before filing date & 341084.08 & 987145.51 & 10,182 \\
 \cline{1-5}

### 2023-01-11 output/summary_statistics/tables/summary_statistics.tex
Added commas to numbers in summary statistics table

@@
  & Case mediated & 0.41 & 0.49 & 40,727 \\
- & Money judgment & 1890.34 & 5279.49 & 40,727 \\
+ & Money judgment & 1,890.34 & 5,279.49 & 40,727 \\
 \cline{1-5}
@@
 \cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 2471065.61 & 6218383.08 & 36,587 \\
- & Land value & 112575.80 & 659661.29 & 36,587 \\
- & Other value & 10900678.30 & 26482630.60 & 36,587 \\
- & Total property value & 8350204.19 & 22073916.94 & 36,587 \\
+\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 2,471,065.61 & 6,218,383.08 & 36,587 \\
+ & Land value & 112,575.80 & 659,661.29 & 36,587 \\
+ & Other value & 10,900,678.30 & 26,482,630.60 & 36,587 \\
+ & Total property value & 8,350,204.19 & 22,073,916.94 & 36,587 \\
  & Units & 40.76 & 157.57 & 36,587 \\
 \cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 50658.53 & 26562.19 & 35,058 \\
- & Median two bedroom rent (2015) & 1063.30 & 352.38 & 26,191 \\
- & Population density (2010) & 9309.47 & 9457.90 & 35,058 \\
+\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 50,658.53 & 26,562.19 & 35,058 \\
+ & Median two bedroom rent (2015) & 1,063.30 & 352.38 & 26,191 \\
+ & Population density (2010) & 9,309.47 & 9,457.90 & 35,058 \\
  & Portion white (2010) & 0.56 & 0.30 & 35,058 \\
 \cline{1-5}
-\multirow[c]{9}{4cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377384.02 & 316645.29 & 10,096 \\
- & Five years before filing date & 261462.86 & 238040.64 & 9,842 \\
- & Four years before filing date & 280243.32 & 276051.45 & 9,968 \\
- & One year after filing date & 421601.75 & 344328.86 & 10,443 \\
- & One year before filing date & 351172.05 & 311982.74 & 10,190 \\
- & Three years after filing date & 501611.80 & 780467.01 & 5,894 \\
- & Three years before filing date & 307137.16 & 369763.53 & 10,172 \\
- & Two years after filing date & 477948.08 & 457694.83 & 9,175 \\
- & Two years before filing date & 341084.08 & 987145.51 & 10,182 \\
+\multirow[c]{9}{4cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377,384.02 & 316,645.29 & 10,096 \\
+ & Five years before filing date & 261,462.86 & 238,040.64 & 9,842 \\
+ & Four years before filing date & 280,243.32 & 276,051.45 & 9,968 \\
+ & One year after filing date & 421,601.75 & 344,328.86 & 10,443 \\
+ & One year before filing date & 351,172.05 & 311,982.74 & 10,190 \\
+ & Three years after filing date & 501,611.80 & 780,467.01 & 5,894 \\
+ & Three years before filing date & 307,137.16 & 369,763.53 & 10,172 \\
+ & Two years after filing date & 477,948.08 & 457,694.83 & 9,175 \\
+ & Two years before filing date & 341,084.08 & 987,145.51 & 10,182 \\
 \cline{1-5}

### 2023-01-14 output/DiD/tables/balance_table.tex
Added census tract characteristics as pre-treatment covariates

--- 2023-01-08 output/DiD/tables/balance_table.tex
@@
  & Non-payment of rent & 0.72 & -0.01 & 0.77 \\
- & Transferred From Other Court & 0.06 & 0.00 & 0.67 \\
+ & Transferred from other court & 0.02 & -0.02 & 0.00 \\
 \cline{1-5}
@@
 \cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Total property value & 6554743.50 & 184134.63 & 0.79 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Total property value & 6554743.50 & 184134.63 & 0.79 \\
  & Building value & 1897711.00 & 25986.91 & 0.90 \\
@@
  & Other value & 8535625.58 & 232361.89 & 0.78 \\
- & Units & 28.73 & -24.04 & 0.00 \\
+\cline{1-5}
+\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52087.32 & 2566.82 & 0.01 \\
+ & Population density (2010) & 9031.64 & 944.99 & 0.01 \\
+ & Median two bedroom rent (2015) & 1093.36 & 34.26 & 0.05 \\
+ & Portion white (2010) & 0.60 & 0.04 & 0.00 \\
 \cline{1-5}

### 2023-01-14 output/summary_statistics/tables/summary_statistics.tex
Added census tract characteristics as pre-treatment covariates

@@
  & Non-payment of rent & 0.75 & 0.43 & 40,727 \\
- & Transferred from other court & 0.05 & 0.22 & 40,727 \\
+ & Transferred from other court & 0.03 & 0.17 & 40,727 \\
 \cline{1-5}
@@
 \cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 2,471,065.61 & 6,218,383.08 & 36,587 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 2,471,065.61 & 6,218,383.08 & 36,587 \\
  & Land value & 112,575.80 & 659,661.29 & 36,587 \\
@@
  & Total property value & 8,350,204.19 & 22,073,916.94 & 36,587 \\
- & Units & 40.76 & 157.57 & 36,587 \\
 \cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 50,658.53 & 26,562.19 & 35,058 \\
- & Median two bedroom rent (2015) & 1,063.30 & 352.38 & 26,191 \\
- & Population density (2010) & 9,309.47 & 9,457.90 & 35,058 \\
- & Portion white (2010) & 0.56 & 0.30 & 35,058 \\
+\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 27,177.48 & 40,726 \\
+ & Median two bedroom rent (2015) & 1,116.27 & 396.29 & 30,537 \\
+ & Population density (2010) & 9,159.77 & 9,574.14 & 40,726 \\
+ & Portion white (2010) & 0.58 & 0.29 & 40,726 \\
 \cline{1-5}

### 2023-01-14 src/01_build/build_utilities.py

@@ -38,6 +38,7 @@ def geocode_single_point(master_list: List, index: int, latitude: float, longitu
         master_list.append((index, np.nan))
     else:
         try:
+            print(cg.coordinates(longitude, latitude))
             master_list.append((index, cg.coordinates(longitude, latitude)['Census Tracts'][0]['GEOID']))
         except ValueError:
             print("ValueError: Unable to parse response from Census")

### 2023-01-14 src/01_build/scratch.py

@@ -1,0 +1,10 @@
+import numpy as np
+import pandas as pd
+from build_utilities import geocode_single_point
+
+df = pd.read_csv("/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions.csv")
+df2 = pd.read_csv("/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/tracts.csv")
+print(df['Full FIPS (tract)'].astype(str))
+print(df2['tract_geoid'])
+
+print(df2['tract_geoid'].isin(df['Full FIPS (tract)']).sum())

### 2023-01-14 src/02_analysis/analysis_utilities.py

@@ -20,7 +20,7 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                      ("SP Summons and Complaint - Foreclosure", "SP Transfer - Foreclosure"),
                      ("SP Summons and Complaint - No Cause", "SP Transfer- No Cause"),
                      ("SP Summons and Complaint - Non-payment of Rent", "SP Transfer - Non-payment of Rent"),
-                     'Transfer']
+                     ('Transfer', 'Transfer')]
 
     for dummy_column, origin_column, target_value in zip(panel_A_columns, origin_columns, target_values):
         df.loc[:, dummy_column] = np.where((df[origin_column].str.contains(target_value[0])) |
@@ -52,7 +52,7 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     panel_C = pd.concat([panel_C], keys=["Panel C: Defendant and Plaintiff Characteristics"])
 
     # Panel D: Tax Assessment Records From F.Y. Following Eviction Filing
-    panel_D_columns = ['TOTAL_VAL', 'BLDG_VAL', 'LAND_VAL', 'OTHER_VAL', 'UNITS']
+    panel_D_columns = ['TOTAL_VAL', 'BLDG_VAL', 'LAND_VAL', 'OTHER_VAL']
     panel_D = df[sorted(panel_D_columns)].describe().T
     panel_D = pd.concat([panel_D], keys=["Panel D: Assessor Records From Most Recent Pre-Filing F.Y."])
 

### 2023-01-14 src/02_analysis/scratch.py

@@ -1,25 +1,0 @@
-import numpy as np
-import pandas as pd
-from matplotlib import pyplot as plt
-
-from figure_utilities import plot_scatter_with_error_bars
-
-result = pd.read_csv("/Users/arjunshanmugam/Desktop/zpid_result_test.txt", header=None, sep="NOT_A_SEPARATOR")[0]  # Get the first and only column.
-
-split = result.str.split("\"")  # Split on the address's closing quotes.
-# Build one column containing addresses and another containing lists of ZPIDs.
-ZPIDs = split.str[2].str.split(",")
-for index, zpid_list in enumerate(ZPIDs):
-    new_list = [element for element in zpid_list if element != ""]
-    if len(new_list) == 0:
-        ZPIDs.loc[index] = [np.nan]
-    else:
-        ZPIDs.loc[index] = new_list
-ZPIDs = pd.DataFrame(ZPIDs.tolist())
-ZPIDs.columns = "zpid" + (ZPIDs.columns + 1).astype(str)
-addresses = split.str[1]
-addresses.name = "address"
-
-# Return result.
-result = pd.concat([addresses, ZPIDs], axis=1)
-result = pd.wide_to_long(result, stubnames='zpid', i='address', j='j').reset_index().drop(columns='j').reset_index(drop=True)

### 2023-01-14 writing/paper/main.tex
Updates from Overleaf

@@
 
-\usepackage{amssymb,amsmath,amsfonts,booktabs,eurosym,float,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,multicol, multirow,natbib,pdflscape,subfigure,array,hyperref, pdflscape}
-\bibliographystyle{unsrtnat}
+\usepackage{amssymb,amsmath,amsfonts, booktabs, dsfont, eurosym,float,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,multicol, multirow, natbib, pdflscape,array,hyperref}
+\bibliographystyle{rusnat}
+\bibliography{citations}
 
@@
         \end{figure}
-    \begin{landscape}
+
+        \begin{figure}[H]
+            \centering
+            \includegraphics[scale=0.8]{output/DiD/figures/trends_in_zestimates_by_cohort.png}
+            \caption{Trends in Zestimates by Cohort}
+            \label{fig:my_label}
+        \end{figure}
+
     \subsection{Summary Statistics}
@@
         \newpage
-        \begin{table}[H]
-            \centering
-            \small
-            \input{output/summary_statistics/tables/balance_table.tex}
-            \caption{Balance Table}
-            \label{tab:my_label}
-        \end{table}
-    \end{landscape}
 
 \section{Empirical Strategy: Difference-in-Difference}
-    I seek to estimate average treatment effects of plaintiff victory on treated properties.
-Let $G_i$ be the treatment cohort for eviction case $i$; $G_i = g \in \{\text{May}\:2019, \text{June}\:2019, ..., \text{May}\:2021\}$ if eviction case $i$ resulted in a victory for the plaintiff.
-Let $C_i = 1$ if eviction case $i$ resulted in a victory for the defendant and $0$ otherwise.
-I use  the staggered difference-in-difference estimator proposed in \cite{callaway_sant'anna_2021}, which estimates time- and cohort-specific average treatment effects on the treated using canonical difference-in-difference estimators and then aggregates them, weighting by cohort size, to produce summaries of the average treatment effect on the treated.
+    I seek to estimate the average treatment effects of plaintiff victory in eviction cases on treated properties.
+I use the staggered difference-in-difference estimator proposed in \cite{callaway_difference--differences_2021}, which uses two-period, two-unit difference-in-difference estimators to estimate time- and cohort-specific ATTs and then aggregates them, weighting by cohort size, to produce summaries of the ATT.
+Let $G_i$ be the month during which the eviction case involving property $i$ was filed, such that $G_i = g \in \{\text{May} \; 2019, \text{June} \; 2019, ..., \text{May} \; 2021\}$.
+Let $C_i = 1$ if the eviction case involving $i$ resulted in a victory for the defendant and $0$ otherwise.
+If $G_i = g$ and $C_i = 0$, then property $i$ is a treated property and a member of the cohort first treated during month $g$.
+If $C_i=1$, then property $i$ is a never-treated property.
+
+    \subsection{Unconditional Estimates of the ATT}
+    The following is an unconditional estimator for $ATT(g,t)$, the average treatment affect during month $t$ for the cohort first treated during month $g$.
+
+    \begin{align}
+        \hat{ATT}^{nev}_{un}(g, t) = \frac{\sum_i(Y_{i,t} - Y_{i, g-1})\mathds{1}\{G_i=g\}}{\sum_i\mathds{1}\{G_i=g\}} - \frac{\sum_i(Y_{i,t} - Y_{i, g-1})\mathds{1}\{C_i=1\}}{\sum_i\mathds{1}\{C_i=1\}}
+    \end{align}
 
@@
 
-\singlespacing
-\setlength\bibsep{0pt}
-\bibliographystyle{my-style}
-\bibliography{Placeholder}
-
 \clearpage
@@
 
-% \section*{Tables} \label{sec:tab}
-% \addcontentsline{toc}{section}{Tables}
-
-% \clearpage
-
-% \section*{Figures} \label{sec:fig}
-% \addcontentsline{toc}{section}{Figures}
-
-% \clearpage
-
-% \section*{Appendix A. Placeholder} \label{sec:appendixa}
-% \addcontentsline{toc}{section}{Appendix A}
-
+%
 \end{document}

### 2023-01-15 output/DiD/tables/balance_table.tex
CLeaned up summary statistics

--- 2023-01-08 output/DiD/tables/balance_table.tex
@@
 \multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 \\
- & Foreclosure & 0.04 & 0.03 & 0.00 \\
- & No cause & 0.11 & -0.03 & 0.03 \\
- & Non-payment of rent & 0.72 & -0.01 & 0.77 \\
- & Transferred From Other Court & 0.06 & 0.00 & 0.67 \\
+ & No cause & 0.04 & 0.03 & 0.00 \\
+ & Non-payment of rent & 0.11 & -0.03 & 0.03 \\
+ & Defendant has an attorney & 0.72 & -0.01 & 0.77 \\
+ & Plaintiff has an attorney & 0.02 & -0.02 & 0.00 \\
 \cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 \\
- & Plaintiff has an attorney & 0.80 & 0.01 & 0.47 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.37 \\
- & Plaintiff is an entity & 0.66 & 0.03 & 0.13 \\
+\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant is an entity & 0.07 & -0.14 & 0.00 \\
+ & Plaintiff is an entity & 0.80 & 0.01 & 0.47 \\
+ & Total property value & 0.01 & 0.00 & 0.37 \\
+ & Building value & 0.66 & 0.03 & 0.13 \\
 \cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Total property value & 6554743.50 & 184134.63 & 0.79 \\
- & Building value & 1897711.00 & 25986.91 & 0.90 \\
- & Land value & 87585.64 & 22095.39 & 0.21 \\
- & Other value & 8535625.58 & 232361.89 & 0.78 \\
- & Units & 28.73 & -24.04 & 0.00 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Land value & 6554743.50 & 184134.63 & 0.79 \\
+ & Other value & 1897711.00 & 25986.91 & 0.90 \\
+ & Median household income (2016) & 87585.64 & 22095.39 & 0.21 \\
+ & Population density (2010) & 8535625.58 & 232361.89 & 0.78 \\
+\cline{1-5}
+\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median two bedroom rent (2015) & 52087.32 & 2566.82 & 0.01 \\
+ & Portion white (2010) & 9031.64 & 944.99 & 0.01 \\
+ & rent_twobed2015 & 1093.36 & 34.26 & 0.05 \\
+ & share_white2010 & 0.60 & 0.04 & 0.00 \\
 \cline{1-5}

### 2023-01-15 output/summary_statistics/tables/summary_statistics.tex
CLeaned up summary statistics

@@
 \midrule
-\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.33 & 40,727 \\
- & Foreclosure & 0.02 & 0.14 & 40,727 \\
+\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.33 & 40,727 \\
  & No cause & 0.11 & 0.31 & 40,727 \\
  & Non-payment of rent & 0.75 & 0.43 & 40,727 \\
- & Transferred from other court & 0.03 & 0.17 & 40,727 \\
 \cline{1-5}
 \multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,727 \\
+ & Case dismised & 0.29 & 0.45 & 40,727 \\
  & Case duration & 57.81 & 78.29 & 39,087 \\
  & Case heard & 0.06 & 0.23 & 40,727 \\
- & Case involuntarily dismissed & 0.29 & 0.45 & 40,727 \\
  & Case mediated & 0.41 & 0.49 & 40,727 \\
@@
 \cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 2,471,065.61 & 6,218,383.08 & 36,587 \\
- & Land value & 112,575.80 & 659,661.29 & 36,587 \\
- & Other value & 10,900,678.30 & 26,482,630.60 & 36,587 \\
- & Total property value & 8,350,204.19 & 22,073,916.94 & 36,587 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 8,350,204.19 & 22,073,916.94 & 36,587 \\
+ & Land value & 2,471,065.61 & 6,218,383.08 & 36,587 \\
+ & Other value & 112,575.80 & 659,661.29 & 36,587 \\
+ & Total property value & 10,900,678.30 & 26,482,630.60 & 36,587 \\
 \cline{1-5}

### 2023-01-15 src/02_analysis/analysis_utilities.py

@@ -13,14 +13,11 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     :return:
     """
     # Panel A: Case Initiaton
-    panel_A_columns = ['for_cause', 'foreclosure', 'no_cause', 'non_payment', 'transfer']
-    origin_columns = ['initiating_action', 'initiating_action', 'initiating_action', 'initiating_action',
-                      'initiating_action']
+    panel_A_columns = ['for_cause', 'no_cause', 'non_payment']
+    origin_columns = ['initiating_action', 'initiating_action', 'initiating_action']
     target_values = [("SP Summons and Complaint - Cause", "SP Transfer - Cause"),
-                     ("SP Summons and Complaint - Foreclosure", "SP Transfer - Foreclosure"),
                      ("SP Summons and Complaint - No Cause", "SP Transfer- No Cause"),
-                     ("SP Summons and Complaint - Non-payment of Rent", "SP Transfer - Non-payment of Rent"),
-                     ('Transfer', 'Transfer')]
+                     ("SP Summons and Complaint - Non-payment of Rent", "SP Transfer - Non-payment of Rent")]
 
     for dummy_column, origin_column, target_value in zip(panel_A_columns, origin_columns, target_values):
         df.loc[:, dummy_column] = np.where((df[origin_column].str.contains(target_value[0])) |

### 2023-01-15 output/DiD/tables/balance_table.tex
Adjusted rows of balance table

@@
 \toprule
- &  & \textit{} & \multicolumn{2}{|c|}{\textit{Difference in Cases Won by Defendant}} \\
- &  & Cases Won by Plaintiff & Unweighted & P-Value \\
+ &  & \multicolumn{2}{|c|}{\textit{}} & \multicolumn{2}{|c|}{\textit{Difference in Cases Won by Defendant}} & \textit{} \\
+ &  & Cases Won by Plaintiff & count & Unweighted & P-Value & N \\
 \midrule
-\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 \\
- & No cause & 0.04 & 0.03 & 0.00 \\
- & Non-payment of rent & 0.11 & -0.03 & 0.03 \\
- & Defendant has an attorney & 0.72 & -0.01 & 0.77 \\
- & Plaintiff has an attorney & 0.02 & -0.02 & 0.00 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant is an entity & 0.07 & -0.14 & 0.00 \\
- & Plaintiff is an entity & 0.80 & 0.01 & 0.47 \\
- & Total property value & 0.01 & 0.00 & 0.37 \\
- & Building value & 0.66 & 0.03 & 0.13 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Land value & 6554743.50 & 184134.63 & 0.79 \\
- & Other value & 1897711.00 & 25986.91 & 0.90 \\
- & Median household income (2016) & 87585.64 & 22095.39 & 0.21 \\
- & Population density (2010) & 8535625.58 & 232361.89 & 0.78 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median two bedroom rent (2015) & 52087.32 & 2566.82 & 0.01 \\
- & Portion white (2010) & 9031.64 & 944.99 & 0.01 \\
- & rent_twobed2015 & 1093.36 & 34.26 & 0.05 \\
- & share_white2010 & 0.60 & 0.04 & 0.00 \\
-\cline{1-5}
+\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 2440.00 & 0.01 & 0.68 & 3298.00 \\
+ & No cause & 0.11 & 2440.00 & -0.03 & 0.03 & 3298.00 \\
+ & Non-payment of rent & 0.72 & 2440.00 & -0.01 & 0.77 & 3298.00 \\
+\cline{1-7}
+\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & 2440.00 & -0.14 & 0.00 & 3298.00 \\
+ & Plaintiff has an attorney & 0.80 & 2440.00 & 0.01 & 0.47 & 3298.00 \\
+ & Defendant is an entity & 0.01 & 2440.00 & 0.00 & 0.37 & 3298.00 \\
+ & Plaintiff is an entity & 0.66 & 2440.00 & 0.03 & 0.13 & 3298.00 \\
+\cline{1-7}
+\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 6554743.50 & 2206.00 & 184134.63 & 0.79 & 3021.00 \\
+ & Land value & 1897711.00 & 2206.00 & 25986.91 & 0.90 & 3021.00 \\
+ & Other value & 87585.64 & 2206.00 & 22095.39 & 0.21 & 3021.00 \\
+ & Total property value & 8535625.58 & 2206.00 & 232361.89 & 0.78 & 3021.00 \\
+\cline{1-7}
+\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52087.32 & 2439.00 & 2566.82 & 0.01 & 3297.00 \\
+ & Population density (2010) & 9031.64 & 2439.00 & 944.99 & 0.01 & 3297.00 \\
+ & Median two bedroom rent (2015) & 1093.36 & 1866.00 & 34.26 & 0.05 & 2488.00 \\
+ & Portion white (2010) & 0.60 & 2439.00 & 0.04 & 0.00 & 3297.00 \\
+\cline{1-7}
 \bottomrule

### 2023-01-15 output/summary_statistics/tables/summary_statistics.tex
Adjusted rows of balance table

@@
 \toprule
- &  & Mean & S.D. & N \\
-Panel & Variable &  &  &  \\
+ &  & Mean & Median & S.D. & N \\
+Panel & Variable &  &  &  &  \\
 \midrule
-\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.33 & 40,727 \\
- & No cause & 0.11 & 0.31 & 40,727 \\
- & Non-payment of rent & 0.75 & 0.43 & 40,727 \\
-\cline{1-5}
-\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,727 \\
- & Case dismised & 0.29 & 0.45 & 40,727 \\
- & Case duration & 57.81 & 78.29 & 39,087 \\
- & Case heard & 0.06 & 0.23 & 40,727 \\
- & Case mediated & 0.41 & 0.49 & 40,727 \\
- & Money judgment & 1,890.34 & 5,279.49 & 40,727 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,727 \\
- & Defendant is an entity & 0.01 & 0.08 & 40,727 \\
- & Plaintiff has an attorney & 0.84 & 0.37 & 40,727 \\
- & Plaintiff is an entity & 0.70 & 0.46 & 40,727 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 8,350,204.19 & 22,073,916.94 & 36,587 \\
- & Land value & 2,471,065.61 & 6,218,383.08 & 36,587 \\
- & Other value & 112,575.80 & 659,661.29 & 36,587 \\
- & Total property value & 10,900,678.30 & 26,482,630.60 & 36,587 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 27,177.48 & 40,726 \\
- & Median two bedroom rent (2015) & 1,116.27 & 396.29 & 30,537 \\
- & Population density (2010) & 9,159.77 & 9,574.14 & 40,726 \\
- & Portion white (2010) & 0.58 & 0.29 & 40,726 \\
-\cline{1-5}
-\multirow[c]{9}{4cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377,384.02 & 316,645.29 & 10,096 \\
- & Five years before filing date & 261,462.86 & 238,040.64 & 9,842 \\
- & Four years before filing date & 280,243.32 & 276,051.45 & 9,968 \\
- & One year after filing date & 421,601.75 & 344,328.86 & 10,443 \\
- & One year before filing date & 351,172.05 & 311,982.74 & 10,190 \\
- & Three years after filing date & 501,611.80 & 780,467.01 & 5,894 \\
- & Three years before filing date & 307,137.16 & 369,763.53 & 10,172 \\
- & Two years after filing date & 477,948.08 & 457,694.83 & 9,175 \\
- & Two years before filing date & 341,084.08 & 987,145.51 & 10,182 \\
-\cline{1-5}
+\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.000000 & 0.33 & 40,727 \\
+ & No cause & 0.11 & 0.000000 & 0.31 & 40,727 \\
+ & Non-payment of rent & 0.75 & 1.000000 & 0.43 & 40,727 \\
+\cline{1-6}
+\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.000000 & 0.40 & 40,727 \\
+ & Case dismised & 0.29 & 0.000000 & 0.45 & 40,727 \\
+ & Case duration & 57.81 & 21.000000 & 78.29 & 39,087 \\
+ & Case heard & 0.06 & 0.000000 & 0.23 & 40,727 \\
+ & Case mediated & 0.41 & 0.000000 & 0.49 & 40,727 \\
+ & Money judgment & 1,890.34 & 0.000000 & 5,279.49 & 40,727 \\
+\cline{1-6}
+\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.000000 & 0.28 & 40,727 \\
+ & Defendant is an entity & 0.01 & 0.000000 & 0.08 & 40,727 \\
+ & Plaintiff has an attorney & 0.84 & 1.000000 & 0.37 & 40,727 \\
+ & Plaintiff is an entity & 0.70 & 1.000000 & 0.46 & 40,727 \\
+\cline{1-6}
+\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 8,350,204.19 & 636500.000000 & 22,073,916.94 & 36,587 \\
+ & Land value & 2,471,065.61 & 192400.000000 & 6,218,383.08 & 36,587 \\
+ & Other value & 112,575.80 & 1000.000000 & 659,661.29 & 36,587 \\
+ & Total property value & 10,900,678.30 & 954900.000000 & 26,482,630.60 & 36,587 \\
+\cline{1-6}
+\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47105.000000 & 27,177.48 & 40,726 \\
+ & Median two bedroom rent (2015) & 1,116.27 & 1055.000000 & 396.29 & 30,537 \\
+ & Population density (2010) & 9,159.77 & 5978.609400 & 9,574.14 & 40,726 \\
+ & Portion white (2010) & 0.58 & 0.630612 & 0.29 & 40,726 \\
+\cline{1-6}
+\multirow[c]{9}{4cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377,384.02 & 305144.000000 & 316,645.29 & 10,096 \\
+ & Five years before filing date & 261,462.86 & 213270.600000 & 238,040.64 & 9,842 \\
+ & Four years before filing date & 280,243.32 & 225065.750000 & 276,051.45 & 9,968 \\
+ & One year after filing date & 421,601.75 & 347550.000000 & 344,328.86 & 10,443 \\
+ & One year before filing date & 351,172.05 & 278722.250000 & 311,982.74 & 10,190 \\
+ & Three years after filing date & 501,611.80 & 414600.000000 & 780,467.01 & 5,894 \\
+ & Three years before filing date & 307,137.16 & 240097.375000 & 369,763.53 & 10,172 \\
+ & Two years after filing date & 477,948.08 & 393900.000000 & 457,694.83 & 9,175 \\
+ & Two years before filing date & 341,084.08 & 259176.000000 & 987,145.51 & 10,182 \\
+\cline{1-6}
 \bottomrule

### 2023-01-15 src/02_analysis/analysis_utilities.py

@@ -83,6 +83,6 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     panel_F = pd.concat([panel_F], keys=["Panel F: Zestimates Around Filing Date"])
 
     # Concatenate Panels A-E
-    summary_statistics = pd.concat([panel_A, panel_B, panel_C, panel_D, panel_E, panel_F], axis=0)[['mean', 'std', 'count']]
+    summary_statistics = pd.concat([panel_A, panel_B, panel_C, panel_D, panel_E, panel_F], axis=0)[['mean', '50%', 'std', 'count']]
 
     return summary_statistics

### 2023-01-15 output/DiD/tables/balance_table.tex
Adjusted rows of balance table

--- 2023-01-15 output/DiD/tables/balance_table.tex
@@
 \toprule
- &  & \textit{} & \multicolumn{2}{|c|}{\textit{Difference in Cases Won by Defendant}} \\
- &  & Cases Won by Plaintiff & Unweighted & P-Value \\
+ &  & \textit{} & \multicolumn{2}{|c|}{\textit{Difference in Cases Won by Defendant}} & \textit{} \\
+ &  & Cases Won by Plaintiff & Unweighted & P-Value & N \\
 \midrule
-\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 \\
- & No cause & 0.04 & 0.03 & 0.00 \\
- & Non-payment of rent & 0.11 & -0.03 & 0.03 \\
- & Defendant has an attorney & 0.72 & -0.01 & 0.77 \\
- & Plaintiff has an attorney & 0.02 & -0.02 & 0.00 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant is an entity & 0.07 & -0.14 & 0.00 \\
- & Plaintiff is an entity & 0.80 & 0.01 & 0.47 \\
- & Total property value & 0.01 & 0.00 & 0.37 \\
- & Building value & 0.66 & 0.03 & 0.13 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Land value & 6554743.50 & 184134.63 & 0.79 \\
- & Other value & 1897711.00 & 25986.91 & 0.90 \\
- & Median household income (2016) & 87585.64 & 22095.39 & 0.21 \\
- & Population density (2010) & 8535625.58 & 232361.89 & 0.78 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median two bedroom rent (2015) & 52087.32 & 2566.82 & 0.01 \\
- & Portion white (2010) & 9031.64 & 944.99 & 0.01 \\
- & rent_twobed2015 & 1093.36 & 34.26 & 0.05 \\
- & share_white2010 & 0.60 & 0.04 & 0.00 \\
-\cline{1-5}
+\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 3298.00 \\
+ & No cause & 0.11 & -0.03 & 0.03 & 3298.00 \\
+ & Non-payment of rent & 0.72 & -0.01 & 0.77 & 3298.00 \\
+\cline{1-6}
+\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & 3298.00 \\
+ & Plaintiff has an attorney & 0.80 & 0.01 & 0.47 & 3298.00 \\
+ & Defendant is an entity & 0.01 & 0.00 & 0.37 & 3298.00 \\
+ & Plaintiff is an entity & 0.66 & 0.03 & 0.13 & 3298.00 \\
+\cline{1-6}
+\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 6554743.50 & 184134.63 & 0.79 & 3021.00 \\
+ & Land value & 1897711.00 & 25986.91 & 0.90 & 3021.00 \\
+ & Other value & 87585.64 & 22095.39 & 0.21 & 3021.00 \\
+ & Total property value & 8535625.58 & 232361.89 & 0.78 & 3021.00 \\
+\cline{1-6}
+\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52087.32 & 2566.82 & 0.01 & 3297.00 \\
+ & Population density (2010) & 9031.64 & 944.99 & 0.01 & 3297.00 \\
+ & Median two bedroom rent (2015) & 1093.36 & 34.26 & 0.05 & 2488.00 \\
+ & Portion white (2010) & 0.60 & 0.04 & 0.00 & 3297.00 \\
+\cline{1-6}
 \bottomrule

### 2023-01-15 output/summary_statistics/tables/summary_statistics.tex
Adjusted rows of balance table

--- 2023-01-15 output/summary_statistics/tables/summary_statistics.tex
@@
 \toprule
- &  & Mean & S.D. & N \\
-Panel & Variable &  &  &  \\
+ &  & Mean & Median & S.D. & N \\
+Panel & Variable &  &  &  &  \\
 \midrule
-\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.33 & 40,727 \\
- & No cause & 0.11 & 0.31 & 40,727 \\
- & Non-payment of rent & 0.75 & 0.43 & 40,727 \\
-\cline{1-5}
-\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,727 \\
- & Case dismised & 0.29 & 0.45 & 40,727 \\
- & Case duration & 57.81 & 78.29 & 39,087 \\
- & Case heard & 0.06 & 0.23 & 40,727 \\
- & Case mediated & 0.41 & 0.49 & 40,727 \\
- & Money judgment & 1,890.34 & 5,279.49 & 40,727 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,727 \\
- & Defendant is an entity & 0.01 & 0.08 & 40,727 \\
- & Plaintiff has an attorney & 0.84 & 0.37 & 40,727 \\
- & Plaintiff is an entity & 0.70 & 0.46 & 40,727 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 8,350,204.19 & 22,073,916.94 & 36,587 \\
- & Land value & 2,471,065.61 & 6,218,383.08 & 36,587 \\
- & Other value & 112,575.80 & 659,661.29 & 36,587 \\
- & Total property value & 10,900,678.30 & 26,482,630.60 & 36,587 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 27,177.48 & 40,726 \\
- & Median two bedroom rent (2015) & 1,116.27 & 396.29 & 30,537 \\
- & Population density (2010) & 9,159.77 & 9,574.14 & 40,726 \\
- & Portion white (2010) & 0.58 & 0.29 & 40,726 \\
-\cline{1-5}
-\multirow[c]{9}{4cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377,384.02 & 316,645.29 & 10,096 \\
- & Five years before filing date & 261,462.86 & 238,040.64 & 9,842 \\
- & Four years before filing date & 280,243.32 & 276,051.45 & 9,968 \\
- & One year after filing date & 421,601.75 & 344,328.86 & 10,443 \\
- & One year before filing date & 351,172.05 & 311,982.74 & 10,190 \\
- & Three years after filing date & 501,611.80 & 780,467.01 & 5,894 \\
- & Three years before filing date & 307,137.16 & 369,763.53 & 10,172 \\
- & Two years after filing date & 477,948.08 & 457,694.83 & 9,175 \\
- & Two years before filing date & 341,084.08 & 987,145.51 & 10,182 \\
-\cline{1-5}
+\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
+ & No cause & 0.11 & 0.00 & 0.31 & 40,727 \\
+ & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,727 \\
+\cline{1-6}
+\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
+ & Case dismised & 0.29 & 0.00 & 0.45 & 40,727 \\
+ & Case duration & 57.81 & 21.00 & 78.29 & 39,087 \\
+ & Case heard & 0.06 & 0.00 & 0.23 & 40,727 \\
+ & Case mediated & 0.41 & 0.00 & 0.49 & 40,727 \\
+ & Money judgment & 1,890.34 & 0.00 & 5,279.49 & 40,727 \\
+\cline{1-6}
+\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
+ & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,727 \\
+ & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,727 \\
+ & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,727 \\
+\cline{1-6}
+\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 8,350,204.19 & 636,500.00 & 22,073,916.94 & 36,587 \\
+ & Land value & 2,471,065.61 & 192,400.00 & 6,218,383.08 & 36,587 \\
+ & Other value & 112,575.80 & 1,000.00 & 659,661.29 & 36,587 \\
+ & Total property value & 10,900,678.30 & 954,900.00 & 26,482,630.60 & 36,587 \\
+\cline{1-6}
+\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
+ & Median two bedroom rent (2015) & 1,116.27 & 1,055.00 & 396.29 & 30,537 \\
+ & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
+ & Portion white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
+\cline{1-6}
+\multirow[c]{9}{4cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377,384.02 & 305,144.00 & 316,645.29 & 10,096 \\
+ & Five years before filing date & 261,462.86 & 213,270.60 & 238,040.64 & 9,842 \\
+ & Four years before filing date & 280,243.32 & 225,065.75 & 276,051.45 & 9,968 \\
+ & One year after filing date & 421,601.75 & 347,550.00 & 344,328.86 & 10,443 \\
+ & One year before filing date & 351,172.05 & 278,722.25 & 311,982.74 & 10,190 \\
+ & Three years after filing date & 501,611.80 & 414,600.00 & 780,467.01 & 5,894 \\
+ & Three years before filing date & 307,137.16 & 240,097.38 & 369,763.53 & 10,172 \\
+ & Two years after filing date & 477,948.08 & 393,900.00 & 457,694.83 & 9,175 \\
+ & Two years before filing date & 341,084.08 & 259,176.00 & 987,145.51 & 10,182 \\
+\cline{1-6}
 \bottomrule

### 2023-01-15 output/DiD/tables/balance_table.tex
Adjusted rows of balance table

@@
 \midrule
-\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 3298.00 \\
- & No cause & 0.11 & -0.03 & 0.03 & 3298.00 \\
- & Non-payment of rent & 0.72 & -0.01 & 0.77 & 3298.00 \\
+\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.124180 & 0.01 & 0.68 & 3,298.000000 \\
+ & No cause & 0.111066 & -0.03 & 0.03 & 3,298.000000 \\
+ & Non-payment of rent & 0.720902 & -0.01 & 0.77 & 3,298.000000 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & 3298.00 \\
- & Plaintiff has an attorney & 0.80 & 0.01 & 0.47 & 3298.00 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.37 & 3298.00 \\
- & Plaintiff is an entity & 0.66 & 0.03 & 0.13 & 3298.00 \\
+\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.065984 & -0.14 & 0.00 & 3,298.000000 \\
+ & Plaintiff has an attorney & 0.795902 & 0.01 & 0.47 & 3,298.000000 \\
+ & Defendant is an entity & 0.011885 & 0.00 & 0.37 & 3,298.000000 \\
+ & Plaintiff is an entity & 0.659426 & 0.03 & 0.13 & 3,298.000000 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 6554743.50 & 184134.63 & 0.79 & 3021.00 \\
- & Land value & 1897711.00 & 25986.91 & 0.90 & 3021.00 \\
- & Other value & 87585.64 & 22095.39 & 0.21 & 3021.00 \\
- & Total property value & 8535625.58 & 232361.89 & 0.78 & 3021.00 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 6,554,743.504986 & 184,134.63 & 0.79 & 3,021.000000 \\
+ & Land value & 1,897,710.995467 & 25,986.91 & 0.90 & 3,021.000000 \\
+ & Other value & 87,585.642792 & 22,095.39 & 0.21 & 3,021.000000 \\
+ & Total property value & 8,535,625.582956 & 232,361.89 & 0.78 & 3,021.000000 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52087.32 & 2566.82 & 0.01 & 3297.00 \\
- & Population density (2010) & 9031.64 & 944.99 & 0.01 & 3297.00 \\
- & Median two bedroom rent (2015) & 1093.36 & 34.26 & 0.05 & 2488.00 \\
- & Portion white (2010) & 0.60 & 0.04 & 0.00 & 3297.00 \\
+\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.323083 & 2,566.82 & 0.01 & 3,297.000000 \\
+ & Population density (2010) & 9,031.635095 & 944.99 & 0.01 & 3,297.000000 \\
+ & Median two bedroom rent (2015) & 1,093.360129 & 34.26 & 0.05 & 2,488.000000 \\
+ & Portion white (2010) & 0.602099 & 0.04 & 0.00 & 3,297.000000 \\
 \cline{1-6}

### 2023-01-15 output/DiD/tables/balance_table.tex
Adjusted rows of balance table

--- 2023-01-15 output/DiD/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 3298.00 \\
- & No cause & 0.11 & -0.03 & 0.03 & 3298.00 \\
- & Non-payment of rent & 0.72 & -0.01 & 0.77 & 3298.00 \\
+\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 3,298 \\
+ & No cause & 0.11 & -0.03 & 0.03 & 3,298 \\
+ & Non-payment of rent & 0.72 & -0.01 & 0.77 & 3,298 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & 3298.00 \\
- & Plaintiff has an attorney & 0.80 & 0.01 & 0.47 & 3298.00 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.37 & 3298.00 \\
- & Plaintiff is an entity & 0.66 & 0.03 & 0.13 & 3298.00 \\
+\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & 3,298 \\
+ & Plaintiff has an attorney & 0.80 & 0.01 & 0.47 & 3,298 \\
+ & Defendant is an entity & 0.01 & 0.00 & 0.37 & 3,298 \\
+ & Plaintiff is an entity & 0.66 & 0.03 & 0.13 & 3,298 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 6554743.50 & 184134.63 & 0.79 & 3021.00 \\
- & Land value & 1897711.00 & 25986.91 & 0.90 & 3021.00 \\
- & Other value & 87585.64 & 22095.39 & 0.21 & 3021.00 \\
- & Total property value & 8535625.58 & 232361.89 & 0.78 & 3021.00 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 6,554,743.50 & 184,134.63 & 0.79 & 3,021 \\
+ & Land value & 1,897,711.00 & 25,986.91 & 0.90 & 3,021 \\
+ & Other value & 87,585.64 & 22,095.39 & 0.21 & 3,021 \\
+ & Total property value & 8,535,625.58 & 232,361.89 & 0.78 & 3,021 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52087.32 & 2566.82 & 0.01 & 3297.00 \\
- & Population density (2010) & 9031.64 & 944.99 & 0.01 & 3297.00 \\
- & Median two bedroom rent (2015) & 1093.36 & 34.26 & 0.05 & 2488.00 \\
- & Portion white (2010) & 0.60 & 0.04 & 0.00 & 3297.00 \\
+\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 3,297 \\
+ & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 3,297 \\
+ & Median two bedroom rent (2015) & 1,093.36 & 34.26 & 0.05 & 2,488 \\
+ & Portion white (2010) & 0.60 & 0.04 & 0.00 & 3,297 \\
 \cline{1-6}

### 2023-01-15 output/DiD/tables/balance_table.tex
Adjusted rows of balance table

@@
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 6,554,743.50 & 184,134.63 & 0.79 & 3,021 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records}} & Building value & 6,554,743.50 & 184,134.63 & 0.79 & 3,021 \\
  & Land value & 1,897,711.00 & 25,986.91 & 0.90 & 3,021 \\

### 2023-01-15 output/summary_statistics/tables/summary_statistics.tex
Adjusted rows of balance table

@@
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 8,350,204.19 & 636,500.00 & 22,073,916.94 & 36,587 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records}} & Building value & 8,350,204.19 & 636,500.00 & 22,073,916.94 & 36,587 \\
  & Land value & 2,471,065.61 & 192,400.00 & 6,218,383.08 & 36,587 \\

### 2023-01-15 output/summary_statistics/tables/summary_statistics.tex
Updates from Overleaf

@@
 \midrule
-\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
+\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
  & No cause & 0.11 & 0.00 & 0.31 & 40,727 \\
@@
 \cline{1-6}
-\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
+\multirow[c]{6}{3cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
  & Case dismised & 0.29 & 0.00 & 0.45 & 40,727 \\
@@
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
+\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
  & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,727 \\
@@
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records}} & Building value & 8,350,204.19 & 636,500.00 & 22,073,916.94 & 36,587 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 8,350,204.19 & 636,500.00 & 22,073,916.94 & 36,587 \\
  & Land value & 2,471,065.61 & 192,400.00 & 6,218,383.08 & 36,587 \\
@@
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
+\multirow[c]{4}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
  & Median two bedroom rent (2015) & 1,116.27 & 1,055.00 & 396.29 & 30,537 \\
@@
 \cline{1-6}
-\multirow[c]{9}{4cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377,384.02 & 305,144.00 & 316,645.29 & 10,096 \\
+\multirow[c]{9}{3cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377,384.02 & 305,144.00 & 316,645.29 & 10,096 \\
  & Five years before filing date & 261,462.86 & 213,270.60 & 238,040.64 & 9,842 \\

### 2023-01-15 output/summary_statistics/tables/summary_statistics.tex

@@
 \cline{1-6}
-\multirow[c]{4}{3cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 8,350,204.19 & 636,500.00 & 22,073,916.94 & 36,587 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records}} & Building value & 8,350,204.19 & 636,500.00 & 22,073,916.94 & 36,587 \\
  & Land value & 2,471,065.61 & 192,400.00 & 6,218,383.08 & 36,587 \\

### 2023-01-15 output/DiD/tables/balance_table.tex
Adjusted rows of balance table

@@
 \midrule
-\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 3,298 \\
+\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 3,298 \\
  & No cause & 0.11 & -0.03 & 0.03 & 3,298 \\
@@
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & 3,298 \\
+\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & 3,298 \\
  & Plaintiff has an attorney & 0.80 & 0.01 & 0.47 & 3,298 \\
@@
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records}} & Building value & 6,554,743.50 & 184,134.63 & 0.79 & 3,021 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Assessor Records}} & Building value & 6,554,743.50 & 184,134.63 & 0.79 & 3,021 \\
  & Land value & 1,897,711.00 & 25,986.91 & 0.90 & 3,021 \\
@@
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 3,297 \\
+\multirow[c]{4}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 3,297 \\
  & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 3,297 \\

### 2023-01-15 output/summary_statistics/tables/summary_statistics.tex
Adjusted rows of balance table

@@
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records}} & Building value & 8,350,204.19 & 636,500.00 & 22,073,916.94 & 36,587 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Assessor Records}} & Building value & 8,350,204.19 & 636,500.00 & 22,073,916.94 & 36,587 \\
  & Land value & 2,471,065.61 & 192,400.00 & 6,218,383.08 & 36,587 \\

### 2023-01-16 output/DiD/tables/balance_table.tex
Added weighted comparisons to balance table

@@
 \toprule
- &  & \textit{} & \multicolumn{2}{|c|}{\textit{Difference in Cases Won by Defendant}} & \textit{} \\
- &  & Cases Won by Plaintiff & Unweighted & P-Value & N \\
+ &  & \textit{} & \multicolumn{4}{|c|}{\textit{Difference in Cases Won by Defendant}} \\
+ &  & Cases Won by Plaintiff & Unweighted & P-Value & Propensity Score Weighted & P-Value \\
 \midrule
-\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 3,298 \\
- & No cause & 0.11 & -0.03 & 0.03 & 3,298 \\
- & Non-payment of rent & 0.72 & -0.01 & 0.77 & 3,298 \\
-\cline{1-6}
-\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & 3,298 \\
- & Plaintiff has an attorney & 0.80 & 0.01 & 0.47 & 3,298 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.37 & 3,298 \\
- & Plaintiff is an entity & 0.66 & 0.03 & 0.13 & 3,298 \\
-\cline{1-6}
-\multirow[c]{4}{3cm}{\textit{Panel D: Assessor Records}} & Building value & 6,554,743.50 & 184,134.63 & 0.79 & 3,021 \\
- & Land value & 1,897,711.00 & 25,986.91 & 0.90 & 3,021 \\
- & Other value & 87,585.64 & 22,095.39 & 0.21 & 3,021 \\
- & Total property value & 8,535,625.58 & 232,361.89 & 0.78 & 3,021 \\
-\cline{1-6}
-\multirow[c]{4}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 3,297 \\
- & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 3,297 \\
- & Median two bedroom rent (2015) & 1,093.36 & 34.26 & 0.05 & 2,488 \\
- & Portion white (2010) & 0.60 & 0.04 & 0.00 & 3,297 \\
-\cline{1-6}
+\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 0.009452 & 0.47 \\
+ & No cause & 0.11 & -0.03 & 0.03 & -0.025388 & 0.05 \\
+ & Non-payment of rent & 0.72 & -0.01 & 0.76 & -0.006068 & 0.73 \\
+\cline{1-7}
+\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & -0.122710 & 0.00 \\
+ & Plaintiff has an attorney & 0.80 & 0.01 & 0.48 & 0.011622 & 0.47 \\
+ & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.002972 & 0.47 \\
+ & Plaintiff is an entity & 0.66 & 0.03 & 0.12 & 0.028722 & 0.13 \\
+\cline{1-7}
+\multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 0.04 & 0.00 & 0.028645 & 0.01 \\
+ & Population density (2010) & 9,031.64 & 0.06 & 0.25 & 0.058879 & 0.24 \\
+ & Portion white (2010) & 0.60 & 0.06 & 0.01 & 0.050925 & 0.02 \\
+\cline{1-7}
 \bottomrule

### 2023-01-16 output/summary_statistics/tables/summary_statistics.tex
Added weighted comparisons to balance table

@@
 \cline{1-6}
-\multirow[c]{4}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
- & Median two bedroom rent (2015) & 1,116.27 & 1,055.00 & 396.29 & 30,537 \\
+\multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
  & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\

### 2023-01-16 src/02_analysis/figure_utilities.py

@@ -41,6 +41,8 @@ def plot_scatter_with_shaded_errors(ax: plt.Axes,
                                     marker: str = 'o',
                                     error_color: str = figure_and_table_constants.Colors.P1,
                                     error_opacity: float = 0.5,
+                                    edge_color: str = figure_and_table_constants.Colors.P1,
+                                    edge_style: str = '-',
                                     zorder=None):
     """
 
@@ -57,12 +59,21 @@ def plot_scatter_with_shaded_errors(ax: plt.Axes,
     :param error_opacity: 
     :param zorder: 
     """
+
     if zorder is None:
         ax.scatter(x, y, color=point_color, marker=marker, s=point_size, label=label)
+        ax.fill_between(x, y_upper, y_lower, color=error_color, alpha=error_opacity, edgecolor=edge_color,
+                        linestyle=edge_style)
+        ax.axvline(x=x.min(), color='white')
+        ax.axvline(x=x.max(), color='white')
     else:
-        ax.scatter(x, y, color=point_color, marker=marker, s=point_size, label=label, zorder=zorder)
+        ax.fill_between(x, y_upper, y_lower, color=error_color, alpha=error_opacity, edgecolor=edge_color,
+                        linestyle=edge_style, zorder=zorder)
+        ax.axvline(x=x.min(), color='white', zorder=zorder+1)
+        ax.axvline(x=x.max(), color='white', zorder=zorder+1)
+        ax.scatter(x, y, color=point_color, marker=marker, s=point_size, label=label, zorder=zorder+2)
 
-    ax.fill_between(x, y_upper, y_lower, color=error_color, alpha=error_opacity)
+
 
 
 def plot_scatter_with_error_bars(ax: plt.Axes,
@@ -95,9 +106,11 @@ def plot_scatter_with_error_bars(ax: plt.Axes,
     yerr = (y_upper - y_lower) / 2
     ecolor = to_rgba(error_color, alpha=error_opacity)
     if zorder is None:
-        ax.errorbar(x, y, yerr=yerr, color=point_color, ms=point_size, ecolor=ecolor, fmt=marker, label=label, capsize=3)
+        ax.errorbar(x, y, yerr=yerr, color=point_color, ms=point_size, ecolor=ecolor, fmt=marker, label=label,
+                    capsize=3)
     else:
[…]

### 2023-01-16 output/DiD/tables/balance_table.tex
Added weighted comparisons to balance table

@@
-\begin{tabular}{llcccc}
+\begin{tabular}{llccccc}
 \toprule
  &  & \textit{} & \multicolumn{4}{|c|}{\textit{Difference in Cases Won by Defendant}} \\
- &  & Cases Won by Plaintiff & Unweighted & P-Value & Propensity Score Weighted & P-Value \\
+ &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
 \midrule
-\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 0.009452 & 0.47 \\
- & No cause & 0.11 & -0.03 & 0.03 & -0.025388 & 0.05 \\
- & Non-payment of rent & 0.72 & -0.01 & 0.76 & -0.006068 & 0.73 \\
+\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.681457 & 0.009452 & 0.469633 \\
+ & No cause & 0.11 & -0.03 & 0.031417 & -0.025388 & 0.048559 \\
+ & Non-payment of rent & 0.72 & -0.01 & 0.764855 & -0.006068 & 0.734137 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & -0.122710 & 0.00 \\
- & Plaintiff has an attorney & 0.80 & 0.01 & 0.48 & 0.011622 & 0.47 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.002972 & 0.47 \\
- & Plaintiff is an entity & 0.66 & 0.03 & 0.12 & 0.028722 & 0.13 \\
+\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.000000 & -0.122710 & 0.000000 \\
+ & Plaintiff has an attorney & 0.80 & 0.01 & 0.477297 & 0.011622 & 0.472201 \\
+ & Defendant is an entity & 0.01 & 0.00 & 0.365805 & 0.002972 & 0.473092 \\
+ & Plaintiff is an entity & 0.66 & 0.03 & 0.123046 & 0.028722 & 0.130518 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 0.04 & 0.00 & 0.028645 & 0.01 \\
- & Population density (2010) & 9,031.64 & 0.06 & 0.25 & 0.058879 & 0.24 \\
- & Portion white (2010) & 0.60 & 0.06 & 0.01 & 0.050925 & 0.02 \\
+\multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 0.04 & 0.002114 & 0.028645 & 0.011994 \\
+ & Population density (2010) & 9,031.64 & 0.06 & 0.245975 & 0.058879 & 0.235340 \\
+ & Portion white (2010) & 0.60 & 0.06 & 0.007126 & 0.050925 & 0.015556 \\
 \cline{1-7}

### 2023-01-16 output/DiD/tables/balance_table.tex
Added weighted comparisons to balance table

--- 2023-01-16 output/DiD/tables/balance_table.tex
@@
-\begin{tabular}{llcccc}
+\begin{tabular}{llccccc}
 \toprule
- &  & \textit{} & \multicolumn{4}{|c|}{\textit{Difference in Cases Won by Defendant}} \\
- &  & Cases Won by Plaintiff & Unweighted & P-Value & Propensity Score Weighted & P-Value \\
+ &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
+ &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
 \midrule
-\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 0.009452 & 0.47 \\
- & No cause & 0.11 & -0.03 & 0.03 & -0.025388 & 0.05 \\
- & Non-payment of rent & 0.72 & -0.01 & 0.76 & -0.006068 & 0.73 \\
+\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 0.01 & 0.47 \\
+ & No cause & 0.11 & -0.03 & 0.03 & -0.03 & 0.05 \\
+ & Non-payment of rent & 0.72 & -0.01 & 0.76 & -0.01 & 0.73 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & -0.122710 & 0.00 \\
- & Plaintiff has an attorney & 0.80 & 0.01 & 0.48 & 0.011622 & 0.47 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.002972 & 0.47 \\
- & Plaintiff is an entity & 0.66 & 0.03 & 0.12 & 0.028722 & 0.13 \\
+\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & -0.12 & 0.00 \\
+ & Plaintiff has an attorney & 0.80 & 0.01 & 0.48 & 0.01 & 0.47 \\
+ & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.47 \\
+ & Plaintiff is an entity & 0.66 & 0.03 & 0.12 & 0.03 & 0.13 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 0.04 & 0.00 & 0.028645 & 0.01 \\
- & Population density (2010) & 9,031.64 & 0.06 & 0.25 & 0.058879 & 0.24 \\
- & Portion white (2010) & 0.60 & 0.06 & 0.01 & 0.050925 & 0.02 \\
+\multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 0.04 & 0.00 & 0.03 & 0.01 \\
+ & Population density (2010) & 9,031.64 & 0.06 & 0.25 & 0.06 & 0.24 \\
+ & Portion white (2010) & 0.60 & 0.06 & 0.01 & 0.05 & 0.02 \\
 \cline{1-7}

### 2023-01-16 output/DiD/tables/balance_table.tex
Added weighted comparisons to balance table

@@
  & No cause & 0.11 & -0.03 & 0.03 & -0.03 & 0.05 \\
- & Non-payment of rent & 0.72 & -0.01 & 0.76 & -0.01 & 0.73 \\
+ & Non-payment of rent & 0.72 & -0.01 & 0.76 & -0.01 & 0.74 \\
 \cline{1-7}
 \multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & -0.12 & 0.00 \\
- & Plaintiff has an attorney & 0.80 & 0.01 & 0.48 & 0.01 & 0.47 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.47 \\
+ & Plaintiff has an attorney & 0.80 & 0.01 & 0.48 & 0.01 & 0.45 \\
+ & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.49 \\
  & Plaintiff is an entity & 0.66 & 0.03 & 0.12 & 0.03 & 0.13 \\
@@
 \multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 0.04 & 0.00 & 0.03 & 0.01 \\
- & Population density (2010) & 9,031.64 & 0.06 & 0.25 & 0.06 & 0.24 \\
- & Portion white (2010) & 0.60 & 0.06 & 0.01 & 0.05 & 0.02 \\
+ & Population density (2010) & 9,031.64 & 2,582.84 & 0.10 & 2,257.08 & 0.15 \\
+ & Portion white (2010) & 0.60 & 0.06 & 0.25 & 0.06 & 0.25 \\
+\cline{1-7}
+\multirow[c]{3}{3cm}{\textit{Panel F: Zestimates Before Filing Date}} & Two years before filing date & 323,394.56 & 0.06 & 0.01 & 0.05 & 0.02 \\
+ & One year before filing date & 346,196.66 & 0.08 & 0.00 & 0.07 & 0.00 \\
+ & Change in Zestimate over five years before treatment & 22,802.10 & 0.09 & 0.00 & 0.08 & 0.00 \\
 \cline{1-7}

### 2023-01-16 src/02_analysis/analysis_utilities.py

@@ -7,6 +7,7 @@ import numpy as np
 import figure_utilities
 from os.path import join
 
+
 def aggregate_by_event_time_and_plot(att_gt,
                                      output_folder: str,
                                      filename: str,
@@ -56,6 +57,7 @@ def aggregate_by_event_time_and_plot(att_gt,
 
     plt.show()
     figure_utilities.save_figure_and_close(fig, join(output_folder, filename))
+
 
 def aggregate_by_time_and_plot(att_gt, int_to_month_dictionary: dict, output_folder: str, filename: str, title: str):
     # Get time-aggregated ATTs.
@@ -145,12 +147,14 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     panel_E = df[sorted(panel_E_columns)].describe().T
     panel_E = pd.concat([panel_E], keys=["Panel E: Census Tract Characteristics"])
 
-    # Panel F: Zestimates Around Last Docket Date
+    # Panel F: Zestimates Before Filing
     # Get month of the latest docket date for each row and use to grab Zestimates at different times prior to treatment.
     df.loc[:, treatment_date_variable] = pd.to_datetime(df[treatment_date_variable])
     df.loc[:, 'nan'] = np.nan
     panel_F_columns = []
-    for i in range(-5, 4):
+    start = -2
+    stop = 0
+    for i in range(start, stop):
         # This column contains the year-month which is i years relative to treatment for each property.
         offset_docket_month = (df[treatment_date_variable] + pd.tseries.offsets.DateOffset(years=i)).dt.strftime(
             '%Y-%m').copy()
@@ -162,12 +166,16 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
 
         # Set column accordingly.
         idx, cols = pd.factorize(offset_docket_month)
-        new_col_name = f'zestimate_{i}_years_relative_to_treatment'
+        if i < 0:
+            new_col_name = f'zestimate_minus{-1*i}_years_relative_to_treatment'
+        else:
+            new_col_name = f'zestimate_{i}_years_relative_to_treatment'
         panel_F_columns.append(new_col_name)
         df.loc[:, new_col_name] = df.reindex(cols, axis=1).to_numpy()[np.arange(len(df)), idx]
-
[…]

### 2023-01-17 output/DiD/tables/balance_table.tex
About to switch from relative zestimates as controls

@@
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel F: Zestimates Before Filing Date}} & Two years before filing date & 323,394.56 & 0.06 & 0.01 & 0.05 & 0.02 \\
+\multirow[c]{3}{3cm}{\textit{Panel F: Zestimates Before Filing}} & Two years before filing date & 323,394.56 & 0.06 & 0.01 & 0.05 & 0.02 \\
  & One year before filing date & 346,196.66 & 0.08 & 0.00 & 0.07 & 0.00 \\

### 2023-01-17 src/02_analysis/analysis_utilities.py

@@ -175,7 +175,7 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     df.loc[:, 'pre_treatment_zestimate_change'] = df[panel_F_columns[-1]] - df[panel_F_columns[0]]
     panel_F_columns.append('pre_treatment_zestimate_change')
     panel_F = df[panel_F_columns].describe().T
-    panel_F = pd.concat([panel_F], keys=["Panel F: Zestimates Before Filing Date"])
+    panel_F = pd.concat([panel_F], keys=["Panel F: Zestimates Before Filing"])
 
     # Concatenate Panels A-E
     summary_statistics = pd.concat([panel_A, panel_B, panel_C, panel_E, panel_F], axis=0)[

### 2023-01-17 output/summary_statistics/tables/summary_statistics.tex
Updated Zestimates in summary statistics

@@
 \cline{1-6}
-\multirow[c]{4}{3cm}{\textit{Panel D: Assessor Records}} & Building value & 8,350,204.19 & 636,500.00 & 22,073,916.94 & 36,587 \\
- & Land value & 2,471,065.61 & 192,400.00 & 6,218,383.08 & 36,587 \\
- & Other value & 112,575.80 & 1,000.00 & 659,661.29 & 36,587 \\
- & Total property value & 10,900,678.30 & 954,900.00 & 26,482,630.60 & 36,587 \\
-\cline{1-6}
 \multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
@@
 \cline{1-6}
-\multirow[c]{9}{3cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377,384.02 & 305,144.00 & 316,645.29 & 10,096 \\
- & Five years before filing date & 261,462.86 & 213,270.60 & 238,040.64 & 9,842 \\
- & Four years before filing date & 280,243.32 & 225,065.75 & 276,051.45 & 9,968 \\
- & One year after filing date & 421,601.75 & 347,550.00 & 344,328.86 & 10,443 \\
- & One year before filing date & 351,172.05 & 278,722.25 & 311,982.74 & 10,190 \\
- & Three years after filing date & 501,611.80 & 414,600.00 & 780,467.01 & 5,894 \\
- & Three years before filing date & 307,137.16 & 240,097.38 & 369,763.53 & 10,172 \\
- & Two years after filing date & 477,948.08 & 393,900.00 & 457,694.83 & 9,175 \\
- & Two years before filing date & 341,084.08 & 259,176.00 & 987,145.51 & 10,182 \\
+\multirow[c]{2}{3cm}{\textit{Panel F: Pretreatment Zestimates}} & Change from Jan. 2018 to Jan. 2019 & 22,601.20 & 15,786.00 & 74,245.92 & 10,170 \\
+ & Jan. 2018 & 322,775.21 & 256,528.00 & 298,417.63 & 10,177 \\
 \cline{1-6}

### 2023-01-17 src/02_analysis/analysis_utilities.py

@@ -1,11 +1,13 @@
 """
 Functions useful for analysis.
 """
-import pandas as pd
+from os.path import join
+
 import matplotlib.pyplot as plt
 import numpy as np
+import pandas as pd
+
 import figure_utilities
-from os.path import join
 
 
 def aggregate_by_event_time_and_plot(att_gt,
@@ -148,37 +150,39 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     panel_E = pd.concat([panel_E], keys=["Panel E: Census Tract Characteristics"])
 
     # Panel F: Zestimates Before Filing
-    # Get month of the latest docket date for each row and use to grab Zestimates at different times prior to treatment.
-    df.loc[:, treatment_date_variable] = pd.to_datetime(df[treatment_date_variable])
-    df.loc[:, 'nan'] = np.nan
-    panel_F_columns = []
-    start = -2
-    stop = 0
-    for i in range(start, stop):
-        # This column contains the year-month which is i years relative to treatment for each property.
-        offset_docket_month = (df[treatment_date_variable] + pd.tseries.offsets.DateOffset(years=i)).dt.strftime(
-            '%Y-%m').copy()
-
-        # Some year-months will be outside the range of our data.
-        # For instance, we do not have Zestimates 2 years post-treatment for evictions which occurred in 2022.
-        # For these observations, the offset docket month needs to map to the column of nans we created earlier.
-        offset_docket_month.loc[~offset_docket_month.isin(df.columns)] = 'nan'
-
-        # Set column accordingly.
-        idx, cols = pd.factorize(offset_docket_month)
-        if i < 0:
-            new_col_name = f'zestimate_minus{-1*i}_years_relative_to_treatment'
-        else:
-            new_col_name = f'zestimate_{i}_years_relative_to_treatment'
-        panel_F_columns.append(new_col_name)
-        df.loc[:, new_col_name] = df.reindex(cols, axis=1).to_numpy()[np.arange(len(df)), idx]
-    df.loc[:, 'pre_treatment_zestimate_change'] = df[panel_F_columns[-1]] - df[panel_F_columns[0]]
-    panel_F_columns.append('pre_treatment_zestimate_change')
+    df.loc[:, 'change_in_zestimates_2018_to_2019'] = df['2019-01'] - df['2018-01']
[…]

### 2023-01-17 output/summary_statistics/tables/summary_statistics.tex
Updated Zestimates in summary statistics

@@
 \midrule
-\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change from Jan. 2018 to Jan. 2019 & 22,601.20 & 15,786.00 & 74,245.92 & 10,170 \\
+ & Jan. 2018 & 322,775.21 & 256,528.00 & 298,417.63 & 10,177 \\
+\cline{1-6}
+\multirow[c]{3}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
+ & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
+ & Portion white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
+\cline{1-6}
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
  & No cause & 0.11 & 0.00 & 0.31 & 40,727 \\
@@
 \cline{1-6}
-\multirow[c]{6}{3cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
+ & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,727 \\
+ & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,727 \\
+ & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,727 \\
+\cline{1-6}
+\multirow[c]{6}{3cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
  & Case dismised & 0.29 & 0.00 & 0.45 & 40,727 \\
@@
 \cline{1-6}
-\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,727 \\
- & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,727 \\
- & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,727 \\
-\cline{1-6}
-\multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
- & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
- & Portion white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
-\cline{1-6}
-\multirow[c]{2}{3cm}{\textit{Panel F: Pretreatment Zestimates}} & Change from Jan. 2018 to Jan. 2019 & 22,601.20 & 15,786.00 & 74,245.92 & 10,170 \\
- & Jan. 2018 & 322,775.21 & 256,528.00 & 298,417.63 & 10,177 \\
+\multirow[c]{4}{3cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 377,384.02 & 305,144.00 & 316,645.29 & 10,096 \\
+ & One year after filing date & 421,601.75 & 347,550.00 & 344,328.86 & 10,443 \\
+ & Three years after filing date & 501,611.80 & 414,600.00 & 780,467.01 & 5,894 \\
+ & Two years after filing date & 477,948.08 & 393,900.00 & 457,694.83 & 9,175 \\
 \cline{1-6}

### 2023-01-17 src/02_analysis/analysis_utilities.py

@@ -101,87 +101,99 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     :param treatment_date_variable:
     :return:
     """
-    # Panel A: Case Initiaton
-    panel_A_columns = ['for_cause', 'no_cause', 'non_payment']
+    # Panel A: Pre-treatment Zestimates
+    df.loc[:, 'change_in_zestimates_2018_to_2019'] = df['2019-01'] - df['2018-01']
+    panel_A_columns = ['2018-01', 'change_in_zestimates_2018_to_2019']
+    panel_A = df[panel_A_columns].describe().T
+    panel_A = pd.concat([panel_A], keys=["Panel A: Pre-treatment Zestimates"])
+
+    # Panel B: Census Tract Characteristics
+    panel_B_columns = ['med_hhinc2016', 'popdensity2010', 'share_white2010']
+    panel_B = df[sorted(panel_B_columns)].describe().T
+    panel_B = pd.concat([panel_B], keys=["Panel B: Census Tract Characteristics"])
+
+    # Panel C: Case Initiaton
+    panel_C_columns = ['for_cause', 'no_cause', 'non_payment']
     origin_columns = ['initiating_action', 'initiating_action', 'initiating_action']
     target_values = [("SP Summons and Complaint - Cause", "SP Transfer - Cause"),
                      ("SP Summons and Complaint - No Cause", "SP Transfer- No Cause"),
                      ("SP Summons and Complaint - Non-payment of Rent", "SP Transfer - Non-payment of Rent")]
 
-    for dummy_column, origin_column, target_value in zip(panel_A_columns, origin_columns, target_values):
+    for dummy_column, origin_column, target_value in zip(panel_C_columns, origin_columns, target_values):
         df.loc[:, dummy_column] = np.where((df[origin_column].str.contains(target_value[0])) |
                                            (df[origin_column].str.contains(target_value[1])),
                                            1,
                                            0)
+    panel_C = df[sorted(panel_C_columns)].describe().T
+    panel_C = pd.concat([panel_C], keys=["Panel C: Case Initiation"])
 
-    panel_A = df[sorted(panel_A_columns)].describe().T
-    panel_A = pd.concat([panel_A], keys=["Panel A: Case Initiation"])
+    # Panel D: Defendant and Plaintiff Characteristics
[…]

### 2023-01-17 src/02_analysis/analysis_utilities.py
Updated Zestimates in summary statistics

@@ -103,7 +103,7 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     """
     # Panel A: Pre-treatment Zestimates
     df.loc[:, 'change_in_zestimates_2018_to_2019'] = df['2019-01'] - df['2018-01']
-    panel_A_columns = ['2018-01', 'change_in_zestimates_2018_to_2019']
+    panel_A_columns = ['2017-01', '2018-01', 'change_in_zestimates_2018_to_2019']
     panel_A = df[panel_A_columns].describe().T
     panel_A = pd.concat([panel_A], keys=["Panel A: Pre-treatment Zestimates"])
 
@@ -182,7 +182,7 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                                    axis=0)[['mean', '50%', 'std', 'count']]
 
     variable_display_names_dict = {'for_cause': "For cause", 'no_cause': "No cause",
-                                   'non_payment': "Non-payment of rent",  # Panel A
+                                   'non_payment': "Non-payment of rent",
                                    'case_duration': "Case duration", 'defaulted': "Case defaulted",
                                    'heard': "Case heard",
                                    'judgment': "Money judgment", 'mediated': "Case mediated",
@@ -192,6 +192,7 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                                    'med_hhinc2016': 'Median household income (2016)',
                                    'popdensity2010': 'Population density (2010)',  # Panel E
                                    'share_white2010': 'Portion white (2010)',  # Panel E
+                                   '2017-01': 'Jan. 2017',
                                    '2018-01': 'Jan. 2018', 'change_in_zestimates_2018_to_2019': 'Change from Jan. 2018 to Jan. 2019',
                                    'zestimate_0_years_relative_to_treatment': "At filing date",
                                    'zestimate_1_years_relative_to_treatment': "One year after filing date",

### 2023-01-17 output/DiD/tables/balance_table.tex
Updated Zestimates in summary statistics

--- 2023-01-16 output/DiD/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 0.01 & 0.47 \\
- & No cause & 0.11 & -0.03 & 0.03 & -0.03 & 0.05 \\
- & Non-payment of rent & 0.72 & -0.01 & 0.76 & -0.01 & 0.73 \\
+\multirow[c]{3}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 17,563.13 & 0.03 \\
+ & Jan. 2018 & 320,170.03 & 27,148.19 & 0.00 & 17,292.03 & 0.05 \\
+ & Change from Jan. 2018 to Jan. 2019 & 22,263.71 & 2,086.50 & 0.21 & 1,336.20 & 0.43 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & -0.12 & 0.00 \\
- & Plaintiff has an attorney & 0.80 & 0.01 & 0.48 & 0.01 & 0.47 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.47 \\
- & Plaintiff is an entity & 0.66 & 0.03 & 0.12 & 0.03 & 0.13 \\
+\multirow[c]{3}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,838.37 & 0.08 \\
+ & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 715.29 & 0.05 \\
+ & Portion white (2010) & 0.60 & 0.04 & 0.00 & 0.03 & 0.02 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 0.04 & 0.00 & 0.03 & 0.01 \\
- & Population density (2010) & 9,031.64 & 0.06 & 0.25 & 0.06 & 0.24 \\
- & Portion white (2010) & 0.60 & 0.06 & 0.01 & 0.05 & 0.02 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 0.01 & 0.54 \\
+ & No cause & 0.11 & -0.03 & 0.03 & -0.03 & 0.04 \\
+ & Non-payment of rent & 0.72 & -0.01 & 0.76 & -0.01 & 0.67 \\
+\cline{1-7}
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & -0.12 & 0.00 \\
+ & Plaintiff has an attorney & 0.80 & 0.01 & 0.48 & 0.01 & 0.59 \\
+ & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.57 \\
+ & Plaintiff is an entity & 0.66 & 0.03 & 0.12 & 0.03 & 0.18 \\
 \cline{1-7}

### 2023-01-17 src/02_analysis/analysis_utilities.py

@@ -102,8 +102,10 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     :return:
     """
     # Panel A: Pre-treatment Zestimates
-    df.loc[:, 'change_in_zestimates_2018_to_2019'] = df['2019-01'] - df['2018-01']
-    panel_A_columns = ['2017-01', '2018-01', 'change_in_zestimates_2018_to_2019']
+    df.loc[:, 'twenty_seventeen'] = df['2017-01']
+    df.loc[:, 'twenty_eighteen'] = df['2018-01']
+    df.loc[:, 'change_in_zestimates'] = df['2019-01'] - df['2018-01']
+    panel_A_columns = ['twenty_seventeen', 'twenty_eighteen', 'change_in_zestimates']
     panel_A = df[panel_A_columns].describe().T
     panel_A = pd.concat([panel_A], keys=["Panel A: Pre-treatment Zestimates"])
 
@@ -192,8 +194,8 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                                    'med_hhinc2016': 'Median household income (2016)',
                                    'popdensity2010': 'Population density (2010)',  # Panel E
                                    'share_white2010': 'Portion white (2010)',  # Panel E
-                                   '2017-01': 'Jan. 2017',
-                                   '2018-01': 'Jan. 2018', 'change_in_zestimates_2018_to_2019': 'Change from Jan. 2018 to Jan. 2019',
+                                   'twenty_seventeen': 'Jan. 2017',
+                                   'twenty_eighteen': 'Jan. 2018', 'change_in_zestimates': 'Change from Jan. 2018 to Jan. 2019',
                                    'zestimate_0_years_relative_to_treatment': "At filing date",
                                    'zestimate_1_years_relative_to_treatment': "One year after filing date",
                                    'zestimate_2_years_relative_to_treatment': "Two years after filing date",

### 2023-01-17 output/summary_statistics/tables/summary_statistics.tex
Updated Zestimates in summary statistics
Added more variables to summary statistics table

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change from Jan. 2018 to Jan. 2019 & 22,601.20 & 15,786.00 & 74,245.92 & 10,170 \\
+\multirow[c]{3}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change from Jan. 2018 to Jan. 2019 & 46,593.74 & 37,330.00 & 158,125.14 & 10,160 \\
+ & Jan. 2017 & 298,908.73 & 235,117.00 & 352,754.39 & 10,176 \\
  & Jan. 2018 & 322,775.21 & 256,528.00 & 298,417.63 & 10,177 \\
 \cline{1-6}
-\multirow[c]{3}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
+\multirow[c]{6}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
+ & Number of jobs per sq. mile (2010) & 4,797.07 & 1,355.40 & 17,579.99 & 40,726 \\
  & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
  & Portion white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
+ & Portion with bachelor's degree or higher (2010) & 0.26 & 0.22 & 0.17 & 40,726 \\
+ & Share below  & 0.20 & 0.16 & 0.15 & 40,726 \\
 \cline{1-6}

### 2023-01-17 src/01_build/scratch.py

@@ -1,10 +1,0 @@
-import numpy as np
-import pandas as pd
-from build_utilities import geocode_single_point
-
-df = pd.read_csv("/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions.csv")
-df2 = pd.read_csv("/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/tracts.csv")
-print(df['Full FIPS (tract)'].astype(str))
-print(df2['tract_geoid'])
-
-print(df2['tract_geoid'].isin(df['Full FIPS (tract)']).sum())

### 2023-01-17 src/02_analysis/analysis_utilities.py

@@ -104,13 +104,15 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     # Panel A: Pre-treatment Zestimates
     df.loc[:, 'twenty_seventeen'] = df['2017-01']
     df.loc[:, 'twenty_eighteen'] = df['2018-01']
-    df.loc[:, 'change_in_zestimates'] = df['2019-01'] - df['2018-01']
+    df.loc[:, 'change_in_zestimates'] = df['2019-01'] - df['2017-01']
     panel_A_columns = ['twenty_seventeen', 'twenty_eighteen', 'change_in_zestimates']
     panel_A = df[panel_A_columns].describe().T
     panel_A = pd.concat([panel_A], keys=["Panel A: Pre-treatment Zestimates"])
 
     # Panel B: Census Tract Characteristics
-    panel_B_columns = ['med_hhinc2016', 'popdensity2010', 'share_white2010']
+    # TODO: RE-ADD 'mean_commutetime2000' TO THIS LIST AFTER RE-RUNNING 06_merge.py
+    panel_B_columns = ['med_hhinc2016', 'popdensity2010', 'share_white2010', 'frac_coll_plus2010', 'job_density_2013',
+                        'poor_share2010']
     panel_B = df[sorted(panel_B_columns)].describe().T
     panel_B = pd.concat([panel_B], keys=["Panel B: Census Tract Characteristics"])
 
@@ -192,8 +194,12 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                                    'hasAttyD': "Defendant has an attorney", 'hasAttyP': "Plaintiff has an attorney",
                                    'isEntityD': "Defendant is an entity", 'isEntityP': "Plaintiff is an entity",
                                    'med_hhinc2016': 'Median household income (2016)',
-                                   'popdensity2010': 'Population density (2010)',  # Panel E
-                                   'share_white2010': 'Portion white (2010)',  # Panel E
+                                   'popdensity2010': 'Population density (2010)',
+                                   'share_white2010': 'Portion white (2010)',
+                                   'frac_coll_plus2010': 'Portion with bachelor\'s degree or higher (2010)',
+                                   'job_density_2013': 'Number of jobs per sq. mile (2010)',
+                                   'mean_commutetime2000': 'Mean commute time (2000)',
+                                   'poor_share2010': 'Share below ',
                                    'twenty_seventeen': 'Jan. 2017',
[…]

### 2023-01-17 output/DiD/tables/pre_treatment_covariate_tests.tex
Added covariate tests table

\begin{tabular}{lcc}
\toprule
 &  & \multicolumn{2}{r}{Dependent Variable} \\
 &  & Zestimate, Dec. 2022 & Plaintiff victory \\
\midrule
\multirow[c]{3}{*}{Panel A: Pre-treatment Zestimates} & Zestimate, Jan. 2017 & 0.00 & 0.00 \\
 & Zestimate, Jan. 2018 & 0.00 & 0.00 \\
 & Change from Jan. 2018 to Jan. 2019 & 0.00 & 0.27 \\
\multirow[c]{3}{*}{Panel B: Census Tract Characteristics} & Median household income (2016) & 0.00 & 0.01 \\
 & Population density (2010) & 0.00 & 0.01 \\
 & Portion white (2010) & 0.00 & 0.00 \\
\multirow[c]{3}{*}{Panel C: Case Initiation} & For cause & 0.01 & 0.68 \\
 & No cause & 0.98 & 0.03 \\
 & Non-payment of rent & 0.31 & 0.76 \\
\multirow[c]{4}{*}{Panel D: Defendant and Plaintiff Characteristics} & Defendant has an attorney & 0.37 & 0.00 \\
 & Plaintiff has an attorney & 0.61 & 0.48 \\
 & Defendant is an entity & 0.02 & 0.37 \\
 & Plaintiff is an entity & 0.63 & 0.12 \\
\multirow[c]{6}{*}{Panel E: Case Resolution} & Case duration & 0.57 & 0.00 \\
 & Case defaulted & 0.89 & 0.00 \\
 & Case dismised & 0.00 & 0.00 \\
 & Case heard & 0.25 & 0.00 \\
 & Money judgment & 0.88 & 0.00 \\
 & Case mediated & nan & nan \\
\multirow[c]{4}{*}{Panel F: Post-treatment Zestimates} & At filing date & 0.00 & 0.04 \\
 & One year after filing date & 0.00 & 0.05 \\
 & Two years after filing date & 0.00 & 0.01 \\
 & Three years after filing date & 0.00 & 0.08 \\
\bottomrule
\end{tabular}

### 2023-01-17 src/02_analysis/analysis_utilities.py

@@ -111,6 +111,7 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
 
     # Panel B: Census Tract Characteristics
     # TODO: RE-ADD 'mean_commutetime2000' TO THIS LIST AFTER RE-RUNNING 06_merge.py
+    # TODO: RE-ADD 'traveltime15_2010' TO THIS LIST AFTER RE-RUNNING 06_merge.py
     panel_B_columns = ['med_hhinc2016', 'popdensity2010', 'share_white2010', 'frac_coll_plus2010', 'job_density_2013',
                         'poor_share2010']
     panel_B = df[sorted(panel_B_columns)].describe().T
@@ -199,7 +200,8 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                                    'frac_coll_plus2010': 'Portion with bachelor\'s degree or higher (2010)',
                                    'job_density_2013': 'Number of jobs per sq. mile (2010)',
                                    'mean_commutetime2000': 'Mean commute time (2000)',
-                                   'poor_share2010': 'Share below ',
+                                   'traveltime15_2010': 'Share with commute under 15 min. (2010)',
+                                   'poor_share2010': 'Share below poverty line',
                                    'twenty_seventeen': 'Jan. 2017',
                                    'twenty_eighteen': 'Jan. 2018', 'change_in_zestimates': 'Change from Jan. 2018 to Jan. 2019',
                                    'zestimate_0_years_relative_to_treatment': "At filing date",

### 2023-01-17 output/DiD/tables/pre_treatment_covariate_tests.tex
Added covariate tests table

@@
-\begin{tabular}{lcc}
+\begin{tabular}{llcc}
 \toprule
@@
 \midrule
-\multirow[c]{3}{*}{Panel A: Pre-treatment Zestimates} & Zestimate, Jan. 2017 & 0.00 & 0.00 \\
+\multirow[c]{3}{3cm}{Panel A: Pre-treatment Zestimates} & Zestimate, Jan. 2017 & 0.00 & 0.00 \\
  & Zestimate, Jan. 2018 & 0.00 & 0.00 \\
  & Change from Jan. 2018 to Jan. 2019 & 0.00 & 0.27 \\
-\multirow[c]{3}{*}{Panel B: Census Tract Characteristics} & Median household income (2016) & 0.00 & 0.01 \\
+\multirow[c]{3}{3cm}{Panel B: Census Tract Characteristics} & Median household income (2016) & 0.00 & 0.01 \\
  & Population density (2010) & 0.00 & 0.01 \\
  & Portion white (2010) & 0.00 & 0.00 \\
-\multirow[c]{3}{*}{Panel C: Case Initiation} & For cause & 0.01 & 0.68 \\
+\multirow[c]{3}{3cm}{Panel C: Case Initiation} & For cause & 0.01 & 0.68 \\
  & No cause & 0.98 & 0.03 \\
  & Non-payment of rent & 0.31 & 0.76 \\
-\multirow[c]{4}{*}{Panel D: Defendant and Plaintiff Characteristics} & Defendant has an attorney & 0.37 & 0.00 \\
+\multirow[c]{4}{3cm}{Panel D: Defendant and Plaintiff Characteristics} & Defendant has an attorney & 0.37 & 0.00 \\
  & Plaintiff has an attorney & 0.61 & 0.48 \\
@@
  & Plaintiff is an entity & 0.63 & 0.12 \\
-\multirow[c]{6}{*}{Panel E: Case Resolution} & Case duration & 0.57 & 0.00 \\
+\multirow[c]{6}{3cm}{Panel E: Case Resolution} & Case duration & 0.57 & 0.00 \\
  & Case defaulted & 0.89 & 0.00 \\
@@
  & Case mediated & nan & nan \\
-\multirow[c]{4}{*}{Panel F: Post-treatment Zestimates} & At filing date & 0.00 & 0.04 \\
+\multirow[c]{4}{3cm}{Panel F: Post-treatment Zestimates} & At filing date & 0.00 & 0.04 \\
  & One year after filing date & 0.00 & 0.05 \\

### 2023-01-17 output/DiD/tables/pre_treatment_covariate_tests.tex
Added covariate tests table

@@
 \toprule
- &  & \multicolumn{2}{r}{Dependent Variable} \\
+ &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
  &  & Zestimate, Dec. 2022 & Plaintiff victory \\
 \midrule
-\multirow[c]{3}{3cm}{Panel A: Pre-treatment Zestimates} & Zestimate, Jan. 2017 & 0.00 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 0.00 & 0.00 \\
  & Zestimate, Jan. 2018 & 0.00 & 0.00 \\
  & Change from Jan. 2018 to Jan. 2019 & 0.00 & 0.27 \\
-\multirow[c]{3}{3cm}{Panel B: Census Tract Characteristics} & Median household income (2016) & 0.00 & 0.01 \\
+\cline{1-4}
+\multirow[c]{3}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Median household income (2016) & 0.00 & 0.01 \\
  & Population density (2010) & 0.00 & 0.01 \\
  & Portion white (2010) & 0.00 & 0.00 \\
-\multirow[c]{3}{3cm}{Panel C: Case Initiation} & For cause & 0.01 & 0.68 \\
+\cline{1-4}
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.01 & 0.68 \\
  & No cause & 0.98 & 0.03 \\
  & Non-payment of rent & 0.31 & 0.76 \\
-\multirow[c]{4}{3cm}{Panel D: Defendant and Plaintiff Characteristics} & Defendant has an attorney & 0.37 & 0.00 \\
+\cline{1-4}
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.37 & 0.00 \\
  & Plaintiff has an attorney & 0.61 & 0.48 \\
@@
  & Plaintiff is an entity & 0.63 & 0.12 \\
-\multirow[c]{6}{3cm}{Panel E: Case Resolution} & Case duration & 0.57 & 0.00 \\
+\cline{1-4}
+\multirow[c]{6}{3cm}{\textit{Panel E: Case Resolution}} & Case duration & 0.57 & 0.00 \\
  & Case defaulted & 0.89 & 0.00 \\
@@
  & Case mediated & nan & nan \\
-\multirow[c]{4}{3cm}{Panel F: Post-treatment Zestimates} & At filing date & 0.00 & 0.04 \\
+\cline{1-4}
+\multirow[c]{4}{3cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 0.00 & 0.04 \\
  & One year after filing date & 0.00 & 0.05 \\
@@
  & Three years after filing date & 0.00 & 0.08 \\
+\cline{1-4}
 \bottomrule

### 2023-01-17 output/DiD/tables/pre_treatment_covariate_tests.tex
Added covariate tests table

@@
  &  & Zestimate, Dec. 2022 & Plaintiff victory \\
+ & \emph{Independent Variable} &  &  \\
 \midrule
@@
 \cline{1-4}
-\multirow[c]{6}{3cm}{\textit{Panel E: Case Resolution}} & Case duration & 0.57 & 0.00 \\
- & Case defaulted & 0.89 & 0.00 \\
- & Case dismised & 0.00 & 0.00 \\
- & Case heard & 0.25 & 0.00 \\
- & Money judgment & 0.88 & 0.00 \\
- & Case mediated & nan & nan \\
-\cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 0.00 & 0.04 \\
- & One year after filing date & 0.00 & 0.05 \\
- & Two years after filing date & 0.00 & 0.01 \\
- & Three years after filing date & 0.00 & 0.08 \\
-\cline{1-4}
 \bottomrule

### 2023-01-17 output/DiD/tables/pre_treatment_covariate_tests.tex
Added covariate tests table

@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Median household income (2016) & 0.00 & 0.01 \\
+\multirow[c]{6}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Portion with bachelor's degree or higher (2010) & 0.00 & 0.07 \\
+ & Number of jobs per sq. mile (2010) & 0.00 & 0.63 \\
+ & Median household income (2016) & 0.00 & 0.01 \\
+ & Share below poverty line & 0.70 & 0.01 \\
  & Population density (2010) & 0.00 & 0.01 \\
@@
  & No cause & 0.98 & 0.03 \\
- & Non-payment of rent & 0.31 & 0.76 \\
+ & Non-payment of rent & 0.31 & 0.77 \\
 \cline{1-4}
 \multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.37 & 0.00 \\
- & Plaintiff has an attorney & 0.61 & 0.48 \\
+ & Plaintiff has an attorney & 0.61 & 0.47 \\
  & Defendant is an entity & 0.02 & 0.37 \\
- & Plaintiff is an entity & 0.63 & 0.12 \\
+ & Plaintiff is an entity & 0.62 & 0.13 \\
 \cline{1-4}

### 2023-01-17 output/DiD/tables/balance_table.tex
Added more variables to summary statistics table
Added covariate tests table

@@
 \midrule
-\multirow[c]{3}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 17,563.13 & 0.03 \\
- & Jan. 2018 & 320,170.03 & 27,148.19 & 0.00 & 17,292.03 & 0.05 \\
- & Change from Jan. 2018 to Jan. 2019 & 22,263.71 & 2,086.50 & 0.21 & 1,336.20 & 0.43 \\
+\multirow[c]{3}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 10,202.27 & 0.18 \\
+ & Zestimate, Jan. 2018 & 320,170.03 & 27,148.19 & 0.00 & 9,364.98 & 0.26 \\
+ & Change from Jan. 2018 to Jan. 2019 & 50,491.60 & 2,664.69 & 0.27 & -133.67 & 0.96 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,838.37 & 0.08 \\
- & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 715.29 & 0.05 \\
- & Portion white (2010) & 0.60 & 0.04 & 0.00 & 0.03 & 0.02 \\
+\multirow[c]{6}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Portion with bachelor's degree or higher (2010) & 0.25 & 0.01 & 0.07 & 0.01 & 0.39 \\
+ & Number of jobs per sq. mile (2010) & 4,158.02 & 263.90 & 0.63 & 133.63 & 0.81 \\
+ & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,178.12 & 0.25 \\
+ & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 483.30 & 0.18 \\
+ & Portion white (2010) & 0.60 & 0.04 & 0.00 & 0.02 & 0.07 \\
+ & Share with commute under 15 min. (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.27 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 0.01 & 0.54 \\
- & No cause & 0.11 & -0.03 & 0.03 & -0.03 & 0.04 \\
- & Non-payment of rent & 0.72 & -0.01 & 0.76 & -0.01 & 0.67 \\
+\textit{Panel C: Case Initiation} & For cause & 0.12 & 0.01 & 0.68 & 0.00 & 0.82 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & -0.12 & 0.00 \\
- & Plaintiff has an attorney & 0.80 & 0.01 & 0.48 & 0.01 & 0.59 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.57 \\
- & Plaintiff is an entity & 0.66 & 0.03 & 0.12 & 0.03 & 0.18 \\
+\textit{Panel D: Defendant and Plaintiff Characteristics} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.67 \\
 \cline{1-7}

### 2023-01-17 output/DiD/tables/pre_treatment_covariate_tests.tex
Added covariate tests table

@@
 \cline{1-4}
-\multirow[c]{6}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Portion with bachelor's degree or higher (2010) & 0.00 & 0.07 \\
+\multirow[c]{7}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Portion with bachelor's degree or higher (2010) & 0.00 & 0.07 \\
  & Number of jobs per sq. mile (2010) & 0.00 & 0.63 \\
@@
  & Portion white (2010) & 0.00 & 0.00 \\
+ & Share with commute under 15 min. (2010) & 0.00 & 0.02 \\
 \cline{1-4}

### 2023-01-17 src/02_analysis/analysis_utilities.py

@@ -111,9 +111,8 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
 
     # Panel B: Census Tract Characteristics
     # TODO: RE-ADD 'mean_commutetime2000' TO THIS LIST AFTER RE-RUNNING 06_merge.py
-    # TODO: RE-ADD 'traveltime15_2010' TO THIS LIST AFTER RE-RUNNING 06_merge.py
     panel_B_columns = ['med_hhinc2016', 'popdensity2010', 'share_white2010', 'frac_coll_plus2010', 'job_density_2013',
-                        'poor_share2010']
+                        'poor_share2010', 'traveltime15_2010']
     panel_B = df[sorted(panel_B_columns)].describe().T
     panel_B = pd.concat([panel_B], keys=["Panel B: Census Tract Characteristics"])
 
@@ -202,8 +201,8 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                                    'mean_commutetime2000': 'Mean commute time (2000)',
                                    'traveltime15_2010': 'Share with commute under 15 min. (2010)',
                                    'poor_share2010': 'Share below poverty line',
-                                   'twenty_seventeen': 'Jan. 2017',
-                                   'twenty_eighteen': 'Jan. 2018', 'change_in_zestimates': 'Change from Jan. 2018 to Jan. 2019',
+                                   'twenty_seventeen': 'Zestimate, Jan. 2017',
+                                   'twenty_eighteen': 'Zestimate, Jan. 2018', 'change_in_zestimates': 'Change from Jan. 2018 to Jan. 2019',
                                    'zestimate_0_years_relative_to_treatment': "At filing date",
                                    'zestimate_1_years_relative_to_treatment': "One year after filing date",
                                    'zestimate_2_years_relative_to_treatment': "Two years after filing date",

### 2023-01-17 output/DiD/tables/balance_table.tex
Added covariate tests table

@@
 \midrule
-\multirow[c]{3}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 10,202.27 & 0.18 \\
- & Zestimate, Jan. 2018 & 320,170.03 & 27,148.19 & 0.00 & 9,364.98 & 0.26 \\
- & Change from Jan. 2018 to Jan. 2019 & 50,491.60 & 2,664.69 & 0.27 & -133.67 & 0.96 \\
+\multirow[c]{3}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,945.81 & 26,570.00 & 0.00 & 10,202.27 & 0.18 \\
+ & Zestimate, Jan. 2018 & 320,176.82 & 27,148.19 & 0.00 & 9,364.98 & 0.26 \\
+ & Change from Jan. 2018 to Jan. 2019 & 50,501.64 & 2,664.69 & 0.27 & -133.67 & 0.96 \\
 \cline{1-7}
-\multirow[c]{6}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Portion with bachelor's degree or higher (2010) & 0.25 & 0.01 & 0.07 & 0.01 & 0.39 \\
+\multirow[c]{6}{3cm}{\textit{Panel B}} & Portion with bachelor's degree or higher (2010) & 0.25 & 0.01 & 0.07 & 0.01 & 0.39 \\
  & Number of jobs per sq. mile (2010) & 4,158.02 & 263.90 & 0.63 & 133.63 & 0.81 \\
@@
 \cline{1-7}
-\textit{Panel C: Case Initiation} & For cause & 0.12 & 0.01 & 0.68 & 0.00 & 0.82 \\
+\textit{Panel C} & For cause & 0.12 & 0.01 & 0.68 & 0.00 & 0.82 \\
 \cline{1-7}
-\textit{Panel D: Defendant and Plaintiff Characteristics} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.67 \\
+\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.67 \\
 \cline{1-7}

### 2023-01-17 output/DiD/tables/balance_table.tex
Added clines to tables

@@
 \toprule
- &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
+ &  & \textit{} & \multicolumn{4}{|c|}{\textit{Difference in Cases Won by Defendant}} \\
+\cline{4-7}
+\\
  &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
 \midrule
-\multirow[c]{3}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,945.81 & 26,570.00 & 0.00 & 10,202.27 & 0.18 \\
- & Zestimate, Jan. 2018 & 320,176.82 & 27,148.19 & 0.00 & 9,364.98 & 0.26 \\
- & Change from Jan. 2018 to Jan. 2019 & 50,501.64 & 2,664.69 & 0.27 & -133.67 & 0.96 \\
+\multirow[c]{3}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 10,202.27 & 0.18 \\
+ & Zestimate, Jan. 2018 & 320,170.03 & 27,148.19 & 0.00 & 9,364.98 & 0.26 \\
+ & Change from Jan. 2018 to Jan. 2019 & 50,491.60 & 2,664.69 & 0.27 & -133.67 & 0.96 \\
 \cline{1-7}

### 2023-01-17 output/DiD/tables/balance_table.tex
Updates from Overleaf
Removed vertical lines around outer level of columns in balance table

@@
 \toprule
- &  & \textit{} & \multicolumn{4}{|c|}{\textit{Difference in Cases Won by Defendant}} \\
+ &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
 \cline{4-7}
@@
 \midrule
-\multirow[c]{3}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 10,202.27 & 0.18 \\
- & Zestimate, Jan. 2018 & 320,170.03 & 27,148.19 & 0.00 & 9,364.98 & 0.26 \\
- & Change from Jan. 2018 to Jan. 2019 & 50,491.60 & 2,664.69 & 0.27 & -133.67 & 0.96 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 10,030.65 & 0.18 \\
+ & Zestimate, Jan. 2019 $-$ Zestimate, Jan. 2017 & 50,491.60 & 2,664.69 & 0.27 & -23.86 & 0.99 \\
 \cline{1-7}
-\multirow[c]{6}{3cm}{\textit{Panel B}} & Portion with bachelor's degree or higher (2010) & 0.25 & 0.01 & 0.07 & 0.01 & 0.39 \\
- & Number of jobs per sq. mile (2010) & 4,158.02 & 263.90 & 0.63 & 133.63 & 0.81 \\
- & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,178.12 & 0.25 \\
- & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 483.30 & 0.18 \\
- & Portion white (2010) & 0.60 & 0.04 & 0.00 & 0.02 & 0.07 \\
- & Share with commute under 15 min. (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.27 \\
+\multirow[c]{6}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.25 & 0.01 & 0.07 & 0.01 & 0.40 \\
+ & Jobs per sq. mile (2010) & 4,158.02 & 263.90 & 0.63 & 122.36 & 0.83 \\
+ & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,159.98 & 0.25 \\
+ & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 488.36 & 0.17 \\
+ & Share white (2010) & 0.60 & 0.04 & 0.00 & 0.02 & 0.06 \\
+ & Share with commute <15 min. (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.27 \\
 \cline{1-7}
-\textit{Panel C} & For cause & 0.12 & 0.01 & 0.68 & 0.00 & 0.82 \\
+\textit{Panel C} & For cause & 0.12 & 0.01 & 0.68 & 0.00 & 0.83 \\
 \cline{1-7}
-\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.67 \\
+\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.66 \\
 \cline{1-7}

### 2023-01-17 output/DiD/tables/pre_treatment_covariate_tests.tex
Removed vertical lines around outer level of columns in balance table

--- 2023-01-17 output/DiD/tables/pre_treatment_covariate_tests.tex
@@
  &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
+\cline{3-4}
+\\
  &  & Zestimate, Dec. 2022 & Plaintiff victory \\
@@
 \midrule
-\multirow[c]{3}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 0.00 & 0.00 \\
- & Zestimate, Jan. 2018 & 0.00 & 0.00 \\
- & Change from Jan. 2018 to Jan. 2019 & 0.00 & 0.27 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 0.00 & 0.00 \\
+ & Zestimate, Jan. 2019 $-$ Zestimate, Jan. 2017 & 0.00 & 0.27 \\
 \cline{1-4}
-\multirow[c]{6}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Portion with bachelor's degree or higher (2010) & 0.00 & 0.07 \\
- & Number of jobs per sq. mile (2010) & 0.00 & 0.63 \\
+\multirow[c]{7}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.07 \\
+ & Jobs per sq. mile (2010) & 0.00 & 0.63 \\
  & Median household income (2016) & 0.00 & 0.01 \\
@@
  & Population density (2010) & 0.00 & 0.01 \\
- & Portion white (2010) & 0.00 & 0.00 \\
+ & Share white (2010) & 0.00 & 0.00 \\
+ & Share with commute <15 min. (2010) & 0.00 & 0.02 \\
 \cline{1-4}

### 2023-01-17 output/summary_statistics/tables/summary_statistics.tex
Removed vertical lines around outer level of columns in balance table

--- 2023-01-17 output/summary_statistics/tables/summary_statistics.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change from Jan. 2018 to Jan. 2019 & 22,601.20 & 15,786.00 & 74,245.92 & 10,170 \\
- & Jan. 2018 & 322,775.21 & 256,528.00 & 298,417.63 & 10,177 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 298,908.73 & 235,117.00 & 352,754.39 & 10,176 \\
+ & Zestimate, Jan. 2019 $-$ Zestimate, Jan. 2017 & 46,593.74 & 37,330.00 & 158,125.14 & 10,160 \\
 \cline{1-6}
-\multirow[c]{3}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
+\multirow[c]{7}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per sq. mile (2010) & 4,797.07 & 1,355.40 & 17,579.99 & 40,726 \\
+ & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
  & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
- & Portion white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
+ & Share below poverty line & 0.20 & 0.16 & 0.15 & 40,726 \\
+ & Share white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
+ & Share with bachelor's degree & 0.26 & 0.22 & 0.17 & 40,726 \\
+ & Share with commute <15 min. (2010) & 0.28 & 0.27 & 0.11 & 40,726 \\
 \cline{1-6}

### 2023-01-17 src/02_analysis/analysis_utilities.py

@@ -103,9 +103,8 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     """
     # Panel A: Pre-treatment Zestimates
     df.loc[:, 'twenty_seventeen'] = df['2017-01']
-    df.loc[:, 'twenty_eighteen'] = df['2018-01']
     df.loc[:, 'change_in_zestimates'] = df['2019-01'] - df['2017-01']
-    panel_A_columns = ['twenty_seventeen', 'twenty_eighteen', 'change_in_zestimates']
+    panel_A_columns = ['twenty_seventeen', 'change_in_zestimates']
     panel_A = df[panel_A_columns].describe().T
     panel_A = pd.concat([panel_A], keys=["Panel A: Pre-treatment Zestimates"])
 
@@ -196,13 +195,14 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                                    'med_hhinc2016': 'Median household income (2016)',
                                    'popdensity2010': 'Population density (2010)',
                                    'share_white2010': 'Share white (2010)',
-                                   'frac_coll_plus2010': 'Share with bachelor\'s degree or higher (2010)',
+                                   'frac_coll_plus2010': 'Share with bachelor\'s degree',
                                    'job_density_2013': 'Jobs per sq. mile (2010)',
                                    'mean_commutetime2000': 'Mean commute time (2000)',
-                                   'traveltime15_2010': 'Share with commute under 15 min. (2010)',
+                                   'traveltime15_2010': 'Share with commute <15 min. (2010)',
                                    'poor_share2010': 'Share below poverty line',
                                    'twenty_seventeen': 'Zestimate, Jan. 2017',
-                                   'twenty_eighteen': 'Zestimate, Jan. 2018', 'change_in_zestimates': 'Change from Jan. 2018 to Jan. 2019',
+                                   'twenty_eighteen': 'Zestimate, Jan. 2018',
+                                   'change_in_zestimates': 'Zestimate, Jan. 2019 $-$ Zestimate, Jan. 2017',
                                    'zestimate_0_years_relative_to_treatment': "At filing date",
                                    'zestimate_1_years_relative_to_treatment': "One year after filing date",
                                    'zestimate_2_years_relative_to_treatment': "Two years after filing date",

### 2023-01-17 output/summary_statistics/tables/balance_table.tex
Added median to summary statistics

@@
-\begin{tabular}{llcccc}
+\begin{tabular}{llcccccc}
 \toprule
- &  & \multicolumn{3}{c}{\textit{Cases Won by Defendant}} & \multicolumn{3}{c}{\textit{Cases Won by Plaintiff}} \\
+ &  & \multicolumn{3}{c}{\textit{Cases Won by Defendant}} & \multicolumn{3}{c}{\textit{Cases Won by Plaintiff}} \\ \cline{2-5}
  &  & Median & Mean & N & Median & Mean & N \\

### 2023-01-17 output/summary_statistics/tables/summary_statistics.tex
Removed median from summary statistics

--- 2023-01-17 output/summary_statistics/tables/summary_statistics.tex
@@
 \toprule
- &  & Mean & Median & S.D. & N \\
-Panel & Variable &  &  &  &  \\
+ &  & Mean & S.D. & N \\
+Panel & Variable &  &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change from Jan. 2018 to Jan. 2019 & 22,601.20 & 15,786.00 & 74,245.92 & 10,170 \\
- & Jan. 2018 & 322,775.21 & 256,528.00 & 298,417.63 & 10,177 \\
-\cline{1-6}
-\multirow[c]{3}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
- & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
- & Portion white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
-\cline{1-6}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
- & No cause & 0.11 & 0.00 & 0.31 & 40,727 \\
- & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,727 \\
-\cline{1-6}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,727 \\
- & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,727 \\
- & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,727 \\
-\cline{1-6}
-\multirow[c]{6}{3cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
- & Case dismised & 0.29 & 0.00 & 0.45 & 40,727 \\
- & Case duration & 57.81 & 21.00 & 78.29 & 39,087 \\
- & Case heard & 0.06 & 0.00 & 0.23 & 40,727 \\
- & Case mediated & 0.41 & 0.00 & 0.49 & 40,727 \\
- & Money judgment & 1,890.34 & 0.00 & 5,279.49 & 40,727 \\
-\cline{1-6}
-\multirow[c]{4}{3cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 377,384.02 & 305,144.00 & 316,645.29 & 10,096 \\
- & One year after filing date & 421,601.75 & 347,550.00 & 344,328.86 & 10,443 \\
- & Three years after filing date & 501,611.80 & 414,600.00 & 780,467.01 & 5,894 \\
- & Two years after filing date & 477,948.08 & 393,900.00 & 457,694.83 & 9,175 \\
-\cline{1-6}
+\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 298,908.73 & 352,754.39 & 10,176 \\
+ & Zestimate, Jan. 2019 $-$ Zestimate, Jan. 2017 & 46,593.74 & 158,125.14 & 10,160 \\
+\cline{1-5}
+\multirow[c]{7}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per sq. mile (2010) & 4,797.07 & 17,579.99 & 40,726 \\
+ & Median household income (2016) & 52,659.44 & 27,177.48 & 40,726 \\
+ & Population density (2010) & 9,159.77 & 9,574.14 & 40,726 \\
+ & Share below poverty line & 0.20 & 0.15 & 40,726 \\
+ & Share white (2010) & 0.58 & 0.29 & 40,726 \\
+ & Share with bachelor's degree & 0.26 & 0.17 & 40,726 \\
+ & Share with commute $<$15 min. (2010) & 0.28 & 0.11 & 40,726 \\
+\cline{1-5}
+\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.33 & 40,727 \\
+ & No cause & 0.11 & 0.31 & 40,727 \\
+ & Non-payment of rent & 0.75 & 0.43 & 40,727 \\
+\cline{1-5}
+\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,727 \\
+ & Defendant is an entity & 0.01 & 0.08 & 40,727 \\
+ & Plaintiff has an attorney & 0.84 & 0.37 & 40,727 \\
+ & Plaintiff is an entity & 0.70 & 0.46 & 40,727 \\
+\cline{1-5}
+\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,727 \\
+ & Case dismised & 0.29 & 0.45 & 40,727 \\
+ & Case duration & 57.81 & 78.29 & 39,087 \\
+ & Case heard & 0.06 & 0.23 & 40,727 \\
+ & Case mediated & 0.41 & 0.49 & 40,727 \\
+ & Money judgment & 1,890.34 & 5,279.49 & 40,727 \\
+\cline{1-5}
+\multirow[c]{4}{4cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 377,384.02 & 316,645.29 & 10,096 \\
+ & One year after filing date & 421,601.75 & 344,328.86 & 10,443 \\
+ & Three years after filing date & 501,611.80 & 780,467.01 & 5,894 \\
+ & Two years after filing date & 477,948.08 & 457,694.83 & 9,175 \\
+\cline{1-5}
 \bottomrule

### 2023-01-17 src/02_analysis/analysis_utilities.py

@@ -182,7 +182,7 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
 
     # Concatenate Panels A-E
     summary_statistics = pd.concat([panel_A, panel_B, panel_C, panel_D, panel_E, panel_F],
-                                   axis=0)[['mean', '50%', 'std', 'count']]
+                                   axis=0)[['mean', 'std', 'count']]
 
     variable_display_names_dict = {'for_cause': "For cause", 'no_cause': "No cause",
                                    'non_payment': "Non-payment of rent",
@@ -198,7 +198,7 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                                    'frac_coll_plus2010': 'Share with bachelor\'s degree',
                                    'job_density_2013': 'Jobs per sq. mile (2010)',
                                    'mean_commutetime2000': 'Mean commute time (2000)',
-                                   'traveltime15_2010': 'Share with commute <15 min. (2010)',
+                                   'traveltime15_2010': 'Share with commute $<$15 min. (2010)',
                                    'poor_share2010': 'Share below poverty line',
                                    'twenty_seventeen': 'Zestimate, Jan. 2017',
                                    'twenty_eighteen': 'Zestimate, Jan. 2018',

### 2023-01-17 output/DiD/tables/balance_table.tex
toying with tables'

@@
  & Share white (2010) & 0.60 & 0.04 & 0.00 & 0.02 & 0.06 \\
- & Share with commute <15 min. (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.27 \\
+ & Share with commute $<$15 min. (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.27 \\
 \cline{1-7}

### 2023-01-17 output/DiD/tables/pre_treatment_covariate_tests.tex
toying with tables'

@@
 \multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 0.00 & 0.00 \\
- & Zestimate, Jan. 2019 $-$ Zestimate, Jan. 2017 & 0.00 & 0.27 \\
+ & Change, Jan. 2017 to Jan. 2019 & 0.00 & 0.27 \\
 \cline{1-4}
 \multirow[c]{7}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.07 \\
- & Jobs per sq. mile (2010) & 0.00 & 0.63 \\
+ & Jobs per square mile (2010) & 0.00 & 0.63 \\
  & Median household income (2016) & 0.00 & 0.01 \\
@@
  & Share white (2010) & 0.00 & 0.00 \\
- & Share with commute <15 min. (2010) & 0.00 & 0.02 \\
+ & Share with commute $<$15 minutes (2010) & 0.00 & 0.02 \\
 \cline{1-4}

### 2023-01-17 output/summary_statistics/tables/summary_statistics.tex
toying with tables'

@@
 \toprule
- &  & Mean & S.D. & N \\
-Panel & Variable &  &  &  \\
+ &  & Mean & Median & S.D. & N \\
+Panel & Variable &  &  &  &  \\
 \midrule
-\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 298,908.73 & 352,754.39 & 10,176 \\
- & Zestimate, Jan. 2019 $-$ Zestimate, Jan. 2017 & 46,593.74 & 158,125.14 & 10,160 \\
-\cline{1-5}
-\multirow[c]{7}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per sq. mile (2010) & 4,797.07 & 17,579.99 & 40,726 \\
- & Median household income (2016) & 52,659.44 & 27,177.48 & 40,726 \\
- & Population density (2010) & 9,159.77 & 9,574.14 & 40,726 \\
- & Share below poverty line & 0.20 & 0.15 & 40,726 \\
- & Share white (2010) & 0.58 & 0.29 & 40,726 \\
- & Share with bachelor's degree & 0.26 & 0.17 & 40,726 \\
- & Share with commute $<$15 min. (2010) & 0.28 & 0.11 & 40,726 \\
-\cline{1-5}
-\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.33 & 40,727 \\
- & No cause & 0.11 & 0.31 & 40,727 \\
- & Non-payment of rent & 0.75 & 0.43 & 40,727 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,727 \\
- & Defendant is an entity & 0.01 & 0.08 & 40,727 \\
- & Plaintiff has an attorney & 0.84 & 0.37 & 40,727 \\
- & Plaintiff is an entity & 0.70 & 0.46 & 40,727 \\
-\cline{1-5}
-\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,727 \\
- & Case dismised & 0.29 & 0.45 & 40,727 \\
- & Case duration & 57.81 & 78.29 & 39,087 \\
- & Case heard & 0.06 & 0.23 & 40,727 \\
- & Case mediated & 0.41 & 0.49 & 40,727 \\
- & Money judgment & 1,890.34 & 5,279.49 & 40,727 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 377,384.02 & 316,645.29 & 10,096 \\
- & One year after filing date & 421,601.75 & 344,328.86 & 10,443 \\
- & Three years after filing date & 501,611.80 & 780,467.01 & 5,894 \\
- & Two years after filing date & 477,948.08 & 457,694.83 & 9,175 \\
-\cline{1-5}
+\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change, Jan. 2017 to Jan. 2019 & 46,593.74 & 37,330.00 & 158,125.14 & 10,160 \\
+ & Zestimate, Jan. 2017 & 298,908.73 & 235,117.00 & 352,754.39 & 10,176 \\
+\cline{1-6}
+\multirow[c]{7}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,797.07 & 1,355.40 & 17,579.99 & 40,726 \\
+ & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
+ & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
+ & Share below poverty line & 0.20 & 0.16 & 0.15 & 40,726 \\
+ & Share white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
+ & Share with bachelor's degree & 0.26 & 0.22 & 0.17 & 40,726 \\
+ & Share with commute $<$15 minutes (2010) & 0.28 & 0.27 & 0.11 & 40,726 \\
+\cline{1-6}
+\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
+ & No cause & 0.11 & 0.00 & 0.31 & 40,727 \\
+ & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,727 \\
+\cline{1-6}
+\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
+ & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,727 \\
+ & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,727 \\
+ & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,727 \\
+\cline{1-6}
+\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
+ & Case dismised & 0.29 & 0.00 & 0.45 & 40,727 \\
+ & Case duration & 57.81 & 21.00 & 78.29 & 39,087 \\
+ & Case heard & 0.06 & 0.00 & 0.23 & 40,727 \\
+ & Case mediated & 0.41 & 0.00 & 0.49 & 40,727 \\
+ & Money judgment & 1,890.34 & 0.00 & 5,279.49 & 40,727 \\
+\cline{1-6}
+\multirow[c]{4}{4cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 377,384.02 & 305,144.00 & 316,645.29 & 10,096 \\
+ & One year after filing date & 421,601.75 & 347,550.00 & 344,328.86 & 10,443 \\
+ & Three years after filing date & 501,611.80 & 414,600.00 & 780,467.01 & 5,894 \\
+ & Two years after filing date & 477,948.08 & 393,900.00 & 457,694.83 & 9,175 \\
+\cline{1-6}
 \bottomrule

### 2023-01-17 src/02_analysis/analysis_utilities.py

@@ -182,7 +182,7 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
 
     # Concatenate Panels A-E
     summary_statistics = pd.concat([panel_A, panel_B, panel_C, panel_D, panel_E, panel_F],
-                                   axis=0)[['mean', 'std', 'count']]
+                                   axis=0)[['mean', '50%', 'std', 'count']]
 
     variable_display_names_dict = {'for_cause': "For cause", 'no_cause': "No cause",
                                    'non_payment': "Non-payment of rent",
@@ -196,13 +196,13 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                                    'popdensity2010': 'Population density (2010)',
                                    'share_white2010': 'Share white (2010)',
                                    'frac_coll_plus2010': 'Share with bachelor\'s degree',
-                                   'job_density_2013': 'Jobs per sq. mile (2010)',
+                                   'job_density_2013': 'Jobs per square mile (2010)',
                                    'mean_commutetime2000': 'Mean commute time (2000)',
-                                   'traveltime15_2010': 'Share with commute $<$15 min. (2010)',
+                                   'traveltime15_2010': 'Share with commute $<$15 minutes (2010)',
                                    'poor_share2010': 'Share below poverty line',
                                    'twenty_seventeen': 'Zestimate, Jan. 2017',
                                    'twenty_eighteen': 'Zestimate, Jan. 2018',
-                                   'change_in_zestimates': 'Zestimate, Jan. 2019 $-$ Zestimate, Jan. 2017',
+                                   'change_in_zestimates': 'Change, Jan. 2017 to Jan. 2019',
                                    'zestimate_0_years_relative_to_treatment': "At filing date",
                                    'zestimate_1_years_relative_to_treatment': "One year after filing date",
                                    'zestimate_2_years_relative_to_treatment': "Two years after filing date",

### 2023-01-17 output/DiD/tables/balance_table.tex
Re-added median

--- 2023-01-17 output/DiD/tables/balance_table.tex
@@
 \multirow[c]{2}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 10,030.65 & 0.18 \\
- & Zestimate, Jan. 2019 $-$ Zestimate, Jan. 2017 & 50,491.60 & 2,664.69 & 0.27 & -23.86 & 0.99 \\
+ & Change, Jan. 2017 to Jan. 2019 & 50,491.60 & 2,664.69 & 0.27 & -23.86 & 0.99 \\
 \cline{1-7}
 \multirow[c]{6}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.25 & 0.01 & 0.07 & 0.01 & 0.40 \\
- & Jobs per sq. mile (2010) & 4,158.02 & 263.90 & 0.63 & 122.36 & 0.83 \\
+ & Jobs per square mile (2010) & 4,158.02 & 263.90 & 0.63 & 122.36 & 0.83 \\
  & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,159.98 & 0.25 \\
@@
  & Share white (2010) & 0.60 & 0.04 & 0.00 & 0.02 & 0.06 \\
- & Share with commute <15 min. (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.27 \\
+ & Share with commute $<$15 minutes (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.27 \\
 \cline{1-7}

### 2023-01-17 writing/paper/main.tex
Updates from Overleaf

@@
 
-\geometry{left=1.0in,right=1.0in,top=1.0in,bottom=1.0in}
+\geometry{left=0.5in,right=0.5in,top=1.0in,bottom=1.0in}
 
@@
 
+    This unconditional parallel trends assumption is unlikely to hold.
+Eviction case outcomes are likely to be endogenous to their socoioeconomic surroundings.
+Indeed, covariate exploration table reveals t
+
+    \begin{table}[H]
+        \centering
+        \input{output/DiD/tables/pre_treatment_covariate_tests.tex}
+        \caption{Caption}
+        \label{tab:my_label}
+    \end{table}
+
     \subsection{Estimating the ATT in the Staggered Treatment Case}

### 2023-01-19 output/DiD/tables/balance_table.tex
Dropped months w low sample size

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 10,030.65 & 0.18 \\
- & Change, Jan. 2017 to Jan. 2019 & 50,491.60 & 2,664.69 & 0.27 & -23.86 & 0.99 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,942.14 & 26,566.34 & 0.00 & 14,752.11 & 0.14 \\
+ & Change, Jan. 2017 to Jan. 2019 & 50,491.60 & 2,654.65 & 0.27 & -2,202.60 & 0.49 \\
 \cline{1-7}
-\multirow[c]{6}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.25 & 0.01 & 0.07 & 0.01 & 0.40 \\
- & Jobs per square mile (2010) & 4,158.02 & 263.90 & 0.63 & 122.36 & 0.83 \\
- & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,159.98 & 0.25 \\
- & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 488.36 & 0.17 \\
- & Share white (2010) & 0.60 & 0.04 & 0.00 & 0.02 & 0.06 \\
- & Share with commute $<$15 minutes (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.27 \\
+\multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.25 & 0.01 & 0.07 & 0.00 & 0.96 \\
+ & Jobs per square mile (2010) & 4,158.02 & 263.90 & 0.63 & 322.24 & 0.64 \\
+ & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,497.45 & 0.24 \\
+ & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 787.73 & 0.09 \\
+ & Median two bedroom rent (2015) & 1,093.36 & 34.26 & 0.05 & 6.43 & 0.77 \\
+ & Share white (2010) & 0.60 & 0.04 & 0.00 & 0.03 & 0.02 \\
+ & Share with commute $<$15 minutes (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.60 \\
 \cline{1-7}
-\textit{Panel C} & For cause & 0.12 & 0.01 & 0.68 & 0.00 & 0.83 \\
+\textit{Panel C} & For cause & 0.12 & 0.01 & 0.68 & -0.00 & 0.86 \\
 \cline{1-7}
-\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.66 \\
+\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.89 \\
 \cline{1-7}

### 2023-01-19 output/DiD/tables/pre_treatment_covariate_tests.tex
Dropped months w low sample size

@@
 \cline{1-4}
-\multirow[c]{7}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.07 \\
+\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.07 \\
  & Jobs per square mile (2010) & 0.00 & 0.63 \\
@@
  & Population density (2010) & 0.00 & 0.01 \\
+ & Median two bedroom rent (2015) & 0.00 & 0.05 \\
  & Share white (2010) & 0.00 & 0.00 \\

### 2023-01-19 output/summary_statistics/tables/summary_statistics.tex
Dropped months w low sample size

@@
 \cline{1-6}
-\multirow[c]{7}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,797.07 & 1,355.40 & 17,579.99 & 40,726 \\
+\multirow[c]{8}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,797.07 & 1,355.40 & 17,579.99 & 40,726 \\
  & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
+ & Median two bedroom rent (2015) & 1,116.27 & 1,055.00 & 396.29 & 30,537 \\
  & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\

### 2023-01-19 src/01_build/06_merge.py

@@ -61,7 +61,6 @@ if __name__ == '__main__':
 
     # Merge with Zillow data.
     zestimates_df = pd.read_csv(INPUT_DATA_ZESTIMATES)
-    merged_df.to_csv("~/Desktop/duplicates_check.csv")
     merged_df = zestimates_df.merge(merged_df, on='case_number', how='right', validate='1:1')
     if VERBOSE:
         successfully_matched_observations = (~merged_df['2022-12'].isna()).sum()
@@ -108,7 +107,7 @@ if __name__ == '__main__':
 
     # Save unrestricted data file.
     geographic_columns = ['Accuracy Score', 'Accuracy Type', 'Number', 'Street', 'Unit Type', 'Unit Number', 'City',
-                          'State', 'County', 'Zip', 'Country', 'Source', 'Census Year', 'State FIPS', 'County FIPS',
+                          'State', 'Zip', 'Country', 'Source', 'Census Year', 'State FIPS', 'County FIPS',
                           'Place Name', 'Place FIPS', 'Census Tract Code', 'Census Block Code', 'Census Block Group',
                           'Metro/Micro Statistical Area Code', 'Metro/Micro Statistical Area Type',
                           'Combined Statistical Area Code', 'Metropolitan Division Area Code']

### 2023-01-23 output/DiD/tables/balance_table.tex
Started spatial join

--- 2023-01-17 output/DiD/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 10,030.65 & 0.18 \\
- & Change, Jan. 2017 to Jan. 2019 & 50,491.60 & 2,664.69 & 0.27 & -23.86 & 0.99 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,942.14 & 26,566.34 & 0.00 & 2,765.99 & 0.78 \\
+ & Change, Jan. 2017 to Jan. 2019 & 50,491.60 & 2,654.65 & 0.27 & -3,413.38 & 0.29 \\
 \cline{1-7}
-\multirow[c]{6}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.25 & 0.01 & 0.07 & 0.01 & 0.40 \\
- & Jobs per square mile (2010) & 4,158.02 & 263.90 & 0.63 & 122.36 & 0.83 \\
- & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,159.98 & 0.25 \\
- & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 488.36 & 0.17 \\
- & Share white (2010) & 0.60 & 0.04 & 0.00 & 0.02 & 0.06 \\
- & Share with commute $<$15 minutes (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.27 \\
+\multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.25 & 0.01 & 0.07 & 0.00 & 0.91 \\
+ & Jobs per square mile (2010) & 4,158.02 & 263.90 & 0.63 & 595.71 & 0.42 \\
+ & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 133.06 & 0.92 \\
+ & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 618.56 & 0.19 \\
+ & Median two bedroom rent (2015) & 1,093.36 & 34.26 & 0.05 & 8.67 & 0.68 \\
+ & Share white (2010) & 0.60 & 0.04 & 0.00 & 0.00 & 0.87 \\
+ & Share with commute $<$15 minutes (2010) & 0.29 & -0.01 & 0.02 & -0.01 & 0.32 \\
 \cline{1-7}
-\textit{Panel C} & For cause & 0.12 & 0.01 & 0.68 & 0.00 & 0.83 \\
+\textit{Panel C} & For cause & 0.12 & 0.01 & 0.68 & -0.01 & 0.57 \\
 \cline{1-7}
-\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.66 \\
+\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.63 \\
 \cline{1-7}

### 2023-01-23 src/01_build/03_clean_census_tract_covariates.py

@@ -21,5 +21,7 @@ tracts_df.loc[:, 'tract_geoid'] = tracts_df['state'].astype(str) + tracts_df['co
 
 
 # Save data.
-tracts_df.to_csv(OUTPUT_DATA)
+columns_to_keep = ['tract_geoid', 'med_hhinc2016', 'popdensity2010', 'share_white2010', 'frac_coll_plus2010', 'job_density_2013',
+                   'poor_share2010', 'traveltime15_2010', 'rent_twobed2015', 'czname']
+tracts_df[columns_to_keep].to_csv(OUTPUT_DATA)
 #%%

### 2023-01-23 src/01_build/06_merge.py

@@ -1,172 +1,0 @@
-"""
-06_merge.py
-
-Merge eviction data with assessment values.
-"""
-if __name__ == '__main__':
-    import pandas as pd
-    import geopandas as gpd
-    from build_utilities import geocode_coordinates
-
-    INPUT_DATA_EVICTIONS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions.csv"
-    INPUT_DATA_TAX_PARCELS_EAST = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/Statewide_parcels_SHP/L3_TAXPAR_POLY_ASSESS_EAST.shp"
-    INPUT_DATA_TAX_PARCELS_WEST = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/Statewide_parcels_SHP/L3_TAXPAR_POLY_ASSESS_WEST.shp"
-    INPUT_DATA_TRACTS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/tracts.csv"
-    INPUT_DATA_ZESTIMATES = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/zestimates.csv"
-    INPUT_DATA_ASSESSMENT_VALUES = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/assessor_values.csv"
-    OUTPUT_DATA_UNRESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/unrestricted.csv"
-    OUTPUT_DATA_RESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/restricted.csv"
-    VERBOSE = True
-
-    # Load evictions data.
-    evictions_df = pd.read_csv(INPUT_DATA_EVICTIONS)
-    evictions_gdf = gpd.GeoDataFrame(evictions_df,
-                                     geometry=gpd.points_from_xy(evictions_df['longitude'], evictions_df['latitude']))
-    evictions_gdf = evictions_gdf.set_crs("EPSG:4326")  # crs attribute is currently unassigned.
-
-    # Load tax parcel files.
[…]

### 2023-01-23 src/01_build/06_merge_evictions_with_parcels_and_tracts.py

@@ -1,0 +1,86 @@
+"""
+06_merge_evictions_with_parcels_and_tracts.py
+"""
+
+import pandas as pd
+import geopandas as gpd
+import os
+os.environ['USE_PYGEOS'] = '0'
+
+INPUT_DATA_EVICTIONS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions.csv"
+INPUT_DATA_TRACTS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/tracts.csv"
+INPUT_DATA_TAX_PARCELS_EAST = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/Statewide_parcels_SHP/L3_TAXPAR_POLY_ASSESS_EAST.shp"
+INPUT_DATA_TAX_PARCELS_WEST = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/Statewide_parcels_SHP/L3_TAXPAR_POLY_ASSESS_WEST.shp"
+OUTPUT_DATA_UNRESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions_with_parcels_and_tracts.csv"
+
+VERBOSE = True
+
+# Load evictions data.
+evictions_df = pd.read_csv(INPUT_DATA_EVICTIONS)
+evictions_df.loc[:, 'file_month'] = pd.to_datetime(evictions_df['file_date']).dt.strftime('%Y-%m')
+evictions_df.loc[:, 'file_year'] = pd.to_datetime(evictions_df['file_date']).dt.year
+original_N = len(evictions_df)
+
+# Drop cases missing file_date.
+mask = evictions_df['file_date'].notna()
+if VERBOSE:
+    print(
+        f"Dropping {(~mask).sum()} observations where file_date is missing ({100 * (((~mask).sum()) / original_N):.3} percent "
+        f"of original dataset).")
+evictions_df = evictions_df.loc[mask, :]
+
+# Clean the values in the judgment_for_pdu variable.
+judgment_for_pdu_replacement_dict = {"unknown": "Unknown",
+                                     "plaintiff": "Plaintiff",
+                                     "defendant": "Defendant"}
+evictions_df.loc[:, "judgment_for_pdu"] = evictions_df.loc[:, "judgment_for_pdu"].replace(
[…]

### 2023-01-23 src/01_build/07_merge_evictions_with_outcomes.py

@@ -1,0 +1,161 @@
+"""
+07_merge_evictions_with_outcomes.py
+
+Merge eviction data with assessment values.
+"""
+
+import os
+os.environ['USE_PYGEOS'] = '0'
+import geopandas as gpd
+import pandas as pd
+
+INPUT_DATA_EVICTIONS_PARCELS_AND_TRACTS = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/evictions_with_parcels_and_tracts.csv"
+INPUT_DATA_ZESTIMATES = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/02_intermediate/zestimates.csv"
+INPUT_DATA_CRIME = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/crime_incidents"
+OUTPUT_DATA_UNRESTRICTED = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/unrestricted.csv"
+OUTPUT_DATA_ZILLOW = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/03_cleaned/zestimates_analysis.csv"
+
+VERBOSE = True
+
+# Produce the unrestricted sample---------------------------------------------------------------------------------------
+evictions_with_parcels_and_tracts_df = pd.read_csv(INPUT_DATA_EVICTIONS_PARCELS_AND_TRACTS).drop(index=29305)
+
+# TODO: Merge with crime data-------------------------------------------------------------------------------------------
+crime_df = pd.concat([pd.read_csv(os.path.join(INPUT_DATA_CRIME, file)) for file in os.listdir(INPUT_DATA_CRIME)],
+                     axis=0)  # Read crime data.
+crime_df = crime_df.dropna(subset=['Long', 'Lat', 'OCCURRED_ON_DATE'])
+crime_df = (gpd  # Convert crime data to a GeoDataFrame.
+            .GeoDataFrame(crime_df,
+                          geometry=gpd.points_from_xy(crime_df['Long'], crime_df['Lat']))
+            .set_crs("EPSG:4326")
+            .to_crs("EPSG:26986")
+            .drop(columns=['Lat', 'Long', 'Location', 'UCR_PART', 'HOUR', 'DAY_OF_WEEK', 'YEAR', 'MONTH',
[…]

### 2023-01-23 src/01_build/scratch.py

@@ -1,0 +1,3 @@
+data = "/Users/arjunshanmugam/Documents/GitHub/seniorthesis/data/01_raw/crime_incidents"
+import os
+print(os.listdir(data))

### 2023-01-23 src/02_analysis/analysis_utilities.py

@@ -109,7 +109,6 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     panel_A = pd.concat([panel_A], keys=["Panel A: Pre-treatment Zestimates"])
 
     # Panel B: Census Tract Characteristics
-    # TODO: RE-ADD 'mean_commutetime2000' TO THIS LIST AFTER RE-RUNNING 06_merge.py
     panel_B_columns = ['med_hhinc2016', 'popdensity2010', 'share_white2010', 'frac_coll_plus2010', 'job_density_2013',
                         'poor_share2010', 'traveltime15_2010', 'rent_twobed2015']
     panel_B = df[sorted(panel_B_columns)].describe().T

### 2023-01-23 writing/paper/main.tex

--- 2023-01-14 writing/paper/main.tex
@@
 \bibliographystyle{rusnat}
-\bibliography{citations}
 
@@
 
-    \subsection{Tax Assessment Records}
-    \subsection{Zestimates}
-        \begin{figure}[H]
-            \centering
-            \includegraphics{output/summary_statistics/figures/trends_in_zestimates.png}
-            \caption{Trends in Zestimates}
-            \label{fig:my_label}
-        \end{figure}
-
         \begin{figure}[H]
@@
 
-\section{Empirical Strategy: Difference-in-Difference}
+\section{Empirical Strategy: Difference-in-Differences}
     I seek to estimate the average treatment effects of plaintiff victory in eviction cases on treated properties.
 I use the staggered difference-in-difference estimator proposed in \cite{callaway_difference--differences_2021}, which uses two-period, two-unit difference-in-difference estimators to estimate time- and cohort-specific ATTs and then aggregates them, weighting by cohort size, to produce summaries of the ATT.
+
     Let $G_i$ be the month during which the eviction case involving property $i$ was filed, such that $G_i = g \in \{\text{May} \; 2019, \text{June} \; 2019, ..., \text{May} \; 2021\}$.
 Let $C_i = 1$ if the eviction case involving $i$ resulted in a victory for the defendant and $0$ otherwise.
-If $G_i = g$ and $C_i = 0$, then property $i$ is a treated property and a member of the cohort first treated during month $g$.
+If $G_i = g$ and $C_i = 0$, then property $i$ is a treated property and a member of the cohort first treated during month $g$ (cohort $g$).
 If $C_i=1$, then property $i$ is a never-treated property.
+Let $Y_{i,t}$ be property $i$'s Zestimate during month $t$ and define $\Delta Y_{i, g-1, t} \equiv Y_{i,t} - Y_{i,g-1}$ so that $\Delta Y_{i, g-1, t}$ is the change in property $i$'s Zestimate between months $t$ and $g-1$.
 
     \subsection{Unconditional Estimates of the ATT}
-    The following is an unconditional estimator for $ATT(g,t)$, the average treatment affect during month $t$ for the cohort first treated during month $g$.
+    The following is an unconditional estimator for $ATT(g,t)$, the average treatment affect during month $t$ for cohort $g$.
+    \begin{align}
+        \hat{ATT}^{nev}_{un}(g, t) = \frac{\sum_i\Delta Y_{i, g-1, t}\mathds{1}\{G_i=g\}}{\sum_i\mathds{1}\{G_i=g\}} - \frac{\sum_i\Delta Y_{i, g-1, t}\mathds{1}\{C_i=1\}}{\sum_i\mathds{1}\{C_i=1\}}
+    \end{align}
+    The above estimator will identify $ATT(g,t)$ under the assumption that the change in untreated potential outcomes between periods $g-1$ and $t$ is the same among units in cohort $g$ as it is among never-treated units.
 
+    \subsection{D.R. Estimates of the ATT}
+
+    The above unconditional parallel trends assumption is unlikely to hold, as eviction case outcomes and zestimates may be related to their socioeconomic surroundings.
+Table 3 explores this theory further, reporting results from univariate regressions of January 2022 Zestimates and an indicator for plaintiff victory on the pre-treatment characteristics listed in Panels A through D of Table 2.
+Each cell gives the p-value from a regression of the variable which labels its column on the variable which labels its row.
+Table 3 shows significant associations between pre-treatment characteristics and Zestimates and pre-treatment characteristics and case outcomes, suggesting that the unconditional parallel trends assumption imposed earlier may not be valid.
+
+    \begin{table}[H]
+        \centering
+        \input{output/DiD/tables/pre_treatment_covariate_tests.tex}
+        \caption{Relationship Between Pre-Treatment Characteristics and the Dependent and Independent Variables}
+        \label{tab:my_label}
+    \end{table}
+
+    My next strategy uses covariates to construct a more credible counterfactual for the observed path of outcomes in the treatment group using the doubly robust difference-in-differences estimator proposed by \cite{santanna_doubly_2018}.
+For each property, let $X_i$ be a vector containing the covariates whose univariate regression coefficients from column 1 of table 3 are significant at the 5 percent level.
+To attempt to identify $ATT(g, t)$ using the doubly robust estimator, I first estimate $\hat{p}_g(X_i)$, a logit regression propensity score model for being in cohort $g$.
+I assign a weight $\hat{w}_i(X_i) \equiv\frac{\hat{p}_g(X_i)}{1 - \hat{p}_g(X_i)}$ to each never-treated property $i$; $\hat{w}_i(X_i) \equiv 1$ for treated properties.
+Define $\hat{w}^*_i(X_i) = \frac{\hat{w}_i(X_i)}{\sum_i \hat{w}_i(X_i)}$.
+Second, using only never-treated counties, I regress $\Delta Y_{i, g-1, t}$ on $X_j$, weighting by $\hat{w}_i(X_i)$.
+Using the estimated coefficients $\hat{\beta}_{g-1, t}^{X}$, I define $\Delta \hat{\mu}_{g-1, t}(X_i) \equiv \hat{\beta}_{g-1, t}^{X}X_i$ so that $\Delta \hat{\mu}_{g-1, t}(X_i)$ is the predicted change in property $i$'s Zestimate between months $t$ and $g-1$.
+    The doubly robust estimator for $ATT(g, t)$ is as follows.
     \begin{align}
-        \hat{ATT}^{nev}_{un}(g, t) = \frac{\sum_i(Y_{i,t} - Y_{i, g-1})\mathds{1}\{G_i=g\}}{\sum_i\mathds{1}\{G_i=g\}} - \frac{\sum_i(Y_{i,t} - Y_{i, g-1})\mathds{1}\{C_i=1\}}{\sum_i\mathds{1}\{C_i=1\}}
+        \hat{ATT}^{nev}_{DR, X}(g,t) = \frac{1}{N}\sum_i[(\frac{D_i}{\Bar{D_i}} - \frac{\hat{w}^*_i(X_i)C_i}{\Bar{C_i}})(\Delta Y_{i, g-1, t} - \hat{\mu}_{g-1, t}(X_i))]
     \end{align}
+    Note that $\Bar{D_i}$ and $\Bar{C_i}$ are sample averages. Under the assumption of parallel trends among units with the same covariates, $\hat{ATT}^{nev}_{DR, X}(g,t)$ will identify $ATT(g, t)$.
 
-    \subsection{Estimating the ATT in the Staggered Treatment Case}
-    I will use Callaway and Sant'Anna' (2021)'s multiperiod, staggered treatment difference-in-difference estimators.
-The following bullets summarize the empirical strategy informally; this information will eventually be placed appropriately into the subsection headers below this brief summary.
-    \begin{enumerate}
-        \item Reject conventional TWFE-DiD estimator.
-This estimator essentially estimates the ATT by performing a bunch of 2 unit, 2 period DiDs, then averages the calculated treatment effects.
-Goodman-Bacon (2021) shows that this estimator is composed in part of DiD estimates involving \emph{two units which are both treated during both periods}.
-This is in violation of the spirit of DiD.
-These incorrect DiD estimates are known as ``forbidden comparisons.''
-        \item The way to properly recover the ATT is to basically perform all of the ``non-forbidden'' comparisons possible in our panel dataset. More formally:
-        \begin{enumerate}
-            \item We begin with a panel dataset of properties whose Zestimates are observed monthly.
-At each property $i$, an eviction case concludes during month $G_i=g$, resulting in a plaintiff victory or a defendant victory.
-These properties are collectively known as ``cohort $g$.'' If the eviction case at property $i$ resulted in a defendant victory, let $C_i=1$
-            \item Break the units into ``cohorts'' according to the month in which their cases conclude. 
-            \item We estimate $ATT(g, t)$, which is the average treatment effect on the treated for cohort $g$ at time $t$, by calculating the sample analog of:
+    Columns 2 and 3 of table 4 shows significant pre-treatment imbalance in covariates between the treatment and control groups.
+Each row of column 2 reports the coefficient from a univariate regression of one covariate on an indicator for plaintiff victory.
+Column 3 reports the p-values associated with each of these coefficients.
+In each row of column 4, I regress one covariate on an indicator for plaintiff victory and $\hat{w}_i(X_i)$ and report the coefficient on the indicator for plaintiff victory.
+Column 5 reports the p-values associated with each coefficient and shows that conditioning on pre-treatment covariates makes virtually all pre-treatment differences in covariates insignificant.
 
-            $E[Y_t - Y_{g-1}|G=g] - [Y_t - Y_{g-1}|C=1]$
-
-            \item Intuitively, $ATT(g, t)$ comes from 2 period, 2 unit difference in difference estimate.
-The treatment group contains all units where we observe a plaintiff victory and the case was resolved at time $g$.
-The control group contains all units where we observe a defendant victory and the case was resolved at time $g$.
-We adjust the change in observed outcomes in the treatment group by the change in observed outcomes in the control group to get our estimate.
-
-        \end{enumerate}
-        \item The parallel trends and no anticipation assumptions are extended to the staggered treatment context.
-            \begin{enumerate}
-                \item \textbf{Staggered Treatment Adoption Assumption.} Let $D_it=1$ if unit $i$ has been treated by period $t$ and $D_it=0$ otherwise.
-Then, for $t=1,...,\tau$, $D_{it}=1 \rightarrow D_{it+1} = 1$.
-Basically, once a unit becomes treated, it stays treated.
-
-                \item \textbf{Parallel Trends Assumption Based On Never Treated Units}. For all $g=2,...,\tau, t=2,...,\tau$ with $t\geq g$, we have
-
-                $E[Y_t(0)-Y_{g-1}(0)|G=g]$ = $E[Y_t(0)-Y_{g-1}(0)|C=1]$
-
-                Basically, for every possible 2 unit, 2 period DiD that we can run in our panel dataset between treated units and never-treated units, the canonical parallel trends assumption holds.
-
-                \item \textbf{Parallel Trends Assumption Based On Not Yet Treated Units}. For all $g=2,...,\tau, s, t=2,...,\tau$ with $t \geq g$ and $s \geq t$, we have
-
-                $E[Y_t(0) - Y_{t-1}(0)|G=g] = E[Y_t(0) - Y_{t-1}(0)|D_s=1, G \neq g]$
-
-                This assumption allows us to use \emph{not yet treated} observations as a comparison group for \emph{treated} units.
-This is clearly a stronger assumption than the previous one and I have to think hard about whether I can make it in my case.
-Note that the graph in section 5.3 does NOT make this assumption.
-
-            \end{enumerate}
-        \item Now, we have a bunch of $ATT(g, t)$s. How do we aggregate them?
-            \begin{enumerate}
-                \item Take frequency-weighted averages across $t$ to get $ATT(g)$s, or ATTs for each cohort.
-                \item Take frequency-weighted averages across $g$ to get $ATT(t)$s, or ATTs for each time period.
-                \item Most convincing: calculate event time $e = t - g$.
-Now, $ATT(g, e_i)$ expresses the ATT on cohort $g$ at time relative to the end of the eviction case involving property $i$.
-Take frequency weighted averages across $g$ to get $ATT(e)s$, or ATTs for each period relative to the treatment period.
-            \end{enumerate}
-    \end{enumerate}
+    The estimator defined in equation 2 simultaneously models the counterfactual change in \emph{observed} outcomes for untreated properties ($\hat{w}_i(X_i)$) and the \emph{predicted} change in outcomes for untreated properties ($\hat{\mu}_{g-1, t}(X_i)$).
+As long as one of these two models is correctly specified, the doubly robust estimator will identify $ATT(g, t)$.
 
@@
         \input{output/DiD/tables/balance_table.tex}
-        \caption{Caption}
+        \caption{Balance Tests}
         \label{tab:my_label}
@@
 
-    \subsection{Parallel Trends Assumptions in the Staggered Treatment Case}
-
-        \subsection{Testing Parallel Trends Empirically Using Rambachan and Roth (2022)}
     \subsection{Aggregating Treatment Effects Across Cohort and Time}
@@
 \section{Results} \label{sec:result}
-    \subsection{ATTs Across Cohorts}
-    \subsection{ATTs Across Time Periods}
-    \subsection{Event-Study ATTs}
+
+    \subsection{Unconditional Estimates of the ATT}
+
     \begin{figure}[H]
         \centering
-            \includegraphics{output/DiD/figures/att_gt_estimates_event_study.png}
-            \caption{$ATT(e)$s}
+        \includegraphics{output/DiD/figures/att_gt_unconditional_event_study_short_horizon.png}
+        \caption{}
+        \label{fig:my_label}
+    \end{figure}
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics{output/DiD/figures/att_gt_unconditional_event_study_long_horizon.png}
+        \caption{}
+        \label{fig:my_label}
+    \end{figure}
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics{output/DiD/figures/att_gt_unconditional_time.png}
+        \caption{}
+        \label{fig:my_label}
+    \end{figure}
+
+    \subsection{D.R. Estimates of the ATT}
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics{output/DiD/figures/att_gt_dr_event_study_short_horizon.png}
+        \caption{}
+        \label{fig:my_label}
+    \end{figure}
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics{output/DiD/figures/att_gt_dr_event_study_long_horizon.png}
+        \caption{}
+        \label{fig:my_label}
+    \end{figure}
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics{output/DiD/figures/att_gt_dr_time.png}
+        \caption{}
         \label{fig:my_label}
@@
 \section{Conclusion} \label{sec:conclusion}
+
+\bibliography{citations}
 

### 2023-02-25 output/DiD/tables/balance_table.tex

--- 2023-01-17 output/DiD/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 10,030.65 & 0.18 \\
- & Change, Jan. 2017 to Jan. 2019 & 50,491.60 & 2,664.69 & 0.27 & -23.86 & 0.99 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,945.81 & 26,673.96 & 0.00 & 3,189.17 & 0.75 \\
+ & Change, Jan. 2017 to Jan. 2019 & 50,501.64 & 2,697.85 & 0.27 & -3,196.88 & 0.32 \\
 \cline{1-7}
-\multirow[c]{6}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.25 & 0.01 & 0.07 & 0.01 & 0.40 \\
- & Jobs per square mile (2010) & 4,158.02 & 263.90 & 0.63 & 122.36 & 0.83 \\
- & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,159.98 & 0.25 \\
- & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 488.36 & 0.17 \\
- & Share white (2010) & 0.60 & 0.04 & 0.00 & 0.02 & 0.06 \\
- & Share with commute $<$15 minutes (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.27 \\
+\multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.25 & 0.01 & 0.09 & -0.00 & 0.96 \\
+ & Jobs per square mile (2010) & 4,161.51 & 259.78 & 0.64 & 668.27 & 0.37 \\
+ & Median household income (2016) & 52,084.78 & 2,271.04 & 0.03 & -211.14 & 0.87 \\
+ & Population density (2010) & 9,018.27 & 962.56 & 0.01 & 644.23 & 0.17 \\
+ & Median two bedroom rent (2015) & 1,093.52 & 33.19 & 0.05 & 8.19 & 0.69 \\
+ & Share white (2010) & 0.60 & 0.03 & 0.00 & -0.00 & 0.94 \\
+ & Share with commute $<$15 minutes (2010) & 0.29 & -0.01 & 0.02 & -0.01 & 0.29 \\
 \cline{1-7}
-\textit{Panel C} & For cause & 0.12 & 0.01 & 0.68 & 0.00 & 0.83 \\
+\textit{Panel C} & For cause & 0.12 & 0.01 & 0.67 & -0.01 & 0.56 \\
 \cline{1-7}
-\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.66 \\
+\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.36 & 0.00 & 0.64 \\
 \cline{1-7}

### 2023-02-25 output/DiD/tables/pre_treatment_covariate_tests.tex

--- 2023-01-17 output/DiD/tables/pre_treatment_covariate_tests.tex
@@
 \cline{1-4}
-\multirow[c]{7}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.07 \\
- & Jobs per square mile (2010) & 0.00 & 0.63 \\
- & Median household income (2016) & 0.00 & 0.01 \\
- & Share below poverty line & 0.70 & 0.01 \\
+\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.09 \\
+ & Jobs per square mile (2010) & 0.00 & 0.64 \\
+ & Median household income (2016) & 0.00 & 0.03 \\
+ & Share below poverty line & 0.69 & 0.01 \\
  & Population density (2010) & 0.00 & 0.01 \\
+ & Median two bedroom rent (2015) & 0.00 & 0.05 \\
  & Share white (2010) & 0.00 & 0.00 \\
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.01 & 0.68 \\
- & No cause & 0.98 & 0.03 \\
- & Non-payment of rent & 0.31 & 0.77 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.01 & 0.67 \\
+ & No cause & 0.99 & 0.03 \\
+ & Non-payment of rent & 0.31 & 0.75 \\
 \cline{1-4}
 \multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.37 & 0.00 \\
- & Plaintiff has an attorney & 0.61 & 0.47 \\
- & Defendant is an entity & 0.02 & 0.37 \\
- & Plaintiff is an entity & 0.62 & 0.13 \\
+ & Plaintiff has an attorney & 0.61 & 0.49 \\
+ & Defendant is an entity & 0.02 & 0.36 \\
+ & Plaintiff is an entity & 0.62 & 0.11 \\
 \cline{1-4}

### 2023-02-27 output/DiD_crime/tables/balance_table.tex
Abstracted DiD code

--- 2023-01-23 output/DiD/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,942.14 & 26,566.34 & 0.00 & 2,765.99 & 0.78 \\
- & Change, Jan. 2017 to Jan. 2019 & 50,491.60 & 2,654.65 & 0.27 & -3,413.38 & 0.29 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & Crimes reported, Jan. 2017 & 1.51 & 0.35 & 0.57 & 0.14 & 0.82 \\
+ & Change in Crimes Reported, Jan. 2017 to Jan. 2019 & -0.02 & 0.07 & 0.50 & 0.05 & 0.65 \\
 \cline{1-7}
-\multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.25 & 0.01 & 0.07 & 0.00 & 0.91 \\
- & Jobs per square mile (2010) & 4,158.02 & 263.90 & 0.63 & 595.71 & 0.42 \\
- & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 133.06 & 0.92 \\
- & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 618.56 & 0.19 \\
- & Median two bedroom rent (2015) & 1,093.36 & 34.26 & 0.05 & 8.67 & 0.68 \\
- & Share white (2010) & 0.60 & 0.04 & 0.00 & 0.00 & 0.87 \\
- & Share with commute $<$15 minutes (2010) & 0.29 & -0.01 & 0.02 & -0.01 & 0.32 \\
+\textit{Panel B} & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & -0.01 & 0.11 \\
 \cline{1-7}
-\textit{Panel C} & For cause & 0.12 & 0.01 & 0.68 & -0.01 & 0.57 \\
-\cline{1-7}
-\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.63 \\
+\textit{Panel D} & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.01 & 0.16 \\
 \cline{1-7}

### 2023-02-27 output/DiD_crime/tables/pre_treatment_covariate_tests.tex
Abstracted DiD code

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Crime Incidents, Dec. 2022 & Plaintiff victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Crimes reported, Jan. 2017 & 0.00 & 0.57 \\
 & Change in Crimes Reported, Jan. 2017 to Jan. 2019 & 0.00 & 0.50 \\
\cline{1-4}
\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.87 & 0.24 \\
 & Jobs per square mile (2010) & 0.15 & 0.16 \\
 & Median household income (2016) & 0.59 & 0.19 \\
 & Share below poverty line & 0.78 & 0.14 \\
 & Population density (2010) & 0.08 & 0.06 \\
 & Median two bedroom rent (2015) & 0.14 & 0.50 \\
 & Share white (2010) & 0.41 & 0.10 \\
 & Share with commute $<$15 minutes (2010) & 0.01 & 0.23 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.53 & 0.48 \\
 & No cause & 0.41 & 0.00 \\
 & Non-payment of rent & 0.76 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.58 & 0.00 \\
 & Plaintiff has an attorney & 0.22 & 0.00 \\
 & Defendant is an entity & 0.39 & 0.00 \\
 & Plaintiff is an entity & 0.03 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-02-27 output/summary_statistics/tables/summary_statistics.tex
Abstracted DiD code

--- 2023-01-17 output/summary_statistics/tables/summary_statistics.tex
@@
 \toprule
- &  & Mean & S.D. & N \\
-Panel & Variable &  &  &  \\
+ &  & Mean & Median & S.D. & N \\
+Panel & Variable &  &  &  &  \\
 \midrule
-\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 298,908.73 & 352,754.39 & 10,176 \\
- & Zestimate, Jan. 2019 $-$ Zestimate, Jan. 2017 & 46,593.74 & 158,125.14 & 10,160 \\
-\cline{1-5}
-\multirow[c]{7}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per sq. mile (2010) & 4,797.07 & 17,579.99 & 40,726 \\
- & Median household income (2016) & 52,659.44 & 27,177.48 & 40,726 \\
- & Population density (2010) & 9,159.77 & 9,574.14 & 40,726 \\
- & Share below poverty line & 0.20 & 0.15 & 40,726 \\
- & Share white (2010) & 0.58 & 0.29 & 40,726 \\
- & Share with bachelor's degree & 0.26 & 0.17 & 40,726 \\
- & Share with commute $<$15 min. (2010) & 0.28 & 0.11 & 40,726 \\
-\cline{1-5}
-\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.33 & 40,727 \\
- & No cause & 0.11 & 0.31 & 40,727 \\
- & Non-payment of rent & 0.75 & 0.43 & 40,727 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,727 \\
- & Defendant is an entity & 0.01 & 0.08 & 40,727 \\
- & Plaintiff has an attorney & 0.84 & 0.37 & 40,727 \\
- & Plaintiff is an entity & 0.70 & 0.46 & 40,727 \\
-\cline{1-5}
-\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,727 \\
- & Case dismised & 0.29 & 0.45 & 40,727 \\
- & Case duration & 57.81 & 78.29 & 39,087 \\
- & Case heard & 0.06 & 0.23 & 40,727 \\
- & Case mediated & 0.41 & 0.49 & 40,727 \\
- & Money judgment & 1,890.34 & 5,279.49 & 40,727 \\
-\cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 377,384.02 & 316,645.29 & 10,096 \\
- & One year after filing date & 421,601.75 & 344,328.86 & 10,443 \\
- & Three years after filing date & 501,611.80 & 780,467.01 & 5,894 \\
- & Two years after filing date & 477,948.08 & 457,694.83 & 9,175 \\
-\cline{1-5}
+\multirow[c]{4}{4cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change in Crimes Reported, Jan. 2017 to Jan. 2019 & -0.01 & 0.00 & 0.76 & 40,734 \\
+ & Change in Zestimate, Jan. 2017 to Jan. 2019 & 46,593.08 & 37,330.00 & 158,125.24 & 10,160 \\
+ & Crimes reported, Jan. 2017 & 0.21 & 0.00 & 4.79 & 40,734 \\
+ & Zestimate, Jan. 2017 & 298,898.22 & 235,078.00 & 352,756.46 & 10,176 \\
+\cline{1-6}
+\multirow[c]{8}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,802.71 & 1,355.40 & 17,583.20 & 40,732 \\
+ & Median household income (2016) & 52,695.02 & 47,105.00 & 27,212.35 & 40,732 \\
+ & Median two bedroom rent (2015) & 1,116.73 & 1,055.00 & 396.69 & 30,546 \\
+ & Population density (2010) & 9,151.92 & 5,982.68 & 9,537.28 & 40,732 \\
+ & Share below poverty line & 0.20 & 0.16 & 0.15 & 40,732 \\
+ & Share white (2010) & 0.58 & 0.63 & 0.29 & 40,732 \\
+ & Share with bachelor's degree & 0.26 & 0.22 & 0.17 & 40,732 \\
+ & Share with commute $<$15 minutes (2010) & 0.28 & 0.27 & 0.11 & 40,732 \\
+\cline{1-6}
+\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,734 \\
+ & No cause & 0.11 & 0.00 & 0.31 & 40,734 \\
+ & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,734 \\
+\cline{1-6}
+\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,734 \\
+ & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,734 \\
+ & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,734 \\
+ & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,734 \\
+\cline{1-6}
+\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,734 \\
+ & Case dismised & 0.29 & 0.00 & 0.45 & 40,734 \\
+ & Case duration & 57.81 & 21.00 & 78.28 & 39,094 \\
+ & Case heard & 0.06 & 0.00 & 0.23 & 40,734 \\
+ & Case mediated & 0.41 & 0.00 & 0.49 & 40,734 \\
+ & Money judgment & 1,890.02 & 0.00 & 5,279.08 & 40,734 \\
+\cline{1-6}
+\multirow[c]{4}{4cm}{\textit{Panel F: Post-treatment Zestimates}} & Crimes one year after filing date & 0.19 & 0.00 & 4.32 & 40,734 \\
+ & Crimes two years after filing date & 0.18 & 0.00 & 4.40 & 35,684 \\
+ & Zestimate one year after filing date & 421,590.21 & 347,444.00 & 344,333.24 & 10,443 \\
+ & Zestimate two years after filing date & 477,931.84 & 393,800.00 & 457,699.06 & 9,175 \\
+\cline{1-6}
 \bottomrule

### 2023-03-03 src/02_analysis/analysis_utilities.py
Updated analysis utilities

@@ -12,6 +12,31 @@ from differences.did.pscore_cal import pscore_mle
 from typing import List
 
 
+def generate_variable_names(analysis: str):
+    if analysis == 'zestimate':
+        pass
+    elif analysis == 'crimes_own_parcel':
+        # Store list of crime variable names and create dictionaries which map between month variable names to integers.
+        years = [str(year) for year in range(2015, 2023)]
+        months = ["0" + str(month) for month in range(1, 10)] + [str(month) for month in range(10, 13)]
+        value_vars = [str(year) + "-" + str(month) for year in years for month in months]
+        value_vars = value_vars[5:]
+        value_vars.append('2023-01')
+        value_vars_crime = [value_var + "_crimes_own_parcel" for value_var in value_vars]
+        month_to_int_dictionary = {key: value + 1 for value, key in enumerate(value_vars)}
+        int_to_month_dictionary = {key + 1: value for key, value in enumerate(value_vars)}
+
+        to_return = value_vars_crime
+    elif analysis == 'any_crime_500m':
+        pass
+    elif analysis == 'any_crime_100m':
+        pass
+    else:
+        raise ValueError("Unrecognized argument for parameter analysis.")
+
+    return to_return, month_to_int_dictionary, int_to_month_dictionary
+
+
 def prepare_df(df: pd.DataFrame, analysis: str, treatment_date_variable: str, pre_treatment_covariates: List[str],
                value_vars: List[str], month_to_int_dictionary):
     if analysis == 'crime':
@@ -163,29 +188,40 @@ def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.D
 
 
 def select_controls(df: pd.DataFrame, analysis: str, output_directory: str):
-    # Choose covariates to include in D.R. model.
-    # Run produce summary statistics on the DataFrame to add pre-treatment covariate columns.
-    summary_statistics, variable_display_names_dict = produce_summary_statistics(df, 'file_date')
-
-    if analysis == 'crime':
-        independent_variable = 'judgment_for_plaintiff'
-        dependent_variable = 'final_month_of_panel_crimes'
-        df.loc[:, dependent_variable] = df.loc[:, '2022-12_crimes']  # Create alias column for Patchy.
-        summary_statistics = (summary_statistics
-                              .drop('twenty_seventeen_zestimate', level=1, axis=0)
[…]

### 2023-03-08 output/crimes_own_parcel/tables/balance_table.tex

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_200m & 18.17 & 0.31 & 0.72 & 0.56 & 0.73 \\
 & pre_treatment_change_in_any_crime_200m & 0.15 & 0.84 & 0.07 & 0.32 & 0.73 \\
\cline{1-7}
\multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
 & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,528.39 & 0.00 \\
 & Median household income (2016) & 48,035.65 & 1,777.65 & 0.19 & 3,418.21 & 0.18 \\
 & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.87 \\
 & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 518.25 & 0.71 \\
 & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 176.55 & 0.03 \\
 & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.01 \\
\cline{1-7}
\textit{Panel C} & No cause & 0.05 & -0.05 & 0.00 & -0.11 & 0.00 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel D}} & Plaintiff has an attorney & 0.88 & 0.07 & 0.00 & 0.20 & 0.00 \\
 & Defendant is an entity & 0.01 & -0.04 & 0.00 & 0.01 & 0.23 \\
 & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-03-08 output/summary_statistics/tables/summary_statistics.tex

--- 2023-01-17 output/summary_statistics/tables/summary_statistics.tex
@@
 \midrule
-\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change, Jan. 2017 to Jan. 2019 & 46,593.74 & 37,330.00 & 158,125.14 & 10,160 \\
- & Zestimate, Jan. 2017 & 298,908.73 & 235,117.00 & 352,754.39 & 10,176 \\
+\multirow[c]{14}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Zestimate, Jan. 2017 & 298,898.22 & 235,078.00 & 352,756.46 & 10,176 \\
+ & pre_treatment_change_in_any_crime_140m & 0.02 & 0.00 & 2.42 & 40,734 \\
+ & pre_treatment_change_in_any_crime_200m & 0.05 & 0.00 & 3.31 & 40,734 \\
+ & pre_treatment_change_in_any_crime_60m & 0.01 & 0.00 & 1.16 & 40,734 \\
+ & pre_treatment_change_in_any_crime_60m & 0.01 & 0.00 & 1.16 & 40,734 \\
+ & pre_treatment_change_in_any_crime_90m & 0.03 & 0.00 & 1.71 & 40,734 \\
+ & pre_treatment_change_in_any_crime_90m & 0.03 & 0.00 & 1.71 & 40,734 \\
+ & pre_treatment_change_in_zestimate & 46,593.08 & 37,330.00 & 158,125.24 & 10,160 \\
+ & twenty_seventeen_any_crime_140m & 1.41 & 0.00 & 5.01 & 40,734 \\
+ & twenty_seventeen_any_crime_200m & 2.68 & 0.00 & 8.69 & 40,734 \\
+ & twenty_seventeen_any_crime_60m & 0.29 & 0.00 & 1.31 & 40,734 \\
+ & twenty_seventeen_any_crime_60m & 0.29 & 0.00 & 1.31 & 40,734 \\
+ & twenty_seventeen_any_crime_90m & 0.62 & 0.00 & 2.42 & 40,734 \\
+ & twenty_seventeen_any_crime_90m & 0.62 & 0.00 & 2.42 & 40,734 \\
 \cline{1-6}
-\multirow[c]{7}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,797.07 & 1,355.40 & 17,579.99 & 40,726 \\
- & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
- & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
- & Share below poverty line & 0.20 & 0.16 & 0.15 & 40,726 \\
- & Share white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
- & Share with bachelor's degree & 0.26 & 0.22 & 0.17 & 40,726 \\
- & Share with commute $<$15 minutes (2010) & 0.28 & 0.27 & 0.11 & 40,726 \\
+\multirow[c]{8}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,802.71 & 1,355.40 & 17,583.20 & 40,732 \\
+ & Median household income (2016) & 52,695.02 & 47,105.00 & 27,212.35 & 40,732 \\
+ & Median two bedroom rent (2015) & 1,116.73 & 1,055.00 & 396.69 & 30,546 \\
+ & Population density (2010) & 9,151.92 & 5,982.68 & 9,537.28 & 40,732 \\
+ & Share below poverty line & 0.20 & 0.16 & 0.15 & 40,732 \\
+ & Share white (2010) & 0.58 & 0.63 & 0.29 & 40,732 \\
+ & Share with bachelor's degree & 0.26 & 0.22 & 0.17 & 40,732 \\
+ & Share with commute $<$15 minutes (2010) & 0.28 & 0.27 & 0.11 & 40,732 \\
 \cline{1-6}
-\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
- & No cause & 0.11 & 0.00 & 0.31 & 40,727 \\
- & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,727 \\
+\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,734 \\
+ & No cause & 0.11 & 0.00 & 0.31 & 40,734 \\
+ & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,734 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,727 \\
- & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,727 \\
- & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,727 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,734 \\
+ & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,734 \\
+ & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,734 \\
+ & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,734 \\
 \cline{1-6}
-\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
- & Case dismised & 0.29 & 0.00 & 0.45 & 40,727 \\
- & Case duration & 57.81 & 21.00 & 78.29 & 39,087 \\
- & Case heard & 0.06 & 0.00 & 0.23 & 40,727 \\
- & Case mediated & 0.41 & 0.00 & 0.49 & 40,727 \\
- & Money judgment & 1,890.34 & 0.00 & 5,279.49 & 40,727 \\
+\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,734 \\
+ & Case dismised & 0.29 & 0.00 & 0.45 & 40,734 \\
+ & Case duration & 57.81 & 21.00 & 78.28 & 39,094 \\
+ & Case heard & 0.06 & 0.00 & 0.23 & 40,734 \\
+ & Case mediated & 0.41 & 0.00 & 0.49 & 40,734 \\
+ & Money judgment & 1,890.02 & 0.00 & 5,279.08 & 40,734 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 377,384.02 & 305,144.00 & 316,645.29 & 10,096 \\
- & One year after filing date & 421,601.75 & 347,550.00 & 344,328.86 & 10,443 \\
- & Three years after filing date & 501,611.80 & 414,600.00 & 780,467.01 & 5,894 \\
- & Two years after filing date & 477,948.08 & 393,900.00 & 457,694.83 & 9,175 \\
+\multirow[c]{14}{4cm}{\textit{Panel F: Post-treatment Outcomes}} & Zestimate one year after filing date & 421,590.21 & 347,444.00 & 344,333.24 & 10,443 \\
+ & Zestimate two years after filing date & 477,931.84 & 393,800.00 & 457,699.06 & 9,175 \\
+ & any_crime_140m_1_years_relative_to_treatment & 1.41 & 0.00 & 4.90 & 40,734 \\
+ & any_crime_140m_2_years_relative_to_treatment & 1.50 & 0.00 & 5.04 & 35,684 \\
+ & any_crime_200m_1_years_relative_to_treatment & 2.65 & 0.00 & 8.37 & 40,734 \\
+ & any_crime_200m_2_years_relative_to_treatment & 2.84 & 0.00 & 8.74 & 35,684 \\
+ & any_crime_60m_1_years_relative_to_treatment & 0.31 & 0.00 & 1.41 & 40,734 \\
+ & any_crime_60m_1_years_relative_to_treatment & 0.31 & 0.00 & 1.41 & 40,734 \\
+ & any_crime_60m_2_years_relative_to_treatment & 0.34 & 0.00 & 1.44 & 35,684 \\
+ & any_crime_60m_2_years_relative_to_treatment & 0.34 & 0.00 & 1.44 & 35,684 \\
+ & any_crime_90m_1_years_relative_to_treatment & 0.66 & 0.00 & 2.50 & 40,734 \\
+ & any_crime_90m_1_years_relative_to_treatment & 0.66 & 0.00 & 2.50 & 40,734 \\
+ & any_crime_90m_2_years_relative_to_treatment & 0.69 & 0.00 & 2.53 & 35,684 \\
+ & any_crime_90m_2_years_relative_to_treatment & 0.69 & 0.00 & 2.53 & 35,684 \\
 \cline{1-6}

### 2023-03-08 output/crime_140m/tables/balance_table.tex
ra models

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_140m & 9.70 & 0.56 & 0.31 & 1.64 & 0.13 \\
 & pre_treatment_change_in_any_crime_140m & -1.03 & 0.02 & 0.95 & -0.12 & 0.86 \\
\cline{1-7}
\multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
 & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,479.47 & 0.00 \\
 & Median household income (2016) & 48,035.65 & 1,777.65 & 0.19 & 3,359.04 & 0.19 \\
 & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 511.85 & 0.72 \\
 & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 177.05 & 0.03 \\
 & Share white (2010) & 0.31 & 0.02 & 0.10 & 0.09 & 0.00 \\
 & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel C}} & No cause & 0.05 & -0.05 & 0.00 & -0.11 & 0.00 \\
 & Non-payment of rent & 0.78 & 0.07 & 0.00 & 0.16 & 0.00 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel D}} & Plaintiff has an attorney & 0.88 & 0.07 & 0.00 & 0.21 & 0.00 \\
 & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-03-08 output/crime_200m/tables/pre_treatment_covariate_tests.tex
ra models

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Any Crime Incidents Within 200m, Dec. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_200m & 0.00 & 0.36 \\
 & pre_treatment_change_in_any_crime_200m & 0.00 & 0.62 \\
\cline{1-4}
\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.24 \\
 & Jobs per square mile (2010) & 0.00 & 0.16 \\
 & Median household income (2016) & 0.06 & 0.19 \\
 & Share below poverty line & 0.01 & 0.14 \\
 & Population density (2010) & 0.00 & 0.06 \\
 & Median two bedroom rent (2015) & 0.00 & 0.50 \\
 & Share white (2010) & 0.17 & 0.10 \\
 & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.17 & 0.48 \\
 & No cause & 0.01 & 0.00 \\
 & Non-payment of rent & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.53 & 0.00 \\
 & Plaintiff has an attorney & 0.81 & 0.00 \\
 & Defendant is an entity & 0.53 & 0.00 \\
 & Plaintiff is an entity & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-03-08 output/crime_90m/tables/balance_table.tex
ra models

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_90m & 4.27 & 0.44 & 0.09 & 0.64 & 0.20 \\
 & pre_treatment_change_in_any_crime_90m & -0.38 & -0.10 & 0.61 & -0.09 & 0.80 \\
\cline{1-7}
\multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
 & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,507.90 & 0.00 \\
 & Median household income (2016) & 48,035.65 & 1,777.65 & 0.19 & 3,395.82 & 0.19 \\
 & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 473.98 & 0.74 \\
 & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 176.71 & 0.03 \\
 & Share white (2010) & 0.31 & 0.02 & 0.10 & 0.09 & 0.00 \\
 & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel C}} & For cause & 0.17 & -0.01 & 0.48 & -0.03 & 0.37 \\
 & Non-payment of rent & 0.78 & 0.07 & 0.00 & 0.16 & 0.00 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel D}} & Plaintiff has an attorney & 0.88 & 0.07 & 0.00 & 0.21 & 0.00 \\
 & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-03-08 src/02_analysis/analysis_utilities.py

@@ -170,7 +170,8 @@ def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.D
     treatment_means = treatment_means.loc[pre_treatment_panels, :]
     # Do not include rows corresponding to other outcomes in the covariate exploration table.
     outcomes = ['zestimate', 'any_crime_60m', 'any_crime_90m',
-                'any_crime_140m', 'any_crime_200m']  # Create list of all outcomes.
+                'any_crime_140m', 'any_crime_200m',
+                'any_crime_280m', 'any_crime_400m']  # Create list of all outcomes.
     outcomes.remove(analysis)  # Remove the one which is being currently studied.
     unneeded_outcomes = outcomes
     for unneeded_outcome in unneeded_outcomes:  # For each outcome not currently being studied...
@@ -284,7 +285,8 @@ def select_controls(df: pd.DataFrame, analysis: str, output_directory: str):
 
     # Do not include rows corresponding to other outcomes in the covariate exploration table.
     outcomes = ['zestimate', 'any_crime_60m', 'any_crime_90m',
-                'any_crime_140m', 'any_crime_200m']  # Create list of all outcomes.
+                'any_crime_140m', 'any_crime_200m',
+                'any_crime_280m', 'any_crime_400m']  # Create list of all outcomes.
     outcomes.remove(analysis)  # Remove the one which is being currently studied.
     unneeded_outcomes = outcomes
     for unneeded_outcome in unneeded_outcomes:  # For each outcome not currently being studied...
@@ -440,7 +442,8 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     """
     # Panel A: Pre-treatment Outcomes
     outcomes = ['zestimate', 'any_crime_60m', 'any_crime_90m',
-                'any_crime_140m', 'any_crime_200m']  # Create list of all outcomes.
+                'any_crime_140m', 'any_crime_200m',
+                'any_crime_280m', 'any_crime_400m']  # Create list of all outcomes.
     panel_A_columns = []
     for outcome in outcomes:
         # Create alias column for Patchy.

### 2023-03-08 output/crime_140m/tables/pre_treatment_covariate_tests.tex

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Any Crime Incidents Within 140m, Dec. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_140m & 0.00 & 0.31 \\
 & pre_treatment_change_in_any_crime_140m & 0.00 & 0.95 \\
\cline{1-4}
\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.24 \\
 & Jobs per square mile (2010) & 0.00 & 0.16 \\
 & Median household income (2016) & 0.00 & 0.19 \\
 & Share below poverty line & 0.09 & 0.14 \\
 & Population density (2010) & 0.00 & 0.06 \\
 & Median two bedroom rent (2015) & 0.00 & 0.50 \\
 & Share white (2010) & 0.00 & 0.10 \\
 & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.18 & 0.48 \\
 & No cause & 0.03 & 0.00 \\
 & Non-payment of rent & 0.01 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 \\
 & Plaintiff has an attorney & 0.00 & 0.00 \\
 & Defendant is an entity & 0.86 & 0.00 \\
 & Plaintiff is an entity & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-03-08 output/crime_200m/tables/balance_table.tex

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_200m & 18.26 & 0.79 & 0.36 & 0.62 & 0.71 \\
 & pre_treatment_change_in_any_crime_200m & -2.30 & 0.26 & 0.62 & 0.75 & 0.43 \\
\cline{1-7}
\multirow[c]{6}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
 & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,395.48 & 0.00 \\
 & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.85 \\
 & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 531.25 & 0.71 \\
 & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 176.95 & 0.03 \\
 & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel C}} & No cause & 0.05 & -0.05 & 0.00 & -0.11 & 0.00 \\
 & Non-payment of rent & 0.78 & 0.07 & 0.00 & 0.16 & 0.00 \\
\cline{1-7}
\textit{Panel D} & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-03-08 output/crime_280m/tables/balance_table.tex

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_280m & 33.62 & 1.43 & 0.30 & 0.47 & 0.86 \\
 & pre_treatment_change_in_any_crime_280m & -4.88 & -0.58 & 0.42 & 0.36 & 0.79 \\
\cline{1-7}
\multirow[c]{6}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
 & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,397.32 & 0.00 \\
 & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.85 \\
 & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 497.91 & 0.72 \\
 & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 177.21 & 0.03 \\
 & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
\cline{1-7}
\textit{Panel C} & No cause & 0.05 & -0.05 & 0.00 & -0.11 & 0.00 \\
\cline{1-7}
\textit{Panel D} & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-03-08 output/crime_280m/tables/pre_treatment_covariate_tests.tex

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Any Crime Incidents Within 280m, Dec. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_280m & 0.00 & 0.30 \\
 & pre_treatment_change_in_any_crime_280m & 0.00 & 0.42 \\
\cline{1-4}
\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.24 \\
 & Jobs per square mile (2010) & 0.00 & 0.16 \\
 & Median household income (2016) & 0.10 & 0.19 \\
 & Share below poverty line & 0.00 & 0.14 \\
 & Population density (2010) & 0.00 & 0.06 \\
 & Median two bedroom rent (2015) & 0.00 & 0.50 \\
 & Share white (2010) & 0.64 & 0.10 \\
 & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.54 & 0.48 \\
 & No cause & 0.04 & 0.00 \\
 & Non-payment of rent & 0.06 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.33 & 0.00 \\
 & Plaintiff has an attorney & 0.93 & 0.00 \\
 & Defendant is an entity & 0.18 & 0.00 \\
 & Plaintiff is an entity & 0.01 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-03-08 output/crime_60m/tables/balance_table.tex

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & twenty_seventeen_any_crime_60m & 2.03 & -0.04 & 0.83 & 0.12 & 0.66 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
 & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,355.85 & 0.00 \\
 & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 533.46 & 0.71 \\
 & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 174.33 & 0.03 \\
 & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
\cline{1-7}
\textit{Panel C} & Non-payment of rent & 0.78 & 0.07 & 0.00 & 0.16 & 0.00 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel D}} & Defendant has an attorney & 0.06 & -0.18 & 0.00 & -0.23 & 0.00 \\
 & Plaintiff has an attorney & 0.88 & 0.07 & 0.00 & 0.21 & 0.00 \\
 & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-03-08 output/crime_60m/tables/pre_treatment_covariate_tests.tex

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Any Crime Incidents Within 60m, Dec. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_60m & 0.00 & 0.83 \\
 & pre_treatment_change_in_any_crime_60m & 0.72 & 0.19 \\
\cline{1-4}
\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.02 & 0.24 \\
 & Jobs per square mile (2010) & 0.00 & 0.16 \\
 & Median household income (2016) & 0.13 & 0.19 \\
 & Share below poverty line & 0.33 & 0.14 \\
 & Population density (2010) & 0.00 & 0.06 \\
 & Median two bedroom rent (2015) & 0.00 & 0.50 \\
 & Share white (2010) & 0.47 & 0.10 \\
 & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.24 & 0.48 \\
 & No cause & 0.08 & 0.00 \\
 & Non-payment of rent & 0.03 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.04 & 0.00 \\
 & Plaintiff has an attorney & 0.00 & 0.00 \\
 & Defendant is an entity & 0.40 & 0.00 \\
 & Plaintiff is an entity & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-03-08 output/crime_90m/tables/pre_treatment_covariate_tests.tex

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Any Crime Incidents Within 90m, Dec. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_90m & 0.00 & 0.09 \\
 & pre_treatment_change_in_any_crime_90m & 0.03 & 0.61 \\
\cline{1-4}
\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.24 \\
 & Jobs per square mile (2010) & 0.00 & 0.16 \\
 & Median household income (2016) & 0.00 & 0.19 \\
 & Share below poverty line & 0.67 & 0.14 \\
 & Population density (2010) & 0.00 & 0.06 \\
 & Median two bedroom rent (2015) & 0.00 & 0.50 \\
 & Share white (2010) & 0.02 & 0.10 \\
 & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.05 & 0.48 \\
 & No cause & 0.08 & 0.00 \\
 & Non-payment of rent & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.08 & 0.00 \\
 & Plaintiff has an attorney & 0.00 & 0.00 \\
 & Defendant is an entity & 0.32 & 0.00 \\
 & Plaintiff is an entity & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-03-12 output/crime_140m/tables/balance_table.tex
Removed adjusted crime count method

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_140m & 9.70 & 0.56 & 0.31 & 1.64 & 0.13 \\
- & pre_treatment_change_in_any_crime_140m & -1.03 & 0.02 & 0.95 & -0.12 & 0.86 \\
+\textit{Panel A} & twenty_seventeen_any_crime_140m & 0.93 & -0.01 & 0.91 & 0.00 & 0.99 \\
 \cline{1-7}
 \multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
- & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,479.47 & 0.00 \\
- & Median household income (2016) & 48,035.65 & 1,777.65 & 0.19 & 3,359.04 & 0.19 \\
- & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 511.85 & 0.72 \\
- & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 177.05 & 0.03 \\
+ & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,396.49 & 0.00 \\
+ & Median household income (2016) & 48,035.65 & 1,777.65 & 0.19 & 3,321.13 & 0.20 \\
+ & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.85 \\
+ & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 178.07 & 0.03 \\
  & Share white (2010) & 0.31 & 0.02 & 0.10 & 0.09 & 0.00 \\
@@
 \cline{1-7}
-\multirow[c]{2}{3cm}{\textit{Panel C}} & No cause & 0.05 & -0.05 & 0.00 & -0.11 & 0.00 \\
+\multirow[c]{2}{3cm}{\textit{Panel C}} & For cause & 0.17 & -0.01 & 0.48 & -0.03 & 0.35 \\
  & Non-payment of rent & 0.78 & 0.07 & 0.00 & 0.16 & 0.00 \\

### 2023-03-12 output/crime_140m/tables/pre_treatment_covariate_tests.tex
Removed adjusted crime count method

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_140m & 0.00 & 0.31 \\
- & pre_treatment_change_in_any_crime_140m & 0.00 & 0.95 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_140m & 0.00 & 0.91 \\
+ & pre_treatment_change_in_any_crime_140m & 0.14 & 0.45 \\
 \cline{1-4}
@@
  & Median household income (2016) & 0.00 & 0.19 \\
- & Share below poverty line & 0.09 & 0.14 \\
- & Population density (2010) & 0.00 & 0.06 \\
+ & Share below poverty line & 0.00 & 0.14 \\
+ & Population density (2010) & 0.07 & 0.06 \\
  & Median two bedroom rent (2015) & 0.00 & 0.50 \\
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.18 & 0.48 \\
- & No cause & 0.03 & 0.00 \\
- & Non-payment of rent & 0.01 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.04 & 0.48 \\
+ & No cause & 0.49 & 0.00 \\
+ & Non-payment of rent & 0.02 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.92 & 0.00 \\
  & Plaintiff has an attorney & 0.00 & 0.00 \\
- & Defendant is an entity & 0.86 & 0.00 \\
+ & Defendant is an entity & 0.30 & 0.00 \\
  & Plaintiff is an entity & 0.00 & 0.00 \\

### 2023-03-12 output/crime_200m/tables/balance_table.tex
Removed adjusted crime count method

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_200m & 18.26 & 0.79 & 0.36 & 0.62 & 0.71 \\
- & pre_treatment_change_in_any_crime_200m & -2.30 & 0.26 & 0.62 & 0.75 & 0.43 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_200m & 18.17 & 0.31 & 0.72 & 0.57 & 0.73 \\
+ & pre_treatment_change_in_any_crime_200m & 0.16 & 0.84 & 0.07 & 0.32 & 0.72 \\
 \cline{1-7}
-\multirow[c]{6}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
- & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,395.48 & 0.00 \\
- & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.85 \\
- & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 531.25 & 0.71 \\
- & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 176.95 & 0.03 \\
- & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
+\multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
+ & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,528.16 & 0.00 \\
+ & Median household income (2016) & 48,035.65 & 1,777.65 & 0.19 & 3,418.57 & 0.18 \\
+ & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.87 \\
+ & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 518.02 & 0.71 \\
+ & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 176.55 & 0.03 \\
+ & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.01 \\
 \cline{1-7}
-\multirow[c]{2}{3cm}{\textit{Panel C}} & No cause & 0.05 & -0.05 & 0.00 & -0.11 & 0.00 \\
- & Non-payment of rent & 0.78 & 0.07 & 0.00 & 0.16 & 0.00 \\
+\textit{Panel C} & No cause & 0.05 & -0.05 & 0.00 & -0.11 & 0.00 \\
 \cline{1-7}
-\textit{Panel D} & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel D}} & Plaintiff has an attorney & 0.88 & 0.07 & 0.00 & 0.20 & 0.00 \\
+ & Defendant is an entity & 0.01 & -0.04 & 0.00 & 0.01 & 0.23 \\
+ & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
 \cline{1-7}

### 2023-03-12 output/crime_200m/tables/pre_treatment_covariate_tests.tex
Removed adjusted crime count method

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_200m & 0.00 & 0.36 \\
- & pre_treatment_change_in_any_crime_200m & 0.00 & 0.62 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_200m & 0.00 & 0.72 \\
+ & pre_treatment_change_in_any_crime_200m & 0.00 & 0.07 \\
 \cline{1-4}
@@
  & Jobs per square mile (2010) & 0.00 & 0.16 \\
- & Median household income (2016) & 0.06 & 0.19 \\
- & Share below poverty line & 0.01 & 0.14 \\
+ & Median household income (2016) & 0.00 & 0.19 \\
+ & Share below poverty line & 0.00 & 0.14 \\
  & Population density (2010) & 0.00 & 0.06 \\
  & Median two bedroom rent (2015) & 0.00 & 0.50 \\
- & Share white (2010) & 0.17 & 0.10 \\
+ & Share white (2010) & 0.13 & 0.10 \\
  & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.17 & 0.48 \\
- & No cause & 0.01 & 0.00 \\
- & Non-payment of rent & 0.00 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.94 & 0.48 \\
+ & No cause & 0.00 & 0.00 \\
+ & Non-payment of rent & 0.08 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.53 & 0.00 \\
- & Plaintiff has an attorney & 0.81 & 0.00 \\
- & Defendant is an entity & 0.53 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.80 & 0.00 \\
+ & Plaintiff has an attorney & 0.00 & 0.00 \\
+ & Defendant is an entity & 0.05 & 0.00 \\
  & Plaintiff is an entity & 0.00 & 0.00 \\

### 2023-03-12 output/crime_280m/tables/balance_table.tex
Removed adjusted crime count method

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_280m & 33.62 & 1.43 & 0.30 & 0.47 & 0.86 \\
- & pre_treatment_change_in_any_crime_280m & -4.88 & -0.58 & 0.42 & 0.36 & 0.79 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_280m & 33.56 & 0.76 & 0.57 & 0.72 & 0.77 \\
+ & pre_treatment_change_in_any_crime_280m & 0.54 & 1.55 & 0.01 & 0.33 & 0.78 \\
 \cline{1-7}
-\multirow[c]{6}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
- & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,397.32 & 0.00 \\
- & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.85 \\
- & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 497.91 & 0.72 \\
- & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 177.21 & 0.03 \\
+\multirow[c]{7}{3cm}{\textit{Panel B}} & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,430.78 & 0.00 \\
+ & Median household income (2016) & 48,035.65 & 1,777.65 & 0.19 & 3,350.72 & 0.19 \\
+ & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.86 \\
+ & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 516.07 & 0.71 \\
+ & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 175.33 & 0.03 \\
+ & Share white (2010) & 0.31 & 0.02 & 0.10 & 0.09 & 0.00 \\
  & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\

### 2023-03-12 output/crime_280m/tables/pre_treatment_covariate_tests.tex
Removed adjusted crime count method

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_280m & 0.00 & 0.30 \\
- & pre_treatment_change_in_any_crime_280m & 0.00 & 0.42 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_280m & 0.00 & 0.57 \\
+ & pre_treatment_change_in_any_crime_280m & 0.00 & 0.01 \\
 \cline{1-4}
-\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.24 \\
+\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.10 & 0.24 \\
  & Jobs per square mile (2010) & 0.00 & 0.16 \\
- & Median household income (2016) & 0.10 & 0.19 \\
+ & Median household income (2016) & 0.00 & 0.19 \\
  & Share below poverty line & 0.00 & 0.14 \\
@@
  & Median two bedroom rent (2015) & 0.00 & 0.50 \\
- & Share white (2010) & 0.64 & 0.10 \\
+ & Share white (2010) & 0.00 & 0.10 \\
  & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.54 & 0.48 \\
- & No cause & 0.04 & 0.00 \\
- & Non-payment of rent & 0.06 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.72 & 0.48 \\
+ & No cause & 0.00 & 0.00 \\
+ & Non-payment of rent & 0.17 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.33 & 0.00 \\
- & Plaintiff has an attorney & 0.93 & 0.00 \\
- & Defendant is an entity & 0.18 & 0.00 \\
- & Plaintiff is an entity & 0.01 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.92 & 0.00 \\
+ & Plaintiff has an attorney & 0.08 & 0.00 \\
+ & Defendant is an entity & 0.39 & 0.00 \\
+ & Plaintiff is an entity & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-03-12 output/crime_60m/tables/balance_table.tex
Removed adjusted crime count method

@@
 \midrule
-\textit{Panel A} & twenty_seventeen_any_crime_60m & 2.03 & -0.04 & 0.83 & 0.12 & 0.66 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_60m & 0.47 & 0.03 & 0.49 & -0.00 & 0.95 \\
+ & pre_treatment_change_in_any_crime_60m & -0.03 & 0.01 & 0.79 & 0.01 & 0.87 \\
 \cline{1-7}
-\multirow[c]{5}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
- & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,355.85 & 0.00 \\
- & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 533.46 & 0.71 \\
- & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 174.33 & 0.03 \\
- & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
+\multirow[c]{3}{3cm}{\textit{Panel B}} & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 903.79 & 0.69 \\
+ & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & -271.38 & 0.68 \\
+ & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & -0.00 & 0.42 \\
 \cline{1-7}
-\textit{Panel C} & Non-payment of rent & 0.78 & 0.07 & 0.00 & 0.16 & 0.00 \\
-\cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel D}} & Defendant has an attorney & 0.06 & -0.18 & 0.00 & -0.23 & 0.00 \\
- & Plaintiff has an attorney & 0.88 & 0.07 & 0.00 & 0.21 & 0.00 \\
- & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
+\multirow[c]{2}{3cm}{\textit{Panel D}} & Plaintiff has an attorney & 0.88 & 0.07 & 0.00 & -0.00 & 0.93 \\
+ & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.02 & 0.27 \\
 \cline{1-7}

### 2023-03-12 output/crime_60m/tables/pre_treatment_covariate_tests.tex
Removed adjusted crime count method

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_60m & 0.00 & 0.83 \\
- & pre_treatment_change_in_any_crime_60m & 0.72 & 0.19 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_60m & 0.00 & 0.49 \\
+ & pre_treatment_change_in_any_crime_60m & 0.00 & 0.79 \\
 \cline{1-4}
-\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.02 & 0.24 \\
+\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.94 & 0.24 \\
  & Jobs per square mile (2010) & 0.00 & 0.16 \\
- & Median household income (2016) & 0.13 & 0.19 \\
- & Share below poverty line & 0.33 & 0.14 \\
- & Population density (2010) & 0.00 & 0.06 \\
- & Median two bedroom rent (2015) & 0.00 & 0.50 \\
- & Share white (2010) & 0.47 & 0.10 \\
- & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
+ & Median household income (2016) & 0.09 & 0.19 \\
+ & Share below poverty line & 0.96 & 0.14 \\
+ & Population density (2010) & 0.02 & 0.06 \\
+ & Median two bedroom rent (2015) & 0.72 & 0.50 \\
+ & Share white (2010) & 0.88 & 0.10 \\
+ & Share with commute $<$15 minutes (2010) & 0.01 & 0.23 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.24 & 0.48 \\
- & No cause & 0.08 & 0.00 \\
- & Non-payment of rent & 0.03 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.22 & 0.48 \\
+ & No cause & 0.70 & 0.00 \\
+ & Non-payment of rent & 0.08 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.04 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.06 & 0.00 \\
  & Plaintiff has an attorney & 0.00 & 0.00 \\
- & Defendant is an entity & 0.40 & 0.00 \\
- & Plaintiff is an entity & 0.00 & 0.00 \\
+ & Defendant is an entity & 0.84 & 0.00 \\
+ & Plaintiff is an entity & 0.01 & 0.00 \\
 \cline{1-4}

### 2023-03-12 output/crime_90m/tables/balance_table.tex
Removed adjusted crime count method

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_90m & 4.27 & 0.44 & 0.09 & 0.64 & 0.20 \\
- & pre_treatment_change_in_any_crime_90m & -0.38 & -0.10 & 0.61 & -0.09 & 0.80 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_90m & 0.68 & 0.02 & 0.77 & -0.12 & 0.26 \\
+ & pre_treatment_change_in_any_crime_90m & -0.02 & 0.01 & 0.91 & 0.03 & 0.76 \\
 \cline{1-7}
-\multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
- & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,507.90 & 0.00 \\
- & Median household income (2016) & 48,035.65 & 1,777.65 & 0.19 & 3,395.82 & 0.19 \\
- & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 473.98 & 0.74 \\
- & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 176.71 & 0.03 \\
+\multirow[c]{8}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
+ & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,393.10 & 0.00 \\
+ & Median household income (2016) & 48,035.65 & 1,777.65 & 0.19 & 3,315.55 & 0.20 \\
+ & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.85 \\
+ & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 537.03 & 0.70 \\
+ & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 177.10 & 0.03 \\
  & Share white (2010) & 0.31 & 0.02 & 0.10 & 0.09 & 0.00 \\
  & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
-\cline{1-7}
-\multirow[c]{2}{3cm}{\textit{Panel C}} & For cause & 0.17 & -0.01 & 0.48 & -0.03 & 0.37 \\
- & Non-payment of rent & 0.78 & 0.07 & 0.00 & 0.16 & 0.00 \\
 \cline{1-7}

### 2023-03-12 output/crime_90m/tables/pre_treatment_covariate_tests.tex
Removed adjusted crime count method

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_90m & 0.00 & 0.09 \\
- & pre_treatment_change_in_any_crime_90m & 0.03 & 0.61 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_90m & 0.00 & 0.77 \\
+ & pre_treatment_change_in_any_crime_90m & 0.00 & 0.91 \\
 \cline{1-4}
@@
  & Median household income (2016) & 0.00 & 0.19 \\
- & Share below poverty line & 0.67 & 0.14 \\
+ & Share below poverty line & 0.04 & 0.14 \\
  & Population density (2010) & 0.00 & 0.06 \\
  & Median two bedroom rent (2015) & 0.00 & 0.50 \\
- & Share white (2010) & 0.02 & 0.10 \\
+ & Share white (2010) & 0.00 & 0.10 \\
  & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.05 & 0.48 \\
- & No cause & 0.08 & 0.00 \\
- & Non-payment of rent & 0.00 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.15 & 0.48 \\
+ & No cause & 0.65 & 0.00 \\
+ & Non-payment of rent & 0.07 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.08 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.32 & 0.00 \\
  & Plaintiff has an attorney & 0.00 & 0.00 \\
- & Defendant is an entity & 0.32 & 0.00 \\
+ & Defendant is an entity & 0.59 & 0.00 \\
  & Plaintiff is an entity & 0.00 & 0.00 \\

### 2023-03-13 output/crime_140m/tables/balance_table.tex
updated analysis utilities to accomodate new outcomes

@@
 \midrule
-\textit{Panel A} & twenty_seventeen_any_crime_140m & 0.93 & -0.01 & 0.91 & 0.00 & 0.99 \\
+\textit{Panel A} & twenty_seventeen_group_1_crimes_200m & 1.38 & 0.09 & 0.35 & 0.02 & 0.89 \\
 \cline{1-7}
-\multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
- & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,396.49 & 0.00 \\
- & Median household income (2016) & 48,035.65 & 1,777.65 & 0.19 & 3,321.13 & 0.20 \\
- & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.85 \\
- & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 178.07 & 0.03 \\
- & Share white (2010) & 0.31 & 0.02 & 0.10 & 0.09 & 0.00 \\
- & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
+\multirow[c]{7}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.01 & 0.24 & 0.05 & 0.01 \\
+ & job_density_2013 & 16,069.14 & 3,197.93 & 0.16 & 5,413.87 & 0.16 \\
+ & poor_share2010 & 0.27 & 0.01 & 0.14 & -0.01 & 0.33 \\
+ & popdensity2010 & 23,086.04 & 1,373.15 & 0.06 & 483.47 & 0.68 \\
+ & rent_twobed2015 & 1,339.99 & -29.55 & 0.50 & 30.88 & 0.67 \\
+ & share_white2010 & 0.31 & 0.02 & 0.10 & 0.05 & 0.04 \\
+ & traveltime15_2010 & 0.16 & 0.01 & 0.23 & 0.01 & 0.20 \\
 \cline{1-7}
-\multirow[c]{2}{3cm}{\textit{Panel C}} & For cause & 0.17 & -0.01 & 0.48 & -0.03 & 0.35 \\
- & Non-payment of rent & 0.78 & 0.07 & 0.00 & 0.16 & 0.00 \\
+\textit{Panel C} & no_cause & 0.05 & -0.05 & 0.00 & -0.08 & 0.00 \\
 \cline{1-7}
-\multirow[c]{2}{3cm}{\textit{Panel D}} & Plaintiff has an attorney & 0.88 & 0.07 & 0.00 & 0.21 & 0.00 \\
- & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & 0.07 & 0.00 & 0.11 & 0.00 \\
+ & isEntityD & 0.01 & -0.04 & 0.00 & 0.01 & 0.17 \\
+ & isEntityP & 0.81 & 0.10 & 0.00 & 0.12 & 0.00 \\
 \cline{1-7}

### 2023-03-13 output/crime_140m/tables/pre_treatment_covariate_tests.tex
updated analysis utilities to accomodate new outcomes

@@
 \\
- &  & Any Crime Incidents Within 140m, Dec. 2022 & Plaintiff Victory \\
+ &  & Assault-Related Crime Incidents Within 200m, Oct. 2022 & Plaintiff Victory \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_140m & 0.00 & 0.91 \\
- & pre_treatment_change_in_any_crime_140m & 0.14 & 0.45 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_1_crimes_200m & 0.00 & 0.35 \\
+ & pre_treatment_change_in_group_1_crimes_200m & 0.90 & 0.96 \\
 \cline{1-4}
-\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.24 \\
- & Jobs per square mile (2010) & 0.00 & 0.16 \\
- & Median household income (2016) & 0.00 & 0.19 \\
- & Share below poverty line & 0.00 & 0.14 \\
- & Population density (2010) & 0.07 & 0.06 \\
- & Median two bedroom rent (2015) & 0.00 & 0.50 \\
- & Share white (2010) & 0.00 & 0.10 \\
- & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
+\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.24 \\
+ & job_density_2013 & 0.00 & 0.16 \\
+ & med_hhinc2016 & 0.59 & 0.19 \\
+ & poor_share2010 & 0.00 & 0.14 \\
+ & popdensity2010 & 0.00 & 0.06 \\
+ & rent_twobed2015 & 0.00 & 0.50 \\
+ & share_white2010 & 0.00 & 0.10 \\
+ & traveltime15_2010 & 0.00 & 0.23 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.04 & 0.48 \\
- & No cause & 0.49 & 0.00 \\
- & Non-payment of rent & 0.02 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.92 & 0.48 \\
+ & no_cause & 0.00 & 0.00 \\
+ & non_payment & 0.06 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.92 & 0.00 \\
- & Plaintiff has an attorney & 0.00 & 0.00 \\
- & Defendant is an entity & 0.30 & 0.00 \\
- & Plaintiff is an entity & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.81 & 0.00 \\
+ & hasAttyP & 0.02 & 0.00 \\
+ & isEntityD & 0.00 & 0.00 \\
+ & isEntityP & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-03-13 output/crime_200m/tables/balance_table.tex
updated analysis utilities to accomodate new outcomes

--- 2023-03-08 output/crime_200m/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_200m & 18.26 & 0.79 & 0.36 & 0.62 & 0.71 \\
- & pre_treatment_change_in_any_crime_200m & -2.30 & 0.26 & 0.62 & 0.75 & 0.43 \\
+\textit{Panel A} & twenty_seventeen_group_0_crimes_50m & 1.43 & -0.20 & 0.16 & -0.16 & 0.26 \\
 \cline{1-7}
-\multirow[c]{6}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
- & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,395.48 & 0.00 \\
- & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.85 \\
- & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 531.25 & 0.71 \\
- & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 176.95 & 0.03 \\
- & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
+\multirow[c]{3}{3cm}{\textit{Panel B}} & job_density_2013 & 16,069.14 & 3,197.93 & 0.16 & 843.09 & 0.71 \\
+ & popdensity2010 & 23,086.04 & 1,373.15 & 0.06 & -365.58 & 0.58 \\
+ & traveltime15_2010 & 0.16 & 0.01 & 0.23 & -0.00 & 0.34 \\
 \cline{1-7}
-\multirow[c]{2}{3cm}{\textit{Panel C}} & No cause & 0.05 & -0.05 & 0.00 & -0.11 & 0.00 \\
- & Non-payment of rent & 0.78 & 0.07 & 0.00 & 0.16 & 0.00 \\
+\textit{Panel C} & non_payment & 0.78 & 0.07 & 0.00 & -0.00 & 0.92 \\
 \cline{1-7}
-\textit{Panel D} & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
+\textit{Panel D} & isEntityP & 0.81 & 0.10 & 0.00 & 0.01 & 0.40 \\
 \cline{1-7}

### 2023-03-13 output/crime_200m/tables/pre_treatment_covariate_tests.tex
updated analysis utilities to accomodate new outcomes

@@
 \\
- &  & Any Crime Incidents Within 200m, Dec. 2022 & Plaintiff Victory \\
+ &  & Crime Incidents Within 50m, Oct. 2022 & Plaintiff Victory \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_200m & 0.00 & 0.72 \\
- & pre_treatment_change_in_any_crime_200m & 0.00 & 0.07 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_0_crimes_50m & 0.00 & 0.16 \\
+ & pre_treatment_change_in_group_0_crimes_50m & 0.22 & 0.06 \\
 \cline{1-4}
-\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.24 \\
- & Jobs per square mile (2010) & 0.00 & 0.16 \\
- & Median household income (2016) & 0.00 & 0.19 \\
- & Share below poverty line & 0.00 & 0.14 \\
- & Population density (2010) & 0.00 & 0.06 \\
- & Median two bedroom rent (2015) & 0.00 & 0.50 \\
- & Share white (2010) & 0.13 & 0.10 \\
- & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
+\multirow[c]{7}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.09 & 0.24 \\
+ & job_density_2013 & 0.00 & 0.16 \\
+ & med_hhinc2016 & 0.73 & 0.19 \\
+ & poor_share2010 & 0.50 & 0.14 \\
+ & popdensity2010 & 0.04 & 0.06 \\
+ & share_white2010 & 0.96 & 0.10 \\
+ & traveltime15_2010 & 0.00 & 0.23 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.94 & 0.48 \\
- & No cause & 0.00 & 0.00 \\
- & Non-payment of rent & 0.08 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.13 & 0.48 \\
+ & no_cause & 0.24 & 0.00 \\
+ & non_payment & 0.03 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.80 & 0.00 \\
- & Plaintiff has an attorney & 0.00 & 0.00 \\
- & Defendant is an entity & 0.05 & 0.00 \\
- & Plaintiff is an entity & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.34 & 0.00 \\
+ & hasAttyP & 0.09 & 0.00 \\
+ & isEntityD & 0.38 & 0.00 \\
+ & isEntityP & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-03-13 output/crime_90m/tables/balance_table.tex
updated analysis utilities to accomodate new outcomes

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_90m & 0.68 & 0.02 & 0.77 & -0.12 & 0.26 \\
- & pre_treatment_change_in_any_crime_90m & -0.02 & 0.01 & 0.91 & 0.03 & 0.76 \\
+\textit{Panel A} & twenty_seventeen_group_1_crimes_150m & 0.86 & 0.14 & 0.05 & 0.03 & 0.68 \\
 \cline{1-7}
-\multirow[c]{8}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
- & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,393.10 & 0.00 \\
- & Median household income (2016) & 48,035.65 & 1,777.65 & 0.19 & 3,315.55 & 0.20 \\
- & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.85 \\
- & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 537.03 & 0.70 \\
- & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 177.10 & 0.03 \\
- & Share white (2010) & 0.31 & 0.02 & 0.10 & 0.09 & 0.00 \\
- & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
+\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.01 & 0.24 & -0.01 & 0.60 \\
+ & poor_share2010 & 0.27 & 0.01 & 0.14 & -0.01 & 0.43 \\
+ & share_white2010 & 0.31 & 0.02 & 0.10 & -0.00 & 0.94 \\
+ & traveltime15_2010 & 0.16 & 0.01 & 0.23 & -0.00 & 0.44 \\
 \cline{1-7}
-\multirow[c]{2}{3cm}{\textit{Panel D}} & Plaintiff has an attorney & 0.88 & 0.07 & 0.00 & 0.21 & 0.00 \\
- & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
+\textit{Panel C} & non_payment & 0.78 & 0.07 & 0.00 & 0.00 & 0.99 \\
+\cline{1-7}
+\textit{Panel D} & isEntityP & 0.81 & 0.10 & 0.00 & 0.01 & 0.38 \\
 \cline{1-7}

### 2023-03-13 output/crime_90m/tables/pre_treatment_covariate_tests.tex
updated analysis utilities to accomodate new outcomes

@@
 \\
- &  & Any Crime Incidents Within 90m, Dec. 2022 & Plaintiff Victory \\
+ &  & Assault-Related Crime Incidents Within 150m, Oct. 2022 & Plaintiff Victory \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_90m & 0.00 & 0.77 \\
- & pre_treatment_change_in_any_crime_90m & 0.00 & 0.91 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_1_crimes_150m & 0.00 & 0.05 \\
+ & pre_treatment_change_in_group_1_crimes_150m & 0.40 & 0.45 \\
 \cline{1-4}
-\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.24 \\
- & Jobs per square mile (2010) & 0.00 & 0.16 \\
- & Median household income (2016) & 0.00 & 0.19 \\
- & Share below poverty line & 0.04 & 0.14 \\
- & Population density (2010) & 0.00 & 0.06 \\
- & Median two bedroom rent (2015) & 0.00 & 0.50 \\
- & Share white (2010) & 0.00 & 0.10 \\
- & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.24 \\
+ & med_hhinc2016 & 0.58 & 0.19 \\
+ & poor_share2010 & 0.00 & 0.14 \\
+ & share_white2010 & 0.00 & 0.10 \\
+ & traveltime15_2010 & 0.00 & 0.23 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.15 & 0.48 \\
- & No cause & 0.65 & 0.00 \\
- & Non-payment of rent & 0.07 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.31 & 0.48 \\
+ & no_cause & 0.08 & 0.00 \\
+ & non_payment & 0.04 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.32 & 0.00 \\
- & Plaintiff has an attorney & 0.00 & 0.00 \\
- & Defendant is an entity & 0.59 & 0.00 \\
- & Plaintiff is an entity & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.47 & 0.00 \\
+ & hasAttyP & 0.07 & 0.00 \\
+ & isEntityD & 0.80 & 0.00 \\
+ & isEntityP & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-03-13 src/02_analysis/analysis_utilities.py

@@ -2,28 +2,28 @@
 Functions useful for analysis.
 """
 from os.path import join
-
+from sklearn.preprocessing import StandardScaler
 import matplotlib.pyplot as plt
 import numpy as np
 import pandas as pd
 import statsmodels.formula.api as smf
 import figure_utilities
+from analysis_constants import Variables
 from differences.did.pscore_cal import pscore_mle
 from typing import List
 
 
 def generate_variable_names(analysis: str):
     if analysis == 'zestimate':
+        # For zestimate analysis, need to create column names for 2012-12 through 2022-12
         years = [str(year) for year in range(2013, 2023)]
         months = ["0" + str(month) for month in range(1, 10)] + [str(month) for month in range(10, 13)]
         value_vars = ["2012-12"] + [str(year) + "-" + str(month) for year in years for month in months]
         value_vars_zestimate = [value_var + "_zestimate" for value_var in value_vars]
         month_to_int_dictionary = {key: value + 1 for value, key in enumerate(value_vars)}
         int_to_month_dictionary = {key + 1: value for key, value in enumerate(value_vars)}
-
-        to_return = value_vars_zestimate
-    elif analysis == 'any_crime_60m':
-        # Store list of crime variable names and create dictionaries which map between month variable names to integers.
+        return value_vars_zestimate, month_to_int_dictionary, int_to_month_dictionary
+    elif 'crime' in analysis:
         years = [str(year) for year in range(2015, 2023)]
         months = ["0" + str(month) for month in range(1, 10)] + [str(month) for month in range(10, 13)]
         value_vars = [str(year) + "-" + str(month) for year in years for month in months]
@@ -32,91 +32,15 @@ def generate_variable_names(analysis: str):
         value_vars_crime = [value_var + f"_{analysis}" for value_var in value_vars]
         month_to_int_dictionary = {key: value + 1 for value, key in enumerate(value_vars)}
         int_to_month_dictionary = {key + 1: value for key, value in enumerate(value_vars)}
-
-        to_return = value_vars_crime
-    elif analysis == 'any_crime_90m':
-        # Store list of crime variable names and create dictionaries which map between month variable names to integers.
-        years = [str(year) for year in range(2015, 2023)]
-        months = ["0" + str(month) for month in range(1, 10)] + [str(month) for month in range(10, 13)]
[…]

### 2023-03-15 output/group_1_crimes_100m/tables/balance_table.tex
Produced figures for presentation;'

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_group_1_crimes_100m & 0.41 & 0.07 & 0.01 & 0.03 & 0.45 \\
 & pre_treatment_change_in_group_1_crimes_100m & 0.04 & -0.02 & 0.56 & 0.01 & 0.87 \\
\cline{1-7}
\multirow[c]{6}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & 0.03 & 0.02 \\
 & job_density_2013 & 16,069.14 & 926.91 & 0.52 & 1,906.77 & 0.36 \\
 & poor_share2010 & 0.27 & -0.00 & 0.53 & -0.03 & 0.00 \\
 & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -39.79 & 0.95 \\
 & rent_twobed2015 & 1,339.99 & -73.79 & 0.01 & -48.83 & 0.25 \\
 & traveltime15_2010 & 0.16 & -0.01 & 0.01 & -0.02 & 0.00 \\
\cline{1-7}
\textit{Panel D} & isEntityP & 0.81 & -0.06 & 0.00 & -0.06 & 0.00 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-03-15 output/group_1_crimes_100m/tables/pre_treatment_covariate_tests.tex
Produced figures for presentation;'

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Assault-Related Crime Incidents Within 100m, Oct. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_1_crimes_100m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_1_crimes_100m & 0.00 & 0.56 \\
\cline{1-4}
\multirow[c]{7}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.78 \\
 & job_density_2013 & 0.00 & 0.52 \\
 & med_hhinc2016 & 0.09 & 0.12 \\
 & poor_share2010 & 0.00 & 0.53 \\
 & popdensity2010 & 0.03 & 0.01 \\
 & rent_twobed2015 & 0.00 & 0.01 \\
 & traveltime15_2010 & 0.00 & 0.01 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.15 & 0.00 \\
 & no_cause & 0.34 & 0.90 \\
 & non_payment & 0.05 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.15 & 0.00 \\
 & hasAttyP & 0.54 & 0.00 \\
 & isEntityD & 0.14 & 0.01 \\
 & isEntityP & 0.02 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-03-15 output/group_2_crimes_100m/tables/pre_treatment_covariate_tests.tex
Produced figures for presentation;'

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Drug-Related Crime Incidents Within 100m, Oct. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_2_crimes_100m & nan & 0.34 \\
 & pre_treatment_change_in_group_2_crimes_100m & nan & 0.70 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & nan & 0.78 \\
 & job_density_2013 & nan & 0.52 \\
 & med_hhinc2016 & nan & 0.12 \\
 & poor_share2010 & nan & 0.53 \\
 & popdensity2010 & nan & 0.01 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & nan & 0.00 \\
 & no_cause & nan & 0.90 \\
 & non_payment & nan & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & nan & 0.00 \\
 & hasAttyP & nan & 0.00 \\
 & isEntityD & nan & 0.01 \\
 & isEntityP & nan & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-03-15 output/group_3_crimes_100m/tables/pre_treatment_covariate_tests.tex
Produced figures for presentation;'

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Investigations Within 100m, Oct. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_3_crimes_100m & 0.00 & 0.08 \\
 & pre_treatment_change_in_group_3_crimes_100m & 0.05 & 0.45 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.78 \\
 & job_density_2013 & 0.00 & 0.52 \\
 & med_hhinc2016 & 0.19 & 0.12 \\
 & poor_share2010 & 0.45 & 0.53 \\
 & popdensity2010 & 0.00 & 0.01 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.00 & 0.00 \\
 & no_cause & 0.01 & 0.90 \\
 & non_payment & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.80 & 0.00 \\
 & hasAttyP & 0.00 & 0.00 \\
 & isEntityD & 0.00 & 0.01 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-03-15 output/summary_statistics/tables/summary_statistics.tex
Produced figures for presentation;'

--- 2023-01-19 output/summary_statistics/tables/summary_statistics.tex
@@
 \midrule
-\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change, Jan. 2017 to Jan. 2019 & 46,593.74 & 37,330.00 & 158,125.14 & 10,160 \\
- & Zestimate, Jan. 2017 & 298,908.73 & 235,117.00 & 352,754.39 & 10,176 \\
+\multirow[c]{34}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & pre_treatment_change_in_group_0_crimes_100m & -0.08 & 0.00 & 1.65 & 40,734 \\
+ & pre_treatment_change_in_group_0_crimes_150m & -0.19 & 0.00 & 2.74 & 40,734 \\
+ & pre_treatment_change_in_group_0_crimes_200m & -0.36 & 0.00 & 3.68 & 40,734 \\
+ & pre_treatment_change_in_group_0_crimes_50m & -0.01 & 0.00 & 0.82 & 40,734 \\
+ & pre_treatment_change_in_group_1_crimes_100m & 0.00 & 0.00 & 0.39 & 40,734 \\
+ & pre_treatment_change_in_group_1_crimes_150m & 0.01 & 0.00 & 0.53 & 40,734 \\
+ & pre_treatment_change_in_group_1_crimes_200m & 0.02 & 0.00 & 0.69 & 40,734 \\
+ & pre_treatment_change_in_group_1_crimes_50m & 0.00 & 0.00 & 0.21 & 40,734 \\
+ & pre_treatment_change_in_group_2_crimes_100m & -0.00 & 0.00 & 0.37 & 40,734 \\
+ & pre_treatment_change_in_group_2_crimes_150m & -0.01 & 0.00 & 0.59 & 40,734 \\
+ & pre_treatment_change_in_group_2_crimes_200m & -0.03 & 0.00 & 0.84 & 40,734 \\
+ & pre_treatment_change_in_group_2_crimes_50m & -0.00 & 0.00 & 0.14 & 40,734 \\
+ & pre_treatment_change_in_group_3_crimes_100m & 0.01 & 0.00 & 0.40 & 40,734 \\
+ & pre_treatment_change_in_group_3_crimes_150m & 0.01 & 0.00 & 0.57 & 40,734 \\
+ & pre_treatment_change_in_group_3_crimes_200m & 0.02 & 0.00 & 0.76 & 40,734 \\
+ & pre_treatment_change_in_group_3_crimes_50m & 0.00 & 0.00 & 0.22 & 40,734 \\
+ & pre_treatment_change_in_zestimate & 46,593.08 & 37,330.00 & 158,125.24 & 10,160 \\
+ & twenty_seventeen_group_0_crimes_100m & 0.77 & 0.00 & 2.89 & 40,734 \\
+ & twenty_seventeen_group_0_crimes_150m & 1.59 & 0.00 & 5.61 & 40,734 \\
+ & twenty_seventeen_group_0_crimes_200m & 2.70 & 0.00 & 8.82 & 40,734 \\
+ & twenty_seventeen_group_0_crimes_50m & 0.22 & 0.00 & 1.11 & 40,734 \\
+ & twenty_seventeen_group_1_crimes_100m & 0.06 & 0.00 & 0.34 & 40,734 \\
+ & twenty_seventeen_group_1_crimes_150m & 0.12 & 0.00 & 0.59 & 40,734 \\
+ & twenty_seventeen_group_1_crimes_200m & 0.21 & 0.00 & 0.83 & 40,734 \\
+ & twenty_seventeen_group_1_crimes_50m & 0.02 & 0.00 & 0.16 & 40,734 \\
+ & twenty_seventeen_group_2_crimes_100m & 0.03 & 0.00 & 0.37 & 40,734 \\
+ & twenty_seventeen_group_2_crimes_150m & 0.06 & 0.00 & 0.56 & 40,734 \\
+ & twenty_seventeen_group_2_crimes_200m & 0.11 & 0.00 & 0.86 & 40,734 \\
+ & twenty_seventeen_group_2_crimes_50m & 0.01 & 0.00 & 0.26 & 40,734 \\
+ & twenty_seventeen_group_3_crimes_100m & 0.07 & 0.00 & 0.36 & 40,734 \\
+ & twenty_seventeen_group_3_crimes_150m & 0.14 & 0.00 & 0.63 & 40,734 \\
+ & twenty_seventeen_group_3_crimes_200m & 0.25 & 0.00 & 1.02 & 40,734 \\
+ & twenty_seventeen_group_3_crimes_50m & 0.02 & 0.00 & 0.16 & 40,734 \\
+ & twenty_seventeen_zestimate & 298,898.22 & 235,078.00 & 352,756.46 & 10,176 \\
 \cline{1-6}
-\multirow[c]{8}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,797.07 & 1,355.40 & 17,579.99 & 40,726 \\
- & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
- & Median two bedroom rent (2015) & 1,116.27 & 1,055.00 & 396.29 & 30,537 \\
- & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
- & Share below poverty line & 0.20 & 0.16 & 0.15 & 40,726 \\
- & Share white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
- & Share with bachelor's degree & 0.26 & 0.22 & 0.17 & 40,726 \\
- & Share with commute $<$15 minutes (2010) & 0.28 & 0.27 & 0.11 & 40,726 \\
+\multirow[c]{8}{4cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.26 & 0.22 & 0.17 & 40,732 \\
+ & job_density_2013 & 4,802.71 & 1,355.40 & 17,583.20 & 40,732 \\
+ & med_hhinc2016 & 52,695.02 & 47,105.00 & 27,212.35 & 40,732 \\
+ & poor_share2010 & 0.20 & 0.16 & 0.15 & 40,732 \\
+ & popdensity2010 & 9,151.92 & 5,982.68 & 9,537.28 & 40,732 \\
+ & rent_twobed2015 & 1,116.73 & 1,055.00 & 396.69 & 30,546 \\
+ & share_white2010 & 0.58 & 0.63 & 0.29 & 40,732 \\
+ & traveltime15_2010 & 0.28 & 0.27 & 0.11 & 40,732 \\
 \cline{1-6}
-\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
- & No cause & 0.11 & 0.00 & 0.31 & 40,727 \\
- & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,727 \\
+\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.12 & 0.00 & 0.33 & 40,734 \\
+ & no_cause & 0.11 & 0.00 & 0.31 & 40,734 \\
+ & non_payment & 0.75 & 1.00 & 0.43 & 40,734 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,727 \\
- & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,727 \\
- & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,727 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.09 & 0.00 & 0.28 & 40,734 \\
+ & hasAttyP & 0.84 & 1.00 & 0.37 & 40,734 \\
+ & isEntityD & 0.01 & 0.00 & 0.08 & 40,734 \\
+ & isEntityP & 0.70 & 1.00 & 0.46 & 40,734 \\
 \cline{1-6}
-\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
- & Case dismised & 0.29 & 0.00 & 0.45 & 40,727 \\
- & Case duration & 57.81 & 21.00 & 78.29 & 39,087 \\
- & Case heard & 0.06 & 0.00 & 0.23 & 40,727 \\
- & Case mediated & 0.41 & 0.00 & 0.49 & 40,727 \\
- & Money judgment & 1,890.34 & 0.00 & 5,279.49 & 40,727 \\
+\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & case_duration & 57.81 & 21.00 & 78.28 & 39,094 \\
+ & defaulted & 0.20 & 0.00 & 0.40 & 40,734 \\
+ & dismissed & 0.29 & 0.00 & 0.45 & 40,734 \\
+ & heard & 0.06 & 0.00 & 0.23 & 40,734 \\
+ & judgment & 1,890.02 & 0.00 & 5,279.08 & 40,734 \\
+ & mediated & 0.41 & 0.00 & 0.49 & 40,734 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 377,384.02 & 305,144.00 & 316,645.29 & 10,096 \\
- & One year after filing date & 421,601.75 & 347,550.00 & 344,328.86 & 10,443 \\
- & Three years after filing date & 501,611.80 & 414,600.00 & 780,467.01 & 5,894 \\
- & Two years after filing date & 477,948.08 & 393,900.00 & 457,694.83 & 9,175 \\
+\multirow[c]{34}{4cm}{\textit{Panel F: Post-treatment Outcomes}} & group_0_crimes_100m_1_years_relative_to_treatment & 0.52 & 0.00 & 2.57 & 40,734 \\
+ & group_0_crimes_100m_2_years_relative_to_treatment & 0.52 & 0.00 & 2.21 & 35,684 \\
+ & group_0_crimes_150m_1_years_relative_to_treatment & 1.08 & 0.00 & 5.19 & 40,734 \\
+ & group_0_crimes_150m_2_years_relative_to_treatment & 1.11 & 0.00 & 5.26 & 35,684 \\
+ & group_0_crimes_200m_1_years_relative_to_treatment & 1.93 & 0.00 & 8.75 & 40,734 \\
+ & group_0_crimes_200m_2_years_relative_to_treatment & 2.01 & 0.00 & 9.13 & 35,684 \\
+ & group_0_crimes_50m_1_years_relative_to_treatment & 0.15 & 0.00 & 1.43 & 40,734 \\
+ & group_0_crimes_50m_2_years_relative_to_treatment & 0.16 & 0.00 & 0.86 & 35,684 \\
+ & group_1_crimes_100m_1_years_relative_to_treatment & 0.04 & 0.00 & 0.28 & 40,734 \\
+ & group_1_crimes_100m_2_years_relative_to_treatment & 0.04 & 0.00 & 0.25 & 35,684 \\
+ & group_1_crimes_150m_1_years_relative_to_treatment & 0.08 & 0.00 & 0.44 & 40,734 \\
+ & group_1_crimes_150m_2_years_relative_to_treatment & 0.08 & 0.00 & 0.42 & 35,684 \\
+ & group_1_crimes_200m_1_years_relative_to_treatment & 0.13 & 0.00 & 0.66 & 40,734 \\
+ & group_1_crimes_200m_2_years_relative_to_treatment & 0.13 & 0.00 & 0.64 & 35,684 \\
+ & group_1_crimes_50m_1_years_relative_to_treatment & 0.01 & 0.00 & 0.16 & 40,734 \\
+ & group_1_crimes_50m_2_years_relative_to_treatment & 0.01 & 0.00 & 0.12 & 35,684 \\
+ & group_2_crimes_100m_1_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 40,734 \\
+ & group_2_crimes_100m_2_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 35,684 \\
+ & group_2_crimes_150m_1_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 40,734 \\
+ & group_2_crimes_150m_2_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 35,684 \\
+ & group_2_crimes_200m_1_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 40,734 \\
+ & group_2_crimes_200m_2_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 35,684 \\
+ & group_2_crimes_50m_1_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 40,734 \\
+ & group_2_crimes_50m_2_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 35,684 \\
+ & group_3_crimes_100m_1_years_relative_to_treatment & 0.08 & 0.00 & 0.53 & 40,734 \\
+ & group_3_crimes_100m_2_years_relative_to_treatment & 0.09 & 0.00 & 0.50 & 35,684 \\
+ & group_3_crimes_150m_1_years_relative_to_treatment & 0.16 & 0.00 & 0.79 & 40,734 \\
+ & group_3_crimes_150m_2_years_relative_to_treatment & 0.18 & 0.00 & 0.87 & 35,684 \\
+ & group_3_crimes_200m_1_years_relative_to_treatment & 0.28 & 0.00 & 1.23 & 40,734 \\
+ & group_3_crimes_200m_2_years_relative_to_treatment & 0.33 & 0.00 & 1.50 & 35,684 \\
+ & group_3_crimes_50m_1_years_relative_to_treatment & 0.02 & 0.00 & 0.30 & 40,734 \\
+ & group_3_crimes_50m_2_years_relative_to_treatment & 0.03 & 0.00 & 0.21 & 35,684 \\
+ & zestimate_1_years_relative_to_treatment & 421,590.21 & 347,444.00 & 344,333.24 & 10,443 \\
+ & zestimate_2_years_relative_to_treatment & 477,931.84 & 393,800.00 & 457,699.06 & 9,175 \\
 \cline{1-6}

### 2023-03-15 src/02_analysis/analysis_utilities.py

@@ -57,6 +57,7 @@ def prepare_df(df: pd.DataFrame, analysis: str, treatment_date_variable: str, pr
     # Standardize control variables.
     [pre_treatment_covariates.remove(missing_indicator) for missing_indicator in missing_indicators]
     df.loc[:, pre_treatment_covariates] = StandardScaler().fit_transform(df[pre_treatment_covariates])
+    [pre_treatment_covariates.append(missing_indicator) for missing_indicator in missing_indicators]
 
     # Convert months from string format to integer format.
     df.loc[:, 'month'] = df['month'].str.replace(f"_{analysis}", '', regex=False).replace(month_to_int_dictionary)
@@ -412,8 +413,8 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     panel_A = pd.concat([panel_A], keys=["Panel A: Pre-treatment Outcomes"])
 
     # Panel B: Census Tract Characteristics
-    panel_B_columns = ['med_hhinc2016', 'popdensity2010', 'share_white2010', 'frac_coll_plus2010', 'job_density_2013',
-                       'poor_share2010', 'traveltime15_2010', 'rent_twobed2015']
+    panel_B_columns = ['med_hhinc2016', 'popdensity2010', 'frac_coll_plus2010', 'job_density_2013',
+                       'poor_share2010']
     panel_B = df[sorted(panel_B_columns)].describe().T
     panel_B = pd.concat([panel_B], keys=["Panel B: Census Tract Characteristics"])
 

### 2023-03-15 writing/presentations/march_15.tex

--- 2022-12-23 writing/presentations/december_7.tex
@@
        \end{enumerate}
-       \item Sociologists have found large effects of evictions using non-experimental methods
+       \item Sociologists have found large effects of evictions using non-experimental methods, but economists 
        \begin{enumerate}
@@
         \end{enumerate}
-        \item Assessment values data from the Massachusetts Office of Geographic Information Services
+        \item Crime data from the Boston Police Department (BPD)
         \begin{enumerate}
-            \item Unbalanced panel data on assessor values for nearly every property in Massachussetts
+            \item Incident-level data for every incident that BPD has responded to since 2015
+            \item Coordinates of each incident
         \end{enumerate}
-        \item Link evictions to assessment records on fiscal year and location
+        \item Create 100m radius around every eviction and match to crimes which fall into that radius
     \end{enumerate}

### 2023-03-15 output/summary_statistics/tables/summary_statistics.tex
Produced figures for presentation;'

--- 2023-02-27 output/summary_statistics/tables/summary_statistics.tex
@@
 \midrule
-\multirow[c]{4}{4cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change in Crimes Reported, Jan. 2017 to Jan. 2019 & -0.01 & 0.00 & 0.76 & 40,734 \\
- & Change in Zestimate, Jan. 2017 to Jan. 2019 & 46,593.08 & 37,330.00 & 158,125.24 & 10,160 \\
- & Crimes reported, Jan. 2017 & 0.21 & 0.00 & 4.79 & 40,734 \\
- & Zestimate, Jan. 2017 & 298,898.22 & 235,078.00 & 352,756.46 & 10,176 \\
+\multirow[c]{6}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & pre_treatment_change_in_group_0_crimes_100m & -0.54 & 0.00 & 4.26 & 6,060 \\
+ & pre_treatment_change_in_group_1_crimes_100m & 0.01 & 0.00 & 1.00 & 6,060 \\
+ & pre_treatment_change_in_group_3_crimes_100m & 0.05 & 0.00 & 1.04 & 6,060 \\
+ & twenty_seventeen_group_0_crimes_100m & 5.16 & 4.00 & 5.77 & 6,060 \\
+ & twenty_seventeen_group_1_crimes_100m & 0.41 & 0.00 & 0.80 & 6,060 \\
+ & twenty_seventeen_group_3_crimes_100m & 0.45 & 0.00 & 0.82 & 6,060 \\
 \cline{1-6}
-\multirow[c]{8}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,802.71 & 1,355.40 & 17,583.20 & 40,732 \\
- & Median household income (2016) & 52,695.02 & 47,105.00 & 27,212.35 & 40,732 \\
- & Median two bedroom rent (2015) & 1,116.73 & 1,055.00 & 396.69 & 30,546 \\
- & Population density (2010) & 9,151.92 & 5,982.68 & 9,537.28 & 40,732 \\
- & Share below poverty line & 0.20 & 0.16 & 0.15 & 40,732 \\
- & Share white (2010) & 0.58 & 0.63 & 0.29 & 40,732 \\
- & Share with bachelor's degree & 0.26 & 0.22 & 0.17 & 40,732 \\
- & Share with commute $<$15 minutes (2010) & 0.28 & 0.27 & 0.11 & 40,732 \\
+\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.31 & 0.24 & 0.22 & 6,060 \\
+ & job_density_2013 & 14,806.08 & 2,425.15 & 40,595.37 & 6,060 \\
+ & med_hhinc2016 & 47,188.87 & 41,146.00 & 24,703.65 & 6,060 \\
+ & poor_share2010 & 0.28 & 0.25 & 0.14 & 6,060 \\
+ & popdensity2010 & 22,704.52 & 20,644.44 & 13,091.45 & 6,060 \\
 \cline{1-6}
-\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,734 \\
- & No cause & 0.11 & 0.00 & 0.31 & 40,734 \\
- & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,734 \\
+\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.17 & 0.00 & 0.37 & 6,060 \\
+ & no_cause & 0.05 & 0.00 & 0.22 & 6,060 \\
+ & non_payment & 0.78 & 1.00 & 0.42 & 6,060 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,734 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,734 \\
- & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,734 \\
- & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,734 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.08 & 0.00 & 0.27 & 6,060 \\
+ & hasAttyP & 0.88 & 1.00 & 0.32 & 6,060 \\
+ & isEntityD & 0.02 & 0.00 & 0.14 & 6,060 \\
+ & isEntityP & 0.81 & 1.00 & 0.39 & 6,060 \\
 \cline{1-6}
-\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,734 \\
- & Case dismised & 0.29 & 0.00 & 0.45 & 40,734 \\
- & Case duration & 57.81 & 21.00 & 78.28 & 39,094 \\
- & Case heard & 0.06 & 0.00 & 0.23 & 40,734 \\
- & Case mediated & 0.41 & 0.00 & 0.49 & 40,734 \\
- & Money judgment & 1,890.02 & 0.00 & 5,279.08 & 40,734 \\
+\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & case_duration & 58.17 & 19.00 & 88.96 & 5,500 \\
+ & defaulted & 0.19 & 0.00 & 0.39 & 6,060 \\
+ & dismissed & 0.27 & 0.00 & 0.44 & 6,060 \\
+ & heard & 0.03 & 0.00 & 0.17 & 6,060 \\
+ & judgment & 1,938.57 & 0.00 & 5,337.87 & 6,060 \\
+ & mediated & 0.40 & 0.00 & 0.49 & 6,060 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel F: Post-treatment Zestimates}} & Crimes one year after filing date & 0.19 & 0.00 & 4.32 & 40,734 \\
- & Crimes two years after filing date & 0.18 & 0.00 & 4.40 & 35,684 \\
- & Zestimate one year after filing date & 421,590.21 & 347,444.00 & 344,333.24 & 10,443 \\
- & Zestimate two years after filing date & 477,931.84 & 393,800.00 & 457,699.06 & 9,175 \\
+\multirow[c]{34}{4cm}{\textit{Panel F: Post-treatment Outcomes}} & group_0_crimes_100m_1_years_relative_to_treatment & 3.46 & 2.00 & 5.84 & 6,060 \\
+ & group_0_crimes_100m_2_years_relative_to_treatment & 3.49 & 2.00 & 4.72 & 5,338 \\
+ & group_0_crimes_150m_1_years_relative_to_treatment & 7.26 & 5.00 & 11.68 & 6,060 \\
+ & group_0_crimes_150m_2_years_relative_to_treatment & 7.38 & 5.00 & 11.77 & 5,338 \\
+ & group_0_crimes_200m_1_years_relative_to_treatment & 12.94 & 9.00 & 19.28 & 6,060 \\
+ & group_0_crimes_200m_2_years_relative_to_treatment & 13.39 & 9.00 & 20.13 & 5,338 \\
+ & group_0_crimes_50m_1_years_relative_to_treatment & 1.03 & 0.00 & 3.59 & 6,060 \\
+ & group_0_crimes_50m_2_years_relative_to_treatment & 1.04 & 0.00 & 2.01 & 5,338 \\
+ & group_1_crimes_100m_1_years_relative_to_treatment & 0.27 & 0.00 & 0.67 & 6,060 \\
+ & group_1_crimes_100m_2_years_relative_to_treatment & 0.24 & 0.00 & 0.60 & 5,338 \\
+ & group_1_crimes_150m_1_years_relative_to_treatment & 0.54 & 0.00 & 1.04 & 6,060 \\
+ & group_1_crimes_150m_2_years_relative_to_treatment & 0.51 & 0.00 & 0.97 & 5,338 \\
+ & group_1_crimes_200m_1_years_relative_to_treatment & 0.91 & 0.00 & 1.49 & 6,060 \\
+ & group_1_crimes_200m_2_years_relative_to_treatment & 0.88 & 0.00 & 1.43 & 5,338 \\
+ & group_1_crimes_50m_1_years_relative_to_treatment & 0.09 & 0.00 & 0.41 & 6,060 \\
+ & group_1_crimes_50m_2_years_relative_to_treatment & 0.07 & 0.00 & 0.30 & 5,338 \\
+ & group_2_crimes_100m_1_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 6,060 \\
+ & group_2_crimes_100m_2_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 5,338 \\
+ & group_2_crimes_150m_1_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 6,060 \\
+ & group_2_crimes_150m_2_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 5,338 \\
+ & group_2_crimes_200m_1_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 6,060 \\
+ & group_2_crimes_200m_2_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 5,338 \\
+ & group_2_crimes_50m_1_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 6,060 \\
+ & group_2_crimes_50m_2_years_relative_to_treatment & 0.00 & 0.00 & 0.00 & 5,338 \\
+ & group_3_crimes_100m_1_years_relative_to_treatment & 0.55 & 0.00 & 1.28 & 6,060 \\
+ & group_3_crimes_100m_2_years_relative_to_treatment & 0.60 & 0.00 & 1.16 & 5,338 \\
+ & group_3_crimes_150m_1_years_relative_to_treatment & 1.08 & 1.00 & 1.80 & 6,060 \\
+ & group_3_crimes_150m_2_years_relative_to_treatment & 1.22 & 1.00 & 1.96 & 5,338 \\
+ & group_3_crimes_200m_1_years_relative_to_treatment & 1.87 & 1.00 & 2.68 & 6,060 \\
+ & group_3_crimes_200m_2_years_relative_to_treatment & 2.21 & 1.00 & 3.29 & 5,338 \\
+ & group_3_crimes_50m_1_years_relative_to_treatment & 0.17 & 0.00 & 0.76 & 6,060 \\
+ & group_3_crimes_50m_2_years_relative_to_treatment & 0.18 & 0.00 & 0.51 & 5,338 \\
+ & zestimate_1_years_relative_to_treatment & 793,120.53 & 708,645.00 & 498,598.36 & 1,154 \\
+ & zestimate_2_years_relative_to_treatment & 879,154.76 & 788,300.00 & 577,909.62 & 1,041 \\
 \cline{1-6}

### 2023-03-16 output/group_1_crimes_100m/tables/balance_table.tex
re-ran analyses with file_date as treatment timing

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_group_1_crimes_100m & 0.41 & 0.07 & 0.01 & 0.03 & 0.45 \\
- & pre_treatment_change_in_group_1_crimes_100m & 0.04 & -0.02 & 0.56 & 0.01 & 0.87 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_group_1_crimes_100m & 0.41 & 0.07 & 0.01 & -0.00 & 0.85 \\
+ & pre_treatment_change_in_group_1_crimes_100m & 0.04 & -0.02 & 0.56 & -0.00 & 0.91 \\
 \cline{1-7}
-\multirow[c]{6}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & 0.03 & 0.02 \\
- & job_density_2013 & 16,069.14 & 926.91 & 0.52 & 1,906.77 & 0.36 \\
- & poor_share2010 & 0.27 & -0.00 & 0.53 & -0.03 & 0.00 \\
- & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -39.79 & 0.95 \\
- & rent_twobed2015 & 1,339.99 & -73.79 & 0.01 & -48.83 & 0.25 \\
- & traveltime15_2010 & 0.16 & -0.01 & 0.01 & -0.02 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.01 & 0.15 \\
+ & job_density_2013 & 16,069.14 & 926.91 & 0.52 & -413.06 & 0.77 \\
+ & poor_share2010 & 0.27 & -0.00 & 0.53 & -0.01 & 0.05 \\
+ & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -607.79 & 0.07 \\
 \cline{1-7}
-\textit{Panel D} & isEntityP & 0.81 & -0.06 & 0.00 & -0.06 & 0.00 \\
+\textit{Panel D} & isEntityP & 0.81 & -0.06 & 0.00 & -0.04 & 0.00 \\
 \cline{1-7}

### 2023-03-16 src/02_analysis/analysis_utilities.py

@@ -62,6 +62,10 @@ def prepare_df(df: pd.DataFrame, analysis: str, treatment_date_variable: str, pr
     # Convert months from string format to integer format.
     df.loc[:, 'month'] = df['month'].str.replace(f"_{analysis}", '', regex=False).replace(month_to_int_dictionary)
     df.loc[:, treatment_month_variable] = df[treatment_month_variable].replace(month_to_int_dictionary)
+
+    # Generate alias treatment month variable which will not be used for DiD so that we can calculate sample size later.
+    df.loc[:, treatment_month_variable+'_alias'] = df[treatment_month_variable]
+
     # Set treatment month to 0 for untreated observations.
     never_treated_mask = (df['judgment_for_plaintiff'] == 0)
     df.loc[never_treated_mask, treatment_month_variable] = np.NaN
@@ -346,7 +350,8 @@ def aggregate_by_event_time_and_plot(att_gt,
 
     # Plot sample size at each event-time.
     df_copy = df.copy().reset_index()
-    df_copy.loc[:, 'event_time'] = df_copy['month'] - df_copy[treatment_month_variable]
+    df_copy.loc[:, 'event_time'] = df_copy['month'] - df_copy[treatment_month_variable+'_alias']
+
     cases_per_year = df_copy.groupby('event_time')['case_number'].nunique().loc[start_period:end_period]
     x = cases_per_year.index
     y = cases_per_year.values

### 2023-03-23 output/group_0_crimes_100m/tables/balance_table.tex

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_group_0_crimes_100m & 5.25 & 0.35 & 0.08 & -0.12 & 0.55 \\
 & pre_treatment_change_in_group_0_crimes_100m & -0.46 & 0.02 & 0.87 & 0.01 & 0.93 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.01 & 0.27 \\
 & job_density_2013 & 16,069.14 & 926.91 & 0.52 & -363.43 & 0.80 \\
 & med_hhinc2016 & 48,035.65 & 1,312.56 & 0.12 & -1,172.96 & 0.14 \\
 & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -528.45 & 0.18 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel C}} & no_cause & 0.05 & -0.00 & 0.90 & -0.00 & 0.86 \\
 & non_payment & 0.78 & -0.07 & 0.00 & -0.02 & 0.05 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.03 & 0.02 \\
 & isEntityD & 0.01 & -0.01 & 0.01 & -0.00 & 0.82 \\
 & isEntityP & 0.81 & -0.06 & 0.00 & -0.02 & 0.03 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-03-23 output/group_0_crimes_100m/tables/pre_treatment_covariate_tests.tex

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Crime Incidents Within 100m, Oct. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_0_crimes_100m & 0.00 & 0.08 \\
 & pre_treatment_change_in_group_0_crimes_100m & 0.00 & 0.87 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.78 \\
 & job_density_2013 & 0.00 & 0.52 \\
 & med_hhinc2016 & 0.01 & 0.12 \\
 & poor_share2010 & 0.57 & 0.53 \\
 & popdensity2010 & 0.00 & 0.01 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.06 & 0.00 \\
 & no_cause & 0.00 & 0.90 \\
 & non_payment & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.44 & 0.00 \\
 & hasAttyP & 0.01 & 0.00 \\
 & isEntityD & 0.00 & 0.01 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-03-23 output/group_1_crimes_100m/tables/pre_treatment_covariate_tests.tex

@@
 \cline{1-4}
-\multirow[c]{7}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.78 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.78 \\
  & job_density_2013 & 0.00 & 0.52 \\
@@
  & popdensity2010 & 0.03 & 0.01 \\
- & rent_twobed2015 & 0.00 & 0.01 \\
- & traveltime15_2010 & 0.00 & 0.01 \\
 \cline{1-4}

### 2023-03-23 output/group_3_crimes_100m/tables/balance_table.tex

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_group_3_crimes_100m & 0.45 & 0.05 & 0.08 & -0.00 & 0.95 \\
 & pre_treatment_change_in_group_3_crimes_100m & 0.06 & -0.03 & 0.45 & -0.00 & 0.99 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.00 & 0.86 \\
 & job_density_2013 & 16,069.14 & 926.91 & 0.52 & -65.36 & 0.96 \\
 & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -94.31 & 0.83 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel C}} & for_cause & 0.17 & 0.07 & 0.00 & -0.00 & 0.96 \\
 & no_cause & 0.05 & -0.00 & 0.90 & -0.00 & 0.98 \\
 & non_payment & 0.78 & -0.07 & 0.00 & -0.00 & 0.75 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.00 & 0.69 \\
 & isEntityD & 0.01 & -0.01 & 0.01 & -0.00 & 0.98 \\
 & isEntityP & 0.81 & -0.06 & 0.00 & -0.00 & 0.72 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-03-23 writing/presentations/march_15.tex

@@
        \end{enumerate}
-       \item Sociologists have found large effects of evictions using non-experimental methods, but economists 
+       \item Sociologists have found large effects of evictions using non-experimental methods=
+       \item Economists are just beginning to study eviction
        \begin{enumerate}
@@
 \begin{enumerate}
-    \item Strong negative correlation between the presence of eviction and property values
-    \item Several potential channels through which eviction might affect property values
+    \item Strong negative correlation between the presence of eviction and crime
+    \item Several potential channels through which eviction might affect crime
     \begin{enumerate}
-        \item Evidence suggests that longer tenancy can increase property values
+        \item Maybe eviction weakens community bonds that discourage crime
+        \item Maybe evicted tenants are more likely to commit crime after receiving notice of eviction
         \item Or, perhaps landlords are evicting problematic tenants
     \end{enumerate}
-    \item Either way—property values determine school district 
-    funding, so kids' outcomes could be at stake
-    \item Ideally, I would have \emph{market} values instead of assessment values
+    \item Either way, understanding effect is important to understanding how eviction is affecting communitiies
+    \item Kroeger and La Mattina (2020): Nuisance ordinances increase eviction risk in Ohio
+    \item Falcone (2022): Evictions cause crime! But only if nuisance ordinances affect crime only through evictions...
 \end{enumerate}

### 2023-03-31 output/group_0_crimes_100m/tables/balance_table.tex
biweekly analysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_group_0_crimes_100m & 5.25 & 0.35 & 0.08 & -0.12 & 0.55 \\
- & pre_treatment_change_in_group_0_crimes_100m & -0.46 & 0.02 & 0.87 & 0.01 & 0.93 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_100m & 7.20 & 0.54 & 0.04 & -0.05 & 0.83 \\
+ & pre_treatment_change_in_group_2_crimes_100m & 0.03 & -0.03 & 0.13 & -0.00 & 0.95 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.01 & 0.27 \\
- & job_density_2013 & 16,069.14 & 926.91 & 0.52 & -363.43 & 0.80 \\
- & med_hhinc2016 & 48,035.65 & 1,312.56 & 0.12 & -1,172.96 & 0.14 \\
- & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -528.45 & 0.18 \\
+\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.00 & 0.68 \\
+ & med_hhinc2016 & 48,035.65 & 1,312.56 & 0.12 & -429.96 & 0.60 \\
+ & poor_share2010 & 0.27 & -0.00 & 0.53 & -0.00 & 0.57 \\
+ & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -185.35 & 0.65 \\
 \cline{1-7}
-\multirow[c]{2}{3cm}{\textit{Panel C}} & no_cause & 0.05 & -0.00 & 0.90 & -0.00 & 0.86 \\
- & non_payment & 0.78 & -0.07 & 0.00 & -0.02 & 0.05 \\
-\cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.03 & 0.02 \\
- & isEntityD & 0.01 & -0.01 & 0.01 & -0.00 & 0.82 \\
- & isEntityP & 0.81 & -0.06 & 0.00 & -0.02 & 0.03 \\
+\multirow[c]{2}{3cm}{\textit{Panel D}} & isEntityD & 0.01 & -0.01 & 0.01 & -0.00 & 0.90 \\
+ & isEntityP & 0.81 & -0.06 & 0.00 & -0.01 & 0.30 \\
 \cline{1-7}

### 2023-03-31 output/group_0_crimes_100m/tables/pre_treatment_covariate_tests.tex
biweekly analysis

@@
 \\
- &  & Crime Incidents Within 100m, Oct. 2022 & Plaintiff Victory \\
+ &  &  &  \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_0_crimes_100m & 0.00 & 0.08 \\
- & pre_treatment_change_in_group_0_crimes_100m & 0.00 & 0.87 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_100m & 0.00 & 0.04 \\
+ & pre_treatment_change_in_group_2_crimes_100m & 0.00 & 0.13 \\
 \cline{1-4}
 \multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.78 \\
- & job_density_2013 & 0.00 & 0.52 \\
- & med_hhinc2016 & 0.01 & 0.12 \\
- & poor_share2010 & 0.57 & 0.53 \\
+ & job_density_2013 & 0.75 & 0.52 \\
+ & med_hhinc2016 & 0.00 & 0.12 \\
+ & poor_share2010 & 0.03 & 0.53 \\
  & popdensity2010 & 0.00 & 0.01 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.06 & 0.00 \\
- & no_cause & 0.00 & 0.90 \\
- & non_payment & 0.00 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.28 & 0.00 \\
+ & no_cause & 0.45 & 0.90 \\
+ & non_payment & 0.22 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.44 & 0.00 \\
- & hasAttyP & 0.01 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.28 & 0.00 \\
+ & hasAttyP & 0.21 & 0.00 \\
  & isEntityD & 0.00 & 0.01 \\
- & isEntityP & 0.00 & 0.00 \\
+ & isEntityP & 0.01 & 0.00 \\
 \cline{1-4}

### 2023-03-31 output/group_1_crimes_100m/tables/balance_table.tex
biweekly analysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_group_1_crimes_100m & 0.41 & 0.07 & 0.01 & -0.00 & 0.85 \\
- & pre_treatment_change_in_group_1_crimes_100m & 0.04 & -0.02 & 0.56 & -0.00 & 0.91 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_group_1_crimes_100m & 0.25 & 0.04 & 0.00 & -0.00 & 0.68 \\
+ & pre_treatment_change_in_group_1_crimes_100m & 0.01 & -0.01 & 0.44 & -0.00 & 0.90 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.01 & 0.15 \\
- & job_density_2013 & 16,069.14 & 926.91 & 0.52 & -413.06 & 0.77 \\
- & poor_share2010 & 0.27 & -0.00 & 0.53 & -0.01 & 0.05 \\
- & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -607.79 & 0.07 \\
+\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.01 & 0.08 \\
+ & job_density_2013 & 16,069.14 & 926.91 & 0.52 & -529.05 & 0.71 \\
+ & poor_share2010 & 0.27 & -0.00 & 0.53 & -0.01 & 0.02 \\
+ & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -773.92 & 0.02 \\
+\cline{1-7}
+\textit{Panel C} & non_payment & 0.78 & -0.07 & 0.00 & -0.04 & 0.00 \\
 \cline{1-7}

### 2023-03-31 output/group_1_crimes_100m/tables/pre_treatment_covariate_tests.tex
biweekly analysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_1_crimes_100m & 0.00 & 0.01 \\
- & pre_treatment_change_in_group_1_crimes_100m & 0.00 & 0.56 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_1_crimes_100m & 0.00 & 0.00 \\
+ & pre_treatment_change_in_group_1_crimes_100m & 0.00 & 0.44 \\
 \cline{1-4}
@@
  & job_density_2013 & 0.00 & 0.52 \\
- & med_hhinc2016 & 0.09 & 0.12 \\
+ & med_hhinc2016 & 0.45 & 0.12 \\
  & poor_share2010 & 0.00 & 0.53 \\
- & popdensity2010 & 0.03 & 0.01 \\
+ & popdensity2010 & 0.00 & 0.01 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.15 & 0.00 \\
- & no_cause & 0.34 & 0.90 \\
- & non_payment & 0.05 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.06 & 0.00 \\
+ & no_cause & 0.22 & 0.90 \\
+ & non_payment & 0.01 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.15 & 0.00 \\
- & hasAttyP & 0.54 & 0.00 \\
- & isEntityD & 0.14 & 0.01 \\
- & isEntityP & 0.02 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.26 & 0.00 \\
+ & hasAttyP & 0.27 & 0.00 \\
+ & isEntityD & 0.31 & 0.01 \\
+ & isEntityP & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-03-31 output/summary_statistics/tables/summary_statistics.tex
biweekly analysis

--- 2023-03-08 output/summary_statistics/tables/summary_statistics.tex
@@
 \midrule
-\multirow[c]{14}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Zestimate, Jan. 2017 & 298,898.22 & 235,078.00 & 352,756.46 & 10,176 \\
- & pre_treatment_change_in_any_crime_140m & 0.02 & 0.00 & 2.42 & 40,734 \\
- & pre_treatment_change_in_any_crime_200m & 0.05 & 0.00 & 3.31 & 40,734 \\
- & pre_treatment_change_in_any_crime_60m & 0.01 & 0.00 & 1.16 & 40,734 \\
- & pre_treatment_change_in_any_crime_60m & 0.01 & 0.00 & 1.16 & 40,734 \\
- & pre_treatment_change_in_any_crime_90m & 0.03 & 0.00 & 1.71 & 40,734 \\
- & pre_treatment_change_in_any_crime_90m & 0.03 & 0.00 & 1.71 & 40,734 \\
- & pre_treatment_change_in_zestimate & 46,593.08 & 37,330.00 & 158,125.24 & 10,160 \\
- & twenty_seventeen_any_crime_140m & 1.41 & 0.00 & 5.01 & 40,734 \\
- & twenty_seventeen_any_crime_200m & 2.68 & 0.00 & 8.69 & 40,734 \\
- & twenty_seventeen_any_crime_60m & 0.29 & 0.00 & 1.31 & 40,734 \\
- & twenty_seventeen_any_crime_60m & 0.29 & 0.00 & 1.31 & 40,734 \\
- & twenty_seventeen_any_crime_90m & 0.62 & 0.00 & 2.42 & 40,734 \\
- & twenty_seventeen_any_crime_90m & 0.62 & 0.00 & 2.42 & 40,734 \\
+\multirow[c]{6}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & pre_treatment_change_in_group_0_crimes_100m & -0.30 & 0.00 & 2.38 & 6,060 \\
+ & pre_treatment_change_in_group_1_crimes_100m & 0.02 & 0.00 & 0.66 & 6,060 \\
+ & pre_treatment_change_in_group_2_crimes_100m & 0.03 & 0.00 & 0.68 & 6,060 \\
+ & twenty_seventeen_group_0_crimes_100m & 2.32 & 2.00 & 2.83 & 6,060 \\
+ & twenty_seventeen_group_1_crimes_100m & 0.17 & 0.00 & 0.47 & 6,060 \\
+ & twenty_seventeen_group_2_crimes_100m & 0.19 & 0.00 & 0.47 & 6,060 \\
 \cline{1-6}
-\multirow[c]{8}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,802.71 & 1,355.40 & 17,583.20 & 40,732 \\
- & Median household income (2016) & 52,695.02 & 47,105.00 & 27,212.35 & 40,732 \\
- & Median two bedroom rent (2015) & 1,116.73 & 1,055.00 & 396.69 & 30,546 \\
- & Population density (2010) & 9,151.92 & 5,982.68 & 9,537.28 & 40,732 \\
- & Share below poverty line & 0.20 & 0.16 & 0.15 & 40,732 \\
- & Share white (2010) & 0.58 & 0.63 & 0.29 & 40,732 \\
- & Share with bachelor's degree & 0.26 & 0.22 & 0.17 & 40,732 \\
- & Share with commute $<$15 minutes (2010) & 0.28 & 0.27 & 0.11 & 40,732 \\
+\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.31 & 0.24 & 0.22 & 6,060 \\
+ & job_density_2013 & 14,806.08 & 2,425.15 & 40,595.37 & 6,060 \\
+ & med_hhinc2016 & 47,188.87 & 41,146.00 & 24,703.65 & 6,060 \\
+ & poor_share2010 & 0.28 & 0.25 & 0.14 & 6,060 \\
+ & popdensity2010 & 22,704.52 & 20,644.44 & 13,091.45 & 6,060 \\
 \cline{1-6}
-\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,734 \\
- & No cause & 0.11 & 0.00 & 0.31 & 40,734 \\
- & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,734 \\
+\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.17 & 0.00 & 0.37 & 6,060 \\
+ & no_cause & 0.05 & 0.00 & 0.22 & 6,060 \\
+ & non_payment & 0.78 & 1.00 & 0.42 & 6,060 \\
 \cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,734 \\
- & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,734 \\
- & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,734 \\
- & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,734 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.08 & 0.00 & 0.27 & 6,060 \\
+ & hasAttyP & 0.88 & 1.00 & 0.32 & 6,060 \\
+ & isEntityD & 0.02 & 0.00 & 0.14 & 6,060 \\
+ & isEntityP & 0.81 & 1.00 & 0.39 & 6,060 \\
 \cline{1-6}
-\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,734 \\
- & Case dismised & 0.29 & 0.00 & 0.45 & 40,734 \\
- & Case duration & 57.81 & 21.00 & 78.28 & 39,094 \\
- & Case heard & 0.06 & 0.00 & 0.23 & 40,734 \\
- & Case mediated & 0.41 & 0.00 & 0.49 & 40,734 \\
- & Money judgment & 1,890.02 & 0.00 & 5,279.08 & 40,734 \\
+\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & case_duration & 58.17 & 19.00 & 88.96 & 5,500 \\
+ & defaulted & 0.19 & 0.00 & 0.39 & 6,060 \\
+ & dismissed & 0.27 & 0.00 & 0.44 & 6,060 \\
+ & heard & 0.03 & 0.00 & 0.17 & 6,060 \\
+ & judgment & 1,938.57 & 0.00 & 5,337.87 & 6,060 \\
+ & mediated & 0.40 & 0.00 & 0.49 & 6,060 \\
 \cline{1-6}
-\multirow[c]{14}{4cm}{\textit{Panel F: Post-treatment Outcomes}} & Zestimate one year after filing date & 421,590.21 & 347,444.00 & 344,333.24 & 10,443 \\
- & Zestimate two years after filing date & 477,931.84 & 393,800.00 & 457,699.06 & 9,175 \\
- & any_crime_140m_1_years_relative_to_treatment & 1.41 & 0.00 & 4.90 & 40,734 \\
- & any_crime_140m_2_years_relative_to_treatment & 1.50 & 0.00 & 5.04 & 35,684 \\
- & any_crime_200m_1_years_relative_to_treatment & 2.65 & 0.00 & 8.37 & 40,734 \\
- & any_crime_200m_2_years_relative_to_treatment & 2.84 & 0.00 & 8.74 & 35,684 \\
- & any_crime_60m_1_years_relative_to_treatment & 0.31 & 0.00 & 1.41 & 40,734 \\
- & any_crime_60m_1_years_relative_to_treatment & 0.31 & 0.00 & 1.41 & 40,734 \\
- & any_crime_60m_2_years_relative_to_treatment & 0.34 & 0.00 & 1.44 & 35,684 \\
- & any_crime_60m_2_years_relative_to_treatment & 0.34 & 0.00 & 1.44 & 35,684 \\
- & any_crime_90m_1_years_relative_to_treatment & 0.66 & 0.00 & 2.50 & 40,734 \\
- & any_crime_90m_1_years_relative_to_treatment & 0.66 & 0.00 & 2.50 & 40,734 \\
- & any_crime_90m_2_years_relative_to_treatment & 0.69 & 0.00 & 2.53 & 35,684 \\
- & any_crime_90m_2_years_relative_to_treatment & 0.69 & 0.00 & 2.53 & 35,684 \\
+\multirow[c]{6}{4cm}{\textit{Panel F: Post-treatment Outcomes}} & group_0_crimes_100m_1_years_relative_to_treatment & 1.46 & 1.00 & 3.05 & 3,039 \\
+ & group_0_crimes_100m_2_years_relative_to_treatment & 1.48 & 1.00 & 2.31 & 2,830 \\
+ & group_1_crimes_100m_1_years_relative_to_treatment & 0.14 & 0.00 & 0.45 & 3,039 \\
+ & group_1_crimes_100m_2_years_relative_to_treatment & 0.10 & 0.00 & 0.36 & 2,830 \\
+ & group_2_crimes_100m_1_years_relative_to_treatment & 0.20 & 0.00 & 0.55 & 3,039 \\
+ & group_2_crimes_100m_2_years_relative_to_treatment & 0.22 & 0.00 & 0.63 & 2,830 \\
 \cline{1-6}

### 2023-03-31 src/02_analysis/analysis_constants.py

@@ -1,6 +1,0 @@
-class Variables:
-    outcomes = ['zestimate',
-                'group_0_crimes_50m', 'group_0_crimes_100m', 'group_0_crimes_150m', 'group_0_crimes_200m',
-                'group_1_crimes_50m', 'group_1_crimes_100m', 'group_1_crimes_150m', 'group_1_crimes_200m',
-                'group_2_crimes_50m', 'group_2_crimes_100m', 'group_2_crimes_150m', 'group_2_crimes_200m',
-                'group_3_crimes_50m', 'group_3_crimes_100m', 'group_3_crimes_150m', 'group_3_crimes_200m']

### 2023-03-31 src/02_analysis/constants.py

@@ -1,0 +1,2 @@
+class Variables:
+    outcomes = ['group_0_crimes_100m', 'group_1_crimes_100m', 'group_2_crimes_100m']

### 2023-03-31 src/02_analysis/figure_utilities.py

@@ -7,6 +7,8 @@ and plot on that axis. They do not interact with Matplotlib Figure instances.
 Thus, the user must instantiate all subplots and close all figures
 separately.
 """
+from os.path import join
+
 import matplotlib.pyplot as plt
 import numpy as np
 from matplotlib.axes import Axes
@@ -15,6 +17,90 @@ from matplotlib.colors import to_rgba
 
 import figure_and_table_constants
 import matplotlib.transforms as transforms
+
+def aggregate_by_event_time_and_plot(att_gt,
+                                     output_folder: str,
+                                     filename: str,
+                                     start_period: int,
+                                     end_period: int,
+                                     title: str,
+                                     treatment_month_variable: str,
+                                     df: pd.DataFrame):
+    # Get event study-aggregated ATT(t)s.
+    results_df = att_gt.aggregate('event')
+    results_df = results_df.loc[start_period:end_period]
+    results_df.columns = results_df.columns.droplevel().droplevel()
+
+    # Plot event study-style plot of ATTs.
+    fig, (ax, ax2) = plt.subplots(2, 1, sharex=True, height_ratios=[4, 1], layout='constrained')
+    x = results_df.index
+    y = results_df['ATT']
+    y_upper = results_df['upper']
+    y_lower = results_df['lower']
+    ax.set_ylabel("ATT")
+    ax.set_title(title)
+    plot_labeled_vline(ax, x=0, text="Treatment Month", color='black', linestyle='-',
+                                        text_y_location_normalized=0.95)
+    plot_scatter_with_shaded_errors(ax,
+                                                     x.values,
+                                                     y.values,
+                                                     y_upper.values,
+                                                     y_lower.values,
+                                                     point_color='black',
+                                                     error_color='white',
+                                                     edge_color='grey',
+                                                     edge_style='--',
+                                                     zorder=1)
+    plot_labeled_hline(ax, y=0, text="", color='black', linestyle='-', zorder=6)
+
+    # Plot sample size at each event-time.
+    df_copy = df.copy().reset_index()
+    df_copy.loc[:, 'event_time'] = df_copy['month'] - df_copy[treatment_month_variable+'_alias']
+
+    cases_per_year = df_copy.groupby('event_time')['case_number'].nunique().loc[start_period:end_period]
+    x = cases_per_year.index
+    y = cases_per_year.values
+    ax2.plot(x, y, color='black')
[…]

### 2023-03-31 src/02_analysis/panel_utilities.py

@@ -1,0 +1,75 @@
+import pandas as pd
+from sklearn.preprocessing import StandardScaler
+import numpy as np
+from constants import Variables
+from typing import List, Union
+
+
+def get_value_variable_names(df, analysis: str):
+    all_columns = pd.Series(df.columns)  # Create Series containing all columns.
+    value_columns = all_columns[all_columns.str.contains(analysis)]  # Create Series containing only value var. names.
+    value_columns = pd.Series(value_columns.sort_values().reset_index(drop=True))  # Sort and reset index.
+    int_to_period_dictionary = value_columns.str.replace(f"_{analysis}", "", regex=False).to_dict()
+    period_to_int_dictionary = {v: k for k, v in list(int_to_period_dictionary.items())}
+    return value_columns.tolist(), period_to_int_dictionary, int_to_period_dictionary
+
+
+def convert_weekly_panel_to_biweekly_panel(df: pd.DataFrame, analyses: Union[List[str], str]):
+    if isinstance(analyses, str):  # If user passes string instead of list of string, create a list.
+        analyses = [analyses]
+    for analysis in analyses:
+        weekly_value_vars_crime, _, _ = get_value_variable_names(df, analysis)
+        for i, value_var in enumerate(weekly_value_vars_crime):
+            # If the index of the current week is odd or if we are at the last week in the panel...
+            if i % 2 == 1:
+                # Drop odd-index column from panel as its crime counts have been subsumed into previous week.
+                df = df.drop(columns=value_var)
+                # Update dictionary so that we can replace file week with the previous week.
+                df.loc[:, 'file_week'] = df['file_week'].replace(value_var.replace(f"_{analysis}", ""),
+                                                                 weekly_value_vars_crime[i - 1].replace(f"_{analysis}", ""))
+                continue
+            if i == len(weekly_value_vars_crime) - 1:
+                # Drop column corresponding to the last week of the panel from the dataset.
+                df = df.drop(columns=value_var)
+                # Drop rows with this week as their file_week.
+                df = df.loc[df['file_week'] != value_var.replace(f"_{analysis}", ""), :]
+                continue
+
+            # If we are neither at an odd index week nor at the last week in the panel, sum current week's crime counts with next week's crime counts.
+            df.loc[:, value_var] = df.loc[:, value_var] + df.loc[:, weekly_value_vars_crime[i + 1]]
[…]

### 2023-04-02 output/group_0_crimes_100m/tables/balance_table.tex
edited merge script

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_100m & 7.20 & 0.54 & 0.04 & -0.05 & 0.83 \\
- & pre_treatment_change_in_group_2_crimes_100m & 0.03 & -0.03 & 0.13 & -0.00 & 0.95 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_4_crimes_100m & 1.67 & -0.05 & 0.74 & -0.07 & 0.62 \\
+ & pre_treatment_change_in_group_4_crimes_100m & -0.02 & -0.00 & 0.87 & 0.00 & 1.00 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.00 & 0.68 \\
- & med_hhinc2016 & 48,035.65 & 1,312.56 & 0.12 & -429.96 & 0.60 \\
- & poor_share2010 & 0.27 & -0.00 & 0.53 & -0.00 & 0.57 \\
- & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -185.35 & 0.65 \\
+\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.01 & 0.11 \\
+ & job_density_2013 & 16,069.14 & 926.91 & 0.52 & -234.26 & 0.87 \\
+ & med_hhinc2016 & 48,035.65 & 1,312.56 & 0.12 & -1,185.57 & 0.00 \\
 \cline{1-7}
-\multirow[c]{2}{3cm}{\textit{Panel D}} & isEntityD & 0.01 & -0.01 & 0.01 & -0.00 & 0.90 \\
- & isEntityP & 0.81 & -0.06 & 0.00 & -0.01 & 0.30 \\
+\textit{Panel D} & isEntityP & 0.81 & -0.06 & 0.00 & -0.05 & 0.00 \\
 \cline{1-7}

### 2023-04-02 output/group_0_crimes_100m/tables/pre_treatment_covariate_tests.tex
edited merge script

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_100m & 0.00 & 0.04 \\
- & pre_treatment_change_in_group_2_crimes_100m & 0.00 & 0.13 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_100m & 0.00 & 0.74 \\
+ & pre_treatment_change_in_group_4_crimes_100m & 0.00 & 0.87 \\
 \cline{1-4}
 \multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.78 \\
- & job_density_2013 & 0.75 & 0.52 \\
+ & job_density_2013 & 0.00 & 0.52 \\
  & med_hhinc2016 & 0.00 & 0.12 \\
- & poor_share2010 & 0.03 & 0.53 \\
- & popdensity2010 & 0.00 & 0.01 \\
+ & poor_share2010 & 0.24 & 0.53 \\
+ & popdensity2010 & 0.18 & 0.01 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.28 & 0.00 \\
- & no_cause & 0.45 & 0.90 \\
- & non_payment & 0.22 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.21 & 0.00 \\
+ & no_cause & 0.52 & 0.90 \\
+ & non_payment & 0.16 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.28 & 0.00 \\
- & hasAttyP & 0.21 & 0.00 \\
- & isEntityD & 0.00 & 0.01 \\
- & isEntityP & 0.01 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.99 & 0.00 \\
+ & hasAttyP & 0.26 & 0.00 \\
+ & isEntityD & 0.63 & 0.01 \\
+ & isEntityP & 0.03 & 0.00 \\
 \cline{1-4}

### 2023-04-02 output/group_3_crimes_50m/tables/pre_treatment_covariate_tests.tex

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_50m & 0.00 & 0.05 \\
 & pre_treatment_change_in_group_1_crimes_50m & 0.00 & 0.84 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.24 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.01 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.37 & 0.00 \\
 & no_cause & 0.07 & 0.95 \\
 & non_payment & 0.86 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.03 & 0.00 \\
 & hasAttyP & 0.64 & 0.00 \\
 & isEntityD & 0.25 & 0.06 \\
 & isEntityP & 0.15 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-02 output/group_4_crimes_50m/tables/balance_table.tex

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_1_crimes_50m & 1.74 & 0.21 & 0.05 & 0.02 & 0.86 \\
 & pre_treatment_change_in_group_1_crimes_50m & 0.01 & -0.00 & 0.84 & 0.00 & 0.99 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 149.47 & 0.92 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 640.26 & 0.47 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.43 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 282.08 & 0.50 \\
\cline{1-7}
\textit{Panel D} & hasAttyD & 0.07 & -0.03 & 0.00 & 0.00 & 0.75 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-03 output/group_0_crimes_100m/tables/balance_table.tex
rann aalysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_4_crimes_100m & 1.67 & -0.05 & 0.74 & -0.07 & 0.62 \\
- & pre_treatment_change_in_group_4_crimes_100m & -0.02 & -0.00 & 0.87 & 0.00 & 1.00 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_0_crimes_100m & 69.43 & 5.31 & 0.03 & -0.53 & 0.82 \\
+ & pre_treatment_change_in_group_0_crimes_100m & -0.23 & 0.00 & 0.96 & 0.00 & 0.98 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.01 & 0.11 \\
- & job_density_2013 & 16,069.14 & 926.91 & 0.52 & -234.26 & 0.87 \\
- & med_hhinc2016 & 48,035.65 & 1,312.56 & 0.12 & -1,185.57 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.75 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -133.88 & 0.93 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -373.19 & 0.67 \\
+ & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.69 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -179.26 & 0.69 \\
 \cline{1-7}
-\textit{Panel D} & isEntityP & 0.81 & -0.06 & 0.00 & -0.05 & 0.00 \\
+\textit{Panel C} & non_payment & 0.77 & -0.08 & 0.00 & -0.01 & 0.61 \\
+\cline{1-7}
+\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.01 & 0.52 \\
+ & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.98 \\
+ & isEntityP & 0.81 & -0.07 & 0.00 & -0.01 & 0.59 \\
 \cline{1-7}

### 2023-04-03 output/group_0_crimes_100m/tables/pre_treatment_covariate_tests.tex
rann aalysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_100m & 0.00 & 0.74 \\
- & pre_treatment_change_in_group_4_crimes_100m & 0.00 & 0.87 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_100m & 0.00 & 0.03 \\
+ & pre_treatment_change_in_group_0_crimes_100m & 0.01 & 0.96 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.78 \\
- & job_density_2013 & 0.00 & 0.52 \\
- & med_hhinc2016 & 0.00 & 0.12 \\
- & poor_share2010 & 0.24 & 0.53 \\
- & popdensity2010 & 0.18 & 0.01 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
+ & job_density_2013 & 0.00 & 0.10 \\
+ & med_hhinc2016 & 0.00 & 0.05 \\
+ & poor_share2010 & 0.00 & 0.96 \\
+ & popdensity2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.21 & 0.00 \\
- & no_cause & 0.52 & 0.90 \\
- & non_payment & 0.16 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.33 & 0.00 \\
+ & no_cause & 0.09 & 0.95 \\
+ & non_payment & 0.04 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.99 & 0.00 \\
- & hasAttyP & 0.26 & 0.00 \\
- & isEntityD & 0.63 & 0.01 \\
- & isEntityP & 0.03 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.62 & 0.00 \\
+ & hasAttyP & 0.00 & 0.00 \\
+ & isEntityD & 0.00 & 0.06 \\
+ & isEntityP & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-03 output/group_0_crimes_500m/tables/pre_treatment_covariate_tests.tex
rann aalysis

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_500m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_0_crimes_500m & 0.00 & 0.30 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.21 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.21 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.47 & 0.00 \\
 & no_cause & 0.01 & 0.95 \\
 & non_payment & 0.03 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.13 & 0.00 \\
 & hasAttyP & 0.36 & 0.00 \\
 & isEntityD & 0.12 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-03 output/group_0_crimes_50m/tables/balance_table.tex
rann aalysis

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_0_crimes_50m & 18.99 & 1.54 & 0.09 & -0.25 & 0.78 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.55 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -205.80 & 0.89 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.44 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -311.00 & 0.44 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.01 & 0.20 \\
 & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.93 \\
 & isEntityP & 0.81 & -0.07 & 0.00 & -0.01 & 0.23 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-03 output/group_0_crimes_50m/tables/pre_treatment_covariate_tests.tex
rann aalysis

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_50m & 0.00 & 0.09 \\
 & pre_treatment_change_in_group_0_crimes_50m & 0.09 & 0.35 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.75 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.31 & 0.00 \\
 & no_cause & 0.41 & 0.95 \\
 & non_payment & 0.14 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.23 & 0.00 \\
 & hasAttyP & 0.03 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-03 output/group_1_crimes_50m/tables/balance_table.tex
rann aalysis

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_1_crimes_50m & 1.72 & 0.20 & 0.05 & 0.02 & 0.86 \\
 & pre_treatment_change_in_group_1_crimes_50m & 0.01 & -0.00 & 0.84 & 0.00 & 0.99 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 149.36 & 0.92 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 640.38 & 0.47 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.43 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 282.08 & 0.50 \\
\cline{1-7}
\textit{Panel D} & hasAttyD & 0.07 & -0.03 & 0.00 & 0.00 & 0.75 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-03 output/group_1_crimes_50m/tables/pre_treatment_covariate_tests.tex
rann aalysis

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_50m & 0.00 & 0.05 \\
 & pre_treatment_change_in_group_1_crimes_50m & 0.00 & 0.84 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.34 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.02 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.29 & 0.00 \\
 & no_cause & 0.08 & 0.95 \\
 & non_payment & 0.99 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.04 & 0.00 \\
 & hasAttyP & 0.55 & 0.00 \\
 & isEntityD & 0.27 & 0.06 \\
 & isEntityP & 0.19 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-03 output/group_2_crimes_1000m/tables/balance_table.tex
rann aalysis

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_1000m & 140.20 & 7.77 & 0.14 & -2.13 & 0.68 \\
 & pre_treatment_change_in_group_2_crimes_1000m & -1.01 & 0.17 & 0.13 & 0.02 & 0.88 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.01 & 0.52 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -253.43 & 0.87 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -743.41 & 0.39 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.41 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel C}} & no_cause & 0.05 & 0.00 & 0.95 & -0.00 & 0.92 \\
 & non_payment & 0.77 & -0.08 & 0.00 & -0.01 & 0.29 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.01 & 0.20 \\
 & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.95 \\
 & isEntityP & 0.81 & -0.07 & 0.00 & -0.01 & 0.27 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-03 output/group_2_crimes_1000m/tables/pre_treatment_covariate_tests.tex
rann aalysis

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_1000m & 0.00 & 0.14 \\
 & pre_treatment_change_in_group_2_crimes_1000m & 0.00 & 0.13 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.01 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.50 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.31 & 0.00 \\
 & no_cause & 0.00 & 0.95 \\
 & non_payment & 0.01 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.11 & 0.00 \\
 & hasAttyP & 0.01 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-03 output/group_2_crimes_50m/tables/balance_table.tex
rann aalysis

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_50m & 0.79 & 0.16 & 0.15 & -0.02 & 0.77 \\
 & pre_treatment_change_in_group_2_crimes_50m & -0.01 & 0.00 & 0.67 & -0.00 & 0.91 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.62 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -279.43 & 0.79 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 472.04 & 0.52 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-03 output/group_2_crimes_50m/tables/pre_treatment_covariate_tests.tex
rann aalysis

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_50m & 0.00 & 0.15 \\
 & pre_treatment_change_in_group_2_crimes_50m & 0.00 & 0.67 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.04 & 0.05 \\
 & poor_share2010 & 0.53 & 0.96 \\
 & popdensity2010 & 0.46 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.72 & 0.00 \\
 & no_cause & 0.25 & 0.95 \\
 & non_payment & 0.72 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.61 & 0.00 \\
 & hasAttyP & 0.39 & 0.00 \\
 & isEntityD & 0.45 & 0.06 \\
 & isEntityP & 0.13 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-03 output/group_3_crimes_1000m/tables/balance_table.tex
rann aalysis

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_3_crimes_1000m & 59.18 & 3.58 & 0.18 & 0.65 & 0.80 \\
 & pre_treatment_change_in_group_3_crimes_1000m & -0.67 & -0.05 & 0.50 & -0.01 & 0.93 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.60 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 113.69 & 0.94 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 593.73 & 0.49 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.44 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 253.66 & 0.52 \\
\cline{1-7}
\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.87 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-03 output/group_3_crimes_1000m/tables/pre_treatment_covariate_tests.tex
rann aalysis

--- 2023-04-03 output/group_0_crimes_100m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_100m & 0.00 & 0.03 \\
- & pre_treatment_change_in_group_0_crimes_100m & 0.01 & 0.96 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_1000m & 0.00 & 0.18 \\
+ & pre_treatment_change_in_group_3_crimes_1000m & 0.00 & 0.50 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.33 & 0.00 \\
- & no_cause & 0.09 & 0.95 \\
- & non_payment & 0.04 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.45 & 0.00 \\
+ & no_cause & 0.16 & 0.95 \\
+ & non_payment & 0.14 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.62 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.67 & 0.00 \\
+ & hasAttyP & 0.13 & 0.00 \\
  & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+ & isEntityP & 0.53 & 0.00 \\
 \cline{1-4}

### 2023-04-03 output/group_3_crimes_100m/tables/balance_table.tex
rann aalysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_group_3_crimes_100m & 0.45 & 0.05 & 0.08 & -0.00 & 0.95 \\
- & pre_treatment_change_in_group_3_crimes_100m & 0.06 & -0.03 & 0.45 & -0.00 & 0.99 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_3_crimes_100m & 0.95 & 0.07 & 0.67 & 0.00 & 1.00 \\
+ & pre_treatment_change_in_group_3_crimes_100m & -0.02 & -0.01 & 0.23 & 0.00 & 0.73 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.00 & 0.86 \\
- & job_density_2013 & 16,069.14 & 926.91 & 0.52 & -65.36 & 0.96 \\
- & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -94.31 & 0.83 \\
-\cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel C}} & for_cause & 0.17 & 0.07 & 0.00 & -0.00 & 0.96 \\
- & no_cause & 0.05 & -0.00 & 0.90 & -0.00 & 0.98 \\
- & non_payment & 0.78 & -0.07 & 0.00 & -0.00 & 0.75 \\
-\cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.00 & 0.69 \\
- & isEntityD & 0.01 & -0.01 & 0.01 & -0.00 & 0.98 \\
- & isEntityP & 0.81 & -0.06 & 0.00 & -0.00 & 0.72 \\
+\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.63 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 441.33 & 0.52 \\
+ & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.28 \\
 \cline{1-7}

### 2023-04-03 output/group_3_crimes_100m/tables/pre_treatment_covariate_tests.tex
rann aalysis

@@
 \\
- &  & Investigations Within 100m, Oct. 2022 & Plaintiff Victory \\
+ &  &  &  \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_3_crimes_100m & 0.00 & 0.08 \\
- & pre_treatment_change_in_group_3_crimes_100m & 0.05 & 0.45 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_100m & 0.00 & 0.67 \\
+ & pre_treatment_change_in_group_3_crimes_100m & 0.00 & 0.23 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.78 \\
- & job_density_2013 & 0.00 & 0.52 \\
- & med_hhinc2016 & 0.19 & 0.12 \\
- & poor_share2010 & 0.45 & 0.53 \\
- & popdensity2010 & 0.00 & 0.01 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.03 & 0.22 \\
+ & job_density_2013 & 0.06 & 0.10 \\
+ & med_hhinc2016 & 0.01 & 0.05 \\
+ & poor_share2010 & 0.00 & 0.96 \\
+ & popdensity2010 & 0.75 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.00 & 0.00 \\
- & no_cause & 0.01 & 0.90 \\
- & non_payment & 0.00 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.30 & 0.00 \\
+ & no_cause & 0.28 & 0.95 \\
+ & non_payment & 0.97 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.80 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
- & isEntityD & 0.00 & 0.01 \\
- & isEntityP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.24 & 0.00 \\
+ & hasAttyP & 0.43 & 0.00 \\
+ & isEntityD & 0.82 & 0.06 \\
+ & isEntityP & 0.17 & 0.00 \\
 \cline{1-4}

### 2023-04-03 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
rann aalysis

--- 2023-04-03 output/group_0_crimes_100m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_100m & 0.00 & 0.03 \\
- & pre_treatment_change_in_group_0_crimes_100m & 0.01 & 0.96 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.87 \\
+ & pre_treatment_change_in_group_3_crimes_500m & 0.00 & 0.67 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.33 & 0.00 \\
- & no_cause & 0.09 & 0.95 \\
- & non_payment & 0.04 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.22 & 0.00 \\
+ & no_cause & 0.28 & 0.95 \\
+ & non_payment & 0.09 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.62 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.84 & 0.00 \\
+ & hasAttyP & 0.07 & 0.00 \\
  & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+ & isEntityP & 0.11 & 0.00 \\
 \cline{1-4}

### 2023-04-03 output/group_3_crimes_50m/tables/balance_table.tex
rann aalysis

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_3_crimes_50m & 0.24 & 0.07 & 0.01 & -0.01 & 0.44 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.01 & 0.08 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -0.91 & 1.00 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,927.86 & 0.03 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 706.17 & 0.11 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-03 output/group_3_crimes_50m/tables/pre_treatment_covariate_tests.tex
rann aalysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_50m & 0.00 & 0.05 \\
- & pre_treatment_change_in_group_1_crimes_50m & 0.00 & 0.84 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_50m & 0.02 & 0.01 \\
+ & pre_treatment_change_in_group_3_crimes_50m & 0.19 & 0.41 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.24 & 0.22 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
  & job_density_2013 & 0.00 & 0.10 \\
  & med_hhinc2016 & 0.01 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
+ & poor_share2010 & 0.98 & 0.96 \\
  & popdensity2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.37 & 0.00 \\
- & no_cause & 0.07 & 0.95 \\
- & non_payment & 0.86 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.71 & 0.00 \\
+ & no_cause & 0.29 & 0.95 \\
+ & non_payment & 0.61 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.03 & 0.00 \\
- & hasAttyP & 0.64 & 0.00 \\
- & isEntityD & 0.25 & 0.06 \\
- & isEntityP & 0.15 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.12 & 0.00 \\
+ & hasAttyP & 0.30 & 0.00 \\
+ & isEntityD & 0.43 & 0.06 \\
+ & isEntityP & 0.49 & 0.00 \\
 \cline{1-4}

### 2023-04-03 output/group_4_crimes_1000m/tables/pre_treatment_covariate_tests.tex
rann aalysis

--- 2023-04-03 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.87 \\
- & pre_treatment_change_in_group_3_crimes_500m & 0.00 & 0.67 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_1000m & 0.00 & 0.00 \\
+ & pre_treatment_change_in_group_4_crimes_1000m & 0.00 & 0.03 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.22 & 0.00 \\
- & no_cause & 0.28 & 0.95 \\
- & non_payment & 0.09 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.16 & 0.00 \\
+ & no_cause & 0.61 & 0.95 \\
+ & non_payment & 0.18 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.84 & 0.00 \\
- & hasAttyP & 0.07 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.26 & 0.00 \\
+ & hasAttyP & 0.00 & 0.00 \\
  & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.11 & 0.00 \\
+ & isEntityP & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-03 output/group_4_crimes_100m/tables/balance_table.tex
rann aalysis

--- 2023-04-03 output/group_3_crimes_50m/tables/balance_table.tex
@@
 \midrule
-\textit{Panel A} & total_twenty_seventeen_group_3_crimes_50m & 0.24 & 0.07 & 0.01 & -0.01 & 0.44 \\
-\cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.01 & 0.08 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -0.91 & 1.00 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,927.86 & 0.03 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 706.17 & 0.11 \\
+\textit{Panel A} & total_twenty_seventeen_group_4_crimes_100m & 0.06 & 0.02 & 0.01 & -0.00 & 0.88 \\
 \cline{1-7}

### 2023-04-03 output/group_4_crimes_100m/tables/pre_treatment_covariate_tests.tex
rann aalysis

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_100m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_4_crimes_100m & 1.00 & 0.00 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.15 & 0.22 \\
 & job_density_2013 & 0.51 & 0.10 \\
 & med_hhinc2016 & 0.05 & 0.05 \\
 & poor_share2010 & 0.14 & 0.96 \\
 & popdensity2010 & 0.52 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.86 & 0.00 \\
 & no_cause & 0.92 & 0.95 \\
 & non_payment & 0.83 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.89 & 0.00 \\
 & hasAttyP & 0.88 & 0.00 \\
 & isEntityD & 0.95 & 0.06 \\
 & isEntityP & 0.84 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-03 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
rann aalysis

--- 2023-04-03 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.87 \\
- & pre_treatment_change_in_group_3_crimes_500m & 0.00 & 0.67 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.00 \\
+ & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.48 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.22 & 0.00 \\
- & no_cause & 0.28 & 0.95 \\
- & non_payment & 0.09 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.35 & 0.00 \\
+ & no_cause & 0.67 & 0.95 \\
+ & non_payment & 0.28 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.84 & 0.00 \\
- & hasAttyP & 0.07 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.11 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.78 & 0.00 \\
+ & hasAttyP & 0.51 & 0.00 \\
+ & isEntityD & 0.28 & 0.06 \\
+ & isEntityP & 0.92 & 0.00 \\
 \cline{1-4}

### 2023-04-03 output/group_4_crimes_50m/tables/balance_table.tex
rann aalysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_1_crimes_50m & 1.74 & 0.21 & 0.05 & 0.02 & 0.86 \\
- & pre_treatment_change_in_group_1_crimes_50m & 0.01 & -0.00 & 0.84 & 0.00 & 0.99 \\
+\textit{Panel A} & total_twenty_seventeen_group_4_crimes_50m & 0.02 & 0.01 & 0.01 & -0.00 & 0.43 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 149.47 & 0.92 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 640.26 & 0.47 \\
- & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.43 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 282.08 & 0.50 \\
-\cline{1-7}
-\textit{Panel D} & hasAttyD & 0.07 & -0.03 & 0.00 & 0.00 & 0.75 \\
+\textit{Panel B} & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 757.12 & 0.37 \\
 \cline{1-7}

### 2023-04-03 output/group_4_crimes_50m/tables/pre_treatment_covariate_tests.tex
rann aalysis

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_50m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_4_crimes_50m & 0.99 & 0.17 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.28 & 0.22 \\
 & job_density_2013 & 0.40 & 0.10 \\
 & med_hhinc2016 & 0.03 & 0.05 \\
 & poor_share2010 & 0.06 & 0.96 \\
 & popdensity2010 & 0.43 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.82 & 0.00 \\
 & no_cause & 0.90 & 0.95 \\
 & non_payment & 0.78 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.86 & 0.00 \\
 & hasAttyP & 0.84 & 0.00 \\
 & isEntityD & 0.93 & 0.06 \\
 & isEntityP & 0.80 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-03 src/02_analysis/constants.py

@@ -1,15 +1,22 @@
 class Variables:
-<<<<<<< HEAD
-    outcomes = ['group_0_crimes_500m',
-                'group_1_crimes_500m',
-                'group_2_crimes_500m', 
-                'group_3_crimes_500m',
-                'group_4_crimes_500m']
-=======
     outcomes = ['group_0_crimes_50m',
                 'group_1_crimes_50m',
                 'group_2_crimes_50m',
                 'group_3_crimes_50m',
                 'group_4_crimes_50m',
-                'group_5_crimes_50m']
->>>>>>> 680591684e02dfd7cfa4c25bbe88df310844c4e9
+                'group_0_crimes_100m',
+                'group_1_crimes_100m',
+                'group_2_crimes_100m', 
+                'group_3_crimes_100m',
+                'group_4_crimes_100m',
+                'group_0_crimes_500m',
+                'group_1_crimes_500m',
+                'group_2_crimes_500m', 
+                'group_3_crimes_500m',
+                'group_4_crimes_500m',
+                'group_0_crimes_1000m',
+                'group_1_crimes_1000m',
+                'group_2_crimes_1000m', 
+                'group_3_crimes_1000m',
+                'group_4_crimes_1000m']
+

### 2023-04-03 src/02_analysis/figure_utilities.py

@@ -39,7 +39,8 @@ def aggregate_by_event_time_and_plot(att_gt,
     y_lower = results_df['lower']
     ax.set_ylabel("ATT")
     ax.set_title(title)
-    plot_labeled_vline(ax, x=0, text="Treatment Month", color='black', linestyle='-',
+    ax.set_xlabel("Two Week Period Relative to Treatment")
+    plot_labeled_vline(ax, x=0, text="Treatment", color='black', linestyle='-',
                                         text_y_location_normalized=0.95)
     plot_scatter_with_shaded_errors(ax,
                                                      x.values,
@@ -52,10 +53,7 @@ def aggregate_by_event_time_and_plot(att_gt,
                                                      edge_style='--',
                                                      zorder=1)
     plot_labeled_hline(ax, y=0, text="", color='black', linestyle='-', zorder=6)
-<<<<<<< HEAD
-=======
 
->>>>>>> 680591684e02dfd7cfa4c25bbe88df310844c4e9
     plt.show()
     save_figure_and_close(fig, join(output_folder, filename))
 
@@ -73,6 +71,7 @@ def aggregate_by_time_and_plot(att_gt, int_to_month_dictionary: dict, output_fol
     y_lower = results_df.iloc[:, 2]
     ax.set_xlabel("Month")
     ax.set_ylabel("ATT")
+    ax.set_xlabel("Two Week Period Relative to Treatment")
     ax.set_title(title)
     plot_labeled_vline(ax, x=results_df.index.tolist()[0], text="Earliest Treatment Date in Sample",
                                         color='black', linestyle='-',
@@ -88,7 +87,6 @@ def aggregate_by_time_and_plot(att_gt, int_to_month_dictionary: dict, output_fol
                                                      edge_style='--',
                                                      zorder=1)
     plot_labeled_hline(ax, y=0, text="", color='black', linestyle='-')
-    ax.set_xticks(range(0, len(x), 12))
     plt.show()
     save_figure_and_close(fig, join(output_folder, filename))
 

### 2023-04-06 output/group_0_crimes_1000m/tables/balance_table.tex
produced all figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_0_crimes_1000m & 4,045.37 & 166.49 & 0.04 & -69.57 & 0.38 \\
 & pre_treatment_change_in_group_0_crimes_1000m & -25.13 & -2.31 & 0.02 & 0.42 & 0.66 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.01 & 0.47 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -282.06 & 0.85 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -836.51 & 0.34 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.36 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -396.09 & 0.37 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel C}} & no_cause & 0.05 & 0.00 & 0.95 & -0.00 & 0.91 \\
 & non_payment & 0.77 & -0.08 & 0.00 & -0.01 & 0.26 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyD & 0.07 & -0.03 & 0.00 & -0.00 & 0.88 \\
 & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.94 \\
 & isEntityP & 0.81 & -0.07 & 0.00 & -0.01 & 0.23 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-06 output/group_0_crimes_1000m/tables/pre_treatment_covariate_tests.tex
produced all figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_1000m & 0.00 & 0.04 \\
 & pre_treatment_change_in_group_0_crimes_1000m & 0.00 & 0.02 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.02 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.11 & 0.00 \\
 & no_cause & 0.00 & 0.95 \\
 & non_payment & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.01 & 0.00 \\
 & hasAttyP & 0.69 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.05 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-06 output/group_0_crimes_100m/tables/balance_table.tex
produced all figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_0_crimes_100m & 69.43 & 5.31 & 0.03 & -0.53 & 0.82 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_0_crimes_100m & 69.20 & 5.24 & 0.03 & -0.53 & 0.82 \\
  & pre_treatment_change_in_group_0_crimes_100m & -0.23 & 0.00 & 0.96 & 0.00 & 0.98 \\
@@
 \multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.75 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -133.88 & 0.93 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -373.19 & 0.67 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -133.94 & 0.93 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -374.02 & 0.67 \\
  & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.69 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -179.26 & 0.69 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -179.58 & 0.69 \\
 \cline{1-7}

### 2023-04-06 output/group_0_crimes_100m/tables/pre_treatment_covariate_tests.tex
produced all figures

@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.33 & 0.00 \\
- & no_cause & 0.09 & 0.95 \\
- & non_payment & 0.04 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.27 & 0.00 \\
+ & no_cause & 0.12 & 0.95 \\
+ & non_payment & 0.03 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.62 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.65 & 0.00 \\
  & hasAttyP & 0.00 & 0.00 \\

### 2023-04-06 output/group_0_crimes_500m/tables/pre_treatment_covariate_tests.tex
produced all figures

@@
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.21 & 0.22 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.20 & 0.22 \\
  & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.21 & 0.05 \\
+ & med_hhinc2016 & 0.22 & 0.05 \\
  & poor_share2010 & 0.00 & 0.96 \\
@@
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.13 & 0.00 \\
- & hasAttyP & 0.36 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.12 & 0.00 \\
+ & hasAttyP & 0.37 & 0.00 \\
  & isEntityD & 0.12 & 0.06 \\

### 2023-04-06 output/group_0_crimes_50m/tables/balance_table.tex
produced all figures

@@
 \midrule
-\textit{Panel A} & total_twenty_seventeen_group_0_crimes_50m & 18.99 & 1.54 & 0.09 & -0.25 & 0.78 \\
+\textit{Panel A} & total_twenty_seventeen_group_0_crimes_50m & 19.08 & 1.56 & 0.09 & -0.25 & 0.78 \\
 \cline{1-7}
 \multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.55 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -205.80 & 0.89 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -205.84 & 0.89 \\
  & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.44 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -311.00 & 0.44 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -311.10 & 0.44 \\
 \cline{1-7}

### 2023-04-06 output/group_0_crimes_50m/tables/pre_treatment_covariate_tests.tex
produced all figures

@@
 \multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_50m & 0.00 & 0.09 \\
- & pre_treatment_change_in_group_0_crimes_50m & 0.09 & 0.35 \\
+ & pre_treatment_change_in_group_0_crimes_50m & 0.11 & 0.44 \\
 \cline{1-4}
@@
  & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.75 & 0.05 \\
+ & med_hhinc2016 & 0.83 & 0.05 \\
  & poor_share2010 & 0.00 & 0.96 \\
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.31 & 0.00 \\
- & no_cause & 0.41 & 0.95 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.32 & 0.00 \\
+ & no_cause & 0.40 & 0.95 \\
  & non_payment & 0.14 & 0.00 \\

### 2023-04-06 output/group_1_crimes_1000m/tables/pre_treatment_covariate_tests.tex
produced all figures

--- 2023-04-03 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.00 \\
- & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.48 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_1000m & 0.00 & 0.08 \\
+ & pre_treatment_change_in_group_1_crimes_1000m & 0.05 & 0.07 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.35 & 0.00 \\
- & no_cause & 0.67 & 0.95 \\
- & non_payment & 0.28 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.23 & 0.00 \\
+ & no_cause & 0.01 & 0.95 \\
+ & non_payment & 0.01 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.78 & 0.00 \\
- & hasAttyP & 0.51 & 0.00 \\
- & isEntityD & 0.28 & 0.06 \\
- & isEntityP & 0.92 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.00 & 0.00 \\
+ & hasAttyP & 0.00 & 0.00 \\
+ & isEntityD & 0.00 & 0.06 \\
+ & isEntityP & 0.27 & 0.00 \\
 \cline{1-4}

### 2023-04-06 output/group_1_crimes_100m/tables/balance_table.tex
produced all figures

--- 2023-03-16 output/group_1_crimes_100m/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_group_1_crimes_100m & 0.41 & 0.07 & 0.01 & -0.00 & 0.85 \\
- & pre_treatment_change_in_group_1_crimes_100m & 0.04 & -0.02 & 0.56 & -0.00 & 0.91 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_1_crimes_100m & 6.12 & 0.63 & 0.02 & 0.01 & 0.98 \\
+ & pre_treatment_change_in_group_1_crimes_100m & 0.04 & 0.01 & 0.69 & 0.00 & 1.00 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.01 & 0.15 \\
- & job_density_2013 & 16,069.14 & 926.91 & 0.52 & -413.06 & 0.77 \\
- & poor_share2010 & 0.27 & -0.00 & 0.53 & -0.01 & 0.05 \\
- & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -607.79 & 0.07 \\
+\multirow[c]{4}{3cm}{\textit{Panel B}} & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 18.32 & 0.99 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 67.08 & 0.94 \\
+ & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.94 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 30.40 & 0.95 \\
 \cline{1-7}
-\textit{Panel D} & isEntityP & 0.81 & -0.06 & 0.00 & -0.04 & 0.00 \\
+\multirow[c]{2}{3cm}{\textit{Panel D}} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.99 \\
+ & isEntityP & 0.81 & -0.07 & 0.00 & 0.00 & 0.88 \\
 \cline{1-7}

### 2023-04-06 output/group_1_crimes_100m/tables/pre_treatment_covariate_tests.tex
produced all figures

@@
 \\
- &  & Assault-Related Crime Incidents Within 100m, Oct. 2022 & Plaintiff Victory \\
+ &  &  &  \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_1_crimes_100m & 0.00 & 0.00 \\
- & pre_treatment_change_in_group_1_crimes_100m & 0.00 & 0.44 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_100m & 0.00 & 0.02 \\
+ & pre_treatment_change_in_group_1_crimes_100m & 0.00 & 0.69 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.78 \\
- & job_density_2013 & 0.00 & 0.52 \\
- & med_hhinc2016 & 0.45 & 0.12 \\
- & poor_share2010 & 0.00 & 0.53 \\
- & popdensity2010 & 0.00 & 0.01 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.55 & 0.22 \\
+ & job_density_2013 & 0.00 & 0.10 \\
+ & med_hhinc2016 & 0.00 & 0.05 \\
+ & poor_share2010 & 0.00 & 0.96 \\
+ & popdensity2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.06 & 0.00 \\
- & no_cause & 0.22 & 0.90 \\
- & non_payment & 0.01 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.31 & 0.00 \\
+ & no_cause & 0.40 & 0.95 \\
+ & non_payment & 0.81 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.26 & 0.00 \\
- & hasAttyP & 0.27 & 0.00 \\
- & isEntityD & 0.31 & 0.01 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.07 & 0.00 \\
+ & hasAttyP & 0.53 & 0.00 \\
+ & isEntityD & 0.02 & 0.06 \\
  & isEntityP & 0.00 & 0.00 \\

### 2023-04-06 output/group_1_crimes_500m/tables/balance_table.tex
produced all figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_1_crimes_500m & 95.93 & 5.50 & 0.02 & 1.21 & 0.57 \\
 & pre_treatment_change_in_group_1_crimes_500m & -0.07 & -0.09 & 0.36 & 0.00 & 0.97 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.56 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 131.16 & 0.93 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 666.70 & 0.45 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.39 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 285.95 & 0.48 \\
\cline{1-7}
\textit{Panel C} & no_cause & 0.05 & 0.00 & 0.95 & 0.00 & 0.92 \\
\cline{1-7}
\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.86 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-06 output/group_1_crimes_500m/tables/pre_treatment_covariate_tests.tex
produced all figures

--- 2023-04-03 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.00 \\
- & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.48 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_500m & 0.00 & 0.02 \\
+ & pre_treatment_change_in_group_1_crimes_500m & 0.00 & 0.36 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.35 & 0.00 \\
- & no_cause & 0.67 & 0.95 \\
- & non_payment & 0.28 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.56 & 0.00 \\
+ & no_cause & 0.02 & 0.95 \\
+ & non_payment & 0.06 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.78 & 0.00 \\
- & hasAttyP & 0.51 & 0.00 \\
- & isEntityD & 0.28 & 0.06 \\
- & isEntityP & 0.92 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.05 & 0.00 \\
+ & hasAttyP & 0.52 & 0.00 \\
+ & isEntityD & 0.00 & 0.06 \\
+ & isEntityP & 0.25 & 0.00 \\
 \cline{1-4}

### 2023-04-06 output/group_1_crimes_50m/tables/balance_table.tex
produced all figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_1_crimes_50m & 1.72 & 0.20 & 0.05 & 0.02 & 0.86 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_1_crimes_50m & 1.72 & 0.21 & 0.05 & 0.02 & 0.86 \\
  & pre_treatment_change_in_group_1_crimes_50m & 0.01 & -0.00 & 0.84 & 0.00 & 0.99 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 149.36 & 0.92 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 640.38 & 0.47 \\
+\multirow[c]{4}{3cm}{\textit{Panel B}} & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 149.61 & 0.92 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 640.49 & 0.47 \\
  & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.43 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 282.08 & 0.50 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 282.20 & 0.50 \\
 \cline{1-7}

### 2023-04-06 output/group_1_crimes_50m/tables/pre_treatment_covariate_tests.tex
produced all figures

@@
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.34 & 0.22 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.29 & 0.22 \\
  & job_density_2013 & 0.00 & 0.10 \\
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.29 & 0.00 \\
- & no_cause & 0.08 & 0.95 \\
- & non_payment & 0.99 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.34 & 0.00 \\
+ & no_cause & 0.07 & 0.95 \\
+ & non_payment & 0.90 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.04 & 0.00 \\
- & hasAttyP & 0.55 & 0.00 \\
- & isEntityD & 0.27 & 0.06 \\
- & isEntityP & 0.19 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.03 & 0.00 \\
+ & hasAttyP & 0.61 & 0.00 \\
+ & isEntityD & 0.26 & 0.06 \\
+ & isEntityP & 0.16 & 0.00 \\
 \cline{1-4}

### 2023-04-06 output/group_2_crimes_1000m/tables/balance_table.tex
produced all figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_1000m & 140.20 & 7.77 & 0.14 & -2.13 & 0.68 \\
- & pre_treatment_change_in_group_2_crimes_1000m & -1.01 & 0.17 & 0.13 & 0.02 & 0.88 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_1000m & 59.18 & 3.58 & 0.18 & 0.65 & 0.80 \\
+ & pre_treatment_change_in_group_2_crimes_1000m & -0.67 & -0.05 & 0.49 & -0.01 & 0.93 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.01 & 0.52 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -253.43 & 0.87 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -743.41 & 0.39 \\
- & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.41 \\
+\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.60 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 113.80 & 0.94 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 593.54 & 0.49 \\
+ & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.44 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 253.63 & 0.52 \\
 \cline{1-7}
-\multirow[c]{2}{3cm}{\textit{Panel C}} & no_cause & 0.05 & 0.00 & 0.95 & -0.00 & 0.92 \\
- & non_payment & 0.77 & -0.08 & 0.00 & -0.01 & 0.29 \\
-\cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.01 & 0.20 \\
- & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.95 \\
- & isEntityP & 0.81 & -0.07 & 0.00 & -0.01 & 0.27 \\
+\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.87 \\
 \cline{1-7}

### 2023-04-06 output/group_2_crimes_1000m/tables/pre_treatment_covariate_tests.tex
produced all figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_1000m & 0.00 & 0.14 \\
- & pre_treatment_change_in_group_2_crimes_1000m & 0.00 & 0.13 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_1000m & 0.00 & 0.18 \\
+ & pre_treatment_change_in_group_2_crimes_1000m & 0.00 & 0.49 \\
 \cline{1-4}
 \multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.01 & 0.10 \\
+ & job_density_2013 & 0.00 & 0.10 \\
  & med_hhinc2016 & 0.00 & 0.05 \\
  & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.50 & 0.00 \\
+ & popdensity2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.31 & 0.00 \\
- & no_cause & 0.00 & 0.95 \\
- & non_payment & 0.01 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.37 & 0.00 \\
+ & no_cause & 0.16 & 0.95 \\
+ & non_payment & 0.11 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.11 & 0.00 \\
- & hasAttyP & 0.01 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.66 & 0.00 \\
+ & hasAttyP & 0.14 & 0.00 \\
  & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+ & isEntityP & 0.54 & 0.00 \\
 \cline{1-4}

### 2023-04-06 output/group_2_crimes_100m/tables/balance_table.tex
produced all figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_100m & 0.96 & 0.08 & 0.64 & -0.00 & 0.99 \\
 & pre_treatment_change_in_group_2_crimes_100m & -0.02 & -0.01 & 0.23 & 0.00 & 0.73 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.64 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 435.35 & 0.52 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.27 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-06 output/group_2_crimes_100m/tables/pre_treatment_covariate_tests.tex
produced all figures

@@
 \\
- &  & Drug-Related Crime Incidents Within 100m, Oct. 2022 & Plaintiff Victory \\
+ &  &  &  \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_2_crimes_100m & nan & 0.34 \\
- & pre_treatment_change_in_group_2_crimes_100m & nan & 0.70 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_100m & 0.00 & 0.64 \\
+ & pre_treatment_change_in_group_2_crimes_100m & 0.00 & 0.23 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & nan & 0.78 \\
- & job_density_2013 & nan & 0.52 \\
- & med_hhinc2016 & nan & 0.12 \\
- & poor_share2010 & nan & 0.53 \\
- & popdensity2010 & nan & 0.01 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.02 & 0.22 \\
+ & job_density_2013 & 0.17 & 0.10 \\
+ & med_hhinc2016 & 0.00 & 0.05 \\
+ & poor_share2010 & 0.00 & 0.96 \\
+ & popdensity2010 & 0.79 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & nan & 0.00 \\
- & no_cause & nan & 0.90 \\
- & non_payment & nan & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.43 & 0.00 \\
+ & no_cause & 0.29 & 0.95 \\
+ & non_payment & 0.80 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & nan & 0.00 \\
- & hasAttyP & nan & 0.00 \\
- & isEntityD & nan & 0.01 \\
- & isEntityP & nan & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.22 & 0.00 \\
+ & hasAttyP & 0.45 & 0.00 \\
+ & isEntityD & 0.81 & 0.06 \\
+ & isEntityP & 0.18 & 0.00 \\
 \cline{1-4}

### 2023-04-06 output/group_2_crimes_500m/tables/pre_treatment_covariate_tests.tex
produced all figures

--- 2023-04-03 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.87 \\
- & pre_treatment_change_in_group_3_crimes_500m & 0.00 & 0.67 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_500m & 0.00 & 0.87 \\
+ & pre_treatment_change_in_group_2_crimes_500m & 0.00 & 0.67 \\
 \cline{1-4}

### 2023-04-06 output/group_2_crimes_50m/tables/balance_table.tex
produced all figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_50m & 0.79 & 0.16 & 0.15 & -0.02 & 0.77 \\
- & pre_treatment_change_in_group_2_crimes_50m & -0.01 & 0.00 & 0.67 & -0.00 & 0.91 \\
+\textit{Panel A} & total_twenty_seventeen_group_2_crimes_50m & 0.24 & 0.07 & 0.01 & -0.01 & 0.45 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.62 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -279.43 & 0.79 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 472.04 & 0.52 \\
+\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.01 & 0.08 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -42.73 & 0.98 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,914.99 & 0.04 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 688.17 & 0.12 \\
 \cline{1-7}

### 2023-04-06 output/group_2_crimes_50m/tables/pre_treatment_covariate_tests.tex
produced all figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_50m & 0.00 & 0.15 \\
- & pre_treatment_change_in_group_2_crimes_50m & 0.00 & 0.67 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_50m & 0.03 & 0.01 \\
+ & pre_treatment_change_in_group_2_crimes_50m & 0.19 & 0.41 \\
 \cline{1-4}
@@
  & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.04 & 0.05 \\
- & poor_share2010 & 0.53 & 0.96 \\
- & popdensity2010 & 0.46 & 0.00 \\
+ & med_hhinc2016 & 0.01 & 0.05 \\
+ & poor_share2010 & 0.98 & 0.96 \\
+ & popdensity2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.72 & 0.00 \\
- & no_cause & 0.25 & 0.95 \\
- & non_payment & 0.72 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.71 & 0.00 \\
+ & no_cause & 0.29 & 0.95 \\
+ & non_payment & 0.61 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.61 & 0.00 \\
- & hasAttyP & 0.39 & 0.00 \\
- & isEntityD & 0.45 & 0.06 \\
- & isEntityP & 0.13 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.12 & 0.00 \\
+ & hasAttyP & 0.30 & 0.00 \\
+ & isEntityD & 0.43 & 0.06 \\
+ & isEntityP & 0.49 & 0.00 \\
 \cline{1-4}

### 2023-04-06 output/group_3_crimes_1000m/tables/balance_table.tex
produced all figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_3_crimes_1000m & 59.18 & 3.58 & 0.18 & 0.65 & 0.80 \\
- & pre_treatment_change_in_group_3_crimes_1000m & -0.67 & -0.05 & 0.50 & -0.01 & 0.93 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_3_crimes_1000m & 58.60 & 2.49 & 0.08 & 0.42 & 0.75 \\
+ & pre_treatment_change_in_group_3_crimes_1000m & -2.38 & -0.18 & 0.07 & -0.01 & 0.87 \\
 \cline{1-7}
-\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.60 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 113.69 & 0.94 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 593.73 & 0.49 \\
- & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.44 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 253.66 & 0.52 \\
+\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.75 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 64.90 & 0.96 \\
+ & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.64 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 152.34 & 0.68 \\
 \cline{1-7}
-\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.87 \\
+\textit{Panel C} & no_cause & 0.05 & 0.00 & 0.95 & 0.00 & 0.96 \\
+\cline{1-7}
+\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.92 \\
 \cline{1-7}

### 2023-04-06 output/group_3_crimes_1000m/tables/pre_treatment_covariate_tests.tex
produced all figures

--- 2023-04-03 output/group_0_crimes_100m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_100m & 0.00 & 0.03 \\
- & pre_treatment_change_in_group_0_crimes_100m & 0.01 & 0.96 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_1000m & 0.00 & 0.08 \\
+ & pre_treatment_change_in_group_3_crimes_1000m & 0.00 & 0.07 \\
 \cline{1-4}
@@
  & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
+ & med_hhinc2016 & 0.18 & 0.05 \\
  & poor_share2010 & 0.00 & 0.96 \\
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.33 & 0.00 \\
- & no_cause & 0.09 & 0.95 \\
- & non_payment & 0.04 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.41 & 0.00 \\
+ & no_cause & 0.02 & 0.95 \\
+ & non_payment & 0.56 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.62 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.42 & 0.00 \\
+ & hasAttyP & 0.82 & 0.00 \\
  & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+ & isEntityP & 0.25 & 0.00 \\
 \cline{1-4}

### 2023-04-06 output/group_3_crimes_100m/tables/balance_table.tex
produced all figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_3_crimes_100m & 0.95 & 0.07 & 0.67 & 0.00 & 1.00 \\
- & pre_treatment_change_in_group_3_crimes_100m & -0.02 & -0.01 & 0.23 & 0.00 & 0.73 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_3_crimes_100m & 1.09 & 0.22 & 0.04 & 0.05 & 0.63 \\
+ & pre_treatment_change_in_group_3_crimes_100m & -0.05 & -0.01 & 0.54 & -0.00 & 0.85 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.63 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 441.33 & 0.52 \\
- & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.28 \\
+\multirow[c]{2}{3cm}{\textit{Panel B}} & job_density_2013 & 17,324.75 & 6,144.92 & 0.01 & 2,223.13 & 0.36 \\
+ & poor_share2010 & 0.28 & 0.02 & 0.02 & -0.01 & 0.31 \\
+\cline{1-7}
+\textit{Panel D} & isEntityP & 0.81 & 0.13 & 0.00 & 0.02 & 0.19 \\
 \cline{1-7}

### 2023-04-06 output/group_3_crimes_100m/tables/pre_treatment_covariate_tests.tex
produced all figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_100m & 0.00 & 0.67 \\
- & pre_treatment_change_in_group_3_crimes_100m & 0.00 & 0.23 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_100m & 0.00 & 0.04 \\
+ & pre_treatment_change_in_group_3_crimes_100m & 0.00 & 0.54 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.03 & 0.22 \\
- & job_density_2013 & 0.06 & 0.10 \\
- & med_hhinc2016 & 0.01 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.75 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.72 & 0.09 \\
+ & job_density_2013 & 0.00 & 0.01 \\
+ & med_hhinc2016 & 0.12 & 0.13 \\
+ & poor_share2010 & 0.00 & 0.02 \\
+ & popdensity2010 & 0.11 & 0.03 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.30 & 0.00 \\
- & no_cause & 0.28 & 0.95 \\
- & non_payment & 0.97 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.71 & 0.50 \\
+ & no_cause & 0.14 & 0.00 \\
+ & non_payment & 0.69 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.24 & 0.00 \\
- & hasAttyP & 0.43 & 0.00 \\
- & isEntityD & 0.82 & 0.06 \\
- & isEntityP & 0.17 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.10 & 0.00 \\
+ & hasAttyP & 0.15 & 0.00 \\
+ & isEntityD & 0.61 & 0.00 \\
+ & isEntityP & 0.02 & 0.00 \\
 \cline{1-4}

### 2023-04-06 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
produced all figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.87 \\
- & pre_treatment_change_in_group_3_crimes_500m & 0.00 & 0.67 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.01 \\
+ & pre_treatment_change_in_group_3_crimes_500m & 0.00 & 0.55 \\
 \cline{1-4}
@@
  & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+ & popdensity2010 & 0.05 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.22 & 0.00 \\
- & no_cause & 0.28 & 0.95 \\
- & non_payment & 0.09 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.18 & 0.00 \\
+ & no_cause & 0.27 & 0.95 \\
+ & non_payment & 0.07 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.84 & 0.00 \\
- & hasAttyP & 0.07 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.11 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.68 & 0.00 \\
+ & hasAttyP & 0.42 & 0.00 \\
+ & isEntityD & 0.02 & 0.06 \\
+ & isEntityP & 0.16 & 0.00 \\
 \cline{1-4}

### 2023-04-06 output/group_3_crimes_50m/tables/balance_table.tex
produced all figures

@@
 \midrule
-\textit{Panel A} & total_twenty_seventeen_group_3_crimes_50m & 0.24 & 0.07 & 0.01 & -0.01 & 0.44 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_3_crimes_50m & 0.35 & 0.07 & 0.01 & -0.01 & 0.48 \\
+ & pre_treatment_change_in_group_3_crimes_50m & -0.02 & -0.01 & 0.11 & 0.00 & 0.51 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.01 & 0.08 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -0.91 & 1.00 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,927.86 & 0.03 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 706.17 & 0.11 \\
+\multirow[c]{3}{3cm}{\textit{Panel B}} & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -153.52 & 0.91 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,794.81 & 0.05 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 608.96 & 0.15 \\
 \cline{1-7}

### 2023-04-06 output/group_3_crimes_50m/tables/pre_treatment_covariate_tests.tex
produced all figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_50m & 0.02 & 0.01 \\
- & pre_treatment_change_in_group_3_crimes_50m & 0.19 & 0.41 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_50m & 0.00 & 0.01 \\
+ & pre_treatment_change_in_group_3_crimes_50m & 0.00 & 0.11 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.44 & 0.22 \\
  & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.01 & 0.05 \\
- & poor_share2010 & 0.98 & 0.96 \\
+ & med_hhinc2016 & 0.00 & 0.05 \\
+ & poor_share2010 & 0.74 & 0.96 \\
  & popdensity2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.71 & 0.00 \\
- & no_cause & 0.29 & 0.95 \\
- & non_payment & 0.61 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.15 & 0.00 \\
+ & no_cause & 0.57 & 0.95 \\
+ & non_payment & 0.35 & 0.00 \\
 \cline{1-4}
 \multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.12 & 0.00 \\
- & hasAttyP & 0.30 & 0.00 \\
- & isEntityD & 0.43 & 0.06 \\
- & isEntityP & 0.49 & 0.00 \\
+ & hasAttyP & 0.61 & 0.00 \\
+ & isEntityD & 0.70 & 0.06 \\
+ & isEntityP & 0.58 & 0.00 \\
 \cline{1-4}

### 2023-04-06 output/group_4_crimes_100m/tables/pre_treatment_covariate_tests.tex
produced all figures

@@
 \multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_100m & 0.00 & 0.01 \\
- & pre_treatment_change_in_group_4_crimes_100m & 1.00 & 0.00 \\
+ & pre_treatment_change_in_group_4_crimes_100m & 0.37 & 0.64 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.15 & 0.22 \\
- & job_density_2013 & 0.51 & 0.10 \\
- & med_hhinc2016 & 0.05 & 0.05 \\
- & poor_share2010 & 0.14 & 0.96 \\
- & popdensity2010 & 0.52 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
+ & job_density_2013 & 0.00 & 0.10 \\
+ & med_hhinc2016 & 0.00 & 0.05 \\
+ & poor_share2010 & 0.11 & 0.96 \\
+ & popdensity2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.86 & 0.00 \\
- & no_cause & 0.92 & 0.95 \\
- & non_payment & 0.83 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.05 & 0.00 \\
+ & no_cause & 0.37 & 0.95 \\
+ & non_payment & 0.02 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.89 & 0.00 \\
- & hasAttyP & 0.88 & 0.00 \\
- & isEntityD & 0.95 & 0.06 \\
- & isEntityP & 0.84 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.71 & 0.00 \\
+ & hasAttyP & 0.78 & 0.00 \\
+ & isEntityD & 0.29 & 0.06 \\
+ & isEntityP & 0.04 & 0.00 \\
 \cline{1-4}

### 2023-04-06 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
produced all figures

@@
 \multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.00 \\
- & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.48 \\
+ & pre_treatment_change_in_group_4_crimes_500m & 0.01 & 0.03 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.48 & 0.22 \\
  & job_density_2013 & 0.00 & 0.10 \\
  & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
+ & poor_share2010 & 0.48 & 0.96 \\
  & popdensity2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.35 & 0.00 \\
- & no_cause & 0.67 & 0.95 \\
- & non_payment & 0.28 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.45 & 0.00 \\
+ & no_cause & 0.02 & 0.95 \\
+ & non_payment & 0.60 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.78 & 0.00 \\
- & hasAttyP & 0.51 & 0.00 \\
- & isEntityD & 0.28 & 0.06 \\
- & isEntityP & 0.92 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.59 & 0.00 \\
+ & hasAttyP & 0.18 & 0.00 \\
+ & isEntityD & 0.02 & 0.06 \\
+ & isEntityP & 0.36 & 0.00 \\
 \cline{1-4}

### 2023-04-06 output/group_4_crimes_50m/tables/balance_table.tex
produced all figures

@@
 \midrule
-\textit{Panel A} & total_twenty_seventeen_group_4_crimes_50m & 0.02 & 0.01 & 0.01 & -0.00 & 0.43 \\
+\textit{Panel A} & total_twenty_seventeen_group_4_crimes_50m & 0.39 & 0.08 & 0.01 & -0.01 & 0.69 \\
 \cline{1-7}
-\textit{Panel B} & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 757.12 & 0.37 \\
+\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.01 & 0.17 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -458.26 & 0.75 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -1,467.75 & 0.04 \\
+\cline{1-7}
+\textit{Panel C} & non_payment & 0.77 & -0.08 & 0.00 & -0.03 & 0.02 \\
 \cline{1-7}

### 2023-04-06 output/group_6_crimes_1000m/tables/balance_table.tex
Updated constants

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_4_crimes_1000m & 3.40 & 0.30 & 0.00 & -0.01 & 0.93 \\
 & pre_treatment_change_in_group_4_crimes_1000m & 0.17 & -0.05 & 0.03 & -0.00 & 0.98 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.92 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -34.03 & 0.98 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -110.46 & 0.90 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.90 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -51.28 & 0.91 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.00 & 0.83 \\
 & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.99 \\
 & isEntityP & 0.81 & -0.07 & 0.00 & -0.00 & 0.85 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-06 output/group_7_crimes_100m/tables/balance_table.tex
Updated constants

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_4_crimes_100m & 1.44 & 0.15 & 0.01 & -0.03 & 0.59 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.01 & 0.38 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -331.93 & 0.83 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -1,008.08 & 0.23 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -474.79 & 0.26 \\
\cline{1-7}
\textit{Panel C} & non_payment & 0.77 & -0.08 & 0.00 & -0.02 & 0.14 \\
\cline{1-7}
\textit{Panel D} & isEntityP & 0.81 & -0.07 & 0.00 & -0.02 & 0.13 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-06 output/group_7_crimes_50m/tables/pre_treatment_covariate_tests.tex
Updated constants

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_50m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_4_crimes_50m & 0.99 & 0.12 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.02 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.01 & 0.05 \\
 & poor_share2010 & 0.49 & 0.96 \\
 & popdensity2010 & 0.36 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.11 & 0.00 \\
 & no_cause & 0.23 & 0.95 \\
 & non_payment & 0.03 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.35 & 0.00 \\
 & hasAttyP & 0.63 & 0.00 \\
 & isEntityD & 0.43 & 0.06 \\
 & isEntityP & 0.68 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-06 src/02_analysis/constants.py

@@ -4,19 +4,31 @@ class Variables:
                 'group_2_crimes_50m',
                 'group_3_crimes_50m',
                 'group_4_crimes_50m',
+                'group_5_crimes_50m',
+                'group_6_crimes_50m',
+                'group_7_crimes_50m',
                 'group_0_crimes_100m',
                 'group_1_crimes_100m',
                 'group_2_crimes_100m', 
                 'group_3_crimes_100m',
                 'group_4_crimes_100m',
+                'group_5_crimes_100m',
+                'group_6_crimes_100m',
+                'group_7_crimes_100m',
                 'group_0_crimes_500m',
                 'group_1_crimes_500m',
                 'group_2_crimes_500m', 
                 'group_3_crimes_500m',
                 'group_4_crimes_500m',
+                'group_5_crimes_500m',
+                'group_6_crimes_500m',
+                'group_7_crimes_500m',
                 'group_0_crimes_1000m',
                 'group_1_crimes_1000m',
                 'group_2_crimes_1000m', 
                 'group_3_crimes_1000m',
-                'group_4_crimes_1000m']
+                'group_4_crimes_1000m',
+                'group_5_crimes_1000m',
+                'group_6_crimes_1000m',
+                'group_7_crimes_1000m']
 

### 2023-04-08 output/group_0_crimes_1000m/tables/balance_table.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_0_crimes_1000m & 4,045.37 & 166.49 & 0.04 & -69.57 & 0.38 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_0_crimes_1000m & 4,045.37 & 166.28 & 0.04 & -69.59 & 0.38 \\
  & pre_treatment_change_in_group_0_crimes_1000m & -25.13 & -2.31 & 0.02 & 0.42 & 0.66 \\
@@
 \multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.01 & 0.47 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -282.06 & 0.85 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -836.51 & 0.34 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -282.14 & 0.85 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -836.74 & 0.34 \\
  & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.36 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -396.09 & 0.37 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -396.20 & 0.37 \\
 \cline{1-7}

### 2023-04-08 output/group_0_crimes_100m/tables/balance_table.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_0_crimes_100m & 69.20 & 5.24 & 0.03 & -0.53 & 0.82 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_0_crimes_100m & 69.96 & 5.30 & 0.03 & -0.54 & 0.82 \\
  & pre_treatment_change_in_group_0_crimes_100m & -0.23 & 0.00 & 0.96 & 0.00 & 0.98 \\
@@
 \multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.75 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -133.94 & 0.93 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -374.02 & 0.67 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -134.09 & 0.93 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -374.22 & 0.67 \\
  & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.69 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -179.58 & 0.69 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -179.71 & 0.69 \\
 \cline{1-7}

### 2023-04-08 output/group_0_crimes_50m/tables/balance_table.tex
gennerated figures

@@
 \midrule
-\textit{Panel A} & total_twenty_seventeen_group_0_crimes_50m & 19.08 & 1.56 & 0.09 & -0.25 & 0.78 \\
+\textit{Panel A} & total_twenty_seventeen_group_0_crimes_50m & 19.30 & 1.58 & 0.09 & -0.25 & 0.78 \\
 \cline{1-7}
 \multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.55 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -205.84 & 0.89 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -205.76 & 0.89 \\
  & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.44 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -311.10 & 0.44 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -311.13 & 0.44 \\
 \cline{1-7}

### 2023-04-08 output/group_0_crimes_50m/tables/pre_treatment_covariate_tests.tex
gennerated figures

@@
 \multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_50m & 0.00 & 0.09 \\
- & pre_treatment_change_in_group_0_crimes_50m & 0.11 & 0.44 \\
+ & pre_treatment_change_in_group_0_crimes_50m & 0.07 & 0.44 \\
 \cline{1-4}
@@
  & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.83 & 0.05 \\
+ & med_hhinc2016 & 0.73 & 0.05 \\
  & poor_share2010 & 0.00 & 0.96 \\
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.32 & 0.00 \\
- & no_cause & 0.40 & 0.95 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.30 & 0.00 \\
+ & no_cause & 0.41 & 0.95 \\
  & non_payment & 0.14 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.23 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.22 & 0.00 \\
  & hasAttyP & 0.03 & 0.00 \\

### 2023-04-08 output/group_1_crimes_1000m/tables/pre_treatment_covariate_tests.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_1000m & 0.00 & 0.08 \\
- & pre_treatment_change_in_group_1_crimes_1000m & 0.05 & 0.07 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_1000m & 0.00 & 0.09 \\
+ & pre_treatment_change_in_group_1_crimes_1000m & 0.38 & 0.06 \\
 \cline{1-4}
@@
  & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.27 & 0.00 \\
+ & isEntityP & 0.21 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_1_crimes_100m/tables/balance_table.tex
gennerated figures

--- 2023-03-16 output/group_1_crimes_100m/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_group_1_crimes_100m & 0.41 & 0.07 & 0.01 & -0.00 & 0.85 \\
- & pre_treatment_change_in_group_1_crimes_100m & 0.04 & -0.02 & 0.56 & -0.00 & 0.91 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_1_crimes_100m & 6.22 & 0.63 & 0.02 & -0.01 & 0.98 \\
+ & pre_treatment_change_in_group_1_crimes_100m & 0.04 & 0.01 & 0.78 & -0.00 & 1.00 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.01 & 0.15 \\
- & job_density_2013 & 16,069.14 & 926.91 & 0.52 & -413.06 & 0.77 \\
- & poor_share2010 & 0.27 & -0.00 & 0.53 & -0.01 & 0.05 \\
- & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -607.79 & 0.07 \\
+\multirow[c]{4}{3cm}{\textit{Panel B}} & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -13.70 & 0.99 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -47.38 & 0.96 \\
+ & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.96 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -21.71 & 0.96 \\
 \cline{1-7}
-\textit{Panel D} & isEntityP & 0.81 & -0.06 & 0.00 & -0.04 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyD & 0.07 & -0.03 & 0.00 & -0.00 & 0.99 \\
+ & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.99 \\
+ & isEntityP & 0.81 & -0.07 & 0.00 & -0.00 & 0.93 \\
 \cline{1-7}

### 2023-04-08 output/group_1_crimes_100m/tables/pre_treatment_covariate_tests.tex
gennerated figures

@@
 \multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_100m & 0.00 & 0.02 \\
- & pre_treatment_change_in_group_1_crimes_100m & 0.00 & 0.69 \\
+ & pre_treatment_change_in_group_1_crimes_100m & 0.00 & 0.78 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.55 & 0.22 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.46 & 0.22 \\
  & job_density_2013 & 0.00 & 0.10 \\
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.31 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.41 & 0.00 \\
  & no_cause & 0.40 & 0.95 \\
- & non_payment & 0.81 & 0.00 \\
+ & non_payment & 0.95 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.07 & 0.00 \\
- & hasAttyP & 0.53 & 0.00 \\
- & isEntityD & 0.02 & 0.06 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.05 & 0.00 \\
+ & hasAttyP & 0.58 & 0.00 \\
+ & isEntityD & 0.01 & 0.06 \\
  & isEntityP & 0.00 & 0.00 \\

### 2023-04-08 output/group_1_crimes_500m/tables/balance_table.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_1_crimes_500m & 95.93 & 5.50 & 0.02 & 1.21 & 0.57 \\
- & pre_treatment_change_in_group_1_crimes_500m & -0.07 & -0.09 & 0.36 & 0.00 & 0.97 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_1_crimes_500m & 96.93 & 5.41 & 0.02 & 1.14 & 0.61 \\
+ & pre_treatment_change_in_group_1_crimes_500m & -0.06 & -0.08 & 0.43 & 0.00 & 0.99 \\
 \cline{1-7}
-\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.56 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 131.16 & 0.93 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 666.70 & 0.45 \\
- & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.39 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 285.95 & 0.48 \\
+\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.60 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 152.60 & 0.92 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 599.16 & 0.50 \\
+ & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.47 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 268.01 & 0.53 \\
 \cline{1-7}
-\textit{Panel C} & no_cause & 0.05 & 0.00 & 0.95 & 0.00 & 0.92 \\
+\textit{Panel C} & no_cause & 0.05 & 0.00 & 0.95 & 0.00 & 0.93 \\
 \cline{1-7}
-\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.86 \\
+\multirow[c]{2}{3cm}{\textit{Panel D}} & hasAttyD & 0.07 & -0.03 & 0.00 & 0.00 & 0.81 \\
+ & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.91 \\
 \cline{1-7}

### 2023-04-08 output/group_1_crimes_500m/tables/pre_treatment_covariate_tests.tex
gennerated figures

@@
 \multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_500m & 0.00 & 0.02 \\
- & pre_treatment_change_in_group_1_crimes_500m & 0.00 & 0.36 \\
+ & pre_treatment_change_in_group_1_crimes_500m & 0.00 & 0.43 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.56 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.51 & 0.00 \\
  & no_cause & 0.02 & 0.95 \\
- & non_payment & 0.06 & 0.00 \\
+ & non_payment & 0.05 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.05 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.04 & 0.00 \\
  & hasAttyP & 0.52 & 0.00 \\
  & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.25 & 0.00 \\
+ & isEntityP & 0.34 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_1_crimes_50m/tables/balance_table.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_1_crimes_50m & 1.72 & 0.21 & 0.05 & 0.02 & 0.86 \\
- & pre_treatment_change_in_group_1_crimes_50m & 0.01 & -0.00 & 0.84 & 0.00 & 0.99 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_1_crimes_50m & 1.75 & 0.20 & 0.06 & 0.02 & 0.86 \\
+ & pre_treatment_change_in_group_1_crimes_50m & 0.01 & -0.00 & 0.75 & 0.00 & 0.98 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 149.61 & 0.92 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 640.49 & 0.47 \\
+\multirow[c]{4}{3cm}{\textit{Panel B}} & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 149.22 & 0.92 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 640.01 & 0.47 \\
  & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.43 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 282.20 & 0.50 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 281.91 & 0.50 \\
 \cline{1-7}

### 2023-04-08 output/group_1_crimes_50m/tables/pre_treatment_covariate_tests.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_50m & 0.00 & 0.05 \\
- & pre_treatment_change_in_group_1_crimes_50m & 0.00 & 0.84 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_50m & 0.00 & 0.06 \\
+ & pre_treatment_change_in_group_1_crimes_50m & 0.00 & 0.75 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.29 & 0.22 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.22 & 0.22 \\
  & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.02 & 0.05 \\
+ & med_hhinc2016 & 0.01 & 0.05 \\
  & poor_share2010 & 0.00 & 0.96 \\
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.34 & 0.00 \\
- & no_cause & 0.07 & 0.95 \\
- & non_payment & 0.90 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.38 & 0.00 \\
+ & no_cause & 0.06 & 0.95 \\
+ & non_payment & 0.84 & 0.00 \\
 \cline{1-4}
 \multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.03 & 0.00 \\
- & hasAttyP & 0.61 & 0.00 \\
- & isEntityD & 0.26 & 0.06 \\
- & isEntityP & 0.16 & 0.00 \\
+ & hasAttyP & 0.66 & 0.00 \\
+ & isEntityD & 0.25 & 0.06 \\
+ & isEntityP & 0.19 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_2_crimes_1000m/tables/balance_table.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_1000m & 59.18 & 3.58 & 0.18 & 0.65 & 0.80 \\
- & pre_treatment_change_in_group_2_crimes_1000m & -0.67 & -0.05 & 0.49 & -0.01 & 0.93 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_1000m & 59.19 & 3.58 & 0.18 & 0.65 & 0.80 \\
+ & pre_treatment_change_in_group_2_crimes_1000m & -0.67 & -0.05 & 0.50 & -0.01 & 0.93 \\
 \cline{1-7}
 \multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.60 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 113.80 & 0.94 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 593.54 & 0.49 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 113.70 & 0.94 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 593.73 & 0.49 \\
  & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.44 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 253.63 & 0.52 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 253.67 & 0.52 \\
 \cline{1-7}

### 2023-04-08 output/group_2_crimes_1000m/tables/pre_treatment_covariate_tests.tex
gennerated figures

@@
 \multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_1000m & 0.00 & 0.18 \\
- & pre_treatment_change_in_group_2_crimes_1000m & 0.00 & 0.49 \\
+ & pre_treatment_change_in_group_2_crimes_1000m & 0.00 & 0.50 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.37 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.45 & 0.00 \\
  & no_cause & 0.16 & 0.95 \\
- & non_payment & 0.11 & 0.00 \\
+ & non_payment & 0.14 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.66 & 0.00 \\
- & hasAttyP & 0.14 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.67 & 0.00 \\
+ & hasAttyP & 0.13 & 0.00 \\
  & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.54 & 0.00 \\
+ & isEntityP & 0.53 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_2_crimes_100m/tables/balance_table.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_100m & 0.96 & 0.08 & 0.64 & -0.00 & 0.99 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_100m & 0.97 & 0.07 & 0.65 & -0.00 & 0.99 \\
  & pre_treatment_change_in_group_2_crimes_100m & -0.02 & -0.01 & 0.23 & 0.00 & 0.73 \\
@@
 \multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.64 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 435.35 & 0.52 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 436.85 & 0.52 \\
  & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.27 \\

### 2023-04-08 output/group_2_crimes_100m/tables/pre_treatment_covariate_tests.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_100m & 0.00 & 0.64 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_100m & 0.00 & 0.65 \\
  & pre_treatment_change_in_group_2_crimes_100m & 0.00 & 0.23 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.02 & 0.22 \\
- & job_density_2013 & 0.17 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.03 & 0.22 \\
+ & job_density_2013 & 0.06 & 0.10 \\
+ & med_hhinc2016 & 0.01 & 0.05 \\
  & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.79 & 0.00 \\
+ & popdensity2010 & 0.75 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.43 & 0.00 \\
- & no_cause & 0.29 & 0.95 \\
- & non_payment & 0.80 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.30 & 0.00 \\
+ & no_cause & 0.28 & 0.95 \\
+ & non_payment & 0.97 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.22 & 0.00 \\
- & hasAttyP & 0.45 & 0.00 \\
- & isEntityD & 0.81 & 0.06 \\
- & isEntityP & 0.18 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.24 & 0.00 \\
+ & hasAttyP & 0.43 & 0.00 \\
+ & isEntityD & 0.82 & 0.06 \\
+ & isEntityP & 0.17 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_2_crimes_50m/tables/balance_table.tex
gennerated figures

@@
 \midrule
-\textit{Panel A} & total_twenty_seventeen_group_2_crimes_50m & 0.24 & 0.07 & 0.01 & -0.01 & 0.45 \\
+\textit{Panel A} & total_twenty_seventeen_group_2_crimes_50m & 0.24 & 0.07 & 0.01 & -0.01 & 0.44 \\
 \cline{1-7}
 \multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.01 & 0.08 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -42.73 & 0.98 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,914.99 & 0.04 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 688.17 & 0.12 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -31.22 & 0.98 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,919.52 & 0.03 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 693.49 & 0.11 \\
 \cline{1-7}

### 2023-04-08 output/group_2_crimes_50m/tables/pre_treatment_covariate_tests.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_50m & 0.03 & 0.01 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_50m & 0.02 & 0.01 \\
  & pre_treatment_change_in_group_2_crimes_50m & 0.19 & 0.41 \\

### 2023-04-08 output/group_3_crimes_1000m/tables/balance_table.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_3_crimes_1000m & 58.60 & 2.49 & 0.08 & 0.42 & 0.75 \\
- & pre_treatment_change_in_group_3_crimes_1000m & -2.38 & -0.18 & 0.07 & -0.01 & 0.87 \\
+\textit{Panel A} & total_twenty_seventeen_group_3_crimes_1000m & 415.94 & 15.64 & 0.04 & 0.55 & 0.94 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.75 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 64.90 & 0.96 \\
- & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.64 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 152.34 & 0.68 \\
+\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.96 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 19.55 & 0.99 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 64.10 & 0.94 \\
+ & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.94 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 29.70 & 0.95 \\
 \cline{1-7}
-\textit{Panel C} & no_cause & 0.05 & 0.00 & 0.95 & 0.00 & 0.96 \\
-\cline{1-7}
-\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.92 \\
+\multirow[c]{2}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & 0.00 & 0.89 \\
+ & isEntityP & 0.81 & -0.07 & 0.00 & 0.00 & 0.89 \\
 \cline{1-7}

### 2023-04-08 output/group_3_crimes_1000m/tables/pre_treatment_covariate_tests.tex
gennerated figures

--- 2023-04-03 output/group_0_crimes_100m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_100m & 0.00 & 0.03 \\
- & pre_treatment_change_in_group_0_crimes_100m & 0.01 & 0.96 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_1000m & 0.00 & 0.04 \\
+ & pre_treatment_change_in_group_3_crimes_1000m & 0.61 & 0.17 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.33 & 0.00 \\
- & no_cause & 0.09 & 0.95 \\
- & non_payment & 0.04 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.45 & 0.00 \\
+ & no_cause & 0.26 & 0.95 \\
+ & non_payment & 0.95 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.62 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.99 & 0.00 \\
  & hasAttyP & 0.00 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
+ & isEntityD & 0.15 & 0.06 \\
  & isEntityP & 0.00 & 0.00 \\

### 2023-04-08 output/group_3_crimes_100m/tables/balance_table.tex
gennerated figures

--- 2023-04-03 output/group_3_crimes_100m/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_3_crimes_100m & 0.95 & 0.07 & 0.67 & 0.00 & 1.00 \\
- & pre_treatment_change_in_group_3_crimes_100m & -0.02 & -0.01 & 0.23 & 0.00 & 0.73 \\
+\textit{Panel A} & total_twenty_seventeen_group_3_crimes_100m & 7.20 & 0.82 & 0.04 & -0.03 & 0.94 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.63 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 441.33 & 0.52 \\
- & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.28 \\
+\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.02 & 0.09 & -0.01 & 0.52 \\
+ & job_density_2013 & 17,324.75 & 6,144.92 & 0.01 & 1,756.80 & 0.47 \\
+ & med_hhinc2016 & 48,534.18 & 2,249.48 & 0.13 & -1,615.62 & 0.22 \\
+ & popdensity2010 & 23,285.59 & 1,707.93 & 0.03 & -500.51 & 0.47 \\
+\cline{1-7}
+\textit{Panel D} & isEntityD & 0.02 & -0.04 & 0.00 & -0.02 & 0.01 \\
 \cline{1-7}

### 2023-04-08 output/group_3_crimes_100m/tables/pre_treatment_covariate_tests.tex
gennerated figures

@@
 \multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_100m & 0.00 & 0.04 \\
- & pre_treatment_change_in_group_3_crimes_100m & 0.00 & 0.54 \\
+ & pre_treatment_change_in_group_3_crimes_100m & 0.24 & 0.33 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.72 & 0.09 \\
- & job_density_2013 & 0.00 & 0.01 \\
- & med_hhinc2016 & 0.12 & 0.13 \\
- & poor_share2010 & 0.00 & 0.02 \\
- & popdensity2010 & 0.11 & 0.03 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.09 \\
+ & job_density_2013 & 0.02 & 0.01 \\
+ & med_hhinc2016 & 0.00 & 0.13 \\
+ & poor_share2010 & 0.29 & 0.02 \\
+ & popdensity2010 & 0.00 & 0.03 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.71 & 0.50 \\
- & no_cause & 0.14 & 0.00 \\
- & non_payment & 0.69 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.19 & 0.50 \\
+ & no_cause & 0.42 & 0.00 \\
+ & non_payment & 0.08 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.10 & 0.00 \\
- & hasAttyP & 0.15 & 0.00 \\
- & isEntityD & 0.61 & 0.00 \\
- & isEntityP & 0.02 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.75 & 0.00 \\
+ & hasAttyP & 0.31 & 0.00 \\
+ & isEntityD & 0.00 & 0.00 \\
+ & isEntityP & 0.05 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.01 \\
- & pre_treatment_change_in_group_3_crimes_500m & 0.00 & 0.55 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.02 \\
+ & pre_treatment_change_in_group_3_crimes_500m & 0.04 & 0.81 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.01 & 0.22 \\
  & job_density_2013 & 0.00 & 0.10 \\
@@
  & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.05 & 0.00 \\
+ & popdensity2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.18 & 0.00 \\
- & no_cause & 0.27 & 0.95 \\
- & non_payment & 0.07 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.75 & 0.00 \\
+ & no_cause & 0.94 & 0.95 \\
+ & non_payment & 0.85 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.68 & 0.00 \\
- & hasAttyP & 0.42 & 0.00 \\
- & isEntityD & 0.02 & 0.06 \\
- & isEntityP & 0.16 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.43 & 0.00 \\
+ & hasAttyP & 0.41 & 0.00 \\
+ & isEntityD & 0.00 & 0.06 \\
+ & isEntityP & 0.64 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_3_crimes_50m/tables/balance_table.tex
gennerated figures

--- 2023-04-03 output/group_3_crimes_50m/tables/balance_table.tex
@@
 \midrule
-\textit{Panel A} & total_twenty_seventeen_group_3_crimes_50m & 0.24 & 0.07 & 0.01 & -0.01 & 0.44 \\
-\cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.01 & 0.08 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -0.91 & 1.00 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,927.86 & 0.03 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 706.17 & 0.11 \\
+\textit{Panel A} & total_twenty_seventeen_group_3_crimes_50m & 2.07 & 0.22 & 0.07 & -0.01 & 0.31 \\
 \cline{1-7}

### 2023-04-08 output/group_3_crimes_50m/tables/pre_treatment_covariate_tests.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_50m & 0.00 & 0.01 \\
- & pre_treatment_change_in_group_3_crimes_50m & 0.00 & 0.11 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_50m & 0.00 & 0.07 \\
+ & pre_treatment_change_in_group_3_crimes_50m & 0.51 & 0.87 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.44 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.74 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.18 & 0.22 \\
+ & job_density_2013 & 0.32 & 0.10 \\
+ & med_hhinc2016 & 0.28 & 0.05 \\
+ & poor_share2010 & 0.22 & 0.96 \\
+ & popdensity2010 & 0.22 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.15 & 0.00 \\
- & no_cause & 0.57 & 0.95 \\
- & non_payment & 0.35 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.29 & 0.00 \\
+ & no_cause & 0.35 & 0.95 \\
+ & non_payment & 0.14 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.12 & 0.00 \\
- & hasAttyP & 0.61 & 0.00 \\
- & isEntityD & 0.70 & 0.06 \\
- & isEntityP & 0.58 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.63 & 0.00 \\
+ & hasAttyP & 0.68 & 0.00 \\
+ & isEntityD & 0.33 & 0.06 \\
+ & isEntityP & 0.78 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_4_crimes_1000m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_4_crimes_1000m & 451.08 & 28.66 & 0.05 & -1.03 & 0.94 \\
 & pre_treatment_change_in_group_4_crimes_1000m & -4.07 & -0.15 & 0.41 & 0.01 & 0.96 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.93 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -47.10 & 0.98 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -103.33 & 0.91 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.92 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -52.82 & 0.91 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel C}} & for_cause & 0.17 & 0.08 & 0.00 & -0.00 & 0.94 \\
 & no_cause & 0.05 & 0.00 & 0.95 & -0.00 & 0.99 \\
 & non_payment & 0.77 & -0.08 & 0.00 & -0.00 & 0.93 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel D}} & hasAttyD & 0.07 & -0.03 & 0.00 & 0.00 & 1.00 \\
 & hasAttyP & 0.88 & -0.04 & 0.00 & -0.00 & 0.89 \\
 & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 1.00 \\
 & isEntityP & 0.81 & -0.07 & 0.00 & -0.00 & 0.92 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_4_crimes_1000m/tables/pre_treatment_covariate_tests.tex
gennerated figures

--- 2023-04-03 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.87 \\
- & pre_treatment_change_in_group_3_crimes_500m & 0.00 & 0.67 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_1000m & 0.00 & 0.05 \\
+ & pre_treatment_change_in_group_4_crimes_1000m & 0.00 & 0.41 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.22 & 0.00 \\
- & no_cause & 0.28 & 0.95 \\
- & non_payment & 0.09 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.01 & 0.00 \\
+ & no_cause & 0.00 & 0.95 \\
+ & non_payment & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.84 & 0.00 \\
- & hasAttyP & 0.07 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.00 & 0.00 \\
+ & hasAttyP & 0.00 & 0.00 \\
  & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.11 & 0.00 \\
+ & isEntityP & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_4_crimes_100m/tables/balance_table.tex
gennerated figures

@@
 \midrule
-\textit{Panel A} & total_twenty_seventeen_group_4_crimes_100m & 0.06 & 0.02 & 0.01 & -0.00 & 0.88 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_4_crimes_100m & 7.78 & 0.18 & 0.79 & -0.09 & 0.90 \\
+ & pre_treatment_change_in_group_4_crimes_100m & -0.03 & -0.02 & 0.49 & 0.00 & 0.99 \\
+\cline{1-7}
+\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.65 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -180.58 & 0.91 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -529.96 & 0.55 \\
+ & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.56 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -251.53 & 0.58 \\
+\cline{1-7}
+\textit{Panel C} & non_payment & 0.77 & -0.08 & 0.00 & -0.01 & 0.46 \\
+\cline{1-7}
+\multirow[c]{4}{3cm}{\textit{Panel D}} & hasAttyD & 0.07 & -0.03 & 0.00 & -0.00 & 0.93 \\
+ & hasAttyP & 0.88 & -0.04 & 0.00 & -0.01 & 0.36 \\
+ & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.96 \\
+ & isEntityP & 0.81 & -0.07 & 0.00 & -0.01 & 0.44 \\
 \cline{1-7}

### 2023-04-08 output/group_4_crimes_100m/tables/pre_treatment_covariate_tests.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_100m & 0.00 & 0.01 \\
- & pre_treatment_change_in_group_4_crimes_100m & 0.37 & 0.64 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_100m & 0.00 & 0.79 \\
+ & pre_treatment_change_in_group_4_crimes_100m & 0.00 & 0.49 \\
 \cline{1-4}
@@
  & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.11 & 0.96 \\
+ & poor_share2010 & 0.00 & 0.96 \\
  & popdensity2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.05 & 0.00 \\
- & no_cause & 0.37 & 0.95 \\
- & non_payment & 0.02 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.30 & 0.00 \\
+ & no_cause & 0.06 & 0.95 \\
+ & non_payment & 0.03 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.71 & 0.00 \\
- & hasAttyP & 0.78 & 0.00 \\
- & isEntityD & 0.29 & 0.06 \\
- & isEntityP & 0.04 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.04 & 0.00 \\
+ & hasAttyP & 0.00 & 0.00 \\
+ & isEntityD & 0.00 & 0.06 \\
+ & isEntityP & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
gennerated figures

--- 2023-04-03 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.00 \\
- & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.48 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.01 \\
+ & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.27 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.35 & 0.00 \\
- & no_cause & 0.67 & 0.95 \\
- & non_payment & 0.28 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.08 & 0.00 \\
+ & no_cause & 0.00 & 0.95 \\
+ & non_payment & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.78 & 0.00 \\
- & hasAttyP & 0.51 & 0.00 \\
- & isEntityD & 0.28 & 0.06 \\
- & isEntityP & 0.92 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.26 & 0.00 \\
+ & hasAttyP & 0.00 & 0.00 \\
+ & isEntityD & 0.06 & 0.06 \\
+ & isEntityP & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_4_crimes_50m/tables/balance_table.tex
gennerated figures

--- 2023-04-03 output/group_4_crimes_50m/tables/balance_table.tex
@@
 \midrule
-\textit{Panel A} & total_twenty_seventeen_group_4_crimes_50m & 0.02 & 0.01 & 0.01 & -0.00 & 0.43 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_4_crimes_50m & 1.77 & -0.10 & 0.54 & -0.05 & 0.77 \\
+ & pre_treatment_change_in_group_4_crimes_50m & 0.01 & 0.01 & 0.48 & 0.00 & 1.00 \\
 \cline{1-7}
-\textit{Panel B} & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 757.12 & 0.37 \\
+\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.01 & 0.26 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -391.41 & 0.79 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -578.94 & 0.11 \\
+\cline{1-7}
+\multirow[c]{2}{3cm}{\textit{Panel D}} & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.89 \\
+ & isEntityP & 0.81 & -0.07 & 0.00 & -0.02 & 0.04 \\
 \cline{1-7}

### 2023-04-08 output/group_4_crimes_50m/tables/pre_treatment_covariate_tests.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_50m & 0.00 & 0.01 \\
- & pre_treatment_change_in_group_4_crimes_50m & 0.99 & 0.17 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_50m & 0.00 & 0.54 \\
+ & pre_treatment_change_in_group_4_crimes_50m & 0.01 & 0.48 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.28 & 0.22 \\
- & job_density_2013 & 0.40 & 0.10 \\
- & med_hhinc2016 & 0.03 & 0.05 \\
- & poor_share2010 & 0.06 & 0.96 \\
- & popdensity2010 & 0.43 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
+ & job_density_2013 & 0.00 & 0.10 \\
+ & med_hhinc2016 & 0.65 & 0.05 \\
+ & poor_share2010 & 0.33 & 0.96 \\
+ & popdensity2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.82 & 0.00 \\
- & no_cause & 0.90 & 0.95 \\
- & non_payment & 0.78 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.67 & 0.00 \\
+ & no_cause & 0.09 & 0.95 \\
+ & non_payment & 0.16 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.86 & 0.00 \\
- & hasAttyP & 0.84 & 0.00 \\
- & isEntityD & 0.93 & 0.06 \\
- & isEntityP & 0.80 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.45 & 0.00 \\
+ & hasAttyP & 0.13 & 0.00 \\
+ & isEntityD & 0.00 & 0.06 \\
+ & isEntityP & 0.02 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_5_crimes_1000m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_5_crimes_1000m & 214.01 & 2.04 & 0.76 & -2.08 & 0.75 \\
 & pre_treatment_change_in_group_5_crimes_1000m & 0.22 & 0.02 & 0.90 & -0.00 & 0.99 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.69 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -167.46 & 0.91 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -471.88 & 0.59 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.61 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -226.08 & 0.61 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel C}} & no_cause & 0.05 & 0.00 & 0.95 & -0.00 & 0.95 \\
 & non_payment & 0.77 & -0.08 & 0.00 & -0.01 & 0.52 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.01 & 0.42 \\
 & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.97 \\
 & isEntityP & 0.81 & -0.07 & 0.00 & -0.01 & 0.50 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_5_crimes_1000m/tables/pre_treatment_covariate_tests.tex
gennerated figures

--- 2023-04-06 output/group_2_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_500m & 0.00 & 0.87 \\
- & pre_treatment_change_in_group_2_crimes_500m & 0.00 & 0.67 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_5_crimes_1000m & 0.00 & 0.76 \\
+ & pre_treatment_change_in_group_5_crimes_1000m & 0.00 & 0.90 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.22 & 0.00 \\
- & no_cause & 0.28 & 0.95 \\
- & non_payment & 0.09 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.31 & 0.00 \\
+ & no_cause & 0.01 & 0.95 \\
+ & non_payment & 0.01 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.84 & 0.00 \\
- & hasAttyP & 0.07 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.95 & 0.00 \\
+ & hasAttyP & 0.00 & 0.00 \\
  & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.11 & 0.00 \\
+ & isEntityP & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_5_crimes_100m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_5_crimes_100m & 3.87 & 0.18 & 0.24 & -0.05 & 0.75 \\
 & pre_treatment_change_in_group_5_crimes_100m & 0.01 & -0.01 & 0.52 & -0.00 & 0.98 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.60 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -159.16 & 0.91 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -261.65 & 0.45 \\
\cline{1-7}
\textit{Panel D} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.01 & 0.21 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_5_crimes_100m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_5_crimes_100m & 0.00 & 0.24 \\
 & pre_treatment_change_in_group_5_crimes_100m & 0.00 & 0.52 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.58 & 0.05 \\
 & poor_share2010 & 0.20 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.58 & 0.00 \\
 & no_cause & 0.05 & 0.95 \\
 & non_payment & 0.13 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.80 & 0.00 \\
 & hasAttyP & 0.03 & 0.00 \\
 & isEntityD & 0.33 & 0.06 \\
 & isEntityP & 0.24 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_5_crimes_500m/tables/pre_treatment_covariate_tests.tex
gennerated figures

--- 2023-04-06 output/group_2_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_500m & 0.00 & 0.87 \\
- & pre_treatment_change_in_group_2_crimes_500m & 0.00 & 0.67 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_5_crimes_500m & 0.00 & 0.37 \\
+ & pre_treatment_change_in_group_5_crimes_500m & 0.00 & 0.05 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.22 & 0.00 \\
- & no_cause & 0.28 & 0.95 \\
- & non_payment & 0.09 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.43 & 0.00 \\
+ & no_cause & 0.03 & 0.95 \\
+ & non_payment & 0.03 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.84 & 0.00 \\
- & hasAttyP & 0.07 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.61 & 0.00 \\
+ & hasAttyP & 0.00 & 0.00 \\
  & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.11 & 0.00 \\
+ & isEntityP & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-08 output/group_5_crimes_50m/tables/balance_table.tex
gennerated figures

--- 2023-04-08 output/group_5_crimes_100m/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_5_crimes_100m & 3.87 & 0.18 & 0.24 & -0.05 & 0.75 \\
- & pre_treatment_change_in_group_5_crimes_100m & 0.01 & -0.01 & 0.52 & -0.00 & 0.98 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_5_crimes_50m & 1.13 & 0.03 & 0.69 & 0.04 & 0.55 \\
+ & pre_treatment_change_in_group_5_crimes_50m & 0.01 & -0.00 & 0.72 & 0.00 & 0.71 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.60 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -159.16 & 0.91 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -261.65 & 0.45 \\
-\cline{1-7}
-\textit{Panel D} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.01 & 0.21 \\
+\textit{Panel B} & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 88.93 & 0.51 \\
 \cline{1-7}

### 2023-04-08 output/group_5_crimes_50m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_5_crimes_50m & 0.00 & 0.69 \\
 & pre_treatment_change_in_group_5_crimes_50m & 0.00 & 0.72 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.13 & 0.22 \\
 & job_density_2013 & 0.17 & 0.10 \\
 & med_hhinc2016 & 0.60 & 0.05 \\
 & poor_share2010 & 0.34 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.47 & 0.00 \\
 & no_cause & 0.18 & 0.95 \\
 & non_payment & 0.14 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.88 & 0.00 \\
 & hasAttyP & 0.07 & 0.00 \\
 & isEntityD & 0.27 & 0.06 \\
 & isEntityP & 0.14 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_6_crimes_1000m/tables/balance_table.tex
gennerated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_4_crimes_1000m & 3.40 & 0.30 & 0.00 & -0.01 & 0.93 \\
- & pre_treatment_change_in_group_4_crimes_1000m & 0.17 & -0.05 & 0.03 & -0.00 & 0.98 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_6_crimes_1000m & 202.74 & 9.39 & 0.02 & -0.38 & 0.92 \\
+ & pre_treatment_change_in_group_6_crimes_1000m & -2.85 & -0.09 & 0.60 & 0.00 & 0.98 \\
 \cline{1-7}
-\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.92 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -34.03 & 0.98 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -110.46 & 0.90 \\
- & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.90 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -51.28 & 0.91 \\
+\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.94 \\
+ & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -49.22 & 0.97 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -87.71 & 0.92 \\
+ & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.94 \\
+ & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -47.77 & 0.92 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.00 & 0.83 \\
- & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.99 \\
- & isEntityP & 0.81 & -0.07 & 0.00 & -0.00 & 0.85 \\
+\multirow[c]{3}{3cm}{\textit{Panel C}} & for_cause & 0.17 & 0.08 & 0.00 & -0.00 & 0.92 \\
+ & no_cause & 0.05 & 0.00 & 0.95 & -0.00 & 0.99 \\
+ & non_payment & 0.77 & -0.08 & 0.00 & -0.00 & 0.97 \\
+\cline{1-7}
+\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.00 & 0.93 \\
+ & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.99 \\
+ & isEntityP & 0.81 & -0.07 & 0.00 & -0.00 & 0.96 \\
 \cline{1-7}

### 2023-04-08 output/group_6_crimes_1000m/tables/pre_treatment_covariate_tests.tex
gennerated figures

--- 2023-04-08 output/group_5_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_5_crimes_500m & 0.00 & 0.37 \\
- & pre_treatment_change_in_group_5_crimes_500m & 0.00 & 0.05 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_6_crimes_1000m & 0.00 & 0.02 \\
+ & pre_treatment_change_in_group_6_crimes_1000m & 0.00 & 0.60 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.43 & 0.00 \\
- & no_cause & 0.03 & 0.95 \\
- & non_payment & 0.03 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.03 & 0.00 \\
+ & no_cause & 0.00 & 0.95 \\
+ & non_payment & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.61 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.09 & 0.00 \\
  & hasAttyP & 0.00 & 0.00 \\

### 2023-04-08 output/group_6_crimes_100m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_6_crimes_100m & 3.30 & 0.27 & 0.01 & 0.08 & 0.38 \\
 & pre_treatment_change_in_group_6_crimes_100m & -0.06 & 0.02 & 0.35 & -0.01 & 0.67 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.01 & 0.12 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 105.30 & 0.94 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,740.34 & 0.06 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 671.17 & 0.13 \\
\cline{1-7}
\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.41 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_6_crimes_100m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_6_crimes_100m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_6_crimes_100m & 0.00 & 0.35 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.04 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.56 & 0.96 \\
 & popdensity2010 & 0.01 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.28 & 0.00 \\
 & no_cause & 0.61 & 0.95 \\
 & non_payment & 0.52 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.64 & 0.00 \\
 & hasAttyP & 0.81 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.84 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_6_crimes_500m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_6_crimes_500m & 0.00 & 0.00 \\
 & pre_treatment_change_in_group_6_crimes_500m & 0.00 & 0.07 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.63 & 0.05 \\
 & poor_share2010 & 0.55 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.26 & 0.00 \\
 & no_cause & 0.22 & 0.95 \\
 & non_payment & 0.13 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.66 & 0.00 \\
 & hasAttyP & 0.00 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_6_crimes_50m/tables/balance_table.tex
gennerated figures

--- 2023-04-08 output/group_6_crimes_100m/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_6_crimes_100m & 3.30 & 0.27 & 0.01 & 0.08 & 0.38 \\
- & pre_treatment_change_in_group_6_crimes_100m & -0.06 & 0.02 & 0.35 & -0.01 & 0.67 \\
+\multirow[c]{2}{3cm}{\textit{Panel B}} & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 345.62 & 0.82 \\
+ & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,321.57 & 0.15 \\
 \cline{1-7}
-\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.01 & 0.12 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 105.30 & 0.94 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,740.34 & 0.06 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 671.17 & 0.13 \\
-\cline{1-7}
-\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.41 \\
+\textit{Panel C} & for_cause & 0.17 & 0.08 & 0.00 & 0.00 & 0.98 \\
 \cline{1-7}

### 2023-04-08 output/group_6_crimes_50m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_6_crimes_50m & 0.29 & 0.25 \\
 & pre_treatment_change_in_group_6_crimes_50m & 0.68 & 0.66 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.30 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.01 & 0.05 \\
 & poor_share2010 & 0.75 & 0.96 \\
 & popdensity2010 & 0.50 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.02 & 0.00 \\
 & no_cause & 0.08 & 0.95 \\
 & non_payment & 0.27 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.23 & 0.00 \\
 & hasAttyP & 0.68 & 0.00 \\
 & isEntityD & 0.72 & 0.06 \\
 & isEntityP & 0.98 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 src/02_analysis/constants.py

@@ -6,7 +6,6 @@ class Variables:
                 'group_4_crimes_50m',
                 'group_5_crimes_50m',
                 'group_6_crimes_50m',
-                'group_7_crimes_50m',
                 'group_0_crimes_100m',
                 'group_1_crimes_100m',
                 'group_2_crimes_100m', 
@@ -14,7 +13,6 @@ class Variables:
                 'group_4_crimes_100m',
                 'group_5_crimes_100m',
                 'group_6_crimes_100m',
-                'group_7_crimes_100m',
                 'group_0_crimes_500m',
                 'group_1_crimes_500m',
                 'group_2_crimes_500m', 
@@ -22,13 +20,11 @@ class Variables:
                 'group_4_crimes_500m',
                 'group_5_crimes_500m',
                 'group_6_crimes_500m',
-                'group_7_crimes_500m',
                 'group_0_crimes_1000m',
                 'group_1_crimes_1000m',
                 'group_2_crimes_1000m', 
                 'group_3_crimes_1000m',
                 'group_4_crimes_1000m',
                 'group_5_crimes_1000m',
-                'group_6_crimes_1000m',
-                'group_7_crimes_1000m']
+                'group_6_crimes_1000m']
 

### 2023-04-10 writing/presentations/march_15.tex
Updates from Overleaf

@@
 \useoutertheme{infolines} 
+\usepackage{tabularx}
+\usepackage{multirow}
 
@@
 
-\title[Eviction and Property Values]{Estimating the Effect of Eviction on Assessment Values}
+\title[Eviction and Property Values]{Estimating the Effect of Eviction on Crime}
 
@@
        \end{enumerate}
-       \item Sociologists have found large effects of evictions using non-experimental methods=
+       \item Sociologists have found large effects of evictions using non-experimental methods
        \item Economists are just beginning to study eviction
@@
     \end{enumerate}
-    \item Either way, understanding effect is important to understanding how eviction is affecting communitiies
+    \item Either way, understanding effect is important to understanding how eviction is affecting communities
     \item Kroeger and La Mattina (2020): Nuisance ordinances increase eviction risk in Ohio
@@
         \end{enumerate}
-        \item Create 100m radius around every eviction and match to crimes which fall into that radius
+        \item Create 1000m radius around every eviction and match to crimes which fall into that radius
     \end{enumerate}
@@
     \tiny
-    \input{output/01_exploratory/tables/summary_statistics.tex}
-    \label{tab:my_label}
-\end{table}
-\end{frame}
-
-\begin{frame}{Data}
-\begin{table}[H]
-    \centering
-    \tiny
-    \input{output/01_exploratory/tables/balance_table.tex}
+    \input{output/summary_statistics}
     \label{tab:my_label}
@@
 \begin{frame}{Empirical Strategy}
-    \begin{enumerate}
-        \item Most eviction cases in Massachusetts are filed in the Massachusetts Housing Court
-        \item Within the Housing Court, cases are assigned to about 15 judges quasi-randomly conditional on city and time
-        \item This is the basis for an examiner design study, which uses judge dummies as instruments
-    \end{enumerate}
+
+    Let $G_i$ be the month during which the eviction case involving property $i$ was filed, such that $G_i = g \in \{\text{May} \; 2019, \text{June} \; 2019, ..., \text{May} \; 2021\}$.
+Let $C_i = 1$ if the eviction case involving $i$ resulted in a victory for the defendant and $0$ otherwise.
+If $G_i = g$ and $C_i = 0$, then property $i$ is a treated property and a member of the cohort first treated during month $g$ (cohort $g$).
+If $C_i=1$, then property $i$ is a never-treated property.
+
+    Let $Y_{i,t}$ be property $i$'s outcome during month $t$ and define $\Delta Y_{i, g-1, t} \equiv Y_{i,t} - Y_{i,g-1}$ so that $\Delta Y_{i, g-1, t}$ is the change in property $i$'s Zestimate between months $t$ and $g-1$.
+
+    The following is an unconditional estimator for $ATT(g,t)$, the average treatment affect during month $t$ for cohort $g$.
+    \begin{align}
+        \hat{ATT}^{nev}_{un}(g, t) = \frac{\sum_i\Delta Y_{i, g-1, t}\mathds{1}\{G_i=g\}}{\sum_i\mathds{1}\{G_i=g\}} - \frac{\sum_i\Delta Y_{i, g-1, t}\mathds{1}\{C_i=1\}}{\sum_i\mathds{1}\{C_i=1\}}
+    \end{align}
+
+\end{frame}
+
+\section{Empirical Strategy}
+\begin{frame}{Empirical Strategy}
+\begin{table}[H]
+    \centering
+    \tiny
+    \input{output/treatment_timings}
+    \label{tab:my_label}
+\end{table}
 \end{frame}
@@
     \tiny
-    \input{output/01_exploratory/tables/placebo_first_stage.tex}
+    \input{output/pre_treatment_covariate_tests}
     \label{tab:my_label}
@@
 
-\begin{frame}{Preliminary Results}
+\begin{frame}{Empirical Strategy}
 \begin{table}[H]
@@
     \tiny
-        \input{output/01_exploratory/tables/ln_total_val_results_table.tex}
+    \input{output/balance_table}
     \label{tab:my_label}
@@
 \end{frame}
-\begin{frame}{Preliminary Results}
+
+\begin{frame}{Results: All Crime}
+
     \begin{table}[H]
@@
         \tiny
-        \input{output/01_exploratory/tables/ln_bldg_val_results_table.tex}
+        \includegraphics[scale=0.6]{output/all.png}
+        \label{tab:my_label}
+    \end{table}
+\end{frame}
+\begin{frame}{Results: Assaults}
+
+    \begin{table}[H]
+        \centering
+        \tiny
+        \includegraphics[scale=0.6]{output/assaults.png}
+        \label{tab:my_label}
+    \end{table}
+\end{frame}
+\begin{frame}{Results: Investigations}
+
+    \begin{table}[H]
+        \centering
+        \tiny
+        \includegraphics[scale=0.6]{output/investigations.png}
         \label{tab:my_label}
@@
     \begin{enumerate}
-        \item Figure out what to do about my lack of power
-        \item Find a systematic way to drop observations in sparse city-years
-        \item Speak to an assessor from Massachusetts to understand whether there is even a mechanism through which I might see an effect
-        \item Think about whether my instrument is truly valid
+        \item Robustness checks
+
+        \item Qualitiative analysis of what is happening in the 2 months before filing
+        \item Am I double counting crimes?
     \end{enumerate}

### 2023-04-10 output/group_0_crimes_1000m/tables/balance_table.tex
Easy switching between monthly and weekly analysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_0_crimes_1000m & 4,045.37 & 166.28 & 0.04 & -69.59 & 0.38 \\
- & pre_treatment_change_in_group_0_crimes_1000m & -25.13 & -2.31 & 0.02 & 0.42 & 0.66 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & Total Group 0 Incidents, 2017 & 3,981.99 & 163.75 & 0.04 & -99.78 & 0.18 \\
+ & $\Delta$ Group 0 Incidents, 2017-2019 & -490.95 & -20.32 & 0.20 & 12.30 & 0.43 \\
 \cline{1-7}
-\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.01 & 0.47 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -282.14 & 0.85 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -836.74 & 0.34 \\
- & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.36 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -396.20 & 0.37 \\
+\multirow[c]{4}{3cm}{\textit{Panel B}} & Bachelor's degree, 2010 & 0.33 & 0.01 & 0.22 & -0.01 & 0.28 \\
+ & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & -398.45 & 0.79 \\
+ & Poverty rate, 2010 & 0.28 & -0.00 & 0.96 & -0.01 & 0.17 \\
+ & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & -573.69 & 0.16 \\
 \cline{1-7}
-\multirow[c]{2}{3cm}{\textit{Panel C}} & no_cause & 0.05 & 0.00 & 0.95 & -0.00 & 0.91 \\
- & non_payment & 0.77 & -0.08 & 0.00 & -0.01 & 0.26 \\
+\multirow[c]{2}{3cm}{\textit{Panel C}} & Filing without cause & 0.05 & 0.00 & 0.95 & -0.00 & 0.87 \\
+ & Filing for nonpayment & 0.77 & -0.08 & 0.00 & -0.02 & 0.08 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyD & 0.07 & -0.03 & 0.00 & -0.00 & 0.88 \\
- & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.94 \\
- & isEntityP & 0.81 & -0.07 & 0.00 & -0.01 & 0.23 \\
+\multirow[c]{2}{3cm}{\textit{Panel D}} & Defendant has attorney & 0.07 & -0.03 & 0.00 & -0.00 & 0.80 \\
+ & Defendant is entity & 0.02 & -0.01 & 0.06 & -0.00 & 0.90 \\
 \cline{1-7}

### 2023-04-10 output/group_0_crimes_1000m/tables/pre_treatment_covariate_tests.tex
Easy switching between monthly and weekly analysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_1000m & 0.00 & 0.04 \\
- & pre_treatment_change_in_group_0_crimes_1000m & 0.00 & 0.02 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 0 Incidents, 2017 & 0.00 & 0.04 \\
+ & $\Delta$ Group 0 Incidents, 2017-2019 & 0.00 & 0.20 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.02 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.71 & 0.05 \\
+ & Poverty rate, 2010 & 0.00 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.11 & 0.00 \\
- & no_cause & 0.00 & 0.95 \\
- & non_payment & 0.00 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.06 & 0.00 \\
+ & Filing without cause & 0.01 & 0.95 \\
+ & Filing for nonpayment & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.01 & 0.00 \\
- & hasAttyP & 0.69 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.05 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.01 & 0.00 \\
+ & Plaintiff has attorney & 0.33 & 0.00 \\
+ & Defendant is entity & 0.00 & 0.06 \\
+ & Plaintiff is entity & 0.22 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_1_crimes_1000m/tables/pre_treatment_covariate_tests.tex
Easy switching between monthly and weekly analysis

--- 2023-04-03 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.00 \\
- & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.48 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 1 Incidents, 2017 & 0.00 & 0.09 \\
+ & $\Delta$ Group 1 Incidents, 2017-2019 & 0.00 & 0.38 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.00 & 0.05 \\
+ & Poverty rate, 2010 & 0.00 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.35 & 0.00 \\
- & no_cause & 0.67 & 0.95 \\
- & non_payment & 0.28 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.44 & 0.00 \\
+ & Filing without cause & 0.11 & 0.95 \\
+ & Filing for nonpayment & 0.10 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.78 & 0.00 \\
- & hasAttyP & 0.51 & 0.00 \\
- & isEntityD & 0.28 & 0.06 \\
- & isEntityP & 0.92 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.00 & 0.00 \\
+ & Plaintiff has attorney & 0.00 & 0.00 \\
+ & Defendant is entity & 0.00 & 0.06 \\
+ & Plaintiff is entity & 0.04 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_2_crimes_1000m/tables/balance_table.tex
Easy switching between monthly and weekly analysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_1000m & 59.19 & 3.58 & 0.18 & 0.65 & 0.80 \\
- & pre_treatment_change_in_group_2_crimes_1000m & -0.67 & -0.05 & 0.50 & -0.01 & 0.93 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & Total Group 2 Incidents, 2017 & 58.13 & 3.46 & 0.19 & 0.12 & 0.96 \\
+ & $\Delta$ Group 2 Incidents, 2017-2019 & -10.95 & -0.05 & 0.92 & -0.03 & 0.96 \\
 \cline{1-7}
-\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.60 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 113.70 & 0.94 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 593.73 & 0.49 \\
- & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.44 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 253.67 & 0.52 \\
+\multirow[c]{5}{3cm}{\textit{Panel B}} & Bachelor's degree, 2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.93 \\
+ & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & 29.56 & 0.98 \\
+ & Median household income, 2016 & 48,534.18 & 1,788.07 & 0.05 & 104.87 & 0.91 \\
+ & Poverty rate, 2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.90 \\
+ & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & 47.81 & 0.91 \\
 \cline{1-7}
-\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.87 \\
+\multirow[c]{2}{3cm}{\textit{Panel D}} & Defendant is entity & 0.02 & -0.01 & 0.06 & 0.00 & 0.99 \\
+ & Plaintiff is entity & 0.81 & -0.07 & 0.00 & 0.00 & 0.82 \\
 \cline{1-7}

### 2023-04-10 output/group_2_crimes_1000m/tables/pre_treatment_covariate_tests.tex
Easy switching between monthly and weekly analysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_1000m & 0.00 & 0.18 \\
- & pre_treatment_change_in_group_2_crimes_1000m & 0.00 & 0.50 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 2 Incidents, 2017 & 0.00 & 0.19 \\
+ & $\Delta$ Group 2 Incidents, 2017-2019 & 0.00 & 0.92 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.00 & 0.05 \\
+ & Poverty rate, 2010 & 0.00 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.45 & 0.00 \\
- & no_cause & 0.16 & 0.95 \\
- & non_payment & 0.14 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.96 & 0.00 \\
+ & Filing without cause & 0.72 & 0.95 \\
+ & Filing for nonpayment & 0.92 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.67 & 0.00 \\
- & hasAttyP & 0.13 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.53 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.41 & 0.00 \\
+ & Plaintiff has attorney & 0.44 & 0.00 \\
+ & Defendant is entity & 0.00 & 0.06 \\
+ & Plaintiff is entity & 0.04 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_3_crimes_1000m/tables/balance_table.tex
Easy switching between monthly and weekly analysis

@@
 \midrule
-\textit{Panel A} & total_twenty_seventeen_group_3_crimes_1000m & 415.94 & 15.64 & 0.04 & 0.55 & 0.94 \\
+\textit{Panel A} & Total Group 3 Incidents, 2017 & 410.15 & 15.31 & 0.04 & -1.86 & 0.79 \\
 \cline{1-7}
-\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.96 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 19.55 & 0.99 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 64.10 & 0.94 \\
- & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.94 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 29.70 & 0.95 \\
+\multirow[c]{4}{3cm}{\textit{Panel B}} & Bachelor's degree, 2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.85 \\
+ & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & -66.40 & 0.96 \\
+ & Median household income, 2016 & 48,534.18 & 1,788.07 & 0.05 & -220.39 & 0.80 \\
+ & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & -101.84 & 0.81 \\
 \cline{1-7}
-\multirow[c]{2}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & 0.00 & 0.89 \\
- & isEntityP & 0.81 & -0.07 & 0.00 & 0.00 & 0.89 \\
+\multirow[c]{2}{3cm}{\textit{Panel D}} & Plaintiff has attorney & 0.88 & -0.04 & 0.00 & -0.00 & 0.65 \\
+ & Plaintiff is entity & 0.81 & -0.07 & 0.00 & -0.00 & 0.65 \\
 \cline{1-7}

### 2023-04-10 output/group_3_crimes_1000m/tables/pre_treatment_covariate_tests.tex
Easy switching between monthly and weekly analysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_1000m & 0.00 & 0.04 \\
- & pre_treatment_change_in_group_3_crimes_1000m & 0.61 & 0.17 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 3 Incidents, 2017 & 0.00 & 0.04 \\
+ & $\Delta$ Group 3 Incidents, 2017-2019 & 0.05 & 0.05 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.00 & 0.05 \\
+ & Poverty rate, 2010 & 0.37 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.45 & 0.00 \\
- & no_cause & 0.26 & 0.95 \\
- & non_payment & 0.95 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.43 & 0.00 \\
+ & Filing without cause & 0.30 & 0.95 \\
+ & Filing for nonpayment & 0.92 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.99 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
- & isEntityD & 0.15 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.95 & 0.00 \\
+ & Plaintiff has attorney & 0.00 & 0.00 \\
+ & Defendant is entity & 0.14 & 0.06 \\
+ & Plaintiff is entity & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/summary_statistics/tables/summary_statistics.tex
Easy switching between monthly and weekly analysis

@@
 \toprule
- &  & Mean & Median & S.D. & N \\
-Panel & Variable &  &  &  &  \\
+ &  & Mean & S.D. & N \\
+Panel & Variable &  &  &  \\
 \midrule
-\multirow[c]{6}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & pre_treatment_change_in_group_0_crimes_100m & -0.30 & 0.00 & 2.38 & 6,060 \\
- & pre_treatment_change_in_group_1_crimes_100m & 0.02 & 0.00 & 0.66 & 6,060 \\
- & pre_treatment_change_in_group_2_crimes_100m & 0.03 & 0.00 & 0.68 & 6,060 \\
- & twenty_seventeen_group_0_crimes_100m & 2.32 & 2.00 & 2.83 & 6,060 \\
- & twenty_seventeen_group_1_crimes_100m & 0.17 & 0.00 & 0.47 & 6,060 \\
- & twenty_seventeen_group_2_crimes_100m & 0.19 & 0.00 & 0.47 & 6,060 \\
-\cline{1-6}
-\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.31 & 0.24 & 0.22 & 6,060 \\
- & job_density_2013 & 14,806.08 & 2,425.15 & 40,595.37 & 6,060 \\
- & med_hhinc2016 & 47,188.87 & 41,146.00 & 24,703.65 & 6,060 \\
- & poor_share2010 & 0.28 & 0.25 & 0.14 & 6,060 \\
- & popdensity2010 & 22,704.52 & 20,644.44 & 13,091.45 & 6,060 \\
-\cline{1-6}
-\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.17 & 0.00 & 0.37 & 6,060 \\
- & no_cause & 0.05 & 0.00 & 0.22 & 6,060 \\
- & non_payment & 0.78 & 1.00 & 0.42 & 6,060 \\
-\cline{1-6}
-\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.08 & 0.00 & 0.27 & 6,060 \\
- & hasAttyP & 0.88 & 1.00 & 0.32 & 6,060 \\
- & isEntityD & 0.02 & 0.00 & 0.14 & 6,060 \\
- & isEntityP & 0.81 & 1.00 & 0.39 & 6,060 \\
-\cline{1-6}
-\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & case_duration & 58.17 & 19.00 & 88.96 & 5,500 \\
- & defaulted & 0.19 & 0.00 & 0.39 & 6,060 \\
- & dismissed & 0.27 & 0.00 & 0.44 & 6,060 \\
- & heard & 0.03 & 0.00 & 0.17 & 6,060 \\
- & judgment & 1,938.57 & 0.00 & 5,337.87 & 6,060 \\
- & mediated & 0.40 & 0.00 & 0.49 & 6,060 \\
-\cline{1-6}
-\multirow[c]{6}{4cm}{\textit{Panel F: Post-treatment Outcomes}} & group_0_crimes_100m_1_years_relative_to_treatment & 1.46 & 1.00 & 3.05 & 3,039 \\
- & group_0_crimes_100m_2_years_relative_to_treatment & 1.48 & 1.00 & 2.31 & 2,830 \\
- & group_1_crimes_100m_1_years_relative_to_treatment & 0.14 & 0.00 & 0.45 & 3,039 \\
- & group_1_crimes_100m_2_years_relative_to_treatment & 0.10 & 0.00 & 0.36 & 2,830 \\
- & group_2_crimes_100m_1_years_relative_to_treatment & 0.20 & 0.00 & 0.55 & 3,039 \\
- & group_2_crimes_100m_2_years_relative_to_treatment & 0.22 & 0.00 & 0.63 & 2,830 \\
-\cline{1-6}
+\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & $\Delta$ Group 0 Incidents, 2017-2019 & -532.85 & 465.54 & 6,060 \\
+ & Total Group 0 Incidents, 2017 & 4,068.25 & 2,258.29 & 6,060 \\
+\cline{1-5}
+\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.31 & 0.22 & 6,060 \\
+ & Job density, 2013 & 14,806.08 & 40,595.37 & 6,060 \\
+ & Median household income, 2016 & 47,188.87 & 24,703.65 & 6,060 \\
+ & Poverty rate, 2010 & 0.28 & 0.14 & 6,060 \\
+ & Population density, 2010 & 22,704.52 & 13,091.45 & 6,060 \\
+\cline{1-5}
+\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.17 & 0.37 & 6,060 \\
+ & Filing without cause & 0.05 & 0.22 & 6,060 \\
+ & Filing for nonpayment & 0.78 & 0.42 & 6,060 \\
+\cline{1-5}
+\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.08 & 0.27 & 6,060 \\
+ & Plaintiff has attorney & 0.88 & 0.32 & 6,060 \\
+ & Defendant is entity & 0.02 & 0.14 & 6,060 \\
+ & Plaintiff is entity & 0.81 & 0.39 & 6,060 \\
+\cline{1-5}
+\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 58.17 & 88.96 & 5,500 \\
+ & Judgment by default & 0.19 & 0.39 & 6,060 \\
+ & Case dismissed & 0.27 & 0.44 & 6,060 \\
+ & Case heard & 0.03 & 0.17 & 6,060 \\
+ & Money judgment & 1,938.57 & 5,337.87 & 6,060 \\
+ & Case mediated & 0.40 & 0.49 & 6,060 \\
+\cline{1-5}
 \bottomrule

### 2023-04-10 src/02_analysis/stats_utilities.py

@@ -13,12 +13,6 @@ from differences.did.pscore_cal import pscore_mle
 from typing import List
 
 
-
-
-
-
-
-
 def add_missing_indicators(df: pd.DataFrame, missing_variables: List[str], pre_treatment_covariates: List[str]):
     missing_indicators = []
     for missing_variable in missing_variables:
@@ -27,6 +21,7 @@ def add_missing_indicators(df: pd.DataFrame, missing_variables: List[str], pre_t
         pre_treatment_covariates.append(missing_variable + '_missing')
         missing_indicators.append(missing_variable + '_missing')
     return missing_indicators
+
 
 def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.DataFrame, output_directory: str):
     # Store pre-treatment panel names.
@@ -111,6 +106,7 @@ def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.D
     # Export to LaTeX.
     filename = join(output_directory, "balance_table.tex")
     latex = (balance_table
+             .rename(index=variable_display_names_dict)
              .style
              .format(thousands=",",
                      na_rep='',
@@ -136,7 +132,7 @@ def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.D
 
 def select_controls(df: pd.DataFrame, treatment_date_variable: str, analysis: str, output_directory: str):
     """Choose covariates to include in D.R. model."""
-    covariate_exploration_table_columns = ["", ""] # TODO: Add column naming logic.
+    covariate_exploration_table_columns = ["", ""]  # TODO: Add column naming logic.
 
     # Run produce summary statistics on the DataFrame to get names of column names of potential pre-treatment covaiates.
     summary_statistics, variable_display_names_dict = produce_summary_statistics(df, 'latest_docket_date')
@@ -153,7 +149,10 @@ def select_controls(df: pd.DataFrame, treatment_date_variable: str, analysis: st
     # Store independent and dependent variables.
     independent_variable = 'judgment_for_plaintiff'
     dependent_variable = f'change_in_{analysis}_over_all_treated_weeks'
-    last_week_in_panel = '2023-02'
+    if "month" in treatment_date_variable:
+        last_week_in_panel = '2023-01'
+    else:
+        last_week_in_panel = '2023-00'
     first_treated_week = df[treatment_date_variable].sort_values().iloc[0]
[…]

### 2023-04-10 output/group_0_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited to 500m annalysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_500m & 0.00 & 0.01 \\
- & pre_treatment_change_in_group_0_crimes_500m & 0.00 & 0.30 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 0 Incidents, 2017 & 0.00 & 0.01 \\
+ & $\Delta$ Group 0 Incidents, 2017-2019 & 0.00 & 0.19 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.20 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.22 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.38 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.91 & 0.05 \\
+ & Poverty rate, 2010 & 0.00 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.47 & 0.00 \\
- & no_cause & 0.01 & 0.95 \\
- & non_payment & 0.03 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.36 & 0.00 \\
+ & Filing without cause & 0.02 & 0.95 \\
+ & Filing for nonpayment & 0.03 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.12 & 0.00 \\
- & hasAttyP & 0.37 & 0.00 \\
- & isEntityD & 0.12 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.09 & 0.00 \\
+ & Plaintiff has attorney & 0.85 & 0.00 \\
+ & Defendant is entity & 0.01 & 0.06 \\
+ & Plaintiff is entity & 0.06 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_1_crimes_500m/tables/balance_table.tex
limited to 500m annalysis

--- 2023-04-06 output/group_1_crimes_500m/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_1_crimes_500m & 95.93 & 5.50 & 0.02 & 1.21 & 0.57 \\
- & pre_treatment_change_in_group_1_crimes_500m & -0.07 & -0.09 & 0.36 & 0.00 & 0.97 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & Total Group 1 Incidents, 2017 & 95.23 & 5.45 & 0.02 & 1.12 & 0.59 \\
+ & $\Delta$ Group 1 Incidents, 2017-2019 & 2.34 & 1.50 & 0.09 & -0.05 & 0.96 \\
 \cline{1-7}
-\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.56 \\
- & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 131.16 & 0.93 \\
- & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 666.70 & 0.45 \\
- & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.39 \\
- & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 285.95 & 0.48 \\
+\multirow[c]{5}{3cm}{\textit{Panel B}} & Bachelor's degree, 2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.58 \\
+ & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & 122.05 & 0.93 \\
+ & Median household income, 2016 & 48,534.18 & 1,788.07 & 0.05 & 623.35 & 0.47 \\
+ & Poverty rate, 2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.42 \\
+ & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & 267.17 & 0.50 \\
 \cline{1-7}
-\textit{Panel C} & no_cause & 0.05 & 0.00 & 0.95 & 0.00 & 0.92 \\
-\cline{1-7}
-\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.86 \\
+\textit{Panel D} & Defendant is entity & 0.02 & -0.01 & 0.06 & 0.00 & 0.87 \\
 \cline{1-7}

### 2023-04-10 output/group_1_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited to 500m annalysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_500m & 0.00 & 0.02 \\
- & pre_treatment_change_in_group_1_crimes_500m & 0.00 & 0.43 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 1 Incidents, 2017 & 0.00 & 0.02 \\
+ & $\Delta$ Group 1 Incidents, 2017-2019 & 0.00 & 0.09 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.00 & 0.05 \\
+ & Poverty rate, 2010 & 0.00 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.51 & 0.00 \\
- & no_cause & 0.02 & 0.95 \\
- & non_payment & 0.05 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.86 & 0.00 \\
+ & Filing without cause & 0.15 & 0.95 \\
+ & Filing for nonpayment & 0.54 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.04 & 0.00 \\
- & hasAttyP & 0.52 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.34 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.10 & 0.00 \\
+ & Plaintiff has attorney & 0.12 & 0.00 \\
+ & Defendant is entity & 0.00 & 0.06 \\
+ & Plaintiff is entity & 1.00 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_2_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited to 500m annalysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_500m & 0.00 & 0.87 \\
- & pre_treatment_change_in_group_2_crimes_500m & 0.00 & 0.67 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 2 Incidents, 2017 & 0.00 & 0.83 \\
+ & $\Delta$ Group 2 Incidents, 2017-2019 & 0.00 & 0.50 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.00 & 0.05 \\
+ & Poverty rate, 2010 & 0.00 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.22 & 0.00 \\
- & no_cause & 0.28 & 0.95 \\
- & non_payment & 0.09 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.52 & 0.00 \\
+ & Filing without cause & 0.81 & 0.95 \\
+ & Filing for nonpayment & 0.49 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.84 & 0.00 \\
- & hasAttyP & 0.07 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.11 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.56 & 0.00 \\
+ & Plaintiff has attorney & 0.84 & 0.00 \\
+ & Defendant is entity & 0.00 & 0.06 \\
+ & Plaintiff is entity & 0.93 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited to 500m annalysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.02 \\
- & pre_treatment_change_in_group_3_crimes_500m & 0.04 & 0.81 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 3 Incidents, 2017 & 0.00 & 0.02 \\
+ & $\Delta$ Group 3 Incidents, 2017-2019 & 0.00 & 0.03 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.01 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.24 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.40 & 0.05 \\
+ & Poverty rate, 2010 & 0.20 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.75 & 0.00 \\
- & no_cause & 0.94 & 0.95 \\
- & non_payment & 0.85 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.43 & 0.00 \\
+ & Filing without cause & 0.30 & 0.95 \\
+ & Filing for nonpayment & 0.98 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.43 & 0.00 \\
- & hasAttyP & 0.41 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.64 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.54 & 0.00 \\
+ & Plaintiff has attorney & 0.00 & 0.00 \\
+ & Defendant is entity & 0.17 & 0.06 \\
+ & Plaintiff is entity & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited to 500m annalysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.01 \\
- & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.27 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 4 Incidents, 2017 & 0.00 & 0.01 \\
+ & $\Delta$ Group 4 Incidents, 2017-2019 & 0.00 & 0.92 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.00 & 0.05 \\
+ & Poverty rate, 2010 & 0.00 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.08 & 0.00 \\
- & no_cause & 0.00 & 0.95 \\
- & non_payment & 0.00 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.02 & 0.00 \\
+ & Filing without cause & 0.01 & 0.95 \\
+ & Filing for nonpayment & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.26 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
- & isEntityD & 0.06 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.37 & 0.00 \\
+ & Plaintiff has attorney & 0.00 & 0.00 \\
+ & Defendant is entity & 0.04 & 0.06 \\
+ & Plaintiff is entity & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_5_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited to 500m annalysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_5_crimes_500m & 0.00 & 0.37 \\
- & pre_treatment_change_in_group_5_crimes_500m & 0.00 & 0.05 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 5 Incidents, 2017 & 0.00 & 0.36 \\
+ & $\Delta$ Group 5 Incidents, 2017-2019 & 0.00 & 0.53 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.00 & 0.05 \\
+ & Poverty rate, 2010 & 0.00 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.43 & 0.00 \\
- & no_cause & 0.03 & 0.95 \\
- & non_payment & 0.03 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.39 & 0.00 \\
+ & Filing without cause & 0.00 & 0.95 \\
+ & Filing for nonpayment & 0.01 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.61 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.09 & 0.00 \\
+ & Plaintiff has attorney & 0.00 & 0.00 \\
+ & Defendant is entity & 0.67 & 0.06 \\
+ & Plaintiff is entity & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_6_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited to 500m annalysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_6_crimes_500m & 0.00 & 0.00 \\
- & pre_treatment_change_in_group_6_crimes_500m & 0.00 & 0.07 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 6 Incidents, 2017 & 0.00 & 0.00 \\
+ & $\Delta$ Group 6 Incidents, 2017-2019 & 0.00 & 0.45 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.63 & 0.05 \\
- & poor_share2010 & 0.55 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.51 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.09 & 0.05 \\
+ & Poverty rate, 2010 & 0.00 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.26 & 0.00 \\
- & no_cause & 0.22 & 0.95 \\
- & non_payment & 0.13 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.28 & 0.00 \\
+ & Filing without cause & 0.86 & 0.95 \\
+ & Filing for nonpayment & 0.40 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.66 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.49 & 0.00 \\
+ & Plaintiff has attorney & 0.24 & 0.00 \\
+ & Defendant is entity & 0.00 & 0.06 \\
+ & Plaintiff is entity & 0.37 & 0.00 \\
 \cline{1-4}

### 2023-04-10 src/02_analysis/figure_utilities.py

@@ -35,11 +35,12 @@ def aggregate_by_event_time_and_plot(att_gt,
     fig, ax = plt.subplots(layout='constrained')
     x = results_df.index
     y = results_df['ATT']
-    y_upper = results_df['upper']
-    y_lower = results_df['lower']
+    y_upper = results_df['upper'].where(results_df['upper'].notna(), y)
+    y_lower = results_df['lower'].where(results_df['lower'].notna(), y)
     ax.set_ylabel("ATT")
     ax.set_title(title)
-    ax.set_xlabel("Two Week Period Relative to Treatment")
+    ax.set_xlabel("Month Relative to Treatment")
+    ax.set_xticks(x)
     plot_labeled_vline(ax, x=0, text="Treatment", color='black', linestyle='-',
                                         text_y_location_normalized=0.95)
     plot_scatter_with_shaded_errors(ax,
@@ -71,7 +72,7 @@ def aggregate_by_time_and_plot(att_gt, int_to_month_dictionary: dict, output_fol
     y_lower = results_df.iloc[:, 2]
     ax.set_xlabel("Month")
     ax.set_ylabel("ATT")
-    ax.set_xlabel("Two Week Period Relative to Treatment")
+    ax.set_xlabel("Month Relative to Treatment")
     ax.set_title(title)
     plot_labeled_vline(ax, x=results_df.index.tolist()[0], text="Earliest Treatment Date in Sample",
                                         color='black', linestyle='-',

### 2023-04-10 output/group_0_crimes_500m/tables/pre_treatment_covariate_tests.tex
ready tos tart writign

@@
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.38 & 0.22 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.40 & 0.22 \\
  & Job density, 2013 & 0.00 & 0.10 \\
- & Median household income, 2016 & 0.91 & 0.05 \\
+ & Median household income, 2016 & 0.88 & 0.05 \\
  & Poverty rate, 2010 & 0.00 & 0.96 \\
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.36 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.34 & 0.00 \\
  & Filing without cause & 0.02 & 0.95 \\
@@
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.09 & 0.00 \\
- & Plaintiff has attorney & 0.85 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.10 & 0.00 \\
+ & Plaintiff has attorney & 0.98 & 0.00 \\
  & Defendant is entity & 0.01 & 0.06 \\
- & Plaintiff is entity & 0.06 & 0.00 \\
+ & Plaintiff is entity & 0.04 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_1_crimes_500m/tables/balance_table.tex
ready tos tart writign

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & Total Group 1 Incidents, 2017 & 95.23 & 5.45 & 0.02 & 1.12 & 0.59 \\
- & $\Delta$ Group 1 Incidents, 2017-2019 & 2.34 & 1.50 & 0.09 & -0.05 & 0.96 \\
+\multirow[c]{2}{3cm}{\textit{Panel A}} & Total Group 1 Incidents, 2017 & 59.33 & 3.74 & 0.00 & 1.22 & 0.24 \\
+ & $\Delta$ Group 1 Incidents, 2017-2019 & -14.54 & -0.44 & 0.45 & -0.35 & 0.56 \\
 \cline{1-7}
-\multirow[c]{5}{3cm}{\textit{Panel B}} & Bachelor's degree, 2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.58 \\
- & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & 122.05 & 0.93 \\
- & Median household income, 2016 & 48,534.18 & 1,788.07 & 0.05 & 623.35 & 0.47 \\
- & Poverty rate, 2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.42 \\
- & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & 267.17 & 0.50 \\
+\multirow[c]{3}{3cm}{\textit{Panel B}} & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & 207.41 & 0.89 \\
+ & Poverty rate, 2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.13 \\
+ & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & 479.29 & 0.27 \\
 \cline{1-7}
-\textit{Panel D} & Defendant is entity & 0.02 & -0.01 & 0.06 & 0.00 & 0.87 \\
+\textit{Panel D} & Defendant is entity & 0.02 & -0.01 & 0.06 & 0.00 & 0.75 \\
 \cline{1-7}

### 2023-04-10 output/group_1_crimes_500m/tables/pre_treatment_covariate_tests.tex
ready tos tart writign

--- 2023-04-08 output/group_1_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_500m & 0.00 & 0.02 \\
- & pre_treatment_change_in_group_1_crimes_500m & 0.00 & 0.43 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 1 Incidents, 2017 & 0.00 & 0.00 \\
+ & $\Delta$ Group 1 Incidents, 2017-2019 & 0.00 & 0.45 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.51 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.09 & 0.05 \\
+ & Poverty rate, 2010 & 0.00 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.51 & 0.00 \\
- & no_cause & 0.02 & 0.95 \\
- & non_payment & 0.05 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.28 & 0.00 \\
+ & Filing without cause & 0.86 & 0.95 \\
+ & Filing for nonpayment & 0.40 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.04 & 0.00 \\
- & hasAttyP & 0.52 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.34 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.49 & 0.00 \\
+ & Plaintiff has attorney & 0.24 & 0.00 \\
+ & Defendant is entity & 0.00 & 0.06 \\
+ & Plaintiff is entity & 0.37 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_2_crimes_500m/tables/pre_treatment_covariate_tests.tex
ready tos tart writign

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 2 Incidents, 2017 & 0.00 & 0.83 \\
- & $\Delta$ Group 2 Incidents, 2017-2019 & 0.00 & 0.50 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 2 Incidents, 2017 & 0.00 & 0.02 \\
+ & $\Delta$ Group 2 Incidents, 2017-2019 & 0.00 & 0.09 \\
 \cline{1-4}
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.52 & 0.00 \\
- & Filing without cause & 0.81 & 0.95 \\
- & Filing for nonpayment & 0.49 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.86 & 0.00 \\
+ & Filing without cause & 0.15 & 0.95 \\
+ & Filing for nonpayment & 0.54 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.56 & 0.00 \\
- & Plaintiff has attorney & 0.84 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.10 & 0.00 \\
+ & Plaintiff has attorney & 0.12 & 0.00 \\
  & Defendant is entity & 0.00 & 0.06 \\
- & Plaintiff is entity & 0.93 & 0.00 \\
+ & Plaintiff is entity & 1.00 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
ready tos tart writign

--- 2023-04-08 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.02 \\
- & pre_treatment_change_in_group_3_crimes_500m & 0.04 & 0.81 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 3 Incidents, 2017 & 0.00 & 0.03 \\
+ & $\Delta$ Group 3 Incidents, 2017-2019 & 0.00 & 0.55 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.01 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.00 & 0.05 \\
+ & Poverty rate, 2010 & 0.09 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.75 & 0.00 \\
- & no_cause & 0.94 & 0.95 \\
- & non_payment & 0.85 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.06 & 0.00 \\
+ & Filing without cause & 0.02 & 0.95 \\
+ & Filing for nonpayment & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.43 & 0.00 \\
- & hasAttyP & 0.41 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.64 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.38 & 0.00 \\
+ & Plaintiff has attorney & 0.09 & 0.00 \\
+ & Defendant is entity & 0.00 & 0.06 \\
+ & Plaintiff is entity & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
ready tos tart writign

--- 2023-04-08 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.01 \\
- & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.27 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 4 Incidents, 2017 & 0.00 & 0.40 \\
+ & $\Delta$ Group 4 Incidents, 2017-2019 & 0.00 & 0.46 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
+ & Job density, 2013 & 0.12 & 0.10 \\
+ & Median household income, 2016 & 0.00 & 0.05 \\
+ & Poverty rate, 2010 & 0.00 & 0.96 \\
+ & Population density, 2010 & 0.33 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.08 & 0.00 \\
- & no_cause & 0.00 & 0.95 \\
- & non_payment & 0.00 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.38 & 0.00 \\
+ & Filing without cause & 0.16 & 0.95 \\
+ & Filing for nonpayment & 0.93 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.26 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
- & isEntityD & 0.06 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.13 & 0.00 \\
+ & Plaintiff has attorney & 0.75 & 0.00 \\
+ & Defendant is entity & 0.01 & 0.06 \\
+ & Plaintiff is entity & 0.45 & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_5_crimes_500m/tables/pre_treatment_covariate_tests.tex
ready tos tart writign

--- 2023-04-08 output/group_5_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_5_crimes_500m & 0.00 & 0.37 \\
- & pre_treatment_change_in_group_5_crimes_500m & 0.00 & 0.05 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 5 Incidents, 2017 & nan & nan \\
+ & $\Delta$ Group 5 Incidents, 2017-2019 & nan & nan \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & nan & 0.22 \\
+ & Job density, 2013 & nan & 0.10 \\
+ & Median household income, 2016 & nan & 0.05 \\
+ & Poverty rate, 2010 & nan & 0.96 \\
+ & Population density, 2010 & nan & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.43 & 0.00 \\
- & no_cause & 0.03 & 0.95 \\
- & non_payment & 0.03 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & nan & 0.00 \\
+ & Filing without cause & nan & 0.95 \\
+ & Filing for nonpayment & nan & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.61 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & nan & 0.00 \\
+ & Plaintiff has attorney & nan & 0.00 \\
+ & Defendant is entity & nan & 0.06 \\
+ & Plaintiff is entity & nan & 0.00 \\
 \cline{1-4}

### 2023-04-10 output/group_6_crimes_500m/tables/pre_treatment_covariate_tests.tex
ready tos tart writign

--- 2023-04-08 output/group_6_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_6_crimes_500m & 0.00 & 0.00 \\
- & pre_treatment_change_in_group_6_crimes_500m & 0.00 & 0.07 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 6 Incidents, 2017 & 0.00 & 0.01 \\
+ & $\Delta$ Group 6 Incidents, 2017-2019 & 0.00 & 0.58 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.63 & 0.05 \\
- & poor_share2010 & 0.55 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
+ & Job density, 2013 & 0.00 & 0.10 \\
+ & Median household income, 2016 & 0.00 & 0.05 \\
+ & Poverty rate, 2010 & 0.00 & 0.96 \\
+ & Population density, 2010 & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.26 & 0.00 \\
- & no_cause & 0.22 & 0.95 \\
- & non_payment & 0.13 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.03 & 0.00 \\
+ & Filing without cause & 0.01 & 0.95 \\
+ & Filing for nonpayment & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.66 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.30 & 0.00 \\
+ & Plaintiff has attorney & 0.00 & 0.00 \\
+ & Defendant is entity & 0.13 & 0.06 \\
+ & Plaintiff is entity & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-11 writing/paper/main.tex
Updates from Overleaf

@@
 
-\geometry{left=0.5in,right=0.5in,top=1.0in,bottom=1.0in}
-
 \begin{document}
@@
 \begin{titlepage}
-\title{Arjun Shanmugam's Senior Thesis}
+\title{Eviction and Crime: Evidence from Boston}
 \author{Arjun Shanmugam}
@@
 \begin{abstract}
-\noindent Placeholder\\
+\noindent This paper investigates the effects of eviction on crime incident frequency within 500 meters of the property where the eviction occurred.
+I use a difference-in-differences research design based on the staggered conclusion of eviction cases in Boston, Massachusetts between June 2019 and November 2022.
+Using properties where eviction was unsuccessful as the counterfactual for properties where eviction was successful, I find negative effects of eviction on crime which persist for about eleven months after case resolution.
+The magnitudes of these effects are approximately 0.5 percent of the mean number of crimes per month within 500 meters of a property in 2017.
+Placebo tests using larceny and burglary incident responses as an outcome variable suggest that these effects are driven by the movement of individuals involved in crime incidents outside the radii of properties where evictions are successful.
 
@@
 \section{Introduction} \label{sec:introduction}
-\bibliography{writing/paper/citations}
-\subsection{Literature Review}
+Fueled by stagnating incomes and rising housing costs, an eviction crisis has burdened low-income families in the United States for decades.
+Most poor renting families in America spend over half of their incomes on rent, meaning that unanticipated shocks can force families into homelessness \citep{desmond_evicted:_2017}.
+A number of studies have investigated the effects of eviction on individuals, motivated by its high prevalence in the United States relative to other rich countries \citep{oecd_affordable_housing_database_hc3.3._2021} and non-experimental evidence that it is destructive to its victims.
+But comparatively less work has explored how eviction impacts small communities.
+Researchers have noted that eviction is negatively associated with both economic connnectedness, the degree of interaction between low- and high- income people, and social cohesiveness, the degree to which social networks are fragmented into cliques \citep{weaver_no_2023, chetty_social_2022}.
+Understanding the ways that eviction interacts with the social fabric of small communities is critical to understanding its full range of impacts.
+
+This paper seeks to reinforce our knowledge of eviction's effects on small communities by estimating the effect of eviction on the frequency of crime incidents within 500 meters of a property.
+Empirical research of eviction and its impacts faces two main roadblocks \citep{collinson_eviction_2022}.
+The first is the difficulty of conducting analysis at the individual- or property-level.
+Eviction case records are often scattered across disjoint public and private organizations and difficult to obtain in bulk.
+It is also challenging to link eviction case records to individual- and property-level outcomes.
+I overcome this barrier by obtaining crime incident-level data from the Boston Police Department and eviction case-level data from MassLandlords, a trade association of landlords in Massachusetts.
+Armed with records of every eviction case resolved in Massachusetts Housing Court since June 2019 and every Boston Police Department crime incident response since August 2015, I spatially join each eviction record from Boston with any crime incident responses which occurred within 500 meters of the associated property.
+Using this comprehensive crime incident response data, I produce a panel that allows me to observe crime incident counts near each property for several years before and after case resolution.
+
+The second main roadblock to empirical eviction research is the endogeneity of eviction.
+For instance, partly due to generations of housing policies which sought to systematically exclude African-Americans from home ownership, eviction is strongly correlated with race \citep{rothstein_color_2017}.
+Eviction is also correlated with income, renter-occupied rates, and a host of other socioeconomic variables, many of which are also correlated with crime levels.
+I attempt to address this second barrier in two ways.
+First, I restrict my study to properties where an eviction case was filed.
+I use properties where an eviction was filed but unsuccessful as the counterfactual for properties where an eviction was successful.
+Properties where evictions are successful are more similar to properties where evictions are unsuccessfully filed than to properties which are not involved in eviction filings \citep{robinson_eviction_2021}.
+In this sense, restricting my analysis to properties involved in an eviction case makes the treatment properties more similar to control properties and should reduce the potential for bias in my estimates.
+Second, taking advantage of my rich outcome data, I use a difference-in-differences research design based on the staggered conclusions of eviction cases which eliminates bias in my estimates from confounders that are invariant over time.
+
+It is, however, possible that the assumptions underlying the difference-in-differences framework hold only conditional on certain pre-treatment characteristics.
+I algorithmically select pre-treatment characteristics which are significant predictors of trends in the outcome variable over the treatment period.
+I estimate a propensity score model which models the probability of a successful eviction based on the selected pre-treatment characteristics.
+I show that reweighting counterfactual properties using inverse propensity scores eliminates significant differences in observable characteristics between properties where evictions were successful and properties where evictions were unsuccessful.
+Then, I produce new difference-in-differences estimates using \cite{santanna_doubly_2020}'s doubly robust estimator, controlling for the selected pre-treatmennt characteristics.
+It models outcome differences and rewights counterfactual properties by their inverse propensity for successful eviction \citep{santanna_doubly_2020}.
+
+Doubly robust estimates suggest that eviction has small negative effects on the prevalence of crime incidents in the 500 meters surrounding a property.
+These estimates are significantly different from zero for most of the first 10 months after case resolution.
+Their magnitudes are approximately 0.5 percent of the number of crime incident responses within 500 meters of the average property in my sample during 2017.
+I do not find evidence of pre-treatment differences in crime incident response trends between properties where evictions were successful and properties where evictions were unsuccessful.
+I hypothesize that these results are driven by the movement of individuals involved in crime incidents outside the immediate radii of properties where evictions are successful.
+To test this hypothesis, I produce ``placebo'' estimates of the effect of eviction on larceny and burglary crime incident responses.
+Individuals who commit larceny and burglary generally do not do so within 500 meters of their own homes \textcolor{red}{CITE THIS}.
+Thus, if my estimates of the effect of the eviction on crime really are driven by the forced removal of individuals involved in crime from a property's immediate radius, then we would not expect to measure an effect of eviction on larceny and burglary crime incident responses.
+Indeed, these estimates are indistinguishable from 0, supporting my theory about the mechanism via which eviction at a property reduces crime incident responses in its immediate vicinity.
+
+These findings are important for two reasons.
+First, by suggesting that evicted individuals are more likely to be involved in crime, they tell a previously unseen story of the characteristics of evicted tenants.
+Second, they suggest that evictions may encourage the spread of criminal activity across locales.
+Anecdotal evidence suggests that evicted tenants tend to ``couch surf'' with relatives and friends immediately after experiencing eviction.
+If evicted tenants are more likely than non-evicted tenants to be involved in crime, then evictions could be encouraging the spread of criminal incidents across municipalities.
+\textcolor{red}{CITE MASS LANDLORDS}
+
+I contribute to a wide literature which studies the effects of eviction on important determinants of social well being.
+Evicted mothers are more likely to be depressed; low-income workers are more likely to lose their jobs after being evicted; and at the height of the pandemic, eviction moratoria limited households’ food insecurity and mental stress \citep{desmond_housing_2016, desmond_evictions_2015, an_more_2021}.
+This paper is also related to a burgeoning literature in economics which seeks to apply quasi-experimental methods to study the effects of eviction.
+\cite{collinson_eviction_2022} exploit random assignment of eviction cases to judges of varying leniency to estimate the effects of eviction on outcomes such as consumption of durables and homelessness.
+In contrast to most research in sociology, they find relatively small effects on social and economic outcomes, further underscoring the importance of quasi-experimental evidence in this context.
+
+This paper is one of relatively few in the economics literature to address the relationship between eviction and crime.
+\cite{kroeger_nuisance_2020} studies nuisance ordinances—municipal laws which punish landlords for crimes that occur on their properties—and finds that they make eviction filings more common across cities in Ohio.
+\cite{falcone_evictions_2022} expands on this finding, arguing that evictions increase crime at the municipality level under the assumption that nuisance ordinances affect crime only by making evictions more common.
+My research distinguishes itself from these studies in two ways.
+First, I study the effect of eviction on crime incident responses, not crimes.
+Second, I seek to estimate the causal effect of an eviction on crime in its immediate surroundings as opposed to in the city or town in which it occurs.
+
+Section 2 discusses the institutional context of the study.
+Section 3 discusses in greater depth the data I obtain and the dataset I assemble for my analysis.
+Section 4 outlinnes my empirical strategy.
+Section 5 provides and discusses results, and Section 6 concludes.
 
@@
         \subsubsection{The Eviction Process}
-    \subsection{Property Tax Assessment}
-        \subsubsection{The Property Value Assessment Process}
-    \subsection{Zestimates}
-        \subsubsection{How Are Zestimates Produced?}
-        \subsubsection{Reliability}
+    \subsection{Crime Incident Responses}
+
 \section{Data} \label{sec:data}
-    \begin{landscape}
+
     \subsection{Evictions Data}
+
+        \newpage
         \begin{figure}[H]
@@
 
+        \begin{landscape}
         \begin{figure}[H]
             \centering
-            \includegraphics{output/summary_statistics/figures/filings_over_time.png}
-            \caption{Eviction Filings Over Time}
+            \includegraphics[scale=1.25]{output/summary_statistics/figures/filings_over_time.png}
+            \caption{Eviction Filings Over Time in Boston}
             \label{fig:my_label}
@@
             \centering
+            \small
             \input{output/summary_statistics/tables/treatment_timings.tex}
@@
 
-        \begin{figure}[H]
-            \centering
-            \includegraphics[scale=0.8]{output/DiD/figures/trends_in_zestimates_by_cohort.png}
-            \caption{Trends in Zestimates by Cohort}
-            \label{fig:my_label}
-        \end{figure}
-
     \subsection{Summary Statistics}
@@
             \small
-            \input{output/summary_statistics/tables/summary_statistics.tex}
+            \input{output/summary_statistics/tables/summary_statistics}
             \caption{Summary Statistics}
@@
         \centering
-        \input{output/DiD/tables/pre_treatment_covariate_tests.tex}
+        \input{}
         \caption{Relationship Between Pre-Treatment Characteristics and the Dependent and Independent Variables}
@@
         \centering
-        \input{output/DiD/tables/balance_table.tex}
+        \input{}
         \caption{Balance Tests}
@@
 
-    \begin{figure}[H]
-        \centering
-        \includegraphics{output/DiD/figures/att_gt_unconditional_event_study_short_horizon.png}
-        \caption{}
-        \label{fig:my_label}
-    \end{figure}
-
-    \begin{figure}[H]
-        \centering
-        \includegraphics{output/DiD/figures/att_gt_unconditional_event_study_long_horizon.png}
-        \caption{}
-        \label{fig:my_label}
-    \end{figure}
-
-    \begin{figure}[H]
-        \centering
-        \includegraphics{output/DiD/figures/att_gt_unconditional_time.png}
-        \caption{}
-        \label{fig:my_label}
-    \end{figure}
-
     \subsection{D.R. Estimates of the ATT}
-
-    \begin{figure}[H]
-        \centering
-        \includegraphics{output/DiD/figures/att_gt_dr_event_study_short_horizon.png}
-        \caption{}
-        \label{fig:my_label}
-    \end{figure}
-
-    \begin{figure}[H]
-        \centering
-        \includegraphics{output/DiD/figures/att_gt_dr_event_study_long_horizon.png}
-        \caption{}
-        \label{fig:my_label}
-    \end{figure}
-
-    \begin{figure}[H]
-        \centering
-        \includegraphics{output/DiD/figures/att_gt_dr_time.png}
-        \caption{}
-        \label{fig:my_label}
-    \end{figure}
 

### 2023-04-12 writing/paper/main.tex
Updates from Overleaf

@@
 \begin{abstract}
-\noindent This paper investigates the effects of eviction on crime incident frequency within 500 meters of the property where the eviction occurred.
-I use a difference-in-differences research design based on the staggered conclusion of eviction cases in Boston, Massachusetts between June 2019 and November 2022.
-Using properties where eviction was unsuccessful as the counterfactual for properties where eviction was successful, I find negative effects of eviction on crime which persist for about eleven months after case resolution.
-The magnitudes of these effects are approximately 0.5 percent of the mean number of crimes per month within 500 meters of a property in 2017.
+\noindent This paper investigates the effects of eviction on the frequency of crime incident responses in the immediate vicinity of a property.
+I use a difference-in-differences research design based on the staggered conclusion of eviction cases in Boston, Massachusetts between June 2019 and March 2020.
+Using properties where eviction was unsuccessful as the counterfactual for properties where eviction was successful, I find negative effects of eviction on crime incident responses which persist for about eleven months after case resolution.
+The magnitudes of these effects are approximately 0.5 percent of the mean number of crimes per month in the immediate vicinity of a property in 2017.
 Placebo tests using larceny and burglary incident responses as an outcome variable suggest that these effects are driven by the movement of individuals involved in crime incidents outside the radii of properties where evictions are successful.
+Analysis of treatment effects using only cases resolved before the beginning of the pandemic provides evidence against the hypothesis that my results are driven by a pandemic-related shift in characteristics of evicted tenants.
 
@@
 Then, I produce new difference-in-differences estimates using \cite{santanna_doubly_2020}'s doubly robust estimator, controlling for the selected pre-treatmennt characteristics.
-It models outcome differences and rewights counterfactual properties by their inverse propensity for successful eviction \citep{santanna_doubly_2020}.
+It models outcome differences and rewights counterfactual properties by their inverse propensity for being the site of a successful eviction \citep{santanna_doubly_2020}.
 
@@
 Their magnitudes are approximately 0.5 percent of the number of crime incident responses within 500 meters of the average property in my sample during 2017.
-I do not find evidence of pre-treatment differences in crime incident response trends between properties where evictions were successful and properties where evictions were unsuccessful.
+I do not find evidence of pre-treatment differences in crime incident response trends between properties where evictions were successful and properties where evictions were unsuccessful \textcolor{red}{make sure this is true}.
+
 I hypothesize that these results are driven by the movement of individuals involved in crime incidents outside the immediate radii of properties where evictions are successful.
@@
 Section 3 discusses in greater depth the data I obtain and the dataset I assemble for my analysis.
-Section 4 outlinnes my empirical strategy.
+Section 4 outlines my empirical strategy.
 Section 5 provides and discusses results, and Section 6 concludes.
+
+ADD DISCUSISON NOF PANDEMIC: ONLY THE MOST SERIOUS EVICTIONS PROCEEDED, BIASING EVICTEES TO BE MORE SERIOUS OFFENDERS
 
@@
     \subsection{Eviction in Massachusetts}
-        \subsubsection{The Massachusetts Housing Court}
+        \subsubsection{Legal Landscape of Eviction}
+        Eviction cases—known formally as summary process cases—fall under the purview of the Massachusetts Trial Court.
+In particular, three sub-departments of the Trial Court have jurisdiction over summary process cases: District Court, Boston Municipal Court, and Housing Court \textcolor{red}{CITE}.
+Evictions may be filed in any of these three courts.
+The District Court maintains a large number of locations throughout the state of Massachusetts and Boston Municipal Court operates only within the city limits of Boston.
+
+        The vast majority of summary process cases are adjudicated in the Housing Court, established in 1971 with the specific purpose of dealing with housing-related matters.
+The court has been expanded several times since then.
+Since the passage of the most recent Housing Court expansion law in 2017, every Massachusetts resident has access to a Housing Court \citep{gee_housing_2017}.
+Across the state, 15 judges preside over cases across six divisions: Central, Eastern, Metro South, Northeast, Southeast, and Western.
+
+        \begin{figure}
+            \centering
+            \includegraphics{research/institutional_context/sources/map_of_where_court_sits_-_jan_2019.pdf}
+            \caption{Divisions of the Massachusetts Housing Court}
+        \end{figure}
+
+        Four features distinguish the Housing Court as a legal institution from the District Court and Boston Municipal Court \citep{noauthor_housing_nodate}.
+First, it is led by justices with significant knowledge and experience when it comes to housing-related legal matters, such as summary process cases.
+Second, it is staffed by housing specialists, employees of the Court with detailed knowledge of Massachusetts housing law who provide information and referrals to resources for landlords and tenants.
+Third, it offers a service known as mediation, in which cases may be resolved prior to arguments in front of a judge.
+Mediation is facilitated by a housing specialist, who helps the defendant and plaintiff come to an agreement and records promises made by both sides.
+Rather than risk defeat at the hands of a judge, many tenants and landlords prefer to reach mutually agreeable terms of resolution during mediation.
+If either party violates the terms of the specified mediation agreement, the other may return to the judge in a more favorable legal position.
+Fourth, either party in a summary process case filed in District Court or Boston Municipal Court has the right to transfer the case to the Housing Court at any time prior to trial .
+For these reasons, tenant advocacy groups and landlord associations alike in Massachusetts generally recommend filing summary process cases in the Housing Court \citep{noauthor_massachusetts_nodate, noauthor_housing_nodate}.
+
         \subsubsection{The Eviction Process}
+        Tenants in Massachusetts can rent from landlords under the terms of a lease or without one.
+If a tenant is renting from a landlord without a lease, their tenancy is \textit{at will}.
+The nature of the agreement between the tenant and the landlord—the \textit{landlord-tenant agreement}—determines the steps that the landlord must take to evict the tenant.
+
+        A landlord in Massachusetts begins the eviction process by serving her tenant with a \textit{notice to quit}, which serves as written notice of her desire to terminate tenancy.
+While a landlord may deliver the notice to quit herself, many landlords choose to hire a local law enforcement officer to do so for around 40 dollars.
+This guarantees that an independent third party can vouch that the notice was properly served.
+A notice to quit is served for \textit{nonpayment of rent}, \textit{cause}, or \textit{no fault} and gives an amount of time after which the landlord-tenant agreement will be terminated if no action is taken by the tenant.
+
+        If the notice to quit is served for nonpayment of rent, then regardless of the nature of the landlord-tenant agreement, this time period given by the notice to quit is 14 days.
+The tenant may \textit{cure} the nonpayment of rent, nullifying the notice to quit, by paying the landlord all owed rent with interest and costs within 14 days \footnote{Tenants at-will do not have the option to cure nonpayment of rent if they have received a separate notice to quit for nonpayment of rent during the last 12 months.}.
+If the notice to quit is served for cause and a lease defines the landlord-tenant agreement, then the amount of time that given by the notice to quit must be specified in the lease.
+If the landlord-tenant agreement is at will, then the time period given by the notice to quit is 30 days.
+No fault notices to quit waiting period of 30 days or one full rental period—whichever is longer—before tenancy can be terminated.
+
+        After the length of time specified by the notice to quit has passed \footnote{If the notice to quit was for nonpayment of rent, the specified length of time must pass without curing of the nonpayment by the tenant.}, the tenant's rental agreement has ended.
+To continue with the eviction, the landlord is required to hire a local law enforcement officer to serve the tenant with a \textit{summary process summons and complaint}.
+Massachusetts law says that the summary process summons and complaint must then be filed with the court on a Monday between seven and 30 days after it was served.
+The date on which the summons and complaint is filed with the court is known as the \textit{entry date}.
+If a landlord fails to follow any of the above protocol—say, by serving a notice to quit that specifies too short of a time period or by failing to deliver a summary process summons and complaint to the tenant—her case may be dismissed, automatically awarding victory to the tenant.
+
     \subsection{Crime Incident Responses}

### 2023-04-12 output/group_0_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited analysis to pre-pandemic months

--- 2023-04-06 output/group_0_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_500m & 0.00 & 0.01 \\
- & pre_treatment_change_in_group_0_crimes_500m & 0.00 & 0.30 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.53 \\
+ & Change in Crime Incidents, 2017-2019 & 0.00 & 0.34 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.20 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.22 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.34 & 0.03 \\
+ & Job density, 2013 & 0.00 & 0.29 \\
+ & Median household income, 2016 & 0.06 & 0.01 \\
+ & Poverty rate, 2010 & 0.00 & 0.01 \\
+ & Population density, 2010 & 0.00 & 0.57 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.47 & 0.00 \\
- & no_cause & 0.01 & 0.95 \\
- & non_payment & 0.03 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.03 & 0.00 \\
+ & Filing without cause & 0.02 & 0.16 \\
+ & Filing for nonpayment & 0.00 & 0.04 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.12 & 0.00 \\
- & hasAttyP & 0.37 & 0.00 \\
- & isEntityD & 0.12 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.25 & 0.00 \\
+ & Plaintiff has attorney & 0.38 & 0.06 \\
+ & Defendant is entity & 0.00 & 0.13 \\
+ & Plaintiff is entity & 0.02 & 0.00 \\
 \cline{1-4}

### 2023-04-12 output/group_1_crimes_500m/tables/balance_table.tex
limited analysis to pre-pandemic months

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & Total Group 1 Incidents, 2017 & 59.33 & 3.74 & 0.00 & 1.22 & 0.24 \\
- & $\Delta$ Group 1 Incidents, 2017-2019 & -14.54 & -0.44 & 0.45 & -0.35 & 0.56 \\
+\multirow[c]{2}{.75cm}{\textit{Panel A}} & Total Group 1 Incidents, 2017 & 2.98 & 0.26 & 0.10 & 0.00 & 0.98 \\
+ & $\Delta$ Group 1 Incidents, 2017-2019 & 12.72 & 0.07 & 0.92 & -0.18 & 0.79 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel B}} & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & 207.41 & 0.89 \\
- & Poverty rate, 2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.13 \\
- & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & 479.29 & 0.27 \\
-\cline{1-7}
-\textit{Panel D} & Defendant is entity & 0.02 & -0.01 & 0.06 & 0.00 & 0.75 \\
+\multirow[c]{5}{.75cm}{\textit{Panel B}} & Bachelor's degree, 2010 & 0.32 & 0.02 & 0.03 & -0.00 & 0.98 \\
+ & Job density, 2013 & 17,879.13 & 2,380.87 & 0.29 & 184.04 & 0.93 \\
+ & Median household income, 2016 & 47,493.96 & 3,485.70 & 0.01 & -54.60 & 0.94 \\
+ & Poverty rate, 2010 & 0.28 & -0.02 & 0.01 & -0.01 & 0.22 \\
+ & Population density, 2010 & 23,692.02 & 403.43 & 0.57 & -282.90 & 0.68 \\
 \cline{1-7}

### 2023-04-12 output/group_1_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited analysis to pre-pandemic months

--- 2023-04-08 output/group_1_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_500m & 0.00 & 0.02 \\
- & pre_treatment_change_in_group_1_crimes_500m & 0.00 & 0.43 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 1 Incidents, 2017 & 0.00 & 0.10 \\
+ & $\Delta$ Group 1 Incidents, 2017-2019 & 0.00 & 0.92 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.03 \\
+ & Job density, 2013 & 0.00 & 0.29 \\
+ & Median household income, 2016 & 0.00 & 0.01 \\
+ & Poverty rate, 2010 & 0.00 & 0.01 \\
+ & Population density, 2010 & 0.01 & 0.57 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.51 & 0.00 \\
- & no_cause & 0.02 & 0.95 \\
- & non_payment & 0.05 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.10 & 0.00 \\
+ & Filing without cause & 0.38 & 0.16 \\
+ & Filing for nonpayment & 0.31 & 0.04 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.04 & 0.00 \\
- & hasAttyP & 0.52 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.34 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.29 & 0.00 \\
+ & Plaintiff has attorney & 0.33 & 0.06 \\
+ & Defendant is entity & 0.52 & 0.13 \\
+ & Plaintiff is entity & 0.73 & 0.00 \\
 \cline{1-4}

### 2023-04-12 output/group_2_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited analysis to pre-pandemic months

--- 2023-04-06 output/group_2_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_500m & 0.00 & 0.87 \\
- & pre_treatment_change_in_group_2_crimes_500m & 0.00 & 0.67 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 2 Incidents, 2017 & 0.00 & 0.96 \\
+ & $\Delta$ Group 2 Incidents, 2017-2019 & 0.00 & 0.03 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.03 \\
+ & Job density, 2013 & 0.00 & 0.29 \\
+ & Median household income, 2016 & 0.00 & 0.01 \\
+ & Poverty rate, 2010 & 0.00 & 0.01 \\
+ & Population density, 2010 & 0.00 & 0.57 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.22 & 0.00 \\
- & no_cause & 0.28 & 0.95 \\
- & non_payment & 0.09 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.39 & 0.00 \\
+ & Filing without cause & 0.70 & 0.16 \\
+ & Filing for nonpayment & 0.65 & 0.04 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.84 & 0.00 \\
- & hasAttyP & 0.07 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.11 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.86 & 0.00 \\
+ & Plaintiff has attorney & 0.27 & 0.06 \\
+ & Defendant is entity & 0.10 & 0.13 \\
+ & Plaintiff is entity & 0.17 & 0.00 \\
 \cline{1-4}

### 2023-04-12 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited analysis to pre-pandemic months

--- 2023-04-08 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.02 \\
- & pre_treatment_change_in_group_3_crimes_500m & 0.04 & 0.81 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 3 Incidents, 2017 & 0.00 & 0.16 \\
+ & $\Delta$ Group 3 Incidents, 2017-2019 & 0.00 & 0.07 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.01 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.03 \\
+ & Job density, 2013 & 0.00 & 0.29 \\
+ & Median household income, 2016 & 0.00 & 0.01 \\
+ & Poverty rate, 2010 & 0.00 & 0.01 \\
+ & Population density, 2010 & 0.00 & 0.57 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.75 & 0.00 \\
- & no_cause & 0.94 & 0.95 \\
- & non_payment & 0.85 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.03 & 0.00 \\
+ & Filing without cause & 0.02 & 0.16 \\
+ & Filing for nonpayment & 0.00 & 0.04 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.43 & 0.00 \\
- & hasAttyP & 0.41 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.64 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.27 & 0.00 \\
+ & Plaintiff has attorney & 0.00 & 0.06 \\
+ & Defendant is entity & 0.01 & 0.13 \\
+ & Plaintiff is entity & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-12 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited analysis to pre-pandemic months

--- 2023-04-08 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.01 \\
- & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.27 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 4 Incidents, 2017 & 0.00 & 0.56 \\
+ & $\Delta$ Group 4 Incidents, 2017-2019 & 0.00 & 0.90 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.64 & 0.03 \\
+ & Job density, 2013 & 0.00 & 0.29 \\
+ & Median household income, 2016 & 0.54 & 0.01 \\
+ & Poverty rate, 2010 & 0.25 & 0.01 \\
+ & Population density, 2010 & 0.00 & 0.57 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.08 & 0.00 \\
- & no_cause & 0.00 & 0.95 \\
- & non_payment & 0.00 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.10 & 0.00 \\
+ & Filing without cause & 0.28 & 0.16 \\
+ & Filing for nonpayment & 0.07 & 0.04 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.26 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
- & isEntityD & 0.06 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.31 & 0.00 \\
+ & Plaintiff has attorney & 0.67 & 0.06 \\
+ & Defendant is entity & 0.19 & 0.13 \\
+ & Plaintiff is entity & 0.65 & 0.00 \\
 \cline{1-4}

### 2023-04-12 output/group_5_crimes_500m/tables/pre_treatment_covariate_tests.tex
limited analysis to pre-pandemic months

--- 2023-04-08 output/group_5_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_5_crimes_500m & 0.00 & 0.37 \\
- & pre_treatment_change_in_group_5_crimes_500m & 0.00 & 0.05 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 5 Incidents, 2017 & 0.00 & 0.94 \\
+ & $\Delta$ Group 5 Incidents, 2017-2019 & 0.00 & 0.90 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.00 & 0.05 \\
- & poor_share2010 & 0.00 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.03 \\
+ & Job density, 2013 & 0.00 & 0.29 \\
+ & Median household income, 2016 & 0.00 & 0.01 \\
+ & Poverty rate, 2010 & 0.00 & 0.01 \\
+ & Population density, 2010 & 0.00 & 0.57 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.43 & 0.00 \\
- & no_cause & 0.03 & 0.95 \\
- & non_payment & 0.03 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.98 & 0.00 \\
+ & Filing without cause & 0.27 & 0.16 \\
+ & Filing for nonpayment & 0.47 & 0.04 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.61 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.49 & 0.00 \\
+ & Plaintiff has attorney & 0.00 & 0.06 \\
+ & Defendant is entity & 0.00 & 0.13 \\
+ & Plaintiff is entity & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-12 output/summary_statistics/tables/summary_statistics.tex
colored map
limited analysis to pre-pandemic months

@@
 \midrule
-\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & $\Delta$ Group 0 Incidents, 2017-2019 & -532.85 & 465.54 & 6,060 \\
- & Total Group 0 Incidents, 2017 & 4,068.25 & 2,258.29 & 6,060 \\
+\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in Crime Incidents, 2017-2019 & -158.19 & 221.79 & 6,060 \\
+ & Total Crime Incidents, 2017 & 1,179.33 & 708.44 & 6,060 \\
 \cline{1-5}

### 2023-04-12 src/02_analysis/constants.py

@@ -1,30 +1,9 @@
 class Variables:
-    outcomes = ['group_0_crimes_50m',
-                'group_1_crimes_50m',
-                'group_2_crimes_50m',
-                'group_3_crimes_50m',
-                'group_4_crimes_50m',
-                'group_5_crimes_50m',
-                'group_6_crimes_50m',
-                'group_0_crimes_100m',
-                'group_1_crimes_100m',
-                'group_2_crimes_100m', 
-                'group_3_crimes_100m',
-                'group_4_crimes_100m',
-                'group_5_crimes_100m',
-                'group_6_crimes_100m',
-                'group_0_crimes_500m',
+    outcomes = ['group_0_crimes_500m',
                 'group_1_crimes_500m',
                 'group_2_crimes_500m', 
                 'group_3_crimes_500m',
                 'group_4_crimes_500m',
                 'group_5_crimes_500m',
-                'group_6_crimes_500m',
-                'group_0_crimes_1000m',
-                'group_1_crimes_1000m',
-                'group_2_crimes_1000m', 
-                'group_3_crimes_1000m',
-                'group_4_crimes_1000m',
-                'group_5_crimes_1000m',
-                'group_6_crimes_1000m']
+                'group_6_crimes_500m']
 

### 2023-04-12 src/02_analysis/figure_utilities.py

@@ -49,9 +49,9 @@ def aggregate_by_event_time_and_plot(att_gt,
                                                      y_upper.values,
                                                      y_lower.values,
                                                      point_color='black',
-                                                     error_color='white',
+                                                     error_color='grey',
                                                      edge_color='grey',
-                                                     edge_style='--',
+                                                     edge_style='-',
                                                      zorder=1)
     plot_labeled_hline(ax, y=0, text="", color='black', linestyle='-', zorder=6)
 

### 2023-04-12 src/02_analysis/stats_utilities.py

@@ -121,7 +121,7 @@ def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.D
                        column_format="llccccc",
                        hrules=True,
                        multicol_align='c',
-                       clines="skip-last;data")).replace("{*}", "{3cm}")
+                       clines="skip-last;data")).replace("{*}", "{.75cm}")
     latex = latex.split("\\\\\n")
     latex.insert(1, "\\cline{4-7}\n")
     latex = "\\\\\n".join(latex)
@@ -324,6 +324,12 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                                    }
     outcomes = Variables.outcomes.copy()  # Create list of all outcomes.
     for outcome in outcomes:
+        if outcome.split('_')[1] == '0':
+            pretreatment_change_display_name = f"Change in Crime Incidents, 2017-2019"
+            variable_display_names_dict[f'pre_treatment_change_in_{outcome}'] = pretreatment_change_display_name
+            pretreatment_level_display_name = f"Total Crime Incidents, 2017"
+            variable_display_names_dict[f'total_twenty_seventeen_{outcome}'] = pretreatment_level_display_name
+            continue
         pretreatment_change_display_name = f"$\Delta$ Group {outcome.split('_')[1]} Incidents, 2017-2019"
         variable_display_names_dict[f'pre_treatment_change_in_{outcome}'] = pretreatment_change_display_name
         pretreatment_level_display_name = f"Total Group {outcome.split('_')[1]} Incidents, 2017"

### 2023-04-12 output/group_0_crimes_warm_500m/tables/pre_treatment_covariate_tests.tex
Added alternative analyses

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.88 \\
 & Change in Crime Incidents, 2017-2019 & 0.00 & 0.60 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.44 & 0.07 \\
 & Job density, 2013 & 0.00 & 0.15 \\
 & Median household income, 2016 & 0.56 & 0.03 \\
 & Poverty rate, 2010 & 0.00 & 0.00 \\
 & Population density, 2010 & 0.00 & 0.80 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.05 & 0.01 \\
 & Filing without cause & 0.08 & 0.59 \\
 & Filing for nonpayment & 0.01 & 0.02 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.77 & 0.04 \\
 & Plaintiff has attorney & 0.84 & 0.19 \\
 & Defendant is entity & 0.00 & 0.07 \\
 & Plaintiff is entity & 0.26 & 0.03 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-12 output/group_2_crimes_500m/tables/pre_treatment_covariate_tests.tex
Added alternative analyses

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 2 Incidents, 2017 & 0.00 & 0.96 \\
- & $\Delta$ Group 2 Incidents, 2017-2019 & 0.00 & 0.03 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 2 Incidents, 2017 & 0.00 & 0.78 \\
+ & $\Delta$ Group 2 Incidents, 2017-2019 & 0.00 & 0.95 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.03 \\
- & Job density, 2013 & 0.00 & 0.29 \\
- & Median household income, 2016 & 0.00 & 0.01 \\
- & Poverty rate, 2010 & 0.00 & 0.01 \\
- & Population density, 2010 & 0.00 & 0.57 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.07 \\
+ & Job density, 2013 & 0.00 & 0.15 \\
+ & Median household income, 2016 & 0.00 & 0.03 \\
+ & Poverty rate, 2010 & 0.00 & 0.00 \\
+ & Population density, 2010 & 0.00 & 0.80 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.39 & 0.00 \\
- & Filing without cause & 0.70 & 0.16 \\
- & Filing for nonpayment & 0.65 & 0.04 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.67 & 0.01 \\
+ & Filing without cause & 0.89 & 0.59 \\
+ & Filing for nonpayment & 0.61 & 0.02 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.86 & 0.00 \\
- & Plaintiff has attorney & 0.27 & 0.06 \\
- & Defendant is entity & 0.10 & 0.13 \\
- & Plaintiff is entity & 0.17 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.88 & 0.04 \\
+ & Plaintiff has attorney & 0.67 & 0.19 \\
+ & Defendant is entity & 0.36 & 0.07 \\
+ & Plaintiff is entity & 0.27 & 0.03 \\
 \cline{1-4}

### 2023-04-12 output/summary_statistics/tables/summary_statistics.tex
Added alternative analyses

@@
 \midrule
-\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in Crime Incidents, 2017-2019 & -158.19 & 221.79 & 6,060 \\
- & Total Crime Incidents, 2017 & 1,179.33 & 708.44 & 6,060 \\
+\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in Crime Incidents, 2017-2019 & -164.98 & 222.44 & 3,171 \\
+ & Total Crime Incidents, 2017 & 1,230.16 & 697.53 & 3,171 \\
 \cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.31 & 0.22 & 6,060 \\
- & Job density, 2013 & 14,806.08 & 40,595.37 & 6,060 \\
- & Median household income, 2016 & 47,188.87 & 24,703.65 & 6,060 \\
- & Poverty rate, 2010 & 0.28 & 0.14 & 6,060 \\
- & Population density, 2010 & 22,704.52 & 13,091.45 & 6,060 \\
+\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.30 & 0.21 & 3,171 \\
+ & Job density, 2013 & 15,603.89 & 41,982.90 & 3,171 \\
+ & Median household income, 2016 & 46,085.28 & 24,946.22 & 3,171 \\
+ & Poverty rate, 2010 & 0.29 & 0.15 & 3,171 \\
+ & Population density, 2010 & 23,385.01 & 13,324.90 & 3,171 \\
 \cline{1-5}
-\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.17 & 0.37 & 6,060 \\
- & Filing without cause & 0.05 & 0.22 & 6,060 \\
- & Filing for nonpayment & 0.78 & 0.42 & 6,060 \\
+\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.16 & 0.36 & 3,171 \\
+ & Filing without cause & 0.05 & 0.23 & 3,171 \\
+ & Filing for nonpayment & 0.79 & 0.41 & 3,171 \\
 \cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.08 & 0.27 & 6,060 \\
- & Plaintiff has attorney & 0.88 & 0.32 & 6,060 \\
- & Defendant is entity & 0.02 & 0.14 & 6,060 \\
- & Plaintiff is entity & 0.81 & 0.39 & 6,060 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.04 & 0.20 & 3,171 \\
+ & Plaintiff has attorney & 0.87 & 0.34 & 3,171 \\
+ & Defendant is entity & 0.02 & 0.13 & 3,171 \\
+ & Plaintiff is entity & 0.82 & 0.39 & 3,171 \\
 \cline{1-5}
-\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 58.17 & 88.96 & 5,500 \\
- & Judgment by default & 0.19 & 0.39 & 6,060 \\
- & Case dismissed & 0.27 & 0.44 & 6,060 \\
- & Case heard & 0.03 & 0.17 & 6,060 \\
- & Money judgment & 1,938.57 & 5,337.87 & 6,060 \\
- & Case mediated & 0.40 & 0.49 & 6,060 \\
+\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 22.33 & 23.38 & 3,039 \\
+ & Judgment by default & 0.25 & 0.43 & 3,171 \\
+ & Case dismissed & 0.20 & 0.40 & 3,171 \\
+ & Case heard & 0.02 & 0.14 & 3,171 \\
+ & Money judgment & 1,806.43 & 4,135.66 & 3,171 \\
+ & Case mediated & 0.48 & 0.50 & 3,171 \\
 \cline{1-5}

### 2023-04-12 src/02_analysis/figure_utilities.py

@@ -40,7 +40,7 @@ def aggregate_by_event_time_and_plot(att_gt,
     ax.set_ylabel("ATT")
     ax.set_title(title)
     ax.set_xlabel("Month Relative to Treatment")
-    ax.set_xticks(x)
+    ax.set_xticks(range(start_period, end_period + 1, 6))
     plot_labeled_vline(ax, x=0, text="Treatment", color='black', linestyle='-',
                                         text_y_location_normalized=0.95)
     plot_scatter_with_shaded_errors(ax,

### 2023-04-12 src/02_analysis/stats_utilities.py

@@ -254,10 +254,11 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     panel_D = pd.concat([panel_D], keys=["Panel D: Defendant and Plaintiff Characteristics"])
 
     # Panel E: Case Resolution
-    panel_E_columns = ['mediated', 'dismissed', 'defaulted', 'heard']
+    panel_E_columns = ['mediated', 'dismissed', 'defaulted', 'heard', 'levied', 'issued', 'requested',
+                       'unknown_execution']
     origin_columns = ['disposition_found', 'disposition_found', 'disposition_found',
-                      'disposition_found']
-    target_values = ["Mediated", "Dismissed", "Defaulted", "Heard"]
+                      'disposition_found', 'execution', 'execution', 'execution', 'execution']
+    target_values = ["Mediated", "Dismissed", "Defaulted", "Heard", "Levied", "Issued", "Requested", np.nan]
 
     for dummy_column, origin_column, target_value in zip(panel_E_columns, origin_columns, target_values):
         df.loc[:, dummy_column] = np.where(df[origin_column] == target_value, 1, 0)
@@ -319,7 +320,10 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                                     'dismissed': "Case dismissed",
                                    "judgment": "Money judgment",
                                    "mediated": "Case mediated",
-
+                                   'levied': "Execution levied",
+                                   'issued': "Execution issued",
+                                   'requested': "Execution requested",
+                                   'unknown_execution': "Execution status unknown"
 
                                    }
     outcomes = Variables.outcomes.copy()  # Create list of all outcomes.

### 2023-04-12 writing/paper/main.tex

@@
 
+\begin{landscape}
+
         \begin{figure}
             \centering
-            \includegraphics{research/institutional_context/sources/map_of_where_court_sits_-_jan_2019.pdf}
-            \caption{Divisions of the Massachusetts Housing Court}
+            \includegraphics[scale=0.75]{research/institutional_context/sources/map_of_where_court_sits_-_jan_2019.pdf}
+            \caption{Divisions of the Massachusetts Housing Court \citep{housing_court_4_all_housing_nodate}}
         \end{figure}
+\end{landscape}
 
@@
 To continue with the eviction, the landlord is required to hire a local law enforcement officer to serve the tenant with a \textit{summary process summons and complaint}.
-Massachusetts law says that the summary process summons and complaint must then be filed with the court on a Monday between seven and 30 days after it was served.
+Massachusetts law says that the landlord must then file the summary process complaint with the court on a Monday between seven and 30 days after it was served.
 The date on which the summons and complaint is filed with the court is known as the \textit{entry date}.
 If a landlord fails to follow any of the above protocol—say, by serving a notice to quit that specifies too short of a time period or by failing to deliver a summary process summons and complaint to the tenant—her case may be dismissed, automatically awarding victory to the tenant.
+
+        Upon receiving the summons and complaint, the tenant may file a Summary Process Answer form with the court.
+This is the tenant's opportunity to provide \textit{defenses}, or legal reasons that the landlord should not evict the tenant, and \textit{counterclaims}, or claims that the tenant has against the landlord.
+The tenant may also file for \textit{discovery} at this stage.
+Discovery is the process by which the tenant may request information from her landlord, which the landlord must provide under oath.
+Tenants often use discovery as a means of postponing a trial: as long as the court receives the request for discovery before mediation begins, the eviction process is halted by two weeks.
+
+        Once the summons and complaint has been filed with the court, the tenant has had a chance to answer, and the discovery process is finished, mediation begins.
+Housing specialists facilitate mediation with the goal of avoiding a trial by producing a legally binding agreement acceptable for both the tenant and the landlord.
+Mediation is confidential—matters discussed during mediation may not go before a judge.
+
+        If mediation does not result in an agreement between the landlord and the tenant, a trial is held in front of a judge, who rules in favor of the landlord, the plaintiff, or the tenant, the defendant.
+If the judge rules in favor of the tenant, the eviction process has concluded.
+If the judge rules in favor of the landlord, then the tenant has ten days after the judgment to appeal the case.
+After the tenth day, the landlord may obtain an \textit{execution for possession} from the court.
+For the next 90 days, the landlord may hire a law enforcement officer to force a tenant to leave the property with 48 hours notice.
 
@@
 \section{Empirical Strategy: Difference-in-Differences}
+    \subsection{Conceptualizing Treatment}
     I seek to estimate the average treatment effects of plaintiff victory in eviction cases on treated properties.

### 2023-04-12 writing/paper/main.tex
Updates from Overleaf

@@
 \noindent This paper investigates the effects of eviction on the frequency of crime incident responses in the immediate vicinity of a property.
-I use a difference-in-differences research design based on the staggered conclusion of eviction cases in Boston, Massachusetts between June 2019 and March 2020.
-Using properties where eviction was unsuccessful as the counterfactual for properties where eviction was successful, I find negative effects of eviction on crime incident responses which persist for about eleven months after case resolution.
-The magnitudes of these effects are approximately 0.5 percent of the mean number of crimes per month in the immediate vicinity of a property in 2017.
+I use a doubly robust difference-in-differences research design based on the staggered conclusion of eviction cases in Boston, Massachusetts between April 2019 and March 2020.
+Using properties where eviction was unsuccessful as the counterfactual for properties where eviction was successful, I find negative effects of eviction on crime incident responses which persist for 3 years after case resolution.
+Point estimates of the magnitudes of these effects are approximately between 2 and 4 percent of the mean number of crimes per month in the immediate vicinity of a property in 2017.
+Effects are driven by impacts during warm months.
+
 Placebo tests using larceny and burglary incident responses as an outcome variable suggest that these effects are driven by the movement of individuals involved in crime incidents outside the radii of properties where evictions are successful.
@@
 It is also challenging to link eviction case records to individual- and property-level outcomes.
-I overcome this barrier by obtaining crime incident-level data from the Boston Police Department and eviction case-level data from MassLandlords, a trade association of landlords in Massachusetts.
-Armed with records of every eviction case resolved in Massachusetts Housing Court since June 2019 and every Boston Police Department crime incident response since August 2015, I spatially join each eviction record from Boston with any crime incident responses which occurred within 500 meters of the associated property.
+I overcome this barrier by obtaining crime incident-level data from the Boston Police Department (BPD) and eviction case-level data from MassLandlords, a trade association of landlords in Massachusetts.
+Armed with records of every eviction case resolved in Massachusetts Housing Court since June 2019 and every BPD crime incident response since August 2015, I spatially join each eviction record from Boston with any crime incident responses which occurred within 500 meters of the associated property.
 Using this comprehensive crime incident response data, I produce a panel that allows me to observe crime incident counts near each property for several years before and after case resolution.
@@
 
-ADD DISCUSISON NOF PANDEMIC: ONLY THE MOST SERIOUS EVICTIONS PROCEEDED, BIASING EVICTEES TO BE MORE SERIOUS OFFENDERS
-
 \section{Institutional Context}
@@
 
-        \subsubsection{The Eviction Process}
+        \subsubsection{The Eviction Process in Massachusetts}
         Tenants in Massachusetts can rent from landlords under the terms of a lease or without one.
@@
 
-    \subsection{Crime Incident Responses}
+    \subsection{Crime in Boston}
+
+    1. How much crime is in Boston compared to most cities?
+    2. Where is crime worst in Boston?
+    3. When does the boston police department respond to an incident?
 
@@
     \subsection{Evictions Data}
+    I obtain records of every summary process case filed in Boston since April 2019 from MassLandlords, a trade association of landlords in Massachusetts.
+At the beginning of the pandemic, MassLandlords developed a sophisticated system for manually collecting and programatically scraping court dockets.
+Crucially, each record includes the resolution of the case, the last date on the case docket, and the address of the disputed property.
+Each record also includes details such as the court in which the case was initially filed, the duration of the case, whether the tenant and landlord had attorneys, and the type of notice to quit that was initially filed by the landlord.
+I use a paid geocoding service known as Geocodio to obtain highly accurate latitude and longitude coordinates for each property.
 
-        \newpage
+    I restrict my sample in 4 ways.
+First, I drop all records which could not be geocoded.
+Second, I drop the less than one percent of records for which a latest docket date could not be found.
+Third, I drop all cases which were resolved through mediation.
+Lastly, I drop cases for which a judgment could not be found.
+Out of \textcolor{red}{X} cases filed in Boston between April 2019 and March 2020, I am left with a sample of \textcolor{red}{Y} cases.
+Figure 1 displays the number of evictions in my sample filed during each month.
+
+        \begin{figure}[H]
+            \centering
+            \includegraphics{output/summary_statistics/figures/filings_over_time.png}
+            \caption{Eviction Filings Over Time in Boston}
+            \label{fig:my_label}
+        \end{figure}
+
+    \subsection{Crime Incidents Data}
+    I obtain incident-level records of every crime incident to which BPD offers responded to from August 2015 to present.
+Each record includes the a date, latitude and longitude coordinates, and an offense code indicating the type of crime incident that occurred.
+I drop all records missing any of these three variables.
+
+    \subsection{Census Tract Characteristics Data}
+    I obtain time-invariant census tract level characteristics of the properties in my sample from Opportunity Insights \citep{chetty_impacts_2018}.
+This data includes information such as population density, job density, median household income, and poverty rate.
+Figure 2 plots the locations of the evictions in my sample, coloring Boston's census tracts according to their poverty rates.
+It shows that the density of eviction filings tends to be higher in poor areas.
+
             \begin{figure}[H]
@@
 
-        \begin{landscape}
-        \begin{figure}[H]
+    \subsection{Merged Dataset}
+    My final dataset is a panel dataset of nearby crime incident counts at the property month-level.
+To produce this dataset, I use GIS tools to draw circles of radius 500 meters around each property in my dataset of evictions.
+I match each property with all crimes that fall within its radius.
+Then, for each property, I count the number of crimes that occurred within its radius during each month from August 2015 to present.
+
+    Table 1 contains descriptive statistics for the panel dataset.
+
+         \begin{table}[H]
             \centering
-            \includegraphics[scale=1.25]{output/summary_statistics/figures/filings_over_time.png}
-            \caption{Eviction Filings Over Time in Boston}
-            \label{fig:my_label}
-        \end{figure}
-\end{landscape}
+            \small
+            \input{output/summary_statistics/tables/summary_statistics}
+            \caption{Summary Statistics}
+            \label{tab:table_1}
+        \end{table}
+
        \begin{table}[H]
@@
         \end{table}
-
-    \subsection{Summary Statistics}
-         \begin{table}[H]
-            \centering
-            \small
-            \input{output/summary_statistics/tables/summary_statistics}
-            \caption{Summary Statistics}
-            \label{tab:table_1}
-        \end{table}
-        \newpage
 

### 2023-04-12 output/group_0_crimes_500m/tables/pre_treatment_covariate_tests.tex
generated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.53 \\
- & Change in Crime Incidents, 2017-2019 & 0.00 & 0.34 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.54 \\
+ & Change in Crime Incidents, 2017-2019 & 0.00 & 0.40 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.34 & 0.03 \\
- & Job density, 2013 & 0.00 & 0.29 \\
- & Median household income, 2016 & 0.06 & 0.01 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.09 & 0.65 \\
+ & Job density, 2013 & 0.00 & 0.97 \\
+ & Median household income, 2016 & 0.68 & 0.07 \\
  & Poverty rate, 2010 & 0.00 & 0.01 \\
- & Population density, 2010 & 0.00 & 0.57 \\
+ & Population density, 2010 & 0.00 & 0.65 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.03 & 0.00 \\
- & Filing without cause & 0.02 & 0.16 \\
- & Filing for nonpayment & 0.00 & 0.04 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.41 & 0.01 \\
+ & Filing without cause & 0.01 & 0.02 \\
+ & Filing for nonpayment & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.25 & 0.00 \\
- & Plaintiff has attorney & 0.38 & 0.06 \\
- & Defendant is entity & 0.00 & 0.13 \\
- & Plaintiff is entity & 0.02 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.04 & 0.00 \\
+ & Plaintiff has attorney & 0.63 & 0.00 \\
+ & Defendant is entity & 0.00 & 0.09 \\
+ & Plaintiff is entity & 0.03 & 0.00 \\
 \cline{1-4}

### 2023-04-12 output/group_0_crimes_warm_500m/tables/pre_treatment_covariate_tests.tex
generated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.88 \\
- & Change in Crime Incidents, 2017-2019 & 0.00 & 0.60 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.55 \\
+ & Change in Crime Incidents, 2017-2019 & 0.00 & 0.26 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.44 & 0.07 \\
- & Job density, 2013 & 0.00 & 0.15 \\
- & Median household income, 2016 & 0.56 & 0.03 \\
- & Poverty rate, 2010 & 0.00 & 0.00 \\
- & Population density, 2010 & 0.00 & 0.80 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.93 \\
+ & Job density, 2013 & 0.00 & 0.73 \\
+ & Median household income, 2016 & 0.00 & 0.11 \\
+ & Poverty rate, 2010 & 0.69 & 0.66 \\
+ & Population density, 2010 & 0.00 & 0.23 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.05 & 0.01 \\
- & Filing without cause & 0.08 & 0.59 \\
- & Filing for nonpayment & 0.01 & 0.02 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.48 & 0.00 \\
+ & Filing without cause & 0.05 & 0.00 \\
+ & Filing for nonpayment & 0.00 & 0.04 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.77 & 0.04 \\
- & Plaintiff has attorney & 0.84 & 0.19 \\
- & Defendant is entity & 0.00 & 0.07 \\
- & Plaintiff is entity & 0.26 & 0.03 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.02 & 0.00 \\
+ & Plaintiff has attorney & 0.92 & 0.00 \\
+ & Defendant is entity & 0.14 & 0.00 \\
+ & Plaintiff is entity & 0.51 & 0.01 \\
 \cline{1-4}

### 2023-04-12 output/summary_statistics/tables/summary_statistics.tex
generated figures

@@
 \midrule
-\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in Crime Incidents, 2017-2019 & -164.98 & 222.44 & 3,171 \\
- & Total Crime Incidents, 2017 & 1,230.16 & 697.53 & 3,171 \\
+\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in Crime Incidents, 2017-2019 & -152.00 & 217.38 & 1,632 \\
+ & Total Crime Incidents, 2017 & 1,162.73 & 714.55 & 1,632 \\
 \cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.30 & 0.21 & 3,171 \\
- & Job density, 2013 & 15,603.89 & 41,982.90 & 3,171 \\
- & Median household income, 2016 & 46,085.28 & 24,946.22 & 3,171 \\
- & Poverty rate, 2010 & 0.29 & 0.15 & 3,171 \\
- & Population density, 2010 & 23,385.01 & 13,324.90 & 3,171 \\
+\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.31 & 0.22 & 1,632 \\
+ & Job density, 2013 & 16,511.95 & 43,184.21 & 1,632 \\
+ & Median household income, 2016 & 46,399.34 & 25,059.82 & 1,632 \\
+ & Poverty rate, 2010 & 0.29 & 0.15 & 1,632 \\
+ & Population density, 2010 & 23,373.29 & 14,260.04 & 1,632 \\
 \cline{1-5}
-\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.16 & 0.36 & 3,171 \\
- & Filing without cause & 0.05 & 0.23 & 3,171 \\
- & Filing for nonpayment & 0.79 & 0.41 & 3,171 \\
+\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.11 & 0.32 & 1,632 \\
+ & Filing without cause & 0.04 & 0.20 & 1,632 \\
+ & Filing for nonpayment & 0.76 & 0.43 & 1,632 \\
 \cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.04 & 0.20 & 3,171 \\
- & Plaintiff has attorney & 0.87 & 0.34 & 3,171 \\
- & Defendant is entity & 0.02 & 0.13 & 3,171 \\
- & Plaintiff is entity & 0.82 & 0.39 & 3,171 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.03 & 0.18 & 1,632 \\
+ & Plaintiff has attorney & 0.91 & 0.29 & 1,632 \\
+ & Defendant is entity & 0.02 & 0.15 & 1,632 \\
+ & Plaintiff is entity & 0.84 & 0.36 & 1,632 \\
 \cline{1-5}
-\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 22.33 & 23.38 & 3,039 \\
- & Judgment by default & 0.25 & 0.43 & 3,171 \\
- & Case dismissed & 0.20 & 0.40 & 3,171 \\
- & Case heard & 0.02 & 0.14 & 3,171 \\
- & Money judgment & 1,806.43 & 4,135.66 & 3,171 \\
- & Case mediated & 0.48 & 0.50 & 3,171 \\
+\multirow[c]{10}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 19.82 & 24.51 & 1,538 \\
+ & Judgment by default & 0.48 & 0.50 & 1,632 \\
+ & Case dismissed & 0.41 & 0.49 & 1,632 \\
+ & Case heard & 0.05 & 0.21 & 1,632 \\
+ & Execution issued & 0.30 & 0.46 & 1,632 \\
+ & Money judgment & 1,456.98 & 3,445.07 & 1,632 \\
+ & Execution levied & 0.06 & 0.23 & 1,632 \\
+ & Case mediated & 0.00 & 0.00 & 1,632 \\
+ & Execution requested & 0.02 & 0.15 & 1,632 \\
+ & Execution status unknown & 0.00 & 0.00 & 1,632 \\
 \cline{1-5}

### 2023-04-12 src/02_analysis/stats_utilities.py

@@ -258,7 +258,7 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                        'unknown_execution']
     origin_columns = ['disposition_found', 'disposition_found', 'disposition_found',
                       'disposition_found', 'execution', 'execution', 'execution', 'execution']
-    target_values = ["Mediated", "Dismissed", "Defaulted", "Heard", "Levied", "Issued", "Requested", np.nan]
+    target_values = ["Mediated", "Dismissed", "Defaulted", "Heard", "Levied", "Issued", "Requested", None]
 
     for dummy_column, origin_column, target_value in zip(panel_E_columns, origin_columns, target_values):
         df.loc[:, dummy_column] = np.where(df[origin_column] == target_value, 1, 0)

### 2023-04-12 output/group_0_crimes_500m/tables/pre_treatment_covariate_tests.tex
generated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.54 \\
- & Change in Crime Incidents, 2017-2019 & 0.00 & 0.40 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.47 \\
+ & Change in Crime Incidents, 2017-2019 & 0.00 & 0.46 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.09 & 0.65 \\
- & Job density, 2013 & 0.00 & 0.97 \\
- & Median household income, 2016 & 0.68 & 0.07 \\
- & Poverty rate, 2010 & 0.00 & 0.01 \\
- & Population density, 2010 & 0.00 & 0.65 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.07 & 0.63 \\
+ & Job density, 2013 & 0.00 & 0.70 \\
+ & Median household income, 2016 & 0.49 & 0.03 \\
+ & Poverty rate, 2010 & 0.00 & 0.00 \\
+ & Population density, 2010 & 0.00 & 0.86 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.41 & 0.01 \\
- & Filing without cause & 0.01 & 0.02 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.21 & 0.00 \\
+ & Filing without cause & 0.01 & 0.03 \\
  & Filing for nonpayment & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.04 & 0.00 \\
- & Plaintiff has attorney & 0.63 & 0.00 \\
- & Defendant is entity & 0.00 & 0.09 \\
- & Plaintiff is entity & 0.03 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.02 & 0.00 \\
+ & Plaintiff has attorney & 0.25 & 0.00 \\
+ & Defendant is entity & 0.00 & 0.15 \\
+ & Plaintiff is entity & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-12 output/group_0_crimes_warm_500m/tables/pre_treatment_covariate_tests.tex
generated figures

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.55 \\
- & Change in Crime Incidents, 2017-2019 & 0.00 & 0.26 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.05 \\
+ & Change in Crime Incidents, 2017-2019 & 0.00 & 0.93 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.93 \\
- & Job density, 2013 & 0.00 & 0.73 \\
- & Median household income, 2016 & 0.00 & 0.11 \\
- & Poverty rate, 2010 & 0.69 & 0.66 \\
- & Population density, 2010 & 0.00 & 0.23 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.02 & 0.63 \\
+ & Job density, 2013 & 0.00 & 0.56 \\
+ & Median household income, 2016 & 0.13 & 0.19 \\
+ & Poverty rate, 2010 & 0.00 & 0.00 \\
+ & Population density, 2010 & 0.00 & 0.14 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.48 & 0.00 \\
- & Filing without cause & 0.05 & 0.00 \\
- & Filing for nonpayment & 0.00 & 0.04 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.71 & 0.01 \\
+ & Filing without cause & 0.11 & 0.75 \\
+ & Filing for nonpayment & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.02 & 0.00 \\
- & Plaintiff has attorney & 0.92 & 0.00 \\
- & Defendant is entity & 0.14 & 0.00 \\
- & Plaintiff is entity & 0.51 & 0.01 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.19 & 0.00 \\
+ & Plaintiff has attorney & 0.70 & 0.07 \\
+ & Defendant is entity & 0.00 & 0.04 \\
+ & Plaintiff is entity & 0.19 & 0.00 \\
 \cline{1-4}

### 2023-04-12 src/02_analysis/stats_utilities.py

@@ -254,11 +254,11 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     panel_D = pd.concat([panel_D], keys=["Panel D: Defendant and Plaintiff Characteristics"])
 
     # Panel E: Case Resolution
-    panel_E_columns = ['mediated', 'dismissed', 'defaulted', 'heard', 'levied', 'issued', 'requested',
+    panel_E_columns = ['dismissed', 'defaulted', 'heard', 'levied', 'issued', 'requested',
                        'unknown_execution']
-    origin_columns = ['disposition_found', 'disposition_found', 'disposition_found',
+    origin_columns = ['disposition_found', 'disposition_found',
                       'disposition_found', 'execution', 'execution', 'execution', 'execution']
-    target_values = ["Mediated", "Dismissed", "Defaulted", "Heard", "Levied", "Issued", "Requested", None]
+    target_values = ["Dismissed", "Defaulted", "Heard", "Levied", "Issued", "Requested", None]
 
     for dummy_column, origin_column, target_value in zip(panel_E_columns, origin_columns, target_values):
         df.loc[:, dummy_column] = np.where(df[origin_column] == target_value, 1, 0)

### 2023-04-12 writing/paper/main.tex

@@
 
-    I restrict my sample in 4 ways.
-First, I drop all records which could not be geocoded.
-Second, I drop the less than one percent of records for which a latest docket date could not be found.
-Third, I drop all cases which were resolved through mediation.
-Lastly, I drop cases for which a judgment could not be found.
-Out of \textcolor{red}{X} cases filed in Boston between April 2019 and March 2020, I am left with a sample of \textcolor{red}{Y} cases.
-Figure 1 displays the number of evictions in my sample filed during each month.
+    I restrict my sample in two ways.
+First, I drop 1651 cases which were resolved through mediation.
+Second, I drop 69 cases which were not resolved through mediation, but for which a final judgment could not be found.
+Out of just under 3352 Boston summary process cases adjudicated between April 2019 and March 2020, I am left with a sample of 1632 cases.
+Figure 2 displays the number of evictions in my sample filed during each month.
 
@@
 It shows that the density of eviction filings tends to be higher in poor areas.
+This result is consistent with existing research that finds strong associations between poverty and the prevalence of eviction \citep{desmond_housing_2016}.
+Indeed, <>, mirroring the findings of \cite{collinson_eviction_2022} in New York City and Chicago.
 
@@
 \section{Empirical Strategy: Difference-in-Differences}
-    \subsection{Conceptualizing Treatment}
-    I seek to estimate the average treatment effects of plaintiff victory in eviction cases on treated properties.
 I use the staggered difference-in-difference estimator proposed in \cite{callaway_difference--differences_2021}, which uses two-period, two-unit difference-in-difference estimators to estimate time- and cohort-specific ATTs and then aggregates them, weighting by cohort size, to produce summaries of the ATT.
+    \subsection{Conceptualizing Experiment}
+    \textbf{Treatment group.} I consider any property which was the site of an eviction case that was heard by a judge and decided in favor of the plaintiff or decided by default in favor of the plaintiff a treated property.
 
-    Let $G_i$ be the month during which the eviction case involving property $i$ was filed, such that $G_i = g \in \{\text{May} \; 2019, \text{June} \; 2019, ..., \text{May} \; 2021\}$.
+    \textbf{Control group.} I consider any property which was the site of an eviction case that was heard by a judge and decided in favor of the defendant or decided by dismissal in favor of the defendant a treated property.
+
+    \textbf{Treatment timing.} I consider each property's treatment timing to be the month of its latest docket date.
+
+       \subsection{Unconditional Estimates of the ATT}
+
+    Let $G_i$ be the month of the latest docket date in the eviction case involving property $i$, such that $G_i = g \in \{\text{April} \; 2019, \text{May} \; 2019, ..., \text{March} \; 2020\}$.
 Let $C_i = 1$ if the eviction case involving $i$ resulted in a victory for the defendant and $0$ otherwise.
@@
 
-    \subsection{Unconditional Estimates of the ATT}
     The following is an unconditional estimator for $ATT(g,t)$, the average treatment affect during month $t$ for cohort $g$.

### 2023-04-12 output/group_0_crimes_500m/tables/pre_treatment_covariate_tests.tex
generated figures

@@
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.07 & 0.63 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.75 & 0.63 \\
  & Job density, 2013 & 0.00 & 0.70 \\
- & Median household income, 2016 & 0.49 & 0.03 \\
+ & Median household income, 2016 & 0.01 & 0.03 \\
  & Poverty rate, 2010 & 0.00 & 0.00 \\
@@
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.21 & 0.00 \\
- & Filing without cause & 0.01 & 0.03 \\
- & Filing for nonpayment & 0.00 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.12 & 0.00 \\
+ & Filing without cause & 0.80 & 0.03 \\
+ & Filing for nonpayment & 0.01 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.02 & 0.00 \\
- & Plaintiff has attorney & 0.25 & 0.00 \\
- & Defendant is entity & 0.00 & 0.15 \\
- & Plaintiff is entity & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.50 & 0.00 \\
+ & Plaintiff has attorney & 0.21 & 0.00 \\
+ & Defendant is entity & 0.13 & 0.15 \\
+ & Plaintiff is entity & 0.01 & 0.00 \\
 \cline{1-4}

### 2023-04-12 src/02_analysis/stats_utilities.py

@@ -132,7 +132,7 @@ def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.D
 
 def select_controls(df: pd.DataFrame, treatment_date_variable: str, analysis: str, output_directory: str):
     """Choose covariates to include in D.R. model."""
-    covariate_exploration_table_columns = ["", ""]  # TODO: Add column naming logic.
+    covariate_exploration_table_columns = ["Change in Crime Incidents, April 2019-March 2020", "Treated Property"]  # TODO: Add column naming logic.
 
     # Run produce summary statistics on the DataFrame to get names of column names of potential pre-treatment covaiates.
     summary_statistics, variable_display_names_dict = produce_summary_statistics(df, 'latest_docket_date')
@@ -150,7 +150,7 @@ def select_controls(df: pd.DataFrame, treatment_date_variable: str, analysis: st
     independent_variable = 'judgment_for_plaintiff'
     dependent_variable = f'change_in_{analysis}_over_all_treated_weeks'
     if "month" in treatment_date_variable:
-        last_week_in_panel = '2023-01'
+        last_week_in_panel = '2020-03'
     else:
         last_week_in_panel = '2023-00'
     first_treated_week = df[treatment_date_variable].sort_values().iloc[0]

### 2023-04-12 output/group_1_crimes_500m/tables/pre_treatment_covariate_tests.tex
added column names to covariate exploration table

@@
 \\
- &  &  &  \\
+ &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 1 Incidents, 2017 & 0.00 & 0.10 \\
- & $\Delta$ Group 1 Incidents, 2017-2019 & 0.00 & 0.92 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 1 Incidents, 2017 & 0.00 & 0.80 \\
+ & $\Delta$ Group 1 Incidents, 2017-2019 & 0.00 & 0.83 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.03 \\
- & Job density, 2013 & 0.00 & 0.29 \\
- & Median household income, 2016 & 0.00 & 0.01 \\
- & Poverty rate, 2010 & 0.00 & 0.01 \\
- & Population density, 2010 & 0.01 & 0.57 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.63 \\
+ & Job density, 2013 & 0.00 & 0.70 \\
+ & Median household income, 2016 & 0.00 & 0.03 \\
+ & Poverty rate, 2010 & 0.00 & 0.00 \\
+ & Population density, 2010 & 0.04 & 0.86 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.10 & 0.00 \\
- & Filing without cause & 0.38 & 0.16 \\
- & Filing for nonpayment & 0.31 & 0.04 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.06 & 0.00 \\
+ & Filing without cause & 0.48 & 0.03 \\
+ & Filing for nonpayment & 0.85 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.29 & 0.00 \\
- & Plaintiff has attorney & 0.33 & 0.06 \\
- & Defendant is entity & 0.52 & 0.13 \\
- & Plaintiff is entity & 0.73 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.37 & 0.00 \\
+ & Plaintiff has attorney & 0.78 & 0.00 \\
+ & Defendant is entity & 0.73 & 0.15 \\
+ & Plaintiff is entity & 0.55 & 0.00 \\
 \cline{1-4}

### 2023-04-12 writing/paper/main.tex

@@
 
-    \textbf{Treatment timing.} I consider each property's treatment timing to be the month of its latest docket date.
-
        \subsection{Unconditional Estimates of the ATT}
@@
     Let $G_i$ be the month of the latest docket date in the eviction case involving property $i$, such that $G_i = g \in \{\text{April} \; 2019, \text{May} \; 2019, ..., \text{March} \; 2020\}$.
-Let $C_i = 1$ if the eviction case involving $i$ resulted in a victory for the defendant and $0$ otherwise.
+Let $C_i = 1$ property $i$ is treated at some point during the sample period and $0$ otherwise.
 If $G_i = g$ and $C_i = 0$, then property $i$ is a treated property and a member of the cohort first treated during month $g$ (cohort $g$).
 If $C_i=1$, then property $i$ is a never-treated property.
-Let $Y_{i,t}$ be property $i$'s Zestimate during month $t$ and define $\Delta Y_{i, g-1, t} \equiv Y_{i,t} - Y_{i,g-1}$ so that $\Delta Y_{i, g-1, t}$ is the change in property $i$'s Zestimate between months $t$ and $g-1$.
+Let $Y_{i,t}$ be property $i$'s crime incident count during month $t$ and define $\Delta Y_{i, g-1, t} \equiv Y_{i,t} - Y_{i,g-1}$ so that $\Delta Y_{i, g-1, t}$ is the change in property $i$'s crime incident count between months $t$ and $g-1$.
 
@@
 
-    The above unconditional parallel trends assumption is unlikely to hold, as eviction case outcomes and zestimates may be related to their socioeconomic surroundings.
-Table 3 explores this theory further, reporting results from univariate regressions of January 2022 Zestimates and an indicator for plaintiff victory on the pre-treatment characteristics listed in Panels A through D of Table 2.
+    The above unconditional parallel trends assumption is unlikely to hold, as eviction case outcomes and crime incident counts may be related to their socioeconomic surroundings.
+Table 3 explores this theory further, reporting results from univariate regressions of the change in crime incidents between May 2020 and April 2019 and an indicator for treatment on the pre-treatment characteristics listed in Panels A through D of Table 2.
 Each cell gives the p-value from a regression of the variable which labels its column on the variable which labels its row.
-Table 3 shows significant associations between pre-treatment characteristics and Zestimates and pre-treatment characteristics and case outcomes, suggesting that the unconditional parallel trends assumption imposed earlier may not be valid.
+Table 3 shows significant associations between pre-treatment characteristics and trends in crime incident counts and pre-treatment characteristics and case outcomes, suggesting that the unconditional parallel trends assumption imposed earlier may not be valid.
 
@@
         \centering
-        \input{}
+        \input{output/group_0_crimes_500m/tables/pre_treatment_covariate_tests}
         \caption{Relationship Between Pre-Treatment Characteristics and the Dependent and Independent Variables}
@@
 Second, using only never-treated counties, I regress $\Delta Y_{i, g-1, t}$ on $X_j$, weighting by $\hat{w}_i(X_i)$.
-Using the estimated coefficients $\hat{\beta}_{g-1, t}^{X}$, I define $\Delta \hat{\mu}_{g-1, t}(X_i) \equiv \hat{\beta}_{g-1, t}^{X}X_i$ so that $\Delta \hat{\mu}_{g-1, t}(X_i)$ is the predicted change in property $i$'s Zestimate between months $t$ and $g-1$.
+Using the estimated coefficients $\hat{\beta}_{g-1, t}^{X}$, I define $\Delta \hat{\mu}_{g-1, t}(X_i) \equiv \hat{\beta}_{g-1, t}^{X}X_i$ so that $\Delta \hat{\mu}_{g-1, t}(X_i)$ is the predicted change in property $i$'s crime incident counts between months $t$ and $g-1$.
     The doubly robust estimator for $ATT(g, t)$ is as follows.
@@
 
-    \newpage
     \begin{landscape}
+
     \begin{table}[H]
         \centering
-        \input{}
+        \input{output/group_0_crimes_500m/tables/balance_table}
         \caption{Balance Tests}
@@
     \end{table}
+
     \end{landscape}
 
-    \subsection{Aggregating Treatment Effects Across Cohort and Time}
-        \subsubsection{ATTs Across Cohorts}
-        \subsubsection{ATTs Across Time Periods}
-        \subsubsection{Event-Study ATTs}
+    \subsection{Aggregating Treatment Effects}
+        \subsection{}
 

### 2023-04-12 writing/paper/main.tex
Updates from Overleaf

@@
 Point estimates of the magnitudes of these effects are approximately between 2 and 4 percent of the mean number of crimes per month in the immediate vicinity of a property in 2017.
-Effects are driven by impacts during warm months.
 
@@
 
-    \subsection{Crime in Boston}
+    \subsection{Crime in Boston TODO}
 
@@
 In each row of column 4, I regress one covariate on an indicator for plaintiff victory and $\hat{w}_i(X_i)$ and report the coefficient on the indicator for plaintiff victory.
-Column 5 reports the p-values associated with each coefficient and shows that conditioning on pre-treatment covariates makes virtually all pre-treatment differences in covariates insignificant.
+Column 5 reports the p-values associated with each coefficient and shows that conditioning on pre-treatment covariates makes almost all pre-treatment differences in covariates insignificant.
 
@@
     \subsection{Aggregating Treatment Effects}
-        \subsection{}
+        The estimator in equation (2) produces estimates of $ATT(g, t)$ for each cohort at many different time periods.
+As such, following the recommendations of \cite{callaway_difference--differences_2021}, I aggregate my estimates of these $ATT(g, t)$ parameters according to time since treatment.
+For each $ATT(g, t)$, time since treatment $e$ is equal to $t-g$.
+I produce 95 percent confidence intervals around my estimates of $ATT(e)$ across diferent event times.
 
-\section{Results} \label{sec:result}
-
-    \subsection{Unconditional Estimates of the ATT}
+\section{Results and Mechanisms} \label{sec:result}
 
     \subsection{D.R. Estimates of the ATT}
+    \begin{figure}
+        \centering
+        \includegraphics{output/group_0_crimes_500m/figures/att_gt_dr_event_study_long_horizon.png}
+        \caption{Caption}
+        \label{fig:my_label}
+    \end{figure}
+
+    \subsection{Mechanisms}
 

### 2023-04-12 output/group_1_crimes_500m/tables/balance_table.tex

--- 2023-04-10 output/group_1_crimes_500m/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & Total Group 1 Incidents, 2017 & 59.33 & 3.74 & 0.00 & 1.22 & 0.24 \\
- & $\Delta$ Group 1 Incidents, 2017-2019 & -14.54 & -0.44 & 0.45 & -0.35 & 0.56 \\
+\multirow[c]{2}{.75cm}{\textit{Panel A}} & Total Group 1 Incidents, 2017 & 57.77 & -0.39 & 0.80 & -0.94 & 0.55 \\
+ & $\Delta$ Group 1 Incidents, 2017-2019 & -13.98 & 0.17 & 0.83 & 0.24 & 0.76 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel B}} & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & 207.41 & 0.89 \\
- & Poverty rate, 2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.13 \\
- & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & 479.29 & 0.27 \\
-\cline{1-7}
-\textit{Panel D} & Defendant is entity & 0.02 & -0.01 & 0.06 & 0.00 & 0.75 \\
+\multirow[c]{5}{.75cm}{\textit{Panel B}} & Bachelor's degree, 2010 & 0.32 & 0.01 & 0.63 & -0.00 & 0.72 \\
+ & Job density, 2013 & 16,161.03 & -845.94 & 0.70 & -398.30 & 0.85 \\
+ & Median household income, 2016 & 47,553.06 & 2,781.21 & 0.03 & -208.23 & 0.78 \\
+ & Poverty rate, 2010 & 0.28 & -0.02 & 0.00 & -0.01 & 0.16 \\
+ & Population density, 2010 & 23,320.19 & -128.01 & 0.86 & -374.93 & 0.60 \\
 \cline{1-7}

### 2023-04-12 output/group_6_crimes_500m/tables/pre_treatment_covariate_tests.tex

--- 2023-04-08 output/group_6_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \\
- &  &  &  \\
+ &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_6_crimes_500m & 0.00 & 0.00 \\
- & pre_treatment_change_in_group_6_crimes_500m & 0.00 & 0.07 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 6 Incidents, 2017 & 0.00 & 0.55 \\
+ & $\Delta$ Group 6 Incidents, 2017-2019 & 0.00 & 0.70 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
- & job_density_2013 & 0.00 & 0.10 \\
- & med_hhinc2016 & 0.63 & 0.05 \\
- & poor_share2010 & 0.55 & 0.96 \\
- & popdensity2010 & 0.00 & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.63 \\
+ & Job density, 2013 & 0.00 & 0.70 \\
+ & Median household income, 2016 & 0.91 & 0.03 \\
+ & Poverty rate, 2010 & 0.00 & 0.00 \\
+ & Population density, 2010 & 0.00 & 0.86 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.26 & 0.00 \\
- & no_cause & 0.22 & 0.95 \\
- & non_payment & 0.13 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.05 & 0.00 \\
+ & Filing without cause & 0.96 & 0.03 \\
+ & Filing for nonpayment & 0.03 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.66 & 0.00 \\
- & hasAttyP & 0.00 & 0.00 \\
- & isEntityD & 0.00 & 0.06 \\
- & isEntityP & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.44 & 0.00 \\
+ & Plaintiff has attorney & 0.14 & 0.00 \\
+ & Defendant is entity & 0.23 & 0.15 \\
+ & Plaintiff is entity & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-12 writing/paper/main.tex

@@
 I use the staggered difference-in-difference estimator proposed in \cite{callaway_difference--differences_2021}, which uses two-period, two-unit difference-in-difference estimators to estimate time- and cohort-specific ATTs and then aggregates them, weighting by cohort size, to produce summaries of the ATT.
+
+There are two main reasons that the traditional two-way fixed effects estimator is inferior to \cite{callaway_difference--differences_2021}'s estimator.
+\cite{goodman-bacon_difference--differences_2021} shows that the treatment effect produced by the two-way fixed effects estimator is a weighted average of many canonical two unit, two period difference-in-differences estimates.
+The first reason that the two-way fixed effects estimator is inferior is that some of these two unit, two period difference-in-differences estimates make ``forbidden comparisons'' between units which have both already been treated.
+Because these comparisons use already treated units as the counterfactual for other already treated units, they are inconsistent with the spirit of a quasi-experimental approach.
+\cite{callaway_difference--differences_2021}'s estimator individually calculates only those two unit, two period difference-in-differences estimates which make comparisons between treated and untreated units.
+The second reason is that the two-way fixed estimator weights this average of two unit, two period difference-in-differences estimates using treatment variances, whereas \cite{callaway_difference--differences_2021}'s estimator simply uses  the share of treated units.
+
     \subsection{Conceptualizing Experiment}
@@
         The estimator in equation (2) produces estimates of $ATT(g, t)$ for each cohort at many different time periods.
-As such, following the recommendations of \cite{callaway_difference--differences_2021}, I aggregate my estimates of these $ATT(g, t)$ parameters according to time since treatment.
+As such, following \cite{callaway_difference--differences_2021} and \cite{goodman-bacon_changes_2019}, I aggregate my estimates of these $ATT(g, t)$ parameters according to time since treatment.
 For each $ATT(g, t)$, time since treatment $e$ is equal to $t-g$.
-I produce 95 percent confidence intervals around my estimates of $ATT(e)$ across diferent event times.
+I produce 95 percent confidence intervals around my estimates of $ATT(e)$ across different event times.
 

### 2023-04-12 writing/paper/main.tex

@@
     \subsection{Evictions Data}
-    I obtain records of every summary process case filed in Boston since April 2019 from MassLandlords, a trade association of landlords in Massachusetts.
+    I obtain records of every summary process case that concluded in Boston between April 2019 and Janury 2023 from MassLandlords, a trade association of landlords in Massachusetts.
 At the beginning of the pandemic, MassLandlords developed a sophisticated system for manually collecting and programatically scraping court dockets.
@@
 
-    I restrict my sample in two ways.
-First, I drop 1651 cases which were resolved through mediation.
-Second, I drop 69 cases which were not resolved through mediation, but for which a final judgment could not be found.
-Out of just under 3352 Boston summary process cases adjudicated between April 2019 and March 2020, I am left with a sample of 1632 cases.
+    I restrict my sample in five ways.
+First, I drop all cases missing a most recent docket date.
+Second, I drop all cases missing property addresses.
+Third, I drop cases which concluded during April 2020 or later.
+Fourth, I drop all cases resolved through mediation.
+Lastly, I drop all cases for which a judgment could not be scraped.
+Table 1 outlines how these sample restrictions altered the number of observations in my study.
 Figure 2 displays the number of evictions in my sample filed during each month.
@@
 
+\begin{landscape}
+\newgeometry{top=10cm}
+    \thispagestyle{empty} 
     \begin{table}[H]
@@
         \input{output/group_0_crimes_500m/tables/pre_treatment_covariate_tests}
-        \caption{Relationship Between Pre-Treatment Characteristics and the Dependent and Independent Variables}
+        \caption{Pre-Treatment Covariate Tests}
         \label{tab:my_label}
     \end{table}
+\restoregeometry
+    \end{landscape}
 
@@
 Define $\hat{w}^*_i(X_i) = \frac{\hat{w}_i(X_i)}{\sum_i \hat{w}_i(X_i)}$.
-Second, using only never-treated counties, I regress $\Delta Y_{i, g-1, t}$ on $X_j$, weighting by $\hat{w}_i(X_i)$.
+Second, using only never-treated properties, I regress $\Delta Y_{i, g-1, t}$ on $X_j$, weighting by $\hat{w}_i(X_i)$.
 Using the estimated coefficients $\hat{\beta}_{g-1, t}^{X}$, I define $\Delta \hat{\mu}_{g-1, t}(X_i) \equiv \hat{\beta}_{g-1, t}^{X}X_i$ so that $\Delta \hat{\mu}_{g-1, t}(X_i)$ is the predicted change in property $i$'s crime incident counts between months $t$ and $g-1$.
@@
     \subsection{D.R. Estimates of the ATT}
-    \begin{figure}
+    \begin{figure}[H]
         \centering
         \includegraphics{output/group_0_crimes_500m/figures/att_gt_dr_event_study_long_horizon.png}
-        \caption{Caption}
+        \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters}
         \label{fig:my_label}

### 2023-04-12 output/group_0_crimes_execution_levied_500m/tables/pre_treatment_covariate_tests.tex
ran cold and warm months analysis

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.00 \\
 & Change in Crime Incidents, 2017-2019 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.17 & 0.00 \\
 & Job density, 2013 & 0.00 & 0.00 \\
 & Median household income, 2016 & 0.70 & 0.00 \\
 & Poverty rate, 2010 & 0.01 & 0.69 \\
 & Population density, 2010 & 0.00 & 0.74 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.16 & 0.17 \\
 & Filing without cause & 0.28 & 0.05 \\
 & Filing for nonpayment & 0.04 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & nan & nan \\
 & Plaintiff has attorney & 0.18 & 0.00 \\
 & Defendant is entity & 0.04 & 0.63 \\
 & Plaintiff is entity & 0.12 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-12 src/02_analysis/figure_utilities.py

@@ -35,6 +35,10 @@ def aggregate_by_event_time_and_plot(att_gt,
     fig, ax = plt.subplots(layout='constrained')
     x = results_df.index
     y = results_df['ATT']
+    print(y.loc[1:36].min())
+    print(y.loc[1:36].median())
+    print(y.loc[1:36].mean())
+    print(y.loc[1:36].max())
     y_upper = results_df['upper'].where(results_df['upper'].notna(), y)
     y_lower = results_df['lower'].where(results_df['lower'].notna(), y)
     ax.set_ylabel("ATT")

### 2023-04-12 writing/paper/main.tex
Updates from Overleaf

@@
 
+\begin{table}[H]
+    \centering
+    \input{output/summary_statistics/tables/sample_restriction}
+    \caption{Sample Construction}
+    \label{tab:my_label}
+\end{table}
+
         \begin{figure}[H]
@@
 Each record includes the a date, latitude and longitude coordinates, and an offense code indicating the type of crime incident that occurred.
-I drop all records missing any of these three variables.
+I drop all crime incident records missing any of these three variables.
 
@@
 This result is consistent with existing research that finds strong associations between poverty and the prevalence of eviction \citep{desmond_housing_2016}.
-Indeed, <>, mirroring the findings of \cite{collinson_eviction_2022} in New York City and Chicago.
+Indeed, 64 percent of eviction cases won by the plaintiff concern properties in census tracts with povery rates above 20 percent.
+This descriptive finding mirrors that of \cite{collinson_eviction_2022}: they show that 58 percent of evictions in New York and 46 percent of evictions in Cook County occur in census tracts with poverty rates above 20 percent.
 
@@
             \centering
-            \includegraphics{output/summary_statistics/figures/evictions_map.png}
+            \includegraphics[scale=1.3]{output/summary_statistics/figures/evictions_map.png}
             \caption{Spatial Incidence of Eviction}
@@
 
-    Table 1 contains descriptive statistics for the panel dataset.
+    Table 1 contains descriptive statistics for the panel dataset. \textcolor{red}{TODO}
 
@@
 
-\section{Results and Mechanisms} \label{sec:result}
+\section{Results and Potential Mechanisms} \label{sec:result}
 
-    \subsection{D.R. Estimates of the ATT}
+    \subsection{Doubly Robust Estimates of the ATT}
+    Doubly robust estimates of event-time aggregated treatment effects become negative and significantly different from zero during month two after treatment, and remain so for the next 34 months.
+\textcolor{red}{My identifying assumption of parallel trends between groups with the same pre-treatment characteristics appears satisfied; treatment effects at event times $-5$ through $-1$ are extremely close to 0.
+Treatment effects at event times $-6$ through $-1$ are not significantly different from 0.} Crime incident counts in the vicinity of treated properties and the vicinity of untreated properties only begin to change relative to each other after treatment occurs.
+
+    Treatment effects from months 1 to 36 after treatment range from -1.54 to -4.94.
+The magnitudes of these point estimates are between 1.60 and 5.15 percent of the average number of crimes per month in a single property's radius in 2017
+
+    the fact that they increase gradually during first three months after treatment is consistent with the fact that landlords have 90 days to file for execution.
     \begin{figure}[H]
@@
     \subsection{Mechanisms}
+
+    In this section, I argue that the most likely mechanism for the treatment effects I observe is the removal of targets of, accessories to, and/or culprits of crime incidents from the immediate vicinity of the property.
+Three pieces of evidence support this hypothesis.
+
+    First, the steady increase in estimated treatment effects during the first three months after treatment is consistent with the timeline by which tenants are removed from properties.
+During months 0, 1, 2, and 3 relative to treatment, the magnitude of treatment effects steadily increases.
+This steady increase in estimated treatment effects during the first three months after treatment is consistent with the fact that an execution for possession remains valid for 90 days after its issuance and suggests that progressively more tenants are removed from units during the first three months after treatment.
+In contrast, treatment effect magnitudes at event times 4 and greater do not follow any clear pattern.
+
+    Second, treatment effects are driven by evictions that were concluded during warm months.
+Post-treatment impacts of eviction are uniformly smaller in magnitude during cold months and largely insignificant from 0, as shown in Figures 4 and 5.
+
+    Third, placebo tests using \<crimes that are most common in wealthy areas\> as an outcome do not show evidence
+
+    1. placebo test
+
+    2. warm results
+
+    3. Steady increase
+
+    Point estimates of the post-treatment $ATT(e)$'s become negative and significantly different from zero almost immediately after treatment and remain so for the next three years.
+Assuming that the units in my sample are vacant for less than three years after eviction, this means that treatment effects are negative both while the property is vacant and once a new tenant arrives.
+
+    This suggests two things about evicted tenants. First, it suggests that just before eviction, they are culprits of, accessories to, or targets of crime incidents.
+
+    Point estimates of the post-treatment ATT remain negative and significantly different from zero not just for the first few months after treatment, but for the first three years after treatment.
+
+    \subsection{Robustness}
+    \subsection{How does the lack of execution data bias my results?}
 

### 2023-04-13 output/group_0_crimes_warm_500m/tables/pre_treatment_covariate_tests.tex
placebo figure

@@
 \\
- &  &  &  \\
+ &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.05 \\
- & Change in Crime Incidents, 2017-2019 & 0.00 & 0.93 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.42 \\
+ & Change in Crime Incidents, 2017-2019 & 0.00 & 0.26 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.02 & 0.63 \\
- & Job density, 2013 & 0.00 & 0.56 \\
- & Median household income, 2016 & 0.13 & 0.19 \\
- & Poverty rate, 2010 & 0.00 & 0.00 \\
- & Population density, 2010 & 0.00 & 0.14 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.88 \\
+ & Job density, 2013 & 0.00 & 0.62 \\
+ & Median household income, 2016 & 0.00 & 0.06 \\
+ & Poverty rate, 2010 & 0.00 & 0.60 \\
+ & Population density, 2010 & 0.00 & 0.38 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.71 & 0.01 \\
- & Filing without cause & 0.11 & 0.75 \\
- & Filing for nonpayment & 0.00 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.11 & 0.01 \\
+ & Filing without cause & 0.72 & 0.00 \\
+ & Filing for nonpayment & 0.04 & 0.04 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.19 & 0.00 \\
- & Plaintiff has attorney & 0.70 & 0.07 \\
- & Defendant is entity & 0.00 & 0.04 \\
- & Plaintiff is entity & 0.19 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.91 & 0.00 \\
+ & Plaintiff has attorney & 0.53 & 0.00 \\
+ & Defendant is entity & 0.31 & 0.00 \\
+ & Plaintiff is entity & 0.01 & 0.02 \\
 \cline{1-4}

### 2023-04-13 output/group_1_crimes_500m/tables/balance_table.tex
placebo figure

--- 2023-04-10 output/group_1_crimes_500m/tables/balance_table.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A}} & Total Group 1 Incidents, 2017 & 59.33 & 3.74 & 0.00 & 1.22 & 0.24 \\
- & $\Delta$ Group 1 Incidents, 2017-2019 & -14.54 & -0.44 & 0.45 & -0.35 & 0.56 \\
+\textit{Panel A} & Total Group 1 Incidents, 2017 & 81.75 & -2.95 & 0.50 & -2.42 & 0.58 \\
 \cline{1-7}
-\multirow[c]{3}{3cm}{\textit{Panel B}} & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & 207.41 & 0.89 \\
- & Poverty rate, 2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.13 \\
- & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & 479.29 & 0.27 \\
+\multirow[c]{5}{.75cm}{\textit{Panel B}} & Bachelor's degree, 2010 & 0.32 & 0.00 & 0.81 & -0.01 & 0.44 \\
+ & Job density, 2013 & 16,161.03 & -1,272.66 & 0.55 & -535.86 & 0.80 \\
+ & Median household income, 2016 & 47,553.06 & 2,997.87 & 0.01 & -1,006.45 & 0.32 \\
+ & Poverty rate, 2010 & 0.28 & -0.02 & 0.00 & -0.01 & 0.21 \\
+ & Population density, 2010 & 23,320.19 & -297.77 & 0.67 & -643.10 & 0.37 \\
 \cline{1-7}
-\textit{Panel D} & Defendant is entity & 0.02 & -0.01 & 0.06 & 0.00 & 0.75 \\
+\textit{Panel C} & Filing for nonpayment & 0.72 & -0.11 & 0.00 & -0.03 & 0.08 \\
+\cline{1-7}
+\multirow[c]{2}{.75cm}{\textit{Panel D}} & Plaintiff has attorney & 0.88 & -0.05 & 0.00 & -0.03 & 0.05 \\
+ & Plaintiff is entity & 0.81 & -0.08 & 0.00 & -0.03 & 0.08 \\
 \cline{1-7}

### 2023-04-13 output/group_1_crimes_500m/tables/pre_treatment_covariate_tests.tex
placebo figure

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 1 Incidents, 2017 & 0.00 & 0.80 \\
- & $\Delta$ Group 1 Incidents, 2017-2019 & 0.00 & 0.83 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 1 Incidents, 2017 & 0.00 & 0.50 \\
+ & $\Delta$ Group 1 Incidents, 2017-2019 & 0.17 & 0.04 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.63 \\
- & Job density, 2013 & 0.00 & 0.70 \\
- & Median household income, 2016 & 0.00 & 0.03 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.81 \\
+ & Job density, 2013 & 0.00 & 0.55 \\
+ & Median household income, 2016 & 0.00 & 0.01 \\
  & Poverty rate, 2010 & 0.00 & 0.00 \\
- & Population density, 2010 & 0.04 & 0.86 \\
+ & Population density, 2010 & 0.01 & 0.67 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.06 & 0.00 \\
- & Filing without cause & 0.48 & 0.03 \\
- & Filing for nonpayment & 0.85 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.15 & 0.01 \\
+ & Filing without cause & 0.46 & 0.03 \\
+ & Filing for nonpayment & 0.02 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.37 & 0.00 \\
- & Plaintiff has attorney & 0.78 & 0.00 \\
- & Defendant is entity & 0.73 & 0.15 \\
- & Plaintiff is entity & 0.55 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.15 & 0.00 \\
+ & Plaintiff has attorney & 0.00 & 0.00 \\
+ & Defendant is entity & 0.21 & 0.24 \\
+ & Plaintiff is entity & 0.00 & 0.00 \\
 \cline{1-4}

### 2023-04-13 output/group_2_crimes_500m/tables/pre_treatment_covariate_tests.tex
placebo figure

@@
 \\
- &  &  &  \\
+ &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 2 Incidents, 2017 & 0.00 & 0.78 \\
- & $\Delta$ Group 2 Incidents, 2017-2019 & 0.00 & 0.95 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 2 Incidents, 2017 & 0.00 & 0.92 \\
+ & $\Delta$ Group 2 Incidents, 2017-2019 & 0.00 & 0.14 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.07 \\
- & Job density, 2013 & 0.00 & 0.15 \\
- & Median household income, 2016 & 0.00 & 0.03 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.81 \\
+ & Job density, 2013 & 0.00 & 0.55 \\
+ & Median household income, 2016 & 0.00 & 0.01 \\
  & Poverty rate, 2010 & 0.00 & 0.00 \\
- & Population density, 2010 & 0.00 & 0.80 \\
+ & Population density, 2010 & 0.02 & 0.67 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.67 & 0.01 \\
- & Filing without cause & 0.89 & 0.59 \\
- & Filing for nonpayment & 0.61 & 0.02 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.16 & 0.01 \\
+ & Filing without cause & 0.67 & 0.03 \\
+ & Filing for nonpayment & 0.01 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.88 & 0.04 \\
- & Plaintiff has attorney & 0.67 & 0.19 \\
- & Defendant is entity & 0.36 & 0.07 \\
- & Plaintiff is entity & 0.27 & 0.03 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.91 & 0.00 \\
+ & Plaintiff has attorney & 0.79 & 0.00 \\
+ & Defendant is entity & 0.06 & 0.24 \\
+ & Plaintiff is entity & 0.33 & 0.00 \\
 \cline{1-4}

### 2023-04-13 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
placebo figure

@@
 \\
- &  &  &  \\
+ &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 3 Incidents, 2017 & 0.00 & 0.16 \\
- & $\Delta$ Group 3 Incidents, 2017-2019 & 0.00 & 0.07 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 3 Incidents, 2017 & nan & nan \\
+ & $\Delta$ Group 3 Incidents, 2017-2019 & nan & nan \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.03 \\
- & Job density, 2013 & 0.00 & 0.29 \\
- & Median household income, 2016 & 0.00 & 0.01 \\
- & Poverty rate, 2010 & 0.00 & 0.01 \\
- & Population density, 2010 & 0.00 & 0.57 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & nan & 0.81 \\
+ & Job density, 2013 & nan & 0.55 \\
+ & Median household income, 2016 & nan & 0.01 \\
+ & Poverty rate, 2010 & nan & 0.00 \\
+ & Population density, 2010 & nan & 0.67 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.03 & 0.00 \\
- & Filing without cause & 0.02 & 0.16 \\
- & Filing for nonpayment & 0.00 & 0.04 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & nan & 0.01 \\
+ & Filing without cause & nan & 0.03 \\
+ & Filing for nonpayment & nan & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.27 & 0.00 \\
- & Plaintiff has attorney & 0.00 & 0.06 \\
- & Defendant is entity & 0.01 & 0.13 \\
- & Plaintiff is entity & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & nan & 0.00 \\
+ & Plaintiff has attorney & nan & 0.00 \\
+ & Defendant is entity & nan & 0.24 \\
+ & Plaintiff is entity & nan & 0.00 \\
 \cline{1-4}

### 2023-04-13 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
placebo figure

@@
 \\
- &  &  &  \\
+ &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 4 Incidents, 2017 & 0.00 & 0.56 \\
- & $\Delta$ Group 4 Incidents, 2017-2019 & 0.00 & 0.90 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 4 Incidents, 2017 & 0.00 & 0.23 \\
+ & $\Delta$ Group 4 Incidents, 2017-2019 & 0.00 & 0.06 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.64 & 0.03 \\
- & Job density, 2013 & 0.00 & 0.29 \\
- & Median household income, 2016 & 0.54 & 0.01 \\
- & Poverty rate, 2010 & 0.25 & 0.01 \\
- & Population density, 2010 & 0.00 & 0.57 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.01 & 0.81 \\
+ & Job density, 2013 & 0.38 & 0.55 \\
+ & Median household income, 2016 & 0.00 & 0.01 \\
+ & Poverty rate, 2010 & 0.05 & 0.00 \\
+ & Population density, 2010 & 0.00 & 0.67 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.10 & 0.00 \\
- & Filing without cause & 0.28 & 0.16 \\
- & Filing for nonpayment & 0.07 & 0.04 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.13 & 0.01 \\
+ & Filing without cause & 0.66 & 0.03 \\
+ & Filing for nonpayment & 0.16 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.31 & 0.00 \\
- & Plaintiff has attorney & 0.67 & 0.06 \\
- & Defendant is entity & 0.19 & 0.13 \\
- & Plaintiff is entity & 0.65 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.49 & 0.00 \\
+ & Plaintiff has attorney & 0.44 & 0.00 \\
+ & Defendant is entity & 0.60 & 0.24 \\
+ & Plaintiff is entity & 0.20 & 0.00 \\
 \cline{1-4}

### 2023-04-13 output/group_5_crimes_500m/tables/pre_treatment_covariate_tests.tex
placebo figure

--- 2023-04-10 output/group_5_crimes_500m/tables/pre_treatment_covariate_tests.tex
@@
 \\
- &  &  &  \\
+ &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
  & \emph{Independent Variable} &  &  \\
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 5 Incidents, 2017 & nan & nan \\
- & $\Delta$ Group 5 Incidents, 2017-2019 & nan & nan \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 5 Incidents, 2017 & 0.00 & 0.25 \\
+ & $\Delta$ Group 5 Incidents, 2017-2019 & 0.00 & 0.25 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & nan & 0.22 \\
- & Job density, 2013 & nan & 0.10 \\
- & Median household income, 2016 & nan & 0.05 \\
- & Poverty rate, 2010 & nan & 0.96 \\
- & Population density, 2010 & nan & 0.00 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.81 \\
+ & Job density, 2013 & 0.00 & 0.55 \\
+ & Median household income, 2016 & 0.00 & 0.01 \\
+ & Poverty rate, 2010 & 0.00 & 0.00 \\
+ & Population density, 2010 & 0.41 & 0.67 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & nan & 0.00 \\
- & Filing without cause & nan & 0.95 \\
- & Filing for nonpayment & nan & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.59 & 0.01 \\
+ & Filing without cause & 0.17 & 0.03 \\
+ & Filing for nonpayment & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & nan & 0.00 \\
- & Plaintiff has attorney & nan & 0.00 \\
- & Defendant is entity & nan & 0.06 \\
- & Plaintiff is entity & nan & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.33 & 0.00 \\
+ & Plaintiff has attorney & 0.75 & 0.00 \\
+ & Defendant is entity & 0.00 & 0.24 \\
+ & Plaintiff is entity & 0.90 & 0.00 \\
 \cline{1-4}

### 2023-04-13 src/02_analysis/constants.py

@@ -1,9 +1,5 @@
 class Variables:
     outcomes = ['group_0_crimes_500m',
                 'group_1_crimes_500m',
-                'group_2_crimes_500m', 
-                'group_3_crimes_500m',
-                'group_4_crimes_500m',
-                'group_5_crimes_500m',
-                'group_6_crimes_500m']
+                'group_2_crimes_500m']
 

### 2023-04-13 writing/paper/main.tex

@@
     Treatment effects from months 1 to 36 after treatment range from -1.54 to -4.94.
-The magnitudes of these point estimates are between 1.60 and 5.15 percent of the average number of crimes per month in a single property's radius in 2017
+The magnitudes of these point estimates are between 1.60 and 5.15 percent of the average number of crimes per month in a single property's radius in 2017.
 
-    the fact that they increase gradually during first three months after treatment is consistent with the fact that landlords have 90 days to file for execution.
     \begin{figure}[H]
@@
 
-    In this section, I argue that the most likely mechanism for the treatment effects I observe is the removal of targets of, accessories to, and/or culprits of crime incidents from the immediate vicinity of the property.
+    In this section, I argue that the most likely mechanism for the treatment effects I observe is the removal of individuals who are targets of, accessories to, and/or culprits of crime incidents from the immediate vicinity of the property.
 Three pieces of evidence support this hypothesis.
@@
 
+    Second, a placebo test using crimes that are more common in wealthier census tracts do not produce significant treatment effects.
+If the above mechanism is correct—if the effects I observe are the result of the removal of individuals who interact with crime in some capacity—then my model should estimate weaker effects of eviction on crime incidents which are less common in areas with similar poverty rates to areas where evictions are common.
+To implement this placebo test, I first restrict my crime dataset only to crimes which occurred between January 2019 and March 2020.
+For each category of crime incident in my data, I calculate the median, 75th percentile, and 99th percentile of the poverty rates of the census tracts in which that cateogry of incident occurred.
+I listed the ten crime incident categories with the ten lowest median census tract poverty rates.
+From these ten categories, I selected three: shoplifting, motor vehicle accidents, and motor vehicle towing.
+Table 4 gives information about the distribution of poverty rates in census tracts where these crimes occur, along with information about the distribution of poverty rates in census tracts where evictions are filed.
+Column 1 shows that the poverty rate of the median census tract containing a shoplifting, motor vehicle accident, or motor vehicle towing incident has a much lower poverty rate than the poverty rate of the median census tract containing an eviction filing.
+Similar results are shown in columns 2 and 3.
+Table 4 shows that shoplifting, motor vehicle accident, and motor vehicle towing incidents tend to occur in census tracts with much lower poverty rates than eviction filings.
+
+    \begin{table}[H]
+        \centering
+        \input
+        \caption{Caption}
+        \label{tab:my_label}
+    \end{table}
+
+    Figure 5 shows that applying the doubly robust estimator from the previous section produces treatment effects that extremely small in magnitude compared to the treatment effects estimated using all crime incidents as the outcome variable.
+Point estimates are not uniformly positive or negative.
+The lack of a treatment effect of eviction on crimes which are less common in high poverty areas and which theory suggests should not be affected by eviction provides strong evidence for the mechanism I hypothesize.
+
+    I select three categories of crime incidents which are more common in
+
     Second, treatment effects are driven by evictions that were concluded during warm months.
 Post-treatment impacts of eviction are uniformly smaller in magnitude during cold months and largely insignificant from 0, as shown in Figures 4 and 5.
+\textcolor{red}{todo!}
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics{output/group_0_crimes_warm_500m/figures/att_gt_dr_event_study_long_horizon.png}
+        \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters (Cases Concluded During Warm Months)}
+        \label{fig:my_label}
+    \end{figure}
+
+       \begin{figure}[H]
+        \centering
+        \includegraphics{output/group_0_crimes_cold_500m/figures/att_gt_dr_event_study_long_horizon.png}
+        \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters (Cases Concluded During Cold Months)}
+        \label{fig:my_label}
+    \end{figure}
 

### 2023-04-13 output/group_0_crimes_cold_500m/tables/pre_treatment_covariate_tests.tex
Ran cold month analysis

--- 2023-04-13 output/group_0_crimes_warm_500m/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.42 \\
- & Change in Crime Incidents, 2017-2019 & 0.00 & 0.26 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.43 \\
+ & Change in Crime Incidents, 2017-2019 & 0.00 & 0.27 \\
 \cline{1-4}

### 2023-04-13 writing/paper/main.tex
Updates from Overleaf

@@
 
+\begin{landscape}
+
     \begin{table}[H]
         \centering
-        \input
-        \caption{Caption}
+        \input{output/group_0_crimes_500m/tables/placebo_poverty_rates}
+        \caption{TODO}
         \label{tab:my_label}
     \end{table}
+    \end{landscape}
 
@@
 
-    I select three categories of crime incidents which are more common in
+    \begin{figure}
+        \centering
+        \includegraphics{output/group_1_crimes_500m/figures/att_gt_dr_event_study_long_horizon.png}
+        \caption{TODO}
+        \label{fig:my_label}
+    \end{figure}
 
-    Second, treatment effects are driven by evictions that were concluded during warm months.
+    Third, treatment effects are driven by evictions that were concluded during warm months.
 Post-treatment impacts of eviction are uniformly smaller in magnitude during cold months and largely insignificant from 0, as shown in Figures 4 and 5.
-\textcolor{red}{todo!}
+A large body of research has found evidence of significant seasonal increases in crime during warmer months \citep{lauritsen_seasonal_2014}.
+The fact that treatment effects are largest during warm months is consistent with the hypothesis that evicted tenants interact with crime to a greater extent than the tenants that replace them.
 
@@
         \centering
-        \includegraphics{output/group_0_crimes_warm_500m/figures/att_gt_dr_event_study_long_horizon.png}
+        \includegraphics{output/group_0_crimes_cold_500m/figures/att_gt_dr_event_study_long_horizon.png}
         \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters (Cases Concluded During Warm Months)}
@@
         \centering
-        \includegraphics{output/group_0_crimes_cold_500m/figures/att_gt_dr_event_study_long_horizon.png}
+        \includegraphics{output/group/figures/att_gt_unconditional_event_study_long_horizon.png}
         \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters (Cases Concluded During Cold Months)}
@@
 
-    Third, placebo tests using \<crimes that are most common in wealthy areas\> as an outcome do not show evidence
+    \subsection{Robustness}
+    1. Remove large apartment buildings
 
-    1. placebo test
-
-    2. warm results
-
-    3. Steady increase
-
-    Point estimates of the post-treatment $ATT(e)$'s become negative and significantly different from zero almost immediately after treatment and remain so for the next three years.
-Assuming that the units in my sample are vacant for less than three years after eviction, this means that treatment effects are negative both while the property is vacant and once a new tenant arrives.
-
-    This suggests two things about evicted tenants. First, it suggests that just before eviction, they are culprits of, accessories to, or targets of crime incidents.
-
-    Point estimates of the post-treatment ATT remain negative and significantly different from zero not just for the first few months after treatment, but for the first three years after treatment.
-
-    \subsection{Robustness}
     \subsection{How does the lack of execution data bias my results?}

### 2023-04-13 output/group_0_crimes_warm_500m/tables/pre_treatment_covariate_tests.tex
Ran war, month analysis

@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.42 \\
- & Change in Crime Incidents, 2017-2019 & 0.00 & 0.26 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.06 \\
+ & Change in Crime Incidents, 2017-2019 & 0.00 & 0.98 \\
 \cline{1-4}
-\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.88 \\
- & Job density, 2013 & 0.00 & 0.62 \\
- & Median household income, 2016 & 0.00 & 0.06 \\
- & Poverty rate, 2010 & 0.00 & 0.60 \\
- & Population density, 2010 & 0.00 & 0.38 \\
+\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.76 \\
+ & Job density, 2013 & 0.00 & 0.58 \\
+ & Median household income, 2016 & 0.00 & 0.16 \\
+ & Poverty rate, 2010 & 0.00 & 0.00 \\
+ & Population density, 2010 & 0.00 & 0.13 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.11 & 0.01 \\
- & Filing without cause & 0.72 & 0.00 \\
- & Filing for nonpayment & 0.04 & 0.04 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.93 & 0.01 \\
+ & Filing without cause & 0.73 & 0.90 \\
+ & Filing for nonpayment & 0.42 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.91 & 0.00 \\
- & Plaintiff has attorney & 0.53 & 0.00 \\
- & Defendant is entity & 0.31 & 0.00 \\
- & Plaintiff is entity & 0.01 & 0.02 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.44 & 0.00 \\
+ & Plaintiff has attorney & 0.44 & 0.05 \\
+ & Defendant is entity & 0.09 & 0.03 \\
+ & Plaintiff is entity & 0.28 & 0.00 \\
 \cline{1-4}

### 2023-04-14 output/final_paper/tables/pre_treatment_covariate_tests.tex
combined analysis into one file

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.42 \\
 & Change in Crime Incidents, 2017-2019 & 0.00 & 0.50 \\
\cline{1-4}
\multirow[c]{6}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.73 & 0.81 \\
 & Job density, 2013 & 0.00 & 0.55 \\
 & Median household income, 2016 & 0.00 & 0.01 \\
 & Poverty rate, 2010 & 0.00 & 0.00 \\
 & Population density, 2010 & 0.00 & 0.67 \\
 & share_white2010 & 0.00 & 0.35 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.14 & 0.01 \\
 & Filing without cause & 0.93 & 0.03 \\
 & Filing for nonpayment & 0.02 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.55 & 0.00 \\
 & Plaintiff has attorney & 0.29 & 0.00 \\
 & Defendant is entity & 0.12 & 0.24 \\
 & Plaintiff is entity & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-14 output/final_paper/tables/summary_statistics.tex
combined analysis into one file

\begin{tabular}{llcccc}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in Crime Incidents, 2017-2019 & -152.24 & 217.71 & 1,689 \\
 & Total Crime Incidents, 2017 & 1,164.18 & 714.31 & 1,689 \\
\cline{1-5}
\multirow[c]{6}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.32 & 0.22 & 1,689 \\
 & Job density, 2013 & 16,714.10 & 43,368.36 & 1,689 \\
 & Median household income, 2016 & 46,250.26 & 24,935.09 & 1,689 \\
 & Poverty rate, 2010 & 0.29 & 0.15 & 1,689 \\
 & Population density, 2010 & 23,449.59 & 14,401.77 & 1,689 \\
 & share_white2010 & 0.31 & 0.27 & 1,689 \\
\cline{1-5}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.11 & 0.32 & 1,689 \\
 & Filing without cause & 0.04 & 0.20 & 1,689 \\
 & Filing for nonpayment & 0.76 & 0.43 & 1,689 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.03 & 0.18 & 1,689 \\
 & Plaintiff has attorney & 0.91 & 0.29 & 1,689 \\
 & Defendant is entity & 0.02 & 0.15 & 1,689 \\
 & Plaintiff is entity & 0.84 & 0.36 & 1,689 \\
\cline{1-5}
\multirow[c]{9}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 20.10 & 25.06 & 1,595 \\
 & Judgment by default & 0.46 & 0.50 & 1,689 \\
 & Case dismissed & 0.43 & 0.50 & 1,689 \\
 & Case heard & 0.05 & 0.21 & 1,689 \\
 & Execution issued & 0.30 & 0.46 & 1,689 \\
 & Money judgment & 1,488.32 & 3,429.81 & 1,689 \\
 & Execution levied & 0.06 & 0.24 & 1,689 \\
 & Execution requested & 0.03 & 0.16 & 1,689 \\
 & Execution status unknown & 0.00 & 0.00 & 1,689 \\
\cline{1-5}
\bottomrule
\end{tabular}

### 2023-04-14 src/02_analysis/figure_utilities.py

@@ -19,26 +19,18 @@ import figure_and_table_constants
 import matplotlib.transforms as transforms
 
 def aggregate_by_event_time_and_plot(att_gt,
-                                     output_folder: str,
-                                     filename: str,
                                      start_period: int,
                                      end_period: int,
                                      title: str,
-                                     treatment_month_variable: str,
-                                     df: pd.DataFrame):
+                                     ax: Axes):
     # Get event study-aggregated ATT(t)s.
     results_df = att_gt.aggregate('event')
     results_df = results_df.loc[start_period:end_period]
     results_df.columns = results_df.columns.droplevel().droplevel()
 
     # Plot event study-style plot of ATTs.
-    fig, ax = plt.subplots(layout='constrained')
     x = results_df.index
     y = results_df['ATT']
-    print(y.loc[1:36].min())
-    print(y.loc[1:36].median())
-    print(y.loc[1:36].mean())
-    print(y.loc[1:36].max())
     y_upper = results_df['upper'].where(results_df['upper'].notna(), y)
     y_lower = results_df['lower'].where(results_df['lower'].notna(), y)
     ax.set_ylabel("ATT")
@@ -47,21 +39,27 @@ def aggregate_by_event_time_and_plot(att_gt,
     ax.set_xticks(range(start_period, end_period + 1, 6))
     plot_labeled_vline(ax, x=0, text="Treatment", color='black', linestyle='-',
                                         text_y_location_normalized=0.95)
+
+
     plot_scatter_with_shaded_errors(ax,
                                                      x.values,
                                                      y.values,
                                                      y_upper.values,
                                                      y_lower.values,
                                                      point_color='black',
-                                                     error_color='grey',
+                                                     error_color='white',
                                                      edge_color='grey',
-                                                     edge_style='-',
+                                                     edge_style='--',
                                                      zorder=1)
     plot_labeled_hline(ax, y=0, text="", color='black', linestyle='-', zorder=6)
 
-    plt.show()
-    save_figure_and_close(fig, join(output_folder, filename))
+    # Label graph with average treatment effect across positive relative periods.
+    average_post_treatment_att = att_gt.aggregate('event', overall=True)
+    point_estimate = round(average_post_treatment_att['EventAggregationOverall'].iloc[0, 0], 2)
[…]

### 2023-04-14 src/02_analysis/stats_utilities.py

@@ -23,7 +23,7 @@ def add_missing_indicators(df: pd.DataFrame, missing_variables: List[str], pre_t
     return missing_indicators
 
 
-def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.DataFrame, output_directory: str):
+def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.DataFrame, output_directory: str = None):
     # Store pre-treatment panel names.
     pre_treatment_panels = ['Panel A: Pre-treatment Outcomes',
                             'Panel B: Census Tract Characteristics',
@@ -102,37 +102,39 @@ def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.D
                                                 "Panel B: Census Tract Characteristics": "Panel B",
                                                 "Panel C: Case Initiation": "Panel C",
                                                 "Panel D: Defendant and Plaintiff Characteristics": "Panel D"})
+    if output_directory is not None:
+        # Export to LaTeX.
+        filename = join(output_directory, "balance_table.tex")
+        latex = (balance_table
+                 .rename(index=variable_display_names_dict)
+                 .style
+                 .format(thousands=",",
+                         na_rep='',
+                         formatter={('', 'Cases Won by Plaintiff'): "{:,.2f}",
+                                    ('Difference in Cases Won by Defendant', 'Unweighted'): "{:,.2f}",
+                                    ('Difference in Cases Won by Defendant', '\\emph{p}'): "{:,.2f}",
+                                    ('Difference in Cases Won by Defendant', 'Weighted'): "{:,.2f}",
+                                    ('', 'N'): "{:,.0f}"})
+                 .format_index("\\textit{{{}}}", escape="latex", axis=0, level=0)
+                 .format_index("\\textit{{{}}}", escape="latex", axis=1, level=0)
+                 .to_latex(None,
+                           column_format="llccccc",
+                           hrules=True,
+                           multicol_align='c',
+                           clines="skip-last;data")).replace("{*}", "{.75cm}")
+        latex = latex.split("\\\\\n")
+        latex.insert(1, "\\cline{4-7}\n")
+        latex = "\\\\\n".join(latex)
 
-    # Export to LaTeX.
-    filename = join(output_directory, "balance_table.tex")
-    latex = (balance_table
-             .rename(index=variable_display_names_dict)
-             .style
-             .format(thousands=",",
-                     na_rep='',
[…]

### 2023-04-17 output/final_paper/tables/pre_treatment_covariate_tests.tex
Moved analysis to single file

@@
  & Population density, 2010 & 0.00 & 0.67 \\
- & share_white2010 & 0.00 & 0.35 \\
+ & Share white, 2010 & 0.00 & 0.35 \\
 \cline{1-4}

### 2023-04-17 output/final_paper/tables/summary_statistics.tex
Moved analysis to single file

@@
  & Population density, 2010 & 23,449.59 & 14,401.77 & 1,689 \\
- & share_white2010 & 0.31 & 0.27 & 1,689 \\
+ & Share white, 2010 & 0.31 & 0.27 & 1,689 \\
 \cline{1-5}
@@
 \cline{1-5}
-\multirow[c]{9}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 20.10 & 25.06 & 1,595 \\
+\multirow[c]{5}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 20.10 & 25.06 & 1,595 \\
  & Judgment by default & 0.46 & 0.50 & 1,689 \\
@@
  & Case heard & 0.05 & 0.21 & 1,689 \\
- & Execution issued & 0.30 & 0.46 & 1,689 \\
  & Money judgment & 1,488.32 & 3,429.81 & 1,689 \\
- & Execution levied & 0.06 & 0.24 & 1,689 \\
- & Execution requested & 0.03 & 0.16 & 1,689 \\
- & Execution status unknown & 0.00 & 0.00 & 1,689 \\
 \cline{1-5}

### 2023-04-17 src/02_analysis/constants.py

@@ -1,5 +1,11 @@
 class Variables:
     outcomes = ['group_0_crimes_500m',
                 'group_1_crimes_500m',
-                'group_2_crimes_500m']
+                'group_2_crimes_500m',
+                'group_0_crimes_250m',
+                'group_1_crimes_250m',
+                'group_2_crimes_250m',
+                'group_0_crimes_125m',
+                'group_1_crimes_125m',
+                'group_2_crimes_125m']
 

### 2023-04-17 src/02_analysis/figure_utilities.py

@@ -36,7 +36,7 @@ def aggregate_by_event_time_and_plot(att_gt,
     ax.set_ylabel("ATT")
     ax.set_title(title)
     ax.set_xlabel("Month Relative to Treatment")
-    ax.set_xticks(range(start_period, end_period + 1, 6))
+    ax.set_xticks([-5, 0, 6, 12, 18, 24, 30, 36])
     plot_labeled_vline(ax, x=0, text="Treatment", color='black', linestyle='-',
                                         text_y_location_normalized=0.95)
 
@@ -59,7 +59,7 @@ def aggregate_by_event_time_and_plot(att_gt,
     se = round(average_post_treatment_att['EventAggregationOverall'].iloc[0, 1], 2)
     label = f"Avg.\nPost-Treatment\nATT: {point_estimate}\n(SE: {se})"
 
-    plot_labeled_hline(ax, y=point_estimate, size='x-small', text=label, color='black', linestyle='--', zorder=6, text_x_location_normalized=0.085)
+    plot_labeled_hline(ax, y=point_estimate, size='x-small', text=label, color='black', linestyle='--', zorder=6, text_x_location_normalized=1.085)
 
 def aggregate_by_time_and_plot(att_gt, int_to_month_dictionary: dict, output_folder: str, filename: str, title: str):
     # Get time-aggregated ATTs.

### 2023-04-17 src/02_analysis/run_all_analysis.py

@@ -1,0 +1,691 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# In[2]:
+
+
+import contextily as cx
+import figure_utilities
+import figure_and_table_constants
+import constants
+from stats_utilities import produce_summary_statistics, select_controls, test_balance
+import geopandas as gpd
+import matplotlib.pyplot as plt
+from panel_utilities import get_value_variable_names, prepare_df_for_DiD
+plt.rcParams["figure.dpi"] = 300
+plt.rcParams['savefig.dpi'] = 300
+import os
+from differences import ATTgt, TWFE
+import pandas as pd
+import censusdata
+
+# Store paths.
+INPUT_DATA_PANEL = "../../data/03_cleaned/crime_analysis_monthly.parquet"
+INPUT_DATA_TRACTS = "../../data/02_intermediate/tracts.csv"
+INPUT_DATA_BOSTON_TRACTS_SHAPEFILE = "../../data/01_raw/Census_2010_Tracts"
+
+OUTPUT_TABLES = "../../output/final_paper/tables"
+OUTPUT_FIGURES = "../../output/final_paper/figures"
+
+# Read unrestricted dataset into memory.
+df = pd.read_parquet(INPUT_DATA_PANEL)
+
+# So we can use 'case_number' like a column
+df = df.reset_index()
+
+# Get ACS 1-year estimates for Boston
+boston_data = censusdata.download('acs1', 2015, censusdata.censusgeo([('state', '25'), ('place', '07000')]),
+                                   ['B01001_001E', 'B01001_001M'])
+print(boston_data)
+print(not_a_variable)
+
+# # Summary Statistics
+
+# In[ ]:
+
+
+# Plot evictions spatially.
+unrestricted_gdf = gpd.GeoDataFrame(df,
+                                    geometry=gpd.points_from_xy(df['Longitude'],
+                                                                df['Latitude']))
+unrestricted_gdf = unrestricted_gdf.set_crs("EPSG:4326")
+unrestricted_gdf = unrestricted_gdf.to_crs("EPSG:3857")
+fig, ax = plt.subplots(figsize=(8, 10))
+ax.set_yticklabels([])
+ax.set_yticks([])
+ax.set_xticklabels([])
+ax.set_xticks([])
+unrestricted_gdf.plot(ax=ax,
+                      color='black',
+                      markersize=0.05)
[…]

### 2023-04-17 src/02_analysis/stats_utilities.py

@@ -258,11 +258,10 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     panel_D = pd.concat([panel_D], keys=["Panel D: Defendant and Plaintiff Characteristics"])
 
     # Panel E: Case Resolution
-    panel_E_columns = ['dismissed', 'defaulted', 'heard', 'levied', 'issued', 'requested',
-                       'unknown_execution']
+    panel_E_columns = ['dismissed', 'defaulted', 'heard']
     origin_columns = ['disposition_found', 'disposition_found',
-                      'disposition_found', 'execution', 'execution', 'execution', 'execution']
-    target_values = ["Dismissed", "Defaulted", "Heard", "Levied", "Issued", "Requested", None]
+                      'disposition_found']
+    target_values = ["Dismissed", "Defaulted", "Heard"]
 
     for dummy_column, origin_column, target_value in zip(panel_E_columns, origin_columns, target_values):
         df.loc[:, dummy_column] = np.where(df[origin_column] == target_value, 1, 0)
@@ -309,6 +308,7 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
                                    'job_density_2013': "Job density, 2013",
                                    'med_hhinc2016': "Median household income, 2016",
                                    'poor_share2010': "Poverty rate, 2010",
+                                   'share_white2010': "Share white, 2010",
                                    'popdensity2010': "Population density, 2010",
                                    'for_cause': "Filing for cause",
                                    'no_cause': "Filing without cause",

### 2023-08-01 output/final_paper/tables/pre_treatment_covariate_tests.tex
cleaned up results folder

--- 2023-04-14 output/final_paper/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.42 \\
- & Change in Crime Incidents, 2017-2019 & 0.00 & 0.50 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.42 & 0.40 \\
+ & Change in Crime Incidents, 2017-2019 & 0.00 & 0.01 \\
 \cline{1-4}
-\multirow[c]{6}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.73 & 0.81 \\
+\multirow[c]{6}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.96 & 0.81 \\
  & Job density, 2013 & 0.00 & 0.55 \\
- & Median household income, 2016 & 0.00 & 0.01 \\
- & Poverty rate, 2010 & 0.00 & 0.00 \\
+ & Median household income, 2016 & 0.36 & 0.01 \\
+ & Poverty rate, 2010 & 0.04 & 0.00 \\
  & Population density, 2010 & 0.00 & 0.67 \\
- & share_white2010 & 0.00 & 0.35 \\
+ & Share white, 2010 & 0.05 & 0.35 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.14 & 0.01 \\
- & Filing without cause & 0.93 & 0.03 \\
- & Filing for nonpayment & 0.02 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.94 & 0.01 \\
+ & Filing without cause & 0.30 & 0.03 \\
+ & Filing for nonpayment & 0.28 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.55 & 0.00 \\
- & Plaintiff has attorney & 0.29 & 0.00 \\
- & Defendant is entity & 0.12 & 0.24 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.98 & 0.00 \\
+ & Plaintiff has attorney & 0.16 & 0.00 \\
+ & Defendant is entity & 0.66 & 0.24 \\
  & Plaintiff is entity & 0.00 & 0.00 \\

### 2023-08-02 output/final_paper/tables/pre_treatment_covariate_tests.tex
claned up results

--- 2023-04-14 output/final_paper/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.42 \\
- & Change in Crime Incidents, 2017-2019 & 0.00 & 0.50 \\
+\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.46 \\
+ & Change in Crime Incidents, 2017-2019 & 0.00 & 0.80 \\
 \cline{1-4}
-\multirow[c]{6}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.73 & 0.81 \\
- & Job density, 2013 & 0.00 & 0.55 \\
- & Median household income, 2016 & 0.00 & 0.01 \\
- & Poverty rate, 2010 & 0.00 & 0.00 \\
- & Population density, 2010 & 0.00 & 0.67 \\
- & share_white2010 & 0.00 & 0.35 \\
+\multirow[c]{6}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.31 & 0.82 \\
+ & Job density, 2013 & 0.00 & 0.56 \\
+ & Median household income, 2016 & 0.00 & 0.00 \\
+ & Poverty rate, 2010 & 0.00 & 0.01 \\
+ & Population density, 2010 & 0.00 & 0.50 \\
+ & Share white, 2010 & 0.00 & 0.23 \\
 \cline{1-4}
-\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.14 & 0.01 \\
- & Filing without cause & 0.93 & 0.03 \\
- & Filing for nonpayment & 0.02 & 0.00 \\
+\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.01 & 0.03 \\
+ & Filing without cause & 0.72 & 0.37 \\
+ & Filing for nonpayment & 0.00 & 0.00 \\
 \cline{1-4}
-\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.55 & 0.00 \\
- & Plaintiff has attorney & 0.29 & 0.00 \\
- & Defendant is entity & 0.12 & 0.24 \\
- & Plaintiff is entity & 0.00 & 0.00 \\
+\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.48 & 0.00 \\
+ & Plaintiff has attorney & 0.55 & 0.00 \\
+ & Defendant is entity & 0.22 & 0.32 \\
+ & Plaintiff is entity & 0.03 & 0.00 \\
 \cline{1-4}

### 2023-08-02 output/final_paper/tables/summary_statistics.tex
claned up results

@@
 \midrule
-\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in Crime Incidents, 2017-2019 & -152.24 & 217.71 & 1,689 \\
- & Total Crime Incidents, 2017 & 1,164.18 & 714.31 & 1,689 \\
+\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in Crime Incidents, 2017-2019 & -150.97 & 216.45 & 1,909 \\
+ & Total Crime Incidents, 2017 & 1,164.90 & 717.22 & 1,909 \\
 \cline{1-5}
-\multirow[c]{6}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.32 & 0.22 & 1,689 \\
- & Job density, 2013 & 16,714.10 & 43,368.36 & 1,689 \\
- & Median household income, 2016 & 46,250.26 & 24,935.09 & 1,689 \\
- & Poverty rate, 2010 & 0.29 & 0.15 & 1,689 \\
- & Population density, 2010 & 23,449.59 & 14,401.77 & 1,689 \\
- & Share white, 2010 & 0.31 & 0.27 & 1,689 \\
+\multirow[c]{6}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.32 & 0.22 & 1,909 \\
+ & Job density, 2013 & 16,845.17 & 44,087.24 & 1,909 \\
+ & Median household income, 2016 & 46,653.89 & 24,977.84 & 1,909 \\
+ & Poverty rate, 2010 & 0.29 & 0.15 & 1,909 \\
+ & Population density, 2010 & 23,451.78 & 14,298.74 & 1,909 \\
+ & Share white, 2010 & 0.31 & 0.27 & 1,909 \\
 \cline{1-5}
-\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.11 & 0.32 & 1,689 \\
- & Filing without cause & 0.04 & 0.20 & 1,689 \\
- & Filing for nonpayment & 0.76 & 0.43 & 1,689 \\
+\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.13 & 0.34 & 1,909 \\
+ & Filing without cause & 0.05 & 0.22 & 1,909 \\
+ & Filing for nonpayment & 0.74 & 0.44 & 1,909 \\
 \cline{1-5}
-\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.03 & 0.18 & 1,689 \\
- & Plaintiff has attorney & 0.91 & 0.29 & 1,689 \\
- & Defendant is entity & 0.02 & 0.15 & 1,689 \\
- & Plaintiff is entity & 0.84 & 0.36 & 1,689 \\
+\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.05 & 0.22 & 1,909 \\
+ & Plaintiff has attorney & 0.91 & 0.29 & 1,909 \\
+ & Defendant is entity & 0.02 & 0.15 & 1,909 \\
+ & Plaintiff is entity & 0.83 & 0.38 & 1,909 \\
 \cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 20.10 & 25.06 & 1,595 \\
- & Judgment by default & 0.46 & 0.50 & 1,689 \\
- & Case dismissed & 0.43 & 0.50 & 1,689 \\
- & Case heard & 0.05 & 0.21 & 1,689 \\
- & Money judgment & 1,488.32 & 3,429.81 & 1,689 \\
+\multirow[c]{5}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 41.75 & 81.98 & 1,814 \\
+ & Judgment by default & 0.46 & 0.50 & 1,909 \\
+ & Case dismissed & 0.44 & 0.50 & 1,909 \\
+ & Case heard & 0.05 & 0.22 & 1,909 \\
+ & Money judgment & 1,748.60 & 4,708.19 & 1,909 \\
 \cline{1-5}

### 2023-08-02 src/02_analysis/stats_utilities.py

@@ -271,8 +271,8 @@ def produce_summary_statistics(df: pd.DataFrame, treatment_date_variable: str):
     for i in range(start, stop + 1):
         for outcome in outcomes:
             # This column contains the year-month which is i years relative to treatment for each property.
-            offset_docket_month = (df[treatment_date_variable] + pd.tseries.offsets.DateOffset(years=i)) \
-                                      .dt.strftime('%Y-%m').copy() + "_" + outcome
+            offset_docket_month = pd.to_datetime(df.loc[:, treatment_date_variable] +
+                                                 pd.tseries.offsets.DateOffset(years=i)).dt.strftime('%Y-%m').copy() + "_" + outcome
 
             # Some year-months will be outside the range of our data.
             # For instance, we do not have outcomes 2 years post-treatment for evictions which occurred in 2022.

### 2023-08-07 output/final_paper/tables/summary_statistics.tex
moved variable generation into merge script

--- 2023-04-17 output/final_paper/tables/summary_statistics.tex
@@
 \midrule
-\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in Crime Incidents, 2017-2019 & -152.24 & 217.71 & 1,689 \\
- & Total Crime Incidents, 2017 & 1,164.18 & 714.31 & 1,689 \\
+\multirow[c]{3}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in Crime Incidents, 2017-2019 & -43.28 & 117.45 & 1,689 \\
+ & relative_pre_treatment_change_in_group_0_crimes_250m & -3.93 & 26.59 & 1,689 \\
+ & Total Crime Incidents, 2017 & 342.76 & 256.18 & 1,689 \\
 \cline{1-5}
@@
 \cline{1-5}
-\multirow[c]{5}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 20.10 & 25.06 & 1,595 \\
+\multirow[c]{7}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 20.10 & 25.06 & 1,595 \\
+ & Case duration & 20.10 & 25.06 & 1,595 \\
  & Judgment by default & 0.46 & 0.50 & 1,689 \\
@@
  & Money judgment & 1,488.32 & 3,429.81 & 1,689 \\
+ & Money judgment & 1,488.32 & 3,429.81 & 1,689 \\
 \cline{1-5}

### 2023-08-07 src/constants.py

@@ -9,7 +9,10 @@ class Variables:
                 'group_1_crimes_125m',
                 'group_2_crimes_125m']
 
-
+class Analysis:
+    MAIN_RESULTS_RADIUS = 250
+    MINIMUM_PRE_PERIOD = -12
+    MAXIMUM_POST_PERIOD = 36
 class Colors:
     P1 = "#29B6A4"
     P2 = "#FAA523"

### 2023-08-07 src/panel_utilities.py

@@ -1,0 +1,57 @@
+import pandas as pd
+from sklearn.preprocessing import StandardScaler
+import numpy as np
+from constants import Variables
+from typing import List, Union
+
+
+def get_value_variable_names(df, analysis: str):
+    all_columns = pd.Series(df.columns)  # Create Series containing all columns.
+    value_columns = all_columns[all_columns.str.contains(analysis)]  # Create Series containing only value var. names.
+    value_columns = pd.Series(value_columns.sort_values().reset_index(drop=True))  # Sort and reset index.
+    non_value_variable_strings = [f"pre_treatment_change_in_{analysis}", f"total_twenty_seventeen_{analysis}",
+                                  f"relative_pre_treatment_change_in_{analysis}", f"total_twenty_nineteen_{analysis}"]
+    value_columns = value_columns.loc[~value_columns.isin(non_value_variable_strings)]
+    int_to_period_dictionary = value_columns.str.replace(f"_{analysis}", "", regex=False).to_dict()
+    period_to_int_dictionary = {v: k for k, v in list(int_to_period_dictionary.items())}
+    return value_columns.tolist(), period_to_int_dictionary, int_to_period_dictionary
+
+def prepare_df_for_DiD(df: pd.DataFrame, analysis: str, treatment_date_variable: str,
+                       pre_treatment_covariates: List[str],
+                       missing_indicators: List[str],
+                       value_vars: List[str],
+                       period_to_int_dictionary):
+    if analysis not in Variables.outcomes:
+        raise ValueError("Unrecognized argument for parameter analysis.")
+
+    # Add latest docket date dummies
+    latest_docket_month_dummies = pd.get_dummies(df['latest_docket_month'],
+                                                 drop_first=True)
+    df = pd.concat([df, latest_docket_month_dummies], axis=1)
+    [pre_treatment_covariates.append(col) for col in latest_docket_month_dummies.columns]
+    
+    # Reshape from wide to long.
+    df = pd.melt(df,
+                 id_vars=['case_number', treatment_date_variable, 'judgment_for_plaintiff'] + pre_treatment_covariates,
+                 value_vars=value_vars, var_name='month', value_name=analysis)
+    df = df.sort_values(by=['case_number', 'month'])
+
+    # Standardize control variables.
+    [pre_treatment_covariates.remove(missing_indicator) for missing_indicator in missing_indicators]
[…]

### 2023-08-07 src/stats_utilities.py

@@ -8,27 +8,12 @@ import numpy as np
 import pandas as pd
 import statsmodels.formula.api as smf
 import figure_utilities
-from constants import Variables
+import constants
 from differences.did.pscore_cal import pscore_mle
 from typing import List
 
 
-
-
-
-
-
-
-def add_missing_indicators(df: pd.DataFrame, missing_variables: List[str], pre_treatment_covariates: List[str]):
-    missing_indicators = []
-    for missing_variable in missing_variables:
-        df.loc[:, missing_variable] = df[missing_variable].fillna(0)
-        df.loc[:, missing_variable + '_missing'] = np.where(df['rent_twobed2015'] == 0, 1, 0)
-        pre_treatment_covariates.append(missing_variable + '_missing')
-        missing_indicators.append(missing_variable + '_missing')
-    return missing_indicators
-
-def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.DataFrame, output_directory: str):
+def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.DataFrame, output_directory: str = None):
     # Store pre-treatment panel names.
     pre_treatment_panels = ['Panel A: Pre-treatment Outcomes',
                             'Panel B: Census Tract Characteristics',
@@ -44,7 +29,7 @@ def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.D
         df.copy().loc[df['judgment_for_plaintiff'] == 1, :], 'latest_docket_date')
     treatment_means = treatment_means.loc[pre_treatment_panels, :]
     # Do not include rows corresponding to other outcomes in the covariate exploration table.
-    outcomes = Variables.outcomes.copy()  # Create list of all outcomes.
+    outcomes = constants.Variables.outcomes.copy()  # Create list of all outcomes.
     outcomes.remove(analysis)  # Remove the one which is being currently studied.
     unneeded_outcomes = outcomes
     for unneeded_outcome in unneeded_outcomes:  # For each outcome not currently being studied...
@@ -107,42 +92,45 @@ def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.D
                                                 "Panel B: Census Tract Characteristics": "Panel B",
                                                 "Panel C: Case Initiation": "Panel C",
                                                 "Panel D: Defendant and Plaintiff Characteristics": "Panel D"})
+    if output_directory is not None:
+        # Export to LaTeX.
[…]

### 2023-08-07 output/final_paper/tables/pre_treatment_covariate_tests.tex
moved main results to own doc

--- 2023-08-01 output/final_paper/tables/pre_treatment_covariate_tests.tex
@@
 \midrule
-\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.42 & 0.40 \\
+\multirow[c]{3}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.42 & 0.40 \\
  & Change in Crime Incidents, 2017-2019 & 0.00 & 0.01 \\
+ & relative_pre_treatment_change_in_group_0_crimes_250m & 0.00 & 0.20 \\
 \cline{1-4}

### 2023-08-07 src/stats_utilities.py

@@ -36,8 +36,9 @@ def test_balance(df: pd.DataFrame, analysis: str, covariate_exploration_df: pd.D
         # Drop related variables from the summary statistics table.
         treatment_means = treatment_means.drop(f'total_twenty_seventeen_{unneeded_outcome}', level=1, axis=0)
         treatment_means = treatment_means.drop(f'pre_treatment_change_in_{unneeded_outcome}', level=1, axis=0)
+        treatment_means = treatment_means.drop(f'relative_pre_treatment_change_in_{unneeded_outcome}', level=1, axis=0)
 
-    treatment_means = (treatment_means.loc[predicts_outcome_mask, 'mean']
+    treatment_means = (treatment_means.loc[:, 'mean']
                        .rename("Cases Won by Plaintiff"))
     # Save pre-treatment covariates for use in D.R. DiD estimator.
     pre_treatment_covariates = treatment_means.index.get_level_values(1).tolist()
@@ -137,6 +138,7 @@ def select_controls(df: pd.DataFrame, treatment_date_variable: str, analysis: st
         # Drop related variables from the summary statistics table.
         summary_statistics = summary_statistics.drop(f'total_twenty_seventeen_{unneeded_outcome}', level=1, axis=0)
         summary_statistics = summary_statistics.drop(f'pre_treatment_change_in_{unneeded_outcome}', level=1, axis=0)
+        summary_statistics = summary_statistics.drop(f'relative_pre_treatment_change_in_{unneeded_outcome}', level=1, axis=0)
 
     # Store independent and dependent variables.
     independent_variable = 'judgment_for_plaintiff'

### 2023-09-14 output/pre_treatment_covariate_tests.tex

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Crime Incidents Within 100m, Oct. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & All crimes, 2019-01 & 0.00 & 0.08 \\
 & $\Delta$ crimes, 2017-2019 & 0.00 & 0.87 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac\_coll\_plus2010 & 0.00 & 0.78 \\
 & job\_density\_2013 & 0.00 & 0.52 \\
 & med\_hhinc2016 & 0.01 & 0.12 \\
 & poor\_share2010 & 0.57 & 0.53 \\
 & popdensity2010 & 0.00 & 0.01 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for\_cause & 0.06 & 0.00 \\
 & no\_cause & 0.00 & 0.90 \\
 & non\_payment & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.44 & 0.00 \\
 & hasAttyP & 0.01 & 0.00 \\
 & isEntityD & 0.00 & 0.01 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-09-14 output/summary_statistics.tex

\begin{tabular}{llcccc}
\toprule
 &  & Mean & Median & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{6}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in all crimes, 2017-2019 & -0.54 & 0.00 & 4.26 & 6,060 \\
 & Change in assaults, 2017-2019 & 0.01 & 0.00 & 1.00 & 6,060 \\
 & Change in investigations, 2017-2019 & 0.05 & 0.00 & 1.04 & 6,060 \\
 & All crimes, 2019-01 & 5.16 & 4.00 & 5.77 & 6,060 \\
 & Assault crimes, 2019-01 & 0.41 & 0.00 & 0.80 & 6,060 \\
 & Investigations, 2019-01 & 0.45 & 0.00 & 0.82 & 6,060 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & frac\_coll\_plus2010 & 0.31 & 0.24 & 0.22 & 6,060 \\
 & job\_density\_2013 & 14,806.08 & 2,425.15 & 40,595.37 & 6,060 \\
 & med\_hhinc2016 & 47,188.87 & 41,146.00 & 24,703.65 & 6,060 \\
 & poor\_share2010 & 0.28 & 0.25 & 0.14 & 6,060 \\
 & popdensity2010 & 22,704.52 & 20,644.44 & 13,091.45 & 6,060 \\
\cline{1-6}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & for\_cause & 0.17 & 0.00 & 0.37 & 6,060 \\
 & no\_cause & 0.05 & 0.00 & 0.22 & 6,060 \\
 & non\_payment & 0.78 & 1.00 & 0.42 & 6,060 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.08 & 0.00 & 0.27 & 6,060 \\
 & hasAttyP & 0.88 & 1.00 & 0.32 & 6,060 \\
 & isEntityD & 0.02 & 0.00 & 0.14 & 6,060 \\
 & isEntityP & 0.81 & 1.00 & 0.39 & 6,060 \\
\cline{1-6}
\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & case\_duration & 58.17 & 19.00 & 88.96 & 5,500 \\
 & defaulted & 0.19 & 0.00 & 0.39 & 6,060 \\
 & dismissed & 0.27 & 0.00 & 0.44 & 6,060 \\
 & heard & 0.03 & 0.00 & 0.17 & 6,060 \\
 & judgment & 1,938.57 & 0.00 & 5,337.87 & 6,060 \\
 & mediated & 0.40 & 0.00 & 0.49 & 6,060 \\
\cline{1-6}
\bottomrule
\end{tabular}
